### 2021-11-19 Manuscript/main.tex
Started work on Manuscript

\documentclass[12pt]{article} % use larger type; default would be 10pt

\usepackage[utf8]{inputenc} % set input encoding (not needed with XeLaTeX)
%%% Examples of Article customizations
% These packages are optional, depending whether you want the features they provide.
% See the LaTeX Companion or other references for full information.

%%% PAGE DIMENSIONS
\usepackage{geometry} % to change the page dimensions
 \geometry{margin=1in} % for example, change the margins to 2 inches all round
% \geometry{landscape} % set up the page for landscape
%   read geometry.pdf for detailed page layout information

\usepackage{graphicx} % support the \includegraphics command and options

% \usepackage[parfill]{parskip} % Activate to begin paragraphs with an empty line rather than an indent

%%% PACKAGES
\usepackage{booktabs} % for much better looking tables
\usepackage{array} % for better arrays (eg matrices) in maths
\usepackage{paralist} % very flexible & customizable lists (eg. enumerate/itemize, etc.)
\usepackage{verbatim} % adds environment for commenting out blocks of text & for better verbatim
\usepackage{subfig} % make it possible to include more than one captioned figure/table in a single float
\usepackage[round]{natbib} % Natural science bibliography package
\usepackage{pdflscape} %Landscape pages
\usepackage{amsmath} %Mathematics 
\usepackage{hyperref} %URLs and Hyperlinks
\hypersetup{hidelinks=true} %Turns off coloured links
\usepackage{longtable} %Multi-page tables
\usepackage{multirow} %Better tables
\usepackage{marvosym} %Male/female/hermaphrodite symbols
\usepackage{caption} %Add captions to non-floats
\usepackage{calc} %Simple arithmetic for arguments
\usepackage{ifthen} %Allows if-then statements
\usepackage[breakable]{tcolorbox} %Allows boxes to be made, and allows boxes to be breakable
\usepackage{capt-of} %Allows captions outside of float environments
\usepackage{setspace} %Double/1.5 spacing

%%% HEADERS & FOOTERS
%\usepackage{fancyhdr} % This should be set AFTER setting up the page geometry
%\pagestyle{fancy} % options: empty , plain , fancy
%\renewcommand{\headrulewidth}{0pt} % customise the layout...
%\lhead{}\chead{}\rhead{}
%\lfoot{}\cfoot{\thepage}\rfoot{}

%Function to create equation sets with captions. From:
%https://tex.stackexchange.com/questions/172452/caption-for-align-environment

%\newcounter{captionedequationset} %numbering
%\newdimen\captionlength
%\newcommand{\captionedequationset}[1]{
%    \refstepcounter{captionedequationset}% Step counter
%    \setlength{\captionlength}{\widthof{#1}} %
%    \addtolength{\captionlength}{\widthof{Equation set~\thecaptionedequationset: }}
%    %If the caption is shorter than the line width then
%    % the caption is centred, otherwise is flushed left.
%    \ifthenelse{\lengthtest{\captionlength < \linewidth }} %
%    {\begin{center}
%            Equation set~\thecaptionedequationset: #1
%        \end{center}} 
%    { \begin{flushleft} 
%        Equation set~\thecaptionedequationset: #1 %
%        \end{flushleft}}
%}

%%% SECTION TITLE APPEARANCE
\usepackage{sectsty}
\allsectionsfont{\sffamily\mdseries\upshape} % (See the fntguide.pdf for font help)
% (This matches ConTeXt defaults)

%%% END Article customizations

%%% The "real" document content comes below...

\title{Bee visitation, pollination services, and plant yield in commodity and hybrid seed canola} 
\author{Samuel Robinson, Ralph Cartar, Stephen Pernal, Riley Waytes, Shelley Hoover}
% \author{Samuel Robinson}

\date{}

\begin{document}
\maketitle
\doublespacing

\begin{abstract}
Insect-mediated pollination of crops is an important input to agricultural production, but pollination management suffers from key mechanistic gaps that hinder its greater utility. 
While pollination services to plants have a solid theoretical and mechanistic framework, agricultural pollination is often treated as a statistical ``black box", without reference to the mechanisms underlying the process of pollination and fruit production.
We present a causal model that links insect visitation to pollination to three separate components of yield, using two types of canola (\textit{Brassica napus}) production systems.
%Visitation by honey bees was strongly related to distance in both commodity and seed canola fields, with visitation decreasing with distance away from the edge of the field (where the hives were located).
%In seed fields, leafcutter bee visitation strongly decreased with distance away from their shelter, but interestingly, also decreased with distance from the edge of the field in high-density shelters, meaning that foragers may be migrating from shelters at the centre of the field to shelters at the edge.
Commodity canola yield was mainly controlled by plant size, and there was no relationship between \textit{Apis mellifera} visitation and pollen deposition, or deposition and seed yield.
In comparison, seed canola yield was also controlled by plant size, but there was also a strong relationship between visitation and pollen deposition, as well as deposition and seed yield.
We also found that \textit{Megachile rotundata} visitation in seed canola strongly increased pollen deposition, but \textit{A. mellifera} visitation did not.
This model serves as a step towards a mechanistic model of pollination services, and points to the contextual importance of pollination services in seed canola production.

\end{abstract}

% Current Intro Structure:
% - Animal pollination = important ecosystem service
%     - NEEDS LEAD-IN TO OTHER PARAGRAPHS
% - Insect visitation can increase fruit production via better pollen deposition
% - Size and number of seeds matured depends on availability of plant resources
% - Trade-offs exist at plant and flower level
% - Pollination is important in canola production
% - Insect pollination can increase yields of commercial canola crops 
% - Fruit production in flowering plants involves a sequence of processes
%     - SEMs are convenient for modeling this
% - In this study, We modeled how distance influences pollinator visitation, which in turn influences ...
%     - List of 5 hypotheses

% Current Discussion structure
% * Visitation
% - Honey bee visitation in seed fields was much higher than commercial fields
% - Hbee decline into field expected, Lbee decline surprising
% - Hbee visitation lower near to leafcutter shelters
%     - Which is causing which?
% * Pollen deposition
% - Hbees don't influence pollen in commodity fields
% - In seed fields, lbees influence pollen, but not hbees
% - Why did honey bees have so little influence on pollen deposition in both commodity and seed canola fields?
% - Any positive pollination effect of honey bees in hybrid seed fields is likely indirect
% * Pod production
% - Commodity field pod production mainly controlled by plant size, not pollen
% - Seed field pod production influenced by plant size & pollen
% * Seed size/number
% - Seed canola size not altered by pollen, but negative relationship b/w seeds per pod & seed size
% - Number of seeds per pod not altered except by year
% * Summary
% - Why no effect of insect pollination in commodity?
% - Implications for pollination management

% WHAT IS MY MAIN STORY?
% Q: What is the relative contribution of bees to seed yield in canola? Do they matter relative to plant resources?
% A: Plant size is the main driver of yield. Leafcutter bees increase pollen deposition and yield, but honey bees do not.
% Hook:
% Bee visitation can enhance seed production in crop plants, but only if pollen deposition is limited and plant resources are available.
% We found that while commodity canola is not pollen-limited, hybrid seed canola is, and while leafcutter bees increase pollen deposition, honey bees do not.

% WHAT DOES THE READER NEED TO KNOW?

%Journals to consider (Impact Factor):
% Behavioural Ecology (2.8): no page limit specified - I think this would be the best at this point
% Ecological Modeling (2.5): no page limit specified
% Ecology Letters (8.6): max 5000 words, 6 figures/tables
% Journal of Applied Ecology (5.8): 7500 words, including refs and caption
% Journal of Animal Ecology (4.6): 8500 words, including refs and captions
% Oikos (3.4): no page limit specified
% Oecologia (2.7): 10 printed pages (~35 submitted pages), 100 Euros per extra page

\section{Introduction}
%SH: PARAGRAPH COULD BE REMOVED/SHORTENED FOR PAPER, BUT FINE FOR THESIS
Animal pollination of agricultural flowering plants is an important ecosystem service that contributes to about 10\% of total crop production value worldwide \citep{gallai2009}, and animal-pollinated plants produce a large number of important micronutrients in the human diet \citep{eilers2011}.
Therefore, understanding the process of animal pollination in crops is economically and ecologically important. %REWORD? ECONOMICS DOESN'T COME INTO THE THESIS, SO MAYBE DON'T MENTION IT? 
Agricultural pollination, however, is largely treated as a single process, even though there are many links in the chain of events that result in the production of a fruit.
Visitation of flowers by animals, typically bees and other insects, can result in pollen deposition on the stigma of the flower, followed by the growth of pollen tubes into the style and fertilization of ovules \citep{erbar2003}. 
After fertilization, the plant may provide resources to fertilized fruits (or ovules within a fruit) to mature them into fruit \citep{goldberg1994}.
Each step has many other underlying processes (\textit{e.g.} stigma receptivity, pollen tube growth, ovule abortion, fruit maturation, reviewed in \citealp{real1983, giovannoni2001, erbar2003, takayama2005}, and others), but even at the level of this coarse approximation, most studies of agricultural pollination fail to account for important underlying processes.
Pollinating animals rarely visit equally on all flowers in a blooming crop field\citep{currie1997, brosi2008, isaacs2010}, but some agronomic studies implicitly make this assumption \citep{phillips1989, bommarco2012, bartomeus2014}. 
Pollen deposition from visitors depends on a number of factors (\textit{e.g} behaviour on flowers, size of pollinator), and whether this deposited pollen from visitors results in increased fruit production depends on the pollination context (\textit{e.g.} self-pollination) and the life history and resource contexts of the plant (\textit{e.g.} annual vs. perennial, determinate vs. indeterminate growth, light, soil nutrients and moisture).
Moving beyond the ``black-box" model of agricultural pollination requires accounting for these steps, and is necessary for understanding the contextual value of pollination services, as well as optimizing crop yield in novel circumstances.
%affect roughly one-third of the world's agricultural crops \citep{klein2007}

Pollinator visitation is not spatially uniform within fields, as most pollinators are central-place foragers, meaning that visitation rates decline with distance away from their nest, and the bloom of flowering crops is not uniform. %REWORD
Smaller bees fly shorter distances than larger bees \citep{greenleaf2007,zurbuchen2010}, so their presence at the centre of large fields can be limited \citep{isaacs2010}. 
Hence, managing the location and density of managed pollinators in relation to their target crops is important for optimal yield of pollinator-dependent crops \citep{fries1983,cresswell2004b}.
Foraging insects will often specialize on certain species or morphs of flowers in order to forage more efficiently \citep{heinrich1976b, goulson1997}. 
However, pollination of hybrid seed crops requires movement of pollen between spatially separated lines of plants, so floral specialization can reduce the pollination services in these systems \citep{waytesMsc, gaffney2019}.
Competition between different species of foraging insects can occur if they deplete floral resources, but foragers can spatially or temporally separate their foraging to reduce competition (\citealp{schaffer1979,thomson1987}, but see \citealp{steffan2000}), thereby increasing their fitness. 
Both resource depletion or interference competition can motivate visitors to reduce competition by increasing their foraging distance, switching between floral morphs more often, or visiting less frequently \citep{heinrich1979, greenleaf2006}.
Thus, variation in visitation is driven by both distance from their nest (see Chapter 2), as well as competition with foragers from other aggregations, and increased competition can benefit plant fitness.
% Much of the worldwide agricultural demand for insect pollination is accomplished by the European honey bee, (\textit{Apis mellifera} L., hereafter ``honey bee") because of its large colony size, ease of transport, and ease of breeding (\citealp{winston1991}, but see also \citealp{winfree2008}).
% However, several other types of pollinators are commonly used, including the alfalfa leafcutting bee, (\textit{Megachile rotundata} F., hereafter ``leafcutter bee"; \citealp{pitts2011}), and a large variety of wild pollinators \citep{rader2015}.

Insect visitation of flowers can enhance fruit production in flowering plants by increasing either the quantity or quality of pollen deposited on the stigma \citep{stephenson1981,burd1994,aizen2007}, providing a larger range of female mate choice for each flower.
Many flowering plant species are capable of self-pollination, but typically produce more fruit or seeds from outcrossed pollen \citep{knight2005} transported from conspecific plants by wind or an animal vector, but not all animal visitors are equal from a flowering plant's perspective.
For example, large-bodied insects can deposit more pollen per visit on the stigma of the flower because they have a greater chance of contacting the stigmatic surface \citep{sahli2007}. 
Pollinator behaviour is also important, as flower-visiting insects may steal nectar, clean off pollen between visits, or travel mainly between flowers on the same plant \citep{thomson1986, herrera1987}.
Finally, the benefit of extra pollen deposition is diminishing \citep{plowright1981}, with very high numbers of pollen grains causing less and less of an increase in fruit production \citep{ashman2004, harder2016}.
%; some are obligate outcrossers, and have self-incompatibility mechanisms in place to prevent fertilization by their own pollen.
% Other plants have separate male and female flowers, or separate male and female plants, so their pollen must be transported from male flowers to female flowers, either by wind or an animal vector.

%REVIEW LANGUAGE
%RC: POINT OF PARAGRAPH SHOULD BE THAT AFTER POLLEN RECEIPT, PLANT STILL HAS TO DECIDE WHETHER TO ACCEPT IT, OR WAIT TO INVEST LATER (FUTURE-PRESENT TRADEOFFS)
%RALPH'S ARGUMENT IS WAY TOO GENERAL. POINT SHOULD BE THAT POLLEN OR RESOURCES CAN BE LIMITING (USUALLY RESOURCES), AND THAT PLANT MAY COMPENSATE FOR LOW POLLEN USING EXTRA GROWTH
Seed production can be limited by plant resources as well as pollen \citep{galen1985, haig1988,campbell1993}, meaning that the benefits of insect pollination depend on the resources available to the plant \citep{stephenson1981, tamburini2017}.
Pollen limitation can also occur at multiple levels within a plant, reducing the number of seeds per fruit, the number of mature fruit, or both \citep{burd1994}.
Low pollen deposition may reduce the number of mature fruit via flower abortion \citep{knight2006}, where poorly-pollinated flowers are cut off from the plant.
Plants with an indeterminate growth strategy may compensate for a high flower abortion rate by simply making more flowers, resulting in similar seed production to pollinated plants \citep{doust1982,lawrence1993, sabbahi2006, bos2007}.
Whether individual plants can compensate for low pollination depends on the time remaining in the season, as well as the resources available to create extra shoots and flowers.
Pollen limitation may also reduce the number of seeds per fruit, so additional pollen may result in a greater number of seeds per fruit \citep{knight2006}, which in turn may result in a reduction in the size per seed \citep{free1968, mazer1987} due to competition between ovules.
Seed size can vary strongly among plants, and can be affected by resources available to the plant \citep{mazer1987, venable1992}. 
For example, \citet{maddox1983} observed a negative size-number tradeoff in \emph{Plantago} seeds, but only after accounting for the positive effect of plant size, indicating that larger plants were better able to provision their seeds.
Since the size and number of offspring are direct determinants of a given plant's fitness, and the yield of the plant in an agricultural setting, allocation strategies that plants use under situations of pollen or resource deficits are important both theoretically, and in the context of food production \citep{bos2007, tamburini2019}. 
%, as the optimum seed size may differ depending on the growing conditions \citep{silvertown1989}.
%Na\"{i}vely, we may expect a size-number tradeoff to result in a single optimal seed size regardless of plant size \citep{smith1974}, but 
%\citep{galen1985} showed that \emph{Clintonia borealis} produced a greater number of larger seeds when supplemented with outcrossed pollen, but only when competing fruits on the stem were removed.
%However, plants may produce more seeds of the same size (\citealp{smith1974}, but see \citealp{venable1992}), or may be limited by the number of ovules per flower \citep{wang2011}.
%Alternatively, they can abort fertilized fruit to re-direct resources to higher-quality pods if too many flowers are fertilized \citep{stephenson1981}.
%Commonly recognized in ecology, but less so in agronomy
%understanding how plants allocate resources in situations of limited pollen deficit and pollen increase
%understanding how pollen deficits change in the context of resource availability,

Insect pollination is especially important in the production of hybrid canola crops (\textit{Brassica napus} L.).
Hybrid ``commodity canola" (used for oil and meal production) is the offspring of two parental ``seed canola" breeding lines, a male-sterile ``female" line and a hermaphroditic  ``male" line \citep{westcott2001,steffan2003,clay2009}. 
Seed canola production requires a large number of pollinators to ensure pollination of the female line (seed from the male line is not harvested), and extra pollination may also increase the yield of commodity canola \citep{morandin2005,rader_phd,bommarco2012,bartomeus2015,perrot2018}. 
However, many studies of commodity canola pollination suffer from either a lack of realistic context, have a number of potential confounding variables, or infer plant-level outcomes from flower-level treatments. 
Greenhouse experiments typically involve unrealistically high pollination, nutrient availability, and water, all of which can influence yield \citep{bartomeus2015,marini2015}.
Field studies often relate yield to indirect measures of pollination services, such as insect abundance, species richness, or distance from sources of potential pollinators \citep{morandin2005,ricketts2008}, rather than direct measures, such as visitation rates or pollen deposition per stigma.
These pollination proxies are then related to measures of yield, such as grams of seed per m$^2$, which may be useful to growers, but provide limited information about how plants dynamically respond to pollen exclusion or addition (but see \citealp{sabbahi2005}).
Net- or cage-treatments exclude insect vistiation from certain plants or flowers, but can alter wind pollination, humidity, light, or pest pressure \citep{olsson1960, neal2004, jauker2008}, meaning that the sole effect of lower insect visitation is confounded by other factors.
These methods offer an incomplete picture of how pollination relates to yield in canola crops \citep{ouvrard2019}, and obscure estimates of pollinator value in a globally valuable crop species \citep{melathopoulos2015}. 
Thus, whether pollination impacts commodity canola production (or if not, why not) is poorly understood.
%and both honey bees and leafcutter bees are used in Canada 
%depending on the variety \citep{hudewenz2013, lindstrom2016}, 
%has hermaphroditic flowers and 
% typically has higher yields than non-hybrid (``traditional") varieties due to heterosis, as it
%  Cross-pollination of two parental lines results in seeds produced by the female line that are used for growing hybrid ``commodity canola",
%, with honey bee hives being placed at the field edge, whereas leafcutter bee shelters are dispersed within the field.
% In Canada, hybrid canola (``commercial canola") was planted across 20.7 million ha of farmland in 2016 (roughly equivalent to the area of the United Kingdom), and contributed C\$26.7 billion to the Canadian economy \citep{statscan_canolaArea2019, CCC_economy2016}.
% As of 2010, 93\% of this canola was transgenic, herbicide-tolerant canola, with transgenic traits encoding for glyphosate or glufocinate resistance in approximately equal proportions \citep{ccc2010}. 
% The ``male" breeding line has both anthers and stigmas (hermaphroditic), but carries a nuclear fertility-restoring trait, meaning that the offspring they sire on the female line will have their anther production restored.

Fruit production in plants involves a sequence of processes (visitation $\rightarrow$ pollen deposition $\rightarrow$ fruit production $\leftarrow$ plant resources), that determine the magnitude of the link between pollination and the components of crop yield.
However, most studies of how pollination relates to crop yield either examine each process independently, or omit intermediate steps in the sequence of events (but see \citealp{saez2018}), meaning that the relative importance of visitation and plant resources are unresolved.
Structural equation models (SEM) provide a framework for empirical analysis of this sequence, as they allow underlying causal assumptions to be formally stated and tested \citep{shipley2009, grace2012}, provide insight into alternative mechanisms that may be at play, and are flexible in many of their assumptions \citep{clough2012}.
SEMs represent an intermediate class of statistical models, occupying a space somewhere between regression-style models and dynamic or agent-based models, making them ideal for generating and testing sets of mechanistic hypotheses \citep{grace2006, kline2013}. 
Using both commodity and seed canola provides an opportunity to compare two plant varieties that differ strongly in their pollination requirements, using a similar type of structural model, while accounting for agricultural differences between varieties (spatial arrangement, planting density, irrigation).
% Since the process linking insect visitation to seed production has several intermediate steps, and is contingent on resource factors, we need a more complete model of crop yield that links plant-level responses to biological processes that occur at the plot and field level.
%Introduce each component of the path analysis

%SH: SEEMS ODD TO HAVE REFS MIXED IN WITH YOUR HYPOTHESES
In this study, we modeled how distance influences pollinator visitation, which in turn influences pollen deposition and seed yield, using commodity and hybrid seed canola crops in Alberta, Canada.
Our five main hypotheses are outlined as follows:
\begin{enumerate} 
    \item Foraging honey bees and leafcutter bees are sensitive to distance due to cost of flight \citep{schmid1985}, and deplete floral resources with visitation. Therefore, insect visitation should decline with distance from their hive or shelter to achieve equivalent rewards \citep{dukas1998, cresswell2000}. 
    \item Visiting bees can deposit pollen on stigmas, so areas with high rates visitation should have more pollen deposition on stigmas than areas with low rates of visitation \citep{mesquida1988c, hoyle2007}, depending on foraging behaviour of the bee \citep{free1983}.
    % \item Plant size is limited by resources, which can be reduced by competition with neighbours, so areas with fewer plants per m$^2$ should have larger plants \citep{angadi2003}. %Not revelvant
    \item Seed production for a given plant is limited by the resources it is able to sequester. Therefore, large plants should have more resources at their disposal, and should produce more fruit per plant and produce a higher number of larger seeds per fruit \citep{galen1985, lawrence1993, marini2015}.
    \item Seed production in resource-rich plants is also limited by pollination. Plants in areas with high pollen deposition should have a higher proportion of successful flowers \citep{sabbahi2005}, and a higher number of seeds per pod \citep{morandin2005}.
\end{enumerate}

%REVIEW
This study assesses the strength of the connections between visitation, pollination, and yield, in a globally important crop species, and identifies the relative importance of bee pollination for seed production, using in-field data from two distinct cropping systems.
Other studies of crop pollination focus on individual components, such as visitation and pollination \citep{cresswell1999, thomson2001}, or visitation and yield \citep{steffan2003, manning2005, hudewenz2013}, but have not incorporated the links in a single framework (but see \citealp{saez2018}, and few have used realistic field data \citep{morandin2005, isaacs2010}.
This work adds to the body of literature examining the resource context of pollination services \citep{haig1988} within cropping systems \citep{marini2015, tamburini2016, fijen2018, tamburini2019}, and identifies directions of future research in seed production systems.

\section{Methods}

\subsection{Data collection}
From June through August of 2014 and 2015, we surveyed 29 commodity canola fields (14 in 2014, 15 in 2015) near Beaverlodge, Alberta and 31 fields (17 in 2014, 14 in 2015) near Lethbridge, Alberta.
Commodity canola fields were selected based on the proximity of honey bee apiaries and site access. 
28 of the 60 fields were stocked with honey bees (mean: 0.6 hives/hectare, SD: 0.58) while 32 fields were unstocked. %range: 0.03 - 3.1 Apiaries were stationed at the edges of fields, often near to shrubs or tree-lines to act as a wind break.
14 of 31 of the fields near Lethbridge were watered using central-pivot irrigation systems.
% We assumed similar numbers of workers per colony at both localities.
% Growers were asked for canola variety information, but there was not enough replication to test for difference between varieties.
% Fields with central-pivot irrigation were mostly circular, but dryland (non-irrigated) fields were usually square or rectangular.

%Maps + climate graphs needed for publication
During 2015 and 2016, we also surveyed 35 hybrid seed canola fields (15 in 2015, 20 in 2016) near Lethbridge, Alberta, from June through August of each year.
Seed fields were all stocked with honey bee hives at a rate of 3.6 hives/ha, with apiaries stationed in the corners of fields, and were also stocked with leafcutter bees in shelters throughout the field.
Shelters used either ``standard" or ``double"  leafcutter bee stocking ($\approx$50,000 vs. 100,000 cocoons/ha), and shelters were placed at either ``standard" or ``double" densities (1.3 vs. 2.6 shelters/ha) in each field.
Double stocking rates were only used in fields with double shelter density. %, creating three combinations of leafcutter bee stocking: ``standard", ``double shelter", and ``double shelter and double stocking".
All seed fields had central-pivot irrigation, and were mostly circular or semi-circular in shape.
%Woudick 5,6 = 64 shelters (single), Woudick 2 = 113 shelters (double + bees), Woudick 3 = 128 shelters Graham 1 = 135 shelters

% We recorded air temperature and wind speed before beginning observations (Table \ref{tab:weather}).
% \begin{table}[h]
%     \centering
%     \begin{tabular}{r|r|l|l|l|l}
%          Year & Area & Nectar volume & Nectar \% & Temperature & Wind Speed \\ \hline
%          2014 & Grande Prairie & 0.82 $\pm$ 0.035 & 56.1 $\pm$ 0.14 & 22.8 $\pm 0.9$ & 16.4 $\pm 2.0$  \\
%          2014 & Lethbridge & 0.85 $\pm$ 0.033 & 58.4 $\pm$ 0.15 & 24.7 $\pm 0.8$ & 4.6 $\pm 0.7$ \\
%          2015 & Grande Prairie & 0.63 $\pm$ 0.025 & 60.4 $\pm$ 0.22 & 21.7 $\pm 0.7$ & 26.7 $\pm 3.9$ \\
%          2015 & Lethbridge & 0.40 $\pm$ 0.021 & 58.4 $\pm$ 0.18 & 27.4 $\pm 0.7$ & 11.7 $\pm 1.5$ \\
%          2016 & Lethbridge & 0 & 0 & 23.5 $\pm 0.7$ & 6.2 $\pm 0.9$ \\
%     \end{tabular}
%     \caption{Nectar volume ($\mu$L), concentration (\%), air temperature (C) and wind speed (km/hr), averaged across all observations for each year and area. Nectar standing crop in seed canola was negligible in 2015 and 2016.}
%     \label{tab:weather}
% \end{table}

In commodity fields, we established plots at 5, 20, 100, and 500m along a transect into the field, starting at the field margin closest to the set of honey bee hives (271 total plots). %used a Garmin\texttrademark eTrex20 GPS, 
In unstocked fields, we began the transect at a field edge close to potential sources of natural pollinating insects, such as forests or grasslands, but observed very few wild pollinators (Table \ref{tab:propVisitors}).
In seed canola fields, bays of ``male" and ``female" plants were planted in 1- and 6-m wide bays, respectively, and leafcutter bee shelters were located in the female bays (Figure \ref{fig:seedfieldPhoto}, \ref{fig:seedfieldPlots}).
We established plots at 5, 20, 100 (250 in 2016), and 400m into the field along a transect from the nearest set of honey bee hives.
We made paired observations in adjacent male and female plots at each distance from the edge of the field (Figure \ref{fig:seedfieldPlots}).
At the edge and centre of each field (5m and 400m), we established another plot in the centre of the female bay to examine the effect of distance away from the male bay.
We also used plot-level leafcutter and honey bee visitation data from Waytes (\citeyear{waytesMsc}, and unpublished; same years and locations) to more accurately estimate the effect of distance from shelter on visitation rates (647 total plots).
We used a Nikon\texttrademark Laser 800S Rangefinder to measure the distance from each plot to the nearest shelter.
All surveys occurred on fair-weather days (median air temperature: 24.5$^\circ$C., range: 17--33) with no rain and as minimal wind as possible (less than 30km/hr).
Mean air temperature was similar between years in Grande Prairie ($\approx$ 22$^\circ$C), but Lethbridge was warmer in 2015 (23 vs. 28$^\circ$C).
Plots were marked with coloured stakes driven into the soil to locate them later in the season. %Full paper should have a table of climate variables. Windspeed needs sorting out (unit problems?)

Within each 1m$^2$ plot, we recorded the number of insect contacting the stigmas and anthers of flowers during 10 minutes (5 min for seed fields during 2015), as well as their taxonomic identity.
We counted visitable flowers in each plot, where ``visitable" was defined as an opened flower whose petals had not yet started to dehisce, and whose style had not elongated more than 3-4 millimeters beyond the anthers.
To assess pollen deposition at the plot level, we collected stigmas from five random open, receptive flowers at each plot, mounted them in fuchsin gel \citep{beattie1971} on depression slides, and counted the pollen on each stigma using a Leica\texttrademark DME 13595 light microscope under 100x magnification (1294 commodity and 1050 seed canola stigmas).
Each field was visited once during the main canola bloom (late June - late July), and again before harvest (mid - late August) to collect plant samples.
We collected three plants and recorded the density of plants per m$^2$ at the same plot where we conducted the visitation observations (789 commodity canola plants, 582 seed canola plants).
After drying the plants at 50$^\circ$C, we weighed the entire plant, counted mature pods, and counted the number of remaining flower pedicels to estimate total flower production.
We randomly sampled five pods from each plant, and counted and weighed the seeds from each pod, (3872 commodity canola pods,  2885 seed canola pods).
Finally, we threshed all the pods for each plant by hand, winnowed them using an air separator, and weighed the total mass of cleaned seeds.

\subsection{Analysis}
To examine how yield is influenced by visitation, we used a piecewise structural equation model framework (pSEM, \citealp{shipley2009}).
Structural equation models are comprised of a set of underlying linear models arranged in a causal network, and provides a framework for testing hypotheses about a complex system \citep{grace2012,lefcheck2015}.
Starting with a simple model (visitation $\rightarrow$ pollen deposition $\rightarrow$ fruit production $\leftarrow$ plant resources), we built more complex models that related measured variables within a causal framework (Figures \ref{fig:commoditySEM} and \ref{fig:seedSEM}).
These models allowed us to infer the relative strength of the main terms (e.g. pollen deposition, plant size) while controlling for other confounding factors (e.g. distance into field).
Fruit set can suppress future vegetative growth and flower production \citep{stephenson1981}, but SEMs do not allow for causal loops \citep{grace2012}, so we included a path from fruit set to flower production.
The direction of the path could plausibly be reversed (whereby large number of flowers reduce the proportion of fruit set), but we considered only the first scenario, as \citet{sabbahi2006} showed that the converse process is more likely (low fruit set causes increased flower production).

The underlying models of each pSEM were specified as generalized linear mixed-effects models (GLMMs, see Equation sets S1 and S2 for model specifications).
We used hierarchical models in order to include processes that occur at different levels; for example, seed size-number trade-offs were modelled at the pod level, whereas pollen deposition was modeled at the flower level.
Normal random effects were used to model variance between fields, within-field (pollen, flower survival, seed count \& size), and within-plot (seed count \& size); if the lowest-level variance term was inestimable, we fit the model without it.
Continuous responses were modeled using log-normal (plant density, plant size), square-root normal (flower density), and exponential-normal distributions (weight per seed), while counts were modeled as a negative-binomial (honey bee visits, pollen grains per stigma, flowers per plant, seeds per pod) or zero-inflated negative-binomial distribution (leafcutter bee visits) with a log-link function.
Visitation models used a $log$(time) term with a slope of 1 (``offset" variable) to account for differences in observation times.
Fruit set (fraction of flowers that matured into pods) was modeled using a beta-binomial distribution with a logit-link function.
Interactions between predictors were evident in honey bee visitation rate (Year:Locality interaction) and plant density (Irrigation:Year) in commodity canola, and for leafcutter bee visitation (Tent Stocking:Distance from edge) in seed canola, and were included in each model (represented as Y-shaped path in Figures \ref{fig:commoditySEM} and \ref{fig:seedSEM}). 
Finally, we created bivariate partial-effect plots of relevant terms within each model to aid in visualising each relationship.

Structural equation models do not have paths between all variables, which may bias the model results if this independence assumption is not true. 
We evaluated evaluating independence claims (``basis set") by using Fisher's C statistic from Shipley's d-separation criteria \citep{shipley2000, shipley2009}.
The initial commodity canola pSEM was misspecfied, as several missing paths were identified for the initial commodity model (Fisher's C=202.1, df=100, p$<<$0.001), but the updated pSEM that included missing paths was judged adequate (C=81.6, df=86, p=0.62).
Similarly, the initial seed field pSEM also had several missing paths (C=37.54, df=56, p=0.027), which we corrected (C=58.10, df=64, p=0.68).
D-separation criteria sets were generated using the \texttt{dagitty} library in R 3.5.1.

% Our initial hypotheses for commodity fields:
% \begin{itemize}
% 	\item Honey bee visitation depends on distance from their hive
%     \item Pollen deposition depends on honey bee visitation
%     \item Seeds per pod depends on pollen deposition
%     \item Weight per seed depends on pollen deposition
%     \item Flower abortion rate depends on pollen deposition
%     \item Total yield depends on seeds per pod, weight per seed, and flower abortion rate
% \end{itemize}

% Our initial hypotheses for seed fields:
% \begin{itemize}
% 	\item Honey bee visitation depends on distance from edge of field (proxy for distance from hives), bay position, bay type, and distance to leafcutter shelter
%     \item leafcutter bee visitation depends on distance from their shelter, bay position, and bay type
%     \item Pollen deposition depends on honey bee and leafcutter visitation
%     \item Seeds per pod depends on pollen deposition
%     \item Weight per seed depends on pollen deposition and seeds per pod
%     \item Flower abortion rate depends on pollen deposition
%     \item Total yield depends on seeds per pod, weight per seed, and flower abortion rate
% \end{itemize}

All component GLMMs of the pSEM were written in Stan 2.17.1 \citep{gelman2015}, and run using \texttt{rstan} 2.18.1.
We used informative normal priors ($\mu=0, \sigma=5$) for fixed effects, and gamma priors ($\alpha=1, \beta=1$) for the variance components.
We ran three separate chains with an adaptive phase of 2000 iterations, and a sampling phase of 2000 iterations, then checked for convergence of the chains ($\hat{R} \approx$1) and low autocorrelation within chains (high $N_{eff}$).
We assessed the adequacy of the underlying probability distribution functions of each model using posterior predictive checks \citep{gelman2013}, and found that the probability distributions were specified correctly (p$\sim$0.5) for all components except seed count.
This means that while the average seed counts (per plant) were unbiased, the variance within a plant was not. 
However, the negative binomial distribution had the closest posterior predictive checks of any other distribution. 
% p-values listed below (also in Tables S3 and S4) are \textit{posterior} p-values, representing the proportion of the posterior distribution that overlapped zero, with Z-scores (mean/standard deviation of posterior) showing the effect size.
% Predictions from models are median values of the posterior, representing the median prediction, while intervals displayed in figures are credible intervals (CIs), representing 95\% of the samples drawn from the posterior distribution (analogous to confidence intervals, see \citealt{gelman2013}).

%RC: REMIND READER OF THE EXPECTATIONS, AND WHETHER HYPOTHESES WERE SUPPORTED/REJECTED, RATHER THAN JUST STATING THE RESULTS
%SH: 1) SET UP LOGIC MORE CLEARLY, FOLLOW IT THROUGH IN SAME WAY AS THE REST OF THE PAPER
%2) BE CONSISTENT IN WORDS/PHRASES
%3) BREAK UP PARAGRAPHS & PROVIDE MORE TRANSITION SENTENCES
%4) TALK ABOUT THE REAL WORLD AS MUCH AS POSSIBLE, RATHER THAN VARIABLES

\section{Results}

%OVERALL SUMMARY FROM SEMS

\subsection{Visitation}

\subsection{Pollen Deposition}

\subsection{Seed Production}

The SEMs revealed that plant size and pollen deposition were the main drivers of yield in seed canola, while only plant size mattered in commodity canola.
Distance from the field edge had a negative effect on honey bee visitation in commodity and seed canola (Z=-3.7, -2.5, respectively), and unexpectedly, had a negative effect on leafcutter bee visitation (Z= -4.4), showing that overall visitation decreases with distance into the field.
The path from leafcutter bee visitation to pollen deposition was strong in seed canola (Z=3.2), but there was no path from honey bee visitation to pollen deposition in either crop type.
Pollen deposition increased fruit set (Z=3.1) and seeds per pod (Z=2.3) in seed canola, but was not present in commodity canola, showing that yield in seed canola, but not commodity canola, is strongly dependent on pollination.
%The path from seeds per pod to weight per seed was negative in seed canola (Z=-15.0) but positive in commodity canola (Z=6.1) 
Both crop types had strong negative paths from flower survival to flowers per plant (commodity Z=-12.5, seed Z=-12.1), indicating that high flower survival suppressed future flower production.
Commodity canola had a similar weight per seed, regardless of the plant size, but in seed canola, plant size had a strong influence on seeds per pod (Z=5.6) and weight per seed (4.6).
Finally, in both crop types, the paths leading from plant size were the dominant signal influencing fruit set (commodity Z=5.8; seed Z=19.9), but the path from pollen deposition to fruit set was only present in seed canola, showing that plant resources matter strongly for both crop types, but that increased pollen deposition only benefits seed canola.

The results of the underlying components of each pSEM are shown in Figures \ref{fig:commoditySEM} and \ref{fig:seedSEM}:

\subsection{Prediction 1: Decline in visitation with distance}
Bee visitation strongly declined with distance away from the hives and shelters, in both commodity and seed canola fields. 
In commodity canola, honey bee visitation sharply declined with distance into the field (Z=-3.7, p$=$0.0002, Figure \ref{fig:hbeeDist_commodity}), decreasing from 8.5 visits/hr at the edge of the field to 3.1 visits/hr at 100 m into the field (at a stocking level of 20 hives).
Visitation rates were higher in both years in Lethbridge (2014: 9.3 visits/hr, 2015: 7.1), but were higher in 2015 than 2014 at Grande Prairie (Z=2.3, p$=$0.02), rising from 5 visits/hr at the field edge in 2014 to 17 visits/hr in 2015. % (at a stocking level of 20 hives). 
Honey bee visitation increased with the number of hives used for stocking (Z=5.3, p$<$0.0001); plot-level visitation at the edge of the field increased from 14.5 visits/hr with an apiary of 20 hives to 22.7 visits/hr with an apiary of 40 hives, while unstocked field edges had 1.8 visits/hr.
In seed canola fields, honey bee visitation also declined with distance into the field (Z=-2.5, p$=$0.01), but not as strongly as in commodity fields (126 visits/hr at edge of field vs. 78 visits/hr at 100 m). 
Honey bee visitation was lower near leafcutter shelters (Z=3.9, p$=$0.001), dropping from 60 visits/hr at 10 m to 34 visit/hr at 2 m, likely due to competition with leafcutter bees (Figure \ref{fig:hbeeDist_both}, \ref{fig:lbeeDist_both}).

Leafcutter bees were much more sensitive to distance from their shelter than honey bees.
Leafcutter bee visitation sharply declined with distance from their shelters (Z=-11.4, p$=$0.0001, 350 visit/hr at 2 m to 83 visit/hr at 10 m), and unexpectedly, was higher at the edge of the field than the centre (Z=-4.4, p$=$0.0001, 114 visits/hr vs 28 visits/hr).
However, there was no difference in visitation rates when the stocking rate of cocoons per shelter was lower (Z=2.2, p$=$0.028), indicating that leafcutters at high stocking densities may migrate to shelters close to the edge of the field (Figure \ref{fig:hbeeDist_both}).
Both leafcutter bees and honey bees visited at similar rates in the male and female bays (leafcutter bee: p$=$0.72, honey bee: p$=$0.32), but within the female bay, leafcutter bee visitation was lower in the centre of the bay (p$=$0.04, 51 vs. 29 visits/hr), while honey bee visitation was higher at the centre of the bay (p$=$0.008, 71 vs. 117 visits/hr, Figure \ref{fig:edgeCentVis_both}).
%Therefore, visitation by both species strongly decreases with distance from the edge of the field, decreases with distance from the leafcutter shelters in seed canola fields, and is done by different bees at the centre of the female bay.

%Visits/hr: In GP, 3.1 in 2014, 10.6 in 2015; in LB 5.9 in 2014, 4.5 in 2015
\begin{figure}
    \centering
    \includegraphics[width=0.9\textwidth,keepaspectratio=true]{slopeNumHivesDistVis.png}
    \caption[Partial effect of distance away from field edge and stocking on honey bee visitation in commodity canola fields]{Partial effect of distance away from field edge and stocking on honey bee visitation in commodity canola fields. Solid lines represents median, and shaded areas represent 95\% CIs. Red line represents overall slope (controlling for region and year).}
    \label{fig:hbeeDist_commodity}
\end{figure}
%PERHAPS INCLUDE FIGURE OF AREA/YEAR EFFECTS IN THE SUPPLEMENTAL?

\begin{figure}
    \centering
    \includegraphics[width=0.9\textwidth,keepaspectratio=true]{slopeHbeeDist_both.png}
    \caption[Partial effect of distance from field edge on bee visitation in seed canola fields]{Partial effect of distance from field edge on honey bee and leafcutter bee visitation in seed canola fields. Solid lines represent medians, and shaded areas represent 95\% CIs.}
    \label{fig:hbeeDist_both}
\end{figure}

\begin{figure}
    \centering
    \includegraphics[width=0.9\textwidth,keepaspectratio=true]{slopeLbeeDistBothBees.png}
    \caption[Partial effect of distance from leafcutter shelter on bee visitation in seed canola fields]{Partial effect of distance from leafcutter shelter on honey bee and leafcutter bee visitation in seed canola fields. Solid lines represent medians, and shaded areas represent 95\% CIs.}
    \label{fig:lbeeDist_both}
\end{figure} %SH: WOULD BE COOL TO HAVE A ``SUM OF BOTH BEES" LINE AS WELL - perhaps in the manusript? may require a separate model of both bees, or possibly just adding model results together

\begin{figure}
    \centering
    \includegraphics[width=0.9\textwidth,keepaspectratio=true]{slopeEdgeCent_both.png}
    \caption[Partial effect of bay position on honey bee and leafcutter bee visitation]{Partial effect of bay position (edge or centre of female bay) on honey bee and leafcutter bee visitation. Coloured points represents median value, and vertical bars represent 95\% CIs.}
    \label{fig:edgeCentVis_both}
\end{figure}

\subsection{Prediction 2: Pollen deposition increased by bee visitation}
Pollen deposition was enhanced by bee visitation in seed canola, but not in commodity canola.
In commodity canola, pollen deposition on stigmas was high (mean: 293 grains per stigma, SD: 385, range: 0--3981), but honey bee visitation did not affect deposition (p$=$0.77, Figure \ref{fig:hbeeVisPol}).
Pollen grains per stigma weakly declined with distance from the edge of the field (p$=$0.07), but this only amounted to an average decrease of 290 grains per stigma at the edge compared to 240 at the field centre (6\% decrease), meaning that distance did not strongly affect pollen deposition either.
Flies were common visitors in commodity fields (Table \ref{tab:propVisitors}), but had no detectable effect on pollen deposition (p$=$0.577), and other flower visitors were rare, so only honey bees and leafcutter bees were considered as potential pollinators.
In seed canola, overall pollen deposition was much lower (mean: 22 grains per stigma, SD: 43, range: 0--578), was strongly increased by leafcutter bee visitation (Z=3.2, p$=$0.002, Figure \ref{fig:visPol_both}, 12 grains/stigma at 6 visits/hr vs. 16 pollen grains at 60 visits/hr), and also decreased with distance from the edge of field (Z=-4.4, p$=$0.0001, Figure \ref{fig:distCentPol}, 23 vs. 11 grains/stigma).
Pollen deposition was lower in the centre of the female bay (Z=-4.5, p$=$0.0001, 23 vs. 13 grains/stigma) independent of visitation rate, suggesting that pollen is lost from bees crossing from male bays, who likely visit flowers at the edge of the bay first \citep{pinnisch1990}. 
There was no direct effect of honey bees on pollen deposition (Z=0.98, p$=$0.33), implying that most of the pollen deposition occurs via leafcutter visitation.

\begin{figure}
    \centering
    \includegraphics[width=0.9\textwidth,keepaspectratio=true]{slopeHbeeVisPol.png}
    \caption[Partial effect of honey bee visitation on pollen deposition in commodity canola]{Partial effect of honey bee visitation on pollen deposition in commodity canola. Solid line represents median, and shaded areas represent 95\% CIs.}
    \label{fig:hbeeVisPol}
\end{figure}

\begin{figure}
    \centering
    \includegraphics[width=0.9\textwidth,keepaspectratio=true]{slopeVisPol_both.png}
    \caption[Partial effects of honey bee and leafcutter bee visitation on pollen deposition in seed canola]{Partial effects of honey bee and leafcutter bee visitation on pollen deposition in seed canola. Solid lines represent medians, and shaded areas represent 95\% CIs.}
    \label{fig:visPol_both}
\end{figure}

\begin{figure} 
    \centering
    \includegraphics[width=0.9\textwidth,keepaspectratio=true]{slopeDistCentPol.png}
    \caption[Partial effect of distance from field edge and bay position on pollen deposition in seed canola]{Partial effect of distance from field edge and bay position on pollen deposition in seed canola. Coloured points represents median, and shaded areas represent 95\% CIs.}
    \label{fig:distCentPol}
\end{figure}

%LH: WRITING BELOW THIS POINT COULD BE MORE ECONOMICAL
\subsection{Prediction 3: Larger plants produce more seeds}

Plant size was largely influenced by plant density, but this differed between commodity and seed canola crops.
Plant density was higher overall in commodity fields (mean: 48.5 plants/m$^2$, SD: 22.9, range: 6--151 ) than seed fields (mean: 39.4 plants/m$^2$, SD: 17.0, range: 11--89), and commodity canola plants were smaller on average (mean: 18.2 g, SD: 14.4, range: 0.8--110.2) than seed canola plants (mean: 30.7 g, SD: 21.2, range: 1.2--144.3).
However, commodity canola plant size was not influenced by plant density (Z=-1.62, p$=$0.10, Figure \ref{fig:plDensPlSize}), indicating that any density-dependence was overwhelmed by other factors, but plant size in seed canola was negatively influenced by planting density (Z=-13.2, p$<$0.0001), and plants were larger at the centre of the field independent of density (Z=5.4, p$<$0.0001).%, possibly because of proximity to the centre of the irrigation system. 
Plant density was slightly lower at the edge of commodity canola fields (Z=1.68, p=0.09), but was much lower in seed canola (Z=5.2, p$<$0.0001), indicating lower seedling survival or seeding density at the edges of the field.
Neither irrigation (p=0.76), site (p=0.86), nor distance from field edge (p=0.70) directly influenced commodity canola plant size, but plants were larger in 2015 (Z=2.5, p=0.01).

\begin{figure} 
    \centering
    \includegraphics[width=\textwidth,keepaspectratio=true]{plDensPlSize_both.png}
    \caption[Partial effects of plant density on plant size]{Partial effects of plant density on plant size, for commodity and seed canola plants. Solid lines represents median, and shaded areas represent 95\% CIs.}
    \label{fig:plDensPlSize}
\end{figure}

Plant size had a strong effect on the number of pods produced, and there was evidence of fruit set suppressing future flower production.
Commodity canola plants produced fewer flowers per plant (mean: 198, SD: 157, range: 13--1419) than seed canola plants (mean: 468, SD: 328, range: 26--2712), and also produced fewer pods per plant (mean: 143, SD: 114, range: 5--892) than seed canola plants (mean: 303, SD: 208, range: 10--1410).
In both commodity and seed canola, plant size had a strong positive effect on the total number of flowers per plant (commodity: Z=92.4, p$<$0.0001, seed: Z=82.7, p$<$0.0001, Figure \ref{fig:plSizeFlwCount}), as well as fruit set (commodity: Z=5.5, p$=$0.0002, seed: Z=19.9, p$<$0.0001, Figure \ref{fig:flwSurv_both}).
Fruit set had a strong negative influence on total flowers per plant (p$<$0.0001) in both commodity (Z=-12.5) and seed canola (Z=-12.1), indicating that high levels of fruit set suppressed future flower production.
Finally, commodity plants were also lower-yielding (mean: 6.8 g of seeds per plant, SD: 6.0, range: 0.01--47.9) than seed canola plants (mean: 9.6, SD: 7.9, range: 0.02--60.8).
However, the harvest index of commodity canola (mean: 0.26, SD: 0.08, range: 0.005--0.65) was higher than seed canola (mean: 0.23, SD: 0.09, range: 0.003--0.55), meaning that commodity plants produced more seeds per gram of biomass than seed canola plants, likely due to the lack of pollen limitation (see below).

\begin{figure} %SH: HARD TO COMPARE BECAUSE OF DIFFERENT AXES
    \centering
    \includegraphics[width=\textwidth,keepaspectratio=true]{plSizeflwCount_both.png}
    \caption[Partial effect of plant size on number of flowers per plant]{Partial effect of plant size on number of flowers per plant, for commodity and seed canola plants. Solid lines represent median, and shaded areas represent 95\% CIs.}
    \label{fig:plSizeFlwCount}
\end{figure}

\begin{figure}
    \centering
    \includegraphics[width=\textwidth,keepaspectratio=true]{plSizeFlwSurv_both.png} 
    \caption[Partial effect of plant size on fruit set]{Partial effect of plant size on fruit set (\% of flowers that became pods), for both commodity and seed canola. Solid lines represent median, and shaded areas represent 95\% CIs.}
    \label{fig:flwSurv_both}
\end{figure}

Plant size had a positive effect on seed size and seeds per pod in seed canola, but not in commodity canola, and the relationship between seed size and number was negative in seed canola but positive in commodity canola.
Commodity canola plants produced more seeds per pod (mean: 23.0 seeds per pod, SD: 7.4) than seed canola (mean: 16.3 seeds per pod, SD: 9.1), but seed mass was lower in commodity canola (mean: 2.74 mg/seed, SD: 1.04) than seed canola mean (mean: 3.59 mg/seed, SD: 1.33).
In commodity canola, plant size did not impact seeds per pod (Z=1.00, p=0.32) or seed size (Z=-0.40, p=0.69, Figure \ref{fig:seedWeightCount_both}), but eed size was positively related to seeds per pod (Z=6.1, p$<$0.0001, Figure \ref{fig:seedWeightCount_both}).
In seed canola, however, seed size increased with plant size (Z=4.7, p$<$0.0001, Figure \ref{fig:seedWeightCount_both}), decreased with seeds per pod (Z=-13.1, p$<$0.0001), and interestingly, increased with plant density (Z=2.9, p$=$0.004), suggesting resource limitation at both the pod and the plant level. 
There were also between-year differences in seeds per pod (commodity canola only: Z=4.7, p$<$0.0001, 21.7 seeds per pod in 2014, 24.6 in 2015) and seed size (commodity canola: Z=2.2, p=0.031, 2.04 mg/seed in 2014, 2.31 mg/seed in 2015; seed canola: Z=3.6, p=0.0003, 3.11mg/seed in 2015, 3.59mg/seed in 2016), pointing to differences in overall growing conditions between years.

\begin{figure}
    \centering
    \includegraphics[width=0.9\textwidth,keepaspectratio=true]{seedWeightSeedCount_both.png}
    \caption[Partial effects of seed count and plant size on seed size]{Partial effects of seed count and plant size on seed size, for both commodity and seed canola. Solid lines represent median, and shaded areas represent 95\% CIs.}
    \label{fig:seedWeightCount_both}
\end{figure}

\subsection{Prediction 4: Pollinated plants produce more seeds}

Pollen deposition increased fruit production and seed production in seed canola, but not in commodity canola.
Pollen deposition had no effect on fruit set (p=0.12), seeds per pod (p=0.94) or seed size (p=0.56) in commodity canola, and there was also no direct effect of honey bee visitation on fruit set (p=0.38), seeds per pod (p=0.55), or seed size (p=0.34).
Seed canola, in contrast, was highly dependent on pollen deposition.
Pollen deposition increased fruit set (Z=3.1, p$=$0.002), and seeds per pod (Z=2.3, p$=$0.02), but had no direct effect on seed size (p$=$0.35).
Fruit set also decreased with three types of distance: distance into the field (Z=-5.3, p$<$0.0001), distance from leafcutter shelters (Z=-3.2, p$=$0.002), and distance from the edge of the female bay (Z=-4.0, p$=$0.0001).
Seeds per pod decreased in the centre of the female bay (Z=-4.6, p$<$0.0001), and was higher in plants with high fruit set (Z=6.0, p$<$0.0001).

\section{Discussion}
%LH: DISCUSSION TOO NARROWLY FOCUSED. WHAT ARE THE BROADER IMPLICATIONS? CONTAINS A LOT OF SPECULATION WITHOUT ANY EVIDENCE/REFERENCES
%SH: RELATE RESULTS TO HYPOTHESES, AND START WITH BIG PICTURE IN ORDER TO DISCUSS
This study examined the relative strength of the path between visitation, pollination, and yield, in two types of canola crops, and showed a strong path between visitation and yield in seed canola, but not in commodity canola.
First, honey bee and leafcutter bee visitation decreased with distance from their hive or shelter, but unexpectedly, leafcutter bees visited more frequently at the edge of the field.
Secondly, honey bees had little (direct) influence on pollen deposition in either crop type, leafcutter bees had a positive effect on pollen deposition in seed canola.
Finally, the model revealed that commodity canola production is largely limited by plant size, while seed canola production is limited by both pollen and plant size.

\subsubsection{Bee visitation} 
Honey bee visitation in both field types declined with distance into the field, but overall visitation was much higher than commodity fields, due to the higher honey bee stocking rate used in seed fields (3.6 vs. mean 0.6 hives/ha).
Since honey bees travel from their hive outside the edge of the field, this decline was not surprising, but we did not expect the similar decrease observed in leafcutter bee visitation with distance into the field, as their shelters are located \textit{within} the field.
This decrease with distance into the field may have been caused by leafcutter bees migrating from shelters at the centre of the field to the edge \citep{goerzen1995}.
Like honey bees, female leafcutter bees are central-place foragers, and tend to not forage far from their nests \citep{peterson2005,pitts2011, brunet2019}.
However, leafcutter bees are not as constrained to their nest site as honey bees, and can drift between shelters in a given field \citep{goerzen1995, pittsSinger2013}.
Leafcutter bees must also forage for leaf materials to create cocoons, but they prefer to build cocoons out of thinner, non-canola leaf types, mainly plants in the families Fabaceae and Rosaceae \citep{sinu2018}.
Seed canola fields have very few weeds within the area of the crop, meaning that leafcutter bees at the centre of the field may have few choices of leaf material, or alternative pollen and nectar sources.
Therefore, leafcutter bees likely move from the shelters at which they were released in the centre of the field to the shelters at the edge of the field, so as to gain access to better leaf material \citep{horne1995}, which is more available off-field, or to better forage for off-field pollen or nectar \citep{horne1995b}.
This would explain why greater visitation occurred at the edge of the field, and may also explain why this pattern was not seen in fields with half-stocked shelters.
To test this, a mark-recapture study of female leafcutter bees could be done to see if bees migrate to shelters at the edge of the field, or if visitation is higher due to other reasons (\textit{e.g.} feral populations migrating to edge of field, long-distance foraging from centre of field as in \citealp{peterson2005}).  %SH: FINE FOR THESIS, BUT CAN BE REMOVED FOR MANUSCRIPT
It would be interesting to see if there is a critical threshold of leafcutter bee density per-shelter that causes them to move to shelters at the edge of the field (similar to \citealp{pittsSinger2013}).
%Honey bees visited flowers at the edge of the field more frequently than those in the middle of the field, as predicted for central-place foragers with nesting aggregations outside the field (\citealp{olsson2014}, see Chapter 2).
%Similarly, the high concentration of canola nectar (\citealp{mohr1990}, 58.3\% brix from Chapter 2) may cause leafcutter bees to choose more diluted nectar under hot and dry conditions, similar to honey bees \citep{ohguchi1983}. % canola pollen is valuable to bees \citep{mohr1988,huang2004},
% Potential future studies should investigate how leafcutter bees shift among shelters after emergence, how cocoon production in seed fields varies with distance, and should investigate inter-cropping leaf material plants (e.g. \emph{Polygonum}, \emph{Pisum}, or other large, thin-leaved plants) to encourage leafcutter bees to stay within the field.

%Leafcutter-honeybee interactions
Honey bee visitation in hybrid seed fields was lower at areas near to leafcutter shelters. 
This may have been driven by avoidance of nectar and pollen competition near shelters, as areas close to leafcutter shelters may become depleted in nectar and pollen, deterring honey bee visitation (similar to \citealp{currie1997}).
Honey bees also suffer from direct interference by leafcutter bees near to their shelters.
Several times during the study, \textit{M. rotundata} females and males directly harassed honey bees during the plot-level observations, tackling honey bees both on the flowers and in the air (also seen by \citealp{batra1978} and \citealp{waytesMsc}). 
Honey bees were never the aggressor in these interactions, so interference between leafcutter bees and honey bees may be unidirectional, at least in areas near leafcutter bee shelters. 
For this reason, we treated high leafcutter visitation as causing lower honey bee visitation in our SEM (Figure \ref{fig:seedSEM}, arrow from leafcutter visit rate to honey bee visit rate).

Honey bee visitation and foraging behaviour varied strongly between the male and female bays of seed fields, as well as within the female bays.
Visitation rates of honey bee foragers were almost twice as high in the centre of the female bay, and conversely, leafcutter bee visitation was almost twice as low.
This could be due to leafcutter bees avoiding competition for nectar with honey bees, but more likely reflects a stronger need for pollen among leafcutter bees than honey bees \citep{cane2011}.
Only 1.4\% of the honey bees in the female bay were pollen foragers (Table \ref{tab:sideWorking}), meaning that foragers who have (recently) come into contact with pollen rare.
Both \citet{waytesMsc} and \citet{gaffney2019} showed that honey bees exhibit floral fidelity during foraging trips, with minimal crossing between male and female bays ($\sim$5\% of observations, \citealp{waytesMsc}), limiting pollen transfer between the male and female flowers.
Side-working was a very common behaviour among honey bees in commodity fields (65\% of the total visits from honey bees during 2015 were side-working), as well as the male bays of seed fields (36\%), but not in the female bays (3\%, Table \ref{tab:sideWorking}).
This behaviour is relatively common on male-fertile flowers of \textit{Brassica} \citep{free1973,free1983,delbrassine1988,mohr1988} as well as other flowering crop flowers \citep{thomson2001}, and may be due to honey bees avoiding contact with the stigmas to increase ease of access to nectar, or to reduce the amount of grooming needed during a nectar foraging bout.
The foragers who were side-working tended to not switch to top-working (personal observation), so this is likely a consistent individual behaviour (at least in experienced foragers).
Therefore, honey bees pollen foragers in seed canola fields appear to avoid flowers in the female bay, and commonly engage in side-working behaviour in both commodity and seed canola fields, limiting their opportunities for pollen transfer (see below).
%However, after controlling for stocking rates, visitation in commodity fields was higher in Grande Prairie in 2015.
%This may have been caused by greater food availability outside of canola fields in 2015, causing foragers to concentrate in canola fields.
%Canola nectar tends to have high sugar concentrations \citep{szabo1985}, so workers may have selected lower-concentration flowers in field margins and ditches, such as \textit{Trifolium} and \textit{Medicago}, instead of the flowers in the canola fields, depending on local abundances in each year and location, but this seems unlikely, as nectar concentrations were higher in 2015 in Grande Prairie (Chapter 2 Appendix).
%Water foraging differences between years may also help to explain this effect, as foraging honey bees tend to avoid concentrated nectar or prioritize water foraging \citep{lindauer1955,kuhnholz1997} during hot weather.
%During 2015, we did notice a large number of foragers in Lethbridge gathering water from pools of water near fields instead of visiting flowers (personal observation), so foragers may have been gathering water instead of foraging on flowers (at least in that region), but this is anecdotal, and would require a formal study to confirm this. 
% Avoidance of concentrated nectar may reflect slower rates of imbibing them \citep{harder1986}.
% Nectar concentrations were slightly higher in GP in 2015 (60 vs 56), but were about 58.4 each year in LB. Soil water and irrigation don't appear to do much (ultimately needs better modelling, though)

\subsection{Pollen deposition}
%Pollen deposition in commodity fields
Honey bee visitation did not increase pollen deposition in commodity canola fields compared to unstocked fields, meaning that wind and/or self-pollination are the likely agents of pollen transfer.
The stigmas and flowers of \emph{Brassica} are not aligned for optimal dispersal and deposition from the wind, so cross-pollination likely occurs mainly via insects \citep{mesquida1982,cresswell2004}.
However, wind-induced self-pollination (plant shaking) can increase yield in \textit{Brassica} \citep{williams1986, mesquida1988c}, and fields without bee pollination have outcrossing rates of about 20\% within the field \citep{rakow1987,becker1992}.
The style of \textit{Brassica} grows past the anthers during maturation, allowing deposition of large amounts of self-pollen, suggesting that self-pollination is the dominant mode of pollination.
Honey bees can assist in deposition of self-pollen, as \citet{ali2011} found that \textit{Apis dorsata} and \textit{Apis florea} can both deposit 100-200 grains of pollen per visit on a canola flower (\emph{B. napus} var. \emph{Bulbul}).
However, \citet{waytesMsc} used male-sterile flowers and found that \textit{A. mellifera} deposit far less outcrossed pollen ($\sim$ 2 grains per visit), suggesting that much of the pollen deposited by honey bees on canola stigmas is self-pollen. 
Because the overall pollen deposition rates found in this study were so high (mean: 293, SD: 385), honey bee visitation seems to have made little difference in the amount of self-pollination.
The typical lifetime of a canola flower is approximately 3 days, and the stigmatic surface is receptive for 24--36 hours within this period \citep{eisikowitch1981,hoyle2007}, so it may be that 10-minutes of observing flower visitors was too short of a time interval to relate to pollen deposition.
This is unlikely, however, as large amounts of pollen were present on commodity canola stigmas even at the centre of unstocked fields (average plot-level visitation rate was 0.23 visits/hr).
These results suggest that stigmas are largely saturated with self-pollen, swamping any extra pollen deposition by honey bees.
%SH: DOING A BACK-OF-ENVELOPE CALC: 0.23 VISITS/HR X 2 GRAINS/VISIT X 12 HR X 3 DAYS = 5-6 GRAINS PER DAY, LESS THAN 1% OF STIGMA LOAD
% This runs contrary to other studies in commodity canola (\citealp{sabbahi2005}, but see \citealp{garibaldi2013} and \citealp{waytesMsc}), so why did

%REVIEW THIS
Honey bee behaviour in seed fields made pollen transfer between male and female plants unlikely, and this was also reflected in the measurements of stigma deposition. 
Deposition was not affected by honey bee visitation, but was strongly increased by leafcutter bee visitation.
Leafcutter bees tend to switch between male and female flowers more frequently than honey bees do \citep{waytesMsc}, transport more viable pollen between flowers \citep{parker2015}, and tend not to side-work canola flowers (\citealp{soroka2001}, personal observation), which may explain their increased pollination efficacy.
We also found that pollen deposition also decreased with distance from the edge of the field, was lower in the centre of the female bays, and that this was not solely explained by leafcutter bee abundance (Figure \ref{fig:seedSEM}).
During foraging bouts, leafcutter bees may travel further between flowers than honey bees do; \citet{brunet2019} found that leafcutter bees foraging in alfalfa (\emph{Medicago sativa} L.) travelled an average of 21 cm between flowers, while honey bees only travelled 16 cm.
However, pollen carryover \citep{thomson1986} to the middle of the bay female is likely reduced, as leafcutters likely visit the edge of the female bay before venturing into the centre.
The decrease of pollen deposition with distance into the field (independent of visitation rates) also suggests that the same visitation rate of pollinators in the centre of the field results in less pollen deposition.
This may be due to lower levels of competition at the centre of the field, leading to a higher nectar (or pollen) standing crop. %LH: more likely that bees at centre of F bays carry less pollen
Foraging \textit{Bombus} take smaller trips between flowers and will forage in smaller areas under nectar-rich conditions (area-restricted search, \citealp{pyke1978b, heinrich1979}), so leafcutter foraging may follow a similar pattern, causing lower pollen deposition at the centre of the field where competition is lower.
%Leafcutter bees are extremely fast fliers, and are difficult to follow after they leave an inflorescence, meaning that tracking their movements during an entire foraging bout would be almost impossible.
% Visits by honey bee foragers were almost twice as high in the centre of the female bay, but pollen deposition was about 40\% lower (  Figure \ref{fig:distCentPol}), which correspondingly is 
% Honey bees in seed fields tended to visit more in the centre of the female bay, even close to the edge of the field, yet pollen deposition was still about 40\% lower (Figure \ref{fig:distCentPol}).
% While we found that leafcutter bees also tend to avoid the centre of the female bays, and decrease with distance into the field, this extra dependence could have been caused by the fact that the visitation data represents a short ``snapshot'' of the pollen deposition process.
% For example, canola flowers are receptive for 1-2 days before the petals dehisce, while the surveys only recorded 5 or 10 minutes of visitation, meaning we may have not captured the deposition process on the time scale that it occurs, and the extra variance is being accounted for by distance from field edge and the centre of the female bay.
% Leafcutter visitation can be extremely sporadic, so the distance and bay position measurements capture differences in the average visitation process better than 10 minute measurements.
% Pollen deposition also likely changes over the course of the season, as flower availability decreases.

Honey bees may have an indirect positive effect on pollen deposition, as they may cause leafcutter bees to travel farther by lowering overall nectar and pollen standing crop, or release airborne pollen from male-fertile flowers.
\citet{pierre2010} showed that honey bees can increase the amount of airborne pollen by foraging on male-fertile flowers and releasing pollen from the anthers, causing increased yields in nearby male-sterile flowers; therefore, honey bees may indirectly contribute to a higher rate of wind pollination.
Honey bees may also cause leafcutter bees to forage at further distances away from their shelters.
Bumble bees move further between flowers when foraging in \textit{Trifolium} fields that have been depleted by honey bees \citet{heinrich1979}, so a similar process could occur in canola seed fields. 
Leafcutter bees do not appear to use area-restricted search \citep{brunet2019}, but we expect that the foraging range of leafcutter bees around their shelters would sitill decrease, because if honey bees lower pollen and nectar levels at the edge of the field, then leafcutter bees should travel shorter distances to gather the same reward (according to the predictions of Chapter 2).
%RC: MAY HAVE TO CHOP FOR THE MANUSCRIPT, BECAUSE IT DOESN'T HAVE OTHER AREA-RESTRICTED SEARCH LIT
We also expect that foraging leafcutter bees would make shorter trips between flowers (similar to \citealp{heinrich1979}), and possibly may switch between bays less frequently \citep{waytesMsc,gaffney2019}, due to a greater floral fidelity on higher-rewarding flowers in the male bay \citep{mesquida1978}.
If this is true, this would result in a lower rate of (overall) pollen deposition by leafcutter bees during the same period.
However, testing this would require observations of seed canola fields that were only stocked with leafcutter bees, which is extremely rare in southern Alberta.
%A simple test of this would be to remove honey bee hives from a seed field, mid-season, and perform observations of leafcutter visitation patterns before and after the removal.

\subsection{Pod production} % The total yield of a canola plant is a function of three components: number of pods per plant, number of seeds per pod, and seed size.
Fruit set (i.e. pod production) in commodity canola was positively affected by plant size, but not by pollen deposition or honey bee visitation.
Both pod production and seeds per pod can increase with extra pollination \citep{jauker2008,sabbahi2005,sabbahi2006,duran2010}, so this lack of effect may be due to a high overall level of pollen deposition (Figure \ref{fig:hbeeVisPol}), even in fields without honey bees.
There was no effect of honey bee visitation on fruit set, seeds per pod, or seed size, indicating that visitation did not seem to cause either \textit{a)} a greater quantity of pollen (see above) or \textit{b)} higher quality (outcrossed) pollen.
Self-pollination (geitanogamy) in canola can result in similar fruit production as outcrossing \citep{rosa2011}, implying that pollen quality is not likely a limiting factor in canola fruit set, at least in some varieties.
Flower number was negatively related to fruit set, which implies a response to pollination (high flower fertilization suppresses further flower production) and/or a reproductive trade-off (greater pod development rate means more competition among pods for resources).
%RC: THESE SCENARIOS AREN'T MUTUALLY EXCLUSIVE
We considered the first scenario to be the stronger effect, as \citet{sabbahi2006} and \citet{mesquida1981} both found that canola plants compensated for experimental removal of flowers by increasing branch and flower production, until the plant reached about 170 pods.
Their final number of pods is similar to the plants from our study (median: 112, range: 5--892), but we found that larger plants also had greater fruit set, in addition to higher flower production, presumably caused by the larger pool of resources that large plants are able to invest into reproduction. 
%This could indicate stronger overall competition between plants in seed fields, but that plant resources are higher in the centre of the crop field than at the edge.

Pollination increased pod production in seed canola, but not in commodity canola, meaning that extra pollination is valuable for seed canola crops, but not commodity canola. 
This is similar to the findings of \citet{mesquida1981} and \citet{steffan2003}, who found that fruit set in male-sterile plants responded positively to visitation, while male-fertile plants (``male" plants in seed fields, all plants in commodity fields) had no response (but see \citealp{adegas1992}).
Pod production in seed canola increased with both pollen deposition and plant size, suggesting that both pollen availability and plant resources constrain pod production. %(\citealp{mesquida1981} did not consider plant size).
However, the effect size of pollen deposition (Z=3.1) was much smaller than that of plant size (Z=19.9), indicating that the factors controlling plant size (fertilizer, plant density, and soil quality) likely constrain pod production more strongly than pollination alone, in both commodity and seed canola plants. %RC: SEEMS AN INTERACTION WOULD TEST THIS BETTER
There were also effects of distance on fruit set, independent of pollen deposition: pod set decreased with distance from the edge of the field and distance to leafcutter shelters independent of pollen deposition, and was lower in the centre of the female bays.
\citet{mesquida1978} also found that fruit set in male-sterile canola declined quickly with distance from the male-fertile plants (due to wind pollination), but the effect we found is likely related to the earlier effect of lower pollen carryover at the centre of the female bays, and possibly the centre of the field.
However, our analysis points to the strong relative importance of plant resources, as well as pollination services \citep{marini2015}, mediated through the effect of leafcutter bee visitation, to the production of hybrid seed canola.

\subsection{Seed number and size}
In commodity canola plants, the number of seeds per pod was only affected by between-year variation, and was unaffected by plant size and pollination.
In contrast, the number of seeds per pod in seed canola was increased by pollen deposition, flower survival, and plant size, and was reduced in the centre of the female bay. 
Position in the female bay influenced pollen deposition, both by wind and insects, indicating that the decrease in seed number at the centre of the bay is ultimately caused by reduced pollen deposition from lower visitation \citep{mesquida1981,mesquida1982}.
Seeds per pod also increased with pollen deposition and plant size, but the effect size of pollen deposition (Z=2.3) was smaller than that of plant size (Z=5.6), suggesting that plant resources limit seed production more strongly than pollen deposition in seed canola.
\citet{mesquida1982} found that in seed canola, pod production, rather than seeds per pod, was the main variable that was reduced by low pollen deposition.
Interestingly, plant density had a positive effect on seed size in seed canola, pointing to a possible reduction in seed count because of shading or crowding, causing an increase in seed size (but see \citealp{angadi2003}).
%Increased plant density within a patch can lead to more pollinator visitation \citep{kunin1997}, but not necessarily more visits per flower \citep{klinkhamer1990}.  
%The between-year differences in commodity canola indicate an influence of weather, as air temperatures above 22$^\circ$C can cause flower sterility in canola \citep{morrison1992, gan2004}. %SH: EFFECT OF WEATHER GOES MUCH DEEPER THAN 22C THRESHOLD
%However, since year did not affect fruit set, the weather effect seems to be limited to ovules, rather than flower abortion (at least in this data set).
% Seeds per pod is highly correlated with ovule number \citep{clark1979,wang2011} and ovule fertility \citep{bouttier1992}, causing variance of seed within plants. 
%\citet{duran2010} showed that complete exclusion of insects (1 mm nets) from commodity canola plants reduced seeds per pod, but that partial exclusion (2.5mm) and control plots had similar seeds per pod.
%Net exclusion of insects can be problematic for comparing yields because exclosures can change microclimate (shade, wind reduction, increased humidity, \citealp{williams1987, kearns1993}), so exclosures may over- or under-estimate the effect of pollination \citep{ouvrard2019}.

%Seed size
Plant size was one of the dominant factors controlling seed size in seed canola, while in commodity canola, plant size did not influence seed size.
Plant size can positively influence seed size in some plant species \citep{maddox1983}, and this appears to be true in canola \citep{riffkin2012} as well as other Brassicaceae \citep{mazer1987}.
Similarly, seeds per pod and seed weight varied positively in commodity canola, this pattern was reversed in seed canola (Figure \ref{fig:seedWeightCount_both}). 
These differences likely occurred because of variation in available seed resources among the parts of the plant \citep{vanNoordwijk1986}, which can cause a positive size-number relationship even in resource-limited plants. 
In commodity canola, pollen is readily available, and there seems to be little difference between outcrossed- and self-pollen \citep{steffan2003, rosa2011}. 
Canola plants produce flowers from the bottom up, and produce fewer, smaller seeds at the ends of the branches because the younger pods have access to fewer resources at the end of the season \citep{sabbahi2006}, resulting in an increased rate of seed abortion \citep{clarke1979}.
Pods with low resources at the end of the season are forced to abort more ovules \citep{wang2011}, causing a positive relationship between seed number and size.
Thus, in commodity canola, variation in resources with plant size is masked by resource variation over time.  
In seed canola, pollen is much rarer (median: 7 grains/stigma vs. 155 in commodity), but plant sizes are similar (or larger) than commodity canola, such that plant resources are still available to developing pods at the end of the season.
This causes a size-number trade-off within pods that is mediated by plant size.
Most studies on commodity canola report a seed size-number trade-off at the level of plant \citep{angadi2003,koltowski2005}, we found a positive relationship at the pod level (but see \citealp{sabbahi2005}).
Perhaps within-plant resource variation is a more likely driver of seed number than pollen deposition, as pollination did not appear to be limiting (Figure \ref{fig:commoditySEM}, weak paths from pollen to yield metrics).
%While we did not quantify pod position on branches, the pods at the end of the branches did appear to have fewer seeds, meaning that some of the variation within plants likely occurred because of late-season seed.
%Why did the same species of plant experience such different relationships between seed size and seed number, and such different effects of plant size (a proxy of resource availability)?
%Because of this abundance of pollen, resource availability decreases over time as the plant matures ovules into seeds, becoming restricted at the end of the season.
% Ovule abortion in \textit{Brassica} is also higher at the beginning and end of the flowering season, likely because of a lower amount of high-quality pollen available at the tails of the season \citep{wang2011}.
% Similarly, the main raceme of canola tends to produce the most seeds per pod, with accessory branches producing fewer, smaller seeds, again due to flowers on branches being produced later in the season than the flowers on the main raceme \citep{clarke1979}.

\subsection{Summary} %RC: VERY CANOLA-FOCUSED
This study assesses the relative importance of pollination and plant resources for the production of canola crops, using field-realistic data from central and southern Alberta.
First, it shows that insect visitation changes across small spatial scales (meters for leafcutter bees, tens of meters for honey bees), and are at odds with the large scales of Albertan crop fields \citep{fritz2015}.
Visitation of both honey bees and leafcutter bees in canola fields is concentrated at the edge of fields, and is lower at the centre of the female bays in seed canola.	
Second, honey bees have little direct influence on pollen deposition in either crop system, likely due to a high background level of pollen deposition on stigmas in commodity canola, whereby extra pollen deposition is of little benefit to plant reproduction.
Seed canola plants, in contrast, have much lower levels of pollen deposition overall, and leafcutter bees deliver a large direct benefit to fruit and seed production. 
The centre of the female bays illustrates this effect: honey bees have a higher visitation rate, but pollen deposition, fruit set, and seed set are all lower.
Finally, both plant size and pollination limit seed production in seed canola, but only plant size limits commodity canola production, showing the relative importance of both pollination and plant resources using in-field data.

Several future lines of work could be followed based on this study.
First, other factors besides total seed yield are important for commodity canola production, such as green seed and oil content \citep{tautorus1994, abbadi2011, ghazani2013}.
Our work identified the effect of bee pollination on seed production in terms of total weight, but may have overlooked these aspects of yield valuation \citep{bommarco2012}. 
Secondly, we found that honey bees appear to add little pollination value for seed canola crops, but since we did not use fields that had no honey bees, there may be unobserved indirect benefits that honey bees add.
For example, they may contribute to better pollination by leafcutter bees by reducing the nectar and pollen standing crop, causing leafcutter bees to forager further away from their shelter \citep{pyke1978b, heinrich1979}, or by increasing the amount of airborne pollen \citep{eisikowitch1981,mesquida1982}.
Third, while the random-intercept model that we used accounts for field-to-field variation in growing conditions, this also means that we may have marginalized across other factors that were not accounted for by plant size, such as nutrients, soil moisture, crop pests, and variety.
Pollination benefits to all flowering crops are contextual, even in highly-pollination dependent crops \citep{tamburini2017, tamburini2019}; that is, the effect of additional pollination depends on the levels of other plant resources available during growth \citep{marini2015, bartomeus2015, gagic2017}.
Finally, SEMs cannot model causal loops \citep{grace2006}, which is closer to the method by which plants respond to lack of pollination (\emph{i.e.} pollination failure $\rightarrow$ plant growth $\rightarrow$ flower production).
Our model serves as an approximation of this process, but could be built upon by using dynamic linear programming techniques \citep{iwasa2000,nord2011} to examine how plants dynamically respond to pollen failure.
These would lend greater understanding to the process of hybrid seed production, and could be used to more accurately predict crop yields in novel scenarios.

%First, honey bees have lower per-visit pollen deposition on canola than \textit{Bombus} or \textit{Megachile} \citep{sahli2007, woodcock2013}.
%This can be compensated for by using a high density of honey bee hives in comparison to the crop area \citep{manning2005, clay2009}, but canola fields in Alberta are very large \citep{fritz2015}, so 
%This suggests that honey bees may not be beneficial to commodity canola production, at least at the low levels of visitation typically provided by smaller apiaries (20-40 hives per apiary) that are typically meant for honey production rather than pollination.
%Second, different canola varieties have different pollination dependence \citep{hudewenz2013}
%Most farmers in Alberta use hybrid varieties of canola, which may be less dependent on insect pollination than traditional canola \citep{lindstrom2016}, so extra pollination may provide very little benefit simply because hybrid varieties have a greater degree of self-compatibility, or are able to compensate for pollination failure better than open-pollinated varieties by producing extra branches and flowers.

\singlespacing

\bibliographystyle{humanbio}
\bibliography{references}
%\bibliography{\string{~/Documents/Papers/bibtexRefs/references}}

\clearpage %Supplemental material
\include{extra_supplemental}
\include{visitors_supplemental}
\include{models_supplemental}

\end{document}

### 2021-11-19 Manuscript/visitors_supplemental.tex
Started work on Manuscript

\pagebreak
%\widetext
\begin{center}
\textbf{\large Appendix B: Supplementary information on visitation}
\end{center}

\section*{Floral visitors in canola fields}

\begin{table}[h]
    \begin{tabular}{r|r|l|r|l}
     & \multicolumn{2}{c|}{Commodity fields} & \multicolumn{2}{c}{Seed fields} \\ \cline{2-5}
    Taxon & Visits & \% & Visits & \% \\ \hline
    Honey bee & 470 & 53.5 & 4850 & 77.1 \\
    Fly & 222 & 25.3 & 74 & 0.878 \\
    Hover fly & 94 & 10.7 & 151 & 1.79 \\
    Other bee & 47 & 5.35 & 30 & 0.356 \\
    Bumble bee & 25 & 2.85 & 0 & 0 \\
    Butterfly & 16 & 1.82 & 0 & 0 \\
    Leafcutter bee & 4 & 0.456 & 1675 & 19.9 \\
    % \hline
    % Total & 828 & - & 6780 & - \\
    \end{tabular}
    \caption[Flower visiting insects observed in commodity and seed canola fields]{Number of flower visitors recorded over a total of 44.8 hours of observation in commodity fields (2014 and 2015), and 46.9 hours of observation in the seed fields (2015 and 2016). ``Fly" refers to larger calyptrate muscoid flies (families Muscidae, Anthomyiidae, Caliphoridae), while ``Hover fly" refers to Syrphid flies. ``Other bee" included Halictid and Andrenid bees, while ``Bumble bee" was \textit{Bombus} spp. ``Butterfly" refers to all visiting Lepidopterans, mostly Pierids.}
    \label{tab:propVisitors}  
\end{table}

\section*{Top-working and side-working by honey bees in canola fields}

During 2015, we recorded whether honey bees were top-working or side-working flowers (see also \citealp{free1973, free1983, mohr1988}).
Top-working bees landed on the top of the flower and inserted their proboscis down between the petals to access the nectaries of the flower, while side-working bees landed on the side of the flower and stole nectar by inserted their proboscis between the petals, avoiding contact with the stigma or anthers. 
Additionally, we recorded whether honey bees were pollen or nectar foragers (pollen foragers had a visible pollen load on their corbicula, while nectar foragers had none).

\begin{table}
\begin{tabular}{r|r|l|r|l|r|l}
               & \multicolumn{2}{c|}{Commodity fields} & \multicolumn{2}{c|}{Seed fields (female bay)} & \multicolumn{2}{c}{Seed fields (male bay)} \\ \cline{2-7}
               & Top & Side & Top & Side & Top & Side           \\ \hline
Pollen forager & 44 & 2 & 12 & 0 & 115 & 0 \\
Nectar forager & 75 & 138 & 832 & 24 & 428 & 242 \\
% Total & 119 & 140 & 844 & 24 & 543 & 242
\end{tabular}
\caption[Foraging behaviours of honey bees on commodity and seed canola flowers]{Foraging behaviours of honey bees on commodity and seed canola flowers, recorded during 2015. ``Top" (top-working) indicates that the bee inserted their proboscis down between the petals from the top of the flower, while ``side" (side-working) indicates that the bee fed from the side of the flower and did not contact the anthers or stigma. Pollen foragers had pollen visible on their corbicula, while nectar foragers had none.}
\label{tab:sideWorking}
\end{table}

Pollen- and nectar-foraging honey bees had different patterns of side-working, both on commodity canola, and the male and female lines of seed canola.
Side-working was common in nectar foragers, but was more common in commodity canola (64\%) than in the male (36\%) or female bays (2.8\%) of seed canola, indicating that a large proportion of honey bees foraging on canola flowers may never come in contact with the stigmas.
Pollen foragers were almost uniformly top-foragers in both commodity and seed fields (Table \ref{tab:sideWorking}), and pollen foragers were much less common in the female bays (1.4\%) than in the male bays (15\%), or in commodity fields (18\%).
Therefore, foraging honey bees in seed canola fields tend to treat male-fertile flowers similar to commodity canola flowers, but seem to top-work flowers more in commodity canola than seed fields.
Leafcutter bee foraging behaviours were not recorded, but seemed to almost exclusively top-work flowers in seed canola fields.

### 2021-11-19 helperFunctions.R

@@ -1,0 +1,68 @@
+#HELPER FUNCTIONS FOR PATH ANALYSIS
+
+#Convenience functions
+logit <- function(x){
+  return(log(x/(1-x)))
+}
+invLogit <- function(x){ 
+  i <- exp(x)/(1+exp(x)) 
+  i[is.nan(i)] <- 1 #If x is large enough, becomes Inf/Inf = NaN, but Lim(invLogit) x->Inf = 1
+  return(i)
+}
+coefs <- function(L){ #Shorter summary from list of L coefficients from a Stan list
+  upr=sapply(L,function(x) round(quantile(x,0.975),3))
+  lwr=sapply(L,function(x) round(quantile(x,0.025),3))
+  meanCoef=sapply(L, mean); stdev=sapply(L, sd)
+  data.frame(median=sapply(L,function(x) round(median(x),3)),
+             lwr=lwr,upr=upr,mean=round(meanCoef,3),sd=round(stdev,3),z=round(meanCoef/stdev,3),
+             overlap=sapply(L,function(x) overlap(x)),
+             pval=round(2*(1-pnorm(abs(meanCoef/stdev),0,1)),4)) }
+#Faster pair plot
+fastPairs <- function(l){ #List l
+  pairs(l,lower.panel=function(x,y){
+    par(usr=c(0,1,0,1))
+    text(0.5, 0.5, round(cor(x,y),2), cex = 1 * exp(abs(cor(x,y))))})
+}
+#Function to calculate R2 for GLMMs. fixVar, ranVar and resVar are either variable names (vector of var names for random effects), or NA, indicating no effect specified
+r2calc <- function(mod,fixVar,ranVar,resVar){
+  fixed <- ifelse(!is.na(fixVar),sd(apply(mod[[fixVar]],2,median)),0) #fixed effect sd
+  if(!is.na(ranVar[1])){
+    ran <- 0
+    for(i in 1:length(ranVar)){ #Adds variances from all levels of random effects
+      ran <- ran + median(mod[[ranVar[i]]])
+    }
+  } else ran <- 0
+  res <- ifelse(!is.na(resVar),median(mod[[resVar]]),0) #residual variance
+  print(paste('Fixed effect var =',round(fixed,4)))
+  print(paste('Random effect var =',round(ran,4)))
+  print(paste('Residual var =',round(res,4)))
[…]

### 2021-11-19 yield path analysis.R

@@ -46,563 +46,9 @@ seedsAllSeed <- mutate(seedsAllSeed,Missing=ifelse(Missing<0,NA,Missing))
 rileyExtra <- read.csv('./Seed field analysis/rileyExtra.csv')
 setwd('~/Projects/UofC/canola_yield_project')
 
-#Convenience functions
-logit <- function(x){
-  return(log(x/(1-x)))
-}
-invLogit <- function(x){ 
-  i <- exp(x)/(1+exp(x)) 
-  i[is.nan(i)] <- 1 #If x is large enough, becomes Inf/Inf = NaN, but Lim(invLogit) x->Inf = 1
-  return(i)
-}
-coefs <- function(L){ #Shorter summary from list of L coefficients from a Stan list
-  upr=sapply(L,function(x) round(quantile(x,0.975),3))
-  lwr=sapply(L,function(x) round(quantile(x,0.025),3))
-  meanCoef=sapply(L, mean); stdev=sapply(L, sd)
-  data.frame(median=sapply(L,function(x) round(median(x),3)),
-             lwr=lwr,upr=upr,mean=round(meanCoef,3),sd=round(stdev,3),z=round(meanCoef/stdev,3),
-             overlap=sapply(L,function(x) overlap(x)),
-             pval=round(2*(1-pnorm(abs(meanCoef/stdev),0,1)),4)) }
-#Faster pair plot
-fastPairs <- function(l){ #List l
-  pairs(l,lower.panel=function(x,y){
-  par(usr=c(0,1,0,1))
-  text(0.5, 0.5, round(cor(x,y),2), cex = 1 * exp(abs(cor(x,y))))})
-}
-#Function to calculate R2 for GLMMs. fixVar, ranVar and resVar are either variable names (vector of var names for random effects), or NA, indicating no effect specified
-r2calc <- function(mod,fixVar,ranVar,resVar){
-  fixed <- ifelse(!is.na(fixVar),sd(apply(mod[[fixVar]],2,median)),0) #fixed effect sd
-  if(!is.na(ranVar[1])){
-    ran <- 0
-    for(i in 1:length(ranVar)){ #Adds variances from all levels of random effects
-      ran <- ran + median(mod[[ranVar[i]]])
-    }
-  } else ran <- 0
-  res <- ifelse(!is.na(resVar),median(mod[[resVar]]),0) #residual variance
[…]

### 2021-12-01 Manuscript/main.tex
Started working on manuscript

@@
 Commodity canola fields were selected based on the proximity of honey bee apiaries and site access. 
-28 of the 60 fields were stocked with honey bees (mean: 0.6 hives/hectare, SD: 0.58) while 32 fields were unstocked.
+28 of the 60 fields were stocked with honey bees at the corner or side of the field (mean: 0.6 hives/hectare, SD: 0.58) while 32 fields were unstocked.
 %range: 0.03 - 3.1 Apiaries were stationed at the edges of fields, often near to shrubs or tree-lines to act as a wind break.
 14 of 31 of the fields near Lethbridge were watered using central-pivot irrigation systems.
-% We assumed similar numbers of workers per colony at both localities.
 % Growers were asked for canola variety information, but there was not enough replication to test for difference between varieties. 
@@
 2.6 shelters/ha) in each field.
-Double stocking rates were only used in fields with double shelter density.
-%, creating three combinations of leafcutter bee stocking: ``standard", ``double shelter", and ``double shelter and double stocking".
+Double stocking rates were only used in fields with double shelter density, creating three combinations of leafcutter bee stocking: ``standard", ``double shelter", and ``double shelter and double stocking".
 All seed fields had central-pivot irrigation, and were mostly circular or semi-circular in shape.
@@
 
-In commodity fields, we established plots at 5, 20, 100, and 500m along a transect into the field, starting at the field margin closest to the set of honey bee hives (271 total plots).
+In commodity fields, we established 1 m$^2$ plots at 5, 20, 100, and 500m along a transect into the field, starting at the field margin closest to the set of honey bee hives (271 total plots).
 %used a Garmin\texttrademark eTrex20 GPS,
 In unstocked fields, we began the transect at a field edge close to potential sources of natural pollinating insects, such as forests or grasslands, but observed very few wild pollinators (Table \ref{tab:propVisitors}).
-In seed canola fields, bays of ``male" and ``female" plants were planted in 1- and 6-m wide bays, respectively, and leafcutter bee shelters were located in the female bays (Figure \ref{fig:seedfieldPhoto}, \ref{fig:seedfieldPlots}).
-We established plots at 5, 20, 100 (250 in 2016), and 400m into the field along a transect from the nearest set of honey bee hives.
-We made paired observations in adjacent male and female plots at each distance from the edge of the field (Figure \ref{fig:seedfieldPlots}).
-At the edge and centre of each field (5m and 400m), we established another plot in the centre of the female bay to examine the effect of distance away from the male bay.
-We also used plot-level leafcutter and honey bee visitation data from Waytes (\citeyear{waytesMsc}, and unpublished; same years and locations) to more accurately estimate the effect of distance from shelter on visitation rates (647 total plots).
+In seed canola fields, bays of ``male" and ``female" plants are typically planted in 1- and 6-m wide bays, respectively, and leafcutter bee shelters were located in the female bays (Figure \ref{fig:seedfieldPhoto}, \ref{fig:seedfieldPlots}).
+We established plots at 5, 20, 100 (250 in 2016), and 400m into the field along a transect from the nearest set of honey bee hives, using pairs of plots at the edge of adjacent male and female bays at each distance (Figure \ref{fig:seedfieldPlots}).
+Bee visitation can vary within female bays (Alfonso Parra, pers.
+comm.), so at the 5m and 400m plot in each field, we established another plot in the centre of the female bay to examine the effect of distance away from the male bay.
 We used a Nikon\texttrademark Laser 800S Rangefinder to measure the distance from each plot to the nearest shelter.
@@
 Mean air temperature was similar between years in Grande Prairie ($\approx$ 22$^\circ$C), but Lethbridge was warmer in 2015 (23 vs. 28$^\circ$C).
-Plots were marked with coloured stakes driven into the soil to locate them later in the season. %Full paper should have a table of climate variables. Windspeed needs sorting out (unit problems?)
+Finally, we incorporated plot-level visitation data from Waytes (\citeyear{waytesMsc}; same years and locations) to more accurately estimate the effect of distance from shelter on visitation rates (647 total plots).
+%Plots were marked with coloured stakes driven into the soil to locate them later in the season. %Full paper should have a table of climate variables. Windspeed needs sorting out (unit problems?)
 
-Within each 1m$^2$ plot, we recorded the number of insect contacting the stigmas and anthers of flowers during 10 minutes (5 min for seed fields during 2015), as well as their taxonomic identity.
-We counted visitable flowers in each plot, where ``visitable" was defined as an opened flower whose petals had not yet started to dehisce, and whose style had not elongated more than 3-4 millimeters beyond the anthers.
-To assess pollen deposition at the plot level, we collected stigmas from five random open, receptive flowers at each plot, mounted them in fuchsin gel \citep{beattie1971} on depression slides, and counted the pollen on each stigma using a Leica\texttrademark DME 13595 light microscope under 100x magnification (1294 commodity and 1050 seed canola stigmas).
-Each field was visited once during the main canola bloom (late June - late July), and again before harvest (mid - late August) to collect plant samples.
-We collected three plants and recorded the density of plants per m$^2$ at the same plot where we conducted the visitation observations (789 commodity canola plants, 582 seed canola plants).
-After drying the plants at 50$^\circ$C, we weighed the entire plant, counted mature pods, and counted the number of remaining flower pedicels to estimate total flower production.
-We randomly sampled five pods from each plant, and counted and weighed the seeds from each pod, (3872 commodity canola pods,  2885 seed canola pods).
-Finally, we threshed all the pods for each plant by hand, winnowed them using an air separator, and weighed the total mass of cleaned seeds.
+Insect visitation and pollination data was collected once during the main canola bloom at each field (late June - late July), and plants were collected before harvest (mid - late August).
+We recorded the number of insect visits that contacted the stigmas and anthers of flowers during 10 minutes of observation (5 min for seed fields during 2015), recorded the taxonomic group of the insect visitors, and counted the number of open, visitable flowers in each plot (petals had not yet started to dehisce, style had not elongated more than 3-4 millimeters beyond the anthers).
+To assess pollen deposition, we collected stigmas from five random open flowers at each plot, mounted them in fuchsin gel \citep{beattie1971} on depression slides, and counted the pollen on each stigma using a Leica\texttrademark DME 13595 light microscope under 100x magnification (1294 commodity and 1050 seed canola stigmas).
+At the end of the growing season, we collected three plants from the same plot and recorded the density of plants per m$^2$ (789 commodity canola plants, 582 seed canola plants).
+After drying the plants, we weighed the entire plant, counted mature pods, and counted the number of flower pedicels to estimate total flower production. % at 50$^\circ$C
+We randomly sampled five pods from each plant, and counted and weighed the seeds from each pod (3872 commodity canola pods, 2885 seed canola pods), then we threshed all the pods for each plant by hand, winnowed them using an air separator, and weighed the total mass of cleaned seeds.
 
@@
 To examine how yield is influenced by visitation, we used a piecewise structural equation model framework (pSEM, \citealp{shipley2009}).
-Structural equation models are comprised of a set of underlying linear models arranged in a causal network, and provides a framework for testing hypotheses about a complex system \citep{grace2012,lefcheck2015}.
+Structural equation models are comprised of a set of underlying linear models arranged in a causal network, and provides a framework for testing hypotheses about a complex system \citep{grace2012, lefcheck2015}.
 Starting with a simple model (visitation $\rightarrow$ pollen deposition $\rightarrow$ fruit production $\leftarrow$ plant resources), we built more complex models that related measured variables within a causal framework (Figures \ref{fig:commoditySEM} and \ref{fig:seedSEM}).
@@
 Fruit set can suppress future vegetative growth and flower production \citep{stephenson1981}, but SEMs do not allow for causal loops \citep{grace2012}, so we included a path from fruit set to flower production.
-The direction of the path could plausibly be reversed (whereby large number of flowers reduce the proportion of fruit set), but we considered only the first scenario, as \citet{sabbahi2006} showed that the converse process is more likely (low fruit set causes increased flower production).
+The direction of the path could plausibly be reversed (where large number of flowers reduce the proportion of fruit set), but we considered only the first scenario, as \citet{sabbahi2006} showed that the converse process is more likely (low fruit set causes increased flower production).
 
 The underlying models of each pSEM were specified as generalized linear mixed-effects models (GLMMs, see Equation sets S1 and S2 for model specifications).
-We used hierarchical models in order to include processes that occur at different levels; for example, seed size-number trade-offs were modelled at the pod level, whereas pollen deposition was modeled at the flower level.
-Normal random effects were used to model variance between fields, within-field (pollen, flower survival, seed count \& size), and within-plot (seed count \& size); if the lowest-level variance term was inestimable, we fit the model without it.
+We used hierarchical (random effects) models to model processes that occur at different levels; for example, seed size-number trade-offs were modelled at the pod level, whereas pollen deposition was modeled at the flower level.
+Random intercepts were used to model variance between fields, within-field (pollen, flower survival, seed count \& size), and within-plot (seed count \& size).
 Continuous responses were modeled using log-normal (plant density, plant size), square-root normal (flower density), and exponential-normal distributions (weight per seed), while counts were modeled as a negative-binomial (honey bee visits, pollen grains per stigma, flowers per plant, seeds per pod) or zero-inflated negative-binomial distribution (leafcutter bee visits) with a log-link function.
@@
 Interactions between predictors were evident in honey bee visitation rate (Year:Locality interaction) and plant density (Irrigation:Year) in commodity canola, and for leafcutter bee visitation (Tent Stocking:Distance from edge) in seed canola, and were included in each model (represented as Y-shaped path in Figures \ref{fig:commoditySEM} and \ref{fig:seedSEM}).
-Finally, we created bivariate partial-effect plots of relevant terms within each model to aid in visualising each relationship.
+%Finally, we created bivariate partial-effect plots of relevant terms within each model to aid in visualising each relationship.
 
@@
 
-%RC: REMIND READER OF THE EXPECTATIONS, AND WHETHER HYPOTHESES WERE SUPPORTED/REJECTED, RATHER THAN JUST STATING THE RESULTS
-%SH: 1) SET UP LOGIC MORE CLEARLY, FOLLOW IT THROUGH IN SAME WAY AS THE REST OF THE PAPER
-%2) BE CONSISTENT IN WORDS/PHRASES
-%3) BREAK UP PARAGRAPHS & PROVIDE MORE TRANSITION SENTENCES
-%4) TALK ABOUT THE REAL WORLD AS MUCH AS POSSIBLE, RATHER THAN VARIABLES
-
 \section{Results}
-
-%OVERALL SUMMARY FROM SEMS
 

### 2021-12-01 yield path analysis.R

@@ -224,10 +224,19 @@ inits <- function() { with(datalist,
 # mod1 <- extract(claims1)
 # coefs(mod1[c(pars,newpar)])
  
-#Full model - 1.7 hrs for 1000 iter
-modPodcount <- stan(file='visitation_pollen_model.stan',data=datalist,iter=1,chains=1,
-                   control=list(adapt_delta=0.8),init=inits)
+# #Full model - 1.7 hrs for 1000 iter
+# modPodcount <- stan(file='visitation_pollen_model.stan',data=datalist,iter=1,chains=1,
+#                    control=list(adapt_delta=0.8),init=inits)
 
+
+#Smaller example - only visitation
+# datalist <- datalist
+modPodcount <- stan(file='visitation_pollen_model2.stan',data=datalist,iter=2000,chains=3,
+                   control=list(adapt_delta=0.8),init=inits)
+print(modPodcount)
+traceplot(modPodcount,pars=c('intVisit',
+                             'slopeDistVis','slopeHiveVis','slopeFlDens', #Visitation
+                             'sigmaVisField','lambdaVisField','visitHbeePhi'))
 
 beep(1)
 # save(modPodcount,file='modPodcount.Rdata')

### 2021-12-07 Seed field analysis/canola seed pollination 2016.R
Updated yield model

@@ -89,8 +89,9 @@ survey=rename(survey,FlDens=Fls.50cm.2) %>%
   #Minimum distance to leafcutter shelter
   mutate(Surveyed=as.Date(Surveyed,format='%b %d, %Y'),minDist=min(LeafShelter1,LeafShelter2,LeafShelter3,LeafShelter4,na.rm=T)) %>%
   select(-LeafShelter1:-LeafShelter4) %>%
-  mutate(StartTime=as.POSIXct(paste(Surveyed,StartTime),format='%b %d, %Y %H:%M'),
-         EndTime=as.POSIXct(paste(Surveyed,EndTime),format='%b %d, %Y %H:%M')) %>%
+  mutate(StartTime=paste(Surveyed,StartTime),EndTime=paste(Surveyed,EndTime)) %>% 
+  mutate(StartTime=as.POSIXct(StartTime,format='%Y-%m-%d %H:%M'),
+         EndTime=as.POSIXct(EndTime,format='%Y-%m-%d %H:%M')) %>%
   mutate(Surveyed=as.Date(Surveyed,format='%b %d, %Y %H:%M'))
 
 #Pollen data

### 2021-12-07 yield path analysis.R

@@ -34,9 +34,6 @@ plantsAllSeed$Field <- gsub('Unrah','Unruh',plantsAllSeed$Field) #Fixes spelling
 seedsAllSeed$Field <- gsub('Unrah','Unruh',seedsAllSeed$Field)
 seedsAllSeed$EdgeCent <- ifelse(seedsAllSeed$EdgeCent=='Cent','Center',seedsAllSeed$EdgeCent) #Fixes cent/center
 rm(allFields,allPlants,allPollen,allSeeds,allSurvey,behav2015,visitors2016,nectar2016,folder)
-#Remove Warnock 4 - plants/seeds observed but not field
-plantsAllSeed <- filter(plantsAllSeed,Field!='Warnock 4')
-seedsAllSeed <- filter(seedsAllSeed,Field!='Warnock 4')
 #Set 'negative' missing pods (mistake in counting) to NA.
 plantsAllComm <- mutate(plantsAllComm,Missing=ifelse(Missing<0,NA,Missing))
 plantsAllSeed <- mutate(plantsAllSeed,Missing=ifelse(Missing<0,NA,Missing))
@@ -150,6 +147,9 @@ datalistPod$seedMass[datalistPod$seedMass>8] <- with(datalistPod,seedMass[seedMa
 datalist <- c(datalistField,datalistPlot,datalistFlw,datalistPlant,datalistPod)
 rm(datalistField,datalistPlot,datalistFlw,datalistPlant,datalistPod,a,b,keep) #Cleanup
 str(datalist)
+
+#Check for NAs
+if(any(sapply(datalist,function(x) sum(is.na(x)))>0)) print("NAs found in datalist")
  
 inits <- function() { with(datalist,
   list(plDens_miss=rep(0,Nplot_densMiss),intPlDens=1, slopeGPPlDens=0, #Plant density
@@ -224,52 +224,54 @@ inits <- function() { with(datalist,
 # mod1 <- extract(claims1)
 # coefs(mod1[c(pars,newpar)])
  
-# #Full model - 1.7 hrs for 1000 iter
-# modPodcount <- stan(file='visitation_pollen_model.stan',data=datalist,iter=1,chains=1,
+#Full model - 1.7 hrs for 1000 iter
+modPodcount <- stan(file='visitation_pollen_model.stan',data=datalist,iter=1,chains=1,
+                   control=list(adapt_delta=0.8),init=0)
+
+# #Smaller example - only visitation
+# # datalist <- datalist
[…]

### 2021-12-08 Manuscript/main.tex
Updated models

@@
 \subsection{Analysis}
-To examine how yield is influenced by visitation, we used a piecewise structural equation model framework (pSEM, \citealp{shipley2009}).
-Structural equation models are comprised of a set of underlying linear models arranged in a causal network, and provides a framework for testing hypotheses about a complex system \citep{grace2012, lefcheck2015}.
-Starting with a simple model (visitation $\rightarrow$ pollen deposition $\rightarrow$ fruit production $\leftarrow$ plant resources), we built more complex models that related measured variables within a causal framework (Figures \ref{fig:commoditySEM} and \ref{fig:seedSEM}).
-These models allowed us to infer the relative strength of the main terms (e.g. pollen deposition, plant size) while controlling for other confounding factors (e.g. distance into field).
-Fruit set can suppress future vegetative growth and flower production \citep{stephenson1981}, but SEMs do not allow for causal loops \citep{grace2012}, so we included a path from fruit set to flower production.
-The direction of the path could plausibly be reversed (where large number of flowers reduce the proportion of fruit set), but we considered only the first scenario, as \citet{sabbahi2006} showed that the converse process is more likely (low fruit set causes increased flower production).
+To examine how yield is influenced by visitation, we used piecewise structural equation models (pSEM, \citealp{shipley2009}).
+Structural equation models are a set of linear models arranged in a causal network, which provides a framework for testing hypotheses about complex systems \citep{grace2012, lefcheck2015}.
+Starting with a simple model (visitation $\rightarrow$ pollen deposition $\rightarrow$ fruit production $\leftarrow$ plant resources), we built a detailed model relating visitation to pollination to seed yield within a causal framework (Figures \ref{fig:commoditySEM} and \ref{fig:seedSEM}).
+These models allowed us to model how visitation ultimately influences seed yield, while controlling for other confounding factors (e.g. distance into field, measurements taken at different fields).
+Fruit set can suppress future vegetative growth and flower production \citep{stephenson1981}, but SEMs do not allow for causal loops \citep{grace2012}, so we included a path from fruit set to flower production as the closest approximation of this process.
+The direction of the path could plausibly be reversed (implying that large flower production reduces the proportion of fruit set), but we considered only the first scenario, as \citet{sabbahi2006} showed that the converse process is more likely (where low fruit set causes increased flower production).
 
 The underlying models of each pSEM were specified as generalized linear mixed-effects models (GLMMs, see Equation sets S1 and S2 for model specifications).
-We used hierarchical (random effects) models to model processes that occur at different levels; for example, seed size-number trade-offs were modelled at the pod level, whereas pollen deposition was modeled at the flower level.
+We used GLMMs to model processes that occur at different levels; for example, seed size-number trade-offs were modelled at the pod level, whereas pollen deposition was modeled at the flower level.
 Random intercepts were used to model variance between fields, within-field (pollen, flower survival, seed count \& size), and within-plot (seed count \& size).
 Continuous responses were modeled using log-normal (plant density, plant size), square-root normal (flower density), and exponential-normal distributions (weight per seed), while counts were modeled as a negative-binomial (honey bee visits, pollen grains per stigma, flowers per plant, seeds per pod) or zero-inflated negative-binomial distribution (leafcutter bee visits) with a log-link function.
-Visitation models used a $log$(time) term with a slope of 1 (``offset" variable) to account for differences in observation times.
-Fruit set (fraction of flowers that matured into pods) was modeled using a beta-binomial distribution with a logit-link function.
+Visitation models used $log$(time) as an ``offset" variable to account for differences in observation times.
+Pod set (fraction of flowers that matured into pods) was modeled using a beta-binomial distribution with a logit-link function.
 Interactions between predictors were evident in honey bee visitation rate (Year:Locality interaction) and plant density (Irrigation:Year) in commodity canola, and for leafcutter bee visitation (Tent Stocking:Distance from edge) in seed canola, and were included in each model (represented as Y-shaped path in Figures \ref{fig:commoditySEM} and \ref{fig:seedSEM}).
-%Finally, we created bivariate partial-effect plots of relevant terms within each model to aid in visualising each relationship.
 
-Structural equation models do not have paths between all variables, which may bias the model results if this independence assumption is not true. 
-We evaluated evaluating independence claims (``basis set") by using Fisher's C statistic from Shipley's d-separation criteria \citep{shipley2000, shipley2009}.
-The initial commodity canola pSEM was misspecfied, as several missing paths were identified for the initial commodity model (Fisher's C=202.1, df=100, p$<<$0.001), but the updated pSEM that included missing paths was judged adequate (C=81.6, df=86, p=0.62).
-Similarly, the initial seed field pSEM also had several missing paths (C=37.54, df=56, p=0.027), which we corrected (C=58.10, df=64, p=0.68).
-D-separation criteria sets were generated using the \texttt{dagitty} library in R 3.5.1.
+Structural equation models do not have paths between all variables, which may bias the model results if this independence assumption is incorrect; this requires testing a ``basis set" of independence claims using Shipley's d-separation criteria \citep{shipley2000, shipley2009}.
+The initial commodity canola pSEM was misspecfied, as several missing paths were identified for the initial commodity model (Fisher's C = 202.1, df = 100, p$<<$0.001), but the updated pSEM that included missing paths was adequate (C = 81.6, df = 86, p = 0.62).
+Similarly, the initial seed field pSEM also had several missing paths (C = 37.54, df = 56, p = 0.027), which we corrected (C = 58.10, df = 64, p = 0.68).
+Basis sets were generated using the \texttt{dagitty} library in R 3.5.1.
 

### 2021-12-08 yield path analysis.R

@@ -51,7 +51,7 @@ source('helperFunctions.R')
 library(rstan)
 setwd('./Models')
 rstan_options(auto_write = TRUE)
-options(mc.cores = 4)
+options(mc.cores = 5)
 # library(shinystan)
 
 #List structure for Stan
@@ -149,7 +149,9 @@ rm(datalistField,datalistPlot,datalistFlw,datalistPlant,datalistPod,a,b,keep) #C
 str(datalist)
 
 #Check for NAs
-if(any(sapply(datalist,function(x) sum(is.na(x)))>0)) print("NAs found in datalist")
+if(any(sapply(datalist,function(x) sum(is.na(x)))>0)){
+  beep(1); print("NAs found in datalist")
+}
  
 inits <- function() { with(datalist,
   list(plDens_miss=rep(0,Nplot_densMiss),intPlDens=1, slopeGPPlDens=0, #Plant density
@@ -205,6 +207,13 @@ inits <- function() { with(datalist,
    ))
 }
 
+# #Look at distributions of average seedcount/seedmass
+# tempdat <- with(datalist,data.frame(avgSeedCount,avgSeedMass,
+#                          plantIndex=factor(plantIndex)))
+# par(mfrow=c(2,1))
+# lm(avgSeedCount~plantIndex,data=tempdat) %>% plot(.,which=c(1,2)) #Looks normal-ish to me
+# lm(avgSeedMass~plantIndex,data=tempdat) %>% plot(.,which=c(1,2))
+
 # #Feed datalist into stan_rdump for use in CmdStan
 # with(datalist,stan_rdump(names(datalist),'tempDat.data.R'))
 # #Feed inits into stan_rdump
@@ -224,9 +233,9 @@ inits <- function() { with(datalist,
 # mod1 <- extract(claims1)
 # coefs(mod1[c(pars,newpar)])
  
-#Full model - 1.7 hrs for 1000 iter
-modPodcount <- stan(file='visitation_pollen_model.stan',data=datalist,iter=1,chains=1,
-                   control=list(adapt_delta=0.8),init=0)
+# #Full model - 1.7 hrs for 1000 iter
+# modPodcount <- stan(file='visitation_pollen_model.stan',data=datalist,iter=1,chains=1,
+#                    control=list(adapt_delta=0.8),init=0)
 
 # #Smaller example - only visitation
 # # datalist <- datalist
[…]

### 2021-12-08 Manuscript/main.tex
Broke model into pieces for easier debugging

@@
 All component GLMMs of the pSEM were written in Stan 2.17.1 \citep{gelman2015}, and run using \texttt{rstan} 2.18.1.
-We used informative normal priors ($\mu=0, \sigma=5$) for fixed effects, and gamma priors ($\alpha=1, \beta=1$) for the variance components.
-We ran three separate chains with an adaptive phase of 2000 iterations, and a sampling phase of 2000 iterations, then checked for convergence of the chains ($\hat{R} \approx$1) and low autocorrelation within chains (high $N_{eff}$).
+We used informative normal priors ($\mu=0, \sigma=5$) for fixed effects, and gamma priors ($\alpha=1.05, \beta=1$) for the variance components.
+We ran four separate chains with an adaptive phase of 1000 iterations, and a sampling phase of 1000 iterations, then checked for convergence of the chains ($\hat{R} \approx$1) and low autocorrelation within chains (high $N_{eff}$).
 We assessed the adequacy of the underlying probability distribution functions of each model using posterior predictive checks \citep{gelman2013}, and found that the probability distributions were specified correctly (p$\sim$0.5) for all components except seed count.
@@
 
-\subsection{Visitation}
-
-\subsection{Pollen Deposition}
-
-\subsection{Seed Production}
-
-The SEMs revealed that plant size and pollen deposition were the main drivers of yield in seed canola, while only plant size mattered in commodity canola.
-Distance from the field edge had a negative effect on honey bee visitation in commodity and seed canola (Z=-3.7, -2.5, respectively), and unexpectedly, had a negative effect on leafcutter bee visitation (Z= -4.4), showing that overall visitation decreases with distance into the field.
+Plant size and pollen deposition were the main drivers of yield in seed canola, while plant size was the main driver of yield in commodity canola.
+Distance from the field edge had a negative effect on honey bee visitation in both commodity and seed canola (Z=-3.7, -2.5, respectively), and unexpectedly, had a negative effect on leafcutter bee visitation (Z= -4.4), showing that overall visitation decreases with distance into the field.
 The path from leafcutter bee visitation to pollen deposition was strong in seed canola (Z=3.2), but there was no path from honey bee visitation to pollen deposition in either crop type.
@@
 
-\subsection{Prediction 1: Decline in visitation with distance}
+\subsection{Visitation}
+
 Bee visitation strongly declined with distance away from the hives and shelters, in both commodity and seed canola fields. 
-In commodity canola, honey bee visitation sharply declined with distance into the field (Z=-3.7, p$=$0.0002, Figure \ref{fig:hbeeDist_commodity}), decreasing from 8.5 visits/hr at the edge of the field to 3.1 visits/hr at 100 m into the field (at a stocking level of 20 hives).
-Visitation rates were higher in both years in Lethbridge (2014: 9.3 visits/hr, 2015: 7.1), but were higher in 2015 than 2014 at Grande Prairie (Z=2.3, p$=$0.02), rising from 5 visits/hr at the field edge in 2014 to 17 visits/hr in 2015.
+In commodity canola, honey bee visitation declined with distance into the field (Z=-3.7, p$=$0.0002, Figure \ref{fig:hbeeDist_commodity}), decreasing from 8.5 visits/hr at the edge of the field to 3.1 visits/hr at 100 m into the field (at a stocking level of 20 hives).
+% Visitation rates were higher in both years in Lethbridge (2014: 9.3 visits/hr, 2015: 7.1), but were higher in 2015 than 2014 at Grande Prairie (Z=2.3, p$=$0.02), rising from 5 visits/hr at the field edge in 2014 to 17 visits/hr in 2015.
 % (at a stocking level of 20 hives).
-Honey bee visitation increased with the number of hives used for stocking (Z=5.3, p$<$0.0001); plot-level visitation at the edge of the field increased from 14.5 visits/hr with an apiary of 20 hives to 22.7 visits/hr with an apiary of 40 hives, while unstocked field edges had 1.8 visits/hr.
+Honey bee visitation increased with the number of hives used for stocking (Z=5.3, p$<$0.0001); plot-level visitation at the edge of the field increased from 14.5 visits/hr with an apiary of 20 hives to 22.7 visits/hr with an apiary of 40 hives, while unstocked field edges had an average of 1.8 visits/hr.
 In seed canola fields, honey bee visitation also declined with distance into the field (Z=-2.5, p$=$0.01), but not as strongly as in commodity fields (126 visits/hr at edge of field vs.
 78 visits/hr at 100 m).
-Honey bee visitation was lower near leafcutter shelters (Z=3.9, p$=$0.001), dropping from 60 visits/hr at 10 m to 34 visit/hr at 2 m, likely due to competition with leafcutter bees (Figure \ref{fig:hbeeDist_both}, \ref{fig:lbeeDist_both}).
+Honey bee visitation was lower near leafcutter shelters (Z=3.9, p$=$0.001), dropping from 60 visits/hr at 10 m to 34 visits/hr at 2 m, likely due to competition with leafcutter bees (Figure \ref{fig:hbeeDist_both}, \ref{fig:lbeeDist_both}).
 
-Leafcutter bees were much more sensitive to distance from their shelter than honey bees.
-Leafcutter bee visitation sharply declined with distance from their shelters (Z=-11.4, p$=$0.0001, 350 visit/hr at 2 m to 83 visit/hr at 10 m), and unexpectedly, was higher at the edge of the field than the centre (Z=-4.4, p$=$0.0001, 114 visits/hr vs 28 visits/hr).
+Leafcutter bees were much more sensitive to distance than honey bees, and visitation declined quickly with distance from their shelters (Z=-11.4, p$=$0.0001, 350 visit/hr at 2 m to 83 visit/hr at 10 m), and unexpectedly, was higher at the edge of the field than the centre (Z=-4.4, p$=$0.0001, 114 visits/hr vs 28 visits/hr).
 However, there was no difference in visitation rates when the stocking rate of cocoons per shelter was lower (Z=2.2, p$=$0.028), indicating that leafcutters at high stocking densities may migrate to shelters close to the edge of the field (Figure \ref{fig:hbeeDist_both}).
@@
 
-\subsection{Prediction 2: Pollen deposition increased by bee visitation}
-Pollen deposition was enhanced by bee visitation in seed canola, but not in commodity canola.
-In commodity canola, pollen deposition on stigmas was high (mean: 293 grains per stigma, SD: 385, range: 0--3981), but honey bee visitation did not affect deposition (p$=$0.77, Figure \ref{fig:hbeeVisPol}).
-Pollen grains per stigma weakly declined with distance from the edge of the field (p$=$0.07), but this only amounted to an average decrease of 290 grains per stigma at the edge compared to 240 at the field centre (6\% decrease), meaning that distance did not strongly affect pollen deposition either.
-Flies were common visitors in commodity fields (Table \ref{tab:propVisitors}), but had no detectable effect on pollen deposition (p$=$0.577), and other flower visitors were rare, so only honey bees and leafcutter bees were considered as potential pollinators.
-In seed canola, overall pollen deposition was much lower (mean: 22 grains per stigma, SD: 43, range: 0--578), was strongly increased by leafcutter bee visitation (Z=3.2, p$=$0.002, Figure \ref{fig:visPol_both}, 12 grains/stigma at 6 visits/hr vs.
+\subsection{Pollen Deposition}
+
+Leafcutter bee visitation increased pollen deposition in seed canola, but honey bees did not increase pollen deposition in either commodity or seed canola.
+Pollen deposition on stigmas was high in commodity canola (mean: 293 grains per stigma, SD: 385, range: 0--3981), but honey bee visitation did not effect deposition (p$=$0.77, Figure \ref{fig:hbeeVisPol}).
+Pollen deposition declined with distance from the edge of the field (p$=$0.07), but this only amounted to a 6\% average decrease (290 grains per stigma at the edge, 240 at field centre).
+Flies were common visitors in commodity fields (Table \ref{tab:propVisitors}), but had no effect on pollen deposition (p$=$0.577), so only honey bees and leafcutter bees were considered as potential pollinators (other flower visitors were rare).
+In seed canola, pollen deposition was much lower (mean: 22 grains per stigma, SD: 43, range: 0--578), and leafcutter bee visitation had a strong positive effect (Z=3.2, p$=$0.002, Figure \ref{fig:visPol_both}, 12 grains/stigma at 6 visits/hr vs.
 16 pollen grains at 60 visits/hr), and also decreased with distance from the edge of field (Z=-4.4, p$=$0.0001, Figure \ref{fig:distCentPol}, 23 vs.
@@
 13 grains/stigma) independent of visitation rate, suggesting that pollen is lost from bees crossing from male bays, who likely visit flowers at the edge of the bay first \citep{pinnisch1990}.
-There was no direct effect of honey bees on pollen deposition (Z=0.98, p$=$0.33), implying that most of the pollen deposition occurs via leafcutter visitation.
+Finally, there was no effect of honey bees on pollen deposition in seed canola fields (Z=0.98, p$=$0.33), implying that most of the pollen deposition is the result of leafcutter visitation.
 
@@
 \end{figure}
+
+\subsection{Seed Production}
 

### 2021-12-08 yield path analysis.R

@@ -27,7 +27,7 @@ fieldsAllComm <- fieldsAll; flowersAllComm <- flowersAll; plantsAllComm <- plant
 seedsAllComm <- seedsAll; surveyAllComm <- surveyAll;
 rm(fieldsAll,flowersAll,plantsAll,seedsAll,surveyAll)
 #Seed field data
-load("./Seed field analysis/seedFieldDataAll.RData")
+load("./Seed field analysis/seedfieldDataAll.RData")
 fieldsAllSeed <- allFields; plantsAllSeed <- allPlants; pollenAllSeed <- allPollen; seedsAllSeed <- allSeeds;
 surveyAllSeed <- allSurvey; 
 plantsAllSeed$Field <- gsub('Unrah','Unruh',plantsAllSeed$Field) #Fixes spelling error
@@ -50,8 +50,8 @@ source('helperFunctions.R')
 # Commodity field visitation and pollen deposition (Stan) ---------------------------------
 library(rstan)
 setwd('./Models')
-rstan_options(auto_write = TRUE)
-options(mc.cores = 5)
+rstan_options(auto_write = TRUE) #Avoids recompilation
+options(mc.cores = 6)
 # library(shinystan)
 
 #List structure for Stan
@@ -247,15 +247,31 @@ inits <- function() { with(datalist,
 # 
 # print(modPodcount,pars=p)
 # traceplot(modPodcount,pars=p)
-
+#
 #Version without pod-level effects
+# #NOTE: something's going wrong with the plant level flower count/survival. Models before this are OK, but collapse once these are added. Dropping plot-level random intercepts doesn't help.
+# modPodcount <- stan(file='visitation_pollen_model3.stan',data=datalist,iter=2000,chains=6,
+#                     control=list(adapt_delta=0.8),init=0); beep(1)
+# # save(modPodcount,file='modPodcount3.Rdata')
 
-#NOTE: something's going wrong with the plant level flower count/survival. Models before this are OK, but collapse once these are added. Dropping plot-level random intercepts doesn't help.
+#Models split into separate stan files (faster)
+modFiles <- dir(pattern = 'commodity.*\\.stan')
[…]

### 2021-12-10 Manuscript/main.tex
Worked on commodity model
- Problem with flwSurv model: betabinomial model won't converge, and binomial has bad posterior predictive check (summed variance)

@@
-\documentclass[12pt]{article} % use larger type; default would be 10pt
+\documentclass[12pt, draft]{article} % use larger type; default would be 10pt
 
@@
 
-Plant size and pollen deposition were the main drivers of yield in seed canola, while plant size was the main driver of yield in commodity canola.
-Distance from the field edge had a negative effect on honey bee visitation in both commodity and seed canola (Z=-3.7, -2.5, respectively), and unexpectedly, had a negative effect on leafcutter bee visitation (Z= -4.4), showing that overall visitation decreases with distance into the field.
-The path from leafcutter bee visitation to pollen deposition was strong in seed canola (Z=3.2), but there was no path from honey bee visitation to pollen deposition in either crop type.
-Pollen deposition increased fruit set (Z=3.1) and seeds per pod (Z=2.3) in seed canola, but was not present in commodity canola, showing that yield in seed canola, but not commodity canola, is strongly dependent on pollination.
-%The path from seeds per pod to weight per seed was negative in seed canola (Z=-15.0) but positive in commodity canola (Z=6.1) 
-Both crop types had strong negative paths from flower survival to flowers per plant (commodity Z=-12.5, seed Z=-12.1), indicating that high flower survival suppressed future flower production.
-Commodity canola had a similar weight per seed, regardless of the plant size, but in seed canola, plant size had a strong influence on seeds per pod (Z=5.6) and weight per seed (4.6).
-Finally, in both crop types, the paths leading from plant size were the dominant signal influencing fruit set (commodity Z=5.8; seed Z=19.9), but the path from pollen deposition to fruit set was only present in seed canola, showing that plant resources matter strongly for both crop types, but that increased pollen deposition only benefits seed canola.
+% %This could probably be reduced to a blurb
+% Plant size and pollen deposition were the main drivers of yield in seed canola, while plant size was the main driver of yield in commodity canola.
+% Distance from the field edge had a negative effect on honey bee visitation in both commodity and seed canola (Z=-3.7, -2.5, respectively), and unexpectedly, had a negative effect on leafcutter bee visitation (Z= -4.4), showing that overall visitation decreases with distance into the field.
+% The path from leafcutter bee visitation to pollen deposition was strong in seed canola (Z=3.2), but there was no path from honey bee visitation to pollen deposition in either crop type.
+% Pollen deposition increased fruit set (Z=3.1) and seeds per pod (Z=2.3) in seed canola, but was not present in commodity canola, showing that yield in seed canola, but not commodity canola, is strongly dependent on pollination.
+% %The path from seeds per pod to weight per seed was negative in seed canola (Z=-15.0) but positive in commodity canola (Z=6.1) 
+% Both crop types had strong negative paths from flower survival to flowers per plant (commodity Z=-12.5, seed Z=-12.1), indicating that high flower survival suppressed future flower production.
+% Commodity canola had a similar weight per seed, regardless of the plant size, but in seed canola, plant size had a strong influence on seeds per pod (Z=5.6) and weight per seed (4.6).
+% Finally, in both crop types, the paths leading from plant size were the dominant signal influencing fruit set (commodity Z=5.8; seed Z=19.9), but the path from pollen deposition to fruit set was only present in seed canola, showing that plant resources matter strongly for both crop types, but that increased pollen deposition only benefits seed canola.
 
@@
 
+\begin{table}
+\centering
+\caption{Summary of main measured variables. Vegetative mass refers to the non-seed plant mass.}
+\begin{tabular}{r|llllll|llllll}
+                                       & \multicolumn{6}{l|}{Commodity Fields}           & \multicolumn{6}{l}{Seed Fields}                    \\
+Parameter                              & Min  & Median & Mean   & Max   & SD     & N    & Min    & Median & Mean   & Max    & SD     & N     \\ \hline
+Honey bee visitation (per min)      & 0    & 0      & 0.17   & 3.64  & 0.48   & 271  & 0      & 2      & 14.15  & 215    & 25.13  & 665   \\
+Leafcutter bee visitation (per min) & -    & -      & -      & -     & -      & -    & 0      & 2      & 13.93  & 212    & 25.49  & 665   \\
+Pollen (\# per stigma)                 & 0    & 155    & 293.32 & 3891  & 385.04 & 1355 & 0      & 7      & 21.76  & 578    & 42.53  & 1080  \\
+Flowers per plant                      & 13   & 157    & 196.05 & 1094  & 150.87 & 789  & 26     & 362.50 & 461.33 & 2712   & 326.59 & 600   \\
+Pods per plant                         & 5    & 112    & 143.17 & 892   & 114.57 & 789  & 10     & 244.50 & 299.41 & 1410   & 207.68 & 600   \\
+Seeds per pod                          & 4.6  & 23.6   & 22.95  & 35.4  & 4.97   & 789  & 1.8    & 16.6   & 16.40  & 30.60  & 5.52   & 600   \\
+Weight per 1000 seeds (g)              & 0.39 & 2.72   & 2.74   & 5.35  & 0.8    & 789  & 1.04   & 3.42   & 3.43   & 5.59   & 0.88   & 600  \\
+Total vegetative mass (g)                    & 0.77 & 14.29  & 18.19  & 110.2 & 14.41  & 789  & 1.1849 & 25.20  & 30.32  & 144.32 & 21.16  & 600   \\
+Total seed mass (g)                          & 0.01 & 5.46   & 6.87   & 47.9  & 5.97   & 789  & 0.02   & 7.54   & 9.50   & 60.77  & 7.90   & 600   
+\end{tabular}
+\end{table}
+
 \subsection{Visitation}
 
-Bee visitation strongly declined with distance away from the hives and shelters, in both commodity and seed canola fields. 
-In commodity canola, honey bee visitation declined with distance into the field (Z=-3.7, p$=$0.0002, Figure \ref{fig:hbeeDist_commodity}), decreasing from 8.5 visits/hr at the edge of the field to 3.1 visits/hr at 100 m into the field (at a stocking level of 20 hives).
+Honey bee visitation decreased with distance away from the apiary, in both commodity and seed canola fields.
+In commodity fields, honey bee visitation decreased with distance from the apiary at the field edge (Z=-3.7, p$=$0.0002, Figure \ref{fig:hbeeDist_commodity}), decreasing from 8.5 visits/hr at the edge of the field to 3.1 visits/hr at 100 m into the field (given a stocking level of 20 hives).
 % Visitation rates were higher in both years in Lethbridge (2014: 9.3 visits/hr, 2015: 7.1), but were higher in 2015 than 2014 at Grande Prairie (Z=2.3, p$=$0.02), rising from 5 visits/hr at the field edge in 2014 to 17 visits/hr in 2015.
 % (at a stocking level of 20 hives).
-Honey bee visitation increased with the number of hives used for stocking (Z=5.3, p$<$0.0001); plot-level visitation at the edge of the field increased from 14.5 visits/hr with an apiary of 20 hives to 22.7 visits/hr with an apiary of 40 hives, while unstocked field edges had an average of 1.8 visits/hr.
-In seed canola fields, honey bee visitation also declined with distance into the field (Z=-2.5, p$=$0.01), but not as strongly as in commodity fields (126 visits/hr at edge of field vs.
+Greater stocking rates increased the honey bee visitation (Z=5.3, p$<$0.0001), with visitation at the edge of the field increasing from 14.5 visits/hr with an apiary of 20 hives to 22.7 visits/hr with an apiary of 40 hives, while unstocked field edges had an average of 1.8 visits/hr.
+In seed canola fields, honey bee visitation also decreased with distance from the apiary (Z=-2.5, p$=$0.01), but the rate of decline was weaker (126 visits/hr at edge of field vs.
 78 visits/hr at 100 m).
@@
 
-Leafcutter bees were much more sensitive to distance than honey bees, and visitation declined quickly with distance from their shelters (Z=-11.4, p$=$0.0001, 350 visit/hr at 2 m to 83 visit/hr at 10 m), and unexpectedly, was higher at the edge of the field than the centre (Z=-4.4, p$=$0.0001, 114 visits/hr vs 28 visits/hr).
-However, there was no difference in visitation rates when the stocking rate of cocoons per shelter was lower (Z=2.2, p$=$0.028), indicating that leafcutters at high stocking densities may migrate to shelters close to the edge of the field (Figure \ref{fig:hbeeDist_both}).
-Both leafcutter bees and honey bees visited at similar rates in the male and female bays (leafcutter bee: p$=$0.72, honey bee: p$=$0.32), but within the female bay, leafcutter bee visitation was lower in the centre of the bay (p$=$0.04, 51 vs.
-29 visits/hr), while honey bee visitation was higher at the centre of the bay (p$=$0.008, 71 vs.
+Leafcutter bee visitation declined rapidly with distance from their shelters (Z=-11.4, p$=$0.0001, 75\% reduction in 10 m), and unexpectedly, was higher at the edge of the field than the centre (Z=-4.4, p$=$0.0001, 114 visits/hr vs 28 visits/hr).
+%350 visit/hr at 2 m to 83 visit/hr at 10 m
+However, there was no difference in visitation rates between the edge and the centre when leafcutter cocoon stocking was lower (Z=2.2, p$=$0.028), indicating that leafcutters at high stocking densities likely aggregate in shelters close to the edge of the field (Figure \ref{fig:hbeeDist_both}).
+There was no difference in visitation rates between the male bay and the edge of the female bays (leafcutter bee: p$=$0.72, honey bee: p$=$0.32). 
+However, leafcutter bee visitation was lower in the centre of the female bay (p$=$0.04, 51 vs.
+29 visits/hr), and honey bee visitation was higher at the centre of the bay (p$=$0.008, 71 vs.
 117 visits/hr, Figure \ref{fig:edgeCentVis_both}).
@@
 
-Leafcutter bee visitation increased pollen deposition in seed canola, but honey bees did not increase pollen deposition in either commodity or seed canola.
+Leafcutter bee visitation increased pollen deposition in seed canola fields, but honey bees did not increase pollen deposition in either commodity or seed canola fields.
 Pollen deposition on stigmas was high in commodity canola (mean: 293 grains per stigma, SD: 385, range: 0--3981), but honey bee visitation did not effect deposition (p$=$0.77, Figure \ref{fig:hbeeVisPol}).
-Pollen deposition declined with distance from the edge of the field (p$=$0.07), but this only amounted to a 6\% average decrease (290 grains per stigma at the edge, 240 at field centre).
-Flies were common visitors in commodity fields (Table \ref{tab:propVisitors}), but had no effect on pollen deposition (p$=$0.577), so only honey bees and leafcutter bees were considered as potential pollinators (other flower visitors were rare).
-In seed canola, pollen deposition was much lower (mean: 22 grains per stigma, SD: 43, range: 0--578), and leafcutter bee visitation had a strong positive effect (Z=3.2, p$=$0.002, Figure \ref{fig:visPol_both}, 12 grains/stigma at 6 visits/hr vs.
-16 pollen grains at 60 visits/hr), and also decreased with distance from the edge of field (Z=-4.4, p$=$0.0001, Figure \ref{fig:distCentPol}, 23 vs.
+Pollen deposition slighly declined with distance from the edge of the field, but this relationship was weak (p$=$0.07) and only amounted to a 6\% average decrease (290 grains per stigma at the edge, 240 at field centre).
+Flies were also common visitors in commodity fields (Table \ref{tab:propVisitors}), but had no effect on pollen deposition (p$=$0.577), so only honey bees and leafcutter bees were considered as potential pollinators (other flower visitors were rare).
+In seed canola, pollen deposition was much lower overall (mean: 22 grains per stigma, SD: 43, range: 0--578), leafcutter bee visitation had a strong positive effect (Z=3.2, p$=$0.002, Figure \ref{fig:visPol_both}, 12 grains/stigma at 6 visits/hr vs.
+16 pollen grains at 60 visits/hr), and was lower at the centre of the field (Z=-4.4, p$=$0.0001, Figure \ref{fig:distCentPol}, 23 vs.
 11 grains/stigma).
-Pollen deposition was lower in the centre of the female bay (Z=-4.5, p$=$0.0001, 23 vs.
-13 grains/stigma) independent of visitation rate, suggesting that pollen is lost from bees crossing from male bays, who likely visit flowers at the edge of the bay first \citep{pinnisch1990}.
+Pollen deposition was also lower at the centre of the female bay (Z=-4.5, p$=$0.0001, 23 vs.
+13 grains/stigma) independent of visitation rate, suggesting that pollen may be lost from bees crossing from male bays, who likely visit flowers at the edge of the bay first \citep{pinnisch1990}.
 Finally, there was no effect of honey bees on pollen deposition in seed canola fields (Z=0.98, p$=$0.33), implying that most of the pollen deposition is the result of leafcutter visitation.
@@
 
-%LH: WRITING BELOW THIS POINT COULD BE MORE ECONOMICAL
-\subsection{Prediction 3: Larger plants produce more seeds}
-
-Plant size was largely influenced by plant density, but this differed between commodity and seed canola crops.
-Plant density was higher overall in commodity fields (mean: 48.5 plants/m$^2$, SD: 22.9, range: 6--151 ) than seed fields (mean: 39.4 plants/m$^2$, SD: 17.0, range: 11--89), and commodity canola plants were smaller on average (mean: 18.2 g, SD: 14.4, range: 0.8--110.2) than seed canola plants (mean: 30.7 g, SD: 21.2, range: 1.2--144.3).
-However, commodity canola plant size was not influenced by plant density (Z=-1.62, p$=$0.10, Figure \ref{fig:plDensPlSize}), indicating that any density-dependence was overwhelmed by other factors, but plant size in seed canola was negatively influenced by planting density (Z=-13.2, p$<$0.0001), and plants were larger at the centre of the field independent of density (Z=5.4, p$<$0.0001).%, possibly because of proximity to the centre of the irrigation system.
-Plant density was slightly lower at the edge of commodity canola fields (Z=1.68, p=0.09), but was much lower in seed canola (Z=5.2, p$<$0.0001), indicating lower seedling survival or seeding density at the edges of the field.
-Neither irrigation (p=0.76), site (p=0.86), nor distance from field edge (p=0.70) directly influenced commodity canola plant size, but plants were larger in 2015 (Z=2.5, p=0.01).
+% % Not sure that this paragraph needs to be here - move to Appendix
+% Plant size was influenced by plant density, but this differed between commodity and seed canola crops.
+% Plant density was higher overall in commodity fields (mean: 48.5 plants/m$^2$, SD: 22.9, range: 6--151 ) than seed fields (mean: 39.4 plants/m$^2$, SD: 17.0, range: 11--89), and commodity canola plants were smaller on average (mean: 18.2 g, SD: 14.4, range: 0.8--110.2) than seed canola plants (mean: 30.7 g, SD: 21.2, range: 1.2--144.3).
+% Plant size was negatively influenced by plant density in seed canola fields (Z=-13.2, p$<$0.0001), but not in commodity canola fields (Z=-1.62, p$=$0.10, Figure \ref{fig:plDensPlSize}), indicating that density-dependence is more variable in commodity fields.
+% Plants were larger at the centre of the field independent of density (Z=5.4, p$<$0.0001).%, possibly because of proximity to the centre of the irrigation system. 
+% Plant density was slightly lower at the edge of commodity canola fields (Z=1.68, p=0.09), but was much lower in seed canola (Z=5.2, p$<$0.0001), indicating lower seedling survival at the edges of the field.
+% Neither irrigation (p=0.76), site (p=0.86), nor distance from field edge (p=0.70) directly influenced commodity canola plant size, but plants were larger in 2015 (Z=2.5, p=0.01).
 
@@
 
-Plant size had a strong effect on the number of pods produced, and there was evidence of fruit set suppressing future flower production.
-Commodity canola plants produced fewer flowers per plant (mean: 198, SD: 157, range: 13--1419) than seed canola plants (mean: 468, SD: 328, range: 26--2712), and also produced fewer pods per plant (mean: 143, SD: 114, range: 5--892) than seed canola plants (mean: 303, SD: 208, range: 10--1410).
+Plant size had by far the strongest positive effect on the number of pods produced, and there was evidence of fruit set suppressing flower production.
+Commodity canola plants produced fewer flowers (mean: 198, SD: 157, range: 13--1419) than seed canola plants (mean: 468, SD: 328, range: 26--2712), and also produced fewer pods per plant (mean: 143, SD: 114, range: 5--892) than seed canola plants (mean: 303, SD: 208, range: 10--1410).
 In both commodity and seed canola, plant size had a strong positive effect on the total number of flowers per plant (commodity: Z=92.4, p$<$0.0001, seed: Z=82.7, p$<$0.0001, Figure \ref{fig:plSizeFlwCount}), as well as fruit set (commodity: Z=5.5, p$=$0.0002, seed: Z=19.9, p$<$0.0001, Figure \ref{fig:flwSurv_both}).

### 2021-12-10 helperFunctions.R

@@ -45,18 +45,44 @@ bpoint <- function(x,int1,slope1,b,slope2) ifelse(x<b,int1+slope1*x,b*slope1+(x-
 effSize <- function(x) unname(median(x)/diff(quantile(x,c(0.025,0.975))))
 #Does 95% of posterior overlap zero?
 overlap <- function(x) {r <- quantile(x,c(0.025,0.975))>=0; xor(r[1],r[2]);}
+
 #Posterior predictive check plots
 PPplots <- function(resid,predResid,actual,pred,main=NULL){
   par(mfrow=c(2,1))
-  plot(resid~predResid,ylab='Sum actual residuals',xlab='Sum simulated residuals',main=main)
+  resRange <- range(resid)
+  pResRange <- range(predResid)
+  xl <- yl <- c(pmin(resRange[1],pResRange[1]),pmax(resRange[2],pResRange[2]))
   x <- sum(resid<predResid)/length(resid)
-  legend('topleft',paste('p =',round(min(x,1-x),3)))
+  plot(resid~predResid,ylab='Sum actual residuals',xlab='Sum simulated residuals',xlim=xl,ylim=yl,
+       main=paste(main,' (p =',round(min(x,1-x),3),')'))
+  # legend('topleft',)
   abline(0,1,col='red') #PP plot
   plot(actual~pred, #Predicted vs Actual
        xlab=paste('Predicted',main),ylab=paste('Actual',main)) 
   abline(0,1,col='red')
   abline(lm(actual~pred),col='red',lty=2)
   par(mfrow=c(1,1))
+}
+
+#Plot of random intercepts
+compareRE <- function(mod,parSet){
+  require(ggpubr)
+  p1 <- extract(mod,pars=parSet)[[1]] %>% 
+    apply(.,2,function(x) quantile(x,c(0.1,0.5,0.9))) %>% 
+    t() %>% data.frame() %>% setNames(c('lwr','med','upr')) %>% 
+    ggplot(aes(sample=med))+ ##q-q plot
+    geom_qq()+
+    geom_qq_line()  
+  p2 <- extract(mod,pars=parSet)[[1]] %>% 
+    apply(.,2,function(x) quantile(x,c(0.1,0.5,0.9))) %>% 
+    t() %>% data.frame() %>% setNames(c('lwr','med','upr')) %>% 
+    tibble::rownames_to_column() %>%
[…]

### 2021-12-10 yield path analysis.R

@@ -97,6 +97,7 @@ datalistPlant <-
   mutate(plantIndex=as.numeric(factor(paste(Year,Field,Distance)))) %>% #Index for plant (which plot?)
   arrange(plantIndex) %>% 
   with(list(Nplant=length(VegMass), #Number of plant samples (some missing)
+            VegMass=VegMass,
   # Nplant_obs=sum(!is.na(VegMass)), #Observed plants
   # Nplant_miss=sum(is.na(VegMass)), #Missing plants
   podCount=Pods, #Successful pods
@@ -259,19 +260,44 @@ modFiles <- dir(pattern = 'commodity.*\\.stan')
 modList <- vector(mode = 'list',length = length(modFiles))
 names(modList) <- gsub('(commodity.*[0-9]{2}|\\.stan)','',modFiles)
 
-for(i in 1:length(modFiles)){
-  modList[i] <- stan(file=modFiles[i],data=datalist,iter=1000,chains=4,control=list(adapt_delta=0.8),init=0)
-}
+# for(i in 1:length(modFiles)){
+#   modList[i] <- stan(file=modFiles[i],data=datalist,iter=1000,chains=4,control=list(adapt_delta=0.8),init=0)
+# }
 
-print(modList[i])
+modList[1] <- stan(file=modFiles[1],data=datalist,iter=2000,chains=4,control=list(adapt_delta=0.8),init=0) #OK
+modList[2] <- stan(file=modFiles[2],data=datalist,iter=2000,chains=4,control=list(adapt_delta=0.8),init=0) #OK
+modList[3] <- stan(file=modFiles[3],data=datalist,iter=1000,chains=4,control=list(adapt_delta=0.8),init=0) #OK
+modList[4] <- stan(file=modFiles[4],data=datalist,iter=1000,chains=4,control=list(adapt_delta=0.8),init=0) #OK
+modList[5] <- stan(file=modFiles[5],data=datalist,iter=2000,chains=4,control=list(adapt_delta=0.8),init=0); beep(1) #Trouble here - try without plDens + pollen components
+modList[6] <- stan(file=modFiles[6],data=datalist,iter=1000,chains=4,control=list(adapt_delta=0.8),init=0)
+modList[7] <- stan(file=modFiles[7],data=datalist,iter=1000,chains=4,control=list(adapt_delta=0.8),init=0)
[…]

### 2021-12-10 helperFunctions.R
Got betabinomial model working

@@ -46,8 +46,31 @@ effSize <- function(x) unname(median(x)/diff(quantile(x,c(0.025,0.975))))
 #Does 95% of posterior overlap zero?
 overlap <- function(x) {r <- quantile(x,c(0.025,0.975))>=0; xor(r[1],r[2]);}
 
+# #Posterior predictive check plots - older version
+# PPplots <- function(resid,predResid,actual,pred,main=NULL){
+#   par(mfrow=c(2,1))
+#   resRange <- range(resid)
+#   pResRange <- range(predResid)
+#   xl <- yl <- c(pmin(resRange[1],pResRange[1]),pmax(resRange[2],pResRange[2]))
+#   x <- sum(resid<predResid)/length(resid)
+#   plot(resid~predResid,ylab='Sum actual residuals',xlab='Sum simulated residuals',xlim=xl,ylim=yl,
+#        main=paste(main,' (p =',round(min(x,1-x),3),')'))
+#   # legend('topleft',)
+#   abline(0,1,col='red') #PP plot
+#   plot(actual~pred, #Predicted vs Actual
+#        xlab=paste('Predicted',main),ylab=paste('Actual',main)) 
+#   abline(0,1,col='red')
+#   abline(lm(actual~pred),col='red',lty=2)
+#   par(mfrow=c(1,1))
+# }
+
 #Posterior predictive check plots
-PPplots <- function(resid,predResid,actual,pred,main=NULL){
+PPplots <- function(mod,actual=NULL,pars=c('resid','predResid','pred'),main=''){
+  modVals <- extract(mod)
+  nam <- names(modVals)
+  resid <- apply(modVals[[which(nam==pars[1])]],1,function(x) sum(abs(x)))
+  predResid <- apply(modVals[[which(nam==pars[2])]],1,function(x) sum(abs(x)))
+  pred <- apply(modVals[[which(nam==pars[3])]],2,median)
   par(mfrow=c(2,1))
   resRange <- range(resid)
   pResRange <- range(predResid)
@@ -58,7 +81,7 @@ PPplots <- function(resid,predResid,actual,pred,main=NULL){
   # legend('topleft',)
   abline(0,1,col='red') #PP plot
   plot(actual~pred, #Predicted vs Actual
-       xlab=paste('Predicted',main),ylab=paste('Actual',main)) 
+       xlab=paste('Predicted',main),ylab=paste('Actual',main))
   abline(0,1,col='red')
   abline(lm(actual~pred),col='red',lty=2)
   par(mfrow=c(1,1))

### 2021-12-10 yield path analysis.R

@@ -51,6 +51,7 @@ source('helperFunctions.R')
 library(rstan)
 setwd('./Models')
 rstan_options(auto_write = TRUE) #Avoids recompilation
+rstan_options(javascript = FALSE)
 options(mc.cores = 6)
 # library(shinystan)
 
@@ -268,8 +269,8 @@ modList[1] <- stan(file=modFiles[1],data=datalist,iter=2000,chains=4,control=lis
 modList[2] <- stan(file=modFiles[2],data=datalist,iter=2000,chains=4,control=list(adapt_delta=0.8),init=0) #OK
 modList[3] <- stan(file=modFiles[3],data=datalist,iter=1000,chains=4,control=list(adapt_delta=0.8),init=0) #OK
 modList[4] <- stan(file=modFiles[4],data=datalist,iter=1000,chains=4,control=list(adapt_delta=0.8),init=0) #OK
-modList[5] <- stan(file=modFiles[5],data=datalist,iter=2000,chains=4,control=list(adapt_delta=0.8),init=0); beep(1) #Trouble here - try without plDens + pollen components
-modList[6] <- stan(file=modFiles[6],data=datalist,iter=1000,chains=4,control=list(adapt_delta=0.8),init=0)
+modList[5] <- stan(file=modFiles[5],data=datalist,iter=1000,chains=4,control=list(adapt_delta=0.8),init=0); beep(1) #Trouble here - segFault when using plDens
+modList[6] <- stan(file=modFiles[6],data=datalist,iter=1000,chains=4,control=list(adapt_delta=0.8),init=0) #OK
 modList[7] <- stan(file=modFiles[7],data=datalist,iter=1000,chains=4,control=list(adapt_delta=0.8),init=0)
 modList[8] <- stan(file=modFiles[8],data=datalist,iter=1000,chains=4,control=list(adapt_delta=0.8),init=0)
 modList[9] <- stan(file=modFiles[9],data=datalist,iter=1000,chains=4,control=list(adapt_delta=0.8),init=0)
@@ -283,15 +284,21 @@ modList[10] <- stan(file=modFiles[10],data=datalist,iter=1000,chains=4,control=l
 #               dispformula=~plSize,family = 'betabinomial',data=dat)
 # summary(m1)
 
-i <- 2
+i <- 6
 # print(modList[i])
 modFiles[i]
 n <- names(modList[[i]]) #Model parameters
[…]

### 2022-06-10 Manuscript/main.tex
Updated commodity claims list

@@
 Structural equation models do not have paths between all variables, which may bias the model results if this independence assumption is incorrect; this requires testing a ``basis set" of independence claims using Shipley's d-separation criteria \citep{shipley2000, shipley2009}.
-The initial commodity canola pSEM was misspecfied, as several missing paths were identified for the initial commodity model (Fisher's C = 202.1, df = 100, p$<<$0.001), but the updated pSEM that included missing paths was adequate (C = 81.6, df = 86, p = 0.62).
+The initial commodity canola pSEM was misspecfied, as several missing paths were identified for the initial commodity model (Fisher's C = 167.5, df = 64, p$<<$0.001), but the updated pSEM that included missing paths was adequate (C = 81.6, df = 86, p = 0.62).
 Similarly, the initial seed field pSEM also had several missing paths (C = 37.54, df = 56, p = 0.027), which we corrected (C = 58.10, df = 64, p = 0.68).

### 2022-06-10 helperFunctions.R

@@ -370,12 +370,12 @@ shipley.dSep <- function(d,p,lab){
     ret <- c(Inf,kval,0)
   } else {
     cstat <- -2*sum(log(pvals)) #C-statistic
-    p <- 1-pchisq(cstat,kval) 
-    ret <- c(cstat,kval,p)
+    cp <- 1-pchisq(cstat,kval) 
+    ret <- c(cstat,kval,cp)
   }
   
   tCol <- rev(ifelse(pvals<0.05,'red','black'))
-  ttl <- paste0('C-stat: ',Inf,', k: ',64,', p: ',0)
+  ttl <- paste0('C-stat: ',formatC(ret[1],3),', k: ',ret[2],', p: ',formatC(ret[3],format='e'))
   
   d %>% mutate(param=factor({{lab}},levels=rev({{lab}}))) %>% 
     mutate(tooLow={{p}}<=0.05) %>% 

### 2022-06-10 yield path analysis commodity.R

@@ -4,6 +4,7 @@
 library(ggplot2)
 library(dplyr)
 library(tidyr)
+library(tibble)
 library(beepr)
 library(xtable)
 
@@ -19,8 +20,8 @@ prestheme=theme(legend.position='right',
 theme_set(theme_bw()+prestheme) #Sets graph theme to B/Ws + prestheme
 rm(prestheme)
 
-# setwd('~/Projects/UofC/canola_yield_project') #Multivac path
-setwd('~/Documents/canola_yield_project') #Galpern machine path
+setwd('~/Projects/UofC/canola_yield_project') #Multivac path
+# setwd('~/Documents/canola_yield_project') #Galpern machine path
 
 source('helperFunctions.R')
 
@@ -245,17 +246,38 @@ options(mc.cores = 6)
 
 # Dagitty claims list for commodity fields 
 
-commDAG <- list(plDens ~ hbeeDist,
-                plSize ~ plDens + hbeeDist,
-                flDens ~ plSize + hbeeDist,
-                hbeeVis ~ hbeeDist + numHives + flDens,
-                pollen ~ hbeeVis + hbeeDist,
-                flwCount ~ plSize + flwSurv,
-                flwSurv ~ hbeeVis + plSize + pollen,
-                seedCount ~ hbeeVis + pollen + plSize,
-                seedWeight ~ hbeeVis + pollen + plSize + seedCount)
+{
+  library(ggdag)
+  nodeCoords <- data.frame(name=c('numHives','hbeeDist','hbeeVis','pollen',
+                                  'plSize','plDens','flDens',
+                                  'flwCount','flwSurv','seedCount','seedWeight'),
+           x=c(0,1,0.5,0.5,
+               1,2,3,
+               3,4,4,4),
+           y=c(5,5,4,3,
+               2,1,2,
+               4.5,4,3.5,3))
+  
+  commDAG <- dagify(plDens ~ hbeeDist,
+                  plSize ~ plDens + hbeeDist,
+                  flDens ~ plSize + hbeeDist + plDens,
+                  hbeeVis ~ hbeeDist + numHives + flDens,
+                  pollen ~ hbeeVis + hbeeDist,
+                  flwCount ~ plSize + flwSurv,
+                  flwSurv ~ hbeeVis + plSize + pollen,
+                  seedCount ~ hbeeVis + pollen + plSize + flwSurv + flwCount,
[…]

### 2022-06-20 Manuscript/main.tex
Worked on commodity models

@@
 14 of 31 of the fields near Lethbridge were watered using central-pivot irrigation systems.
-% Growers were asked for canola variety information, but there was not enough replication to test for difference between varieties. 
+Growers were also asked for canola variety information, but there was not enough replication to test for difference between varieties.
 % Fields with central-pivot irrigation were mostly circular, but dryland (non-irrigated) fields were usually square or rectangular.
@@
 %Maps + climate graphs needed for publication
-During 2015 and 2016, we also surveyed 35 hybrid seed canola fields (15 in 2015, 20 in 2016) near Lethbridge, Alberta, from June through August of each year.
+During 2015 and 2016, we also surveyed 35 hybrid seed canola fields (15 in 2015, 20 in 2016) near Lethbridge, Alberta, from June through August of each year, all of which had central-pivot irrigation
 Seed fields were all stocked with honey bee hives at a rate of 3.6 hives/ha, with apiaries stationed in the corners of fields, and were also stocked with leafcutter bees in shelters throughout the field.
-Shelters used either ``standard" or ``double"  leafcutter bee stocking ($\approx$50,000 vs.
+% Shelters used either ``standard" or ``double"  leafcutter bee stocking ($\approx$50,000 vs.
 100,000 cocoons/ha), and shelters were placed at either ``standard" or ``double" densities (1.3 vs.
 2.6 shelters/ha) in each field.
-Double stocking rates were only used in fields with double shelter density, creating three combinations of leafcutter bee stocking: ``standard", ``double shelter", and ``double shelter and double stocking".
-All seed fields had central-pivot irrigation, and were mostly circular or semi-circular in shape.
+% Double stocking rates were only used in fields with double shelter density, creating three combinations of leafcutter bee stocking: ``standard", ``double shelter", and ``double shelter and double stocking".
+All seed fields .
 %Woudick 5,6 = 64 shelters (single), Woudick 2 = 113 shelters (double + bees), Woudick 3 = 128 shelters Graham 1 = 135 shelters

### 2022-06-20 helperFunctions.R

@@ -31,14 +31,14 @@ parTable <- function(x){
 
 
 #Faster pair plot
-fastPairs <- function(l,pars=NULL){ 
+fastPairs <- function(l,pars=NULL,N=500){ 
   if(class(l)=='stanfit'){
     l <- extract(l,pars=pars)
     if(any(sapply(l,function(x) length(dim(x)))>1)){
       stop('Parameters have more than 1 dimension: ',paste(pars[sapply(l,function(x) length(dim(x))>1)],collapse=', '))
     }
     l <- do.call('cbind',l)
-    if(nrow(l)>500) l <- l[round(seq(1,nrow(l),length.out=500)),]
+    if(nrow(l)>N) l <- l[round(seq(1,nrow(l),length.out=N)),]
   }
   pairs(l,lower.panel=function(x,y){
     par(usr=c(0,1,0,1))

### 2022-06-20 yield path analysis commodity.R

@@ -167,7 +167,7 @@ modList[2] <- stan(file=modFiles[2],data=datalist,iter=2000,chains=4,control=lis
 modList[3] <- stan(file=modFiles[3],data=datalist,iter=2000,chains=4,control=list(adapt_delta=0.8),init=0) #OK - Pollen
 modList[4] <- stan(file=modFiles[4],data=datalist,iter=2000,chains=4,control=list(adapt_delta=0.8),init=0) #OK - Flower count
 modList[5] <- stan(file=modFiles[5],data=datalist,iter=2000,chains=4,control=list(adapt_delta=0.8),init=0); beep(1) #OK - Pod Count (flw survival)
-# modList[5] <- stan(file='commodity_07flwSurv2.stan',data=datalist,iter=2000,chains=4,control=list(adapt_delta=0.8),init=0); beep(1) #Count-only version - OK, but not as biologically interesting I think
+# modList[5] <- stan(file='commodity_07flwSurv2.stan',data=datalist,iter=2000,chains=4,control=list(adapt_delta=0.8),init=0); beep(1) #Pod count-only version - OK, but not as biologically interesting I think
 modList[6] <- stan(file=modFiles[6],data=datalist,iter=2000,chains=4,control=list(adapt_delta=0.8),init=0) #OK - Seed Count
 modList[7] <- stan(file=modFiles[7],data=datalist,iter=2000,chains=4,control=list(adapt_delta=0.8),init=0) #OK - Seed weight
 modList[8] <- stan(file=modFiles[8],data=datalist,iter=2000,chains=4,control=list(adapt_delta=0.8),init=0) #OK - Total yield
@@ -253,10 +253,20 @@ options(mc.cores = 6)
                                   'flwCount','flwSurv','seedCount','seedWeight'),
            x=c(0,1,0.5,0.5,
                1,2,3,
-               3,4,4,4),
+               3,4,5,4),
            y=c(5,5,4,3,
                2,1,2,
-               4.5,4,3.5,3))
+               4.5,4,3.5,2.5))
+  
+  capFirst <- function(x,decap=FALSE){ #Capitalize/decapitalize first letter of a string
+    if(!is.character(x)) stop('Not a character or character vector')
+    if(decap){
+      substr(x, 1, 1) <- tolower(substr(x, 1, 1))
+    } else {
[…]

### 2022-06-27 Manuscript/main.tex
Updated commodity model

@@
 During 2015 and 2016, we also surveyed 35 hybrid seed canola fields (15 in 2015, 20 in 2016) near Lethbridge, Alberta, from June through August of each year, all of which had central-pivot irrigation
-Seed fields were all stocked with honey bee hives at a rate of 3.6 hives/ha, with apiaries stationed in the corners of fields, and were also stocked with leafcutter bees in shelters throughout the field.
-% Shelters used either ``standard" or ``double"  leafcutter bee stocking ($\approx$50,000 vs.
+Seed fields were stocked with honey bee hives at a rate of 3.6 hives/ha, with apiaries stationed in the corners of fields, and were also stocked with LCBs in shelters throughout the field (1.3 or 2.6 shelters/ha).
+% Shelters used either ``standard" or ``double"  LCB stocking ($\approx$50,000 vs.
 100,000 cocoons/ha), and shelters were placed at either ``standard" or ``double" densities (1.3 vs.
 2.6 shelters/ha) in each field.
-% Double stocking rates were only used in fields with double shelter density, creating three combinations of leafcutter bee stocking: ``standard", ``double shelter", and ``double shelter and double stocking".
-All seed fields .
+% Double stocking rates were only used in fields with double shelter density, creating three combinations of LCB stocking: ``standard", ``double shelter", and ``double shelter and double stocking".
 %Woudick 5,6 = 64 shelters (single), Woudick 2 = 113 shelters (double + bees), Woudick 3 = 128 shelters Graham 1 = 135 shelters
@@
 
-In commodity fields, we established 1 m$^2$ plots at 5, 20, 100, and 500m along a transect into the field, starting at the field margin closest to the set of honey bee hives (271 total plots).
-%used a Garmin\texttrademark eTrex20 GPS,
-In unstocked fields, we began the transect at a field edge close to potential sources of natural pollinating insects, such as forests or grasslands, but observed very few wild pollinators (Table \ref{tab:propVisitors}).
-In seed canola fields, bays of ``male" and ``female" plants are typically planted in 1- and 6-m wide bays, respectively, and leafcutter bee shelters were located in the female bays (Figure \ref{fig:seedfieldPhoto}, \ref{fig:seedfieldPlots}).
+In both fields, we established set of plots at varying distance from the sources of pollinators. 
+In commodity fields, we established 1 m$^2$ plots at 5, 20, 100, and 500m, starting at the field margin closest to the set of honey bee hives %(271 total plots), 
+and established plots starting at potential sources of natural pollinating insects in unstocked fields (forests, shrublands, or grasslands), but observed very few wild pollinators (Table \ref{tab:propVisitors}).
+In seed canola fields, bays of hermaphroditic (herafter ``male") and female plants are typically planted in 1- and 6-m wide bays, respectively, and LCB shelters were located in the female bays (Figure \ref{fig:seedfieldPhoto}, \ref{fig:seedfieldPlots}).
 We established plots at 5, 20, 100 (250 in 2016), and 400m into the field along a transect from the nearest set of honey bee hives, using pairs of plots at the edge of adjacent male and female bays at each distance (Figure \ref{fig:seedfieldPlots}).
-Bee visitation can vary within female bays (Alfonso Parra, pers.
-comm.), so at the 5m and 400m plot in each field, we established another plot in the centre of the female bay to examine the effect of distance away from the male bay.
+We established another plot in the centre of the female bay at the 5m and 400m plot in each field to examine how visitation varied within the female bay.
 We used a Nikon\texttrademark Laser 800S Rangefinder to measure the distance from each plot to the nearest shelter.
@@
 Random intercepts were used to model variance between fields, within-field (pollen, flower survival, seed count \& size), and within-plot (seed count \& size).
-Continuous responses were modeled using log-normal (plant density, plant size), square-root normal (flower density), and exponential-normal distributions (weight per seed), while counts were modeled as a negative-binomial (honey bee visits, pollen grains per stigma, flowers per plant, seeds per pod) or zero-inflated negative-binomial distribution (leafcutter bee visits) with a log-link function.
+Continuous responses were modeled using log-normal (plant density, plant size), square-root normal (flower density), and exponential-normal distributions (weight per seed), while counts were modeled as a negative-binomial (honey bee visits, pollen grains per stigma, flowers per plant, seeds per pod) or zero-inflated negative-binomial distribution (LCB visits) with a log-link function.
 Visitation models used $log$(time) as an ``offset" variable to account for differences in observation times.
 Pod set (fraction of flowers that matured into pods) was modeled using a beta-binomial distribution with a logit-link function.
-Interactions between predictors were evident in honey bee visitation rate (Year:Locality interaction) and plant density (Irrigation:Year) in commodity canola, and for leafcutter bee visitation (Tent Stocking:Distance from edge) in seed canola, and were included in each model (represented as Y-shaped path in Figures \ref{fig:commoditySEM} and \ref{fig:seedSEM}).
+Interactions between predictors were evident in honey bee visitation rate (Year:Locality interaction) and plant density (Irrigation:Year) in commodity canola, and for LCB visitation (Tent Stocking:Distance from edge) in seed canola, and were included in each model (represented as Y-shaped path in Figures \ref{fig:commoditySEM} and \ref{fig:seedSEM}).
 
@@
 78 visits/hr at 100 m).
-Honey bee visitation was lower near leafcutter shelters (Z=3.9, p$=$0.001), dropping from 60 visits/hr at 10 m to 34 visits/hr at 2 m, likely due to competition with leafcutter bees (Figure \ref{fig:hbeeDist_both}, \ref{fig:lbeeDist_both}).
+Honey bee visitation was lower near leafcutter shelters (Z=3.9, p$=$0.001), dropping from 60 visits/hr at 10 m to 34 visits/hr at 2 m, likely due to competition with LCBs (Figure \ref{fig:hbeeDist_both}, \ref{fig:lbeeDist_both}).
 
-Leafcutter bee visitation declined rapidly with distance from their shelters (Z=-11.4, p$=$0.0001, 75\% reduction in 10 m), and unexpectedly, was higher at the edge of the field than the centre (Z=-4.4, p$=$0.0001, 114 visits/hr vs 28 visits/hr).
+LCB visitation declined rapidly with distance from their shelters (Z=-11.4, p$=$0.0001, 75\% reduction in 10 m), and unexpectedly, was higher at the edge of the field than the centre (Z=-4.4, p$=$0.0001, 114 visits/hr vs 28 visits/hr).
 %350 visit/hr at 2 m to 83 visit/hr at 10 m
 However, there was no difference in visitation rates between the edge and the centre when leafcutter cocoon stocking was lower (Z=2.2, p$=$0.028), indicating that leafcutters at high stocking densities likely aggregate in shelters close to the edge of the field (Figure \ref{fig:hbeeDist_both}).
-There was no difference in visitation rates between the male bay and the edge of the female bays (leafcutter bee: p$=$0.72, honey bee: p$=$0.32). 
-However, leafcutter bee visitation was lower in the centre of the female bay (p$=$0.04, 51 vs.
+There was no difference in visitation rates between the male bay and the edge of the female bays (LCB: p$=$0.72, honey bee: p$=$0.32). 
+However, LCB visitation was lower in the centre of the female bay (p$=$0.04, 51 vs.
 29 visits/hr), and honey bee visitation was higher at the centre of the bay (p$=$0.008, 71 vs.
@@
 
-Leafcutter bee visitation increased pollen deposition in seed canola fields, but honey bees did not increase pollen deposition in either commodity or seed canola fields.
+LCB visitation increased pollen deposition in seed canola fields, but honey bees did not increase pollen deposition in either commodity or seed canola fields.
 Pollen deposition on stigmas was high in commodity canola (mean: 293 grains per stigma, SD: 385, range: 0--3981), but honey bee visitation did not effect deposition (p$=$0.77, Figure \ref{fig:hbeeVisPol}).
 Pollen deposition slighly declined with distance from the edge of the field, but this relationship was weak (p$=$0.07) and only amounted to a 6\% average decrease (290 grains per stigma at the edge, 240 at field centre).
-Flies were also common visitors in commodity fields (Table \ref{tab:propVisitors}), but had no effect on pollen deposition (p$=$0.577), so only honey bees and leafcutter bees were considered as potential pollinators (other flower visitors were rare).
-In seed canola, pollen deposition was much lower overall (mean: 22 grains per stigma, SD: 43, range: 0--578), leafcutter bee visitation had a strong positive effect (Z=3.2, p$=$0.002, Figure \ref{fig:visPol_both}, 12 grains/stigma at 6 visits/hr vs.
+Flies were also common visitors in commodity fields (Table \ref{tab:propVisitors}), but had no effect on pollen deposition (p$=$0.577), so only honey bees and LCBs were considered as potential pollinators (other flower visitors were rare).
+In seed canola, pollen deposition was much lower overall (mean: 22 grains per stigma, SD: 43, range: 0--578), LCB visitation had a strong positive effect (Z=3.2, p$=$0.002, Figure \ref{fig:visPol_both}, 12 grains/stigma at 6 visits/hr vs.
 16 pollen grains at 60 visits/hr), and was lower at the centre of the field (Z=-4.4, p$=$0.0001, Figure \ref{fig:distCentPol}, 23 vs.
@@
 This study examined the relative strength of the path between visitation, pollination, and yield, in two types of canola crops, and showed a strong path between visitation and yield in seed canola, but not in commodity canola.
-First, honey bee and leafcutter bee visitation decreased with distance from their hive or shelter, but unexpectedly, leafcutter bees visited more frequently at the edge of the field.
-Secondly, honey bees had little (direct) influence on pollen deposition in either crop type, leafcutter bees had a positive effect on pollen deposition in seed canola.
+First, honey bee and LCB visitation decreased with distance from their hive or shelter, but unexpectedly, LCBs visited more frequently at the edge of the field.
+Secondly, honey bees had little (direct) influence on pollen deposition in either crop type, LCBs had a positive effect on pollen deposition in seed canola.
 Finally, the model revealed that commodity canola production is largely limited by plant size, while seed canola production is limited by both pollen and plant size.
@@
 mean 0.6 hives/ha).
-Since honey bees travel from their hive outside the edge of the field, this decline was not surprising, but we did not expect the similar decrease observed in leafcutter bee visitation with distance into the field, as their shelters are located \textit{within} the field.
-This decrease with distance into the field may have been caused by leafcutter bees migrating from shelters at the centre of the field to the edge \citep{goerzen1995}.
-Like honey bees, female leafcutter bees are central-place foragers, and tend to not forage far from their nests \citep{peterson2005,pitts2011, brunet2019}.
-However, leafcutter bees are not as constrained to their nest site as honey bees, and can drift between shelters in a given field \citep{goerzen1995, pittsSinger2013}.
-Leafcutter bees must also forage for leaf materials to create cocoons, but they prefer to build cocoons out of thinner, non-canola leaf types, mainly plants in the families Fabaceae and Rosaceae \citep{sinu2018}.
-Seed canola fields have very few weeds within the area of the crop, meaning that leafcutter bees at the centre of the field may have few choices of leaf material, or alternative pollen and nectar sources.
-Therefore, leafcutter bees likely move from the shelters at which they were released in the centre of the field to the shelters at the edge of the field, so as to gain access to better leaf material \citep{horne1995}, which is more available off-field, or to better forage for off-field pollen or nectar \citep{horne1995b}.
+Since honey bees travel from their hive outside the edge of the field, this decline was not surprising, but we did not expect the similar decrease observed in LCB visitation with distance into the field, as their shelters are located \textit{within} the field.
+This decrease with distance into the field may have been caused by LCBs migrating from shelters at the centre of the field to the edge \citep{goerzen1995}.
+Like honey bees, female LCBs are central-place foragers, and tend to not forage far from their nests \citep{peterson2005,pitts2011, brunet2019}.
+However, LCBs are not as constrained to their nest site as honey bees, and can drift between shelters in a given field \citep{goerzen1995, pittsSinger2013}.
+LCBs must also forage for leaf materials to create cocoons, but they prefer to build cocoons out of thinner, non-canola leaf types, mainly plants in the families Fabaceae and Rosaceae \citep{sinu2018}.
+Seed canola fields have very few weeds within the area of the crop, meaning that LCBs at the centre of the field may have few choices of leaf material, or alternative pollen and nectar sources.
+Therefore, LCBs likely move from the shelters at which they were released in the centre of the field to the shelters at the edge of the field, so as to gain access to better leaf material \citep{horne1995}, which is more available off-field, or to better forage for off-field pollen or nectar \citep{horne1995b}.
 This would explain why greater visitation occurred at the edge of the field, and may also explain why this pattern was not seen in fields with half-stocked shelters.
-To test this, a mark-recapture study of female leafcutter bees could be done to see if bees migrate to shelters at the edge of the field, or if visitation is higher due to other reasons (\textit{e.g.} feral populations migrating to edge of field, long-distance foraging from centre of field as in \citealp{peterson2005}).
+To test this, a mark-recapture study of female LCBs could be done to see if bees migrate to shelters at the edge of the field, or if visitation is higher due to other reasons (\textit{e.g.} feral populations migrating to edge of field, long-distance foraging from centre of field as in \citealp{peterson2005}).
 %SH: FINE FOR THESIS, BUT CAN BE REMOVED FOR MANUSCRIPT
-It would be interesting to see if there is a critical threshold of leafcutter bee density per-shelter that causes them to move to shelters at the edge of the field (similar to \citealp{pittsSinger2013}).
+It would be interesting to see if there is a critical threshold of LCB density per-shelter that causes them to move to shelters at the edge of the field (similar to \citealp{pittsSinger2013}).
 %Honey bees visited flowers at the edge of the field more frequently than those in the middle of the field, as predicted for central-place foragers with nesting aggregations outside the field (\citealp{olsson2014}, see Chapter 2).
@@
 This may have been driven by avoidance of nectar and pollen competition near shelters, as areas close to leafcutter shelters may become depleted in nectar and pollen, deterring honey bee visitation (similar to \citealp{currie1997}).
-Honey bees also suffer from direct interference by leafcutter bees near to their shelters.
+Honey bees also suffer from direct interference by LCBs near to their shelters.
 Several times during the study, \textit{M.
 rotundata} females and males directly harassed honey bees during the plot-level observations, tackling honey bees both on the flowers and in the air (also seen by \citealp{batra1978} and \citealp{waytesMsc}).
-Honey bees were never the aggressor in these interactions, so interference between leafcutter bees and honey bees may be unidirectional, at least in areas near leafcutter bee shelters. 
+Honey bees were never the aggressor in these interactions, so interference between LCBs and honey bees may be unidirectional, at least in areas near LCB shelters. 
 For this reason, we treated high leafcutter visitation as causing lower honey bee visitation in our SEM (Figure \ref{fig:seedSEM}, arrow from leafcutter visit rate to honey bee visit rate).
@@
 Honey bee visitation and foraging behaviour varied strongly between the male and female bays of seed fields, as well as within the female bays.
-Visitation rates of honey bee foragers were almost twice as high in the centre of the female bay, and conversely, leafcutter bee visitation was almost twice as low.
-This could be due to leafcutter bees avoiding competition for nectar with honey bees, but more likely reflects a stronger need for pollen among leafcutter bees than honey bees \citep{cane2011}.
+Visitation rates of honey bee foragers were almost twice as high in the centre of the female bay, and conversely, LCB visitation was almost twice as low.
+This could be due to LCBs avoiding competition for nectar with honey bees, but more likely reflects a stronger need for pollen among LCBs than honey bees \citep{cane2011}.
 Only 1.4\% of the honey bees in the female bay were pollen foragers (Table \ref{tab:sideWorking}), meaning that foragers who have (recently) come into contact with pollen rare.
@@
 Honey bee behaviour in seed fields made pollen transfer between male and female plants unlikely, and this was also reflected in the measurements of stigma deposition. 
-Deposition was not affected by honey bee visitation, but was strongly increased by leafcutter bee visitation.
-Leafcutter bees tend to switch between male and female flowers more frequently than honey bees do \citep{waytesMsc}, transport more viable pollen between flowers \citep{parker2015}, and tend not to side-work canola flowers (\citealp{soroka2001}, personal observation), which may explain their increased pollination efficacy.
-We also found that pollen deposition also decreased with distance from the edge of the field, was lower in the centre of the female bays, and that this was not solely explained by leafcutter bee abundance (Figure \ref{fig:seedSEM}).
-During foraging bouts, leafcutter bees may travel further between flowers than honey bees do; \citet{brunet2019} found that leafcutter bees foraging in alfalfa (\emph{Medicago sativa} L.) travelled an average of 21 cm between flowers, while honey bees only travelled 16 cm.
+Deposition was not affected by honey bee visitation, but was strongly increased by LCB visitation.
+LCBs tend to switch between male and female flowers more frequently than honey bees do \citep{waytesMsc}, transport more viable pollen between flowers \citep{parker2015}, and tend not to side-work canola flowers (\citealp{soroka2001}, personal observation), which may explain their increased pollination efficacy.
+We also found that pollen deposition also decreased with distance from the edge of the field, was lower in the centre of the female bays, and that this was not solely explained by LCB abundance (Figure \ref{fig:seedSEM}).
+During foraging bouts, LCBs may travel further between flowers than honey bees do; \citet{brunet2019} found that LCBs foraging in alfalfa (\emph{Medicago sativa} L.) travelled an average of 21 cm between flowers, while honey bees only travelled 16 cm.
 However, pollen carryover \citep{thomson1986} to the middle of the bay female is likely reduced, as leafcutters likely visit the edge of the female bay before venturing into the centre.
@@
 Foraging \textit{Bombus} take smaller trips between flowers and will forage in smaller areas under nectar-rich conditions (area-restricted search, \citealp{pyke1978b, heinrich1979}), so leafcutter foraging may follow a similar pattern, causing lower pollen deposition at the centre of the field where competition is lower.
-%Leafcutter bees are extremely fast fliers, and are difficult to follow after they leave an inflorescence, meaning that tracking their movements during an entire foraging bout would be almost impossible.
+%LCBs are extremely fast fliers, and are difficult to follow after they leave an inflorescence, meaning that tracking their movements during an entire foraging bout would be almost impossible.
 % Visits by honey bee foragers were almost twice as high in the centre of the female bay, but pollen deposition was about 40\% lower (  Figure \ref{fig:distCentPol}), which correspondingly is 
 % Honey bees in seed fields tended to visit more in the centre of the female bay, even close to the edge of the field, yet pollen deposition was still about 40\% lower (Figure \ref{fig:distCentPol}).
-% While we found that leafcutter bees also tend to avoid the centre of the female bays, and decrease with distance into the field, this extra dependence could have been caused by the fact that the visitation data represents a short ``snapshot'' of the pollen deposition process.
+% While we found that LCBs also tend to avoid the centre of the female bays, and decrease with distance into the field, this extra dependence could have been caused by the fact that the visitation data represents a short ``snapshot'' of the pollen deposition process.
 % For example, canola flowers are receptive for 1-2 days before the petals dehisce, while the surveys only recorded 5 or 10 minutes of visitation, meaning we may have not captured the deposition process on the time scale that it occurs, and the extra variance is being accounted for by distance from field edge and the centre of the female bay.
@@
 
-Honey bees may have an indirect positive effect on pollen deposition, as they may cause leafcutter bees to travel farther by lowering overall nectar and pollen standing crop, or release airborne pollen from male-fertile flowers.
+Honey bees may have an indirect positive effect on pollen deposition, as they may cause LCBs to travel farther by lowering overall nectar and pollen standing crop, or release airborne pollen from male-fertile flowers.
 \citet{pierre2010} showed that honey bees can increase the amount of airborne pollen by foraging on male-fertile flowers and releasing pollen from the anthers, causing increased yields in nearby male-sterile flowers; therefore, honey bees may indirectly contribute to a higher rate of wind pollination.
-Honey bees may also cause leafcutter bees to forage at further distances away from their shelters.
+Honey bees may also cause LCBs to forage at further distances away from their shelters.
 Bumble bees move further between flowers when foraging in \textit{Trifolium} fields that have been depleted by honey bees \citet{heinrich1979}, so a similar process could occur in canola seed fields. 
-Leafcutter bees do not appear to use area-restricted search \citep{brunet2019}, but we expect that the foraging range of leafcutter bees around their shelters would sitill decrease, because if honey bees lower pollen and nectar levels at the edge of the field, then leafcutter bees should travel shorter distances to gather the same reward (according to the predictions of Chapter 2).
+LCBs do not appear to use area-restricted search \citep{brunet2019}, but we expect that the foraging range of leafcutter bees around their shelters would sitill decrease, because if honey bees lower pollen and nectar levels at the edge of the field, then leafcutter bees should travel shorter distances to gather the same reward (according to the predictions of Chapter 2).
 %RC: MAY HAVE TO CHOP FOR THE MANUSCRIPT, BECAUSE IT DOESN'T HAVE OTHER AREA-RESTRICTED SEARCH LIT

### 2022-06-27 helperFunctions.R

@@ -32,19 +32,28 @@ parTable <- function(x){
 
 #Faster pair plot
 fastPairs <- function(l,pars=NULL,N=500){ 
+  library(rstan)
   if(class(l)=='stanfit'){
-    l <- extract(l,pars=pars)
+    l <- rstan::extract(l,pars=pars)
     if(any(sapply(l,function(x) length(dim(x)))>1)){
       stop('Parameters have more than 1 dimension: ',paste(pars[sapply(l,function(x) length(dim(x))>1)],collapse=', '))
     }
     l <- do.call('cbind',l)
-    if(nrow(l)>N) l <- l[round(seq(1,nrow(l),length.out=N)),]
+    if(nrow(l)>N) l <- l[round(seq(1,nrow(l),length.out=N)),,drop=FALSE]
   }
-  pairs(l,lower.panel=function(x,y){
-    par(usr=c(0,1,0,1))
-    text(0.5, 0.5, round(cor(x,y),2), cex = 1 * exp(abs(cor(x,y))))},
-    panel=function(x,y){ points(x,y,pch=19)}
+  if(ncol(l)==1){
+    warning('Only 1 parameter found. Displaying histogram instead of biplot')
+    hist(l,main='',xlab=pars)
+  } else {
+    if(length(ncol(l))>10) warning('More than 10 parameters. Pairplot may take some time.')
+    pairs(l,lower.panel=function(x,y){
+      par(usr=c(0,1,0,1))
+      text(0.5, 0.5, round(cor(x,y),2), cex = 1 * exp(abs(cor(x,y))))},
+      panel=function(x,y){ points(x,y,pch=19)}
     )
+  }
+  
+  
 }
 
 #Function to calculate R2 for GLMMs. fixVar, ranVar and resVar are either variable names (vector of var names for random effects), or NA, indicating no effect specified
@@ -375,7 +384,7 @@ shipley.dSep <- function(d,p,lab){
   }
   
   tCol <- rev(ifelse(pvals<0.05,'red','black'))
-  ttl <- paste0('C-stat: ',formatC(ret[1],3),', k: ',ret[2],', p: ',formatC(ret[3],format='e'))
+  ttl <- paste0('C-stat: ',formatC(ret[1],3),', k: ',ret[2],', p: ',formatC(ret[3],digits=3))
   
   d %>% mutate(param=factor({{lab}},levels=rev({{lab}}))) %>% 
     mutate(tooLow={{p}}<=0.05) %>% 
[…]

### 2022-06-27 yield path analysis commodity.R

@@ -148,7 +148,7 @@ load('./Models/datalist_commodity.Rdata')
 # 
 # save(datalist,file = './Models/datalist_commodity.Rdata')
 
-# Run models ----------------------------
+# Run main models ----------------------------
 
 library(rstan)
 setwd('./Models')
@@ -236,6 +236,95 @@ compareRE(modList[[8]],'ranEffYield_field',2) #Slopes
 compareRE(modList[[8]],'ranEffYield_plot',1,0.3) #Intercepts
 compareRE(modList[[8]],'ranEffYield_plot',2,0.3) #Slopes - right skew
 
+
+# Path diagram ------------------------------------------------------------
+
+library(ggdag)
+nodeCoords <- data.frame(name=c('numHives','hbeeDist','hbeeVis','pollen',
+                                'plSize','plDens','flDens',
+                                'flwCount','flwSurv','seedCount','seedWeight'),
+                         labs=c('Number\nof Hives','Distance','Honey bee\nVisitation','Pollen\nCount',
+                                'Plant\nSize','Plant\nDensity','Flower\nDensity',
+                                'Flowers\nper Plant','Pods\nper Plant','Seeds\nper Pod','Seed\nSize'),
+                         x=c(0,1,0.5,0.5,
+                             2.5,0,1,
+                             3.5,4,2.5,3.5),
+                         y=c(4,4,3,2,
+                             0,1,1,
+                             0,1,3,2))
+
+
+#Specify model
+commDAG <- dagify(plDens ~ hbeeDist,
+                  plSize ~ plDens + hbeeDist,
+                  flDens ~ plSize + hbeeDist + plDens,
+                  hbeeVis ~ hbeeDist + numHives + flDens,
+                  pollen ~ hbeeVis + hbeeDist,
+                  flwCount ~ plSize + flwSurv,
+                  flwSurv ~ hbeeVis + plSize + pollen,
+                  seedCount ~ hbeeVis + pollen + plSize + flwSurv + flwCount,
+                  seedWeight ~ hbeeVis + pollen + plSize + seedCount + plDens + hbeeDist + flwSurv + flwCount + flDens,
[…]

### 2022-06-28 seed visitation test.R
Started on seed canola models
- Tried out a couple visitation models with/without Riley's data, with/without male bays included, and with/without male parameter included

- Conclusion: keep Riley's data but remove male term. Can mention that male bays aren't that different in the Methods section, but not include term in full model

@@ -1,0 +1,176 @@
+#Test of whether Riley's data, and then male bays from my data can be excluded without changing results
+
+# Libraries and ggplot theme 
+library(ggplot2)
+theme_set(theme_classic())
+library(dplyr)
+library(tibble)
+library(tidyr)
+library(beepr)
+
+library(xtable)
+
+setwd('~/Projects/UofC/canola_yield_project') #Multivac path
+
+source('helperFunctions.R')
+
+# Load in data 
+
+load('./Models/datalist_seed.Rdata')
+
+
+#Same datalist, but no male bays
+
+datalist2 <- datalist[!grepl('extra',names(datalist))]
+
+datalist2 <- lapply(datalist2,function(x){
+  isF <- !datalist$isMBay
+  if(any(class(x)=='matrix')){
+    return(x[isF,])
+  } else if(length(x)==360){
+    return(x[isF])
+  } else {
+    return(x)
+  }
+})
+
+datalist2$Nplot <- sum(!datalist$isMBay)
+
+#Get rid of flower and plant level measurements
+datalist2 <- datalist2[1:(which(names(datalist2)=='Nflw')-1)]
+
+#Fix flower density measurements
+flDens <- rep(NA,360)
+flDens[datalist$obsflDens_ind] <- datalist$flDens_obs
+flDens <- flDens[!datalist$isMBay]
+# str(datalist2)
+datalist2$Nplot_flDensObs <- sum(!is.na(flDens))
+datalist2$Nplot_flDensMiss <- sum(is.na(flDens))
+datalist2$flDens_obs <- flDens[!is.na(flDens)]
+datalist2$obsflDens_ind <- which(!is.na(flDens))
+datalist2$missflDens_ind <- which(is.na(flDens))
+rm(flDens)
+
+library(rstan)
+setwd('./Models')
+rstan_options(auto_write = TRUE)
+options(mc.cores = 6)
+
+# Honey bee visitation ----------------------
+
+#Models
+modFiles <- c('seed_04hbeeVis.stan',
+              'seed_04hbeeVis_dropMale.stan',
+              'seed_04hbeeVis_noExtra.stan',
+              'seed_04hbeeVis_noExtra_dropMale.stan',
+              'seed_04hbeeVis_noMale.stan')
+modList <- vector(mode = 'list',length = length(modFiles))
[…]

### 2022-06-28 yield path analysis commodity.R

@@ -405,7 +405,7 @@ modList %>%
   mutate(pval=pnorm(-abs(Z))*2) %>% 
   shipley.dSep(.,pval,param)
 
-debugonce(shipley.dSep)
+# debugonce(shipley.dSep)
 
 # Partial effects plots for commodity fields -----------------------------
 

### 2022-06-28 yield path analysis seed.R

@@ -237,6 +237,7 @@ modList[7] <- stan(file=modFiles[7],data=datalist,iter=2000,chains=4,control=lis
 modList[8] <- stan(file=modFiles[8],data=datalist,iter=2000,chains=4,control=list(adapt_delta=0.8),init=0) #Weight per seed
 modList[9] <- stan(file=modFiles[9],data=datalist,iter=2000,chains=4,control=list(adapt_delta=0.8),init=0) #Yield
 beepr::beep(1)
+
 #Traceplots
 for(i in 1:length(modList)){
   if(!is.null(modList[[i]])){

### 2022-06-29 helperFunctions.R
Worked on seed models

@@ -15,7 +15,7 @@ parTable <- function(x){
   require(dplyr); require(tidyr)
   if(is.null(x)) return(NA)
   n <- names(x) #Model parameters
-  n <- n[(!grepl('(\\[[0-9]+,*[0-9]*\\]|lp)',n))|grepl('[sS]igma',n)] #Drops parameter vectors, unless name contains "sigma" (variance term)
+  n <- n[(!grepl('(\\[[0-9]+,*[0-9]*\\]|lp)',n))|grepl('([sS]igma|slope)',n)] #Drops parameter vectors, unless name contains "sigma" (variance term) or "slope"
   n <- n[!grepl('_miss',n)] #Gets rid of imputed values
   
   parTable <- summary(x,pars=n)$summary %>% 
@@ -200,7 +200,7 @@ PPplots <- function(mod,actual=NULL,pars=c('pred','resid','predResid'),main='',i
 
 #Plot of random intercepts
 compareRE <- function(mod,parSet,colNum=1,alpha=1){
-  
+  if(is.null(mod)) stop('Model not found')
   pars <- extract(mod,pars=parSet)[[1]]
   
   if(length(dim(pars))>2){

### 2022-06-29 yield path analysis seed.R

@@ -7,6 +7,11 @@ library(tidyr)
 library(beepr)
 library(xtable)
 
+library(rstan)
+setwd('./Models')
+rstan_options(auto_write = TRUE)
+options(mc.cores = 6)
+
 #Big-text theme, no grid lines (used for Bayer 2016 presentation)
 prestheme=theme(legend.position='right',
                 legend.text=element_text(size=15),
@@ -19,14 +24,14 @@ prestheme=theme(legend.position='right',
 theme_set(theme_bw()+prestheme) #Sets graph theme to B/Ws + prestheme
 rm(prestheme)
 
-setwd('~/Projects/UofC/canola_yield_project') #Multivac path
+# setwd('~/Projects/UofC/canola_yield_project') #Multivac path
 # setwd('~/Documents/canola_yield_project') #Galpern machine path
 
-source('helperFunctions.R')
+source('../helperFunctions.R')
 
 # Load in data ----------------------
 
-load('./Models/datalist_seed.Rdata')
+load('./datalist_seed.Rdata')
 
 # #Seed field data
 # load("./Seed field analysis/seedfieldDataAll.RData")
@@ -215,12 +220,7 @@ load('./Models/datalist_seed.Rdata')
 
 # Run models ----------------------------
 
-library(rstan)
-setwd('./Models')
-rstan_options(auto_write = TRUE)
-options(mc.cores = 6)
 # library(shinystan)
-
 
 #Models split into separate stan files (faster)
 modFiles <- dir(pattern = 'seed_.*\\.stan')
@@ -242,7 +242,7 @@ beepr::beep(1)
 for(i in 1:length(modList)){
   if(!is.null(modList[[i]])){
     n <- names(modList[[i]]) #Model parameters
-    n <- n[(!grepl('(\\[[0-9]+,*[0-9]*\\]|lp)',n))|grepl('[sS]igma',n)] #Gets rid of parameter vectors, unless it contains "sigma" (variance term)
+    n <- n[(!grepl('(\\[[0-9]+,*[0-9]*\\]|lp)',n))|grepl('([sS]igma|slope)',n)] #Gets rid of parameter vectors, unless it contains "sigma" (variance term) or "slope"
     n <- n[!grepl('_miss',n)] #Gets rid of imputed values
     
     p <- traceplot(modList[[i]],pars=n,inc_warmup=FALSE) #+ geom_hline(yintercept = 0) #Traceplots
[…]

### 2022-06-30 yield path analysis commodity.R
Worked on seed field claims

@@ -243,7 +243,7 @@ library(ggdag)
 nodeCoords <- data.frame(name=c('numHives','hbeeDist','hbeeVis','pollen',
                                 'plSize','plDens','flDens',
                                 'flwCount','flwSurv','seedCount','seedWeight'),
-                         labs=c('Number\nof Hives','Distance','Honey bee\nVisitation','Pollen\nCount',
+                         labs=c('Number\nof Hives','Distance','Honey bee\nVisits','Pollen\nCount',
                                 'Plant\nSize','Plant\nDensity','Flower\nDensity',
                                 'Flowers\nper Plant','Pods\nper Plant','Seeds\nper Pod','Seed\nSize'),
                          x=c(0,1,0.5,0.5,

### 2022-06-30 yield path analysis seed.R

@@ -1,6 +1,6 @@
 #CODE USED IN ANALYSIS OF INSECT VISITATION, NECTAR, AND POLLEN DEPOSITION IN SEED CANOLA FIELDS (2014+2015)
 
-# Libraries and ggplot theme ---------------------------------------------------------
+# Libraries, functions, and seed DAG  ---------------------------------------------------------
 library(ggplot2)
 library(dplyr)
 library(tidyr)
@@ -28,6 +28,38 @@ rm(prestheme)
 # setwd('~/Documents/canola_yield_project') #Galpern machine path
 
 source('../helperFunctions.R')
+
+library(ggdag)
+nodeCoords <- data.frame(name=c('numHives','hbeeDist','lbeeDist','hbeeVis','lbeeVis','pollen',
+                                'plSize','plDens','flDens','cent',
+                                'flwCount','flwSurv','seedCount','seedWeight'),
+                         labs=c('Number\nof Hives','Honey bee\nDistance','Leafcutter\nDistance',
+                                'Honey bee\nVisits','Leafcutter\nVisits','Pollen\nCount',
+                                'Plant\nSize','Plant\nDensity','Flower\nDensity','Bay Centre',
+                                'Flowers\nper Plant','Pods\nper Plant','Seeds\nper Pod','Seed\nSize'),
+                         x=c(0,0,1,0,1,0.5,
+                             2.5,0,1,0.5,
+                             3.5,4,2.5,3.5),
+                         y=c(4,4,4,3,3,2,
+                             0,1,1,0.5,
+                             0,1,3,2))
+
+
+#Specify model
+seedDAG <- dagify(plDens ~ hbeeDist,
+                  plSize ~ plDens + hbeeDist,
+                  flDens ~ hbeeDist,
+                  hbeeVis ~ flDens + hbeeDist + lbeeDist + cent,
+                  lbeeVis ~ flDens + hbeeDist + lbeeDist + cent,
+                  pollen ~ hbeeVis  + lbeeVis + cent + hbeeDist + flDens,
+                  flwCount ~ plSize + cent + flwSurv,
+                  flwSurv ~ pollen + plSize + cent + hbeeDist + lbeeDist + flDens,
[…]

### 2022-07-05 Models/Seed model claims 3/runClaims.R
Ran seed claims set

@@ -1,0 +1,9 @@
+#Run claims
+
+for(N in 1:2){
+  txt <- readLines('./Seed model claims 3/runClaimsTemplate.R')
+  txt <- gsub('MODNUMBER',N,txt)
+  writeLines(txt,'./Seed model claims 3/runClaimsCurrent.R')
+  tempEnv <- new.env()  
+  source('./Seed model claims 3/runClaimsCurrent.R',local=tempEnv,echo=FALSE,chdir = TRUE)
+}

### 2022-07-05 Models/Seed model claims 3/runClaimsCurrent.R

@@ -1,0 +1,75 @@
+#Template for running claim sets
+# wd <- getwd()
+# setwd("C:\\Users\\Samuel\\Documents\\Projects\\UofC\\canola_yield_project\\Models\\Seed model claims 3")
+
+library(ggplot2)
+library(dplyr)
+library(tidyr)
+library(beepr)
+library(xtable)
+
+library(rstan)
+rstan_options(auto_write = TRUE)
+options(mc.cores = 6)
+
+#Big-text theme, no grid lines (used for Bayer 2016 presentation)
+prestheme=theme(legend.position='right',
+                legend.text=element_text(size=15),
+                axis.text=element_text(size=15),
+                axis.title=element_text(size=20),
+                title=element_text(size=20),
+                panel.grid.major=element_blank(),panel.grid.minor=element_blank(),
+                panel.border=element_rect(size=1,colour='black'),
+                strip.text=element_text(size=15))
+theme_set(theme_bw()+prestheme) #Sets graph theme to B/Ws + prestheme
+rm(prestheme)
+
+source("C:\\Users\\Samuel\\Documents\\Projects\\UofC\\canola_yield_project\\helperFunctions.R")
+
+load("C:\\Users\\Samuel\\Documents\\Projects\\UofC\\canola_yield_project\\Models\\datalist_seed.Rdata")
+
+#Get model names, and make list
+modFiles <- dir(path='.',pattern = 'claim.+\\.stan',full.names = FALSE)
+modFiles <- modFiles[!grepl('template',modFiles)]
+modFiles <- modFiles[sapply(read.csv("claimsList_updated.csv")$Filename,function(x){
+  l <- grep(x,modFiles)
+  if(length(l)==0) 0 else l
+})]
+
+i <- 1
+
+if(file.exists(modFiles[i])){
+  print(paste0('Starting model ',modFiles[i]))
+  #Run model
+  # mod <- stan(file=modFiles[i],data=datalist,iter=3000,chains=4,control=list(adapt_delta=0.8),init=0)
+  mod <- stan(file=modFiles[i],data=datalist,iter=400,chains=1,control=list(adapt_delta=0.8),init=0)
+  temp <- parTable(mod) #Get parameter summaries
+  #Save information to csv file
[…]

### 2022-07-05 Models/Seed model claims 3/runClaimsTemplate.R

@@ -1,0 +1,75 @@
+#Template for running claim sets
+
+i <- commandArgs(trailingOnly = TRUE)
+i <- as.numeric(i)
+i <- i[!is.na(i)]
+if(length(i)>1) stop('Too many arguments')
+
+library(ggplot2)
+library(dplyr)
+library(tidyr)
+library(beepr)
+library(xtable)
+
+library(rstan)
+rstan_options(auto_write = TRUE)
+options(mc.cores = 6)
+
+#Big-text theme, no grid lines (used for Bayer 2016 presentation)
+prestheme=theme(legend.position='right',
+                legend.text=element_text(size=15),
+                axis.text=element_text(size=15),
+                axis.title=element_text(size=20),
+                title=element_text(size=20),
+                panel.grid.major=element_blank(),panel.grid.minor=element_blank(),
+                panel.border=element_rect(size=1,colour='black'),
+                strip.text=element_text(size=15))
+theme_set(theme_bw()+prestheme) #Sets graph theme to B/Ws + prestheme
+rm(prestheme)
+
+source("C:\\Users\\Samuel\\Documents\\Projects\\UofC\\canola_yield_project\\helperFunctions.R")
+
+load("C:\\Users\\Samuel\\Documents\\Projects\\UofC\\canola_yield_project\\Models\\datalist_seed.Rdata")
+
+#Get model names, and make list
+modFiles <- dir(path='.',pattern = 'claim.+\\.stan',full.names = FALSE)
+modFiles <- modFiles[!grepl('template',modFiles)]
+modFiles <- modFiles[sapply(read.csv("claimsList_updated.csv")$Filename,function(x){
+  l <- grep(x,modFiles)
+  if(length(l)==0) 0 else l
+})]
+
+if(file.exists(modFiles[i])){
+  print(paste0('Starting model ',modFiles[i]))
+  #Run model
+  mod <- stan(file=modFiles[i],data=datalist,iter=3000,chains=4,control=list(adapt_delta=0.8),init=0)
+  # mod <- stan(file=modFiles[i],data=datalist,iter=400,chains=1,control=list(adapt_delta=0.8),init=0)
+  temp <- parTable(mod) #Get parameter summaries
+  #Save information to csv file
+
[…]

### 2022-07-05 yield path analysis seed.R

@@ -423,13 +423,13 @@ modFiles <- modFiles[sapply(read.csv('./Seed model claims 3/claimsList_updated.c
   })]
 
 
-for(i in 13){
+for(i in 38){
   overwrite <- TRUE
   if(file.exists(modFiles[i])){
     print(paste0('Starting model ',modFiles[i]))
     #Run model
-    mod <- stan(file=modFiles[i],data=datalist,iter=3000,chains=4,control=list(adapt_delta=0.8),init=0)
-    # mod <- stan(file=modFiles[i],data=datalist,iter=500,chains=1,control=list(adapt_delta=0.8),init=0)
+    # mod <- stan(file=modFiles[i],data=datalist,iter=3000,chains=4,control=list(adapt_delta=0.8),init=0)
+    mod <- stan(file=modFiles[i],data=datalist,iter=400,chains=1,control=list(adapt_delta=0.8),init=0)
     temp <- parTable(mod) #Get parameter summaries
     #Save information to csv file
     modList <- read.csv('./Seed model claims 3/claimsList_updated.csv',sep=',',strip.white = TRUE)
@@ -456,7 +456,6 @@ for(i in 13){
     
   } else print(paste0('Model ',i,' not found'))
 }
-
 
 
 #Marginal plots ---------------------

### 2022-07-06 Models/zinbTest.R
Updated claims for seed models
- Still not getting good predictive plots for ZINB models. Made some test scripts for this

@@ -1,0 +1,26 @@
+#Test estimation of ZINB models
+N <- 300
+x <- runif(N,0,5)
+Beta <- c(0.5,0.1)
+X <- model.matrix(~x)
+mu <- exp(X%*%Beta)
+phi <- 0.7 #NB phi
+theta <- 0.3 #Bernoulli theta 
+ziProc <- rbinom(N,1,theta) #(extra zeros)
+nbProc <- rnbinom(N,mu=mu,size=phi)
+y <- ifelse(ziProc==1,0,nbProc)
+# cbind(ziProc,nbProc,y)
+
+datalist <- list(N=N,Nbeta=length(Beta),X=X,y=y)
+
+testMod <- stan(file='./zinbTest.stan',data=datalist,iter=2000,chains=4,init=0) #Run model
+
+p <- c('Beta','phi','theta')
+p2 <- c('Beta[1]','Beta[2]','phi','theta')
+stan_trace(testMod,pars=p)
+stan_dens(testMod,pars=p)
+fastPairs(testMod,p2)
+PPplots(testMod,datalist$y,c('generated','resid','generated_resid'),'y') 
+
+plot(apply(extract(testMod,'generated')[[1]],2,max),
+      datalist$y,xlab='Generated',ylab='Actual')

### 2022-07-06 helperFunctions.R

@@ -79,26 +79,8 @@ effSize <- function(x) unname(median(x)/diff(quantile(x,c(0.025,0.975))))
 #Does 95% of posterior overlap zero?
 overlap <- function(x) {r <- quantile(x,c(0.025,0.975))>=0; xor(r[1],r[2]);}
 
-# #Posterior predictive check plots - older version
-# PPplots <- function(resid,predResid,actual,pred,main=NULL){
-#   par(mfrow=c(2,1))
-#   resRange <- range(resid)
-#   pResRange <- range(predResid)
-#   xl <- yl <- c(pmin(resRange[1],pResRange[1]),pmax(resRange[2],pResRange[2]))
-#   x <- sum(resid<predResid)/length(resid)
-#   plot(resid~predResid,ylab='Sum actual residuals',xlab='Sum simulated residuals',xlim=xl,ylim=yl,
-#        main=paste(main,' (p =',round(min(x,1-x),3),')'))
-#   # legend('topleft',)
-#   abline(0,1,col='red') #PP plot
-#   plot(actual~pred, #Predicted vs Actual
-#        xlab=paste('Predicted',main),ylab=paste('Actual',main)) 
-#   abline(0,1,col='red')
-#   abline(lm(actual~pred),col='red',lty=2)
-#   par(mfrow=c(1,1))
-# }
-
 #Posterior predictive check plots
-PPplots <- function(mod,actual=NULL,pars=c('pred','resid','predResid'),main='',index=NA,jitterX=NA,scale=''){
+PPplots <- function(mod,actual=NULL,pars=c('pred','resid','predResid'),main='',index=NA,jitterX=NA,scale='',ZIpar=NA){
   if(is.null(mod)) stop('Model not found')
   require(ggpubr)
   oldtheme <- theme_get() #Get theme
@@ -190,10 +172,25 @@ PPplots <- function(mod,actual=NULL,pars=c('pred','resid','predResid'),main='',i
     geom_line(aes(y=y))+
     labs(x='Value',y='Density',title='Actual vs Simulated Density')
   
-  p <- ggarrange(p1,p2,p3,ncol=1,nrow=3)
+  if(is.na(ZIpar)){
+    
+    p <- ggarrange(p1,p2,p3,ncol=1,nrow=3)  
+  } else {
+    #Zero-inflation plots
+    propActualZero <- sum(actual==0)/length(actual)
[…]

### 2022-07-06 yield path analysis seed.R

@@ -25,7 +25,7 @@ theme_set(theme_bw()+prestheme) #Sets graph theme to B/Ws + prestheme
 rm(prestheme)
 
 # setwd('~/Projects/UofC/canola_yield_project') #Multivac path
-# setwd('~/Documents/canola_yield_project') #Galpern machine path
+setwd('~/Documents/canola_yield_project/Models') #Galpern machine path
 
 source('../helperFunctions.R')
 
@@ -54,7 +54,7 @@ seedDAG <- dagify(plDens ~ hbeeDist,
                   pollen ~ hbeeVis  + lbeeVis + cent + hbeeDist + flDens,
                   flwCount ~ plSize + cent + flwSurv,
                   flwSurv ~ pollen + plSize + cent + hbeeDist + lbeeDist + flDens,
-                  seedCount ~ pollen + plSize + cent + hbeeDist + flDens + flwSurv,
+                  seedCount ~ pollen + plSize + cent + hbeeDist + flDens + flwSurv + flwCount,
                   seedWeight ~ pollen + seedCount + plSize + plDens + lbeeDist,
                   coords= list(x = setNames(nodeCoords$x,nodeCoords$name),
                                y = setNames(nodeCoords$y,nodeCoords$name)),
@@ -66,10 +66,10 @@ seedDAG <- dagify(plDens ~ hbeeDist,
 load('./datalist_seed.Rdata')
 
 # #Seed field data
-# load("./Seed field analysis/seedfieldDataAll.RData")
+# load("../Seed field analysis/seedfieldDataAll.RData")
 # fieldsAllSeed <- data.frame(allFields); plantsAllSeed <- data.frame(allPlants)
 # pollenAllSeed <- data.frame(allPollen); seedsAllSeed <- data.frame(allSeeds);
-# surveyAllSeed <- data.frame(allSurvey); 
+# surveyAllSeed <- data.frame(allSurvey);
 # plantsAllSeed$Field <- gsub('Unrah','Unruh',plantsAllSeed$Field) #Fixes spelling error
 # seedsAllSeed$Field <- gsub('Unrah','Unruh',seedsAllSeed$Field)
 # seedsAllSeed$EdgeCent <- ifelse(seedsAllSeed$EdgeCent=='Cent','Center',seedsAllSeed$EdgeCent) #Fixes cent/center
@@ -78,7 +78,7 @@ load('./datalist_seed.Rdata')
[…]

### 2022-07-06 Models/zinbTest.R
Updated ZINB test

@@ -1,7 +1,7 @@
 #Test estimation of ZINB models
 N <- 300
 x <- runif(N,0,5)
-Beta <- c(0.5,0.1)
+Beta <- c(0.5,0.2)
 X <- model.matrix(~x)
 mu <- exp(X%*%Beta)
 phi <- 0.7 #NB phi
@@ -20,7 +20,27 @@ p2 <- c('Beta[1]','Beta[2]','phi','theta')
 stan_trace(testMod,pars=p)
 stan_dens(testMod,pars=p)
 fastPairs(testMod,p2)
-PPplots(testMod,datalist$y,c('generated','resid','generated_resid'),'y') 
+PPplots(testMod,datalist$y,c('generated','resid','generated_resid'),'y',ZIpar='theta') #The actual vs generated plot sucks. Can it be improved?
 
-plot(apply(extract(testMod,'generated')[[1]],2,max),
-      datalist$y,xlab='Generated',ylab='Actual')
+#Something like this:
+t(apply(exp(X %*% t(extract(testMod,'Beta')[[1]]))*(1-outer(rep(1,datalist$N),extract(testMod,'theta')[[1]])),
+        1,function(x) quantile(x,c(0.5,0.1,0.9)))) %>% 
+  data.frame() %>% setNames(c('med','lwr','upr')) %>% 
+  mutate(x=x,y=datalist$y) %>% 
+  ggplot(aes(x=med,y=y))+
+  geom_point() + 
+  geom_errorbarh(aes(xmax=upr,xmin=lwr),height=0,alpha=0.1)+
+  geom_smooth(method='lm',se=FALSE,col='blue',linetype='dashed',formula = y~x)+ #Regression line
+  geom_abline(intercept = 0,slope=1,col='blue',linetype='solid')+ #1:1 line
+  labs(x='Predicted',y='Actual') #Axis labels
+
+#Actual plot looks OK
+t(apply(exp(X %*% t(extract(testMod,'Beta')[[1]]))*(1-outer(rep(1,datalist$N),extract(testMod,'theta')[[1]])),
+        1,function(x) quantile(x,c(0.5,0.1,0.9)))) %>% 
+  data.frame() %>% setNames(c('med','lwr','upr')) %>% 
+  mutate(x=x,y=datalist$y) %>% 
+  arrange(x) %>% 
+  ggplot(aes(x=x,y=y))+
+  geom_line(aes(x=x,y=med))+
[…]

### 2022-07-06 helperFunctions.R

@@ -95,9 +95,10 @@ PPplots <- function(mod,actual=NULL,pars=c('pred','resid','predResid'),main='',i
   
   if(main=='') main <- deparse(substitute(actual))
   
-  pred <- apply(modVals[[which(nam==pars[1])]],2,median) #Median predicted value
-  predUpr <- apply(modVals[[which(nam==pars[1])]],2,function(x) quantile(x,0.9)) #Upper predicted
-  predLwr <- apply(modVals[[which(nam==pars[1])]],2,function(x) quantile(x,0.1)) #Lower predicted
+  genVals <- modVals[[which(nam==pars[1])]] #Generated values
+  pred <- apply(genVals,2,median) #Median predicted value
+  predUpr <- apply(genVals,2,function(x) quantile(x,0.9)) #Upper predicted
+  predLwr <- apply(genVals,2,function(x) quantile(x,0.1)) #Lower predicted
   
   resid <- apply(modVals[[which(nam==pars[2])]],1,function(x) sum(abs(x))) #Sum of actual residuals
   predResid <- apply(modVals[[which(nam==pars[3])]],1,function(x) sum(abs(x))) #Sum of simulated residuals
@@ -121,12 +122,12 @@ PPplots <- function(mod,actual=NULL,pars=c('pred','resid','predResid'),main='',i
          title=paste0(main,' (p = ',round(min(x,1-x),3),')'))+
     xlim(xl)+ylim(yl)
   
-  #Actual vs Predicted plot
+  #Actual vs Generated plot
   
-  d2 <- data.frame(actual,pred,predUpr,predLwr) #Data for predicted vs actual plot
+  d2 <- data.frame(actual,pred,predUpr,predLwr) #Data for generated vs actual plot
   
   if(scale=='log'){
-    d2 <- d2 %>% mutate(across(everything(),~.x+0.1)) #If log-log, add 0.1 to predicted and actual
+    d2 <- d2 %>% mutate(across(everything(),~.x+0.1)) #If log-log, add 0.1 to generated and actual
   }
   
   p2 <- d2 %>% ggplot(aes(x=pred,y=actual))
@@ -142,7 +143,7 @@ PPplots <- function(mod,actual=NULL,pars=c('pred','resid','predResid'),main='',i
   p2 <- p2 +
     geom_smooth(method='lm',se=FALSE,col='blue',linetype='dashed',formula = y~x)+ #Regression line
[…]

### 2022-07-08 Manuscript/main.tex
Started on seed canola models
- Tried out a couple visitation models with/without Riley's data, with/without male bays included, and with/without male parameter included

- Conclusion: keep Riley's data but remove male term. Can mention that male bays aren't that different in the Methods section, but not include term in full model
Updated seed model claims

@@
 %Maps + climate graphs needed for publication
-During 2015 and 2016, we also surveyed 35 hybrid seed canola fields (15 in 2015, 20 in 2016) near Lethbridge, Alberta, from June through August of each year, all of which had central-pivot irrigation
-Seed fields were stocked with honey bee hives at a rate of 3.6 hives/ha, with apiaries stationed in the corners of fields, and were also stocked with LCBs in shelters throughout the field (1.3 or 2.6 shelters/ha).
+During 2015 and 2016, we also surveyed 35 hybrid seed canola fields (15 in 2015, 20 in 2016) near Lethbridge, Alberta, from June through August of each year, all of which had central-pivot irrigation.
+In seed canola fields, bays of hermaphroditic (herafter ``male") and female plants are typically planted in 1- and 6-m wide bays, respectively. 
+Seed fields were stocked with honey bee hives at a rate of 3.6 hives/ha, with apiaries stationed in the corners of fields, and were also stocked with LCB shelters at a rate of approximately 2 shelters/ha (Figure \ref{fig:seedfieldPhoto}, \ref{fig:seedfieldPlots}).
+% (1.3 or 2.6 shelters/ha).
 % Shelters used either ``standard" or ``double"  LCB stocking ($\approx$50,000 vs.
@@
 
-In both fields, we established set of plots at varying distance from the sources of pollinators. 
-In commodity fields, we established 1 m$^2$ plots at 5, 20, 100, and 500m, starting at the field margin closest to the set of honey bee hives %(271 total plots), 
-and established plots starting at potential sources of natural pollinating insects in unstocked fields (forests, shrublands, or grasslands), but observed very few wild pollinators (Table \ref{tab:propVisitors}).
-In seed canola fields, bays of hermaphroditic (herafter ``male") and female plants are typically planted in 1- and 6-m wide bays, respectively, and LCB shelters were located in the female bays (Figure \ref{fig:seedfieldPhoto}, \ref{fig:seedfieldPlots}).
-We established plots at 5, 20, 100 (250 in 2016), and 400m into the field along a transect from the nearest set of honey bee hives, using pairs of plots at the edge of adjacent male and female bays at each distance (Figure \ref{fig:seedfieldPlots}).
-We established another plot in the centre of the female bay at the 5m and 400m plot in each field to examine how visitation varied within the female bay.
-We used a Nikon\texttrademark Laser 800S Rangefinder to measure the distance from each plot to the nearest shelter.
-All surveys occurred on fair-weather days (median air temperature: 24.5$^\circ$C., range: 17--33) with no rain and as minimal wind as possible (less than 30km/hr).
-Mean air temperature was similar between years in Grande Prairie ($\approx$ 22$^\circ$C), but Lethbridge was warmer in 2015 (23 vs. 28$^\circ$C).
-Finally, we incorporated plot-level visitation data from Waytes (\citeyear{waytesMsc}; same years and locations) to more accurately estimate the effect of distance from shelter on visitation rates (647 total plots).
+In both field types, we established set of plots at varying distance from the sources of pollinators. 
+In commodity fields, plots were located at 1 m$^2$ plots at 5, 20, 100, and 500 m (271 total plots), starting at the field edge closest to the set of honey bee hives or potential sources of natural pollinating insects in unstocked fields (forests, shrublands, or grasslands).
+We observed very few wild pollinators (Table \ref{tab:propVisitors}), so these were excluded from the analysis.
+In seed fields, we established plots at 5, 20, 100 (250 m in 2016), and 400 m into the field along a transect from the nearest set of honey bee hives, using pairs of plots at the edge of adjacent male and female bays (Figure \ref{fig:seedfieldPlots}).
+To examine within-bay variation in visitation, we established a plot at the centre of the female bay at the 5m and 400m plot in each field. 
+Distances to nearest shelters were measured using a Nikon\texttrademark Laser 800S Rangefinder.
+Finally, we incorporated plot-level visitation data from Waytes (\citeyear{waytesMsc}; same years and locations) to more accurately gauge the effect of distance from shelter on visitation rates (647 total plots).
+All surveys occurred on fair-weather days (median air temperature: 24.5$^\circ$C., range: 17--33) with no rain and as minimal wind (less than 30km/hr).
+% Mean air temperature was similar between years in Grande Prairie ($\approx$ 22$^\circ$C), but Lethbridge was warmer in 2015 (23 vs. 28$^\circ$C).
 %Plots were marked with coloured stakes driven into the soil to locate them later in the season. %Full paper should have a table of climate variables. Windspeed needs sorting out (unit problems?)
 
-Insect visitation and pollination data was collected once during the main canola bloom at each field (late June - late July), and plants were collected before harvest (mid - late August).
-We recorded the number of insect visits that contacted the stigmas and anthers of flowers during 10 minutes of observation (5 min for seed fields during 2015), recorded the taxonomic group of the insect visitors, and counted the number of open, visitable flowers in each plot (petals had not yet started to dehisce, style had not elongated more than 3-4 millimeters beyond the anthers).
-To assess pollen deposition, we collected stigmas from five random open flowers at each plot, mounted them in fuchsin gel \citep{beattie1971} on depression slides, and counted the pollen on each stigma using a Leica\texttrademark DME 13595 light microscope under 100x magnification (1294 commodity and 1050 seed canola stigmas).
-At the end of the growing season, we collected three plants from the same plot and recorded the density of plants per m$^2$ (789 commodity canola plants, 582 seed canola plants).
-After drying the plants, we weighed the entire plant, counted mature pods, and counted the number of flower pedicels to estimate total flower production. % at 50$^\circ$C
-We randomly sampled five pods from each plant, and counted and weighed the seeds from each pod (3872 commodity canola pods, 2885 seed canola pods), then we threshed all the pods for each plant by hand, winnowed them using an air separator, and weighed the total mass of cleaned seeds.
+Insect visitation and pollination data were collected once during the main canola bloom at each field (late June - late July), and plants were collected just prior to harvest (mid - late August).
+We recorded the number of insect visits that contacted the stigmas and anthers of flowers during 10 minutes of observation (5 min for seed fields during 2015), recorded the identity of the visitor, and counted the number of open, visitable flowers in each plot (petals had not yet started to dehisce, style had not elongated more than 3-4 millimeters beyond the anthers).
+To assess pollen deposition, we collected stigmas from five random flowers at each female plot, mounted them in fuchsin gel \citep{beattie1971} on depression slides, and counted the pollen on each stigma using a Leica\texttrademark DME 13595 light microscope under 100x magnification (1294 commodity and 1050 seed canola stigmas).
+At the end of the growing season, we collected three plants from the same female plot and recorded the plant density per m$^2$ (789 commodity canola plants, 582 seed canola plants).
+After drying the plants, we weighed the entire plant, counted mature pods to estimate pod set, and counted the number of flower pedicels to estimate total flower production. % at 50$^\circ$C
+We estimated seed size and seeds per pod by averaging the seed count and weight from five pods on each plant.
+Finally, we threshed all the pods for each plant by hand, winnowed them using an air separator, and weighed the total mass of cleaned seeds. % (3872 commodity canola pods, 2885 seed canola pods)
 
@@
 Starting with a simple model (visitation $\rightarrow$ pollen deposition $\rightarrow$ fruit production $\leftarrow$ plant resources), we built a detailed model relating visitation to pollination to seed yield within a causal framework (Figures \ref{fig:commoditySEM} and \ref{fig:seedSEM}).
-These models allowed us to model how visitation ultimately influences seed yield, while controlling for other confounding factors (e.g. distance into field, measurements taken at different fields).
-Fruit set can suppress future vegetative growth and flower production \citep{stephenson1981}, but SEMs do not allow for causal loops \citep{grace2012}, so we included a path from fruit set to flower production as the closest approximation of this process.
-The direction of the path could plausibly be reversed (implying that large flower production reduces the proportion of fruit set), but we considered only the first scenario, as \citet{sabbahi2006} showed that the converse process is more likely (where low fruit set causes increased flower production).
+These models let us model how visitation ultimately influences seed yield, while controlling for other confounding factors (e.g. distance into field, measurements taken at different fields).
+Pod set can suppress future vegetative growth and flower production \citep{stephenson1981}, but SEMs do not allow for causal loops \citep{grace2012}, so we included a path from pod set to flower production as the closest approximation of this process.
+The direction of the path could be reversed, implying that large flower production reduces the proportion of pod set, but we considered only the first scenario, as \citet{sabbahi2006} showed that low pod set increases flower production.
 
 The underlying models of each pSEM were specified as generalized linear mixed-effects models (GLMMs, see Equation sets S1 and S2 for model specifications).
-We used GLMMs to model processes that occur at different levels; for example, seed size-number trade-offs were modelled at the pod level, whereas pollen deposition was modeled at the flower level.
-Random intercepts were used to model variance between fields, within-field (pollen, flower survival, seed count \& size), and within-plot (seed count \& size).
-Continuous responses were modeled using log-normal (plant density, plant size), square-root normal (flower density), and exponential-normal distributions (weight per seed), while counts were modeled as a negative-binomial (honey bee visits, pollen grains per stigma, flowers per plant, seeds per pod) or zero-inflated negative-binomial distribution (LCB visits) with a log-link function.
+GLMMs can model processes that occur at different levels; for example, seed size was modelled at the plant level, while pollen deposition was modeled at the flower level.
+% Random intercepts were used to model variance between fields, within-field (pollen, flower survival, seed count \& size), and within-plot (seed count \& size).
+Random intercepts were used to model variance at the field level (and plot level, for data collected within plots); however, plot-level variance terms 
+% Plot-level RE omitted from: commodity pollen, commodity flwSurv, commodity seedCount, seed plDens 
+% Continuous responses were modeled using log-normal (plant density, plant size), square-root normal (flower density), and exponential-normal distributions (weight per seed), while counts were modeled as a negative-binomial (honey bee visits, pollen grains per stigma, flowers per plant, seeds per pod) or zero-inflated negative-binomial distribution (LCB visits) with a log-link function.
+(Move to appendix)
 Visitation models used $log$(time) as an ``offset" variable to account for differences in observation times.
-Pod set (fraction of flowers that matured into pods) was modeled using a beta-binomial distribution with a logit-link function.
-Interactions between predictors were evident in honey bee visitation rate (Year:Locality interaction) and plant density (Irrigation:Year) in commodity canola, and for LCB visitation (Tent Stocking:Distance from edge) in seed canola, and were included in each model (represented as Y-shaped path in Figures \ref{fig:commoditySEM} and \ref{fig:seedSEM}).
+Plant and pollen samples were not collected from male bays, and there were no large differences in visitation rates for honey bees or LCBs (p = 0.32, 0.72, respectively) once other terms were included as covariates, so bay identity was excluded from further analysis.
+% Pod set (fraction of flowers that matured into pods) was modeled using a beta-binomial distribution with a logit-link function.
+% Interactions between predictors were evident in honey bee visitation rate (Year:Locality interaction) and plant density (Irrigation:Year) in commodity canola, and for LCB visitation (Tent Stocking:Distance from edge) in seed canola, and were included in each model (represented as Y-shaped path in Figures \ref{fig:commoditySEM} and \ref{fig:seedSEM}).
 
 Structural equation models do not have paths between all variables, which may bias the model results if this independence assumption is incorrect; this requires testing a ``basis set" of independence claims using Shipley's d-separation criteria \citep{shipley2000, shipley2009}.
-The initial commodity canola pSEM was misspecfied, as several missing paths were identified for the initial commodity model (Fisher's C = 167.5, df = 64, p$<<$0.001), but the updated pSEM that included missing paths was adequate (C = 81.6, df = 86, p = 0.62).
-Similarly, the initial seed field pSEM also had several missing paths (C = 37.54, df = 56, p = 0.027), which we corrected (C = 58.10, df = 64, p = 0.68).
+The initial commodity canola pSEM was misspecfied, as several missing paths were identified (Fisher's C = 167.5, df = 64, p$<<$0.001), but the updated pSEM was deemed adequate (C = 81.6, df = 86, p = 0.62).
+Similarly, the initial seed field pSEM also had several missing paths (C = 105.6, df = 76, p = 0.01), which were added, making the updated pSEM adequate (C = 72.2, k = 72, p = 0.47).
 Basis sets were generated using the \texttt{dagitty} library in R 3.5.1.
@@
 All component GLMMs of the pSEM were written in Stan 2.17.1 \citep{gelman2015}, and run using \texttt{rstan} 2.18.1.
-We used informative normal priors ($\mu=0, \sigma=5$) for fixed effects, and gamma priors ($\alpha=1.05, \beta=1$) for the variance components.
-We ran four separate chains with an adaptive phase of 1000 iterations, and a sampling phase of 1000 iterations, then checked for convergence of the chains ($\hat{R} \approx$1) and low autocorrelation within chains (high $N_{eff}$).
-We assessed the adequacy of the underlying probability distribution functions of each model using posterior predictive checks \citep{gelman2013}, and found that the probability distributions were specified correctly (p$\sim$0.5) for all components except seed count.
-This means that while the average seed counts (per plant) were unbiased, the variance within a plant was not. 
-However, the negative binomial distribution had the closest posterior predictive checks of any other distribution. 
+We used weakly informative normal priors ($\mu=0, \sigma=5$) for fixed effects and gamma priors ($\alpha=1, \beta=1$) for the variance components.
+Four separate chains were run with an adaptive phase of 1000 iterations, and a sampling phase of 1000 iterations, then checked for convergence of the chains ($\hat{R} \approx$1) and low autocorrelation within chains (high $N_{eff}$).
+We assessed the underlying probability distribution functions of each model using posterior predictive checks \citep{gelman2013}, and found that the probability distributions were adequately specified (p$\sim$0.5).
+% This means that while the average seed counts (per plant) were unbiased, the variance within a plant was not. 
+% However, the negative binomial distribution had the closest posterior predictive checks of any other distribution. 
 % p-values listed below (also in Tables S3 and S4) are \textit{posterior} p-values, representing the proportion of the posterior distribution that overlapped zero, with Z-scores (mean/standard deviation of posterior) showing the effect size.
@@
 % The path from leafcutter bee visitation to pollen deposition was strong in seed canola (Z=3.2), but there was no path from honey bee visitation to pollen deposition in either crop type.
-% Pollen deposition increased fruit set (Z=3.1) and seeds per pod (Z=2.3) in seed canola, but was not present in commodity canola, showing that yield in seed canola, but not commodity canola, is strongly dependent on pollination.
+% Pollen deposition increased pod set (Z=3.1) and seeds per pod (Z=2.3) in seed canola, but was not present in commodity canola, showing that yield in seed canola, but not commodity canola, is strongly dependent on pollination.
 % %The path from seeds per pod to weight per seed was negative in seed canola (Z=-15.0) but positive in commodity canola (Z=6.1) 
@@
 % Commodity canola had a similar weight per seed, regardless of the plant size, but in seed canola, plant size had a strong influence on seeds per pod (Z=5.6) and weight per seed (4.6).
-% Finally, in both crop types, the paths leading from plant size were the dominant signal influencing fruit set (commodity Z=5.8; seed Z=19.9), but the path from pollen deposition to fruit set was only present in seed canola, showing that plant resources matter strongly for both crop types, but that increased pollen deposition only benefits seed canola.
-
-The results of the underlying components of each pSEM are shown in Figures \ref{fig:commoditySEM} and \ref{fig:seedSEM}:
-
-\begin{table}
-\centering
-\caption{Summary of main measured variables. Vegetative mass refers to the non-seed plant mass.}
-\begin{tabular}{r|llllll|llllll}
-                                       & \multicolumn{6}{l|}{Commodity Fields}           & \multicolumn{6}{l}{Seed Fields}                    \\
-Parameter                              & Min  & Median & Mean   & Max   & SD     & N    & Min    & Median & Mean   & Max    & SD     & N     \\ \hline
-Honey bee visitation (per min)      & 0    & 0      & 0.17   & 3.64  & 0.48   & 271  & 0      & 2      & 14.15  & 215    & 25.13  & 665   \\
-Leafcutter bee visitation (per min) & -    & -      & -      & -     & -      & -    & 0      & 2      & 13.93  & 212    & 25.49  & 665   \\
-Pollen (\# per stigma)                 & 0    & 155    & 293.32 & 3891  & 385.04 & 1355 & 0      & 7      & 21.76  & 578    & 42.53  & 1080  \\
-Flowers per plant                      & 13   & 157    & 196.05 & 1094  & 150.87 & 789  & 26     & 362.50 & 461.33 & 2712   & 326.59 & 600   \\
-Pods per plant                         & 5    & 112    & 143.17 & 892   & 114.57 & 789  & 10     & 244.50 & 299.41 & 1410   & 207.68 & 600   \\
-Seeds per pod                          & 4.6  & 23.6   & 22.95  & 35.4  & 4.97   & 789  & 1.8    & 16.6   & 16.40  & 30.60  & 5.52   & 600   \\
-Weight per 1000 seeds (g)              & 0.39 & 2.72   & 2.74   & 5.35  & 0.8    & 789  & 1.04   & 3.42   & 3.43   & 5.59   & 0.88   & 600  \\
-Total vegetative mass (g)                    & 0.77 & 14.29  & 18.19  & 110.2 & 14.41  & 789  & 1.1849 & 25.20  & 30.32  & 144.32 & 21.16  & 600   \\
-Total seed mass (g)                          & 0.01 & 5.46   & 6.87   & 47.9  & 5.97   & 789  & 0.02   & 7.54   & 9.50   & 60.77  & 7.90   & 600   
-\end{tabular}
-\end{table}
+% Finally, in both crop types, the paths leading from plant size were the dominant signal influencing pod set (commodity Z=5.8; seed Z=19.9), but the path from pollen deposition to pod set was only present in seed canola, showing that plant resources matter strongly for both crop types, but that increased pollen deposition only benefits seed canola.
+% 
+% The results of the underlying components of each pSEM are shown in Figures \ref{fig:commoditySEM} and \ref{fig:seedSEM}:
+% 
+% \begin{table}
+% \centering
+% \caption{Summary of main measured variables. Vegetative mass refers to the non-seed plant mass.}
+% \begin{tabular}{r|llllll|llllll}
+%                                        & \multicolumn{6}{l|}{Commodity Fields}           & \multicolumn{6}{l}{Seed Fields}                    \\
+% Parameter                              & Min  & Median & Mean   & Max   & SD     & N    & Min    & Median & Mean   & Max    & SD     & N     \\ \hline
+% Honey bee visitation (per min)      & 0    & 0      & 0.17   & 3.64  & 0.48   & 271  & 0      & 2      & 14.15  & 215    & 25.13  & 665   \\
+% Leafcutter bee visitation (per min) & -    & -      & -      & -     & -      & -    & 0      & 2      & 13.93  & 212    & 25.49  & 665   \\
+% Pollen (\# per stigma)                 & 0    & 155    & 293.32 & 3891  & 385.04 & 1355 & 0      & 7      & 21.76  & 578    & 42.53  & 1080  \\
+% Flowers per plant                      & 13   & 157    & 196.05 & 1094  & 150.87 & 789  & 26     & 362.50 & 461.33 & 2712   & 326.59 & 600   \\
+% Pods per plant                         & 5    & 112    & 143.17 & 892   & 114.57 & 789  & 10     & 244.50 & 299.41 & 1410   & 207.68 & 600   \\
+% Seeds per pod                          & 4.6  & 23.6   & 22.95  & 35.4  & 4.97   & 789  & 1.8    & 16.6   & 16.40  & 30.60  & 5.52   & 600   \\
+% Weight per 1000 seeds (g)              & 0.39 & 2.72   & 2.74   & 5.35  & 0.8    & 789  & 1.04   & 3.42   & 3.43   & 5.59   & 0.88   & 600  \\
+% Total vegetative mass (g)                    & 0.77 & 14.29  & 18.19  & 110.2 & 14.41  & 789  & 1.1849 & 25.20  & 30.32  & 144.32 & 21.16  & 600   \\
+% Total seed mass (g)                          & 0.01 & 5.46   & 6.87   & 47.9  & 5.97   & 789  & 0.02   & 7.54   & 9.50   & 60.77  & 7.90   & 600   
+% \end{tabular}
+% \end{table}
 
@@
 Honey bee visitation decreased with distance away from the apiary, in both commodity and seed canola fields.
-In commodity fields, honey bee visitation decreased with distance from the apiary at the field edge (Z=-3.7, p$=$0.0002, Figure \ref{fig:hbeeDist_commodity}), decreasing from 8.5 visits/hr at the edge of the field to 3.1 visits/hr at 100 m into the field (given a stocking level of 20 hives).
+In commodity fields, honey bee visitation decreased from 8.5 visits/hr at the edge of the field to 3.1 visits/hr at 100 m into the field (p$=$0.0002, Figure \ref{fig:hbeeDist_commodity}, given a stocking rate of 20 hives).
 % Visitation rates were higher in both years in Lethbridge (2014: 9.3 visits/hr, 2015: 7.1), but were higher in 2015 than 2014 at Grande Prairie (Z=2.3, p$=$0.02), rising from 5 visits/hr at the field edge in 2014 to 17 visits/hr in 2015.
 % (at a stocking level of 20 hives).
-Greater stocking rates increased the honey bee visitation (Z=5.3, p$<$0.0001), with visitation at the edge of the field increasing from 14.5 visits/hr with an apiary of 20 hives to 22.7 visits/hr with an apiary of 40 hives, while unstocked field edges had an average of 1.8 visits/hr.
-In seed canola fields, honey bee visitation also decreased with distance from the apiary (Z=-2.5, p$=$0.01), but the rate of decline was weaker (126 visits/hr at edge of field vs.
-78 visits/hr at 100 m).
-Honey bee visitation was lower near leafcutter shelters (Z=3.9, p$=$0.001), dropping from 60 visits/hr at 10 m to 34 visits/hr at 2 m, likely due to competition with LCBs (Figure \ref{fig:hbeeDist_both}, \ref{fig:lbeeDist_both}).
+Higher stocking rates increased honey bee visitation at the edge of the field from 14.5 visits/hr with an apiary of 20 hives to 22.7 visits/hr with an apiary of 40 hives (Z=5.3, p$<$0.0001), while unstocked field edges had an average of 1.8 visits/hr.
+Honey bee visitation was much higher overall in seed canola fields, but still decreased from 126 visits/hr at edge of field to 78 visits/hr at 100 m from the apiary (Z=-2.5, p$=$0.01). 
+Honey bee visitation was also lower near leafcutter shelters (Z=3.9, p$=$0.001), dropping from 60 visits/hr at 10 m to 34 visits/hr at 2 m, likely due to competition with LCBs (Figure \ref{fig:hbeeDist_both}, \ref{fig:lbeeDist_both}).
 
-LCB visitation declined rapidly with distance from their shelters (Z=-11.4, p$=$0.0001, 75\% reduction in 10 m), and unexpectedly, was higher at the edge of the field than the centre (Z=-4.4, p$=$0.0001, 114 visits/hr vs 28 visits/hr).
-%350 visit/hr at 2 m to 83 visit/hr at 10 m
-However, there was no difference in visitation rates between the edge and the centre when leafcutter cocoon stocking was lower (Z=2.2, p$=$0.028), indicating that leafcutters at high stocking densities likely aggregate in shelters close to the edge of the field (Figure \ref{fig:hbeeDist_both}).
-There was no difference in visitation rates between the male bay and the edge of the female bays (LCB: p$=$0.72, honey bee: p$=$0.32). 
-However, LCB visitation was lower in the centre of the female bay (p$=$0.04, 51 vs.
-29 visits/hr), and honey bee visitation was higher at the centre of the bay (p$=$0.008, 71 vs.
-117 visits/hr, Figure \ref{fig:edgeCentVis_both}).
+LCB visitation declined rapidly with distance from the nearest shelter, showing visitation rates of 350 visits/hr at 2 m declining to 83 visits/hr at 10 m (Z=-11.4, p$=$0.0001). 
+Surprisingly, LCB visitation was also higher at the edge of the field than the centre (Z=-4.4, p$=$0.0001, 114 visits/hr vs 28 visits/hr).
+% However, there was no difference in visitation rates between the edge and the centre when leafcutter cocoon stocking was lower (Z=2.2, p$=$0.028), indicating that leafcutters at high stocking densities likely aggregate in shelters close to the edge of the field (Figure \ref{fig:hbeeDist_both}).
+% There was no difference in visitation rates between the male bay and the edge of the female bays (LCB: p$=$0.72, honey bee: p$=$0.32). 
+LCB visitation was also lower in the centre of the female bays (p$=$0.04, 51 vs.
+29 visits/hr), while honey bee visitation was higher (p$=$0.008, 71 vs.
+117 visits/hr, Figure \ref{fig:edgeCentVis_both}), indicating that pollination is likely done by different species in different parts of the field.
 %Therefore, visitation by both species strongly decreases with distance from the edge of the field, decreases with distance from the leafcutter shelters in seed canola fields, and is done by different bees at the centre of the female bay.
@@
 LCB visitation increased pollen deposition in seed canola fields, but honey bees did not increase pollen deposition in either commodity or seed canola fields.
-Pollen deposition on stigmas was high in commodity canola (mean: 293 grains per stigma, SD: 385, range: 0--3981), but honey bee visitation did not effect deposition (p$=$0.77, Figure \ref{fig:hbeeVisPol}).
-Pollen deposition slighly declined with distance from the edge of the field, but this relationship was weak (p$=$0.07) and only amounted to a 6\% average decrease (290 grains per stigma at the edge, 240 at field centre).
-Flies were also common visitors in commodity fields (Table \ref{tab:propVisitors}), but had no effect on pollen deposition (p$=$0.577), so only honey bees and LCBs were considered as potential pollinators (other flower visitors were rare).
-In seed canola, pollen deposition was much lower overall (mean: 22 grains per stigma, SD: 43, range: 0--578), LCB visitation had a strong positive effect (Z=3.2, p$=$0.002, Figure \ref{fig:visPol_both}, 12 grains/stigma at 6 visits/hr vs.
-16 pollen grains at 60 visits/hr), and was lower at the centre of the field (Z=-4.4, p$=$0.0001, Figure \ref{fig:distCentPol}, 23 vs.
-11 grains/stigma).
-Pollen deposition was also lower at the centre of the female bay (Z=-4.5, p$=$0.0001, 23 vs.
-13 grains/stigma) independent of visitation rate, suggesting that pollen may be lost from bees crossing from male bays, who likely visit flowers at the edge of the bay first \citep{pinnisch1990}.
-Finally, there was no effect of honey bees on pollen deposition in seed canola fields (Z=0.98, p$=$0.33), implying that most of the pollen deposition is the result of leafcutter visitation.
+Pollen deposition on stigmas was high in commodity canola (mean: 293 grains per stigma, SD: 385, range: 0--3981), but honey bee visitation had no impact on this (p$=$0.77, Figure \ref{fig:hbeeVisPol}).
+Pollen deposition slighly declined with distance from the edge of the field, but this relationship was weak (p$=$0.07) and only amounted to a 6\% average decrease (290 grains per stigma at the field edge vs.
+240 at field centre).
+% Flies were also common visitors in commodity fields (Table \ref{tab:propVisitors}), but had no effect on pollen deposition (p$=$0.577), so only honey bees and LCBs were considered as potential pollinators (other flower visitors were rare).
+In seed canola, pollen deposition was much lower overall (mean: 22 grains per stigma, SD: 43, range: 0--578), and decreased from 23 to 11 grains/stigma from the edge to the centre of the field (Z=-4.4, p$=$0.0001, Figure \ref{fig:distCentPol}).
+LCB visits increased pollen deposition from 12 grains/stigma at 6 visits/hr to 16 pollen grains at 60 visits/hr (Z=3.2, p$=$0.002, Figure \ref{fig:visPol_both}), but there was no effect of honey bee visitation (Z=0.98, p$=$0.33), implying that most of the pollen deposition in seed fields is the result of LCB visitation.
+Pollen deposition also decreased from 23 grains/stigma at the edge of the female bay to 13 at the centre of the bay independent of visitation (Z=-4.5, p$=$0.0001), suggesting that pollen may be lost from bees crossing over from male bays \citep{pinnisch1990}.%, who likely visit flowers at the edge of the bay first.
 
@@
 
-Plant size had by far the strongest positive effect on the number of pods produced, and there was evidence of fruit set suppressing flower production.
-Commodity canola plants produced fewer flowers (mean: 198, SD: 157, range: 13--1419) than seed canola plants (mean: 468, SD: 328, range: 26--2712), and also produced fewer pods per plant (mean: 143, SD: 114, range: 5--892) than seed canola plants (mean: 303, SD: 208, range: 10--1410).
-In both commodity and seed canola, plant size had a strong positive effect on the total number of flowers per plant (commodity: Z=92.4, p$<$0.0001, seed: Z=82.7, p$<$0.0001, Figure \ref{fig:plSizeFlwCount}), as well as fruit set (commodity: Z=5.5, p$=$0.0002, seed: Z=19.9, p$<$0.0001, Figure \ref{fig:flwSurv_both}).
-Fruit set had a strong negative influence on total flowers per plant (p$<$0.0001) in both commodity (Z=-12.5) and seed canola (Z=-12.1), indicating that high levels of fruit set suppressed future flower production.
+Plant size had by far the strongest positive effect on the number of pods produced, and there was evidence of pod set suppressing flower production.
+Commodity canola plants produced fewer flowers (mean: 198, SD: 157, range: 13--1419) than seed canola plants (mean: 468, SD: 328, range: 26--2712), and also produced fewer pods per plant (mean: 143, SD: 114, range: 5--892 vs.
+mean: 303, SD: 208, range: 10--1410).
+In both commodity and seed canola, plant size had a strong positive effect on the total number of flowers per plant (both p$<<$0.0001, Figure \ref{fig:plSizeFlwCount}), as well as pod set (both p$<$0.001, Figure \ref{fig:flwSurv_both}).
+Pod set had a strong negative influence on total flowers per plant (p$<$0.0001) in both commodity and seed canola (both p$<<$0.0001), indicating that high pod set suppresses future flower production.
 Finally, commodity plants were also lower-yielding (mean: 6.8 g of seeds per plant, SD: 6.0, range: 0.01--47.9) than seed canola plants (mean: 9.6, SD: 7.9, range: 0.02--60.8).
-However, the harvest index of commodity canola (mean: 0.26, SD: 0.08, range: 0.005--0.65) was higher than seed canola (mean: 0.23, SD: 0.09, range: 0.003--0.55), meaning that commodity plants produced more seeds per gram of biomass than seed canola plants, likely due to the lack of pollen limitation (see below).
+However, the harvest index of commodity canola (mean: 0.26, SD: 0.08, range: 0.005--0.65) was higher than seed canola (mean: 0.23, SD: 0.09, range: 0.003--0.55), meaning that commodity plants produced more seeds per gram of biomass than seed canola plants.%, likely due to the lack of pollen limitation.
 
@@
     \includegraphics[width=\textwidth,keepaspectratio=true]{plSizeFlwSurv_both.png} 
-    \caption[Partial effect of plant size on fruit set]{Partial effect of plant size on fruit set (\% of flowers that became pods), for both commodity and seed canola.
+    \caption[Partial effect of plant size on pod set]{Partial effect of plant size on pod set (\% of flowers that became pods), for both commodity and seed canola.
 Solid lines represent median, and shaded areas represent 95\% CIs.}
@@
 
-Plant size had a positive effect on seed size and seeds per pod in seed canola, but not in commodity canola, and the relationship between seed size and number was negative in seed canola but positive in commodity canola.
-Commodity canola plants produced more seeds per pod (mean: 23.0 seeds per pod, SD: 7.4) than seed canola (mean: 16.3 seeds per pod, SD: 9.1), but seed mass was lower in commodity canola (mean: 2.74 mg/seed, SD: 1.04) than seed canola mean (mean: 3.59 mg/seed, SD: 1.33).
-In commodity canola, plant size did not impact seeds per pod (Z=1.00, p=0.32) or seed size (Z=-0.40, p=0.69, Figure \ref{fig:seedWeightCount_both}), but eed size was positively related to seeds per pod (Z=6.1, p$<$0.0001, Figure \ref{fig:seedWeightCount_both}).
+Plant size had a positive effect on seed size and seeds per pod in seed canola, but not in commodity canola. 
+The relationship between seed size and number was negative in seed canola but positive in commodity canola.
+Commodity canola plants produced more seeds per pod (mean: 23.0 seeds per pod, SD: 7.4) than seed canola (mean: 16.3 seeds per pod, SD: 9.1), 
+but seed size was lower in commodity canola (mean: 2.74 mg/seed, SD: 1.04) than seed canola mean (mean: 3.59 mg/seed, SD: 1.33).
+In commodity canola, plant size did not affect seeds per pod or seed size (p=0.32) or seed size (Z=-0.40, p=0.69, Figure \ref{fig:seedWeightCount_both}), but eed size was positively related to seeds per pod (Z=6.1, p$<$0.0001, Figure \ref{fig:seedWeightCount_both}).
 In seed canola, however, seed size increased with plant size (Z=4.7, p$<$0.0001, Figure \ref{fig:seedWeightCount_both}), decreased with seeds per pod (Z=-13.1, p$<$0.0001), and interestingly, increased with plant density (Z=2.9, p$=$0.004), suggesting resource limitation at both the pod and the plant level.
@@
 Pollen deposition increased fruit production and seed production in seed canola, but not in commodity canola.
-Pollen deposition had no effect on fruit set (p=0.12), seeds per pod (p=0.94) or seed size (p=0.56) in commodity canola, and there was also no direct effect of honey bee visitation on fruit set (p=0.38), seeds per pod (p=0.55), or seed size (p=0.34).
+Pollen deposition had no effect on pod set (p=0.12), seeds per pod (p=0.94) or seed size (p=0.56) in commodity canola, and there was also no direct effect of honey bee visitation on pod set (p=0.38), seeds per pod (p=0.55), or seed size (p=0.34).
 Seed canola, in contrast, was highly dependent on pollen deposition.
-Pollen deposition increased fruit set (Z=3.1, p$=$0.002), and seeds per pod (Z=2.3, p$=$0.02), but had no direct effect on seed size (p$=$0.35).
-Fruit set also decreased with three types of distance: distance into the field (Z=-5.3, p$<$0.0001), distance from leafcutter shelters (Z=-3.2, p$=$0.002), and distance from the edge of the female bay (Z=-4.0, p$=$0.0001).
-Seeds per pod decreased in the centre of the female bay (Z=-4.6, p$<$0.0001), and was higher in plants with high fruit set (Z=6.0, p$<$0.0001).
+Pollen deposition increased pod set (Z=3.1, p$=$0.002), and seeds per pod (Z=2.3, p$=$0.02), but had no direct effect on seed size (p$=$0.35).
+Pod set also decreased with three types of distance: distance into the field (Z=-5.3, p$<$0.0001), distance from leafcutter shelters (Z=-3.2, p$=$0.002), and distance from the edge of the female bay (Z=-4.0, p$=$0.0001).
+Seeds per pod decreased in the centre of the female bay (Z=-4.6, p$<$0.0001), and was higher in plants with high pod set (Z=6.0, p$<$0.0001).
 
@@
 \subsection{Pod production} % The total yield of a canola plant is a function of three components: number of pods per plant, number of seeds per pod, and seed size.
-Fruit set (i.e. pod production) in commodity canola was positively affected by plant size, but not by pollen deposition or honey bee visitation.
+Pod set in commodity canola was positively affected by plant size, but not by pollen deposition or honey bee visitation.
 Both pod production and seeds per pod can increase with extra pollination \citep{jauker2008,sabbahi2005,sabbahi2006,duran2010}, so this lack of effect may be due to a high overall level of pollen deposition (Figure \ref{fig:hbeeVisPol}), even in fields without honey bees.
-There was no effect of honey bee visitation on fruit set, seeds per pod, or seed size, indicating that visitation did not seem to cause either \textit{a)} a greater quantity of pollen (see above) or \textit{b)} higher quality (outcrossed) pollen.
-Self-pollination (geitanogamy) in canola can result in similar fruit production as outcrossing \citep{rosa2011}, implying that pollen quality is not likely a limiting factor in canola fruit set, at least in some varieties.
-Flower number was negatively related to fruit set, which implies a response to pollination (high flower fertilization suppresses further flower production) and/or a reproductive trade-off (greater pod development rate means more competition among pods for resources).
+There was no effect of honey bee visitation on pod set, seeds per pod, or seed size, indicating that visitation did not seem to cause either \textit{a)} a greater quantity of pollen (see above) or \textit{b)} higher quality (outcrossed) pollen.
+Self-pollination (geitanogamy) in canola can result in similar fruit production as outcrossing \citep{rosa2011}, implying that pollen quality is not likely a limiting factor in canola pod set, at least in some varieties.
+Flower number was negatively related to pod set, which implies a response to pollination (high flower fertilization suppresses further flower production) and/or a reproductive trade-off (greater pod development rate means more competition among pods for resources).
 %RC: THESE SCENARIOS AREN'T MUTUALLY EXCLUSIVE
 We considered the first scenario to be the stronger effect, as \citet{sabbahi2006} and \citet{mesquida1981} both found that canola plants compensated for experimental removal of flowers by increasing branch and flower production, until the plant reached about 170 pods.
-Their final number of pods is similar to the plants from our study (median: 112, range: 5--892), but we found that larger plants also had greater fruit set, in addition to higher flower production, presumably caused by the larger pool of resources that large plants are able to invest into reproduction.
+Their final number of pods is similar to the plants from our study (median: 112, range: 5--892), but we found that larger plants also had greater pod set, in addition to higher flower production, presumably caused by the larger pool of resources that large plants are able to invest into reproduction.
 %This could indicate stronger overall competition between plants in seed fields, but that plant resources are higher in the centre of the crop field than at the edge.
@@
 Pollination increased pod production in seed canola, but not in commodity canola, meaning that extra pollination is valuable for seed canola crops, but not commodity canola. 
-This is similar to the findings of \citet{mesquida1981} and \citet{steffan2003}, who found that fruit set in male-sterile plants responded positively to visitation, while male-fertile plants (``male" plants in seed fields, all plants in commodity fields) had no response (but see \citealp{adegas1992}).
+This is similar to the findings of \citet{mesquida1981} and \citet{steffan2003}, who found that pod set in male-sterile plants responded positively to visitation, while male-fertile plants (``male" plants in seed fields, all plants in commodity fields) had no response (but see \citealp{adegas1992}).
 Pod production in seed canola increased with both pollen deposition and plant size, suggesting that both pollen availability and plant resources constrain pod production.
@@
 %RC: SEEMS AN INTERACTION WOULD TEST THIS BETTER
-There were also effects of distance on fruit set, independent of pollen deposition: pod set decreased with distance from the edge of the field and distance to leafcutter shelters independent of pollen deposition, and was lower in the centre of the female bays.
-\citet{mesquida1978} also found that fruit set in male-sterile canola declined quickly with distance from the male-fertile plants (due to wind pollination), but the effect we found is likely related to the earlier effect of lower pollen carryover at the centre of the female bays, and possibly the centre of the field.
+There were also effects of distance on pod set, independent of pollen deposition: pod set decreased with distance from the edge of the field and distance to leafcutter shelters independent of pollen deposition, and was lower in the centre of the female bays.
+\citet{mesquida1978} also found that pod set in male-sterile canola declined quickly with distance from the male-fertile plants (due to wind pollination), but the effect we found is likely related to the earlier effect of lower pollen carryover at the centre of the female bays, and possibly the centre of the field.
 However, our analysis points to the strong relative importance of plant resources, as well as pollination services \citep{marini2015}, mediated through the effect of leafcutter bee visitation, to the production of hybrid seed canola.
@@
 %SH: EFFECT OF WEATHER GOES MUCH DEEPER THAN 22C THRESHOLD
-%However, since year did not affect fruit set, the weather effect seems to be limited to ovules, rather than flower abortion (at least in this data set).
+%However, since year did not affect pod set, the weather effect seems to be limited to ovules, rather than flower abortion (at least in this data set).
 % Seeds per pod is highly correlated with ovule number \citep{clark1979,wang2011} and ovule fertility \citep{bouttier1992}, causing variance of seed within plants. 
@@
 Seed canola plants, in contrast, have much lower levels of pollen deposition overall, and leafcutter bees deliver a large direct benefit to fruit and seed production. 
-The centre of the female bays illustrates this effect: honey bees have a higher visitation rate, but pollen deposition, fruit set, and seed set are all lower.
+The centre of the female bays illustrates this effect: honey bees have a higher visitation rate, but pollen deposition, pod set, and seed set are all lower.
 Finally, both plant size and pollination limit seed production in seed canola, but only plant size limits commodity canola production, showing the relative importance of both pollination and plant resources using in-field data.

### 2022-07-08 Models/Seed model claims 3/runClaims.R

@@ -1,9 +1,0 @@
-#Run claims
-
-for(N in 1:2){
-  txt <- readLines('./Seed model claims 3/runClaimsTemplate.R')
-  txt <- gsub('MODNUMBER',N,txt)
-  writeLines(txt,'./Seed model claims 3/runClaimsCurrent.R')
-  tempEnv <- new.env()  
-  source('./Seed model claims 3/runClaimsCurrent.R',local=tempEnv,echo=FALSE,chdir = TRUE)
-}

### 2022-07-08 Models/Seed model claims 3/runClaims.sh

@@ -1,0 +1,6 @@
+#!/bin/bash
+
+# chmod u+x runClaims.sh #Run this to make shell script executable
+
+# for i in {28..31}; do Rscript ./testScript.R $i; done #Test
+for i in {15}; do Rscript ./runClaimsTemplate.R $i; done #Actual

### 2022-07-08 Models/Seed model claims 3/runClaimsCurrent.R

@@ -1,75 +1,0 @@
-#Template for running claim sets
-# wd <- getwd()
-# setwd("C:\\Users\\Samuel\\Documents\\Projects\\UofC\\canola_yield_project\\Models\\Seed model claims 3")
-
-library(ggplot2)
-library(dplyr)
-library(tidyr)
-library(beepr)
-library(xtable)
-
-library(rstan)
-rstan_options(auto_write = TRUE)
-options(mc.cores = 6)
-
-#Big-text theme, no grid lines (used for Bayer 2016 presentation)
-prestheme=theme(legend.position='right',
-                legend.text=element_text(size=15),
-                axis.text=element_text(size=15),
-                axis.title=element_text(size=20),
-                title=element_text(size=20),
-                panel.grid.major=element_blank(),panel.grid.minor=element_blank(),
-                panel.border=element_rect(size=1,colour='black'),
-                strip.text=element_text(size=15))
-theme_set(theme_bw()+prestheme) #Sets graph theme to B/Ws + prestheme
-rm(prestheme)
-
-source("C:\\Users\\Samuel\\Documents\\Projects\\UofC\\canola_yield_project\\helperFunctions.R")
-
-load("C:\\Users\\Samuel\\Documents\\Projects\\UofC\\canola_yield_project\\Models\\datalist_seed.Rdata")
-
-#Get model names, and make list
-modFiles <- dir(path='.',pattern = 'claim.+\\.stan',full.names = FALSE)
-modFiles <- modFiles[!grepl('template',modFiles)]
-modFiles <- modFiles[sapply(read.csv("claimsList_updated.csv")$Filename,function(x){
-  l <- grep(x,modFiles)
-  if(length(l)==0) 0 else l
-})]
-
-i <- 1
-
-if(file.exists(modFiles[i])){
-  print(paste0('Starting model ',modFiles[i]))
-  #Run model
-  # mod <- stan(file=modFiles[i],data=datalist,iter=3000,chains=4,control=list(adapt_delta=0.8),init=0)
-  mod <- stan(file=modFiles[i],data=datalist,iter=400,chains=1,control=list(adapt_delta=0.8),init=0)
-  temp <- parTable(mod) #Get parameter summaries
-  #Save information to csv file
[…]

### 2022-07-08 Models/Seed model claims 3/runClaimsTemplate.R

@@ -34,7 +34,7 @@ load("C:\\Users\\Samuel\\Documents\\Projects\\UofC\\canola_yield_project\\Models
 #Get model names, and make list
 modFiles <- dir(path='.',pattern = 'claim.+\\.stan',full.names = FALSE)
 modFiles <- modFiles[!grepl('template',modFiles)]
-modFiles <- modFiles[sapply(read.csv("claimsList_updated.csv")$Filename,function(x){
+modFiles <- modFiles[sapply(read.csv("claimsList_updated2.csv")$Filename,function(x){
   l <- grep(x,modFiles)
   if(length(l)==0) 0 else l
 })]
@@ -47,7 +47,7 @@ if(file.exists(modFiles[i])){
   temp <- parTable(mod) #Get parameter summaries
   #Save information to csv file
 
-  csvPath <- "C:\\Users\\Samuel\\Documents\\Projects\\UofC\\canola_yield_project\\Models\\Seed model claims 3\\claimsList_updated.csv"
+  csvPath <- "C:\\Users\\Samuel\\Documents\\Projects\\UofC\\canola_yield_project\\Models\\Seed model claims 3\\claimsList_updated2.csv"
   modList <- read.csv(csvPath,sep=',',strip.white = TRUE)
   modList[i,match(names(temp),names(modList))] <- temp[grepl('claim',temp$param),]
   write.csv(modList,csvPath,row.names = FALSE)
@@ -65,7 +65,7 @@ if(file.exists(modFiles[i])){
   parNam <- parNam[!parNam %in% c('intPollen','slopeVisitPol','slopeHbeeDistPollen','sigmaPolField','pollenPhi')]
 
   p <- traceplot(mod,pars=parNam,inc_warmup=FALSE)+labs(title=gsub('.*/','',modFiles[i]))
-  ggsave(paste0('./',gsub('\\.stan','',modFiles[i]),'.png'),p,width=8,height=8)
+  ggsave(paste0('./',gsub('\\.stan','',modFiles[i]),'.png'),p,width=12,height=8)
   # print(mod,pars=parNam)
   # print(modList[i,match(names(temp),names(modList))])
   # fastPairs(mod,pars=parNam)

### 2022-07-08 Models/Seed model claims 3/testScript.R

@@ -1,0 +1,8 @@
+#Template for running claim sets
+
+i <- commandArgs(trailingOnly = TRUE)
+i <- as.numeric(i)
+i <- i[!is.na(i)]
+if(length(i)>1) stop('Too many arguments')
+
+print(paste('This is a test: ',i))

### 2022-07-08 helperFunctions.R

@@ -230,7 +230,7 @@ g2bushels <- function(x){
 }
 
 #Extract fits for marginal plots
-# mod = stanfit model or dataframe
+# mod = stanfit model or dataframe with parameters 
 # parList = named list with vectors of parameters to predict at (passed through expand.grid)
 # otherPars = character vector of other parameters to add to the dataframe (e.g. zero-inflation)
 # q = quantiles to predict at
@@ -378,7 +378,7 @@ shipley.dSep <- function(d,p,lab){
   }
   
   tCol <- rev(ifelse(pvals<0.05,'red','black'))
-  ttl <- paste0('C-stat: ',formatC(ret[1],3),', k: ',ret[2],', p: ',formatC(ret[3],digits=3))
+  ttl <- paste0('C-stat: ',round(ret[1],2),', k: ',ret[2],', p: ',formatC(ret[3],digits=3))
   
   #(Approximately) how many terms need to be added to make p-value<0.05?
   removeP <- function(p){ #Which p-values should be removed?

### 2022-07-08 yield path analysis seed.R

@@ -8,7 +8,6 @@ library(beepr)
 library(xtable)
 
 library(rstan)
-setwd('./Models')
 rstan_options(auto_write = TRUE)
 options(mc.cores = 6)
 
@@ -24,8 +23,8 @@ prestheme=theme(legend.position='right',
 theme_set(theme_bw()+prestheme) #Sets graph theme to B/Ws + prestheme
 rm(prestheme)
 
-# setwd('~/Projects/UofC/canola_yield_project') #Multivac path
-setwd('~/Documents/canola_yield_project/Models') #Galpern machine path
+setwd('~/Projects/UofC/canola_yield_project/Models') #Multivac path
+# setwd('~/Documents/canola_yield_project/Models') #Galpern machine path
 
 source('../helperFunctions.R')
 
@@ -51,7 +50,7 @@ seedDAG <- dagify(plDens ~ hbeeDist,
                   flDens ~ hbeeDist,
                   hbeeVis ~ flDens + hbeeDist + lbeeDist + cent,
                   lbeeVis ~ flDens + hbeeDist + lbeeDist + cent,
-                  pollen ~ hbeeVis  + lbeeVis + cent + hbeeDist + flDens,
+                  pollen ~ hbeeVis  + lbeeVis + cent + hbeeDist + lbeeDist + flDens,
                   flwCount ~ plSize + cent + flwSurv,
                   flwSurv ~ pollen + plSize + cent + hbeeDist + lbeeDist + flDens,
                   seedCount ~ pollen + plSize + cent + hbeeDist + flDens + flwSurv + flwCount,
@@ -278,7 +277,7 @@ for(i in 1:length(modList)){
     n <- n[!grepl('_miss',n)] #Gets rid of imputed values
     
     p <- traceplot(modList[[i]],pars=n,inc_warmup=FALSE) #+ geom_hline(yintercept = 0) #Traceplots
-    fastPairs(modList[[i]],pars=n)
+    # fastPairs(modList[[i]],pars=n)
     print(modList[[i]],pars=n)
     # p <- stan_plot(modList[[i]],pars=n) #Pointrange plot
     
@@ -378,9 +377,13 @@ tidySeedDAG <- seedDAG %>% #Create tidy dagitty set
 #   geom_dag_text(col='black') +
 #   theme_dag_blank()
 
+tidySeedDAG$data %>% data.frame
+pathCoefs %>% data.frame
+
[…]

### 2022-07-12 Models/zinbTest.R
Updated ZINB test

@@ -1,4 +1,13 @@
+library(tidyverse)
+library(rstan)
+setwd("~/Documents/canola_yield_project/Models")
+source('../helperFunctions.R')
+rstan_options(auto_write = TRUE)
+options(mc.cores = 6)
+theme_set(theme_bw()) #Sets graph theme to B/Ws + prestheme
+
 #Test estimation of ZINB models
+set.seed(1)
 N <- 300
 x <- runif(N,0,5)
 Beta <- c(0.5,0.2)
@@ -20,7 +29,7 @@ p2 <- c('Beta[1]','Beta[2]','phi','theta')
 stan_trace(testMod,pars=p)
 stan_dens(testMod,pars=p)
 fastPairs(testMod,p2)
-PPplots(testMod,datalist$y,c('generated','resid','generated_resid'),'y',ZIpar='theta') #The actual vs generated plot sucks. Can it be improved?
+PPplots(testMod,datalist$y,c('gen','resid','gen_resid'),'y',ZIpar='theta') #The actual vs generated plot sucks. Can it be improved?
 
 #Something like this:
 t(apply(exp(X %*% t(extract(testMod,'Beta')[[1]]))*(1-outer(rep(1,datalist$N),extract(testMod,'theta')[[1]])),

### 2022-07-12 yield path analysis seed.R
Removed plot terms from seed count/weight models

@@ -23,8 +23,8 @@ prestheme=theme(legend.position='right',
 theme_set(theme_bw()+prestheme) #Sets graph theme to B/Ws + prestheme
 rm(prestheme)
 
-setwd('~/Projects/UofC/canola_yield_project/Models') #Multivac path
-# setwd('~/Documents/canola_yield_project/Models') #Galpern machine path
+# setwd('~/Projects/UofC/canola_yield_project/Models') #Multivac path
+setwd('~/Documents/canola_yield_project/Models') #Galpern machine path
 
 source('../helperFunctions.R')
 
@@ -319,9 +319,9 @@ compareRE(modList[[5]],'intFlwCount_plot')
 compareRE(modList[[6]],'intFlwSurv_field')
 compareRE(modList[[6]],'intFlwSurv_plot')
 compareRE(modList[[7]],'intSeedCount_field')
-compareRE(modList[[7]],'intSeedCount_plot') #
+# compareRE(modList[[7]],'intSeedCount_plot') #
 compareRE(modList[[8]],'intSeedWeight_field')
-compareRE(modList[[8]],'intSeedWeight_plot')
+# compareRE(modList[[8]],'intSeedWeight_plot')
 compareRE(modList[[9]],'ranEffYield_field',1) #Intercepts
 compareRE(modList[[9]],'ranEffYield_field',2) #Slopes
 compareRE(modList[[9]],'ranEffYield_plot',1,0.3) #Intercepts

### 2022-07-12 Manuscript/main.tex
Worked on partial plots

@@
 % Random intercepts were used to model variance between fields, within-field (pollen, flower survival, seed count \& size), and within-plot (seed count \& size).
-Random intercepts were used to model variance at the field level (and plot level, for data collected within plots); however, plot-level variance terms 
-% Plot-level RE omitted from: commodity pollen, commodity flwSurv, commodity seedCount, seed plDens 
+Random intercepts were used to model variance at the field level and plot level, but plot-level variance terms had poor traces and low effective sample sizes, indicating low variation within plots.
+Therefore, we omitted plot-level random effects for the commodity field models of pollen deposition, flower survival, seeds per pod, and seed size, and omitted them from the seed field models of seeds per pod and seed size.
 % Continuous responses were modeled using log-normal (plant density, plant size), square-root normal (flower density), and exponential-normal distributions (weight per seed), while counts were modeled as a negative-binomial (honey bee visits, pollen grains per stigma, flowers per plant, seeds per pod) or zero-inflated negative-binomial distribution (LCB visits) with a log-link function.
@@
 Visitation models used $log$(time) as an ``offset" variable to account for differences in observation times.
-Plant and pollen samples were not collected from male bays, and there were no large differences in visitation rates for honey bees or LCBs (p = 0.32, 0.72, respectively) once other terms were included as covariates, so bay identity was excluded from further analysis.
+Plant and pollen samples were not collected from male bays in seed fields, and there were no large differences in visitation rates for honey bees or LCBs (p = 0.32, 0.72, respectively) once other terms were included as covariates, so bay identity was excluded from further analysis.
 % Pod set (fraction of flowers that matured into pods) was modeled using a beta-binomial distribution with a logit-link function.
@@
 Similarly, the initial seed field pSEM also had several missing paths (C = 105.6, df = 76, p = 0.01), which were added, making the updated pSEM adequate (C = 72.2, k = 72, p = 0.47).
-Basis sets were generated using the \texttt{dagitty} library in R 3.5.1.
+Basis sets were generated using the \texttt{dagitty} library in R 4.2.1.
 
@@
 
-All component GLMMs of the pSEM were written in Stan 2.17.1 \citep{gelman2015}, and run using \texttt{rstan} 2.18.1.
+All component GLMMs of the pSEM were written in Stan 2.18.1 \citep{gelman2015} and run using \texttt{rstan} 2.26.13.
 We used weakly informative normal priors ($\mu=0, \sigma=5$) for fixed effects and gamma priors ($\alpha=1, \beta=1$) for the variance components.
 Four separate chains were run with an adaptive phase of 1000 iterations, and a sampling phase of 1000 iterations, then checked for convergence of the chains ($\hat{R} \approx$1) and low autocorrelation within chains (high $N_{eff}$).
-We assessed the underlying probability distribution functions of each model using posterior predictive checks \citep{gelman2013}, and found that the probability distributions were adequately specified (p$\sim$0.5).
+We assessed the underlying probability distribution functions of each model using posterior predictive checks \citep{gelman2013}, and found that the probability distributions were properly specified (p$\sim$0.5).
 % This means that while the average seed counts (per plant) were unbiased, the variance within a plant was not. 

### 2022-07-12 helperFunctions.R

@@ -232,11 +232,11 @@ g2bushels <- function(x){
 #Extract fits for marginal plots
 # mod = stanfit model or dataframe with parameters 
 # parList = named list with vectors of parameters to predict at (passed through expand.grid)
-# otherPars = character vector of other parameters to add to the dataframe (e.g. zero-inflation)
+# otherPars = character vector of other parameters to add to the dataframe
 # q = quantiles to predict at
 # nrep = number of replicates of parameters to generate (for data.frame parameters)
 
-getPreds <- function(mod,parList=NULL,otherPars=NULL,q=c(0.5,0.025,0.975),nrep=4000){
+getPreds <- function(mod,parList=NULL,offset=NULL,ZIpar=NULL,otherPars=NULL,q=c(0.5,0.025,0.975),nrep=4000,trans=NULL){
   if(is.null(parList)) stop('Specify parameters')
   dfNames <- c("param","mean","sd","Z","median",
                "lwr","upr","pval","n_eff","Rhat")
@@ -254,14 +254,6 @@ getPreds <- function(mod,parList=NULL,otherPars=NULL,q=c(0.5,0.025,0.975),nrep=4
       stop(paste0('Parameters not found: ',paste(names(parList)[!names(parList) %in% mod$param],collapse=', ')))
     } 
     chooseRows <- mod$param %in% names(parList) 
-    # if(useQuantiles){
-    #   m1 <- mod[chooseRows,c('lwr','upr')] #Upper/lower ranges  
-    #   m2 <- mod[chooseRows,c('median')] #Median
-    # } else {
-    #   m1 <- data.frame(lwr=mod$mean[chooseRows]-1.96*mod$sd[chooseRows],
-    #                    upr=mod$mean[chooseRows]+1.96*mod$sd[chooseRows])
-    #   m2 <- mod$mean[chooseRows] #Mean
-    # }
     m <- mod[chooseRows,c('mean','sd')] 
     m <- do.call('cbind',lapply(1:nrow(m),function(i) rnorm(nrep,m$mean[i],m$sd[i])))
     colnames(m) <- names(parList)
@@ -279,10 +271,24 @@ getPreds <- function(mod,parList=NULL,otherPars=NULL,q=c(0.5,0.025,0.975),nrep=4
   mm <- expand.grid(parList) #Model matrix
[…]

### 2022-07-12 partial plots.R

@@ -1,0 +1,35 @@
+# MAKES PARTIAL EFFECTS PLOTS FOR SUB-MODELS
+
+# Load everything ---------------------------------------------------------
+library(tidyverse)
+theme_set(theme_bw())
+setwd('~/Documents/canola_yield_project/Figures') #Galpern machine path
+
+source('../helperFunctions.R') #Helper functions
+
+load('../Models/datalist_commodity.Rdata') #Commodity data
+commData <- datalist
+load('../Models/datalist_seed.Rdata') #Seed data
+seedData <- datalist; rm(datalist)
+
+avgCommData <- lapply(commData,function(x) data.frame(min=min(x,na.rm=TRUE),med=median(x,na.rm=TRUE),max=max(x,na.rm=TRUE))) #Summary stats
+avgSeedData <- lapply(seedData,function(x) data.frame(min=min(x,na.rm=TRUE),med=median(x,na.rm=TRUE),max=max(x,na.rm=TRUE))) #Summary stats
+
+load('../Models/modSummaries_commodity.Rdata') #Commodity data models
+load('../Models/modSummaries_seed.Rdata') #Seed data models
+
+# Visitation plots --------------------------------------------------------
+
+#Hbee + Lbee visitation from edge of field/
+
+with(avgCommData,
+     list('intHbeeVis'=1,
+     'slopeHbeeDistHbeeVis'=seq(min(log(dist)),max(log(400)),length=10),
+     'slopeNumHivesHbeeVis'= log(numHives$max), 'slopeFlDensHbeeVis' = avgCommData$flDens$med)) %>% 
+  getPreds(modSummaries_commodity[[2]],parList = .,offset=1,ZIpar = 'phiHbeeVis',trans='exp',q=c(0.5,0.05,0.95)) 
+
+  #   ggplot(aes(x=exp(slopeHbeeDistHbeeVis),y=med))+
+  # geom_ribbon(aes(ymax=upr,ymin=lwr),alpha=0.3)+
+  # geom_line()+
+  # labs(x='Distance from honeybee hives')
+

### 2022-07-12 yield path analysis commodity.R

@@ -20,8 +20,8 @@ prestheme=theme(legend.position='right',
 theme_set(theme_bw()+prestheme) #Sets graph theme to B/Ws + prestheme
 rm(prestheme)
 
-setwd('~/Projects/UofC/canola_yield_project') #Multivac path
-# setwd('~/Documents/canola_yield_project') #Galpern machine path
+# setwd('~/Projects/UofC/canola_yield_project') #Multivac path
+setwd('~/Documents/canola_yield_project') #Galpern machine path
 
 source('helperFunctions.R')
 
@@ -228,9 +228,9 @@ compareRE(modList[[4]],'intFlwCount_plot')
 compareRE(modList[[5]],'intFlwSurv_field')
 compareRE(modList[[5]],'intFlwSurv_plot')
 compareRE(modList[[6]],'intSeedCount_field')
-compareRE(modList[[6]],'intSeedCount_plot') #
+# compareRE(modList[[6]],'intSeedCount_plot') #
 compareRE(modList[[7]],'intSeedWeight_field')
-compareRE(modList[[7]],'intSeedWeight_plot')
+# compareRE(modList[[7]],'intSeedWeight_plot')
 compareRE(modList[[8]],'ranEffYield_field',1) #Intercepts
 compareRE(modList[[8]],'ranEffYield_field',2) #Slopes
 compareRE(modList[[8]],'ranEffYield_plot',1,0.3) #Intercepts
@@ -410,15 +410,15 @@ modList %>%
 # Partial effects plots for commodity fields -----------------------------
 
 #Plant density
+load('modSummaries_commodity.Rdata')
 
 list('intPlDens'=1,
-           'slopeDistPlDens'=with(datalist,seq(min(log(dist)),max(log(dist)),length=10))) %>% 
+           'slopeHbeeDistPlDens'=with(datalist,seq(min(log(dist)),max(log(dist)),length=10))) %>% 
   getPreds(modSummaries_commodity[[1]],parList = .,otherPars = c('sigmaPlDens','sigmaPlDens_field'))
 
-list('intPlDens'=1,
-     'slopeDistPlDens'=with(datalist,seq(min(log(dist)),max(log(dist)),length=10))) %>% 
-  getPreds(modList[[1]],parList = .,otherPars = c('sigmaPlDens','sigmaPlDens_field'))
-
+# list('intPlDens'=1,
[…]

### 2022-07-15 partial plots.R
Worked on partial plots

@@ -3,17 +3,29 @@
 # Load everything ---------------------------------------------------------
 library(tidyverse)
 theme_set(theme_bw())
-setwd('~/Documents/canola_yield_project/Figures') #Galpern machine path
+# setwd('~/Documents/canola_yield_project/Figures') #Galpern machine path
+setwd('~/Projects/UofC/canola_yield_project/Models') #Multivac path
 
 source('../helperFunctions.R') #Helper functions
+
+logCent <- function(x) log(x)-mean(log(x)) #Log-centers data
+summaryDat <- function(x){
+  x <- na.omit(x)
+  data.frame(min=min(x),mean=mean(x),med=median(x),max=max(x))
+} 
 
 load('../Models/datalist_commodity.Rdata') #Commodity data
 commData <- datalist
 load('../Models/datalist_seed.Rdata') #Seed data
 seedData <- datalist; rm(datalist)
 
-avgCommData <- lapply(commData,function(x) data.frame(min=min(x,na.rm=TRUE),med=median(x,na.rm=TRUE),max=max(x,na.rm=TRUE))) #Summary stats
-avgSeedData <- lapply(seedData,function(x) data.frame(min=min(x,na.rm=TRUE),med=median(x,na.rm=TRUE),max=max(x,na.rm=TRUE))) #Summary stats
+#Summary stats (min,median,max) to use for plots
+avgCommData <- lapply(commData,summaryDat) 
+seedData$lbeeDistAll <- with(seedData,c(lbee_dist,lbee_dist_extra))
+seedData$hbeeDistAll <- with(seedData,c(hbee_dist,hbee_dist_extra))
+seedData$clogLbeeDist <- with(seedData,logCent(lbeeDistAll)) #Log-centered distances
+seedData$clogHbeeDist <- with(seedData,logCent(hbeeDistAll))
+avgSeedData <- lapply(seedData,summaryDat) 
 
 load('../Models/modSummaries_commodity.Rdata') #Commodity data models
 load('../Models/modSummaries_seed.Rdata') #Seed data models
@@ -22,11 +34,28 @@ load('../Models/modSummaries_seed.Rdata') #Seed data models
 
 #Hbee + Lbee visitation from edge of field/
 
-with(avgCommData,
[…]

### 2022-07-15 Manuscript/main.tex
Worked on partial effects plots

@@
 Honey bee visitation decreased with distance away from the apiary, in both commodity and seed canola fields.
-In commodity fields, honey bee visitation decreased from 8.5 visits/hr at the edge of the field to 3.1 visits/hr at 100 m into the field (p$=$0.0002, Figure \ref{fig:hbeeDist_commodity}, given a stocking rate of 20 hives).
+In commodity fields, honey bee visitation decreased from 6.4 visits/hr at the edge to 1.0 visits/hr at the centre of the field (400 m) (p$=$0.0002, Figure \ref{fig:hbeeDist_commodity}, apiary of 40 hives).
 % Visitation rates were higher in both years in Lethbridge (2014: 9.3 visits/hr, 2015: 7.1), but were higher in 2015 than 2014 at Grande Prairie (Z=2.3, p$=$0.02), rising from 5 visits/hr at the field edge in 2014 to 17 visits/hr in 2015.
 % (at a stocking level of 20 hives).
-Higher stocking rates increased honey bee visitation at the edge of the field from 14.5 visits/hr with an apiary of 20 hives to 22.7 visits/hr with an apiary of 40 hives (Z=5.3, p$<$0.0001), while unstocked field edges had an average of 1.8 visits/hr.
-Honey bee visitation was much higher overall in seed canola fields, but still decreased from 126 visits/hr at edge of field to 78 visits/hr at 100 m from the apiary (Z=-2.5, p$=$0.01). 
+Higher stocking rates increased honey bee visitation at the edge of the field from 3.9 visits/hr with an apiary of 20 hives, increasing to 6.4 visits/hr with 40 hives (Z=5.3, p$<$0.0001), while unstocked field edges had an average of 0.4 visits/hr.
+Honey bee visitation was much higher overall in seed canola fields, and decreased from 99.5 visits/hr at edge to 78.8 visits/hr at the centre of the field (Z=-2.5, p$=$0.01). 
 Honey bee visitation was also lower near leafcutter shelters (Z=3.9, p$=$0.001), dropping from 60 visits/hr at 10 m to 34 visits/hr at 2 m, likely due to competition with LCBs (Figure \ref{fig:hbeeDist_both}, \ref{fig:lbeeDist_both}).

### 2022-07-15 helperFunctions.R

@@ -243,26 +243,25 @@ getPreds <- function(mod,parList=NULL,offset=NULL,ZIpar=NULL,otherPars=NULL,q=c(
   
   if(class(mod)=='stanfit'){
     m <- extract(mod,par=names(parList))
-    m <- do.call('cbind',m)
-    
+    m <- do.call('cbind',m) #All draws
+    m_mean <- apply(m,1,mean) #Mean values
     if(!is.null(otherPars)){
       extras <- extract(mod,par=otherPars) %>% sapply(.,median)
     }
-    
   } else if(class(mod)=='data.frame' & !any(!names(mod)==dfNames)){ #If using a dataframe
     if(any(!names(parList) %in% mod$param)){
       stop(paste0('Parameters not found: ',paste(names(parList)[!names(parList) %in% mod$param],collapse=', ')))
     } 
     chooseRows <- mod$param %in% names(parList) 
-    m <- mod[chooseRows,c('mean','sd')] 
-    m <- do.call('cbind',lapply(1:nrow(m),function(i) rnorm(nrep,m$mean[i],m$sd[i])))
+    m <- mod[chooseRows,] 
+    m_mean <- setNames(m$mean,names(parList)) #Mean value
+    m <- do.call('cbind',lapply(1:nrow(m),function(i) runif(nrep,m$lwr[i],m$upr[i]))) #Generate draws b/w upr and lower
     colnames(m) <- names(parList)
     
     if(!is.null(otherPars)){
       extras <- mod$median[mod$param %in% otherPars] 
       names(extras) <- otherPars
     }
-    
   } else {
     warning('mod is not stanfit object or dataframe with correct column names')
     return(NA)
@@ -272,18 +271,23 @@ getPreds <- function(mod,parList=NULL,offset=NULL,ZIpar=NULL,otherPars=NULL,q=c(
   mmMat <- as.matrix(mm)
   
   if(!is.null(offset)){ #Add offset term if needed
-    m <- cbind(m,offset=rep(1,nrow(m)))
-    mmMat <- cbind(mmMat,offset=rep(1,nrow(mmMat)))
+    m <- cbind(m,offset=rep(1,nrow(m))) #Slope fixed at 1
+    m_mean <- c(m_mean,setNames(1,'offset'))
[…]

### 2022-07-15 partial plots.R

@@ -3,8 +3,8 @@
 # Load everything ---------------------------------------------------------
 library(tidyverse)
 theme_set(theme_bw())
-# setwd('~/Documents/canola_yield_project/Figures') #Galpern machine path
-setwd('~/Projects/UofC/canola_yield_project/Models') #Multivac path
+setwd('~/Documents/canola_yield_project/Figures') #Galpern machine path
+# setwd('~/Projects/UofC/canola_yield_project/Models') #Multivac path
 
 source('../helperFunctions.R') #Helper functions
 
@@ -23,42 +23,82 @@ seedData <- datalist; rm(datalist)
 avgCommData <- lapply(commData,summaryDat) 
 seedData$lbeeDistAll <- with(seedData,c(lbee_dist,lbee_dist_extra))
 seedData$hbeeDistAll <- with(seedData,c(hbee_dist,hbee_dist_extra))
+
 seedData$clogLbeeDist <- with(seedData,logCent(lbeeDistAll)) #Log-centered distances
 seedData$clogHbeeDist <- with(seedData,logCent(hbeeDistAll))
 avgSeedData <- lapply(seedData,summaryDat) 
+
+avgSeedData$logHbeeDistCent <- mean(log(with(seedData,c(hbee_dist,hbee_dist_extra)))) #Center
+avgSeedData$logLbeeDistCent <- mean(log(with(seedData,c(lbee_dist,lbee_dist_extra))))
 
 load('../Models/modSummaries_commodity.Rdata') #Commodity data models
 load('../Models/modSummaries_seed.Rdata') #Seed data models
 
 # Visitation plots --------------------------------------------------------
 
-#Hbee + Lbee visitation from edge of field/
+timeOffset <- 6 #Use 1 hr offset (1 = 10 mins, 6 = 1 hr)
+
+#Hbee stocking rate numbers
+with(avgCommData,
+           list('intHbeeVis'=1,
+                'slopeHbeeDistHbeeVis'=log(1),
+                'slopeNumHivesHbeeVis'= log(c(0,20,40)+1), 
+                'slopeFlDensHbeeVis' = avgCommData$flDens$mean)) %>% 
+  getPreds(modSummaries_commodity[[2]],parList = .,offset=timeOffset,
[…]

### 2022-07-18 partial plots.R
Worked on partial plots

@@ -3,8 +3,8 @@
 # Load everything ---------------------------------------------------------
 library(tidyverse)
 theme_set(theme_bw())
-setwd('~/Documents/canola_yield_project/Figures') #Galpern machine path
-# setwd('~/Projects/UofC/canola_yield_project/Models') #Multivac path
+# setwd('~/Documents/canola_yield_project/Figures') #Galpern machine path
+setwd('~/Projects/UofC/canola_yield_project/Models') #Multivac path
 
 source('../helperFunctions.R') #Helper functions
 
@@ -77,27 +77,30 @@ bind_rows(d1,d2) %>%
        fill='Field\nType',col='Field\nType')
 
 #Hbee and Lbee visitation from shelters
-  
+
 dists <- log(1:30)-avgSeedData$logLbeeDistCent #Distances
 
-d2 <- with(avgSeedData,
+d1 <- with(avgSeedData,
            list('intHbeeVis'=1,
                 'slopeFlDensHbeeVis' = flDens_obs$mean,
                 'slopeHbeeDistHbeeVis'=clogHbeeDist$mean,
                 'slopeLbeeDistHbeeVis'=dists,
                 'slopeCentHbeeVis'= 0
            )) %>% 
-  getPreds(modSummaries_seed[[2]],parList = .,offset=timeOffset,ZIpar = 'thetaHbeeVis',trans='exp',q=c(0.5,0.05,0.95))
+  getPreds(modSummaries_seed[[2]],parList = .,offset=timeOffset,ZIpar = 'thetaHbeeVis',
+           trans='exp',q=c(0.5,0.05,0.95))
 
-d2 <- with(avgSeedData,
-           list('intHbeeVis'=1,
-                'slopeFlDensHbeeVis' = flDens_obs$mean,
-                'slopeHbeeDistHbeeVis'=seq(min(clogHbeeDist),max(clogHbeeDist),length=20),
-                'slopeLbeeDistHbeeVis'=clogHbeeDist$mean,
-                'slopeCentHbeeVis'= 0
+debugonce(getPreds)
+
+(d2 <- with(avgSeedData,
+           list('intVisitLbeeVis'=1,
+                'slopeFlDensLbeeVis' = flDens_obs$mean,
+                'slopeHbeeDistLbeeVis'=clogHbeeDist$mean,
+                'slopeLbeeDistLbeeVis'=dists,
[…]

### 2022-07-18 Commodity field analysis/commodity canola pollination all.R
Added field size to commodity data

@@ -23,10 +23,11 @@ prestheme=theme(legend.position='right',
 theme_set(theme_classic()+prestheme) #Sets graph theme to B/Ws + prestheme
 rm(prestheme)
 
+#Load and organize everything -----------
+
 #Load from Rdata file
 load("C:\\Users\\Samuel\\Documents\\Projects\\UofC\\canola_yield_project\\Commodity field analysis\\commodityfieldDataAll.RData")
 
-# #Load and organize everything -----------
 # fields2014=read.csv("C:\\Users\\Samuel\\Documents\\Projects\\UofC\\csv files\\field info 2014.csv",stringsAsFactors=F,strip.white=T,na.strings = c("",'NA'))
 # survey2014=read.csv("C:\\Users\\Samuel\\Documents\\Projects\\UofC\\csv files\\survey data 2014.csv",stringsAsFactors=F,strip.white=T,na.strings = c("",'NA'))
 # nectar2014=read.csv("C:\\Users\\Samuel\\Documents\\Projects\\UofC\\csv files\\nectar calibration.csv",stringsAsFactors=F,strip.white=T,na.strings = c("",'NA'))
@@ -119,9 +120,12 @@ load("C:\\Users\\Samuel\\Documents\\Projects\\UofC\\canola_yield_project\\Commod
 # } #Appears to work
 # 
 # #General field data
-# fields2014=transmute(fields2014,Year=2014,Field=paste(Grower,X.), #Concatenates grower name and field number
+# fields2014=
+#   fields2014 %>% 
+#   transmute(Year=2014,Field=paste(Grower,X.), #Concatenates grower name and field number
 #        Area=as.factor(Area), #Converts Area to factor
 #        Lat=Deg.N+Min.N/60,Lon=-(Deg.W+Min.W/60), #Lat/Lon
+#        FieldSize_ha=Field.Size..ha., #Field size (ha)
 #        Variety=as.factor(Variety), #Converts Area to factor
 #        Irrigated=factor(Irrigated,labels=c('Unirrigated','Irrigated')),
 #        Irrigated=factor(Irrigated,levels=c('Irrigated','Unirrigated')),
@@ -132,16 +136,17 @@ load("C:\\Users\\Samuel\\Documents\\Projects\\UofC\\canola_yield_project\\Commod
 #        Surveyed=as.POSIXct(Surveyed,format='%b %d, %Y'),
 #        StartTime=as.POSIXct(paste(Surveyed,Start.Time),format='%Y-%m-%d %H:%M'),
[…]

### 2022-07-18 Commodity field analysis/commodity canola pollination all.R
Updated field sizes

@@ -121,7 +121,7 @@ load("C:\\Users\\Samuel\\Documents\\Projects\\UofC\\canola_yield_project\\Commod
 # 
 # #General field data
 # fields2014=
-#   fields2014 %>% 
+#   fields2014 %>%
 #   transmute(Year=2014,Field=paste(Grower,X.), #Concatenates grower name and field number
 #        Area=as.factor(Area), #Converts Area to factor
 #        Lat=Deg.N+Min.N/60,Lon=-(Deg.W+Min.W/60), #Lat/Lon

### 2022-07-18 Manuscript/main.tex
Worked on partial plots

@@
-\documentclass[12pt, draft]{article} % use larger type; default would be 10pt
+\documentclass[12pt]{article} % use larger type; default would be 10pt
 
@@
 
-%Visits/hr: In GP, 3.1 in 2014, 10.6 in 2015; in LB 5.9 in 2014, 4.5 in 2015
 \begin{figure}
     \centering
-    \includegraphics[width=0.9\textwidth,keepaspectratio=true]{slopeNumHivesDistVis.png}
-    \caption[Partial effect of distance away from field edge and stocking on honey bee visitation in commodity canola fields]{Partial effect of distance away from field edge and stocking on honey bee visitation in commodity canola fields.
-Solid lines represents median, and shaded areas represent 95\% CIs.
-Red line represents overall slope (controlling for region and year).}
+    \includegraphics[width=0.9\textwidth,keepaspectratio=true]{../Figures/allVisits.png}
+    \caption{Effect of distance from a) honey bee apiaries and b) leafcutter shelters on visitation rate.
+Visitation rates in commodity fields are shown at a stocking rate of 40 hives (black line), while stocking rates are at 160 hives in seed fields (yellow line).}
     \label{fig:hbeeDist_commodity}
-\end{figure}
-%PERHAPS INCLUDE FIGURE OF AREA/YEAR EFFECTS IN THE SUPPLEMENTAL?
-
-\begin{figure}
-    \centering
-    \includegraphics[width=0.9\textwidth,keepaspectratio=true]{slopeHbeeDist_both.png}
-    \caption[Partial effect of distance from field edge on bee visitation in seed canola fields]{Partial effect of distance from field edge on honey bee and leafcutter bee visitation in seed canola fields.
-Solid lines represent medians, and shaded areas represent 95\% CIs.}
-    \label{fig:hbeeDist_both}
-\end{figure}
-
-\begin{figure}
-    \centering
-    \includegraphics[width=0.9\textwidth,keepaspectratio=true]{slopeLbeeDistBothBees.png}
-    \caption[Partial effect of distance from leafcutter shelter on bee visitation in seed canola fields]{Partial effect of distance from leafcutter shelter on honey bee and leafcutter bee visitation in seed canola fields.
-Solid lines represent medians, and shaded areas represent 95\% CIs.}
-    \label{fig:lbeeDist_both}
-\end{figure} %SH: WOULD BE COOL TO HAVE A ``SUM OF BOTH BEES" LINE AS WELL - perhaps in the manusript? may require a separate model of both bees, or possibly just adding model results together
-
-\begin{figure}
-    \centering
-    \includegraphics[width=0.9\textwidth,keepaspectratio=true]{slopeEdgeCent_both.png}
-    \caption[Partial effect of bay position on honey bee and leafcutter bee visitation]{Partial effect of bay position (edge or centre of female bay) on honey bee and leafcutter bee visitation.
-Coloured points represents median value, and vertical bars represent 95\% CIs.}
-    \label{fig:edgeCentVis_both}
 \end{figure}

### 2022-07-18 partial plots.R

@@ -2,9 +2,10 @@
 
 # Load everything ---------------------------------------------------------
 library(tidyverse)
+library(ggpubr)
 theme_set(theme_bw())
-# setwd('~/Documents/canola_yield_project/Figures') #Galpern machine path
-setwd('~/Projects/UofC/canola_yield_project/Models') #Multivac path
+setwd('~/Documents/canola_yield_project/Figures') #Galpern machine path
+# setwd('~/Projects/UofC/canola_yield_project/Models') #Multivac path
 
 source('../helperFunctions.R') #Helper functions
 
@@ -20,12 +21,21 @@ load('../Models/datalist_seed.Rdata') #Seed data
 seedData <- datalist; rm(datalist)
 
 #Summary stats (min,median,max) to use for plots
-avgCommData <- lapply(commData,summaryDat) 
-seedData$lbeeDistAll <- with(seedData,c(lbee_dist,lbee_dist_extra))
-seedData$hbeeDistAll <- with(seedData,c(hbee_dist,hbee_dist_extra))
 
+#Commodity data
+commData$logHbeeVis <- log((commData$hbeeVis/commData$totalTime)+1) #Visitation rate
+commData$logHbeeDist <- log(commData$dist) #Distance
+commData$clogHbeeDist <- commData$logHbeeDist-mean(commData$logHbeeDist)
+avgCommData <- lapply(commData,summaryDat) 
+
+#Seed data
+seedData$lbeeDistAll <- with(seedData,c(lbee_dist,lbee_dist_extra)) #Distances
+seedData$hbeeDistAll <- with(seedData,c(hbee_dist,hbee_dist_extra))
 seedData$clogLbeeDist <- with(seedData,logCent(lbeeDistAll)) #Log-centered distances
 seedData$clogHbeeDist <- with(seedData,logCent(hbeeDistAll))
+seedData$logLbeeVis <- log((seedData$lbeeVis/seedData$totalTime)+1) #Visitation rates
+seedData$logHbeeVis <- log((seedData$hbeeVis/seedData$totalTime)+1) 
+
 avgSeedData <- lapply(seedData,summaryDat) 
 
 avgSeedData$logHbeeDistCent <- mean(log(with(seedData,c(hbee_dist,hbee_dist_extra)))) #Center
[…]

### 2022-07-18 yield path analysis commodity.R

@@ -47,7 +47,8 @@ load('./Models/datalist_commodity.Rdata')
 #   numHives=NumHives, #Number of hives/field
 #   is2015=Year==2015, #Is year 2015?
 #   isGP=Area!='Lethbridge', #Is area Grand Prairie?
-#   isIrrigated=Irrigated=='Irrigated' #Is field irrigated?
+#   isIrrigated=Irrigated=='Irrigated', #Is field irrigated?
+#   fieldSize=FieldSize_ha #Field size in hectares
 # ))
 # 
 # datalistPlot <- with(arrange(surveyAllComm,factor(paste(Year,Field,Distance))),list( #Plot-level measurements
@@ -64,8 +65,8 @@ load('./Models/datalist_commodity.Rdata')
 #   plDens_obs=log(PlDens[!is.na(PlDens)]), #(log) Planting density
 #   obsPlDens_ind=which(!is.na(PlDens)), #Index for observed
 #   missPlDens_ind=which(is.na(PlDens)), #Index for missing
-# 
-#   flDens=sqrt(FlDens) #(sqrt) Flower density
+#   flDens=sqrt(FlDens)-mean(sqrt(FlDens)), #(sqrt) Flower density - centered
+#   flDensMean=mean(sqrt(FlDens))
 # ))
 # 
 # datalistFlw <- flowersAllComm %>%
@@ -163,7 +164,7 @@ modList <- vector(mode = 'list',length = length(modFiles))
 names(modList) <- gsub('(commodity.*[0-9]{2}|\\.stan)','',modFiles)
 
 modList[1] <- stan(file=modFiles[1],data=datalist,iter=2000,chains=4,control=list(adapt_delta=0.8),init=0) #OK - Plant density, Plant size, Flower Density
-modList[2] <- stan(file=modFiles[2],data=datalist,iter=2000,chains=4,control=list(adapt_delta=0.8),init=0) #OK - Visitation
+modList[2] <- stan(file=modFiles[2],data=datalist,iter=2000,chains=4,control=list(adapt_delta=0.85),init=0) #OK - Visitation
 modList[3] <- stan(file=modFiles[3],data=datalist,iter=2000,chains=4,control=list(adapt_delta=0.8),init=0) #OK - Pollen
 modList[4] <- stan(file=modFiles[4],data=datalist,iter=2000,chains=4,control=list(adapt_delta=0.8),init=0) #OK - Flower count
[…]

### 2022-07-18 yield path analysis seed.R

@@ -238,16 +238,19 @@ load('./datalist_seed.Rdata')
 # #   podIndex=match(plantList,datalistPlant$plantList)
 # # ))
 # datalistPlant$plantList <- datalistPlot$plotList <-  NULL
-# 
 # datalist <- c(datalistField,datalistPlot,datalistFlw,datalistPlant)
+# 
+# flDensMean <- mean(with(datalist,c(flDens_obs,flDens_obs_extra))) #Center flower density
+# datalist$flDens_obs <- datalist$flDens_obs-flDensMean
+# datalist$flDens_obs_extra <- datalist$flDens_obs_extra-flDensMean
+# datalist$flDensMean <- flDensMean
 # 
 # if(any(sapply(datalist,function(x) sum(is.na(x)))!=0)){ beep(1); print("NAs found in datalist")}
 # 
-# rm(datalistField,datalistPlot,datalistFlw,datalistPlant,rileyFields,samFields) #Cleanup
+# rm(datalistField,datalistPlot,datalistFlw,datalistPlant,rileyFields,samFields,flDensMean) #Cleanup
 # str(datalist)
 # 
 # save(datalist,file = './datalist_seed.Rdata')
-
 
 # Run models ----------------------------
 

### 2022-07-19 partial plots.R
Worked on partial plots

@@ -4,8 +4,8 @@
 library(tidyverse)
 library(ggpubr)
 theme_set(theme_bw())
-setwd('~/Documents/canola_yield_project/Figures') #Galpern machine path
-# setwd('~/Projects/UofC/canola_yield_project/Models') #Multivac path
+# setwd('~/Documents/canola_yield_project/Figures') #Galpern machine path
+setwd('~/Projects/UofC/canola_yield_project/Models') #Multivac path
 
 source('../helperFunctions.R') #Helper functions
 
@@ -186,13 +186,41 @@ ggsave('allVisits.png',p,bg='white',width = 12,height=4)
 
 # Pollen plots ------------------------------------------------------------
 
-hbeeVisComm <- log((0:36)+1)
+#median, mean, max:
+#0,1.72,36 max for commodity, 4,22.6,215 for seed
+hbeeVisComm <- log(seq(0,36,20)+1)
+hbeeVisSeed <- log((seq(0,215,20))+1)
 
-with(avgCommData, #Hbee visitation in commodity
+d1 <- with(avgCommData, #Hbee visitation effect
      list('intPollen'=1,
           'slopeHbeeVisPollen'=hbeeVisComm,
           'slopeHbeeDistPollen'= 0
           )) %>% 
-  getPreds(modSummaries_commodity[[3]],parList = .,offset=timeOffset,trans='exp',q=c(0.5,0.05,0.95)) %>% 
+  getPreds(modSummaries_commodity[[3]],parList = .,trans='exp',q=c(0.5,0.05,0.95)) %>% 
   transmute(vis=0:36,mean,med,lwr,upr)
+
+# dists <- sort(unique(commData$clogHbeeDist))
+# d2 <- with(avgCommData, #Hbee distance effect
+#            list('intPollen'=1,
+#                 'slopeHbeeVisPollen'=mean(log((commData$hbeeVis/commData$totalTime)+1)),
+#                 'slopeHbeeDistPollen'= dists
+#            )) %>% 
+#   getPreds(modSummaries_commodity[[3]],parList = .,trans='exp',q=c(0.5,0.05,0.95)) %>% 
+#   transmute(dist=sort(unique(commData$dist)),mean,med,lwr,upr)
+# 
+# d2 %>% ggplot(aes(x=dist))+
+#   geom_ribbon(aes(ymax=upr,ymin=lwr),alpha=0.3)+
+#   geom_line(aes(y=med))+
+#   labs(x='Dist',y='Pollen')
[…]

### 2022-07-19 Manuscript/main.tex
Worked on partial and SEM plots

@@
 Honey bee visitation decreased with distance away from the apiary, in both commodity and seed canola fields.
-In commodity fields, honey bee visitation decreased from 6.4 visits/hr at the edge to 1.0 visits/hr at the centre of the field (400 m) (p$=$0.0002, Figure \ref{fig:hbeeDist_commodity}, apiary of 40 hives).
+In commodity fields, honey bee visitation decreased from 6.4 visits/hr at the edge to 1.0 visits/hr at the centre of the field (400 m) (p$=$0.0002, Figure \ref{fig:allVis}, apiary of 40 hives).
 % Visitation rates were higher in both years in Lethbridge (2014: 9.3 visits/hr, 2015: 7.1), but were higher in 2015 than 2014 at Grande Prairie (Z=2.3, p$=$0.02), rising from 5 visits/hr at the field edge in 2014 to 17 visits/hr in 2015.
@@
     \includegraphics[width=0.9\textwidth,keepaspectratio=true]{../Figures/allVisits.png}
-    \caption{Effect of distance from a) honey bee apiaries and b) leafcutter shelters on visitation rate.
-Visitation rates in commodity fields are shown at a stocking rate of 40 hives (black line), while stocking rates are at 160 hives in seed fields (yellow line).}
-    \label{fig:hbeeDist_commodity}
+    \caption{Effect of distance from a) honey bee apiaries, b) leafcutter shelters, and c) female bay position on visitation rates.
+Commodity fields are shown at a stocking rate of 40 hives (black line), while stocking rates are at 160 hives in seed fields (yellow line).}
+    \label{fig:allVis}
 \end{figure}
@@
 LCB visitation increased pollen deposition in seed canola fields, but honey bees did not increase pollen deposition in either commodity or seed canola fields.
-Pollen deposition on stigmas was high in commodity canola (mean: 293 grains per stigma, SD: 385, range: 0--3981), but honey bee visitation had no impact on this (p$=$0.77, Figure \ref{fig:hbeeVisPol}).
+Pollen deposition on stigmas was high in commodity canola (mean: 293 grains per stigma, SD: 385, range: 0--3981), but honey bee visitation had no impact on this (p$=$0.77, Figure \ref{fig:allPollen}).
 Pollen deposition slighly declined with distance from the edge of the field, but this relationship was weak (p$=$0.07) and only amounted to a 6\% average decrease (290 grains per stigma at the field edge vs.
@@
     \centering
-    \includegraphics[width=0.9\textwidth,keepaspectratio=true]{slopeHbeeVisPol.png}
-    \caption[Partial effect of honey bee visitation on pollen deposition in commodity canola]{Partial effect of honey bee visitation on pollen deposition in commodity canola.
-Solid line represents median, and shaded areas represent 95\% CIs.}
-    \label{fig:hbeeVisPol}
-\end{figure}
-
-\begin{figure}
-    \centering
-    \includegraphics[width=0.9\textwidth,keepaspectratio=true]{slopeVisPol_both.png}
-    \caption[Partial effects of honey bee and leafcutter bee visitation on pollen deposition in seed canola]{Partial effects of honey bee and leafcutter bee visitation on pollen deposition in seed canola.
-Solid lines represent medians, and shaded areas represent 95\% CIs.}
-    \label{fig:visPol_both}
-\end{figure}
-
-\begin{figure} 
-    \centering
-    \includegraphics[width=0.9\textwidth,keepaspectratio=true]{slopeDistCentPol.png}
-    \caption[Partial effect of distance from field edge and bay position on pollen deposition in seed canola]{Partial effect of distance from field edge and bay position on pollen deposition in seed canola.
-Coloured points represents median, and shaded areas represent 95\% CIs.}
-    \label{fig:distCentPol}
+    \includegraphics[width=0.9\textwidth,keepaspectratio=true]{allPollen.png}
+    \caption{Effect of a) visitation rate, b) distance from apiary (HB) or shelter (LCB), and c) female bay position on pollen deposition.}
+    \label{fig:allPollen}
 \end{figure}
@@
 
-\subsection{Prediction 4: Pollinated plants produce more seeds}
-
-Pollen deposition increased fruit production and seed production in seed canola, but not in commodity canola.
-Pollen deposition had no effect on pod set (p=0.12), seeds per pod (p=0.94) or seed size (p=0.56) in commodity canola, and there was also no direct effect of honey bee visitation on pod set (p=0.38), seeds per pod (p=0.55), or seed size (p=0.34).
-Seed canola, in contrast, was highly dependent on pollen deposition.
-Pollen deposition increased pod set (Z=3.1, p$=$0.002), and seeds per pod (Z=2.3, p$=$0.02), but had no direct effect on seed size (p$=$0.35).
-Pod set also decreased with three types of distance: distance into the field (Z=-5.3, p$<$0.0001), distance from leafcutter shelters (Z=-3.2, p$=$0.002), and distance from the edge of the female bay (Z=-4.0, p$=$0.0001).
-Seeds per pod decreased in the centre of the female bay (Z=-4.6, p$<$0.0001), and was higher in plants with high pod set (Z=6.0, p$<$0.0001).
+% \subsection{Prediction 4: Pollinated plants produce more seeds}
+% 
+% Pollen deposition increased fruit production and seed production in seed canola, but not in commodity canola.
+% Pollen deposition had no effect on pod set (p=0.12), seeds per pod (p=0.94) or seed size (p=0.56) in commodity canola, and there was also no direct effect of honey bee visitation on pod set (p=0.38), seeds per pod (p=0.55), or seed size (p=0.34).
+% Seed canola, in contrast, was highly dependent on pollen deposition.
+% Pollen deposition increased pod set (Z=3.1, p$=$0.002), and seeds per pod (Z=2.3, p$=$0.02), but had no direct effect on seed size (p$=$0.35).
+% Pod set also decreased with three types of distance: distance into the field (Z=-5.3, p$<$0.0001), distance from leafcutter shelters (Z=-3.2, p$=$0.002), and distance from the edge of the female bay (Z=-4.0, p$=$0.0001).
+% Seeds per pod decreased in the centre of the female bay (Z=-4.6, p$<$0.0001), and was higher in plants with high pod set (Z=6.0, p$<$0.0001).
 
@@
 Pod set in commodity canola was positively affected by plant size, but not by pollen deposition or honey bee visitation.
-Both pod production and seeds per pod can increase with extra pollination \citep{jauker2008,sabbahi2005,sabbahi2006,duran2010}, so this lack of effect may be due to a high overall level of pollen deposition (Figure \ref{fig:hbeeVisPol}), even in fields without honey bees.
+Both pod production and seeds per pod can increase with extra pollination \citep{jauker2008,sabbahi2005,sabbahi2006,duran2010}, so this lack of effect may be due to a high overall level of pollen deposition (Figure \ref{fig:allPollen}), even in fields without honey bees.
 There was no effect of honey bee visitation on pod set, seeds per pod, or seed size, indicating that visitation did not seem to cause either \textit{a)} a greater quantity of pollen (see above) or \textit{b)} higher quality (outcrossed) pollen.

### 2022-07-19 partial plots.R

@@ -4,8 +4,8 @@
 library(tidyverse)
 library(ggpubr)
 theme_set(theme_bw())
-# setwd('~/Documents/canola_yield_project/Figures') #Galpern machine path
-setwd('~/Projects/UofC/canola_yield_project/Models') #Multivac path
+setwd('~/Documents/canola_yield_project/Figures') #Galpern machine path
+# setwd('~/Projects/UofC/canola_yield_project/Models') #Multivac path
 
 source('../helperFunctions.R') #Helper functions
 
@@ -186,41 +186,122 @@ ggsave('allVisits.png',p,bg='white',width = 12,height=4)
 
 # Pollen plots ------------------------------------------------------------
 
+#Visitation effects
+
 #median, mean, max:
 #0,1.72,36 max for commodity, 4,22.6,215 for seed
-hbeeVisComm <- log(seq(0,36,20)+1)
-hbeeVisSeed <- log((seq(0,215,20))+1)
+hbeeVisComm <- log(seq(0,max(with(commData,hbeeVis/totalTime)),length=30)+1)
+hbeeVisSeed <- log((seq(0,max(with(seedData,hbeeVis/totalTime)),length=100))+1)
+lbeeVisSeed <- log((seq(0,max(with(seedData,lbeeVis/totalTime)),length=100))+1)
+lab <- c('HB Seed','LCB Seed','HB Commodity') 
+labCols <- c('darkorange','darkgreen','black')
 
-d1 <- with(avgCommData, #Hbee visitation effect
+d1 <- with(avgCommData, #Hbee visitation effect - commodity
      list('intPollen'=1,
           'slopeHbeeVisPollen'=hbeeVisComm,
           'slopeHbeeDistPollen'= 0
           )) %>% 
   getPreds(modSummaries_commodity[[3]],parList = .,trans='exp',q=c(0.5,0.05,0.95)) %>% 
-  transmute(vis=0:36,mean,med,lwr,upr)
+  transmute(vis=exp(hbeeVisComm)-1,mean,med,lwr,upr)
 
-# dists <- sort(unique(commData$clogHbeeDist))
-# d2 <- with(avgCommData, #Hbee distance effect
-#            list('intPollen'=1,
-#                 'slopeHbeeVisPollen'=mean(log((commData$hbeeVis/commData$totalTime)+1)),
[…]

### 2022-07-19 sem plots.R

@@ -1,0 +1,201 @@
+# MAKES SEM PLOTS FOR COMMODITY AND SEED MODELS
+
+# Load everything ---------------------------------------------------------
+
+library(tidyverse)
+library(beepr)
+library(xtable)
+library(ggdag)
+library(ggpubr)
+
+#Big-text theme, no grid lines (used for Bayer 2016 presentation)
+prestheme <- theme(legend.position='right',
+                legend.text=element_text(size=15),
+                axis.text=element_text(size=15),
+                axis.title=element_text(size=20),
+                title=element_text(size=20),
+                panel.grid.major=element_blank(),panel.grid.minor=element_blank(),
+                panel.border=element_rect(size=1,colour='black'),
+                strip.text=element_text(size=15))
+theme_set(theme_bw()+prestheme) #Sets graph theme to B/Ws + prestheme
+rm(prestheme)
+
+# setwd('~/Projects/UofC/canola_yield_project') #Multivac path
+setwd('~/Documents/canola_yield_project') #Galpern machine path
+
+source('helperFunctions.R')
+
+load('./Models/datalist_commodity.Rdata') #Commodity data
+commData <- datalist
+load('./Models/datalist_seed.Rdata') #Seed data
+seedData <- datalist; rm(datalist)
+
+#Model summaries
+load('./Models/modSummaries_commodity.Rdata') 
+load('./Models/modSummaries_seed.Rdata') 
+
+# Commodity SEM plot ----------------------------------------------------------
+
+nodeCoords <- data.frame(name=c('numHives','hbeeDist','hbeeVis','pollen',
+                                'plSize','plDens','flDens',
+                                'flwCount','flwSurv','seedCount','seedWeight'),
+                         labs=c('Number\nof Hives','Distance','Honey bee\nVisits','Pollen\nCount',
+                                'Plant\nSize','Plant\nDensity','Flower\nDensity',
+                                'Flowers\nper Plant','Pods\nper Plant','Seeds\nper Pod','Seed\nSize'),
+                         x=c(0,1,0.5,0.5,
[…]

### 2022-07-19 yield path analysis commodity.R

@@ -240,94 +240,6 @@ compareRE(modList[[8]],'ranEffYield_plot',1,0.3) #Intercepts
 compareRE(modList[[8]],'ranEffYield_plot',2,0.3) #Slopes - right skew
 
 
-# Path diagram ------------------------------------------------------------
-
-library(ggdag)
-nodeCoords <- data.frame(name=c('numHives','hbeeDist','hbeeVis','pollen',
-                                'plSize','plDens','flDens',
-                                'flwCount','flwSurv','seedCount','seedWeight'),
-                         labs=c('Number\nof Hives','Distance','Honey bee\nVisits','Pollen\nCount',
-                                'Plant\nSize','Plant\nDensity','Flower\nDensity',
-                                'Flowers\nper Plant','Pods\nper Plant','Seeds\nper Pod','Seed\nSize'),
-                         x=c(0,1,0.5,0.5,
-                             2.5,0,1,
-                             3.5,4,2.5,3.5),
-                         y=c(4,4,3,2,
-                             0,1,1,
-                             0,1,3,2))
-
-
-#Specify model
-commDAG <- dagify(plDens ~ hbeeDist,
-                  plSize ~ plDens + hbeeDist,
-                  flDens ~ plSize + hbeeDist + plDens,
-                  hbeeVis ~ hbeeDist + numHives + flDens,
-                  pollen ~ hbeeVis + hbeeDist,
-                  flwCount ~ plSize + flwSurv,
-                  flwSurv ~ hbeeVis + plSize + pollen,
-                  seedCount ~ hbeeVis + pollen + plSize + flwSurv + flwCount,
-                  seedWeight ~ hbeeVis + pollen + plSize + seedCount + plDens + hbeeDist + flwSurv + flwCount + flDens,
-                  coords= list(x = setNames(nodeCoords$x,nodeCoords$name),
-                               y = setNames(nodeCoords$y,nodeCoords$name)),
-                  labels=setNames(nodeCoords$labs,nodeCoords$name)
-)
-
-# plot(commDAG)
-
-#Get path coefficients (Z-scores) and match to edges
-
[…]

### 2022-07-19 yield path analysis seed.R

@@ -354,61 +354,6 @@ PPplots(modList[[8]],datalist$seedMass_obs,c('predSeedMass','seedMass_resid','pr
         index=datalist$obsSeedMass_ind,'Seed Mass')
 PPplots(modList[[9]],log(datalist$yield),c('predYield','yield_resid','predYield_resid'),'Seed mass per plant')
 
-# Path diagram ------------------------------------------------------------
-
-load('modSummaries_seed.Rdata')
-
-pathCoefs <- modSummaries_seed %>% #Get path coefficients
-  bind_rows(.id='to') %>% 
-  transmute(to,name=param,Z,pval) %>% 
-  filter(to!='yield',!grepl('(int|sigma|lambda|Phi|phi|rho|nu|theta)',name)) %>% 
-  mutate(to=case_when(
-    to=='flDens' & grepl('PlDens$',name) ~ 'plDens',
-    to=='flDens' & grepl('PlSize$',name) ~ 'plSize',
-    TRUE ~ gsub('avg','seed',to)
-  )) %>% 
-  mutate(name=gsub('slope','',name)) %>% 
-  filter(mapply(grepl,capFirst(to),name)) %>% 
-  mutate(name=mapply(gsub,capFirst(to),'',name)) %>% 
-  mutate(name=capFirst(name,TRUE)) 
-
-tidySeedDAG <- seedDAG %>% #Create tidy dagitty set
-  tidy_dagitty() 
-
-# ggplot(tidySeedDAG,aes(x = x, y = y, xend = xend, yend = yend))+
-#   geom_dag_edges() +
-#   geom_dag_text(col='black') +
-#   theme_dag_blank()
-
-tidySeedDAG$data %>% data.frame
-pathCoefs %>% data.frame
-
-tidySeedDAG$data <- tidySeedDAG$data %>% #Match coefs to dagitty set
-  rename(xstart=x,ystart=y) %>% 
-  full_join(x=pathCoefs,y=.,by=c('to','name')) %>% 
-  filter(!is.na(to)) %>% 
-  mutate(isNeg=Z<0,isSig=pval<0.05) %>% 
-  mutate(L=sqrt(abs(Z)),1) %>% 
-  mutate(edgeLab=ifelse(isSig,as.character(sign(Z)*round(L,1)),'')) %>% 
-  mutate(C=ifelse(isNeg,'red','black')) %>% 
-  mutate(A=ifelse(isSig,1,0.1))
-
[…]

### 2022-07-19 Manuscript/main.tex
Worked on partial plots

@@
 We assessed the underlying probability distribution functions of each model using posterior predictive checks \citep{gelman2013}, and found that the probability distributions were properly specified (p$\sim$0.5).
+p-values listed below (also in Tables S3 and S4) are \textit{posterior} p-values, representing the proportion of the posterior distribution that overlapped zero, with Z-scores (mean/standard deviation of posterior) showing the effect size.
 % This means that while the average seed counts (per plant) were unbiased, the variance within a plant was not. 
 % However, the negative binomial distribution had the closest posterior predictive checks of any other distribution. 
-% p-values listed below (also in Tables S3 and S4) are \textit{posterior} p-values, representing the proportion of the posterior distribution that overlapped zero, with Z-scores (mean/standard deviation of posterior) showing the effect size.
 % Predictions from models are median values of the posterior, representing the median prediction, while intervals displayed in figures are credible intervals (CIs), representing 95\% of the samples drawn from the posterior distribution (analogous to confidence intervals, see \citealt{gelman2013}).
@@
 
-% %This could probably be reduced to a blurb
-% Plant size and pollen deposition were the main drivers of yield in seed canola, while plant size was the main driver of yield in commodity canola.
-% Distance from the field edge had a negative effect on honey bee visitation in both commodity and seed canola (Z=-3.7, -2.5, respectively), and unexpectedly, had a negative effect on leafcutter bee visitation (Z= -4.4), showing that overall visitation decreases with distance into the field.
-% The path from leafcutter bee visitation to pollen deposition was strong in seed canola (Z=3.2), but there was no path from honey bee visitation to pollen deposition in either crop type.
-% Pollen deposition increased pod set (Z=3.1) and seeds per pod (Z=2.3) in seed canola, but was not present in commodity canola, showing that yield in seed canola, but not commodity canola, is strongly dependent on pollination.
-% %The path from seeds per pod to weight per seed was negative in seed canola (Z=-15.0) but positive in commodity canola (Z=6.1) 
-% Both crop types had strong negative paths from flower survival to flowers per plant (commodity Z=-12.5, seed Z=-12.1), indicating that high flower survival suppressed future flower production.
-% Commodity canola had a similar weight per seed, regardless of the plant size, but in seed canola, plant size had a strong influence on seeds per pod (Z=5.6) and weight per seed (4.6).
-% Finally, in both crop types, the paths leading from plant size were the dominant signal influencing pod set (commodity Z=5.8; seed Z=19.9), but the path from pollen deposition to pod set was only present in seed canola, showing that plant resources matter strongly for both crop types, but that increased pollen deposition only benefits seed canola.
-% 
-% The results of the underlying components of each pSEM are shown in Figures \ref{fig:commoditySEM} and \ref{fig:seedSEM}:
-% 
-% \begin{table}
-% \centering
-% \caption{Summary of main measured variables. Vegetative mass refers to the non-seed plant mass.}
-% \begin{tabular}{r|llllll|llllll}
-%                                        & \multicolumn{6}{l|}{Commodity Fields}           & \multicolumn{6}{l}{Seed Fields}                    \\
-% Parameter                              & Min  & Median & Mean   & Max   & SD     & N    & Min    & Median & Mean   & Max    & SD     & N     \\ \hline
-% Honey bee visitation (per min)      & 0    & 0      & 0.17   & 3.64  & 0.48   & 271  & 0      & 2      & 14.15  & 215    & 25.13  & 665   \\
-% Leafcutter bee visitation (per min) & -    & -      & -      & -     & -      & -    & 0      & 2      & 13.93  & 212    & 25.49  & 665   \\
-% Pollen (\# per stigma)                 & 0    & 155    & 293.32 & 3891  & 385.04 & 1355 & 0      & 7      & 21.76  & 578    & 42.53  & 1080  \\
-% Flowers per plant                      & 13   & 157    & 196.05 & 1094  & 150.87 & 789  & 26     & 362.50 & 461.33 & 2712   & 326.59 & 600   \\
-% Pods per plant                         & 5    & 112    & 143.17 & 892   & 114.57 & 789  & 10     & 244.50 & 299.41 & 1410   & 207.68 & 600   \\
-% Seeds per pod                          & 4.6  & 23.6   & 22.95  & 35.4  & 4.97   & 789  & 1.8    & 16.6   & 16.40  & 30.60  & 5.52   & 600   \\
-% Weight per 1000 seeds (g)              & 0.39 & 2.72   & 2.74   & 5.35  & 0.8    & 789  & 1.04   & 3.42   & 3.43   & 5.59   & 0.88   & 600  \\
-% Total vegetative mass (g)                    & 0.77 & 14.29  & 18.19  & 110.2 & 14.41  & 789  & 1.1849 & 25.20  & 30.32  & 144.32 & 21.16  & 600   \\
-% Total seed mass (g)                          & 0.01 & 5.46   & 6.87   & 47.9  & 5.97   & 789  & 0.02   & 7.54   & 9.50   & 60.77  & 7.90   & 600   
-% \end{tabular}
-% \end{table}
+\subsection{Overall path analysis}
+
+Plant size and pollen deposition were the main drivers of seed production in seed canola, while plant size was the main driver in commodity canola (see Figure \ref{fig:allSEM} for paths and effect sizes).
+HB visitation decreased with distance from the edge of the field in both commodity and seed canola; unexpectedly, LCB visitation also decreased with distance from the edge of the field in seed fields.
+LCB visitation strongly increased pollen deposition was strong in seed canola, but there was no strong effect of HB visitation in either crop type.
+Both crop types had strong negative paths from pods per plant to flowers per plant, indicating that high flower survival suppressed future flower production.
+Plant size increased the number of seeds per pod in both crop types, and also increased seed size in seed canola plants.
+Finally, pollen deposition increased pod set and seeds per pod in seed canola, but did not affect seed or pod production in commodity canola, showing that plant resources matter strongly for both crops, but that increased pollen only benefits seed canola crops.
+
+\begin{figure}
+    \centering
+    \includegraphics[width=0.9\textwidth,keepaspectratio=true]{../Figures/allSEM.png}
+    \caption{Results of path analysis in commodity and seed fields.
+The width of each arrow is proportional to the effect size of each component path (number also displayed).
+Transparent arrows show path coefficients whose 95 posterior intervals overlapped zero.}
+    \label{fig:allSEM}
+\end{figure}
 

### 2022-07-19 helperFunctions.R

@@ -6,7 +6,7 @@ logit <- function(x){
 }
 invLogit <- function(x){ 
   i <- exp(x)/(1+exp(x)) 
-  i[is.nan(i)] <- 1 #If x is large enough, becomes Inf/Inf = NaN, but Lim(invLogit) x->Inf = 1
+  # i[is.nan(i)] <- 1 #If x is large enough, becomes Inf/Inf = NaN, but Lim(invLogit) x->Inf = 1
   return(i)
 }
 
@@ -236,7 +236,7 @@ g2bushels <- function(x){
 # q = quantiles to predict at
 # nrep = number of replicates of parameters to generate (for data.frame parameters)
 
-getPreds <- function(mod,parList=NULL,offset=NULL,ZIpar=NULL,otherPars=NULL,q=c(0.5,0.025,0.975),nrep=4000,trans=NULL){
+getPreds <- function(mod,parList=NULL,offset=NULL,ZIpar=NULL,otherPars=NULL,q=c(0.5,0.025,0.975),nrep=4000,trans=NULL,expandGrid=TRUE){
   if(is.null(parList)) stop('Specify parameters')
   dfNames <- c("param","mean","sd","Z","median",
                "lwr","upr","pval","n_eff","Rhat")
@@ -267,7 +267,12 @@ getPreds <- function(mod,parList=NULL,offset=NULL,ZIpar=NULL,otherPars=NULL,q=c(
     return(NA)
   }
   
-  mm <- expand.grid(parList) #Model matrix
+  if(expandGrid){ 
+    mm <- expand.grid(parList) #Create model matrix using expand.grid
+  } else {
+    if(length(unique(sapply(dat,length)))>2) stop('Input parameters have different lengths. Cannot coerce to dataframe')
+    mm <- as.data.frame(parList)
+  }
   mmMat <- as.matrix(mm)
   
   if(!is.null(offset)){ #Add offset term if needed

### 2022-07-19 partial plots.R

@@ -25,7 +25,13 @@ seedData <- datalist; rm(datalist)
 #Commodity data
 commData$logHbeeVis <- log((commData$hbeeVis/commData$totalTime)+1) #Visitation rate
 commData$logHbeeDist <- log(commData$dist) #Distance
-commData$clogHbeeDist <- commData$logHbeeDist-mean(commData$logHbeeDist)
+commData$clogHbeeDist <- commData$logHbeeDist-mean(commData$logHbeeDist) #Centered log distance
+commData$logPodCount <- log(commData$podCount) #Log pod count
+commData$logFlwCount <- log(commData$flwCount) #Log pod count
+commData$propFlwSurv <- commData$podCount/commData$flwCount #Flower survival
+commData$propFlwSurv[commData$propFlwSurv==1] <- 0.99 #Deal with 100% success rates
+commData$logitFlwSurv <- logit(commData$propFlwSurv)
+commData$clogitFlwSurv <- commData$logitFlwSurv-mean(commData$logitFlwSurv) #Centered logit
 avgCommData <- lapply(commData,summaryDat) 
 
 #Seed data
@@ -35,6 +41,7 @@ seedData$clogLbeeDist <- with(seedData,logCent(lbeeDistAll)) #Log-centered dista
 seedData$clogHbeeDist <- with(seedData,logCent(hbeeDistAll))
 seedData$logLbeeVis <- log((seedData$lbeeVis/seedData$totalTime)+1) #Visitation rates
 seedData$logHbeeVis <- log((seedData$hbeeVis/seedData$totalTime)+1) 
+seedData$logFlwCount <- log(seedData$flwCount) #Log flw count
 
 avgSeedData <- lapply(seedData,summaryDat) 
 
@@ -304,4 +311,283 @@ p3 <- with(avgSeedData, #Bay position
 
 ggsave('allPollen.png',p,bg='white',width = 12,height=4)
 
+# Seed production - pollen ---------------------------------------------------
 
+#pollenPlot means - Taken from model output
+commPollenPlot <- seq(-1.2644033,0.9869057,length=20) 
+modSummaries_commodity[[3]]$mean[1] #Intercept
+seedPollenPlot <- seq(-3.573654,2.364599,length=20) 
+modSummaries_seed[[4]]$mean[1] #Intercept
+
[…]

### 2022-07-19 yield path analysis seed.R

@@ -272,6 +272,8 @@ modList[8] <- stan(file=modFiles[8],data=datalist,iter=2000,chains=4,init=0) #We
 modList[9] <- stan(file=modFiles[9],data=datalist,iter=3000,chains=4,init=0) #Yield
 beepr::beep(1)
 
+apply(extract(modList[[4]],pars='pollenMu_plot')[[1]],2,mean) %>% range
+
 #Traceplots
 for(i in 1:length(modList)){
   if(!is.null(modList[[i]])){

### 2022-07-21 helperFunctions.R
Worked on partial plots
Created function to simulate yield through entire SEM

@@ -229,80 +229,6 @@ g2bushels <- function(x){
   # 2204.62 #lbs per tonne
 }
 
-#Extract fits for marginal plots
-# mod = stanfit model or dataframe with parameters 
-# parList = named list with vectors of parameters to predict at (passed through expand.grid)
-# otherPars = character vector of other parameters to add to the dataframe
-# q = quantiles to predict at
-# nrep = number of replicates of parameters to generate (for data.frame parameters)
-
-getPreds <- function(mod,parList=NULL,offset=NULL,ZIpar=NULL,otherPars=NULL,q=c(0.5,0.025,0.975),nrep=4000,trans=NULL,expandGrid=TRUE){
-  if(is.null(parList)) stop('Specify parameters')
-  dfNames <- c("param","mean","sd","Z","median",
-               "lwr","upr","pval","n_eff","Rhat")
-  
-  if(class(mod)=='stanfit'){
-    m <- extract(mod,par=names(parList))
-    m <- do.call('cbind',m) #All draws
-    m_mean <- apply(m,1,mean) #Mean values
-    if(!is.null(otherPars)){
-      extras <- extract(mod,par=otherPars) %>% sapply(.,median)
-    }
-  } else if(class(mod)=='data.frame' & !any(!names(mod)==dfNames)){ #If using a dataframe
-    if(any(!names(parList) %in% mod$param)){
-      stop(paste0('Parameters not found: ',paste(names(parList)[!names(parList) %in% mod$param],collapse=', ')))
-    } 
-    chooseRows <- mod$param %in% names(parList) 
-    m <- mod[chooseRows,] 
-    m_mean <- setNames(m$mean,names(parList)) #Mean value
-    m <- do.call('cbind',lapply(1:nrow(m),function(i) runif(nrep,m$lwr[i],m$upr[i]))) #Generate draws b/w upr and lower
-    colnames(m) <- names(parList)
-    
-    if(!is.null(otherPars)){
-      extras <- mod$median[mod$param %in% otherPars] 
-      names(extras) <- otherPars
-    }
-  } else {
-    warning('mod is not stanfit object or dataframe with correct column names')
-    return(NA)
-  }
-  
-  if(expandGrid){ 
[…]

### 2022-07-21 partial plots.R

@@ -550,44 +550,258 @@ ggsave('allSeeds_plSize.png',p,bg='white',width = 12,height=4)
 
 # Total yield and seed size for commodity fields -----------------------------------------------------
 
-#Fixed terms: plSize, plDens, flDens, hbeeDist, numHives
+# avgCommData$flDensMean$mean #Avg sqrt flw dens
+# avgCommData$logHbeeDist$mean #avg log hbee dist
+# avgCommData$logitFlwSurv$mean #avg logit flw surv
 
-dat <- list(
-  avgPlSize = log(mean(exp(commData$plantSize))), #log avg plant size
-  avgPlDens = log(mean(exp(commData$plDens_obs))), #log avg plant dens
-  avgFlDens = 0, #fl Dens (centered)
-  hbeeDists = 1:100, #1-100 m
-  numHives = log(40+1) #40 hives
-)
+debugonce(genCommYield)
+d <- list()
+d_mean <- genCommYield(dat=d,simPar=TRUE)
+d <- replicate(100,genCommYield(dat=d,simPar = TRUE),simplify = FALSE) %>% bind_rows()
+hist(d$yield_tha); abline(v=d_mean$yield_tha)
 
-dat$clogHbeeDists <- log(dat$hbeeDists)-avgCommData$logHbeeDist$mean
+#Distance and stocking effect
+datList <- list(
+  hbeeDist = rep(1:100,2), #1-100 m
+  plDens=50, #Same plant density
+  numHives = rep(c(0,40),each=100) #0,40 hives
+) 
 
-# datdf <- expand.grid(
-#   avgPlSize = log(mean(exp(commData$plantSize))), #log avg plant size
-#   avgPlDens = log(mean(exp(commData$plDens_obs))), #log avg plant dens
-#   avgFlDens = 0, #fl Dens (centered)
-#   hbeeDists = 0:100, #0-100 m
-#   numHives = log(40+1) #40 hives
-# )
+d_mean <- genCommYield(datList) %>% as.data.frame() %>% 
+  mutate(numHives=factor(numHives))
 
-#Visitation
-dat$hbeeVis <- list('intHbeeVis'=1,
-                    'slopeHbeeDistHbeeVis'=dat$clogHbeeDists,
-                    'slopeNumHivesHbeeVis'= dat$numHives, 'slopeFlDensHbeeVis' = 0) %>% 
[…]

### 2022-07-27 helperFunctions.R
Worked on mvnorm generation
- appears to work, but check

@@ -355,16 +355,16 @@ capFirst <- function(x,decap=FALSE){ #Capitalize/decapitalize first letter of a 
   return(x)
 }
 
-rnormLim <- function(n,mu,Sigma,lwr,upr){ #Generates normally distributed data bounded between upr and lwr
+rnormLim <- function(N,mu,Sigma,lwr,upr){ #Generates normally distributed data bounded between upr and lwr
   if(is.matrix(Sigma)){ #Multivariate normal
-    r <- matrix(NA,N,length(m))
+    r <- matrix(NA,N,length(mu),dimnames = list(1:N,colnames(Sigma)))
     while(any(is.na(r[,1]))){
       r[is.na(r[,1]),] <- MASS::mvrnorm(sum(is.na(r[,1])),mu,Sigma)
-      inLims <- apply(sapply(1:ncol(r),function(i) r[,i]>lwr[i] & r[,i]<upr[i]),1,any)
-      r[!inLims,] <- NA
+      outLims <- apply(matrix(sapply(1:ncol(r),function(i) r[,i]<lwr[i] | r[,i]>upr[i]),nrow=N),1,any)
+      r[outLims,] <- NA
     }
   } else { #Normal
-    r <- rep(NA,n)
+    r <- rep(NA,N)
     while(any(is.na(r))){
       r[is.na(r)] <- rnorm(sum(is.na(r)),mu,Sigma)
       r[r>upr|r<lwr] <- NA
@@ -376,20 +376,24 @@ rnormLim <- function(n,mu,Sigma,lwr,upr){ #Generates normally distributed data b
 #Extract fits for marginal plots
 # mod = stanfit model or dataframe with parameters 
 # parList = named list with vectors of parameters to predict at (passed through expand.grid)
+# offset = time span for count data offset
+# ZIpar = parameter for zero-inflated distribution
+# ENpar = parameter for exponential-normal distribution
 # otherPars = character vector of other parameters to add to the dataframe
 # q = quantiles to predict at
 # nrep = number of replicates of parameters to generate (for data.frame parameters)
 # simPar = get single draw from posterior instead of using mean + quantiles
 
-getPreds <- function(mod,parList=NULL,offset=NULL,ZIpar=NULL,otherPars=NULL,q=c(0.5,0.025,0.975),nrep=4000,trans=NULL,expandGrid=TRUE,simPar=FALSE){
[…]

### 2022-07-27 partial plots.R

@@ -58,9 +58,6 @@ timeOffset <- 6 #Use 1 hr offset (1 = 10 mins, 6 = 1 hr)
 lab <- c('HB Seed','LCB Seed','HB Commodity') 
 labCols <- c('darkorange','darkgreen','black')
 
-debugonce(getPreds)
-debugonce(rnormLim)
-
 #Hbee stocking rate numbers
 with(avgCommData,
            list('intHbeeVis'=1,
@@ -138,6 +135,8 @@ d1 <- with(avgSeedData, #Hbee visits
            trans='exp',q=c(0.5,0.05,0.95)) %>% 
   transmute(dist=1:30,mean,med,lwr,upr)
 
+# debugonce(getPreds)
+
 d2 <- with(avgSeedData, #Lbee visits
            list('intVisitLbeeVis'=1,
                 'slopeFlDensLbeeVis' = 0,
@@ -202,8 +201,8 @@ ggsave('allVisits.png',p,bg='white',width = 12,height=4)
 #median, mean, max:
 #0,1.72,36 max for commodity, 4,22.6,215 for seed
 hbeeVisComm <- log(seq(0,max(with(commData,hbeeVis/totalTime)),length=30)+1)
-hbeeVisSeed <- log((seq(0,max(with(seedData,hbeeVis/totalTime)),length=100))+1)
-lbeeVisSeed <- log((seq(0,max(with(seedData,lbeeVis/totalTime)),length=100))+1)
+hbeeVisSeed <- log((seq(0,100,length=100))+1)
+lbeeVisSeed <- log((seq(0,100,length=100))+1)
 lab <- c('HB Seed','LCB Seed','HB Commodity') 
 labCols <- c('darkorange','darkgreen','black')
 
@@ -250,8 +249,8 @@ p1 <- bind_rows(d2,d3,d1,.id = 'type') %>%
   scale_y_log10()
 
 #Distance effects
-hbeeDistComm <- with(avgCommData,seq(clogHbeeDist$min,log(400)-avgCommData$logHbeeDist$mean,length=100))
-hbeeDistSeed <- with(avgSeedData,seq(clogHbeeDist$min,clogHbeeDist$max,length=100))
+hbeeDistComm <- with(avgCommData,seq(clogHbeeDist$min,log(100)-avgCommData$logHbeeDist$mean,length=100))
[…]

### 2022-07-28 helperFunctions.R
Worked on partial plots

@@ -448,7 +448,7 @@ getPreds <- function(mod,parList=NULL,offset=NULL,ZIpar=NULL,ENpar=NULL,
   } 
   
   if(!is.null(ZIpar)){ #Add ZI term if needed (on log scale)
-    i <- mod$summary$param==ZIpar
+    i <- which(mod$summary$param==ZIpar)
     draws[,i] <- log(1-draws[,i]) #Log-ZI parameter
     colnames(draws)[i] <- 'ZI'
     if(!simPar){
@@ -459,7 +459,7 @@ getPreds <- function(mod,parList=NULL,offset=NULL,ZIpar=NULL,ENpar=NULL,
   }
   
   if(!is.null(ENpar)){ #Add exp-normal term if needed
-    i <- mod$summary$param==ENpar
+    i <- which(mod$summary$param==ENpar)
     draws[,i] <- 1/draws[,i] #EN parameter
     colnames(draws)[i] <- 'EN'
     if(!simPar){

### 2022-07-28 partial plots.R

@@ -5,8 +5,8 @@ library(tidyverse)
 library(ggpubr)
 library(parallel)
 theme_set(theme_bw())
-setwd('~/Documents/canola_yield_project/Figures') #Galpern machine path
-# setwd('~/Projects/UofC/canola_yield_project/Models') #Multivac path
+# setwd('~/Documents/canola_yield_project/Figures') #Galpern machine path
+setwd('~/Projects/UofC/canola_yield_project/Models') #Multivac path
 
 source('../helperFunctions.R') #Helper functions
 
@@ -98,6 +98,7 @@ d2 <- with(avgSeedData, #Hbee visitation in seed fields
 #   labs(x='Distance from apiary (m)',y='Visits per hour',
 #        fill='Field\nType',col='Field\nType')
 
+# debugonce(getPreds)
 d3 <- with(avgSeedData,
                   list('intVisitLbeeVis'=1,
                        'slopeFlDensLbeeVis' = 0,
@@ -109,15 +110,15 @@ d3 <- with(avgSeedData,
                   ZIpar = 'thetaLbeeVis',trans='exp',q=c(0.5,0.05,0.95)) %>% 
   transmute(dist=exp(dists),mean,med,lwr,upr)
 
-p1 <- bind_rows(d2,d3,d1,.id = 'type') %>% 
+(p1 <- bind_rows(d2,d3,d1,.id = 'type') %>% 
   mutate(type=factor(type,labels=lab)) %>% 
   ggplot(aes(x=dist,y=mean))+
   geom_ribbon(aes(ymax=upr,ymin=lwr,fill=type),alpha=0.3)+
   geom_line(aes(col=type))+
-  coord_cartesian(y=c(0,150))+
+  # coord_cartesian(y=c(0,150))+
   labs(x='Distance from apiary (m)',y='Visits per hour',fill=NULL,col=NULL)+
   scale_colour_manual(values=labCols)+
-  scale_fill_manual(values=labCols)
+  scale_fill_manual(values=labCols))
 
 
 #Hbee and Lbee visitation from shelters
@@ -155,7 +156,7 @@ p2 <- bind_rows(d1,d2,.id='type') %>%
   geom_line(aes(col=type))+
   labs(x='Distance from shelter (m)',y='Visits per hour',
        fill=NULL,col=NULL)+
-  coord_cartesian(y=c(0,300))+
+  # coord_cartesian(y=c(0,300))+
   scale_colour_manual(values=labCols)+
   scale_fill_manual(values=labCols)
 

### 2022-07-28 partial plots.R
More work on partial plots

@@ -98,7 +98,6 @@ d2 <- with(avgSeedData, #Hbee visitation in seed fields
 #   labs(x='Distance from apiary (m)',y='Visits per hour',
 #        fill='Field\nType',col='Field\nType')
 
-# debugonce(getPreds)
 d3 <- with(avgSeedData,
                   list('intVisitLbeeVis'=1,
                        'slopeFlDensLbeeVis' = 0,
@@ -110,16 +109,18 @@ d3 <- with(avgSeedData,
                   ZIpar = 'thetaLbeeVis',trans='exp',q=c(0.5,0.05,0.95)) %>% 
   transmute(dist=exp(dists),mean,med,lwr,upr)
 
+
 (p1 <- bind_rows(d2,d3,d1,.id = 'type') %>% 
   mutate(type=factor(type,labels=lab)) %>% 
   ggplot(aes(x=dist,y=mean))+
   geom_ribbon(aes(ymax=upr,ymin=lwr,fill=type),alpha=0.3)+
   geom_line(aes(col=type))+
-  # coord_cartesian(y=c(0,150))+
+  # coord_cartesian(y=c(0,150),clip='on')+
+  ylim(0,150)+
   labs(x='Distance from apiary (m)',y='Visits per hour',fill=NULL,col=NULL)+
   scale_colour_manual(values=labCols)+
-  scale_fill_manual(values=labCols))
-
+  scale_fill_manual(values=labCols)
+)
 
 #Hbee and Lbee visitation from shelters
 
@@ -149,7 +150,7 @@ d2 <- with(avgSeedData, #Lbee visits
            trans='exp',q=c(0.5,0.05,0.95)) %>% 
   transmute(dist=1:30,mean,med,lwr,upr)
 
-p2 <- bind_rows(d1,d2,.id='type') %>% 
+(p2 <- bind_rows(d1,d2,.id='type') %>% 
   mutate(type=factor(type,labels=lab[1:2])) %>% 
   ggplot(aes(x=dist,y=mean))+
   geom_ribbon(aes(ymax=upr,ymin=lwr,fill=type),alpha=0.3)+
@@ -158,7 +159,7 @@ p2 <- bind_rows(d1,d2,.id='type') %>%
        fill=NULL,col=NULL)+
   # coord_cartesian(y=c(0,300))+
   scale_colour_manual(values=labCols)+
-  scale_fill_manual(values=labCols)
+  scale_fill_manual(values=labCols))
 
[…]

### 2022-07-29 partial plots.R
Finished partial plots

@@ -3,10 +3,11 @@
 # Load everything ---------------------------------------------------------
 library(tidyverse)
 library(ggpubr)
+library(metR)
 library(parallel)
 theme_set(theme_bw())
-# setwd('~/Documents/canola_yield_project/Figures') #Galpern machine path
-setwd('~/Projects/UofC/canola_yield_project/Models') #Multivac path
+setwd('~/Documents/canola_yield_project/Figures') #Galpern machine path
+# setwd('~/Projects/UofC/canola_yield_project/Models') #Multivac path
 
 source('../helperFunctions.R') #Helper functions
 
@@ -115,7 +116,7 @@ d3 <- with(avgSeedData,
   ggplot(aes(x=dist,y=mean))+
   geom_ribbon(aes(ymax=upr,ymin=lwr,fill=type),alpha=0.3)+
   geom_line(aes(col=type))+
-  # coord_cartesian(y=c(0,150))+
+  coord_cartesian(y=c(0,150))+
   labs(x='Distance from apiary (m)',y='Visits per hour',fill=NULL,col=NULL)+
   scale_colour_manual(values=labCols)+
   scale_fill_manual(values=labCols))
@@ -149,16 +150,16 @@ d2 <- with(avgSeedData, #Lbee visits
            trans='exp',q=c(0.5,0.05,0.95)) %>% 
   transmute(dist=1:30,mean,med,lwr,upr)
 
-p2 <- bind_rows(d1,d2,.id='type') %>% 
+(p2 <- bind_rows(d1,d2,.id='type') %>% 
   mutate(type=factor(type,labels=lab[1:2])) %>% 
   ggplot(aes(x=dist,y=mean))+
   geom_ribbon(aes(ymax=upr,ymin=lwr,fill=type),alpha=0.3)+
   geom_line(aes(col=type))+
   labs(x='Distance from shelter (m)',y='Visits per hour',
        fill=NULL,col=NULL)+
-  # coord_cartesian(y=c(0,300))+
+  coord_cartesian(y=c(0,300))+
   scale_colour_manual(values=labCols)+
-  scale_fill_manual(values=labCols)
+  scale_fill_manual(values=labCols))
 
 #Center and edge of bays
 d1 <- with(avgSeedData, #Hbee visits
[…]

### 2022-07-29 Manuscript/main.tex
Worked on manuscript

@@
 %    %If the caption is shorter than the line width then
-%    % the caption is centred, otherwise is flushed left.
+%    % the caption is centred, ot is flushed left.
 %    \ifthenelse{\lengthtest{\captionlength < \linewidth }} %
@@
 Structural equation models are a set of linear models arranged in a causal network, which provides a framework for testing hypotheses about complex systems \citep{grace2012, lefcheck2015}.
-Starting with a simple model (visitation $\rightarrow$ pollen deposition $\rightarrow$ fruit production $\leftarrow$ plant resources), we built a detailed model relating visitation to pollination to seed yield within a causal framework (Figures \ref{fig:commoditySEM} and \ref{fig:seedSEM}).
+Starting with a simple model (visitation $\rightarrow$ pollen deposition $\rightarrow$ fruit production $\leftarrow$ plant resources), we built a detailed model relating visitation to pollination to seed yield within a causal framework (see Figure \ref{fig:allSEM} in Results).
 These models let us model how visitation ultimately influences seed yield, while controlling for other confounding factors (e.g. distance into field, measurements taken at different fields).
@@
 % Pod set (fraction of flowers that matured into pods) was modeled using a beta-binomial distribution with a logit-link function.
-% Interactions between predictors were evident in honey bee visitation rate (Year:Locality interaction) and plant density (Irrigation:Year) in commodity canola, and for LCB visitation (Tent Stocking:Distance from edge) in seed canola, and were included in each model (represented as Y-shaped path in Figures \ref{fig:commoditySEM} and \ref{fig:seedSEM}).
+% Interactions between predictors were evident in honey bee visitation rate (Year:Locality interaction) and plant density (Irrigation:Year) in commodity canola, and for LCB visitation (Tent Stocking:Distance from edge) in seed canola, and were included in each model (represented as Y-shaped path in Figures \ref{fig:allSEM} and \ref{fig:allSEM}).
 
@@
 Honey bee visitation decreased with distance away from the apiary, in both commodity and seed canola fields.
-In commodity fields, honey bee visitation decreased from 6.4 visits/hr at the edge to 1.0 visits/hr at the centre of the field (400 m) (p$=$0.0002, Figure \ref{fig:allVis}, apiary of 40 hives).
+In commodity fields, honey bee visitation decreased from 6.4 visits/hr at the edge to 1.0 visits/hr at the centre of the field (400 m) (p$=$0.0002, Figure \ref{fig:allVisits}, apiary of 40 hives).
 % Visitation rates were higher in both years in Lethbridge (2014: 9.3 visits/hr, 2015: 7.1), but were higher in 2015 than 2014 at Grande Prairie (Z=2.3, p$=$0.02), rising from 5 visits/hr at the field edge in 2014 to 17 visits/hr in 2015.
@@
 Honey bee visitation was much higher overall in seed canola fields, and decreased from 99.5 visits/hr at edge to 78.8 visits/hr at the centre of the field (Z=-2.5, p$=$0.01). 
-Honey bee visitation was also lower near leafcutter shelters (Z=3.9, p$=$0.001), dropping from 60 visits/hr at 10 m to 34 visits/hr at 2 m, likely due to competition with LCBs (Figure \ref{fig:hbeeDist_both}, \ref{fig:lbeeDist_both}).
+Honey bee visitation was also lower near leafcutter shelters (Z=3.9, p$=$0.001), dropping from 60 visits/hr at 10 m to 34 visits/hr at 2 m, likely due to competition with LCBs (Figure \ref{fig:allVisits}).
 
@@
 29 visits/hr), while honey bee visitation was higher (p$=$0.008, 71 vs.
-117 visits/hr, Figure \ref{fig:edgeCentVis_both}), indicating that pollination is likely done by different species in different parts of the field.
+117 visits/hr, Figure \ref{fig:allVisits}), indicating that pollination is likely done by different species in different parts of the field.
 %Therefore, visitation by both species strongly decreases with distance from the edge of the field, decreases with distance from the leafcutter shelters in seed canola fields, and is done by different bees at the centre of the female bay.
@@
 Commodity fields are shown at a stocking rate of 40 hives (black line), while stocking rates are at 160 hives in seed fields (yellow line).}
-    \label{fig:allVis}
+    \label{fig:allVisits}
 \end{figure}
@@
     \centering
-    \includegraphics[width=0.9\textwidth,keepaspectratio=true]{allPollen.png}
+    \includegraphics[width=0.9\textwidth,keepaspectratio=true]{../Figures/allPollen.png}
     \caption{Effect of a) visitation rate, b) distance from apiary (HB) or shelter (LCB), and c) female bay position on pollen deposition.}
@@
 
-\begin{figure} 
-    \centering
-    \includegraphics[width=\textwidth,keepaspectratio=true]{plDensPlSize_both.png}
-    \caption[Partial effects of plant density on plant size]{Partial effects of plant density on plant size, for commodity and seed canola plants.
-Solid lines represents median, and shaded areas represent 95\% CIs.}
-    \label{fig:plDensPlSize}
-\end{figure}
-
 Plant size had by far the strongest positive effect on the number of pods produced, and there was evidence of pod set suppressing flower production.
@@
 mean: 303, SD: 208, range: 10--1410).
-In both commodity and seed canola, plant size had a strong positive effect on the total number of flowers per plant (both p$<<$0.0001, Figure \ref{fig:plSizeFlwCount}), as well as pod set (both p$<$0.001, Figure \ref{fig:flwSurv_both}).
+In both commodity and seed canola, plant size had a strong positive effect on the total number of flowers per plant as well as pod set (both p$<$0.001).
 Pod set had a strong negative influence on total flowers per plant (p$<$0.0001) in both commodity and seed canola (both p$<<$0.0001), indicating that high pod set suppresses future flower production.
@@
 However, the harvest index of commodity canola (mean: 0.26, SD: 0.08, range: 0.005--0.65) was higher than seed canola (mean: 0.23, SD: 0.09, range: 0.003--0.55), meaning that commodity plants produced more seeds per gram of biomass than seed canola plants.%, likely due to the lack of pollen limitation.
-
-\begin{figure} %SH: HARD TO COMPARE BECAUSE OF DIFFERENT AXES
-    \centering
-    \includegraphics[width=\textwidth,keepaspectratio=true]{plSizeflwCount_both.png}
-    \caption[Partial effect of plant size on number of flowers per plant]{Partial effect of plant size on number of flowers per plant, for commodity and seed canola plants.
-Solid lines represent median, and shaded areas represent 95\% CIs.}
-    \label{fig:plSizeFlwCount}
-\end{figure}
-
-\begin{figure}
-    \centering
-    \includegraphics[width=\textwidth,keepaspectratio=true]{plSizeFlwSurv_both.png} 
-    \caption[Partial effect of plant size on pod set]{Partial effect of plant size on pod set (\% of flowers that became pods), for both commodity and seed canola.
-Solid lines represent median, and shaded areas represent 95\% CIs.}
-    \label{fig:flwSurv_both}
-\end{figure}
 
@@
 There were also between-year differences in seeds per pod (commodity canola only: Z=4.7, p$<$0.0001, 21.7 seeds per pod in 2014, 24.6 in 2015) and seed size (commodity canola: Z=2.2, p=0.031, 2.04 mg/seed in 2014, 2.31 mg/seed in 2015; seed canola: Z=3.6, p=0.0003, 3.11mg/seed in 2015, 3.59mg/seed in 2016), pointing to differences in overall growing conditions between years.
-
-\begin{figure}
-    \centering
-    \includegraphics[width=0.9\textwidth,keepaspectratio=true]{seedWeightSeedCount_both.png}
-    \caption[Partial effects of seed count and plant size on seed size]{Partial effects of seed count and plant size on seed size, for both commodity and seed canola.
-Solid lines represent median, and shaded areas represent 95\% CIs.}
-    \label{fig:seedWeightCount_both}
-\end{figure}
 
@@
 Honey bees were never the aggressor in these interactions, so interference between LCBs and honey bees may be unidirectional, at least in areas near LCB shelters. 
-For this reason, we treated high leafcutter visitation as causing lower honey bee visitation in our SEM (Figure \ref{fig:seedSEM}, arrow from leafcutter visit rate to honey bee visit rate).
+For this reason, we treated high leafcutter visitation as causing lower honey bee visitation in our SEM (Figure \ref{fig:allSEM}, arrow from leafcutter visit rate to honey bee visit rate).
 
@@
 LCBs tend to switch between male and female flowers more frequently than honey bees do \citep{waytesMsc}, transport more viable pollen between flowers \citep{parker2015}, and tend not to side-work canola flowers (\citealp{soroka2001}, personal observation), which may explain their increased pollination efficacy.
-We also found that pollen deposition also decreased with distance from the edge of the field, was lower in the centre of the female bays, and that this was not solely explained by LCB abundance (Figure \ref{fig:seedSEM}).
+We also found that pollen deposition also decreased with distance from the edge of the field, was lower in the centre of the female bays, and that this was not solely explained by LCB abundance (Figure \ref{fig:allSEM}).
 During foraging bouts, LCBs may travel further between flowers than honey bees do; \citet{brunet2019} found that LCBs foraging in alfalfa (\emph{Medicago sativa} L.) travelled an average of 21 cm between flowers, while honey bees only travelled 16 cm.
@@
 Most studies on commodity canola report a seed size-number trade-off at the level of plant \citep{angadi2003,koltowski2005}, we found a positive relationship at the pod level (but see \citealp{sabbahi2005}).
-Perhaps within-plant resource variation is a more likely driver of seed number than pollen deposition, as pollination did not appear to be limiting (Figure \ref{fig:commoditySEM}, weak paths from pollen to yield metrics).
+Perhaps within-plant resource variation is a more likely driver of seed number than pollen deposition, as pollination did not appear to be limiting (Figure \ref{fig:allSEM}, weak paths from pollen to yield metrics).
 %While we did not quantify pod position on branches, the pods at the end of the branches did appear to have fewer seeds, meaning that some of the variation within plants likely occurred because of late-season seed.

### 2022-07-29 Manuscript/visitors_supplemental.tex
Worked on manuscript

@@
     \end{tabular}
-    \caption[Flower visiting insects observed in commodity and seed canola fields]{Number of flower visitors recorded over a total of 44.8 hours of observation in commodity fields (2014 and 2015), and 46.9 hours of observation in the seed fields (2015 and 2016).
+    \caption{Number of flower visitors recorded over a total of 44.8 hours of observation in commodity fields (2014 and 2015), and 46.9 hours of observation in the seed fields (2015 and 2016).
 ``Fly" refers to larger calyptrate muscoid flies (families Muscidae, Anthomyiidae, Caliphoridae), while ``Hover fly" refers to Syrphid flies.

### 2022-07-29 partial plots.R

@@ -865,6 +865,5 @@ p4 <- bind_rows(d1,d2,.id = 'type') %>%
   scale_fill_manual(values=c('darkorange','darkgreen'))+
   theme(legend.position = c(0.8,0.8))
  
-
 p <- ggarrange(p1,p2,p3,p4,labels = 'auto')
 ggsave('allYield_alternate.png',p,height=10,width=10)

### 2022-07-29 Manuscript/main.tex
Worked on manuscript

@@
 \usepackage{setspace} %Double/1.5 spacing
+\usepackage{multirow} %Multirow tables
 
@@
 This study assesses the strength of the connections between visitation, pollination, and yield, in a globally important crop species, and identifies the relative importance of bee pollination for seed production, using in-field data from two distinct cropping systems.
-Other studies of crop pollination focus on individual components, such as visitation and pollination \citep{cresswell1999, thomson2001}, or visitation and yield \citep{steffan2003, manning2005, hudewenz2013}, but have not incorporated the links in a single framework (but see \citealp{saez2018}, and few have used realistic field data \citep{morandin2005, isaacs2010}.
+Other studies of crop pollination focus on individual components, such as visitation and pollination \citep{cresswell1999, thomson2001}, or visitation and yield \citep{steffan2003, manning2005, hudewenz2013}, but have not incorporated the links in a single framework (but see \citealp{saez2018}), and few have used realistic field data \citep{morandin2005, isaacs2010}.
 This work adds to the body of literature examining the resource context of pollination services \citep{haig1988} within cropping systems \citep{marini2015, tamburini2016, fijen2018, tamburini2019}, and identifies directions of future research in seed production systems.
@@
 
-The underlying models of each pSEM were specified as generalized linear mixed-effects models (GLMMs, see Equation sets S1 and S2 for model specifications).
+The underlying models of each pSEM were specified as generalized linear mixed-effects models (GLMMs).
 GLMMs can model processes that occur at different levels; for example, seed size was modelled at the plant level, while pollen deposition was modeled at the flower level.
@@
 Plant and pollen samples were not collected from male bays in seed fields, and there were no large differences in visitation rates for honey bees or LCBs (p = 0.32, 0.72, respectively) once other terms were included as covariates, so bay identity was excluded from further analysis.
+See Equation sets S1 and S2 for model specifications) Table \ref{tab:dataSummary} for a brief summary of the variables used in each SEM
 % Pod set (fraction of flowers that matured into pods) was modeled using a beta-binomial distribution with a logit-link function.
@@
 
-Honey bee visitation decreased with distance away from the apiary, in both commodity and seed canola fields.
-In commodity fields, honey bee visitation decreased from 6.4 visits/hr at the edge to 1.0 visits/hr at the centre of the field (400 m) (p$=$0.0002, Figure \ref{fig:allVisits}, apiary of 40 hives).
+Honey bee visitation decreased with distance away from the edge of the field in both commodity and seed canola fields.
+In commodity fields, HB visitation decreased from 12 visits/hr at the edge to 1.8 visits/hr at 400 m into the field (Figure \ref{fig:allVisits}a, apiary of 40 hives).
 % Visitation rates were higher in both years in Lethbridge (2014: 9.3 visits/hr, 2015: 7.1), but were higher in 2015 than 2014 at Grande Prairie (Z=2.3, p$=$0.02), rising from 5 visits/hr at the field edge in 2014 to 17 visits/hr in 2015.
 % (at a stocking level of 20 hives).
-Higher stocking rates increased honey bee visitation at the edge of the field from 3.9 visits/hr with an apiary of 20 hives, increasing to 6.4 visits/hr with 40 hives (Z=5.3, p$<$0.0001), while unstocked field edges had an average of 0.4 visits/hr.
-Honey bee visitation was much higher overall in seed canola fields, and decreased from 99.5 visits/hr at edge to 78.8 visits/hr at the centre of the field (Z=-2.5, p$=$0.01). 
-Honey bee visitation was also lower near leafcutter shelters (Z=3.9, p$=$0.001), dropping from 60 visits/hr at 10 m to 34 visits/hr at 2 m, likely due to competition with LCBs (Figure \ref{fig:allVisits}).
+Lower stocking rates decreased HB visitation at the edge of the field to 7.4 visits/hr at 20 hives, while unstocked field edges had an average of 0.8 visits/hr.
+Unsurprisingly (given the higher stocking rate of 160 hives per field), HB visitation was much higher in seed canola fields, and decreased from 96.4 visits/hr at edge to 85.7 visits/hr at the centre of the field (Figure \ref{fig:allVisits}a).
+Visitation was also much lower near LCB shelters, dropping from 81 visits/hr at 20 m to 31 at 2 m (Figure \ref{fig:allVisits}b), likely due to competition with LCBs.
 
-LCB visitation declined rapidly with distance from the nearest shelter, showing visitation rates of 350 visits/hr at 2 m declining to 83 visits/hr at 10 m (Z=-11.4, p$=$0.0001). 
-Surprisingly, LCB visitation was also higher at the edge of the field than the centre (Z=-4.4, p$=$0.0001, 114 visits/hr vs 28 visits/hr).
-% However, there was no difference in visitation rates between the edge and the centre when leafcutter cocoon stocking was lower (Z=2.2, p$=$0.028), indicating that leafcutters at high stocking densities likely aggregate in shelters close to the edge of the field (Figure \ref{fig:hbeeDist_both}).
-% There was no difference in visitation rates between the male bay and the edge of the female bays (LCB: p$=$0.72, honey bee: p$=$0.32). 
-LCB visitation was also lower in the centre of the female bays (p$=$0.04, 51 vs.
-29 visits/hr), while honey bee visitation was higher (p$=$0.008, 71 vs.
-117 visits/hr, Figure \ref{fig:allVisits}), indicating that pollination is likely done by different species in different parts of the field.
+Leafcutter bee visitation was much higher close to their shelters, and surprisingly, was also higher at the edge of the field.
+Visitation dropped from 350 visits/hr at 2 m from the shelter to 50 visits/hr at 20 m (Figure \ref{fig:allVisits}b). 
+Interestingly, LCB visitation decreased from 119 visits/hr at the edge of the field to 25 at the centre.
+% However, there was no difference in visitation rates between the edge and the centre when LCB cocoon stocking was lower (Z=2.2, p$=$0.028), indicating that LCBs at high stocking densities likely aggregate in shelters close to the edge of the field (Figure \ref{fig:hbeeDist_both}).
+% There was no difference in visitation rates between the male bay and the edge of the female bays (LCB: p$=$0.72, HB: p$=$0.32). 
+The difference in LCB visitation between the edge and centre of the female bays was weak (p=0.14), while HB visitation was higher (88 vs.
+139 visits/hr, Figure \ref{fig:allVisits}), indicating that pollination is likely done by different species in different parts of the field.
 %Therefore, visitation by both species strongly decreases with distance from the edge of the field, decreases with distance from the leafcutter shelters in seed canola fields, and is done by different bees at the centre of the female bay.
@@
 
-LCB visitation increased pollen deposition in seed canola fields, but honey bees did not increase pollen deposition in either commodity or seed canola fields.
-Pollen deposition on stigmas was high in commodity canola (mean: 293 grains per stigma, SD: 385, range: 0--3981), but honey bee visitation had no impact on this (p$=$0.77, Figure \ref{fig:allPollen}).
-Pollen deposition slighly declined with distance from the edge of the field, but this relationship was weak (p$=$0.07) and only amounted to a 6\% average decrease (290 grains per stigma at the field edge vs.
-240 at field centre).
+LCB visitation increased pollen deposition in seed canola fields, but honey bees did not increase pollen deposition in commodity or seed canola fields.
+Pollen deposition on stigmas was high in commodity canola (mean: 293 grains/stigma, SD: 385, range: 0--3981), but honey bee visitation had no impact on this (p$=$0.77, Figure \ref{fig:allPollen}a).
+Pollen deposition declined weakly with distance from the edge of the field (p$=$0.09), but this only amounted to a 6\% average decrease (290 grains/stigma at the field edge vs. 240 at field centre).
 % Flies were also common visitors in commodity fields (Table \ref{tab:propVisitors}), but had no effect on pollen deposition (p$=$0.577), so only honey bees and LCBs were considered as potential pollinators (other flower visitors were rare).
-In seed canola, pollen deposition was much lower overall (mean: 22 grains per stigma, SD: 43, range: 0--578), and decreased from 23 to 11 grains/stigma from the edge to the centre of the field (Z=-4.4, p$=$0.0001, Figure \ref{fig:distCentPol}).
-LCB visits increased pollen deposition from 12 grains/stigma at 6 visits/hr to 16 pollen grains at 60 visits/hr (Z=3.2, p$=$0.002, Figure \ref{fig:visPol_both}), but there was no effect of honey bee visitation (Z=0.98, p$=$0.33), implying that most of the pollen deposition in seed fields is the result of LCB visitation.
-Pollen deposition also decreased from 23 grains/stigma at the edge of the female bay to 13 at the centre of the bay independent of visitation (Z=-4.5, p$=$0.0001), suggesting that pollen may be lost from bees crossing over from male bays \citep{pinnisch1990}.%, who likely visit flowers at the edge of the bay first.
+In seed canola, pollen deposition was much lower overall (mean: 22 grains per stigma, SD: 43, range: 0--578), and decreased from 26.3 grains/stigma at the edge to 11.5 at the centre of the field (Figure \ref{fig:allPollen}b) independent of visitation.
+LCB visitation increased pollen deposition from 13 grains/stigma at 0 visits/hr to 25 pollen grains at 100 visits/hr (Figure \ref{fig:allPollen}a), but there was no effect of honey bee visitation (p$=$0.20), implying that most of the pollen deposition in seed fields is the result of LCB visitation.
+Pollen deposition also decreased from 15 grains/stigma at the edge of the female bay to 9 at the centre of the bay independent of visitation, suggesting that pollen may be lost from bees crossing over from male bays.% \citep{pinnisch1990}.%, who likely visit flowers at the edge of the bay first.
 
@@
 
-Plant size had by far the strongest positive effect on the number of pods produced, and there was evidence of pod set suppressing flower production.
-Commodity canola plants produced fewer flowers (mean: 198, SD: 157, range: 13--1419) than seed canola plants (mean: 468, SD: 328, range: 26--2712), and also produced fewer pods per plant (mean: 143, SD: 114, range: 5--892 vs.
-mean: 303, SD: 208, range: 10--1410).
+\begin{figure}
+    \centering
+    \includegraphics[width=0.9\textwidth,keepaspectratio=true]{../Figures/allSeeds.png}
+    \caption{Effect of pollen deposition (top row) and plant size (bottom row) on flower survival, seeds per pod, and seed size.}
+    \label{fig:allSeeds}
+\end{figure}
+
+Plant size had by far the strongest positive effect on the number of pods produced (see plant paths in Figure \ref{fig:allSEM}), and there was evidence of pod set suppressing flower production.
+Commodity canola plants produced fewer flowers than seed canola plants, and also produced fewer pods per plant overall.
 In both commodity and seed canola, plant size had a strong positive effect on the total number of flowers per plant as well as pod set (both p$<$0.001).
@@
 but seed size was lower in commodity canola (mean: 2.74 mg/seed, SD: 1.04) than seed canola mean (mean: 3.59 mg/seed, SD: 1.33).
-In commodity canola, plant size did not affect seeds per pod or seed size (p=0.32) or seed size (Z=-0.40, p=0.69, Figure \ref{fig:seedWeightCount_both}), but eed size was positively related to seeds per pod (Z=6.1, p$<$0.0001, Figure \ref{fig:seedWeightCount_both}).
-In seed canola, however, seed size increased with plant size (Z=4.7, p$<$0.0001, Figure \ref{fig:seedWeightCount_both}), decreased with seeds per pod (Z=-13.1, p$<$0.0001), and interestingly, increased with plant density (Z=2.9, p$=$0.004), suggesting resource limitation at both the pod and the plant level.
+In commodity canola, plant size did not affect seeds per pod or seed size (p=0.32) or seed size (Z=-0.40, p=0.69, Figure \ref{fig:allSeeds}), but seed size was positively related to seeds per pod (Z=6.1, p$<$0.0001, Figure \ref{fig:allSeeds}).
+In seed canola, however, seed size increased with plant size (Z=4.7, p$<$0.0001, Figure \ref{fig:allSeeds}), decreased with seeds per pod (Z=-13.1, p$<$0.0001), and interestingly, increased with plant density (Z=2.9, p$=$0.004), suggesting resource limitation at both the pod and the plant level.
 There were also between-year differences in seeds per pod (commodity canola only: Z=4.7, p$<$0.0001, 21.7 seeds per pod in 2014, 24.6 in 2015) and seed size (commodity canola: Z=2.2, p=0.031, 2.04 mg/seed in 2014, 2.31 mg/seed in 2015; seed canola: Z=3.6, p=0.0003, 3.11mg/seed in 2015, 3.59mg/seed in 2016), pointing to differences in overall growing conditions between years.
@@
 %LCBs are extremely fast fliers, and are difficult to follow after they leave an inflorescence, meaning that tracking their movements during an entire foraging bout would be almost impossible.
-% Visits by honey bee foragers were almost twice as high in the centre of the female bay, but pollen deposition was about 40\% lower (  Figure \ref{fig:distCentPol}), which correspondingly is 
-% Honey bees in seed fields tended to visit more in the centre of the female bay, even close to the edge of the field, yet pollen deposition was still about 40\% lower (Figure \ref{fig:distCentPol}).
+% Visits by honey bee foragers were almost twice as high in the centre of the female bay, but pollen deposition was about 40\% lower (  Figure \ref{fig:allPollen}), which correspondingly is 
+% Honey bees in seed fields tended to visit more in the centre of the female bay, even close to the edge of the field, yet pollen deposition was still about 40\% lower (Figure \ref{fig:allPollen}).
 % While we found that LCBs also tend to avoid the centre of the female bays, and decrease with distance into the field, this extra dependence could have been caused by the fact that the visitation data represents a short ``snapshot'' of the pollen deposition process.
@@
 Plant size can positively influence seed size in some plant species \citep{maddox1983}, and this appears to be true in canola \citep{riffkin2012} as well as other Brassicaceae \citep{mazer1987}.
-Similarly, seeds per pod and seed weight varied positively in commodity canola, this pattern was reversed in seed canola (Figure \ref{fig:seedWeightCount_both}). 
+Similarly, seeds per pod and seed weight varied positively in commodity canola, this pattern was reversed in seed canola (Figure \ref{fig:allSeeds}). 
 These differences likely occurred because of variation in available seed resources among the parts of the plant \citep{vanNoordwijk1986}, which can cause a positive size-number relationship even in resource-limited plants.

### 2022-07-29 partial plots.R

@@ -1,4 +1,5 @@
 # MAKES PARTIAL EFFECTS PLOTS FOR SUB-MODELS
+# ALSO CREATES SUMMARY TABLES OF VARIABLES (DATA) AND PARAMETERS FROM MODELS
 
 # Load everything ---------------------------------------------------------
 library(tidyverse)
@@ -59,13 +60,13 @@ timeOffset <- 6 #Use 1 hr offset (1 = 10 mins, 6 = 1 hr)
 lab <- c('HB Seed','LCB Seed','HB Commodity') 
 labCols <- c('darkorange','darkgreen','black')
 
-#Hbee stocking rate numbers
+#Hbee visitation at edge given different stocking rates
 with(avgCommData,
            list('intHbeeVis'=1,
                 'slopeHbeeDistHbeeVis'=log(1),
                 'slopeNumHivesHbeeVis'= log(c(0,20,40)+1), 
                 'slopeFlDensHbeeVis' = 0)) %>% 
-  getPreds(modSummaries_commodity[[2]],parList = .,offset=timeOffset,
+  getPreds(modSummaries_commodity[['hbeeVis']],parList = .,offset=timeOffset,
            trans='exp',q=c(0.5,0.05,0.95)) %>% 
   transmute(type='Commodity',numHives=c(0,20,40),mean,med,lwr,upr) 
 
@@ -78,7 +79,7 @@ d1 <- with(avgCommData, #Hbee visitation in commodity
      'slopeHbeeDistHbeeVis'=dists,
      'slopeNumHivesHbeeVis'= log(40+1), 
      'slopeFlDensHbeeVis' = 0)) %>% 
-  getPreds(modSummaries_commodity[[2]],parList = .,offset=timeOffset,trans='exp',q=c(0.5,0.05,0.95)) %>% 
+  getPreds(modSummaries_commodity[['hbeeVis']],parList = .,offset=timeOffset,trans='exp',q=c(0.5,0.05,0.95)) %>% 
   transmute(dist=exp(dists),mean,med,lwr,upr)
 
 d2 <- with(avgSeedData, #Hbee visitation in seed fields
@@ -88,7 +89,7 @@ d2 <- with(avgSeedData, #Hbee visitation in seed fields
           'slopeLbeeDistHbeeVis'= 0,
           'slopeCentHbeeVis'= 0
           )) %>% 
[…]

### 2022-07-29 yield path analysis commodity.R

@@ -324,1887 +324,3 @@ modList %>%
   shipley.dSep(.,pval,param)
 
 # debugonce(shipley.dSep)
-
-# Partial effects plots for commodity fields -----------------------------
-
-#Plant density
-load('modSummaries_commodity.Rdata')
-
-list('intPlDens'=1,
-           'slopeHbeeDistPlDens'=with(datalist,seq(min(log(dist)),max(log(dist)),length=10))) %>% 
-  getPreds(modSummaries_commodity[[1]],parList = .,otherPars = c('sigmaPlDens','sigmaPlDens_field'))
-
-# list('intPlDens'=1,
-#      'slopeHbeeDistPlDens'=with(datalist,seq(min(log(dist)),max(log(dist)),length=10))) %>% 
-#   getPreds(modList[[1]],parList = .,otherPars = c('sigmaPlDens','sigmaPlDens_field'))
-
-load('modPodcount.Rdata') #All extracted coefficients in list form (mod3)
-mod3 <- extract(modPodcount) #Get coefficients from stan model
-rm(modPodcount); gc()
-
-#Plot-level data (271 rows)
-plotDat <- with(datalist,data.frame( 
-  field=plotIndex,year=is2015[plotIndex],irrigation=isIrrigated[plotIndex],
-  dist=log(dist)-mean(log(dist)), #Centered on 3.412705
-  GP=isGP[plotIndex],hives=log(numHives[plotIndex]+1), #Log-number of hives
-  plDens=apply(mod3$plDens,2,mean),flDens=flDens,
-  hbeeResid=log((hbeeVis+0.2)/totalTime)-apply(mod3$visitHbeeMu,2,median) #Log-residuals - #maybe not the best
-))
-
-#Model matrix for hbee visits
-MM_hbee <- with(plotDat,data.frame(int=1,year,GP,yearGP=year*GP,dist,hives,flDens,irrigation)) %>% as.matrix()
-#Coefficient matrix for hbee visits
-coef_hbee <- with(mod3,data.frame(intVisit,slopeYearVis,slopeGpVis,slopeYearGpVis,
-                                  slopeDistVis,slopeHiveVis,slopeFlDens,slopeIrrigVis))
-
-#Partial effect of year/area, distance
[…]

### 2022-07-29 yield path analysis seed.R

@@ -647,1329 +647,3 @@ with(mod3,PPplots(apply(seedMass_resid,1,function(x) sum(abs(x))),
                   apply(predSeedMass_resid,1,function(x) sum(abs(x))),
                   datalist$seedMass,apply(mod3$predSeedMass,2,median),
                   main='Weight per seed'))
-
-# Partial effects plots for seed fields -----------------------------------
-load('modPodcount_seed3.Rdata')
-mod3 <- extract(modPodcount_seed)
-rm(modPodcount_seed); gc()
-
-#Plot-level data (647 rows) - visitation data
-plotDat <- with(datalist,data.frame(
-  plot=1:(Nplot+Nplot_extra),
-  hbeeDist=c(hbee_dist,hbee_dist_extra),
-  lbeeDist=c(lbee_dist,lbee_dist_extra), #Centered on 3.113714
-  lbeeVis=c(lbeeVis,lbeeVis_extra),isMBay=c(isMBay,isMBay_extra), #Centered on 4.641845
-  flDens=apply(mod3$flDens,2,mean),isCent=c(isCent,isCent_extra), #Sqrt tranformed - 22
-  halfStock=c(lbeeStocking,lbeeStocking_extra), #half-stocking
-  year=c(is2016,is2016_extra),
-  logLbeeVis=log(1+c(lbeeVis,lbeeVis_extra)/c(totalTime,totalTime_extra)),
-  logHbeeVis=log(1+c(hbeeVis,hbeeVis_extra)/c(totalTime,totalTime_extra)),
-  hbeeResid=log((c(hbeeVis,hbeeVis_extra)+1)/c(totalTime,totalTime_extra))-apply(mod3$visitMu_hbee,2,median), #Log-residuals
-  lbeeResid=log((c(lbeeVis,lbeeVis_extra)+1)/c(totalTime,totalTime_extra))-apply(mod3$visitMu_lbee,2,median)
-)) %>% 
-  mutate(logHbeeDist=log(hbeeDist)-mean(log(hbeeDist)),logLbeeDist=log(lbeeDist)-mean(log(lbeeDist)))
-
-#Model matrix for lbees
-MM_lbeeVis <- with(plotDat,data.frame(int=1,logLbeeDist,logHbeeDist,isMBay,isCent,halfStock,year,flDens,
[…]

### 2022-08-02 partial plots.R
Worked on parameter info tables

@@ -914,19 +914,37 @@ bind_rows(commDatSummary,seedDatSummary,.id='Field Type') %>%
 
 # General summary of parameters for both models ---------------------------
 
+commNames <- data.frame(name=c('numHives','hbeeDist','hbeeVis','pollen',
+                                'plSize','plDens','flDens',
+                                'flwCount','flwSurv','seedCount','seedWeight'),
+                         labs=c('Number of hives','Distance from hives','Honey bee visits','Pollen count',
+                                'Plant size','Plant density','Flower density',
+                                'Flowers per plant','Pods per plant','Seeds per pod','Seed size'))
+
 lapply(modSummaries_commodity,function(x) x$summary) %>% #Get path coefficients
-  bind_rows(.id='to') %>% 
-  transmute(to,name=param,Z,pval) %>% 
-  filter(to!='yield',!grepl('(int|sigma|lambda|Phi|phi|rho)',name)) %>% 
-  mutate(to=case_when(
-    to=='flDens' & grepl('PlDens$',name) ~ 'plDens',
-    to=='flDens' & grepl('PlSize$',name) ~ 'plSize',
-    TRUE ~ gsub('avg','seed',to)
+  bind_rows(.id='model') %>% 
+  filter(model!='yield') %>% #,!grepl('(int|sigma|lambda|Phi|phi|rho)',param)) %>%
+  # mutate(param=gsub('int','Intercept',param))
+  mutate(model=case_when(
+    model=='flDens' & grepl('PlDens$',param) ~ 'plDens',
+    model=='flDens' & grepl('PlSize$',param) ~ 'plSize',
+    TRUE ~ gsub('avg','seed',model)
   )) %>% 
-  mutate(name=gsub('slope','',name)) %>% 
-  filter(mapply(grepl,capFirst(to),name)) %>% 
-  mutate(name=mapply(gsub,capFirst(to),'',name)) %>% 
-  mutate(name=capFirst(name,TRUE)) 
+  mutate(param=gsub('slope','',param)) %>% 
+  filter(mapply(grepl,capFirst(model),param)) %>% 
+  mutate(param=mapply(gsub,capFirst(model),'',param)) %>% 
+  mutate(param=capFirst(param,TRUE)) %>% 
+  left_join(commNames,by=c('model'='name')) %>% 
+  mutate(param=case_when(
+    param=='int' ~ 'Intercept',
[…]

### 2022-08-02 partial plots.R
Worked on summary tables

@@ -873,7 +873,7 @@ p4 <- bind_rows(d1,d2,.id = 'type') %>%
 p <- ggarrange(p1,p2,p3,p4,labels = 'auto')
 ggsave('allYield_alternate.png',p,height=10,width=10)
 
-# General summary of variables for both models -----------------------
+# General summary of variables (data) for both models -----------------------
 
 commDatSummary <- with(commData,list(
   'Number of hives'=numHives,'Distance to edge (m)'=dist,
@@ -906,22 +906,30 @@ seedDatSummary <- with(seedData,list(
   lapply(.,function(x) data.frame(Mean=mean(x),Median=median(x),SD=sd(x),Min=min(x),Max=max(x))) %>% 
   bind_rows(.id='Variable')
   
-bind_rows(commDatSummary,seedDatSummary,.id='Field Type') %>% 
-  mutate(`Field Type`=ifelse(`Field Type`==1,'Commodity','Seed')) %>% 
-  xtable::xtable(.,digits=c(0,0,2,2,2,2,2,2)) %>% 
-  print(.,include.rownames=FALSE,sanitize.text.function=identity)
+# #Version using xtable - needs updating to account for rotated rows
+# bind_rows(commDatSummary,seedDatSummary,.id='Field Type') %>% 
+#   mutate(`Field Type`=ifelse(`Field Type`==1,'Commodity','Seed')) %>% 
+#   xtable::xtable(.,digits=c(0,0,2,2,2,2,2,2)) %>% 
+#   print(.,include.rownames=FALSE,sanitize.text.function=identity)
 
+library(knitr)
+library(kableExtra)
+
+bind_rows(commDatSummary,seedDatSummary,.id='Field Type') %>%
+  mutate(`Field Type`=ifelse(`Field Type`==1,'Commodity','Seed')) %>% 
+  kable(format = 'latex',escape = FALSE,digits=c(0,0,2,2,2,2,2,2)) %>% 
+  collapse_rows(columns=1)
 
 # General summary of parameters for both models ---------------------------
 
 commNames <- data.frame(name=c('numHives','hbeeDist','hbeeVis','pollen',
                                 'plSize','plDens','flDens',
                                 'flwCount','flwSurv','seedCount','seedWeight'),
-                         labs=c('Number of hives','Distance from hives','Honey bee visits','Pollen count',
[…]

### 2022-08-02 yield path analysis seed.R

@@ -43,7 +43,6 @@ nodeCoords <- data.frame(name=c('numHives','hbeeDist','lbeeDist','hbeeVis','lbee
                              0,1,1,0.5,
                              0,1,3,2))
 
-
 #Specify model
 seedDAG <- dagify(plDens ~ hbeeDist,
                   plSize ~ plDens + hbeeDist,
@@ -293,8 +292,8 @@ for(i in 1:length(modList)){
 }
 
 # Get model summaries into a list of tables
-modSummaries_seed <- vector(mode = 'list',length = length(modList)) #Create new empty list
-names(modSummaries_seed) <- names(modList)
+# modSummaries_seed <- vector(mode = 'list',length = length(modList)) #Create new empty list
+# names(modSummaries_seed) <- names(modList)
 load('modSummaries_seed.Rdata') #Load existing list
 #Update model summaries if needed
 temp <- lapply(modList,parTable) #Get parameter summaries
@@ -330,7 +329,7 @@ PPplots(modList[[3]],c(datalist$lbeeVis,datalist$lbeeVis_extra),
 PPplots(modList[[4]],datalist$pollenCount,c('predPollenCount','pollen_resid','predPollen_resid'),
         'Pollen') #OK
 PPplots(modList[[5]],datalist$flwCount,c('predFlwCount','flwCount_resid','predFlwCount_resid'),
-        'Flowers per plant') #OK
+        'Flowers per plant') #PP not great, but everything else is fine - probably due to log-scaling issue
 PPplots(modList[[6]],datalist$podCount,c('predPodCount','podCount_resid','predPodCount_resid'),'Pods per plant') #OK
 PPplots(modList[[7]],datalist$seedCount_obs,c('predSeedCount','seedCount_resid','predSeedCount_resid'),
         index=datalist$obsSeedCount_ind,'Seeds per pod') #OK, but distribution is weird, even with exp-normal. 

### 2022-08-03 Manuscript/main.tex
Added tables of coefficients

@@
 Structural equation models do not have paths between all variables, which may bias the model results if this independence assumption is incorrect; this requires testing a ``basis set" of independence claims using Shipley's d-separation criteria \citep{shipley2000, shipley2009}.
-The initial commodity canola pSEM was misspecfied, as several missing paths were identified (Fisher's C = 167.5, df = 64, p$<<$0.001), but the updated pSEM was deemed adequate (C = 81.6, df = 86, p = 0.62).
+The initial commodity canola pSEM was misspecfied, as several missing paths were identified (Fisher's C = 167.5, df = 64, p$<<$0.001), but the updated pSEM was deemed adequate (C = 52.0, df = 48, p = 0.32).
 Similarly, the initial seed field pSEM also had several missing paths (C = 105.6, df = 76, p = 0.01), which were added, making the updated pSEM adequate (C = 72.2, k = 72, p = 0.47).
@@
 We assessed the underlying probability distribution functions of each model using posterior predictive checks \citep{gelman2013}, and found that the probability distributions were properly specified (p$\sim$0.5).
-p-values listed below (also in Tables S3 and S4) are \textit{posterior} p-values, representing the proportion of the posterior distribution that overlapped zero, with Z-scores (mean/standard deviation of posterior) showing the effect size.
+p-values were calculated using the Z-scores (mean/SD) of the sampled posterior distributions; unless otherwise specified, p-values are lower than 0.05 (see Table \ref{tab:commCoef} and \ref{tab:seedCoef} for more detailed model summaries).
 % This means that while the average seed counts (per plant) were unbiased, the variance within a plant was not. 
@@
 \include{extra_supplemental}
-\include{visitors_supplemental}
-\include{models_supplemental}
+% \include{visitors_supplemental}
+% \include{models_supplemental}
 

### 2022-08-03 partial plots.R

@@ -6,6 +6,8 @@ library(tidyverse)
 library(ggpubr)
 library(metR)
 library(parallel)
+library(knitr)
+library(kableExtra)
 theme_set(theme_bw())
 setwd('~/Documents/canola_yield_project/Figures') #Galpern machine path
 # setwd('~/Projects/UofC/canola_yield_project/Models') #Multivac path
@@ -670,7 +672,7 @@ b <- seq(2.5,3.7,0.1)
 (p2 <- d_mean %>% 
     ggplot(aes(x=hbeeDist,y=lbeeDist,z=yield_tha))+
     geom_contour(col='black',breaks=b)+
-    geom_label_contour(skip=1,breaks=b,fill='white',label.size=0)+
+    geom_label_contour(skip=0,breaks=b,fill='white',label.size=0)+
     labs(x='Honey bee distance',y='Leafcutter distance',fill='Simulated\nyield\n(t/ha)')
   )
 
@@ -765,7 +767,7 @@ d_mean <- genCommYield(datList) %>% as.data.frame() %>%
   ggplot(aes(x=hbeeDist,y=med,group=numHives))+
   geom_ribbon(aes(ymax=upr,ymin=lwr),alpha=0.3)+
   geom_line(data=d_mean,aes(x=hbeeDist,y=seedWeight))+
-  annotate('text',x=c(300,300),y=c(2.85,2.77),label=c('40 hives','0 hives'))+
+  annotate('text',x=c(300,300),y=c(2.825,2.75),label=c('40 hives','0 hives'))+
   labs(x=xaxis,y='Seed size (mg/seed)'))
 
 (p2 <- d %>% mutate(numHives=factor(numHives)) %>% group_by(hbeeDist,numHives) %>% 
@@ -773,7 +775,7 @@ d_mean <- genCommYield(datList) %>% as.data.frame() %>%
   ggplot(aes(x=hbeeDist,y=med,group=numHives))+
   geom_ribbon(aes(ymax=upr,ymin=lwr),alpha=0.3)+
   geom_line(data=d_mean,aes(x=hbeeDist,y=yield_tha))+
-  annotate('text',x=c(300,300),y=c(3.45,3.35),label=c('40 hives','0 hives'))+
+  annotate('text',x=c(300,300),y=c(2.65,2.45),label=c('40 hives','0 hives'))+
   labs(x=xaxis,y='Yield (t/ha)'))
 
[…]

### 2022-08-03 yield path analysis commodity.R

@@ -226,6 +226,7 @@ PPplots(modList[[8]],log(datalist$yield),c('predYield','yield_resid','predYield_
 # Examine random intercept distributions
 compareRE(modList[[1]],'intPlDens_field') 
 compareRE(modList[[1]],'intPlSize_field')
+# compareRE(modList[[1]],'intPlSize_plot') #Not great. Most overlap zero, and N_eff for sigma is low
 compareRE(modList[[1]],'intFlDens_field') 
 compareRE(modList[[2]],'intVisit_field') #skew-normal, but looks OK
 compareRE(modList[[3]],'intPollen_field')
@@ -277,17 +278,16 @@ modFiles <- modFiles[sapply(read.csv('./Commodity model claims 3/claimsList_upda
 # modList <- vector(mode = 'list',length = length(modFiles))
 # names(modList) <- paste0('claim',formatC(1:length(modList),width=2,flag='0'))
 
-# runThese <- 8:24 #1:length(modFiles)
+runThese <- sapply(paste0('commodity_claim',formatC(c(2,3,6,9,10),width = 2,flag = 0),'.stan'),function(x) grep(x,modFiles))
 
-# for(i in runThese){
-{
-  i <- 8
+for(i in runThese){
+  # i <- 8
   overwrite <- TRUE
   if(file.exists(modFiles[i])){
     print(paste0('Starting model ',modFiles[i]))
     mod <- stan(file=modFiles[i],data=datalist,iter=3000,chains=4,control=list(adapt_delta=0.8),init=0)
     
-    temp <- parTable(mod) #Get parameter summaries
+    temp <- parTable(mod)$summary #Get parameter summaries
     #Save information to csv file
     modList <- read.csv('./Commodity model claims 3/claimsList_updated2.csv',sep=',',strip.white = TRUE)
     modList[i,match(names(temp),names(modList))] <- temp[grepl('claim',temp$param),]
@@ -317,10 +317,12 @@ modFiles <- modFiles[sapply(read.csv('./Commodity model claims 3/claimsList_upda
 
 #Calculate C-statistic
 
-modList <- read.csv('./Commodity model claims 3/claimsList_updated2.csv',sep=',',strip.white = TRUE)
-
-modList %>% 
+#Original model
+read.csv('./Commodity model claims 3/claimsList_updated.csv',sep=',',strip.white = TRUE) %>% 
[…]

### 2022-08-03 Manuscript/supplemental.tex
Moved supplementals to single file

%%%%%%%%%% Merge with supplemental materials %%%%%%%%%%
%%%%%%%%%% Prefix a "S" to all equations, figures, tables and reset the counter %%%%%%%%%%
\setcounter{equation}{0} %Resets page, eqn, figure, table numbers
\setcounter{figure}{0}
\setcounter{table}{0}
%\setcounter{page}{1} 
\makeatletter
\renewcommand{\theequation}{S\arabic{equation}} %Adds S to the front of references
\renewcommand{\thefigure}{S\arabic{figure}}
\renewcommand{\thetable}{S\arabic{table}}
\renewcommand{\bibnumfmt}[1]{[S#1]}
\renewcommand{\citenumfont}[1]{S#1}
%\pagenumbering{gobble}

\clearpage
\section*{Appendix A: Additional figures and tables}

\begin{figure}
    \centering
    \includegraphics[width=\textwidth,keepaspectratio=true]{../Figures/FieldLocations.png}
    \caption{Map of sampled fields, showing locations of 29 commodity canola fields (14 during 2014, 15 during 2015), and 35 seed canola fields (15 during 2015, 20 during 2016). Seed canola is grown only in southern Alberta, while commodity canola is grown across both the northern and southern regions.}
    \label{fig:fieldMap}
\end{figure}

\begin{figure}
    \centering
    \includegraphics[width=\textwidth,keepaspectratio=true]{seedfieldBays.jpg}
    \caption[Hybrid seed field near Rainer, AB]{Hybrid seed field near Rainer, AB, showing the outlines of male and female bays in the foreground, with orange leafcutter bee shelters stationed throughout the field. The linear structure on the horizon is the central-pivot irrigation sprinkler.}
    \label{fig:seedfieldPhoto}
\end{figure}

\begin{figure}
    \centering
    \includegraphics[width=0.6\textwidth,keepaspectratio=true]{seedfieldPlots.png}
    \caption[Plot arrangement for surveys in hybrid seed fields]{Plot arrangement for surveys in hybrid seed fields, showing hypothetical arrangement of leafcutter shelters ($\Delta$), and male-fertile (\Hermaphrodite) and female bays (\Female) at 5m from the edge of the field. Plots were placed 5, 20, 100, and 400m along a transect (dashed line) from the field edge nearest to the set of honey bee hives. Plots were placed side-by-side in the male bay and edge of the female bay (``edge" plots), and at the 5m and 400m distances, a plot was placed in the centre of the female bay (``centre" plots).}
    \label{fig:seedfieldPlots}
\end{figure}

\begin{figure}
    \centering
    \includegraphics[width=0.6\textwidth,keepaspectratio=true]{../Figures/seedYield_bayCent.png}
    \caption{Simulation results from seed field models, showing seed size and yield (first and second rows, respectively) for plots at the edge and centre of female bays (first and second column), at varying distances away from HB hives and LCB shelters.}
    \label{fig:seedYield_bayCent}
\end{figure}

\begin{table}[ht]
\caption{Summary of variables used in structural equation models.}
\centering
\begin{tabular}{l|l|r|r|r|r|r}
\hline
Field Type & Variable & Mean & Median & SD & Min & Max\\
\hline
 & Number of hives & 14.80 & 0.00 & 17.03 & 0.00 & 40.00\\
\cline{2-7}
 & Distance to edge (m) & 137.48 & 20.00 & 195.02 & 1.00 & 500.00\\
\cline{2-7}
 & HB visitation (hr$^{-1}$) & 10.31 & 0.00 & 28.80 & 0.00 & 218.18\\
\cline{2-7}
 & Flower density (m$^2$) & 470.33 & 448.00 & 231.32 & 52.00 & 1684.00\\
\cline{2-7}
 & Pollen per stigma & 293.33 & 155.00 & 385.04 & 0.00 & 3891.00\\
\cline{2-7}
 & Plant density (m$^2$) & 3.77 & 3.77 & 0.48 & 1.79 & 5.02\\
\cline{2-7}
 & Plant vegetative mass (g) & 18.15 & 14.32 & 14.07 & 0.77 & 107.66\\
\cline{2-7}
 & Plant seed mass (g) & 6.87 & 5.46 & 5.97 & 0.01 & 47.90\\
\cline{2-7}
 & Flowers per plant & 196.09 & 156.50 & 150.96 & 13.00 & 1094.00\\
\cline{2-7}
 & Pods per plant & 143.15 & 112.00 & 114.64 & 5.00 & 892.00\\
\cline{2-7}
 & Seeds per pod & 22.96 & 23.60 & 4.97 & 4.60 & 35.40\\
\cline{2-7}
\multirow{-12}{*}{\raggedright\arraybackslash Commodity} & Seed size (mg) & 2.74 & 2.73 & 0.80 & 0.39 & 5.35\\
\cline{1-7}
 & Distance to edge (m) & 162.70 & 100.00 & 146.18 & 3.00 & 400.00\\
\cline{2-7}
 & Distance to LCB shelter (m) & 33.51 & 31.00 & 24.63 & 2.00 & 190.00\\
\cline{2-7}
 & HB visitation (hr$^{-1}$) & 112.79 & 24.00 & 187.30 & 0.00 & 1290.00\\
\cline{2-7}
 & LCB visitation (hr$^{-1}$) & 76.15 & 12.00 & 144.88 & 0.00 & 1272.00\\
\cline{2-7}
 & Bay Edge/Centre & 0.13 & 0.00 & 0.34 & 0.00 & 1.00\\
\cline{2-7}
 & Flower density (m$^2$) & 495.02 & 432.00 & 303.35 & 24.00 & 2686.40\\
\cline{2-7}
 & Pollen per stigma & 21.76 & 7.00 & 42.53 & 0.00 & 578.00\\
\cline{2-7}
 & Plant density (m$^2$) & 3.58 & 3.64 & 0.46 & 2.40 & 4.49\\
\cline{2-7}
 & Plant vegetative mass (g) & 30.32 & 25.19 & 21.16 & 1.18 & 144.32\\
\cline{2-7}
 & Plant seed mass (g) & 9.50 & 7.54 & 7.90 & 0.02 & 60.77\\
\cline{2-7}
 & Flowers per plant & 461.32 & 362.50 & 326.59 & 26.00 & 2712.00\\
\cline{2-7}
 & Pods per plant & 299.41 & 244.50 & 207.68 & 10.00 & 1410.00\\
\cline{2-7}
 & Seeds per pod & 16.40 & 16.60 & 5.52 & 1.80 & 30.60\\
\cline{2-7}
\multirow{-14}{*}{\raggedright\arraybackslash Seed} & Seed size (mg) & 3.43 & 3.42 & 0.88 & 1.04 & 5.59\\
\hline
\end{tabular}

\label{tab:dataSummary}
\end{table}

\clearpage

%\widetext
% \begin{center}
% \textbf{\large Appendix B: Supplementary information on visitation}
% \end{center}

\section*{Appendix B: Supplementary information on visitation}
\subsection*{Floral visitors in canola fields}

\begin{table}[h]
    \begin{tabular}{r|r|l|r|l}
     & \multicolumn{2}{c|}{Commodity fields} & \multicolumn{2}{c}{Seed fields} \\ \cline{2-5}
    Taxon & Visits & \% & Visits & \% \\ \hline
    Honey bee & 470 & 53.5 & 4850 & 77.1 \\
    Fly & 222 & 25.3 & 74 & 0.878 \\
    Hover fly & 94 & 10.7 & 151 & 1.79 \\
    Other bee & 47 & 5.35 & 30 & 0.356 \\
    Bumble bee & 25 & 2.85 & 0 & 0 \\
    Butterfly & 16 & 1.82 & 0 & 0 \\
    Leafcutter bee & 4 & 0.456 & 1675 & 19.9 \\
    % \hline
    % Total & 828 & - & 6780 & - \\
    \end{tabular}
    \caption{Number of flower visitors recorded over a total of 44.8 hours of observation in commodity fields (2014 and 2015), and 46.9 hours of observation in the seed fields (2015 and 2016). ``Fly" refers to larger calyptrate muscoid flies (families Muscidae, Anthomyiidae, Caliphoridae), while ``Hover fly" refers to Syrphid flies. ``Other bee" included Halictid and Andrenid bees, while ``Bumble bee" was \textit{Bombus} spp. ``Butterfly" refers to all visiting Lepidopterans, mostly Pierids.}
    \label{tab:propVisitors}  
\end{table}

\subsection*{Top-working and side-working by honey bees in canola fields}

During 2015, we recorded whether honey bees were top-working or side-working flowers (see also \citealp{free1973, free1983, mohr1988}).
Top-working bees landed on the top of the flower and inserted their proboscis down between the petals to access the nectaries of the flower, while side-working bees landed on the side of the flower and stole nectar by inserted their proboscis between the petals, avoiding contact with the stigma or anthers. 
Additionally, we recorded whether honey bees were pollen or nectar foragers (pollen foragers had a visible pollen load on their corbicula, while nectar foragers had none).

\begin{table}
\begin{tabular}{r|r|l|r|l|r|l}
               & \multicolumn{2}{c|}{Commodity fields} & \multicolumn{2}{c|}{Seed fields (female bay)} & \multicolumn{2}{c}{Seed fields (male bay)} \\ \cline{2-7}
               & Top & Side & Top & Side & Top & Side           \\ \hline
Pollen forager & 44 & 2 & 12 & 0 & 115 & 0 \\
Nectar forager & 75 & 138 & 832 & 24 & 428 & 242 \\
% Total & 119 & 140 & 844 & 24 & 543 & 242
\end{tabular}
\caption[Foraging behaviours of honey bees on commodity and seed canola flowers]{Foraging behaviours of honey bees on commodity and seed canola flowers, recorded during 2015. ``Top" (top-working) indicates that the bee inserted their proboscis down between the petals from the top of the flower, while ``side" (side-working) indicates that the bee fed from the side of the flower and did not contact the anthers or stigma. Pollen foragers had pollen visible on their corbicula, while nectar foragers had none.}
\label{tab:sideWorking}
\end{table}

Pollen- and nectar-foraging honey bees had different patterns of side-working, both on commodity canola, and the male and female lines of seed canola.
Side-working was common in nectar foragers, but was more common in commodity canola (64\%) than in the male (36\%) or female bays (2.8\%) of seed canola, indicating that a large proportion of honey bees foraging on canola flowers may never come in contact with the stigmas.
Pollen foragers were almost uniformly top-foragers in both commodity and seed fields (Table \ref{tab:sideWorking}), and pollen foragers were much less common in the female bays (1.4\%) than in the male bays (15\%), or in commodity fields (18\%).
Therefore, foraging honey bees in seed canola fields tend to treat male-fertile flowers similar to commodity canola flowers, but seem to top-work flowers more in commodity canola than seed fields.
Leafcutter bee foraging behaviours were not recorded, but seemed to almost exclusively top-work flowers in seed canola fields.

\clearpage

\section*{Appendix C: Supplementary information on models}

\subsection*{Commodity canola models}

Formulas for commodity canola model using \texttt{lmer}-style R formulas. Terms on right side of $\sim$ indicate fixed effects, while terms in brackets indicate random effects (heirarchical intercepts). \textit{distribution} indicates the type of probability distribution function used to model each variable.

\begin{align*}
    \text{Plant Density} \sim & \text{HB Distance} + (1|\text{Field}), \text{distribution = log-normal} \\
    \text{Plant Size} \sim & \text{Plant Density} + \text{HB Distance} + (1|\text{Field}),\text{distribution = log-normal} \\
    \text{Flower Density} \sim & \text{Plant Size} + \text{HB Distance} + \text{Plant Density} + (1|\text{Field}),\\
    &   \text{distribution = square root-normal} \\
    \text{HB Visits} \sim & \text{offset}(log(\text{Time})) + \text{HB Distance} + \text{Hive Stocking} + \\ 
    &   \text{Flower Density} + (1|\text{Field}), \text{family = negative binomial}\\
    \text{Pollen per Stigma} \sim & \text{HB Visits} + \text{HB Distance} + (1|\text{Field}), \text{distribution = negative binomial} \\
    \text{Flowers per Plant} \sim & \text{Plant Size} + \text{\% Pod Set} + (1|\text{Field}), \phi \sim \text{Plant Size}, \\
    &     \text{distribution = negative binomial} \\
    \text{\% Pod Set} \sim & \text{HB Visits} + \text{Pollen} + \text{Plant Size} + (1|\text{Field}), \text{distribution = beta-binomial} \\
    \text{Seeds per Pod} \sim & \text{HB Visits} + \text{Pollen} + \text{Plant Size} + \text{\% Pod Set} + \text{Flowers per Plant} + (1|\text{Field}),\\ 
    &   \text{distribution = exponential-normal} \\
    \text{Weight per Seed} \sim & \text{HB Visits} + \text{Pollen} + \text{Seeds per Pod} + \text{Plant Size} + \text{Plant Density} +\\
    &   \text{HB Distance} + \text{\% Pod Set} + \text{Flowers per Plant} + \text{Flower Density} + (1|\text{Field}),\\
    &   \text{distribution = exponential-normal} \\
\end{align*}

\subsection*{Seed canola models}

Formulas for seed canola model using \texttt{lmer}-style R formulas. Terms on right side of $\sim$ indicate fixed effects, while terms in brackets indicate random effects (heirarchical intercepts). \textit{distribution} indicates the type of probability distribution function used to model each variable.

\begin{align*}
    \text{Plant Density} \sim & \text{HB Distance} + (1|\text{Field}), \text{distribution = log-normal} \\
    \text{Plant Size} \sim & \text{HB Distance} + \text{Plant Density} + (1|\text{Field}) ,\text{distribution = log-t} \\
    \text{Flower Density} \sim & \text{HB Distance} + (1|\text{Field}), \text{distribution = square root-t} \\
    \text{LCB Visits} \sim & \text{offset}(log(\text{Time})) + \text{HB Distance} + \text{LCB Distance} + \text{Bay Centre} + \\
    &   \text{Flower Density} + (1|\text{Field}), \text{family = ZI negative binomial} \\
    \text{HB Visits} \sim & \text{offset}(log(\text{Time})) + \text{HB Distance} + \text{LCB Distance} + \text{Bay Centre} + \\
    &   \text{Flower Density} + (1|\text{Field}), \text{family = ZI negative binomial} \\
    \text{Pollen per Stigma} \sim & \text{HB Visits} + \text{LCB Visits} + \text{Bay Centre} + \text{HB Distance} + \text{LCB Distance} +\\
    &   \text{Flower Density} + (1|\text{Field}) + (1|\text{Plot}), \text{family = negative binomial} \\
    \text{Flowers per Plant} \sim & \text{Plant Size} + \text{Bay Centre} + \text{\% Pod Set} + (1|\text{Field}),\\
    &   \phi \sim \text{Plant Size}, \text{family = negative binomial} \\
    \text{\% Pod Set} \sim & \text{Pollen} + \text{Plant Size} + \text{Bay Centre} + \text{HB Distance} + \text{LCB Distance} + \\
    &   \text{Flower Density} + (1|\text{Field}) + (1|\text{Plot}), \text{family = beta-binomial} \\
    \text{Seeds per Pod} \sim & \text{Pollen} + \text{Plant Size} + \text{Bay Centre} + \text{HB Distance} + \text{Flower Density} +\\
    &   \text{\% Pod Set} + \text{Flowers per plant} + (1|\text{Field}), \text{family = negative binomial} \\
    \text{Weight per Seed} \sim & \text{Pollen} + \text{Seeds per Pod} + \text{Plant Size} + \text{LCB Distance} +\\
    &   \text{Plant Density} + (1|\text{Field}), \text{family = exponential-normal}\\
\end{align*}

\subsection*{Commodity canola model coefficients}

\begingroup\fontsize{9}{11}\selectfont

\begin{longtable}{l|l|r|r|r|r|r|l|r|r}
\hline
Model & Parameter & Mean & SD & Median & Min & Max & P-value & N$_{eff}$ & $\hat{R}$\\
\hline
\endfirsthead
\multicolumn{10}{@{}l}{\textit{(continued)}}\\
\hline
Model & Parameter & Mean & SD & Median & Min & Max & P-value & N$_{eff}$ & $\hat{R}$\\
\hline
\endhead
 & Intercept & 3.76 & 0.05 & 3.77 & 3.66 & 3.87 & $<$0.0001 & 855 & 1.005\\
\cline{2-10}
 & HB distance & 0.02 & 0.01 & 0.02 & 0.00 & 0.04 & 0.0868 & 10154 & 1.000\\
\cline{2-10}
 & Sigma & 0.31 & 0.02 & 0.31 & 0.28 & 0.34 & - & 5039 & 0.999\\
\cline{2-10}
\multirow{-4}{*}{\raggedright\arraybackslash Plant density} & Sigma (field) & 0.37 & 0.04 & 0.37 & 0.30 & 0.46 & - & 3774 & 1.000\\
\cline{1-10}
 & Intercept & 5.24 & 0.24 & 5.24 & 4.77 & 5.72 & $<$0.0001 & 2108 & 1.001\\
\cline{2-10}
 & Plant density & -0.70 & 0.06 & -0.70 & -0.82 & -0.57 & $<$0.0001 & 2097 & 1.001\\
\cline{2-10}
 & HB distance & 0.03 & 0.01 & 0.03 & 0.01 & 0.06 & 0.0095 & 9212 & 1.000\\
\cline{2-10}
 & Sigma (field) & 0.22 & 0.04 & 0.22 & 0.15 & 0.29 & - & 1456 & 1.000\\
\cline{2-10}
\multirow{-5}{*}{\raggedright\arraybackslash Plant size} & Sigma & 0.64 & 0.02 & 0.64 & 0.61 & 0.68 & - & 7845 & 0.999\\
\cline{1-10}
 & Intercept & 5.74 & 4.70 & 5.70 & -3.62 & 15.01 & 0.222 & 1822 & 1.001\\
\cline{2-10}
 & Plant size & -1.66 & 0.98 & -1.66 & -3.60 & 0.25 & 0.0926 & 1632 & 1.001\\
\cline{2-10}
 & HB distance & 0.75 & 0.11 & 0.75 & 0.53 & 0.96 & $<$0.0001 & 6878 & 1.000\\
\cline{2-10}
 & Plant density & -0.41 & 0.74 & -0.42 & -1.86 & 1.06 & 0.5792 & 2243 & 1.001\\
\cline{2-10}
 & Sigma & 3.52 & 0.17 & 3.51 & 3.19 & 3.87 & - & 4976 & 0.999\\
\cline{2-10}
\multirow{-6}{*}{\raggedright\arraybackslash Flower density} & Sigma (field) & 3.55 & 0.39 & 3.53 & 2.88 & 4.40 & - & 4133 & 1.000\\
\cline{1-10}
 & Intercept & -1.98 & 0.45 & -1.96 & -2.89 & -1.17 & $<$0.0001 & 936 & 1.006\\
\cline{2-10}
 & HB distance & -0.31 & 0.10 & -0.31 & -0.50 & -0.13 & 0.0011 & 3526 & 1.001\\
\cline{2-10}
 & Number of hives & 0.72 & 0.15 & 0.72 & 0.43 & 1.04 & $<$0.0001 & 1534 & 1.003\\
\cline{2-10}
 & Flower density & 0.03 & 0.04 & 0.03 & -0.06 & 0.12 & 0.541 & 2397 & 1.000\\
\cline{2-10}
 & Sigma (field) & 1.44 & 0.34 & 1.43 & 0.80 & 2.14 & - & 494 & 1.014\\
\cline{2-10}
\multirow{-6}{*}{\raggedright\arraybackslash HB visits} & Phi & 0.35 & 0.08 & 0.34 & 0.22 & 0.53 & - & 1630 & 1.003\\
\cline{1-10}
 & Intercept & 2.56 & 0.04 & 2.56 & 2.50 & 2.63 & $<$0.0001 & 594 & 1.006\\
\cline{2-10}
 & Plant size & 0.94 & 0.01 & 0.94 & 0.92 & 0.96 & $<$0.0001 & 1709 & 1.002\\
\cline{2-10}
 & Pods per plant & -0.16 & 0.01 & -0.16 & -0.19 & -0.14 & $<$0.0001 & 2108 & 1.003\\
\cline{2-10}
 & Phi (field) & 0.16 & 0.02 & 0.16 & 0.13 & 0.19 & - & 3461 & 1.000\\
\cline{2-10}
 & Intercept (Phi) & 2.17 & 0.32 & 2.17 & 1.56 & 2.81 & - & 1517 & 1.001\\
\cline{2-10}
 & Plant size (Phi) & 0.66 & 0.11 & 0.66 & 0.44 & 0.87 & - & 1587 & 1.002\\
\cline{2-10}
\multirow{-7}{*}{\raggedright\arraybackslash Flowers per plant} & SigmaPhi (field) & 0.66 & 0.12 & 0.65 & 0.45 & 0.90 & - & 844 & 1.005\\
\cline{1-10}
 & Intercept & 0.66 & 0.08 & 0.66 & 0.50 & 0.82 & $<$0.0001 & 1946 & 0.999\\
\cline{2-10}
 & HB visits & 0.00 & 0.03 & 0.00 & -0.05 & 0.05 & 0.96 & 3292 & 1.000\\
\cline{2-10}
 & Plant size & 0.13 & 0.03 & 0.13 & 0.08 & 0.18 & $<$0.0001 & 3345 & 1.000\\
\cline{2-10}
 & Pollen count & 0.16 & 0.11 & 0.15 & -0.05 & 0.38 & 0.1515 & 638 & 1.002\\
\cline{2-10}
 & Sigma (field) & 0.29 & 0.03 & 0.29 & 0.23 & 0.37 & - & 2675 & 1.000\\
\cline{2-10}
\multirow{-6}{*}{\raggedright\arraybackslash Pods per plant} & Phi & 3.35 & 0.07 & 3.35 & 3.21 & 3.48 & - & 3828 & 1.003\\
\cline{1-10}
 & Intercept & 25.07 & 1.77 & 25.07 & 21.64 & 28.54 & $<$0.0001 & 2277 & 1.000\\
\cline{2-10}
 & HB visits & 0.17 & 0.21 & 0.17 & -0.24 & 0.60 & 0.4284 & 4417 & 1.000\\
\cline{2-10}
 & Pollen count & -0.97 & 0.84 & -0.98 & -2.60 & 0.68 & 0.2447 & 707 & 1.003\\
\cline{2-10}
 & Plant size & 4.31 & 0.65 & 4.31 & 3.03 & 5.58 & $<$0.0001 & 2229 & 1.000\\
\cline{2-10}
 & Pods per plant & 0.56 & 0.29 & 0.56 & 0.00 & 1.12 & 0.0529 & 4888 & 0.999\\
\cline{2-10}
 & Flowers per plant & -2.80 & 0.65 & -2.79 & -4.08 & -1.55 & $<$0.0001 & 2105 & 1.000\\
\cline{2-10}
 & Sigma & 4.06 & 0.12 & 4.06 & 3.83 & 4.29 & - & 6604 & 1.000\\
\cline{2-10}
 & Sigma (field) & 1.98 & 0.26 & 1.96 & 1.51 & 2.53 & - & 2526 & 0.999\\
\cline{2-10}
\multirow{-9}{*}{\raggedright\arraybackslash Seeds per pod} & Lambda & 2.00 & 1.03 & 1.74 & 0.84 & 4.64 & - & 3265 & 1.000\\
\cline{1-10}
 & Intercept & 0.64 & 0.54 & 0.64 & -0.40 & 1.72 & 0.2367 & 1402 & 1.000\\
\cline{2-10}
 & HB visits & 0.02 & 0.04 & 0.02 & -0.05 & 0.09 & 0.6113 & 2748 & 1.000\\
\cline{2-10}
 & Pollen count & -0.15 & 0.17 & -0.15 & -0.48 & 0.20 & 0.3744 & 358 & 1.008\\
\cline{2-10}
 & Seeds per pod & 0.00 & 0.01 & 0.00 & -0.01 & 0.02 & 0.4508 & 3348 & 1.000\\
\cline{2-10}
 & Plant size & -0.03 & 0.12 & -0.03 & -0.26 & 0.20 & 0.7955 & 1633 & 1.000\\
\cline{2-10}
 & Plant density & 0.30 & 0.08 & 0.30 & 0.14 & 0.45 & 0.0001 & 1704 & 1.001\\
\cline{2-10}
 & HB distance & 0.02 & 0.01 & 0.02 & -0.01 & 0.05 & 0.1686 & 1404 & 1.003\\
\cline{2-10}
 & Pods per plant & 0.11 & 0.04 & 0.11 & 0.02 & 0.19 & 0.0159 & 3037 & 1.000\\
\cline{2-10}
 & Flowers per plant & 0.11 & 0.12 & 0.11 & -0.13 & 0.34 & 0.363 & 1526 & 1.000\\
\cline{2-10}
 & Flower density & -0.03 & 0.01 & -0.03 & -0.04 & -0.02 & $<$0.0001 & 2213 & 1.003\\
\cline{2-10}
 & Sigma & 0.52 & 0.03 & 0.52 & 0.46 & 0.59 & - & 2100 & 1.000\\
\cline{2-10}
 & Sigma (field) & 0.47 & 0.05 & 0.47 & 0.37 & 0.58 & - & 2828 & 0.999\\
\cline{2-10}
\multirow{-13}{*}{\raggedright\arraybackslash Seed size} & Lambda & 2.71 & 0.48 & 2.63 & 2.08 & 3.86 & - & 1792 & 1.001\\
\hline
\label{tab:commCoefs}
\end{longtable}
\endgroup{}

\subsection*{Seed canola model coefficients}

\begingroup\fontsize{9}{11}\selectfont

\begin{longtable}{l|l|r|r|r|r|r|l|r|r}
\hline
Model & Parameter & Mean & SD & Median & Min & Max & P-value & N$_{eff}$ & $\hat{R}$\\
\hline
\endfirsthead
\multicolumn{10}{@{}l}{\textit{(continued)}}\\
\hline
Model & Parameter & Mean & SD & Median & Min & Max & P-value & N$_{eff}$ & $\hat{R}$\\
\hline
\endhead
 & Intercept & 3.60 & 0.06 & 3.60 & 3.47 & 3.73 & $<$0.0001 & 524 & 1.004\\
\cline{2-10}
 & HB distance & 0.06 & 0.01 & 0.06 & 0.04 & 0.07 & $<$0.0001 & 5750 & 0.999\\
\cline{2-10}
 & Sigma & 0.27 & 0.01 & 0.27 & 0.24 & 0.30 & - & 5199 & 0.999\\
\cline{2-10}
\multirow{-4}{*}{\raggedright\arraybackslash Plant density} & Sigma (field) & 0.36 & 0.05 & 0.36 & 0.28 & 0.48 & - & 4182 & 1.000\\
\cline{1-10}
 & Intercept & 6.08 & 0.25 & 6.08 & 5.57 & 6.56 & $<$0.0001 & 2480 & 1.000\\
\cline{2-10}
 & Plant density & -0.79 & 0.07 & -0.80 & -0.92 & -0.66 & $<$0.0001 & 2470 & 1.000\\
\cline{2-10}
 & HB distance & 0.07 & 0.01 & 0.07 & 0.05 & 0.10 & $<$0.0001 & 6446 & 0.999\\
\cline{2-10}
 & Sigma & 0.50 & 0.03 & 0.50 & 0.45 & 0.56 & - & 2332 & 1.000\\
\cline{2-10}
 & Sigma (field) & 0.15 & 0.04 & 0.15 & 0.08 & 0.23 & - & 1053 & 1.001\\
\cline{2-10}
\multirow{-6}{*}{\raggedright\arraybackslash Plant size} & Nu (DF) & 1.91 & 0.32 & 1.87 & 1.37 & 2.65 & $<$0.0001 & 2700 & 1.000\\
\cline{1-10}
 & Intercept & 0.48 & 0.56 & 0.46 & -0.58 & 1.64 & 0.3827 & 661 & 1.005\\
\cline{2-10}
 & HB distance & 1.11 & 0.12 & 1.11 & 0.87 & 1.36 & $<$0.0001 & 5389 & 1.000\\
\cline{2-10}
 & Sigma & 4.06 & 0.24 & 4.05 & 3.59 & 4.56 & - & 2404 & 1.001\\
\cline{2-10}
 & Sigma (field) & 3.48 & 0.47 & 3.44 & 2.70 & 4.49 & - & 2640 & 1.001\\
\cline{2-10}
\multirow{-5}{*}{\raggedright\arraybackslash Flower density} & Nu (DF) & 1.88 & 0.38 & 1.84 & 1.30 & 2.68 & $<$0.0001 & 1500 & 1.004\\
\cline{1-10}
 & Intercept & 3.08 & 0.10 & 3.08 & 2.87 & 3.28 & $<$0.0001 & 2722 & 1.002\\
\cline{2-10}
 & Flower density & -0.01 & 0.01 & -0.01 & -0.03 & 0.01 & 0.5267 & 4150 & 1.000\\
\cline{2-10}
 & HB distance & -0.02 & 0.05 & -0.03 & -0.12 & 0.07 & 0.6229 & 4410 & 1.000\\
\cline{2-10}
 & LCB distance & 0.42 & 0.09 & 0.42 & 0.24 & 0.58 & $<$0.0001 & 5053 & 1.000\\
\cline{2-10}
 & Bay centre & 0.45 & 0.21 & 0.45 & 0.07 & 0.88 & 0.0284 & 6486 & 0.999\\
\cline{2-10}
 & Phi & 0.72 & 0.09 & 0.72 & 0.55 & 0.92 & - & 4354 & 1.001\\
\cline{2-10}
 & Theta (ZI) & 0.32 & 0.03 & 0.32 & 0.26 & 0.38 & - & 3955 & 1.001\\
\cline{2-10}
\multirow{-8}{*}{\raggedright\arraybackslash HB visits} & Sigma (field) & 0.41 & 0.11 & 0.41 & 0.22 & 0.64 & - & 600 & 1.001\\
\cline{1-10}
 & Intercept & 2.25 & 0.14 & 2.25 & 1.96 & 2.51 & $<$0.0001 & 1734 & 1.002\\
\cline{2-10}
 & LCB distance & -0.79 & 0.07 & -0.79 & -0.94 & -0.65 & $<$0.0001 & 4016 & 1.000\\
\cline{2-10}
 & HB distance & -0.32 & 0.06 & -0.32 & -0.43 & -0.21 & $<$0.0001 & 5128 & 1.000\\
\cline{2-10}
 & Bay centre & -0.34 & 0.23 & -0.34 & -0.77 & 0.16 & 0.1458 & 6667 & 1.000\\
\cline{2-10}
 & Flower density & 0.03 & 0.01 & 0.03 & 0.01 & 0.05 & 0.0115 & 4364 & 1.000\\
\cline{2-10}
 & Sigma (field) & 0.63 & 0.13 & 0.62 & 0.40 & 0.91 & - & 1072 & 1.004\\
\cline{2-10}
 & Phi & 0.70 & 0.11 & 0.69 & 0.50 & 0.93 & - & 3097 & 0.999\\
\cline{2-10}
\multirow{-8}{*}{\raggedright\arraybackslash LCB visits} & Theta (ZI) & 0.25 & 0.04 & 0.25 & 0.15 & 0.33 & - & 2383 & 1.000\\
\cline{1-10}
 & Intercept & 2.49 & 0.19 & 2.50 & 2.12 & 2.85 & $<$0.0001 & 1141 & 1.002\\
\cline{2-10}
 & HB visits & 0.05 & 0.04 & 0.05 & -0.03 & 0.12 & 0.195 & 2317 & 1.000\\
\cline{2-10}
 & LCB visits & 0.15 & 0.06 & 0.14 & 0.02 & 0.26 & 0.0155 & 2239 & 1.000\\
\cline{2-10}
 & Bay centre & -0.55 & 0.13 & -0.55 & -0.80 & -0.30 & $<$0.0001 & 2540 & 1.000\\
\cline{2-10}
 & HB distance & -0.17 & 0.04 & -0.17 & -0.25 & -0.09 & $<$0.0001 & 2265 & 1.003\\
\cline{2-10}
 & LCB distance & -0.35 & 0.14 & -0.35 & -0.63 & -0.07 & 0.0164 & 2513 & 1.000\\
\cline{2-10}
 & Flower density & -0.03 & 0.02 & -0.03 & -0.06 & 0.01 & 0.1284 & 2058 & 1.001\\
\cline{2-10}
 & Sigma (field) & 0.86 & 0.13 & 0.85 & 0.64 & 1.15 & - & 2978 & 1.000\\
\cline{2-10}
 & Sigma (plot) & 0.65 & 0.06 & 0.65 & 0.53 & 0.78 & - & 1142 & 1.003\\
\cline{2-10}
\multirow{-10}{*}{\raggedright\arraybackslash Pollen count} & Phi & 0.82 & 0.04 & 0.82 & 0.74 & 0.90 & - & 5125 & 0.999\\
\cline{1-10}
 & Intercept & 3.05 & 0.04 & 3.05 & 2.96 & 3.14 & $<$0.0001 & 3283 & 0.999\\
\cline{2-10}
 & Plant size & 0.93 & 0.01 & 0.93 & 0.90 & 0.95 & $<$0.0001 & 3712 & 0.999\\
\cline{2-10}
 & Bay centre & 0.09 & 0.02 & 0.09 & 0.06 & 0.12 & $<$0.0001 & 6790 & 0.999\\
\cline{2-10}
 & Pods per plant & -0.14 & 0.01 & -0.14 & -0.17 & -0.12 & $<$0.0001 & 5503 & 0.999\\
\cline{2-10}
 & Sigma (field) & 0.08 & 0.01 & 0.08 & 0.06 & 0.11 & - & 2649 & 1.000\\
\cline{2-10}
 & Intercept (Phi) & 2.24 & 0.32 & 2.24 & 1.62 & 2.87 & - & 2875 & 1.001\\
\cline{2-10}
\multirow{-7}{*}{\raggedright\arraybackslash Flowers per plant} & Plant size (Phi) & 0.38 & 0.10 & 0.39 & 0.19 & 0.57 & - & 2871 & 1.001\\
\cline{1-10}
 & Intercept & 0.18 & 0.12 & 0.18 & -0.05 & 0.40 & 0.1211 & 2261 & 1.000\\
\cline{2-10}
 & Pollen count & 0.12 & 0.04 & 0.12 & 0.03 & 0.20 & 0.0074 & 915 & 1.004\\
\cline{2-10}
 & Plant size & 0.19 & 0.03 & 0.19 & 0.14 & 0.24 & $<$0.0001 & 4570 & 1.000\\
\cline{2-10}
 & Bay centre & -0.21 & 0.06 & -0.21 & -0.33 & -0.10 & 0.0003 & 1886 & 1.000\\
\cline{2-10}
 & HB distance & -0.12 & 0.02 & -0.12 & -0.15 & -0.08 & $<$0.0001 & 1929 & 1.002\\
\cline{2-10}
 & LCB distance & -0.21 & 0.06 & -0.21 & -0.34 & -0.10 & 0.0005 & 2637 & 1.000\\
\cline{2-10}
 & Flower density & 0.00 & 0.01 & 0.00 & -0.02 & 0.01 & 0.5456 & 2998 & 1.000\\
\cline{2-10}
 & Sigma (plot) & 0.30 & 0.03 & 0.30 & 0.25 & 0.35 & - & 1367 & 1.004\\
\cline{2-10}
 & Sigma (field) & 0.37 & 0.06 & 0.36 & 0.27 & 0.49 & - & 2905 & 1.000\\
\cline{2-10}
 & Intercept (Phi) & 3.07 & 0.38 & 3.05 & 2.36 & 3.85 & - & 2268 & 1.004\\
\cline{2-10}
\multirow{-11}{*}{\raggedright\arraybackslash Pods per plant} & Plant size (Phi) & 0.22 & 0.12 & 0.22 & -0.01 & 0.44 & - & 2538 & 1.003\\
\cline{1-10}
 & Intercept & 25.38 & 2.29 & 25.48 & 20.64 & 29.38 & $<$0.0001 & 1651 & 1.001\\
\cline{2-10}
 & Pollen count & 1.21 & 0.32 & 1.20 & 0.61 & 1.87 & 0.0001 & 1046 & 1.002\\
\cline{2-10}
 & Plant size & 4.76 & 0.78 & 4.76 & 3.24 & 6.23 & $<$0.0001 & 1752 & 1.001\\
\cline{2-10}
 & Bay centre & -0.50 & 0.45 & -0.50 & -1.39 & 0.38 & 0.2639 & 5315 & 0.999\\
\cline{2-10}
 & HB distance & -0.02 & 0.12 & -0.01 & -0.25 & 0.21 & 0.881 & 3007 & 1.000\\
\cline{2-10}
 & Flower density & -0.11 & 0.06 & -0.11 & -0.23 & 0.00 & 0.0451 & 2596 & 1.000\\
\cline{2-10}
 & Pods per plant & 1.65 & 0.35 & 1.65 & 0.94 & 2.34 & $<$0.0001 & 2485 & 1.001\\
\cline{2-10}
 & Flowers per plant & -4.26 & 0.74 & -4.27 & -5.60 & -2.73 & $<$0.0001 & 1571 & 1.001\\
\cline{2-10}
 & Sigma & 4.25 & 0.16 & 4.25 & 3.92 & 4.56 & - & 2951 & 1.000\\
\cline{2-10}
 & Sigma (field) & 1.97 & 0.32 & 1.95 & 1.41 & 2.68 & - & 1767 & 1.002\\
\cline{2-10}
\multirow{-11}{*}{\raggedright\arraybackslash Seeds per pod} & Lambda & 1.67 & 1.00 & 1.39 & 0.60 & 4.28 & - & 2448 & 0.999\\
\cline{1-10}
 & Intercept & 1.17 & 0.50 & 1.18 & 0.21 & 2.16 & 0.0189 & 2004 & 1.001\\
\cline{2-10}
 & Pollen count & -0.02 & 0.05 & -0.02 & -0.12 & 0.08 & 0.7002 & 2345 & 1.000\\
\cline{2-10}
 & Seeds per pod & -0.01 & 0.01 & -0.01 & -0.03 & 0.00 & 0.0765 & 3719 & 0.999\\
\cline{2-10}
 & Plant size & 0.23 & 0.06 & 0.23 & 0.12 & 0.34 & $<$0.0001 & 3607 & 1.000\\
\cline{2-10}
 & Plant density & 0.41 & 0.11 & 0.41 & 0.20 & 0.63 & 0.0002 & 1988 & 1.000\\
\cline{2-10}
 & LCB distance & 0.07 & 0.07 & 0.07 & -0.06 & 0.22 & 0.3146 & 4466 & 1.000\\
\cline{2-10}
 & Sigma & 0.75 & 0.03 & 0.75 & 0.69 & 0.81 & - & 3533 & 1.000\\
\cline{2-10}
 & Sigma (field) & 0.36 & 0.06 & 0.35 & 0.25 & 0.49 & - & 2060 & 1.000\\
\cline{2-10}
\multirow{-9}{*}{\raggedright\arraybackslash Seed size} & Lambda & 4.44 & 1.22 & 4.23 & 2.70 & 7.42 & - & 2125 & 1.000\\
\hline
\label{tab:seedCoefs}
\end{longtable}
\endgroup{}

### 2022-08-03 Manuscript/main.tex
Moved supplementals to single file
Minor updates to manuscript

@@
 We assessed the underlying probability distribution functions of each model using posterior predictive checks \citep{gelman2013}, and found that the probability distributions were properly specified (p$\sim$0.5).
-p-values were calculated using the Z-scores (mean/SD) of the sampled posterior distributions; unless otherwise specified, p-values are lower than 0.05 (see Table \ref{tab:commCoef} and \ref{tab:seedCoef} for more detailed model summaries).
+p-values were calculated using the Z-scores (mean/SD) of the sampled posterior distributions; unless otherwise specified, listed model coefficents have a p-value less than 0.05, and are considered ``strong" effects where p-values are $<0.01$ (see Table \ref{tab:commCoef} and \ref{tab:seedCoef} for more detailed model summaries).
 % This means that while the average seed counts (per plant) were unbiased, the variance within a plant was not. 
@@
 Plant size had by far the strongest positive effect on the number of pods produced (see plant paths in Figure \ref{fig:allSEM}), and there was evidence of pod set suppressing flower production.
-Commodity canola plants produced fewer flowers than seed canola plants, and also produced fewer pods per plant overall.
-In both commodity and seed canola, plant size had a strong positive effect on the total number of flowers per plant as well as pod set (both p$<$0.001).
+Commodity canola plants produced fewer flowers than seed canola plants, and also produced fewer pods per plant overall (Table \ref{tab:dataSummary}).
+In both commodity and seed canola, plant size had a strong positive effect on the total number of flowers per plant as well as pod set.
 Pod set had a strong negative influence on total flowers per plant (p$<$0.0001) in both commodity and seed canola (both p$<<$0.0001), indicating that high pod set suppresses future flower production.
@@
 \bibliography{references}
-%\bibliography{\string{~/Documents/Papers/bibtexRefs/references}}
 
-\clearpage %Supplemental material
-\include{extra_supplemental}
-% \include{visitors_supplemental}
-% \include{models_supplemental}
+%Supplemental material
+\include{supplemental}
 

### 2022-08-04 Manuscript/main.tex
Worked on Results and Discussion

@@
 We also found that \textit{Megachile rotundata} visitation in seed canola strongly increased pollen deposition, but \textit{A. mellifera} visitation did not.
-This model serves as a step towards a mechanistic model of pollination services, and points to the contextual importance of pollination services in seed canola production.
+This model serves as a step towards a dynamic model of pollination services, and points to the contextual importance of pollination services in seed canola production.
 
@@
 
-\section{Introduction}
+\section*{Introduction}
 %SH: PARAGRAPH COULD BE REMOVED/SHORTENED FOR PAPER, BUT FINE FOR THESIS
@@
 However, most studies of how pollination relates to crop yield either examine each process independently, or omit intermediate steps in the sequence of events (but see \citealp{saez2018}), meaning that the relative importance of visitation and plant resources are unresolved.
-Structural equation models (SEM) provide a framework for empirical analysis of this sequence, as they allow underlying causal assumptions to be formally stated and tested \citep{shipley2009, grace2012}, provide insight into alternative mechanisms that may be at play, and are flexible in many of their assumptions \citep{clough2012}.
-SEMs represent an intermediate class of statistical models, occupying a space somewhere between regression-style models and dynamic or agent-based models, making them ideal for generating and testing sets of mechanistic hypotheses \citep{grace2006, kline2013}.
 Using both commodity and seed canola provides an opportunity to compare two plant varieties that differ strongly in their pollination requirements, using a similar type of structural model, while accounting for agricultural differences between varieties (spatial arrangement, planting density, irrigation).
@@
 
-\section{Methods}
+\section*{Methods}
 
-\subsection{Data collection}
+\subsection*{Data collection}
 From June through August of 2014 and 2015, we surveyed 29 commodity canola fields (14 in 2014, 15 in 2015) near Beaverlodge, Alberta and 31 fields (17 in 2014, 14 in 2015) near Lethbridge, Alberta.
@@
 
-\subsection{Analysis}
+\subsection*{Analysis}
 To examine how yield is influenced by visitation, we used piecewise structural equation models (pSEM, \citealp{shipley2009}).
-Structural equation models are a set of linear models arranged in a causal network, which provides a framework for testing hypotheses about complex systems \citep{grace2012, lefcheck2015}.
+Structural equation models (SEMs) are a set of linear models arranged in a causal network, which provides a framework for testing hypotheses about complex systems \citep{grace2012, lefcheck2015}.
+SEMs provide a framework for empirical analysis of complex systems, as they allow causal relationships to be formally tested, can provide insight into alternative mechanisms, and are flexible in their assumptions \citep{shipley2009,clough2012, grace2012}.
+SEMs represent an intermediate class of statistical models, occupying a space somewhere between linear regression (or machine learning) models and dynamic linear models, making them ideal for generating and testing relationships between large sets of variables \citep{grace2006, kline2013}.
 Starting with a simple model (visitation $\rightarrow$ pollen deposition $\rightarrow$ fruit production $\leftarrow$ plant resources), we built a detailed model relating visitation to pollination to seed yield within a causal framework (see Figure \ref{fig:allSEM} in Results).
-These models let us model how visitation ultimately influences seed yield, while controlling for other confounding factors (e.g. distance into field, measurements taken at different fields).
-Pod set can suppress future vegetative growth and flower production \citep{stephenson1981}, but SEMs do not allow for causal loops \citep{grace2012}, so we included a path from pod set to flower production as the closest approximation of this process.
-The direction of the path could be reversed, implying that large flower production reduces the proportion of pod set, but we considered only the first scenario, as \citet{sabbahi2006} showed that low pod set increases flower production.
+After the models were properly fit and validated, we simulated seed size and yield at varying distances from pollinators, using the coefficients for each path in order to show the integrated effect of pollination on yield (while holding plant density constant).
+% These SEMs let us model how visitation ultimately influences seed yield, while controlling for other confounding factors (e.g. distance into field, measurements taken at different fields).
 
@@
 GLMMs can model processes that occur at different levels; for example, seed size was modelled at the plant level, while pollen deposition was modeled at the flower level.
+Random intercepts were used to model variance at the field level and plot level, but plot-level variance terms had poor traces and low effective sample sizes, so we omitted plot-level random effects for all models (except for pollen count and pod set in seed fields, see Table \ref{tab:seedCoefs}).
+Visitation models used $log$(time) as an ``offset" variable to account for differences in observation times.
+We observed LCBs directly harassing HBs during the plot-level observations, attacking HBs both on the flowers and in the air (also seen by \citealp{batra1978} and \citealp{waytesMsc}), but HBs were never the aggressor in these interactions, so we treated LCB vistation as a potential cause of HB visitation (Figure \ref{fig:allSEM}).
+Pod set can suppress future vegetative growth and flower production \citep{stephenson1981}, but SEMs do not allow for causal loops \citep{grace2012}, so we included a path from pod set to flower production as the closest approximation of this process.
+The direction of the path could be reversed, implying that large flower production reduces the proportion of pod set, but we considered only the first scenario, as \citet{sabbahi2006} showed that low pod set increases flower production.
+Plant and pollen samples were not collected from male bays in seed fields, and there were no large differences in visitation rates for honey bees or LCBs (p = 0.32, 0.72, respectively) once other terms were included as covariates, so bay identity was excluded from further analysis.
+See Equation sets S1 and S2 for model specifications) Table \ref{tab:dataSummary} for a brief summary of the variables used in each SEM.
 % Random intercepts were used to model variance between fields, within-field (pollen, flower survival, seed count \& size), and within-plot (seed count \& size).
-Random intercepts were used to model variance at the field level and plot level, but plot-level variance terms had poor traces and low effective sample sizes, indicating low variation within plots.
-Therefore, we omitted plot-level random effects for the commodity field models of pollen deposition, flower survival, seeds per pod, and seed size, and omitted them from the seed field models of seeds per pod and seed size.
 % Continuous responses were modeled using log-normal (plant density, plant size), square-root normal (flower density), and exponential-normal distributions (weight per seed), while counts were modeled as a negative-binomial (honey bee visits, pollen grains per stigma, flowers per plant, seeds per pod) or zero-inflated negative-binomial distribution (LCB visits) with a log-link function.
 (Move to appendix)
-Visitation models used $log$(time) as an ``offset" variable to account for differences in observation times.
-Plant and pollen samples were not collected from male bays in seed fields, and there were no large differences in visitation rates for honey bees or LCBs (p = 0.32, 0.72, respectively) once other terms were included as covariates, so bay identity was excluded from further analysis.
-See Equation sets S1 and S2 for model specifications) Table \ref{tab:dataSummary} for a brief summary of the variables used in each SEM
 % Pod set (fraction of flowers that matured into pods) was modeled using a beta-binomial distribution with a logit-link function.
-% Interactions between predictors were evident in honey bee visitation rate (Year:Locality interaction) and plant density (Irrigation:Year) in commodity canola, and for LCB visitation (Tent Stocking:Distance from edge) in seed canola, and were included in each model (represented as Y-shaped path in Figures \ref{fig:allSEM} and \ref{fig:allSEM}).
 
@@
 
-All component GLMMs of the pSEM were written in Stan 2.18.1 \citep{gelman2015} and run using \texttt{rstan} 2.26.13.
+All component GLMMs of the pSEM were written in Stan 2.18.1 and run using \texttt{rstan} 2.26.13 \citep{gelman2015,Rstan}.
 We used weakly informative normal priors ($\mu=0, \sigma=5$) for fixed effects and gamma priors ($\alpha=1, \beta=1$) for the variance components.
 Four separate chains were run with an adaptive phase of 1000 iterations, and a sampling phase of 1000 iterations, then checked for convergence of the chains ($\hat{R} \approx$1) and low autocorrelation within chains (high $N_{eff}$).
-We assessed the underlying probability distribution functions of each model using posterior predictive checks \citep{gelman2013}, and found that the probability distributions were properly specified (p$\sim$0.5).
-p-values were calculated using the Z-scores (mean/SD) of the sampled posterior distributions; unless otherwise specified, listed model coefficents have a p-value less than 0.05, and are considered ``strong" effects where p-values are $<0.01$ (see Table \ref{tab:commCoef} and \ref{tab:seedCoef} for more detailed model summaries).
-% This means that while the average seed counts (per plant) were unbiased, the variance within a plant was not. 
-% However, the negative binomial distribution had the closest posterior predictive checks of any other distribution. 
-% Predictions from models are median values of the posterior, representing the median prediction, while intervals displayed in figures are credible intervals (CIs), representing 95\% of the samples drawn from the posterior distribution (analogous to confidence intervals, see \citealt{gelman2013}).
+We assessed the underlying probability distribution functions of each model using posterior predictive checks \citep{gelman2013}, and found that the probability distributions were properly specified (i.e.
+simulated data was close to actual data).
+p-values were calculated using the Z-scores (mean/SD) of the sampled posterior distributions; unless otherwise specified, listed model coefficents have a p-value less than 0.05, and are considered ``strong" effects where p-values are $<0.01$ (see Table \ref{tab:commCoefs} and \ref{tab:seedCoefs} for more detailed model summaries).
+Predictions from models are taken from median values of the posterior, while uncertainty is derived from the 95\% credible intervals (CIs).
+Figures were made using \texttt{ggplot2} and \texttt{ggpubr} \citep{wickham2016,kassambara2020}.
 
-\section{Results}
+\section*{Results}
 
-\subsection{Overall path analysis}
+\subsection*{Path analysis}
 
@@
     \centering
-    \includegraphics[width=0.9\textwidth,keepaspectratio=true]{../Figures/allSEM.png}
+    \includegraphics[width=\textwidth,keepaspectratio=true]{../Figures/allSEM.png}
     \caption{Results of path analysis in commodity and seed fields.
 The width of each arrow is proportional to the effect size of each component path (number also displayed).
-Transparent arrows show path coefficients whose 95 posterior intervals overlapped zero.}
+Transparent arrows show path coefficients whose 95\% posterior intervals overlapped zero.}
     \label{fig:allSEM}
@@
 
-\subsection{Visitation}
+\subsection*{Visitation}
 
@@
 In commodity fields, HB visitation decreased from 12 visits/hr at the edge to 1.8 visits/hr at 400 m into the field (Figure \ref{fig:allVisits}a, apiary of 40 hives).
-% Visitation rates were higher in both years in Lethbridge (2014: 9.3 visits/hr, 2015: 7.1), but were higher in 2015 than 2014 at Grande Prairie (Z=2.3, p$=$0.02), rising from 5 visits/hr at the field edge in 2014 to 17 visits/hr in 2015.
-% (at a stocking level of 20 hives).
 Lower stocking rates decreased HB visitation at the edge of the field to 7.4 visits/hr at 20 hives, while unstocked field edges had an average of 0.8 visits/hr.
@@
 Visitation was also much lower near LCB shelters, dropping from 81 visits/hr at 20 m to 31 at 2 m (Figure \ref{fig:allVisits}b), likely due to competition with LCBs.
+% Visitation rates were higher in both years in Lethbridge (2014: 9.3 visits/hr, 2015: 7.1), but were higher in 2015 than 2014 at Grande Prairie (Z=2.3, p$=$0.02), rising from 5 visits/hr at the field edge in 2014 to 17 visits/hr in 2015.
+% (at a stocking level of 20 hives).
 
@@
 Interestingly, LCB visitation decreased from 119 visits/hr at the edge of the field to 25 at the centre.
-% However, there was no difference in visitation rates between the edge and the centre when LCB cocoon stocking was lower (Z=2.2, p$=$0.028), indicating that LCBs at high stocking densities likely aggregate in shelters close to the edge of the field (Figure \ref{fig:hbeeDist_both}).
-% There was no difference in visitation rates between the male bay and the edge of the female bays (LCB: p$=$0.72, HB: p$=$0.32). 
 The difference in LCB visitation between the edge and centre of the female bays was weak (p=0.14), while HB visitation was higher (88 vs.
 139 visits/hr, Figure \ref{fig:allVisits}), indicating that pollination is likely done by different species in different parts of the field.
+% There was no difference in visitation rates between the male bay and the edge of the female bays (LCB: p$=$0.72, HB: p$=$0.32). 
+% However, there was no difference in visitation rates between the edge and the centre when LCB cocoon stocking was lower (Z=2.2, p$=$0.028), indicating that LCBs at high stocking densities likely aggregate in shelters close to the edge of the field (Figure \ref{fig:hbeeDist_both}).
 %Therefore, visitation by both species strongly decreases with distance from the edge of the field, decreases with distance from the leafcutter shelters in seed canola fields, and is done by different bees at the centre of the female bay.
@@
     \centering
-    \includegraphics[width=0.9\textwidth,keepaspectratio=true]{../Figures/allVisits.png}
+    \includegraphics[width=\textwidth,keepaspectratio=true]{../Figures/allVisits.png}
     \caption{Effect of distance from a) honey bee apiaries, b) leafcutter shelters, and c) female bay position on visitation rates.
@@
 
-\subsection{Pollen Deposition}
+\subsection*{Pollen Deposition}
 
@@
 Pollen deposition declined weakly with distance from the edge of the field (p$=$0.09), but this only amounted to a 6\% average decrease (290 grains/stigma at the field edge vs. 240 at field centre).
-% Flies were also common visitors in commodity fields (Table \ref{tab:propVisitors}), but had no effect on pollen deposition (p$=$0.577), so only honey bees and LCBs were considered as potential pollinators (other flower visitors were rare).
 In seed canola, pollen deposition was much lower overall (mean: 22 grains per stigma, SD: 43, range: 0--578), and decreased from 26.3 grains/stigma at the edge to 11.5 at the centre of the field (Figure \ref{fig:allPollen}b) independent of visitation.
@@
 Pollen deposition also decreased from 15 grains/stigma at the edge of the female bay to 9 at the centre of the bay independent of visitation, suggesting that pollen may be lost from bees crossing over from male bays.% \citep{pinnisch1990}.%, who likely visit flowers at the edge of the bay first.
+% Flies were also common visitors in commodity fields (Table \ref{tab:propVisitors}), but had no effect on pollen deposition (p$=$0.577), so only honey bees and LCBs were considered as potential pollinators (other flower visitors were rare).
 
@@
     \centering
-    \includegraphics[width=0.9\textwidth,keepaspectratio=true]{../Figures/allPollen.png}
+    \includegraphics[width=\textwidth,keepaspectratio=true]{../Figures/allPollen.png}
     \caption{Effect of a) visitation rate, b) distance from apiary (HB) or shelter (LCB), and c) female bay position on pollen deposition.}
@@
 
-\subsection{Seed Production}
+\subsection*{Seed Production}
 
@@
     \centering
-    \includegraphics[width=0.9\textwidth,keepaspectratio=true]{../Figures/allSeeds.png}
+    \includegraphics[width=\textwidth,keepaspectratio=true]{../Figures/allSeeds.png}
     \caption{Effect of pollen deposition (top row) and plant size (bottom row) on flower survival, seeds per pod, and seed size.}
@@
 
-Plant size had by far the strongest positive effect on the number of pods produced (see plant paths in Figure \ref{fig:allSEM}), and there was evidence of pod set suppressing flower production.
-Commodity canola plants produced fewer flowers than seed canola plants, and also produced fewer pods per plant overall (Table \ref{tab:dataSummary}).
-In both commodity and seed canola, plant size had a strong positive effect on the total number of flowers per plant as well as pod set.
-Pod set had a strong negative influence on total flowers per plant (p$<$0.0001) in both commodity and seed canola (both p$<<$0.0001), indicating that high pod set suppresses future flower production.
-Finally, commodity plants were also lower-yielding (mean: 6.8 g of seeds per plant, SD: 6.0, range: 0.01--47.9) than seed canola plants (mean: 9.6, SD: 7.9, range: 0.02--60.8).
-However, the harvest index of commodity canola (mean: 0.26, SD: 0.08, range: 0.005--0.65) was higher than seed canola (mean: 0.23, SD: 0.09, range: 0.003--0.55), meaning that commodity plants produced more seeds per gram of biomass than seed canola plants.%, likely due to the lack of pollen limitation.
+Commodity canola produced fewer flowers per plant than seed canola (mean: 196 vs. 461), and also produced fewer pods per plant (143 vs. 299, Table \ref{tab:dataSummary}).
+Commodity canola also produced more seeds per pod than seed plants (mean: 23 vs 16), but seed size was lower in commodity canola (2.74 vs 3.43 mg/seed). 
+Finally, commodity plants were also lower-yielding than seed canola plants (mean: 6.8 vs 9.5 g seed per plant), but produced more seeds per gram of vegetative biomass than seed canola plants (mean: 0.38 vs.
+0.32), likely due to lower pollen limitation.
 
-Plant size had a positive effect on seed size and seeds per pod in seed canola, but not in commodity canola. 
-The relationship between seed size and number was negative in seed canola but positive in commodity canola.
-Commodity canola plants produced more seeds per pod (mean: 23.0 seeds per pod, SD: 7.4) than seed canola (mean: 16.3 seeds per pod, SD: 9.1), 
-but seed size was lower in commodity canola (mean: 2.74 mg/seed, SD: 1.04) than seed canola mean (mean: 3.59 mg/seed, SD: 1.33).
-In commodity canola, plant size did not affect seeds per pod or seed size (p=0.32) or seed size (Z=-0.40, p=0.69, Figure \ref{fig:allSeeds}), but seed size was positively related to seeds per pod (Z=6.1, p$<$0.0001, Figure \ref{fig:allSeeds}).
-In seed canola, however, seed size increased with plant size (Z=4.7, p$<$0.0001, Figure \ref{fig:allSeeds}), decreased with seeds per pod (Z=-13.1, p$<$0.0001), and interestingly, increased with plant density (Z=2.9, p$=$0.004), suggesting resource limitation at both the pod and the plant level.
-There were also between-year differences in seeds per pod (commodity canola only: Z=4.7, p$<$0.0001, 21.7 seeds per pod in 2014, 24.6 in 2015) and seed size (commodity canola: Z=2.2, p=0.031, 2.04 mg/seed in 2014, 2.31 mg/seed in 2015; seed canola: Z=3.6, p=0.0003, 3.11mg/seed in 2015, 3.59mg/seed in 2016), pointing to differences in overall growing conditions between years.
+Plant size had by far the strongest positive effect on the number of pods produced, and there was evidence of pod set suppressing flower production (see plant paths in Figure \ref{fig:allSEM}), but pollen only directly affected production in seed canola.
+In both commodity and seed canola, plant size had a strong positive effect on the total number of flowers per plant as well as \% pod set (Figure \ref{fig:allSeeds} bottom row), but did not increase seed size in commodity canola.
+Plant density also had a positive direct effect on seed size in both crops, indicating that areas with better resources can support better-provisioned (but smaller) plants.
+Pod set also had a strong negative influence on flowers per plant in both crop types, indicating that high pod set suppresses future flower production.
 
-% \subsection{Prediction 4: Pollinated plants produce more seeds}
-% 
-% Pollen deposition increased fruit production and seed production in seed canola, but not in commodity canola.
-% Pollen deposition had no effect on pod set (p=0.12), seeds per pod (p=0.94) or seed size (p=0.56) in commodity canola, and there was also no direct effect of honey bee visitation on pod set (p=0.38), seeds per pod (p=0.55), or seed size (p=0.34).
-% Seed canola, in contrast, was highly dependent on pollen deposition.
-% Pollen deposition increased pod set (Z=3.1, p$=$0.002), and seeds per pod (Z=2.3, p$=$0.02), but had no direct effect on seed size (p$=$0.35).
-% Pod set also decreased with three types of distance: distance into the field (Z=-5.3, p$<$0.0001), distance from leafcutter shelters (Z=-3.2, p$=$0.002), and distance from the edge of the female bay (Z=-4.0, p$=$0.0001).
-% Seeds per pod decreased in the centre of the female bay (Z=-4.6, p$<$0.0001), and was higher in plants with high pod set (Z=6.0, p$<$0.0001).
+Pollen deposition did not alter seed production in commodity canola, nor was there a direct effect of honey bee visitation or distance from field edge (note log-scaled x-axis on Figure \ref{fig:allSeeds}).
+Pod set and seeds per pod in seed canola were increased by higher pollen deposition, and decreased with distance away from HB hives as well as distance from LCB shelters.
+Pod set was also lower in the centre of the female bay, again suggesting that pollen is lost when bees crossing over from male bays.
 
-\section{Discussion}
-%LH: DISCUSSION TOO NARROWLY FOCUSED. WHAT ARE THE BROADER IMPLICATIONS? CONTAINS A LOT OF SPECULATION WITHOUT ANY EVIDENCE/REFERENCES
-%SH: RELATE RESULTS TO HYPOTHESES, AND START WITH BIG PICTURE IN ORDER TO DISCUSS
-This study examined the relative strength of the path between visitation, pollination, and yield, in two types of canola crops, and showed a strong path between visitation and yield in seed canola, but not in commodity canola.
-First, honey bee and LCB visitation decreased with distance from their hive or shelter, but unexpectedly, LCBs visited more frequently at the edge of the field.
-Secondly, honey bees had little (direct) influence on pollen deposition in either crop type, LCBs had a positive effect on pollen deposition in seed canola.
-Finally, the model revealed that commodity canola production is largely limited by plant size, while seed canola production is limited by both pollen and plant size.
+\subsection*{Yield simulations}
 
-\subsubsection{Bee visitation} 
-Honey bee visitation in both field types declined with distance into the field, but overall visitation was much higher than commodity fields, due to the higher honey bee stocking rate used in seed fields (3.6 vs.
-mean 0.6 hives/ha).
-Since honey bees travel from their hive outside the edge of the field, this decline was not surprising, but we did not expect the similar decrease observed in LCB visitation with distance into the field, as their shelters are located \textit{within} the field.
-This decrease with distance into the field may have been caused by LCBs migrating from shelters at the centre of the field to the edge \citep{goerzen1995}.
-Like honey bees, female LCBs are central-place foragers, and tend to not forage far from their nests \citep{peterson2005,pitts2011, brunet2019}.
-However, LCBs are not as constrained to their nest site as honey bees, and can drift between shelters in a given field \citep{goerzen1995, pittsSinger2013}.
-LCBs must also forage for leaf materials to create cocoons, but they prefer to build cocoons out of thinner, non-canola leaf types, mainly plants in the families Fabaceae and Rosaceae \citep{sinu2018}.
-Seed canola fields have very few weeds within the area of the crop, meaning that LCBs at the centre of the field may have few choices of leaf material, or alternative pollen and nectar sources.
-Therefore, LCBs likely move from the shelters at which they were released in the centre of the field to the shelters at the edge of the field, so as to gain access to better leaf material \citep{horne1995}, which is more available off-field, or to better forage for off-field pollen or nectar \citep{horne1995b}.
-This would explain why greater visitation occurred at the edge of the field, and may also explain why this pattern was not seen in fields with half-stocked shelters.
-To test this, a mark-recapture study of female LCBs could be done to see if bees migrate to shelters at the edge of the field, or if visitation is higher due to other reasons (\textit{e.g.} feral populations migrating to edge of field, long-distance foraging from centre of field as in \citealp{peterson2005}).
+The path analysis simulations further confirmed the results of the analysis: HB visitation had little effect on yield in either crop type, but LCB visitation improved yield in seed crops.
+The simulations showed no large effect of HB stocking on seed size or total yield in commodity fields (Figure \ref{fig:allYield}a, b), aside from the effect associated with distance from the edge of the field.
+Similarly, the simulations for seed fields showed a small increase in seed size and total yield with distance from the HB hives at the field edges, but the effect of distance from the leafcutter shelters was much more dramatic (compare the spacing of isolines along the x-axis and y-axis in Figures \ref{fig:allYield}c, d).
+A second set of simulations were run only in seed fields, in order to compare the effect of pollinator distances between the bay edge and centre. 
+This revealed that not only total seed size and overall yield lower at the bay centre, but that the effect of HB distance is effectively \emph{nil} at the bay centre (yield isolines are essentially horizontal in bay centre, and slightly tilted at the bay edge, Figure \ref{fig:allYield_bayCent} second column).
+Interestingly, the simulations also showed evidence of nonlinear behaviour occurring in the centre of seed field bays, where a local minima in yield appears at approximately 25 m away from HB hives and 45 m away from LCB shelters (Figure \ref{fig:allYield_bayCent}) bottom-right panel), likely because of an interaction between seeds per pod, pod count, and seed weight.
+
+\begin{figure}
+    \centering
+    \includegraphics[width=\textwidth,keepaspectratio=true]{../Figures/allYield.png}
+    \caption{Effect of honey bee distance and leafcutter distance on seed size (mg/seed, panels a \& c) and total yield (t/ha, panels b \& d), using coefficients from paths for simulation, while holding plant density constant at its mean value.
+Shaded areas shown in a \& b are 95\% quantiles for the simulations.
+Lines on panels c \& d are isolines of constant seed size (c) or yield (d).}
+    \label{fig:allYield}
+\end{figure}
+
+\begin{figure}
+    \centering
+    \includegraphics[width=\textwidth,keepaspectratio=true]{../Figures/allYield_bayCent.png}
+    \caption{Simulation results from seed field models, showing seed size and yield (first and second rows, respectively) for plots at the edge and centre of female bays (first and second column), at varying distances away from HB hives and LCB shelters.}
+    \label{fig:allYield_bayCent}
+\end{figure}
+
+\section*{Discussion}
+
+This study examined how visitation contributes to pollen deposition and seed yield in two canola crops, and showed a strong link between visitation and yield in seed canola, but not in commodity canola.
+HB and LCB visitation decreased with distance from their respective hive or shelter, but unexpectedly, LCBs were found more at the edge of the crop.
+HB visitation had little direct influence on pollen deposition in either crop type, while LCB visitation had a positive effect on pollen deposition in seed canola.
+We found that commodity canola production is largely limited by plant size, while seed canola production is limited by both pollen and plant size.
+Finally, our simulation results from the path analyses confirmed this, and showed the strong influence of LCB visitation on seed size and yield.
+These results provide more realistic information on the value of pollination services in commodity and seed canola crops, and show how a statistical-mechanistic model of seed production provides richer insite into the process of seed production than linear models alone.
+
+\subsection*{Bee visitation}
+
+HB visitation in both field types declined with distance into the field, but overall visitation was much higher than commodity fields, due to the higher HB stocking rate used in seed fields (3.6 vs.
+0.6 hives/ha).
+Since HBs travel from their hive outside the edge of the field, this decline was not surprising, but we did not expect a similar decrease in LCB visitation with distance into the field, as their shelters are located \textit{within} the field.
+This decrease with distance into the field may have been caused by LCBs migrating from shelters at the centre of the field to the edge \citep{goerzen1995}, as female LCBs are central-place foragers, and tend to not forage far from their nests \citep{peterson2005,pitts2011, brunet2019}.
+However, LCBs are not as constrained to a single nest as HBs are, and can drift between shelters within a given field \citep{goerzen1995, pittsSinger2013}.
+LCBs must also forage for leaf materials to create cocoons, but prefer thinner, non-canola leaf types, mainly plants in the families Fabaceae and Rosaceae \citep{sinu2018}.
+Since seed canola fields have very few weeds within the area of the crop, LCBs at the centre of the field may have few choices of leaf material, or alternative pollen and nectar sources.
+Therefore, LCBs likely move from the shelters at which they were released to the shelters at the edge of the field, so as to gain access to better leaf material or different sources of pollen and nectar \citep{horne1995, horne1995b}.
+% To test this, a mark-recapture study of female LCBs could be done to see if bees migrate to shelters at the edge of the field, or if visitation is higher due to other reasons (\textit{e.g.} feral populations migrating to edge of field, long-distance foraging from centre of field as in \citealp{peterson2005}).
 %SH: FINE FOR THESIS, BUT CAN BE REMOVED FOR MANUSCRIPT
-It would be interesting to see if there is a critical threshold of LCB density per-shelter that causes them to move to shelters at the edge of the field (similar to \citealp{pittsSinger2013}).
-%Honey bees visited flowers at the edge of the field more frequently than those in the middle of the field, as predicted for central-place foragers with nesting aggregations outside the field (\citealp{olsson2014}, see Chapter 2).
-%Similarly, the high concentration of canola nectar (\citealp{mohr1990}, 58.3\% brix from Chapter 2) may cause leafcutter bees to choose more diluted nectar under hot and dry conditions, similar to honey bees \citep{ohguchi1983}.
+% This would explain why LCB visitation was higher at the edge of the field, and may also explain why this pattern was not seen in fields with half-stocked shelters.
+% It would be interesting to see if there is a critical threshold of LCB density per-shelter that causes them to move to shelters at the edge of the field (similar to \citealp{pittsSinger2013}).
+%HBs visited flowers at the edge of the field more frequently than those in the middle of the field, as predicted for central-place foragers with nesting aggregations outside the field (\citealp{olsson2014}, see Chapter 2).
+%Similarly, the high concentration of canola nectar (\citealp{mohr1990}, 58.3\% brix from Chapter 2) may cause leafcutter bees to choose more diluted nectar under hot and dry conditions, similar to HBs \citep{ohguchi1983}.
 % canola pollen is valuable to bees \citep{mohr1988,huang2004},
@@
 %Leafcutter-honeybee interactions
-Honey bee visitation in hybrid seed fields was lower at areas near to leafcutter shelters. 
-This may have been driven by avoidance of nectar and pollen competition near shelters, as areas close to leafcutter shelters may become depleted in nectar and pollen, deterring honey bee visitation (similar to \citealp{currie1997}).
-Honey bees also suffer from direct interference by LCBs near to their shelters.
-Several times during the study, \textit{M.
-rotundata} females and males directly harassed honey bees during the plot-level observations, tackling honey bees both on the flowers and in the air (also seen by \citealp{batra1978} and \citealp{waytesMsc}).
-Honey bees were never the aggressor in these interactions, so interference between LCBs and honey bees may be unidirectional, at least in areas near LCB shelters. 
-For this reason, we treated high leafcutter visitation as causing lower honey bee visitation in our SEM (Figure \ref{fig:allSEM}, arrow from leafcutter visit rate to honey bee visit rate).
+In seed fields, LCB visitation was higher, and HB visitation was correspondingly lower in areas close to LCB shelters. 
+Lower HB visitation may have been driven by lower nectar and pollen resources, as areas close to leafcutter shelters can become depleted in nectar and pollen \citep{currie1997}.
+HBs also suffer from direct interference by LCBs near to their shelters; during the study we observed LCBs directly harassing HBs during the plot-level observations, attacking HBs both on the flowers and in the air (also seen by \citealp{batra1978} and \citealp{waytesMsc}).
+HBs were never the aggressor in these interactions, so we treated high leafcutter visitation as the cause of lower HB visitation in our SEM (Figure \ref{fig:allSEM}, arrow from leafcutter visit rate to HB visit rate).
 
-Honey bee visitation and foraging behaviour varied strongly between the male and female bays of seed fields, as well as within the female bays.
-Visitation rates of honey bee foragers were almost twice as high in the centre of the female bay, and conversely, LCB visitation was almost twice as low.
-This could be due to LCBs avoiding competition for nectar with honey bees, but more likely reflects a stronger need for pollen among LCBs than honey bees \citep{cane2011}.
-Only 1.4\% of the honey bees in the female bay were pollen foragers (Table \ref{tab:sideWorking}), meaning that foragers who have (recently) come into contact with pollen rare.
-Both \citet{waytesMsc} and \citet{gaffney2019} showed that honey bees exhibit floral fidelity during foraging trips, with minimal crossing between male and female bays ($\sim$5\% of observations, \citealp{waytesMsc}), limiting pollen transfer between the male and female flowers.
-Side-working was a very common behaviour among honey bees in commodity fields (65\% of the total visits from honey bees during 2015 were side-working), as well as the male bays of seed fields (36\%), but not in the female bays (3\%, Table \ref{tab:sideWorking}).
-This behaviour is relatively common on male-fertile flowers of \textit{Brassica} \citep{free1973,free1983,delbrassine1988,mohr1988} as well as other flowering crop flowers \citep{thomson2001}, and may be due to honey bees avoiding contact with the stigmas to increase ease of access to nectar, or to reduce the amount of grooming needed during a nectar foraging bout.
+HB visitation and foraging behaviour varied strongly between the male and female bays of seed fields, as well as within the female bays.
+Visitation rates of HB foragers were almost twice as high in the centre of the female bay, and conversely, LCB visitation was almost twice as low.
+This could be due to LCBs avoiding competition for nectar with HBs, but more likely reflects a stronger need for pollen among LCBs than HBs \citep{cane2011}.
+Only 1.4\% of the HBs in the female bay were pollen foragers (Table \ref{tab:sideWorking}), meaning that foragers who have (recently) come into contact with pollen rare.
+Both \citet{waytesMsc} and \citet{gaffney2019} showed that HBs exhibit floral fidelity during foraging trips, with minimal crossing between male and female bays ($\sim$5\% of observations, \citealp{waytesMsc}), limiting pollen transfer between the male and female flowers.
+Side-working was a very common behaviour among HBs in commodity fields (65\% of the total visits from HBs during 2015 were side-working), as well as the male bays of seed fields (36\%), but not in the female bays (3\%, Table \ref{tab:sideWorking}).
+This behaviour is relatively common on male-fertile flowers of \textit{Brassica} \citep{free1973,free1983,delbrassine1988,mohr1988} as well as other flowering crop flowers \citep{thomson2001}, and may be due to HBs avoiding contact with the stigmas to increase ease of access to nectar, or to reduce the amount of grooming needed during a nectar foraging bout.
 The foragers who were side-working tended to not switch to top-working (personal observation), so this is likely a consistent individual behaviour (at least in experienced foragers).
-Therefore, honey bees pollen foragers in seed canola fields appear to avoid flowers in the female bay, and commonly engage in side-working behaviour in both commodity and seed canola fields, limiting their opportunities for pollen transfer (see below).
+Therefore, HBs pollen foragers in seed canola fields appear to avoid flowers in the female bay, and commonly engage in side-working behaviour in both commodity and seed canola fields, limiting their opportunities for pollen transfer (see below).
 %However, after controlling for stocking rates, visitation in commodity fields was higher in Grande Prairie in 2015.
@@
 %Canola nectar tends to have high sugar concentrations \citep{szabo1985}, so workers may have selected lower-concentration flowers in field margins and ditches, such as \textit{Trifolium} and \textit{Medicago}, instead of the flowers in the canola fields, depending on local abundances in each year and location, but this seems unlikely, as nectar concentrations were higher in 2015 in Grande Prairie (Chapter 2 Appendix).
-%Water foraging differences between years may also help to explain this effect, as foraging honey bees tend to avoid concentrated nectar or prioritize water foraging \citep{lindauer1955,kuhnholz1997} during hot weather.
+%Water foraging differences between years may also help to explain this effect, as foraging HBs tend to avoid concentrated nectar or prioritize water foraging \citep{lindauer1955,kuhnholz1997} during hot weather.
 %During 2015, we did notice a large number of foragers in Lethbridge gathering water from pools of water near fields instead of visiting flowers (personal observation), so foragers may have been gathering water instead of foraging on flowers (at least in that region), but this is anecdotal, and would require a formal study to confirm this.
@@
 
-\subsection{Pollen deposition}
+\subsection*{Pollen deposition}
 %Pollen deposition in commodity fields
-Honey bee visitation did not increase pollen deposition in commodity canola fields compared to unstocked fields, meaning that wind and/or self-pollination are the likely agents of pollen transfer.
+HB visitation did not increase pollen deposition in commodity canola fields compared to unstocked fields, meaning that wind and/or self-pollination are the likely agents of pollen transfer.
 The stigmas and flowers of \emph{Brassica} are not aligned for optimal dispersal and deposition from the wind, so cross-pollination likely occurs mainly via insects \citep{mesquida1982,cresswell2004}.
@@
 The style of \textit{Brassica} grows past the anthers during maturation, allowing deposition of large amounts of self-pollen, suggesting that self-pollination is the dominant mode of pollination.
-Honey bees can assist in deposition of self-pollen, as \citet{ali2011} found that \textit{Apis dorsata} and \textit{Apis florea} can both deposit 100-200 grains of pollen per visit on a canola flower (\emph{B.
+HBs can assist in deposition of self-pollen, as \citet{ali2011} found that \textit{Apis dorsata} and \textit{Apis florea} can both deposit 100-200 grains of pollen per visit on a canola flower (\emph{B.
 napus} var.
@@
 However, \citet{waytesMsc} used male-sterile flowers and found that \textit{A.
-mellifera} deposit far less outcrossed pollen ($\sim$ 2 grains per visit), suggesting that much of the pollen deposited by honey bees on canola stigmas is self-pollen.
-Because the overall pollen deposition rates found in this study were so high (mean: 293, SD: 385), honey bee visitation seems to have made little difference in the amount of self-pollination.
+mellifera} deposit far less outcrossed pollen ($\sim$ 2 grains per visit), suggesting that much of the pollen deposited by HBs on canola stigmas is self-pollen.
+Because the overall pollen deposition rates found in this study were so high (mean: 293, SD: 385), HB visitation seems to have made little difference in the amount of self-pollination.
 The typical lifetime of a canola flower is approximately 3 days, and the stigmatic surface is receptive for 24--36 hours within this period \citep{eisikowitch1981,hoyle2007}, so it may be that 10-minutes of observing flower visitors was too short of a time interval to relate to pollen deposition.
 This is unlikely, however, as large amounts of pollen were present on commodity canola stigmas even at the centre of unstocked fields (average plot-level visitation rate was 0.23 visits/hr).
-These results suggest that stigmas are largely saturated with self-pollen, swamping any extra pollen deposition by honey bees.
+These results suggest that stigmas are largely saturated with self-pollen, swamping any extra pollen deposition by HBs.
 %SH: DOING A BACK-OF-ENVELOPE CALC: 0.23 VISITS/HR X 2 GRAINS/VISIT X 12 HR X 3 DAYS = 5-6 GRAINS PER DAY, LESS THAN 1% OF STIGMA LOAD
@@
 %REVIEW THIS
-Honey bee behaviour in seed fields made pollen transfer between male and female plants unlikely, and this was also reflected in the measurements of stigma deposition. 
-Deposition was not affected by honey bee visitation, but was strongly increased by LCB visitation.
-LCBs tend to switch between male and female flowers more frequently than honey bees do \citep{waytesMsc}, transport more viable pollen between flowers \citep{parker2015}, and tend not to side-work canola flowers (\citealp{soroka2001}, personal observation), which may explain their increased pollination efficacy.
+HB behaviour in seed fields made pollen transfer between male and female plants unlikely, and this was also reflected in the measurements of stigma deposition. 
+Deposition was not affected by HB visitation, but was strongly increased by LCB visitation.
+LCBs tend to switch between male and female flowers more frequently than HBs do \citep{waytesMsc}, transport more viable pollen between flowers \citep{parker2015}, and tend not to side-work canola flowers (\citealp{soroka2001}, personal observation), which may explain their increased pollination efficacy.
 We also found that pollen deposition also decreased with distance from the edge of the field, was lower in the centre of the female bays, and that this was not solely explained by LCB abundance (Figure \ref{fig:allSEM}).
-During foraging bouts, LCBs may travel further between flowers than honey bees do; \citet{brunet2019} found that LCBs foraging in alfalfa (\emph{Medicago sativa} L.) travelled an average of 21 cm between flowers, while honey bees only travelled 16 cm.
-However, pollen carryover \citep{thomson1986} to the middle of the bay female is likely reduced, as leafcutters likely visit the edge of the female bay before venturing into the centre.
+During foraging bouts, LCBs may travel further between flowers than HBs do; \citet{brunet2019} found that LCBs foraging in alfalfa (\emph{Medicago sativa} L.) travelled an average of 21 cm between flowers, while HBs only travelled 16 cm.
+However, pollen carryover to the middle of the bay female is likely reduced, as leafcutters likely visit the edge of the female bay before venturing into the centre \citep{thomson1986, pinnisch1990}.
 The decrease of pollen deposition with distance into the field (independent of visitation rates) also suggests that the same visitation rate of pollinators in the centre of the field results in less pollen deposition.
@@
 %LCBs are extremely fast fliers, and are difficult to follow after they leave an inflorescence, meaning that tracking their movements during an entire foraging bout would be almost impossible.
-% Visits by honey bee foragers were almost twice as high in the centre of the female bay, but pollen deposition was about 40\% lower (  Figure \ref{fig:allPollen}), which correspondingly is 
-% Honey bees in seed fields tended to visit more in the centre of the female bay, even close to the edge of the field, yet pollen deposition was still about 40\% lower (Figure \ref{fig:allPollen}).
+% Visits by HB foragers were almost twice as high in the centre of the female bay, but pollen deposition was about 40\% lower (  Figure \ref{fig:allPollen}), which correspondingly is 
+% HBs in seed fields tended to visit more in the centre of the female bay, even close to the edge of the field, yet pollen deposition was still about 40\% lower (Figure \ref{fig:allPollen}).
 % While we found that LCBs also tend to avoid the centre of the female bays, and decrease with distance into the field, this extra dependence could have been caused by the fact that the visitation data represents a short ``snapshot'' of the pollen deposition process.
@@
 
-Honey bees may have an indirect positive effect on pollen deposition, as they may cause LCBs to travel farther by lowering overall nectar and pollen standing crop, or release airborne pollen from male-fertile flowers.
-\citet{pierre2010} showed that honey bees can increase the amount of airborne pollen by foraging on male-fertile flowers and releasing pollen from the anthers, causing increased yields in nearby male-sterile flowers; therefore, honey bees may indirectly contribute to a higher rate of wind pollination.
-Honey bees may also cause LCBs to forage at further distances away from their shelters.
-Bumble bees move further between flowers when foraging in \textit{Trifolium} fields that have been depleted by honey bees \citet{heinrich1979}, so a similar process could occur in canola seed fields. 
-LCBs do not appear to use area-restricted search \citep{brunet2019}, but we expect that the foraging range of leafcutter bees around their shelters would sitill decrease, because if honey bees lower pollen and nectar levels at the edge of the field, then leafcutter bees should travel shorter distances to gather the same reward (according to the predictions of Chapter 2).
+HBs may have an indirect positive effect on pollen deposition, as they may cause LCBs to travel farther by lowering overall nectar and pollen standing crop, or release airborne pollen from male-fertile flowers.
+\citet{pierre2010} showed that HBs can increase the amount of airborne pollen by foraging on male-fertile flowers and releasing pollen from the anthers, causing increased yields in nearby male-sterile flowers; therefore, HBs may indirectly contribute to a higher rate of wind pollination.
+HBs may also cause LCBs to forage at further distances away from their shelters.
+Bumble bees move further between flowers when foraging in \textit{Trifolium} fields that have been depleted by HBs \citet{heinrich1979}, so a similar process could occur in canola seed fields. 
+LCBs do not appear to use area-restricted search \citep{brunet2019}, but we expect that the foraging range of leafcutter bees around their shelters would sitill decrease, because if HBs lower pollen and nectar levels at the edge of the field, then leafcutter bees should travel shorter distances to gather the same reward (according to the predictions of Chapter 2).
 %RC: MAY HAVE TO CHOP FOR THE MANUSCRIPT, BECAUSE IT DOESN'T HAVE OTHER AREA-RESTRICTED SEARCH LIT
@@
 However, testing this would require observations of seed canola fields that were only stocked with leafcutter bees, which is extremely rare in southern Alberta.
-%A simple test of this would be to remove honey bee hives from a seed field, mid-season, and perform observations of leafcutter visitation patterns before and after the removal.
+%A simple test of this would be to remove HB hives from a seed field, mid-season, and perform observations of leafcutter visitation patterns before and after the removal.
 
-\subsection{Pod production} % The total yield of a canola plant is a function of three components: number of pods per plant, number of seeds per pod, and seed size.
-Pod set in commodity canola was positively affected by plant size, but not by pollen deposition or honey bee visitation.
-Both pod production and seeds per pod can increase with extra pollination \citep{jauker2008,sabbahi2005,sabbahi2006,duran2010}, so this lack of effect may be due to a high overall level of pollen deposition (Figure \ref{fig:allPollen}), even in fields without honey bees.
-There was no effect of honey bee visitation on pod set, seeds per pod, or seed size, indicating that visitation did not seem to cause either \textit{a)} a greater quantity of pollen (see above) or \textit{b)} higher quality (outcrossed) pollen.
+\subsection*{Pod production} % The total yield of a canola plant is a function of three components: number of pods per plant, number of seeds per pod, and seed size.
+Pod set in commodity canola was positively affected by plant size, but not by pollen deposition or HB visitation.
+Both pod production and seeds per pod can increase with extra pollination \citep{jauker2008,sabbahi2005,sabbahi2006,duran2010}, so this lack of effect may be due to a high overall level of pollen deposition (Figure \ref{fig:allPollen}), even in fields without HBs.
+There was no effect of HB visitation on pod set, seeds per pod, or seed size, indicating that visitation did not seem to cause either \textit{a)} a greater quantity of pollen (see above) or \textit{b)} higher quality (outcrossed) pollen.
 Self-pollination (geitanogamy) in canola can result in similar fruit production as outcrossing \citep{rosa2011}, implying that pollen quality is not likely a limiting factor in canola pod set, at least in some varieties.
@@
 
-\subsection{Seed number and size}
+\subsection*{Seed number and size}
 In commodity canola plants, the number of seeds per pod was only affected by between-year variation, and was unaffected by plant size and pollination.
@@
 
-\subsection{Summary} %RC: VERY CANOLA-FOCUSED
+\subsection*{Summary} %RC: VERY CANOLA-FOCUSED
 This study assesses the relative importance of pollination and plant resources for the production of canola crops, using field-realistic data from central and southern Alberta.
-First, it shows that insect visitation changes across small spatial scales (meters for leafcutter bees, tens of meters for honey bees), and are at odds with the large scales of Albertan crop fields \citep{fritz2015}.
-Visitation of both honey bees and leafcutter bees in canola fields is concentrated at the edge of fields, and is lower at the centre of the female bays in seed canola.	
-Second, honey bees have little direct influence on pollen deposition in either crop system, likely due to a high background level of pollen deposition on stigmas in commodity canola, whereby extra pollen deposition is of little benefit to plant reproduction.
+First, it shows that insect visitation changes across small spatial scales (meters for leafcutter bees, tens of meters for HBs), and are at odds with the large scales of Albertan crop fields \citep{fritz2015}.
+Visitation of both HBs and leafcutter bees in canola fields is concentrated at the edge of fields, and is lower at the centre of the female bays in seed canola.	
+Second, HBs have little direct influence on pollen deposition in either crop system, likely due to a high background level of pollen deposition on stigmas in commodity canola, whereby extra pollen deposition is of little benefit to plant reproduction.
 Seed canola plants, in contrast, have much lower levels of pollen deposition overall, and leafcutter bees deliver a large direct benefit to fruit and seed production. 
-The centre of the female bays illustrates this effect: honey bees have a higher visitation rate, but pollen deposition, pod set, and seed set are all lower.
+The centre of the female bays illustrates this effect: HBs have a higher visitation rate, but pollen deposition, pod set, and seed set are all lower.
 Finally, both plant size and pollination limit seed production in seed canola, but only plant size limits commodity canola production, showing the relative importance of both pollination and plant resources using in-field data.
@@
 Our work identified the effect of bee pollination on seed production in terms of total weight, but may have overlooked these aspects of yield valuation \citep{bommarco2012}. 
-Secondly, we found that honey bees appear to add little pollination value for seed canola crops, but since we did not use fields that had no honey bees, there may be unobserved indirect benefits that honey bees add.
+Secondly, we found that HBs appear to add little pollination value for seed canola crops, but since we did not use fields that had no HBs, there may be unobserved indirect benefits that HBs add.
 For example, they may contribute to better pollination by leafcutter bees by reducing the nectar and pollen standing crop, causing leafcutter bees to forager further away from their shelter \citep{pyke1978b, heinrich1979}, or by increasing the amount of airborne pollen \citep{eisikowitch1981,mesquida1982}.
@@
 
-%First, honey bees have lower per-visit pollen deposition on canola than \textit{Bombus} or \textit{Megachile} \citep{sahli2007, woodcock2013}.
-%This can be compensated for by using a high density of honey bee hives in comparison to the crop area \citep{manning2005, clay2009}, but canola fields in Alberta are very large \citep{fritz2015}, so 
-%This suggests that honey bees may not be beneficial to commodity canola production, at least at the low levels of visitation typically provided by smaller apiaries (20-40 hives per apiary) that are typically meant for honey production rather than pollination.
+%First, HBs have lower per-visit pollen deposition on canola than \textit{Bombus} or \textit{Megachile} \citep{sahli2007, woodcock2013}.
+%This can be compensated for by using a high density of HB hives in comparison to the crop area \citep{manning2005, clay2009}, but canola fields in Alberta are very large \citep{fritz2015}, so 
+%This suggests that HBs may not be beneficial to commodity canola production, at least at the low levels of visitation typically provided by smaller apiaries (20-40 hives per apiary) that are typically meant for honey production rather than pollination.
 %Second, different canola varieties have different pollination dependence \citep{hudewenz2013}
@@
 \bibliographystyle{humanbio}
-\bibliography{references}
+\bibliography{canola_refs}
 

### 2022-08-04 Manuscript/supplemental.tex
Minor updates to manuscript
Worked on Results and Discussion

@@
 
-\begin{figure}
-    \centering
-    \includegraphics[width=0.6\textwidth,keepaspectratio=true]{../Figures/seedYield_bayCent.png}
-    \caption{Simulation results from seed field models, showing seed size and yield (first and second rows, respectively) for plots at the edge and centre of female bays (first and second column), at varying distances away from HB hives and LCB shelters.}
-    \label{fig:seedYield_bayCent}
-\end{figure}
-
-\begin{table}[ht]
+\begin{table}
 \caption{Summary of variables used in structural equation models.}
 \centering
+
 \begin{tabular}{l|l|r|r|r|r|r}
@@
 \cline{2-7}
+ & Harvest index (g/g) & 0.38 & 0.37 & 0.16 & 0.00 & 1.89\\
+\cline{2-7}
  & Flowers per plant & 196.09 & 156.50 & 150.96 & 13.00 & 1094.00\\
@@
 \cline{2-7}
-\multirow{-12}{*}{\raggedright\arraybackslash Commodity} & Seed size (mg) & 2.74 & 2.73 & 0.80 & 0.39 & 5.35\\
+\multirow{-13}{*}{\raggedright\arraybackslash Commodity} & Seed size (mg) & 2.74 & 2.73 & 0.80 & 0.39 & 5.35\\
 \cline{1-7}
@@
 \cline{2-7}
+ & Harvest index (g/g) & 0.32 & 0.33 & 0.15 & 0.00 & 1.21\\
+\cline{2-7}
  & Flowers per plant & 461.32 & 362.50 & 326.59 & 26.00 & 2712.00\\
@@
 \cline{2-7}
-\multirow{-14}{*}{\raggedright\arraybackslash Seed} & Seed size (mg) & 3.43 & 3.42 & 0.88 & 1.04 & 5.59\\
+\multirow{-15}{*}{\raggedright\arraybackslash Seed} & Seed size (mg) & 3.43 & 3.42 & 0.88 & 1.04 & 5.59\\
 \hline
@@
 
-%\widetext
-% \begin{center}
-% \textbf{\large Appendix B: Supplementary information on visitation}
-% \end{center}
+\section*{Appendix B: Supplementary information on visitation}
 
-\section*{Appendix B: Supplementary information on visitation}
-\subsection*{Floral visitors in canola fields}
+During 2015, we recorded whether honey bees were top-working or side-working flowers (see also \citealp{free1973, free1983, mohr1988}).
+Top-working bees landed on the top of the flower and inserted their proboscis down between the petals to access the nectaries of the flower, while side-working bees landed on the side of the flower and stole nectar by inserted their proboscis between the petals, avoiding contact with the stigma or anthers.
+Additionally, we recorded whether honey bees were pollen or nectar foragers (pollen foragers had a visible pollen load on their corbicula, while nectar foragers had none).
 
-\begin{table}[h]
+Pollen- and nectar-foraging honey bees had different patterns of side-working, both on commodity canola, and the male and female lines of seed canola.
+Side-working was common in nectar foragers, but was more common in commodity canola (64\%) than in the male (36\%) or female bays (2.8\%) of seed canola, indicating that a large proportion of honey bees foraging on canola flowers may never come in contact with the stigmas.
+Pollen foragers were almost uniformly top-foragers in both commodity and seed fields (Table \ref{tab:sideWorking}), and pollen foragers were much less common in the female bays (1.4\%) than in the male bays (15\%), or in commodity fields (18\%).
+Therefore, foraging honey bees in seed canola fields tend to treat male-fertile flowers similar to commodity canola flowers, but seem to top-work flowers more in commodity canola than seed fields.
+Leafcutter bee foraging behaviours were not recorded, but seemed to almost exclusively top-work flowers in seed canola fields.
+
+\begin{table}
     \begin{tabular}{r|r|l|r|l}
@@
 
-\subsection*{Top-working and side-working by honey bees in canola fields}
-
-During 2015, we recorded whether honey bees were top-working or side-working flowers (see also \citealp{free1973, free1983, mohr1988}).
-Top-working bees landed on the top of the flower and inserted their proboscis down between the petals to access the nectaries of the flower, while side-working bees landed on the side of the flower and stole nectar by inserted their proboscis between the petals, avoiding contact with the stigma or anthers.
-Additionally, we recorded whether honey bees were pollen or nectar foragers (pollen foragers had a visible pollen load on their corbicula, while nectar foragers had none).
-
 \begin{table}
@@
 \end{table}
-
-Pollen- and nectar-foraging honey bees had different patterns of side-working, both on commodity canola, and the male and female lines of seed canola.
-Side-working was common in nectar foragers, but was more common in commodity canola (64\%) than in the male (36\%) or female bays (2.8\%) of seed canola, indicating that a large proportion of honey bees foraging on canola flowers may never come in contact with the stigmas.
-Pollen foragers were almost uniformly top-foragers in both commodity and seed fields (Table \ref{tab:sideWorking}), and pollen foragers were much less common in the female bays (1.4\%) than in the male bays (15\%), or in commodity fields (18\%).
-Therefore, foraging honey bees in seed canola fields tend to treat male-fertile flowers similar to commodity canola flowers, but seem to top-work flowers more in commodity canola than seed fields.
-Leafcutter bee foraging behaviours were not recorded, but seemed to almost exclusively top-work flowers in seed canola fields.
 

### 2022-08-04 partial plots.R

@@ -549,6 +549,11 @@ d2 <- with(avgSeedData,
 (p <- ggarrange(p1,p2,p3,p4,p5,p6,nrow=2,ncol=3,common.legend = FALSE))
 ggsave('allSeeds.png',p,bg='white',width = 10,height=6)
 
+# Total yield and seed size - plant density --------------------------
+
+
+
+
 # Total yield and seed size for commodity fields -----------------------------------------------------
 
 # avgCommData$flDensMean$mean #Avg sqrt flw dens
@@ -762,8 +767,10 @@ d_mean <- genCommYield(datList) %>% as.data.frame() %>%
   stopCluster(cl)
   }
 
+quantRanges <- c(0.025,0.975) #Ranges of quantiles to use
+
 (p1 <- d %>% mutate(numHives=factor(numHives)) %>% group_by(hbeeDist,numHives) %>% 
-  summarize(med=median(seedWeight),lwr=quantile(seedWeight,0.1),upr=quantile(seedWeight,0.9)) %>% 
+  summarize(med=median(seedWeight),lwr=quantile(seedWeight,quantRanges[1]),upr=quantile(seedWeight,quantRanges[2])) %>% 
   ggplot(aes(x=hbeeDist,y=med,group=numHives))+
   geom_ribbon(aes(ymax=upr,ymin=lwr),alpha=0.3)+
   geom_line(data=d_mean,aes(x=hbeeDist,y=seedWeight))+
@@ -771,7 +778,7 @@ d_mean <- genCommYield(datList) %>% as.data.frame() %>%
   labs(x=xaxis,y='Seed size (mg/seed)'))
 
 (p2 <- d %>% mutate(numHives=factor(numHives)) %>% group_by(hbeeDist,numHives) %>% 
-  summarize(med=median(yield_tha),lwr=quantile(yield_tha,0.1),upr=quantile(yield_tha,0.9)) %>% 
+  summarize(med=median(yield_tha),lwr=quantile(yield_tha,quantRanges[1]),upr=quantile(yield_tha,quantRanges[2])) %>% 
   ggplot(aes(x=hbeeDist,y=med,group=numHives))+
   geom_ribbon(aes(ymax=upr,ymin=lwr),alpha=0.3)+
   geom_line(data=d_mean,aes(x=hbeeDist,y=yield_tha))+
@@ -802,7 +809,7 @@ b <- seq(3.2,3.6,0.05)
 (p3 <- d_mean %>% 
[…]

### 2022-08-04 sem plots.R

@@ -41,7 +41,7 @@ nodeCoords <- data.frame(name=c('numHives','hbeeDist','hbeeVis','pollen',
                                 'flwCount','flwSurv','seedCount','seedWeight'),
                          labs=c('Number\nof Hives','Distance','Honey bee\nVisits','Pollen\nCount',
                                 'Plant\nSize','Plant\nDensity','Flower\nDensity',
-                                'Flowers\nper Plant','Pods\nper Plant','Seeds\nper Pod','Seed\nSize'),
+                                'Flowers\nper Plant','Pod Set\n(%)','Seeds\nper Pod','Seed\nSize'),
                          x=c(0,1,0.5,0.5,
                              2.5,0,1,
                              3.5,4,2.5,3.5),
@@ -66,7 +66,7 @@ commDAG <- dagify(plDens ~ hbeeDist,
 )
 
 #Get path coefficients (Z-scores) and match to edges
-pathCoefs <- modSummaries_commodity %>% #Get path coefficients
+pathCoefs <- lapply(modSummaries_commodity,function(x) x$summary) %>%  #Get path coefficients
   bind_rows(.id='to') %>% 
   transmute(to,name=param,Z,pval) %>% 
   filter(to!='yield',!grepl('(int|sigma|lambda|Phi|phi|rho)',name)) %>% 
@@ -108,7 +108,7 @@ commDAG$data <- commDAG$data %>% #Match coefs to dagitty set
   annotate('text',x=3.5,y=3.5+0.1,label='Plant Level',size=5)+
   annotate('rect',xmin=2,ymin=-0.5,xmax=4.5,ymax=3.5,fill=NA,col='black',
            linetype='dashed',linejoin='round',size=1)+
-  
+  annotate('label',x=3.25,y=4.25,label='Commodity fields',size=10)+
   geom_dag_edges(aes(edge_width=L,edge_colour=C,edge_alpha=A),
                  arrow_directed=arrow(angle=20,type='open')) +
   geom_dag_edges(aes(label=edgeLab),label_pos=0.45,edge_alpha=0,label_size=6,fontface='bold',label_colour ='black') +
@@ -124,7 +124,7 @@ nodeCoords <- data.frame(name=c('numHives','hbeeDist','lbeeDist','hbeeVis','lbee
                          labs=c('Number\nof Hives','Honey bee\nDistance','Leafcutter\nDistance',
[…]

### 2022-08-05 Manuscript/main.tex
Worked on discussion

@@
 Starting with a simple model (visitation $\rightarrow$ pollen deposition $\rightarrow$ fruit production $\leftarrow$ plant resources), we built a detailed model relating visitation to pollination to seed yield within a causal framework (see Figure \ref{fig:allSEM} in Results).
-After the models were properly fit and validated, we simulated seed size and yield at varying distances from pollinators, using the coefficients for each path in order to show the integrated effect of pollination on yield (while holding plant density constant).
+We also ran a linear model outside of each SEM to predict total yield (g per plant) as a function of the seed size, seeds per pod, and pods per plant (see Table \ref{tab:totalYieldCoefs}).
+After the models were properly fit and validated, we simulated seed size and yield at varying distances from pollinators, using the coefficients from each model to integrate the effect of pollination on yield across all other sub-models (while holding plant density constant).
 % These SEMs let us model how visitation ultimately influences seed yield, while controlling for other confounding factors (e.g. distance into field, measurements taken at different fields).
@@
 The direction of the path could be reversed, implying that large flower production reduces the proportion of pod set, but we considered only the first scenario, as \citet{sabbahi2006} showed that low pod set increases flower production.
-Plant and pollen samples were not collected from male bays in seed fields, and there were no large differences in visitation rates for honey bees or LCBs (p = 0.32, 0.72, respectively) once other terms were included as covariates, so bay identity was excluded from further analysis.
+Plant and pollen samples were not collected from male bays in seed fields, and there were no large differences in visitation rates for honey bees or LCBs (p = 0.32, 0.72, respectively) once other terms were included as covariates, so bay was excluded from further analysis.
 See Equation sets S1 and S2 for model specifications) Table \ref{tab:dataSummary} for a brief summary of the variables used in each SEM.
@@
 
-Leafcutter bee visitation was much higher close to their shelters, and surprisingly, was also higher at the edge of the field.
-Visitation dropped from 350 visits/hr at 2 m from the shelter to 50 visits/hr at 20 m (Figure \ref{fig:allVisits}b). 
-Interestingly, LCB visitation decreased from 119 visits/hr at the edge of the field to 25 at the centre.
-The difference in LCB visitation between the edge and centre of the female bays was weak (p=0.14), while HB visitation was higher (88 vs.
-139 visits/hr, Figure \ref{fig:allVisits}), indicating that pollination is likely done by different species in different parts of the field.
+LCB visitation was much higher close to their shelters, and surprisingly, was also higher at the edge of the field.
+LCB Visitation dropped from 350 visits/hr at 2 m from the shelter to 50 visits/hr at 20 m (Figure \ref{fig:allVisits}b), and also decreased from 119 visits/hr at the edge of the field to 25 at the centre (Figure \ref{fig:allVisits}a, b)
+The difference in LCB visitation between the edge and centre of the female bays was weak (p=0.14), while HB visitation was higher at the centre of the bay (88 vs.
+139 visits/hr, Figure \ref{fig:allVisits}b), indicating that pollination is likely done by different species in different parts of the field.
 % There was no difference in visitation rates between the male bay and the edge of the female bays (LCB: p$=$0.72, HB: p$=$0.32). 
@@
 A second set of simulations were run only in seed fields, in order to compare the effect of pollinator distances between the bay edge and centre. 
-This revealed that not only total seed size and overall yield lower at the bay centre, but that the effect of HB distance is effectively \emph{nil} at the bay centre (yield isolines are essentially horizontal in bay centre, and slightly tilted at the bay edge, Figure \ref{fig:allYield_bayCent} second column).
-Interestingly, the simulations also showed evidence of nonlinear behaviour occurring in the centre of seed field bays, where a local minima in yield appears at approximately 25 m away from HB hives and 45 m away from LCB shelters (Figure \ref{fig:allYield_bayCent}) bottom-right panel), likely because of an interaction between seeds per pod, pod count, and seed weight.
+This revealed that not only total seed size and overall yield lower at the bay centre, but that the effect of HB distance is effectively \emph{nil} at the bay centre (yield isolines are essentially horizontal in bay centre, and slightly tilted at the bay edge, Figure \ref{fig:allYield}d, f).
+Interestingly, the simulations also showed evidence of nonlinear behaviour occurring in the centre of seed field bays, where a local minima in yield appears at approximately 25 m away from HB hives and 45 m away from LCB shelters (Figure \ref{fig:allYield})f), likely because of an interaction between the components of yield (seeds per pod, pods per plant, and weight per seed).
 
@@
     \includegraphics[width=\textwidth,keepaspectratio=true]{../Figures/allYield.png}
-    \caption{Effect of honey bee distance and leafcutter distance on seed size (mg/seed, panels a \& c) and total yield (t/ha, panels b \& d), using coefficients from paths for simulation, while holding plant density constant at its mean value.
+    \caption{Effect of honey bee distance and leafcutter distance on seed size (first column) and total yield (second column), using coefficients from paths for simulation, while holding plant density constant at its mean value.
 Shaded areas shown in a \& b are 95\% quantiles for the simulations.
-Lines on panels c \& d are isolines of constant seed size (c) or yield (d).}
+Lines on panels c - f are isolines of constant seed size (c, e) or yield (d, f).}
     \label{fig:allYield}
-\end{figure}
-
-\begin{figure}
-    \centering
-    \includegraphics[width=\textwidth,keepaspectratio=true]{../Figures/allYield_bayCent.png}
-    \caption{Simulation results from seed field models, showing seed size and yield (first and second rows, respectively) for plots at the edge and centre of female bays (first and second column), at varying distances away from HB hives and LCB shelters.}
-    \label{fig:allYield_bayCent}
 \end{figure}
@@
 HBs also suffer from direct interference by LCBs near to their shelters; during the study we observed LCBs directly harassing HBs during the plot-level observations, attacking HBs both on the flowers and in the air (also seen by \citealp{batra1978} and \citealp{waytesMsc}).
-HBs were never the aggressor in these interactions, so we treated high leafcutter visitation as the cause of lower HB visitation in our SEM (Figure \ref{fig:allSEM}, arrow from leafcutter visit rate to HB visit rate).
+HB visitation and foraging behaviour varied strongly between the edge and centre of the female bays in seed fields, while there was little difference between LCB visitation rates.
+HB visitation rates were almost twice as high at the centre of the female bay, likely reflecting a stronger need for pollen among LCBs than HBs \citep{cane2011} (although interestingly, there was also no difference in LCB visitation between male and female bays).
 
-HB visitation and foraging behaviour varied strongly between the male and female bays of seed fields, as well as within the female bays.
-Visitation rates of HB foragers were almost twice as high in the centre of the female bay, and conversely, LCB visitation was almost twice as low.
-This could be due to LCBs avoiding competition for nectar with HBs, but more likely reflects a stronger need for pollen among LCBs than HBs \citep{cane2011}.
-Only 1.4\% of the HBs in the female bay were pollen foragers (Table \ref{tab:sideWorking}), meaning that foragers who have (recently) come into contact with pollen rare.
+Very few HBs in the female bay were pollen foragers (1.4\%, see Table \ref{tab:sideWorking}), meaning that foragers who have (recently) come into contact with pollen rare.
 Both \citet{waytesMsc} and \citet{gaffney2019} showed that HBs exhibit floral fidelity during foraging trips, with minimal crossing between male and female bays ($\sim$5\% of observations, \citealp{waytesMsc}), limiting pollen transfer between the male and female flowers.
@@
 The foragers who were side-working tended to not switch to top-working (personal observation), so this is likely a consistent individual behaviour (at least in experienced foragers).
-Therefore, HBs pollen foragers in seed canola fields appear to avoid flowers in the female bay, and commonly engage in side-working behaviour in both commodity and seed canola fields, limiting their opportunities for pollen transfer (see below).
+Taken together, these pieces of evidence suggests that HBs have limited opportunities for pollen transfer in both commodity and seed fields, as they commonly engage in side-working behaviour in both field types, and pollen foragers typically avoid female bays in seed canola fields.
+
 %However, after controlling for stocking rates, visitation in commodity fields was higher in Grande Prairie in 2015.
@@
 HB visitation did not increase pollen deposition in commodity canola fields compared to unstocked fields, meaning that wind and/or self-pollination are the likely agents of pollen transfer.
-The stigmas and flowers of \emph{Brassica} are not aligned for optimal dispersal and deposition from the wind, so cross-pollination likely occurs mainly via insects \citep{mesquida1982,cresswell2004}.
+The stigmas and flowers of \emph{Brassica} are not aligned for dispersal and deposition from the wind, so cross-pollination likely occurs mainly via insects \citep{mesquida1982,cresswell2004}.
 However, wind-induced self-pollination (plant shaking) can increase yield in \textit{Brassica} \citep{williams1986, mesquida1988c}, and fields without bee pollination have outcrossing rates of about 20\% within the field \citep{rakow1987,becker1992}.
-The style of \textit{Brassica} grows past the anthers during maturation, allowing deposition of large amounts of self-pollen, suggesting that self-pollination is the dominant mode of pollination.
+% The style of \textit{Brassica} grows past the anthers during maturation, allowing deposition of large amounts of self-pollen, suggesting that self-pollination is the dominant mode of pollination.
 HBs can assist in deposition of self-pollen, as \citet{ali2011} found that \textit{Apis dorsata} and \textit{Apis florea} can both deposit 100-200 grains of pollen per visit on a canola flower (\emph{B.
@@
 \emph{Bulbul}).
-However, \citet{waytesMsc} used male-sterile flowers and found that \textit{A.
-mellifera} deposit far less outcrossed pollen ($\sim$ 2 grains per visit), suggesting that much of the pollen deposited by HBs on canola stigmas is self-pollen.
-Because the overall pollen deposition rates found in this study were so high (mean: 293, SD: 385), HB visitation seems to have made little difference in the amount of self-pollination.
-The typical lifetime of a canola flower is approximately 3 days, and the stigmatic surface is receptive for 24--36 hours within this period \citep{eisikowitch1981,hoyle2007}, so it may be that 10-minutes of observing flower visitors was too short of a time interval to relate to pollen deposition.
-This is unlikely, however, as large amounts of pollen were present on commodity canola stigmas even at the centre of unstocked fields (average plot-level visitation rate was 0.23 visits/hr).
-These results suggest that stigmas are largely saturated with self-pollen, swamping any extra pollen deposition by HBs.
+However, \citet{waytesMsc} used male-sterile flowers from seed canola fields and found that HB pollen foragers deposited far less outcrossed pollen ($\sim$ 2 grains per visit), suggesting that much of the pollen deposited on commodity canola stigmas is self-pollen.
+Because the overall pollen deposition rates found in this study were so high, HB visitation seems to have made little difference in the amount of self-pollination, as large amounts of pollen were present on commodity canola stigmas even at the centre of unstocked fields.
+These results suggest that commodity canola stigmas are largely saturated with self-pollen, swamping any extra pollen deposition by HBs.
+% The typical lifetime of a canola flower is approximately 3 days, and the stigmatic surface is receptive for 24--36 hours within this period \citep{eisikowitch1981,hoyle2007}, so it may be that 10-minutes of observing flower visitors was too short of a time interval to relate to pollen deposition.
+% This is unlikely, however, 
 %SH: DOING A BACK-OF-ENVELOPE CALC: 0.23 VISITS/HR X 2 GRAINS/VISIT X 12 HR X 3 DAYS = 5-6 GRAINS PER DAY, LESS THAN 1% OF STIGMA LOAD
@@
 %REVIEW THIS
-HB behaviour in seed fields made pollen transfer between male and female plants unlikely, and this was also reflected in the measurements of stigma deposition. 
-Deposition was not affected by HB visitation, but was strongly increased by LCB visitation.
-LCBs tend to switch between male and female flowers more frequently than HBs do \citep{waytesMsc}, transport more viable pollen between flowers \citep{parker2015}, and tend not to side-work canola flowers (\citealp{soroka2001}, personal observation), which may explain their increased pollination efficacy.
-We also found that pollen deposition also decreased with distance from the edge of the field, was lower in the centre of the female bays, and that this was not solely explained by LCB abundance (Figure \ref{fig:allSEM}).
-During foraging bouts, LCBs may travel further between flowers than HBs do; \citet{brunet2019} found that LCBs foraging in alfalfa (\emph{Medicago sativa} L.) travelled an average of 21 cm between flowers, while HBs only travelled 16 cm.
-However, pollen carryover to the middle of the bay female is likely reduced, as leafcutters likely visit the edge of the female bay before venturing into the centre \citep{thomson1986, pinnisch1990}.
-The decrease of pollen deposition with distance into the field (independent of visitation rates) also suggests that the same visitation rate of pollinators in the centre of the field results in less pollen deposition.
-This may be due to lower levels of competition at the centre of the field, leading to a higher nectar (or pollen) standing crop. %LH: more likely that bees at centre of F bays carry less pollen
-Foraging \textit{Bombus} take smaller trips between flowers and will forage in smaller areas under nectar-rich conditions (area-restricted search, \citealp{pyke1978b, heinrich1979}), so leafcutter foraging may follow a similar pattern, causing lower pollen deposition at the centre of the field where competition is lower.
+The limited pollen-transfering behaviour of HBs was also reflected in the pollen counts, as deposition strongly increased with LCB visitation, but not with HB visitation.
+LCBs tend to switch between male and female flowers more frequently than HBs do \citep{waytesMsc}, transport more viable pollen between flowers \citep{parker2015}, and tend not to side-work canola flowers \citep{soroka2001}, which may explain their increased pollination efficacy.
+Pollen deposition in seed fields also decreased with distance from the edge of the field, and was lower in the centre of the female bays, but this was not explained solely by LCB abundance (Figure \ref{fig:allSEM}).
+During foraging bouts, LCBs may travel further between flowers than HBs do \citep{brunet2019}, but pollen carryover from the edge to the centre of the bay female is likely reduced, as LCBs likely visit the edge of the female bay before venturing into the centre \citep{thomson1986, pinnisch1990}.
+Pollen counts decreased with distance into the field (independent of visitation), suggests that pollinators are less efficient at transfering pollen.
+Foraging \textit{Bombus} take shorter trips between flowers under nectar-rich conditions (area-restricted search, \citealp{pyke1978b, heinrich1979}), suggesting that HBs and LCBs may operate similarly at the centre of seed fields, causing lower pollen deposition at the centre of the field where competition is lower.
+% This may be due to lower levels of competition at the centre of the field, leading to a higher nectar (or pollen) standing crop. %LH: more likely that bees at centre of F bays carry less pollen
 %LCBs are extremely fast fliers, and are difficult to follow after they leave an inflorescence, meaning that tracking their movements during an entire foraging bout would be almost impossible.
@@
 
-HBs may have an indirect positive effect on pollen deposition, as they may cause LCBs to travel farther by lowering overall nectar and pollen standing crop, or release airborne pollen from male-fertile flowers.
-\citet{pierre2010} showed that HBs can increase the amount of airborne pollen by foraging on male-fertile flowers and releasing pollen from the anthers, causing increased yields in nearby male-sterile flowers; therefore, HBs may indirectly contribute to a higher rate of wind pollination.
-HBs may also cause LCBs to forage at further distances away from their shelters.
-Bumble bees move further between flowers when foraging in \textit{Trifolium} fields that have been depleted by HBs \citet{heinrich1979}, so a similar process could occur in canola seed fields. 
-LCBs do not appear to use area-restricted search \citep{brunet2019}, but we expect that the foraging range of leafcutter bees around their shelters would sitill decrease, because if HBs lower pollen and nectar levels at the edge of the field, then leafcutter bees should travel shorter distances to gather the same reward (according to the predictions of Chapter 2).
-%RC: MAY HAVE TO CHOP FOR THE MANUSCRIPT, BECAUSE IT DOESN'T HAVE OTHER AREA-RESTRICTED SEARCH LIT
-We also expect that foraging leafcutter bees would make shorter trips between flowers (similar to \citealp{heinrich1979}), and possibly may switch between bays less frequently \citep{waytesMsc,gaffney2019}, due to a greater floral fidelity on higher-rewarding flowers in the male bay \citep{mesquida1978}.
-If this is true, this would result in a lower rate of (overall) pollen deposition by leafcutter bees during the same period.
-However, testing this would require observations of seed canola fields that were only stocked with leafcutter bees, which is extremely rare in southern Alberta.
-%A simple test of this would be to remove HB hives from a seed field, mid-season, and perform observations of leafcutter visitation patterns before and after the removal.
+\subsection*{Seed production} % The total yield of a canola plant is a function of three components: number of pods per plant, number of seeds per pod, and seed size.
 
-\subsection*{Pod production} % The total yield of a canola plant is a function of three components: number of pods per plant, number of seeds per pod, and seed size.
-Pod set in commodity canola was positively affected by plant size, but not by pollen deposition or HB visitation.
-Both pod production and seeds per pod can increase with extra pollination \citep{jauker2008,sabbahi2005,sabbahi2006,duran2010}, so this lack of effect may be due to a high overall level of pollen deposition (Figure \ref{fig:allPollen}), even in fields without HBs.
-There was no effect of HB visitation on pod set, seeds per pod, or seed size, indicating that visitation did not seem to cause either \textit{a)} a greater quantity of pollen (see above) or \textit{b)} higher quality (outcrossed) pollen.
-Self-pollination (geitanogamy) in canola can result in similar fruit production as outcrossing \citep{rosa2011}, implying that pollen quality is not likely a limiting factor in canola pod set, at least in some varieties.
-Flower number was negatively related to pod set, which implies a response to pollination (high flower fertilization suppresses further flower production) and/or a reproductive trade-off (greater pod development rate means more competition among pods for resources).
-%RC: THESE SCENARIOS AREN'T MUTUALLY EXCLUSIVE
-We considered the first scenario to be the stronger effect, as \citet{sabbahi2006} and \citet{mesquida1981} both found that canola plants compensated for experimental removal of flowers by increasing branch and flower production, until the plant reached about 170 pods.
-Their final number of pods is similar to the plants from our study (median: 112, range: 5--892), but we found that larger plants also had greater pod set, in addition to higher flower production, presumably caused by the larger pool of resources that large plants are able to invest into reproduction.
+% Plant size was the only important factor in commodity canola seed production (i.e.
+pod set, seed size, and seeds per pod), but both plant size and pollen deposition were the main drivers of production in seed canola.
+
+Plant size increased pod set in commodity canola, but both plant size and pollen increased pod set in seed canola, suggesting that both pollen deposition and plant resources constrain pod production \citep{marini2015}.
+This is similar to the findings of \citet{mesquida1981} and \citet{steffan2003}, who found that pod set in male-sterile plants responded positively to visitation, while male-fertile plants had no response (but see \citealp{adegas1992}).
+Both pod set and seeds per pod can increase with extra pollination \citep{jauker2008,sabbahi2005,sabbahi2006,duran2010}, so the lack of pollination effect in commodity fields may be due to a high overall level of pollen deposition (Figure \ref{fig:allPollen}).
+There was also no additional effect of HB visitation on pod set, meaning that that HB visitation did not cause more pollen deposition (see above) or improve its quality through increased outcrossing (as in \citealt{rosa2011}), but this may depend on the variety \citep{adamidis2019}.
+Flower number was negatively related to pod set, implying that high pod set suppresses further flower production or increases competition among pods for plant resources.
+The first scenario is more likely, as \citet{sabbahi2006} and \citet{mesquida1981} both found that canola plants compensated for experimental removal of flowers by increasing branch and flower production, until the plant reached about 170 pods.
+There were also effects of distance on pod set independent of pollen: pod set decreased with distance from the edge of the field, distance to LCB shelters, and was lower at the centre of the female bays.
+\citet{mesquida1978} also found that pod set in male-sterile canola declined quickly with distance from the male-fertile plants (due to wind pollination), but the effect we found is likely related to the earlier effect of lower pollen carryover at the centre of the female bays, and possibly the centre of the field.
+Finally, the effect size of pollen deposition (Z=3.1) was much smaller than that of plant size (Z=19.9), indicating that the factors controlling plant size (e.g.
+fertilizer application, soil quality) likely constrain pod production more strongly than pollination alone.
+
+%RC: SEEMS AN INTERACTION WOULD TEST THIS BETTER
+% Pollination increased pod production in seed canola, but not in commodity canola, meaning that extra pollination is valuable for seed canola crops, but not commodity canola.
+% Their final number of pods is similar to the plants from our study (mean: 143), but we found that larger plants also had greater pod set, in addition to higher flower production, presumably caused by the larger pool of resources that large plants are able to invest into reproduction.
 %This could indicate stronger overall competition between plants in seed fields, but that plant resources are higher in the centre of the crop field than at the edge.
 
-Pollination increased pod production in seed canola, but not in commodity canola, meaning that extra pollination is valuable for seed canola crops, but not commodity canola. 
-This is similar to the findings of \citet{mesquida1981} and \citet{steffan2003}, who found that pod set in male-sterile plants responded positively to visitation, while male-fertile plants (``male" plants in seed fields, all plants in commodity fields) had no response (but see \citealp{adegas1992}).
-Pod production in seed canola increased with both pollen deposition and plant size, suggesting that both pollen availability and plant resources constrain pod production.
-%(\citealp{mesquida1981} did not consider plant size).
-However, the effect size of pollen deposition (Z=3.1) was much smaller than that of plant size (Z=19.9), indicating that the factors controlling plant size (fertilizer, plant density, and soil quality) likely constrain pod production more strongly than pollination alone, in both commodity and seed canola plants.
-%RC: SEEMS AN INTERACTION WOULD TEST THIS BETTER
-There were also effects of distance on pod set, independent of pollen deposition: pod set decreased with distance from the edge of the field and distance to leafcutter shelters independent of pollen deposition, and was lower in the centre of the female bays.
-\citet{mesquida1978} also found that pod set in male-sterile canola declined quickly with distance from the male-fertile plants (due to wind pollination), but the effect we found is likely related to the earlier effect of lower pollen carryover at the centre of the female bays, and possibly the centre of the field.
-However, our analysis points to the strong relative importance of plant resources, as well as pollination services \citep{marini2015}, mediated through the effect of leafcutter bee visitation, to the production of hybrid seed canola.
+Plant size increased seeds per pod in both crop types, but pollen increased seeds per pod only in seed canola.
 
-\subsection*{Seed number and size}
-In commodity canola plants, the number of seeds per pod was only affected by between-year variation, and was unaffected by plant size and pollination.
 In contrast, the number of seeds per pod in seed canola was increased by pollen deposition, flower survival, and plant size, and was reduced in the centre of the female bay. 
@@
 \subsection*{Summary} %RC: VERY CANOLA-FOCUSED
+
+%Taken from pollen section
+HBs may have an indirect positive effect on pollen deposition, as they may cause LCBs to travel farther by lowering overall nectar and pollen standing crop, or release airborne pollen from male-fertile flowers.
+\citet{pierre2010} showed that HBs can increase the amount of airborne pollen by foraging on male-fertile flowers and releasing pollen from the anthers, causing increased yields in nearby male-sterile flowers; therefore, HBs may indirectly contribute to a higher rate of wind pollination.
+HBs may also cause LCBs to forage at further distances away from their shelters.
+Bumble bees move further between flowers when foraging in \textit{Trifolium} fields that have been depleted by HBs \citet{heinrich1979}, so a similar process could occur in canola seed fields. 
+LCBs do not appear to use area-restricted search \citep{brunet2019}, but we expect that the foraging range of leafcutter bees around their shelters would sitill decrease, because if HBs lower pollen and nectar levels at the edge of the field, then leafcutter bees should travel shorter distances to gather the same reward (according to the predictions of Chapter 2).
+We also expect that foraging leafcutter bees would make shorter trips between flowers (similar to \citealp{heinrich1979}), and possibly may switch between bays less frequently \citep{waytesMsc,gaffney2019}, due to a greater floral fidelity on higher-rewarding flowers in the male bay \citep{mesquida1978}.
+If this is true, this would result in a lower rate of (overall) pollen deposition by leafcutter bees during the same period.
+However, testing this would require observations of seed canola fields that were only stocked with leafcutter bees, which is extremely rare in southern Alberta.
+%RC: MAY HAVE TO CHOP FOR THE MANUSCRIPT, BECAUSE IT DOESN'T HAVE OTHER AREA-RESTRICTED SEARCH LIT
+%A simple test of this would be to remove HB hives from a seed field, mid-season, and perform observations of leafcutter visitation patterns before and after the removal.
+
 This study assesses the relative importance of pollination and plant resources for the production of canola crops, using field-realistic data from central and southern Alberta.

### 2022-08-05 partial plots.R

@@ -745,7 +745,7 @@ ggarrange(p1,p2,ncol=1,nrow=2)
 
 xaxis <- 'Distance from HB hives (m)'
 
-#Commodity fields - distance and stocking effect
+##Commodity fields - distance and stocking effect
 # summary(exp(commData$plantSize))
 # summary(exp(commData$plDens_obs))
 
@@ -769,20 +769,25 @@ d_mean <- genCommYield(datList) %>% as.data.frame() %>%
 
 quantRanges <- c(0.025,0.975) #Ranges of quantiles to use
 
-(p1 <- d %>% mutate(numHives=factor(numHives)) %>% group_by(hbeeDist,numHives) %>% 
-  summarize(med=median(seedWeight),lwr=quantile(seedWeight,quantRanges[1]),upr=quantile(seedWeight,quantRanges[2])) %>% 
-  ggplot(aes(x=hbeeDist,y=med,group=numHives))+
+#Needed for placing annotations at the same place on each plot
+d1 <- d %>% mutate(numHives=factor(numHives)) %>% group_by(hbeeDist,numHives) %>% 
+  summarize(med=median(seedWeight),lwr=quantile(seedWeight,quantRanges[1]),upr=quantile(seedWeight,quantRanges[2]))
+   
+(p1 <- d1 %>% ggplot(aes(x=hbeeDist,y=med,group=numHives))+
   geom_ribbon(aes(ymax=upr,ymin=lwr),alpha=0.3)+
   geom_line(data=d_mean,aes(x=hbeeDist,y=seedWeight))+
   annotate('text',x=c(300,300),y=c(2.825,2.75),label=c('40 hives','0 hives'))+
+  annotate('label',x=300,y=min(d1$lwr)+(max(d1$upr)-min(d1$lwr))*0.2,label='Commodity fields\nSeed size (mg/seed)')+
   labs(x=xaxis,y='Seed size (mg/seed)'))
 
-(p2 <- d %>% mutate(numHives=factor(numHives)) %>% group_by(hbeeDist,numHives) %>% 
-  summarize(med=median(yield_tha),lwr=quantile(yield_tha,quantRanges[1]),upr=quantile(yield_tha,quantRanges[2])) %>% 
-  ggplot(aes(x=hbeeDist,y=med,group=numHives))+
+d2 <-  d %>% mutate(numHives=factor(numHives)) %>% group_by(hbeeDist,numHives) %>% 
[…]

### 2022-08-05 yield path analysis seed.R

@@ -268,7 +268,7 @@ modList[5] <- stan(file=modFiles[5],data=datalist,iter=2000,chains=4,init=0) #Fl
 modList[6] <- stan(file=modFiles[6],data=datalist,iter=2000,chains=4,init=0) #Pod count (flw survival) per plant
 modList[7] <- stan(file=modFiles[7],data=datalist,iter=2000,chains=4,init=0) #Seeds per pod
 modList[8] <- stan(file=modFiles[8],data=datalist,iter=2000,chains=4,init=0) #Weight per seed
-modList[9] <- stan(file=modFiles[9],data=datalist,iter=3000,chains=4,init=0) #Yield
+modList[9] <- stan(file=modFiles[9],data=datalist,iter=3000,chains=4,init=0,control=list(adapt_delta=0.9)) #Yield
 beepr::beep(1)
 
 apply(extract(modList[[4]],pars='pollenMu_plot')[[1]],2,mean) %>% range

### 2022-08-09 Manuscript/main.tex
Worked on Discussion

@@
 
-Plant size increased pod set in commodity canola, but both plant size and pollen increased pod set in seed canola, suggesting that both pollen deposition and plant resources constrain pod production \citep{marini2015}.
+Plant size increased pod set in commodity canola, but both plant size and pollen increased pod set in seed canola, suggesting that both pollen deposition and plant resources constrain pod production.
 This is similar to the findings of \citet{mesquida1981} and \citet{steffan2003}, who found that pod set in male-sterile plants responded positively to visitation, while male-fertile plants had no response (but see \citealp{adegas1992}).
-Both pod set and seeds per pod can increase with extra pollination \citep{jauker2008,sabbahi2005,sabbahi2006,duran2010}, so the lack of pollination effect in commodity fields may be due to a high overall level of pollen deposition (Figure \ref{fig:allPollen}).
-There was also no additional effect of HB visitation on pod set, meaning that that HB visitation did not cause more pollen deposition (see above) or improve its quality through increased outcrossing (as in \citealt{rosa2011}), but this may depend on the variety \citep{adamidis2019}.
-Flower number was negatively related to pod set, implying that high pod set suppresses further flower production or increases competition among pods for plant resources.
+Both pod set and seeds per pod can increase with extra pollination \citep{jauker2008,sabbahi2005,sabbahi2006,duran2010}, so the low influence of pollination in commodity fields may be due to a high overall level of pollen deposition (Figure \ref{fig:allPollen}).
+There was no additional effect of HB visitation on pod set, meaning that that HB visitation did not cause more pollen deposition or improve its quality through increased outcrossing (as in \citealt{rosa2011}), but this may depend on the variety \citep{adamidis2019}.
+Flowers per plant was reduced by pod set, implying that high pod set suppresses further flower production or increases competition among pods for plant resources.
 The first scenario is more likely, as \citet{sabbahi2006} and \citet{mesquida1981} both found that canola plants compensated for experimental removal of flowers by increasing branch and flower production, until the plant reached about 170 pods.
@@
 Finally, the effect size of pollen deposition (Z=3.1) was much smaller than that of plant size (Z=19.9), indicating that the factors controlling plant size (e.g.
-fertilizer application, soil quality) likely constrain pod production more strongly than pollination alone.
+fertilizer application, soil quality) likely constrain pod production more strongly than pollination alone \citep{marini2015}.
 
@@
 
-Plant size increased seeds per pod in both crop types, but pollen increased seeds per pod only in seed canola.
+Plant size increased seeds per pod in both crop types, but the number of seeds per pod in seed canola was also increased by pollen deposition and pod set. 
+Pollen deposition had a smaller effect than plant size (Z=2.3 vs.
+5.6), again suggesting that plant resources limit seed production more strongly than pollen deposition in seed canola \citep{marini2015}.
+\citet{mesquida1982} also found that pod production, rather than seeds per pod, was the main variable controlled by pollen deposition in seed canola.
+Position in the female bay influenced pollen deposition, both by wind and insects, indicating that the decrease in seed number at the centre of the bay is ultimately caused by reduced pollen deposition from lower visitation \citep{mesquida1981,mesquida1982}.
 
-In contrast, the number of seeds per pod in seed canola was increased by pollen deposition, flower survival, and plant size, and was reduced in the centre of the female bay. 
-Position in the female bay influenced pollen deposition, both by wind and insects, indicating that the decrease in seed number at the centre of the bay is ultimately caused by reduced pollen deposition from lower visitation \citep{mesquida1981,mesquida1982}.
-Seeds per pod also increased with pollen deposition and plant size, but the effect size of pollen deposition (Z=2.3) was smaller than that of plant size (Z=5.6), suggesting that plant resources limit seed production more strongly than pollen deposition in seed canola.
-\citet{mesquida1982} found that in seed canola, pod production, rather than seeds per pod, was the main variable that was reduced by low pollen deposition.
-Interestingly, plant density had a positive effect on seed size in seed canola, pointing to a possible reduction in seed count because of shading or crowding, causing an increase in seed size (but see \citealp{angadi2003}).
+Seed size was influenced by plant size in seed canola, but not commodity canola, and was not influenced by pollen or visitation in either crop \citep{riffkin2012}.
+Unexpectedly, plant density had a \emph{positive} effect on seed size in both crop types, which we consider could have been caused by two different processes:
+plant density could be positively related to resource availability if plant survival is higher in plots with better growing conditions (i.e.
+Berkson's paradox \citep{snoep2014}) or plant density may improve the microclimate conditions of the canola stand, reducing heat or desiccation stress on individual plants.
+We consider the first process more likely, as planting density under uniform conditions typically has little effect on seed size \citep{Angadi2003}.
+
 %Increased plant density within a patch can lead to more pollinator visitation \citep{kunin1997}, but not necessarily more visits per flower \citep{klinkhamer1990}.  
@@
 %Seed size
-Plant size was one of the dominant factors controlling seed size in seed canola, while in commodity canola, plant size did not influence seed size.
-Plant size can positively influence seed size in some plant species \citep{maddox1983}, and this appears to be true in canola \citep{riffkin2012} as well as other Brassicaceae \citep{mazer1987}.
-Similarly, seeds per pod and seed weight varied positively in commodity canola, this pattern was reversed in seed canola (Figure \ref{fig:allSeeds}). 
-These differences likely occurred because of variation in available seed resources among the parts of the plant \citep{vanNoordwijk1986}, which can cause a positive size-number relationship even in resource-limited plants.
-In commodity canola, pollen is readily available, and there seems to be little difference between outcrossed- and self-pollen \citep{steffan2003, rosa2011}. 
-Canola plants produce flowers from the bottom up, and produce fewer, smaller seeds at the ends of the branches because the younger pods have access to fewer resources at the end of the season \citep{sabbahi2006}, resulting in an increased rate of seed abortion \citep{clarke1979}.
-Pods with low resources at the end of the season are forced to abort more ovules \citep{wang2011}, causing a positive relationship between seed number and size.
-Thus, in commodity canola, variation in resources with plant size is masked by resource variation over time.  
-In seed canola, pollen is much rarer (median: 7 grains/stigma vs.
+% Plant size was one of the dominant factors controlling seed size in seed canola, while in commodity canola, plant size did not influence seed size.
+% Plant size can positively influence seed size in some plant species \citep{maddox1983}, and this appears to be true in canola \citep{riffkin2012} as well as other Brassicaceae \citep{mazer1987}.
+% Similarly, seeds per pod and seed weight varied positively in commodity canola, this pattern was reversed in seed canola (Figure \ref{fig:allSeeds}). 
+% These differences likely occurred because of variation in available seed resources among the parts of the plant \citep{vanNoordwijk1986}, which can cause a positive size-number relationship even in resource-limited plants.
+% In commodity canola, pollen is readily available, and there seems to be little difference between outcrossed- and self-pollen \citep{steffan2003, rosa2011}. 
+% Canola plants produce flowers from the bottom up, and produce fewer, smaller seeds at the ends of the branches because the younger pods have access to fewer resources at the end of the season \citep{sabbahi2006}, resulting in an increased rate of seed abortion \citep{clarke1979}.
+% Pods with low resources at the end of the season are forced to abort more ovules \citep{wang2011}, causing a positive relationship between seed number and size.
+% Thus, in commodity canola, variation in resources with plant size is masked by resource variation over time.  
+% In seed canola, pollen is much rarer (median: 7 grains/stigma vs.
 155 in commodity), but plant sizes are similar (or larger) than commodity canola, such that plant resources are still available to developing pods at the end of the season.
-This causes a size-number trade-off within pods that is mediated by plant size.
-Most studies on commodity canola report a seed size-number trade-off at the level of plant \citep{angadi2003,koltowski2005}, we found a positive relationship at the pod level (but see \citealp{sabbahi2005}).
-Perhaps within-plant resource variation is a more likely driver of seed number than pollen deposition, as pollination did not appear to be limiting (Figure \ref{fig:allSEM}, weak paths from pollen to yield metrics).
+% This causes a size-number trade-off within pods that is mediated by plant size.
+% Most studies on commodity canola report a seed size-number trade-off at the level of plant \citep{angadi2003,koltowski2005}, we found a positive relationship at the pod level (but see \citealp{sabbahi2005}).
+% Perhaps within-plant resource variation is a more likely driver of seed number than pollen deposition, as pollination did not appear to be limiting (Figure \ref{fig:allSEM}, weak paths from pollen to yield metrics).
 %While we did not quantify pod position on branches, the pods at the end of the branches did appear to have fewer seeds, meaning that some of the variation within plants likely occurred because of late-season seed.

### 2022-08-12 Manuscript/supplemental.tex

@@
 
-\section*{Appendix B: Supplementary information on visitation}
+\section*{Appendix B: Additional information on insect visitors}
 
@@
 
-\section*{Appendix C: Supplementary information on models}
+\section*{Appendix C: Additional information on models}
 
@@
 
-\subsection*{Seed canola models}
-
-Formulas for seed canola model using \texttt{lmer}-style R formulas.
-Terms on right side of $\sim$ indicate fixed effects, while terms in brackets indicate random effects (heirarchical intercepts).
-\textit{distribution} indicates the type of probability distribution function used to model each variable.
-
-\begin{align*}
-    \text{Plant Density} \sim & \text{HB Distance} + (1|\text{Field}), \text{distribution = log-normal} \\
-    \text{Plant Size} \sim & \text{HB Distance} + \text{Plant Density} + (1|\text{Field}) ,\text{distribution = log-t} \\
-    \text{Flower Density} \sim & \text{HB Distance} + (1|\text{Field}), \text{distribution = square root-t} \\
-    \text{LCB Visits} \sim & \text{offset}(log(\text{Time})) + \text{HB Distance} + \text{LCB Distance} + \text{Bay Centre} + \\
-    &   \text{Flower Density} + (1|\text{Field}), \text{family = ZI negative binomial} \\
-    \text{HB Visits} \sim & \text{offset}(log(\text{Time})) + \text{HB Distance} + \text{LCB Distance} + \text{Bay Centre} + \\
-    &   \text{Flower Density} + (1|\text{Field}), \text{family = ZI negative binomial} \\
-    \text{Pollen per Stigma} \sim & \text{HB Visits} + \text{LCB Visits} + \text{Bay Centre} + \text{HB Distance} + \text{LCB Distance} +\\
-    &   \text{Flower Density} + (1|\text{Field}) + (1|\text{Plot}), \text{family = negative binomial} \\
-    \text{Flowers per Plant} \sim & \text{Plant Size} + \text{Bay Centre} + \text{\% Pod Set} + (1|\text{Field}),\\
-    &   \phi \sim \text{Plant Size}, \text{family = negative binomial} \\
-    \text{\% Pod Set} \sim & \text{Pollen} + \text{Plant Size} + \text{Bay Centre} + \text{HB Distance} + \text{LCB Distance} + \\
-    &   \text{Flower Density} + (1|\text{Field}) + (1|\text{Plot}), \text{family = beta-binomial} \\
-    \text{Seeds per Pod} \sim & \text{Pollen} + \text{Plant Size} + \text{Bay Centre} + \text{HB Distance} + \text{Flower Density} +\\
-    &   \text{\% Pod Set} + \text{Flowers per plant} + (1|\text{Field}), \text{family = negative binomial} \\
-    \text{Weight per Seed} \sim & \text{Pollen} + \text{Seeds per Pod} + \text{Plant Size} + \text{LCB Distance} +\\
-    &   \text{Plant Density} + (1|\text{Field}), \text{family = exponential-normal}\\
-\end{align*}
-
-\subsection*{Commodity canola model coefficients}
-
 \begingroup\fontsize{9}{11}\selectfont
@@
 \begin{longtable}{l|l|r|r|r|r|r|l|r|r}
+
+\caption{Summary of parameters for commodity canola models} \\
+
 \hline
@@
 
-\subsection*{Seed canola model coefficients}
+\subsection*{Seed canola models}
+
+Formulas for seed canola model using \texttt{lmer}-style R formulas.
+Terms on right side of $\sim$ indicate fixed effects, while terms in brackets indicate random effects (heirarchical intercepts).
+\textit{distribution} indicates the type of probability distribution function used to model each variable.
+
+\begin{align*}
+    \text{Plant Density} \sim & \text{HB Distance} + (1|\text{Field}), \text{distribution = log-normal} \\
+    \text{Plant Size} \sim & \text{HB Distance} + \text{Plant Density} + (1|\text{Field}) ,\text{distribution = log-t} \\
+    \text{Flower Density} \sim & \text{HB Distance} + (1|\text{Field}), \text{distribution = square root-t} \\
+    \text{LCB Visits} \sim & \text{offset}(log(\text{Time})) + \text{HB Distance} + \text{LCB Distance} + \text{Bay Centre} + \\
+    &   \text{Flower Density} + (1|\text{Field}), \text{family = ZI negative binomial} \\
+    \text{HB Visits} \sim & \text{offset}(log(\text{Time})) + \text{HB Distance} + \text{LCB Distance} + \text{Bay Centre} + \\
+    &   \text{Flower Density} + (1|\text{Field}), \text{family = ZI negative binomial} \\
+    \text{Pollen per Stigma} \sim & \text{HB Visits} + \text{LCB Visits} + \text{Bay Centre} + \text{HB Distance} + \text{LCB Distance} +\\
+    &   \text{Flower Density} + (1|\text{Field}) + (1|\text{Plot}), \text{family = negative binomial} \\
+    \text{Flowers per Plant} \sim & \text{Plant Size} + \text{Bay Centre} + \text{\% Pod Set} + (1|\text{Field}),\\
+    &   \phi \sim \text{Plant Size}, \text{family = negative binomial} \\
+    \text{\% Pod Set} \sim & \text{Pollen} + \text{Plant Size} + \text{Bay Centre} + \text{HB Distance} + \text{LCB Distance} + \\
+    &   \text{Flower Density} + (1|\text{Field}) + (1|\text{Plot}), \text{family = beta-binomial} \\
+    \text{Seeds per Pod} \sim & \text{Pollen} + \text{Plant Size} + \text{Bay Centre} + \text{HB Distance} + \text{Flower Density} +\\
+    &   \text{\% Pod Set} + \text{Flowers per plant} + (1|\text{Field}), \text{family = negative binomial} \\
+    \text{Weight per Seed} \sim & \text{Pollen} + \text{Seeds per Pod} + \text{Plant Size} + \text{LCB Distance} +\\
+    &   \text{Plant Density} + (1|\text{Field}), \text{family = exponential-normal}\\
+\end{align*}
 
@@
 \begin{longtable}{l|l|r|r|r|r|r|l|r|r}
+
+\caption{Summary of parameters for seed canola models} \\
+
 \hline
@@
 \endgroup{}
+
+\clearpage
+
+\subsection*{Total yield models}
+
+Formulas for total yield models are  using \texttt{lmer}-style R formulas.
+Predicted yield for each plant was calculated as: pods per plant $\times$ seeds per pod $\times$ weight per seed.
+Terms on right side of $\sim$ indicate fixed effects, while terms in brackets indicate random intercepts (and slopes).
+
+\begin{align*}
+    \text{Total Yield} \sim & log(\text{Predicted Yield}) + (log(\text{Predicted Yield})|\text{Field}) + \\
+    & (log(\text{Predicted Yield})|\text{Plot}), \text{distribution = log-normal} \\
+\end{align*}
+
+\begin{table}[h]
+\centering\begingroup\fontsize{9}{11}\selectfont
+\caption{Summary of parameters for total yield models}
+
+\begin{tabular}{l|l|r|r|r|r|r|r|r|r|r}
+\hline
+Field Type & Parameter & Mean & SD & Z & median & Min & Max & p-value & N$_{eff}$ & $\hat{R}$\\
+\hline
+ & Intercept & -0.318 & 0.042 & -7.62 & -0.317 & -0.397 & -0.236 & 0.000 & 982 & 1.000\\
+\cline{2-11}
+ & Predicted Yield & 1.007 & 0.018 & 55.64 & 1.007 & 0.972 & 1.044 & 0.000 & 1044 & 1.000\\
+\cline{2-11}
+ & Sigma (field intercept) & 0.119 & 0.041 & 2.89 & 0.112 & 0.051 & 0.216 & 0.004 & 292 & 1.020\\
+\cline{2-11}
+ & Sigma (field slope) & 0.026 & 0.019 & 1.37 & 0.023 & 0.001 & 0.072 & 0.170 & 295 & 1.013\\
+\cline{2-11}
+ & Sigma (plot intercept) & 0.389 & 0.037 & 10.47 & 0.388 & 0.318 & 0.465 & 0.000 & 506 & 1.005\\
+\cline{2-11}
+ & Sigma (plot slope) & 0.169 & 0.017 & 9.86 & 0.168 & 0.135 & 0.204 & 0.000 & 556 & 1.006\\
+\cline{2-11}
+ & Sigma & 0.253 & 0.008 & 33.30 & 0.253 & 0.239 & 0.268 & 0.000 & 2002 & 1.000\\
+\cline{2-11}
+ & Correlation (Int:Slope field) & -0.400 & 0.448 & -0.89 & -0.525 & -0.944 & 0.626 & 0.372 & 660 & 1.005\\
+\cline{2-11}
+\multirow{-9}{*}{\raggedright\arraybackslash Commodity} & Correlation (Int:Slope plot) & -0.989 & 0.007 & -140.44 & -0.990 & -0.998 & -0.972 & 0.000 & 936 & 1.005\\
+\cline{1-11}
+ & Intercept & -0.210 & 0.072 & -2.90 & -0.210 & -0.348 & -0.066 & 0.004 & 738 & 1.007\\
+\cline{2-11}
+ & Predicted Yield & 0.856 & 0.025 & 34.62 & 0.856 & 0.806 & 0.904 & 0.000 & 672 & 1.008\\
+\cline{2-11}
+ & Sigma (field intercept) & 0.040 & 0.018 & 2.28 & 0.038 & 0.011 & 0.079 & 0.022 & 226 & 1.005\\
+\cline{2-11}
+ & Sigma (field slope) & 0.010 & 0.007 & 1.56 & 0.009 & 0.001 & 0.023 & 0.118 & 217 & 1.005\\
+\cline{2-11}
+ & Sigma (plot intercept) & 0.097 & 0.013 & 7.26 & 0.097 & 0.072 & 0.124 & 0.000 & 470 & 1.005\\
+\cline{2-11}
+ & Sigma (plot slope) & 0.032 & 0.005 & 5.83 & 0.032 & 0.021 & 0.043 & 0.000 & 379 & 1.006\\
+\cline{2-11}
+ & Sigma & 0.289 & 0.012 & 23.59 & 0.289 & 0.266 & 0.314 & 0.000 & 1218 & 1.001\\
+\cline{2-11}
+ & Correlation (Int:Slope field) & -0.470 & 0.436 & -1.08 & -0.616 & -0.946 & 0.603 & 0.281 & 457 & 1.005\\
+\cline{2-11}
+\multirow{-9}{*}{\raggedright\arraybackslash Seed} & Correlation (Int:Slope plot) & -0.902 & 0.038 & -23.81 & -0.909 & -0.954 & -0.808 & 0.000 & 486 & 1.007\\
+\hline
+\end{tabular}
+\endgroup{}
+
+\label{tab:totalYieldCoefs}
+\end{table}

### 2022-08-15 Manuscript/main.tex
Worked on Discussion

@@
 %REVIEW THIS
-The limited pollen-transfering behaviour of HBs was also reflected in the pollen counts, as deposition strongly increased with LCB visitation, but not with HB visitation.
+The limited pollen-transferring behaviour of HBs was also reflected in the pollen counts, as deposition strongly increased with LCB visitation, but not with HB visitation.
 LCBs tend to switch between male and female flowers more frequently than HBs do \citep{waytesMsc}, transport more viable pollen between flowers \citep{parker2015}, and tend not to side-work canola flowers \citep{soroka2001}, which may explain their increased pollination efficacy.
@@
 
-Plant size increased pod set in commodity canola, but both plant size and pollen increased pod set in seed canola, suggesting that both pollen deposition and plant resources constrain pod production.
+Plant size increased the rate of pod set in commodity canola, but both plant size and pollen increased pod set in seed canola, suggesting that both pollen deposition and plant resources constrain pod production.
 This is similar to the findings of \citet{mesquida1981} and \citet{steffan2003}, who found that pod set in male-sterile plants responded positively to visitation, while male-fertile plants had no response (but see \citealp{adegas1992}).
@@
 
-Plant size increased seeds per pod in both crop types, but the number of seeds per pod in seed canola was also increased by pollen deposition and pod set. 
-Pollen deposition had a smaller effect than plant size (Z=2.3 vs.
+Extra pollination generally results in canola plants producing more, smaller-sized seeds (see review in \citealt{ouvrard2019}, but see also \citealtt{koltowski2005}), whereby the plant allocates the same number of resources to a greater number of fertilized ovules.
+We found mixed support across both crop types: seed size and number in commodity canola was mainly influenced by plant size, while seed canola was influenced by both plant size and pollen deposition.
+Seeds per pod was increased by plant size in both crop types, suggesting greater rates of ovule maturation in the presence of greater plant resources \citep{bouttier1992}.
+
+Pollen deposition had a smaller effect than plant size (Z = 2.3 vs.
 5.6), again suggesting that plant resources limit seed production more strongly than pollen deposition in seed canola \citep{marini2015}.
-\citet{mesquida1982} also found that pod production, rather than seeds per pod, was the main variable controlled by pollen deposition in seed canola.
-Position in the female bay influenced pollen deposition, both by wind and insects, indicating that the decrease in seed number at the centre of the bay is ultimately caused by reduced pollen deposition from lower visitation \citep{mesquida1981,mesquida1982}.
 
-Seed size was influenced by plant size in seed canola, but not commodity canola, and was not influenced by pollen or visitation in either crop \citep{riffkin2012}.
+In contrast, we found that seed size was influenced by plant size in seed canola alone, and was not influenced by pollen or visitation in either crop.
+
+While we d
+
 Unexpectedly, plant density had a \emph{positive} effect on seed size in both crop types, which we consider could have been caused by two different processes:
 plant density could be positively related to resource availability if plant survival is higher in plots with better growing conditions (i.e.
-Berkson's paradox \citep{snoep2014}) or plant density may improve the microclimate conditions of the canola stand, reducing heat or desiccation stress on individual plants.
+Berkson's paradox, \citep{snoep2014}) or plant density may improve the microclimate conditions of the canola stand, reducing heat or desiccation stress on individual plants.
 We consider the first process more likely, as planting density under uniform conditions typically has little effect on seed size \citep{Angadi2003}.
+
+% The decrease in seed number at the centre of the bay may ultimately be caused by reduced pollen deposition from lower visitation \citep{mesquida1981,mesquida1982}.
 

### 2022-09-06 Manuscript/main.tex
Temp switch to Multivac

@@
 
-This study examined how visitation contributes to pollen deposition and seed yield in two canola crops, and showed a strong link between visitation and yield in seed canola, but not in commodity canola.
+We examined how bee visitation contributes to pollen deposition and seed yield in two canola crops, and showed a strong link between visitation and yield in seed canola, but not in commodity canola.
 HB and LCB visitation decreased with distance from their respective hive or shelter, but unexpectedly, LCBs were found more at the edge of the crop.
@@
 %REVIEW THIS
-The limited pollen-transferring behaviour of HBs was also reflected in the pollen counts, as deposition strongly increased with LCB visitation, but not with HB visitation.
+Pollen count models revealed the limited pollen-transferring behaviour of HBs, as deposition strongly increased with LCB visitation but not HB visitation.
 LCBs tend to switch between male and female flowers more frequently than HBs do \citep{waytesMsc}, transport more viable pollen between flowers \citep{parker2015}, and tend not to side-work canola flowers \citep{soroka2001}, which may explain their increased pollination efficacy.
 Pollen deposition in seed fields also decreased with distance from the edge of the field, and was lower in the centre of the female bays, but this was not explained solely by LCB abundance (Figure \ref{fig:allSEM}).
-During foraging bouts, LCBs may travel further between flowers than HBs do \citep{brunet2019}, but pollen carryover from the edge to the centre of the bay female is likely reduced, as LCBs likely visit the edge of the female bay before venturing into the centre \citep{thomson1986, pinnisch1990}.
+During foraging bouts, LCBs may travel further between flowers than HBs do \citep{brunet2019}, but pollen carryover from the edge to the centre of the bay female is likely reduced, as LCBs likely visit the edge of the female bay before venturing into the centre \citep{thomso=n1986, pinnisch1990}.
 Pollen counts decreased with distance into the field (independent of visitation), suggests that pollinators are less efficient at transfering pollen.

### 2022-09-06 Manuscript/main.tex
Worked on Discussion

@@
 \emph{Bulbul}).
-However, \citet{waytesMsc} used male-sterile flowers from seed canola fields and found that HB pollen foragers deposited far less outcrossed pollen ($\sim$ 2 grains per visit), suggesting that much of the pollen deposited on commodity canola stigmas is self-pollen.
-Because the overall pollen deposition rates found in this study were so high, HB visitation seems to have made little difference in the amount of self-pollination, as large amounts of pollen were present on commodity canola stigmas even at the centre of unstocked fields.
-These results suggest that commodity canola stigmas are largely saturated with self-pollen, swamping any extra pollen deposition by HBs.
+However, \citet{waytesMsc} used male-sterile flowers from seed canola fields and found that HB pollen foragers deposited far less outcrossed pollen ($\sim$ 2 grains per visit), suggesting that much of the pollen deposited on commodity canola stigmas may be self-pollen.
+Because the overall pollen deposition rates found in this study were high, HB visitation seems to have made little difference in the amount of self-pollination, as large amounts of pollen were present on commodity canola stigmas even at the centre of unstocked fields.
+This suggests that commodity canola stigmas are largely saturated with self-pollen, swamping any extra pollen deposition by HBs.
 % The typical lifetime of a canola flower is approximately 3 days, and the stigmatic surface is receptive for 24--36 hours within this period \citep{eisikowitch1981,hoyle2007}, so it may be that 10-minutes of observing flower visitors was too short of a time interval to relate to pollen deposition.
@@
 
-%REVIEW THIS
-Pollen count models revealed the limited pollen-transferring behaviour of HBs, as deposition strongly increased with LCB visitation but not HB visitation.
-LCBs tend to switch between male and female flowers more frequently than HBs do \citep{waytesMsc}, transport more viable pollen between flowers \citep{parker2015}, and tend not to side-work canola flowers \citep{soroka2001}, which may explain their increased pollination efficacy.
-Pollen deposition in seed fields also decreased with distance from the edge of the field, and was lower in the centre of the female bays, but this was not explained solely by LCB abundance (Figure \ref{fig:allSEM}).
-During foraging bouts, LCBs may travel further between flowers than HBs do \citep{brunet2019}, but pollen carryover from the edge to the centre of the bay female is likely reduced, as LCBs likely visit the edge of the female bay before venturing into the centre \citep{thomso=n1986, pinnisch1990}.
-Pollen counts decreased with distance into the field (independent of visitation), suggests that pollinators are less efficient at transfering pollen.
-Foraging \textit{Bombus} take shorter trips between flowers under nectar-rich conditions (area-restricted search, \citealp{pyke1978b, heinrich1979}), suggesting that HBs and LCBs may operate similarly at the centre of seed fields, causing lower pollen deposition at the centre of the field where competition is lower.
-% This may be due to lower levels of competition at the centre of the field, leading to a higher nectar (or pollen) standing crop. %LH: more likely that bees at centre of F bays carry less pollen
-%LCBs are extremely fast fliers, and are difficult to follow after they leave an inflorescence, meaning that tracking their movements during an entire foraging bout would be almost impossible.
-% Visits by HB foragers were almost twice as high in the centre of the female bay, but pollen deposition was about 40\% lower (  Figure \ref{fig:allPollen}), which correspondingly is 
-% HBs in seed fields tended to visit more in the centre of the female bay, even close to the edge of the field, yet pollen deposition was still about 40\% lower (Figure \ref{fig:allPollen}).
-% While we found that LCBs also tend to avoid the centre of the female bays, and decrease with distance into the field, this extra dependence could have been caused by the fact that the visitation data represents a short ``snapshot'' of the pollen deposition process.
-% For example, canola flowers are receptive for 1-2 days before the petals dehisce, while the surveys only recorded 5 or 10 minutes of visitation, meaning we may have not captured the deposition process on the time scale that it occurs, and the extra variance is being accounted for by distance from field edge and the centre of the female bay.
-% Leafcutter visitation can be extremely sporadic, so the distance and bay position measurements capture differences in the average visitation process better than 10 minute measurements.
-% Pollen deposition also likely changes over the course of the season, as flower availability decreases.
+Our models also showed that pollen-transferring behaviour of HBs is limited in seed fields, as deposition strongly increased with LCB visitation but not HB visitation.
+HBs in seed fields tended to visit more in the centre of the female bay, even close to the edge of the field, yet pollen deposition was still about 40\% lower.
+LCBs switch between male and female flowers more frequently than HBs, travel further between flowers, transport more viable pollen, and tend not to side-work canola flowers \citep{soroka2001, parker2015, waytesMsc, brunet2019}, all of which may explain their higher pollination efficacy.
+Pollen deposition in seed fields also decreased with distance from the edge of the field, and was lower in the centre of the female bays independent of visitation, suggesting lower pollen tranfer per visit.
+These may have been caused by two separate processes: a) low pollen carryover with distance into the female bays, and b) shorter trips between flowers at the centre of the field.
+Pollen carryover from the edge to the centre of the bay female is likely reduced as LCBs typically visit the edge of the female bay before venturing into the centre \citep{thomson1986, pinnisch1990}.
+\textit{Bombus} take shorter trips between flowers under nectar-rich conditions \citep{pyke1978b, heinrich1979}, suggesting that HBs and LCBs may operate similarly at the centre of seed fields, resulting in lower pollen transfer.
+While manipulating nectar levels within a field to produce greater travel between flowers could be extremely difficult, this suggests that the optimal width of female bays within seed fields may be lower than is currently practiced.
+
+While we found that HBs have no direct effect on pollen deposition in either crop type, they may have an indirect positive effect caused by: a) increasing airborne pollen from male-fertile flowers \citet{pierre2010}, b) lowering nectar and pollen standing crop, causing LCBs to travel further \citep{pyke1978b, heinrich1979}, or c) lowering floral fidelity on higher-rewarding flowers in the male bays \citep{mesquida1978, waytesMsc,gaffney2019}.
+A simple test of this might be to remove HB hives from a seed field (mid-season) and observe changes in LCB visitation before and after the removal.
 
@@
 \citet{mesquida1978} also found that pod set in male-sterile canola declined quickly with distance from the male-fertile plants (due to wind pollination), but the effect we found is likely related to the earlier effect of lower pollen carryover at the centre of the female bays, and possibly the centre of the field.
-Finally, the effect size of pollen deposition (Z=3.1) was much smaller than that of plant size (Z=19.9), indicating that the factors controlling plant size (e.g.
-fertilizer application, soil quality) likely constrain pod production more strongly than pollination alone \citep{marini2015}.
+Finally, the effect of plant size was roughly 6x larger than that of pollen deposition, indicating that the factors controlling plant size (e.g.
+fertilizer application, soil quality) likely constrain pod production more strongly than pollination alone \citep{marini2015,tamburini2017, gagic2017, tamburini2019}.
 
@@
 Extra pollination generally results in canola plants producing more, smaller-sized seeds (see review in \citealt{ouvrard2019}, but see also \citealtt{koltowski2005}), whereby the plant allocates the same number of resources to a greater number of fertilized ovules.
-We found mixed support across both crop types: seed size and number in commodity canola was mainly influenced by plant size, while seed canola was influenced by both plant size and pollen deposition.
+We found mixed support across both crop types: seed size and number in commodity canola was mainly influenced by plant size, while seed size and number in seed canola was influenced by both plant size and pollen deposition.
 Seeds per pod was increased by plant size in both crop types, suggesting greater rates of ovule maturation in the presence of greater plant resources \citep{bouttier1992}. 
-
-Pollen deposition had a smaller effect than plant size (Z = 2.3 vs.
-5.6), again suggesting that plant resources limit seed production more strongly than pollen deposition in seed canola \citep{marini2015}.
-
-In contrast, we found that seed size was influenced by plant size in seed canola alone, and was not influenced by pollen or visitation in either crop.
-
-While we d
-
+Pollen deposition had a smaller effect on seeds per pod than plant size in seed canola, again suggesting that plant resources limit seed production more strongly than pollen deposition, even in pollen-limited crops \citep{marini2015}.
+In contrast, we found that seed size increased with plant size in seed canola alone, and was not influenced by pollen or visitation in either crop.
 Unexpectedly, plant density had a \emph{positive} effect on seed size in both crop types, which we consider could have been caused by two different processes:
@@
 
-\subsection*{Summary} %RC: VERY CANOLA-FOCUSED
+\subsection*{Conclusion}
 
-%Taken from pollen section
-HBs may have an indirect positive effect on pollen deposition, as they may cause LCBs to travel farther by lowering overall nectar and pollen standing crop, or release airborne pollen from male-fertile flowers.
-\citet{pierre2010} showed that HBs can increase the amount of airborne pollen by foraging on male-fertile flowers and releasing pollen from the anthers, causing increased yields in nearby male-sterile flowers; therefore, HBs may indirectly contribute to a higher rate of wind pollination.
-HBs may also cause LCBs to forage at further distances away from their shelters.
-Bumble bees move further between flowers when foraging in \textit{Trifolium} fields that have been depleted by HBs \citet{heinrich1979}, so a similar process could occur in canola seed fields. 
-LCBs do not appear to use area-restricted search \citep{brunet2019}, but we expect that the foraging range of leafcutter bees around their shelters would sitill decrease, because if HBs lower pollen and nectar levels at the edge of the field, then leafcutter bees should travel shorter distances to gather the same reward (according to the predictions of Chapter 2).
-We also expect that foraging leafcutter bees would make shorter trips between flowers (similar to \citealp{heinrich1979}), and possibly may switch between bays less frequently \citep{waytesMsc,gaffney2019}, due to a greater floral fidelity on higher-rewarding flowers in the male bay \citep{mesquida1978}.
-If this is true, this would result in a lower rate of (overall) pollen deposition by leafcutter bees during the same period.
-However, testing this would require observations of seed canola fields that were only stocked with leafcutter bees, which is extremely rare in southern Alberta.
-%RC: MAY HAVE TO CHOP FOR THE MANUSCRIPT, BECAUSE IT DOESN'T HAVE OTHER AREA-RESTRICTED SEARCH LIT
-%A simple test of this would be to remove HB hives from a seed field, mid-season, and perform observations of leafcutter visitation patterns before and after the removal.
+This study has revealed some of the detailed aspects of pollination in commodity and seed canola crops.
+First, it shows how two important species of commercial pollinators decline with distance from their nesting sites, and how LCBs unexpectedly decline with distance from the edge of the field.
+Second, it sheds light on the relative importance of HBs and LCBs as pollinators, showing that current levels of HB stocking do not strongly influence pollination in commodity canola crops, and that LCBs are likely the primary pollinators of seed canola.
+Finally, it contextualizes the value of pollination alongside plant resources, showing that plant resources and pollen limit production in seed canola, while only plant resources limit commodity production.
+Our unique SEM approach allowed us to formulate and test relationships within a causal framework, which we consider to be extremely valuable, and highly underused in agricultural studies.
+Our model serves as an approximation of a dynamic process, but could be built upon by using dynamic linear models \citep{iwasa2000,nord2011} to examine how plants dynamically respond to changes in pollination.
+These would lend greater understanding to the process of hybrid seed production, and could be used to more accurately predict crop yields in novel scenarios.
 
-This study assesses the relative importance of pollination and plant resources for the production of canola crops, using field-realistic data from central and southern Alberta.
-First, it shows that insect visitation changes across small spatial scales (meters for leafcutter bees, tens of meters for HBs), and are at odds with the large scales of Albertan crop fields \citep{fritz2015}.
-Visitation of both HBs and leafcutter bees in canola fields is concentrated at the edge of fields, and is lower at the centre of the female bays in seed canola.	
-Second, HBs have little direct influence on pollen deposition in either crop system, likely due to a high background level of pollen deposition on stigmas in commodity canola, whereby extra pollen deposition is of little benefit to plant reproduction.
-Seed canola plants, in contrast, have much lower levels of pollen deposition overall, and leafcutter bees deliver a large direct benefit to fruit and seed production. 
-The centre of the female bays illustrates this effect: HBs have a higher visitation rate, but pollen deposition, pod set, and seed set are all lower.
-Finally, both plant size and pollination limit seed production in seed canola, but only plant size limits commodity canola production, showing the relative importance of both pollination and plant resources using in-field data.
-
-Several future lines of work could be followed based on this study.
-First, other factors besides total seed yield are important for commodity canola production, such as green seed and oil content \citep{tautorus1994, abbadi2011, ghazani2013}.
-Our work identified the effect of bee pollination on seed production in terms of total weight, but may have overlooked these aspects of yield valuation \citep{bommarco2012}. 
-Secondly, we found that HBs appear to add little pollination value for seed canola crops, but since we did not use fields that had no HBs, there may be unobserved indirect benefits that HBs add.
-For example, they may contribute to better pollination by leafcutter bees by reducing the nectar and pollen standing crop, causing leafcutter bees to forager further away from their shelter \citep{pyke1978b, heinrich1979}, or by increasing the amount of airborne pollen \citep{eisikowitch1981,mesquida1982}.
-Third, while the random-intercept model that we used accounts for field-to-field variation in growing conditions, this also means that we may have marginalized across other factors that were not accounted for by plant size, such as nutrients, soil moisture, crop pests, and variety.
-Pollination benefits to all flowering crops are contextual, even in highly-pollination dependent crops \citep{tamburini2017, tamburini2019}; that is, the effect of additional pollination depends on the levels of other plant resources available during growth \citep{marini2015, bartomeus2015, gagic2017}.
-Finally, SEMs cannot model causal loops \citep{grace2006}, which is closer to the method by which plants respond to lack of pollination (\emph{i.e.} pollination failure $\rightarrow$ plant growth $\rightarrow$ flower production).
-Our model serves as an approximation of this process, but could be built upon by using dynamic linear programming techniques \citep{iwasa2000,nord2011} to examine how plants dynamically respond to pollen failure.
-These would lend greater understanding to the process of hybrid seed production, and could be used to more accurately predict crop yields in novel scenarios.
+% Several future lines of work could be followed based on this study.
+% First, other factors besides total seed yield are important for commodity canola production, such as green seed and oil content \citep{tautorus1994, abbadi2011, ghazani2013}.
+% Our work identified the effect of bee pollination on seed production in terms of total weight, but may have overlooked these aspects of yield valuation \citep{bommarco2012}. 
+% Secondly, we found that HBs appear to add little pollination value for seed canola crops, but since we did not use fields that had no HBs, there may be unobserved indirect benefits that HBs add.
+% For example, they may contribute to better pollination by leafcutter bees by reducing the nectar and pollen standing crop, causing leafcutter bees to forager further away from their shelter \citep{pyke1978b, heinrich1979}, or by increasing the amount of airborne pollen \citep{eisikowitch1981,mesquida1982}.
+% Third, while the random-intercept model that we used accounts for field-to-field variation in growing conditions, this also means that we may have marginalized across other factors that were not accounted for by plant size, such as nutrients, soil moisture, crop pests, and variety.
+% Pollination benefits to all flowering crops are contextual, even in highly-pollination dependent crops \citep{tamburini2017, tamburini2019}; that is, the effect of additional pollination depends on the levels of other plant resources available during growth \citep{marini2015, bartomeus2015, gagic2017}.
+% Finally, SEMs cannot model causal loops \citep{grace2006}, which is closer to the method by which plants respond to lack of pollination (\emph{i.e.} pollination failure $\rightarrow$ plant growth $\rightarrow$ flower production).
 

### 2022-09-07 Manuscript/main.tex
Worked on intro

@@
 Animal pollination of agricultural flowering plants is an important ecosystem service that contributes to about 10\% of total crop production value worldwide \citep{gallai2009}, and animal-pollinated plants produce a large number of important micronutrients in the human diet \citep{eilers2011}.
-Therefore, understanding the process of animal pollination in crops is economically and ecologically important. %REWORD? ECONOMICS DOESN'T COME INTO THE THESIS, SO MAYBE DON'T MENTION IT? 
-Agricultural pollination, however, is largely treated as a single process, even though there are many links in the chain of events that result in the production of a fruit.
-Visitation of flowers by animals, typically bees and other insects, can result in pollen deposition on the stigma of the flower, followed by the growth of pollen tubes into the style and fertilization of ovules \citep{erbar2003}.
-After fertilization, the plant may provide resources to fertilized fruits (or ovules within a fruit) to mature them into fruit \citep{goldberg1994}.
-Each step has many other underlying processes (\textit{e.g.} stigma receptivity, pollen tube growth, ovule abortion, fruit maturation, reviewed in \citealp{real1983, giovannoni2001, erbar2003, takayama2005}, and others), but even at the level of this coarse approximation, most studies of agricultural pollination fail to account for important underlying processes.
-Pollinating animals rarely visit equally on all flowers in a blooming crop field\citep{currie1997, brosi2008, isaacs2010}, but some agronomic studies implicitly make this assumption \citep{phillips1989, bommarco2012, bartomeus2014}.
-Pollen deposition from visitors depends on a number of factors (\textit{e.g} behaviour on flowers, size of pollinator), and whether this deposited pollen from visitors results in increased fruit production depends on the pollination context (\textit{e.g.} self-pollination) and the life history and resource contexts of the plant (\textit{e.g.} annual vs.
+Pollination, however, is largely treated as a single process, even though there are many links in the chain of events that result in the production of a fruit.
+Visitation of flowers by animals (typically bees or other insects) can increase pollen deposition on the stigma of the flower, followed by fertilization of the ovules, and maturation of the ovaries into mature fruit \citep{erbar2003, goldberg1994}.
+Each step has many other underlying processes (\textit{e.g.} stigma receptivity, pollen tube growth, ovule abortion, fruit maturation, reviewed in \citealp{real1983, giovannoni2001, erbar2003, takayama2005}, and others), but even at this level of approximation, most studies of agricultural pollination fail to account for important underlying processes.
+Moving beyond this ``black-box" model of agricultural pollination requires accounting for these steps, and is needed for contextualizing the value of pollination services, as well as optimizing crop yield in novel circumstances.
+
+% Pollinating animals rarely visit equally on all flowers in a blooming crop field\citep{currie1997, brosi2008, isaacs2010}, but some agronomic studies implicitly make this assumption \citep{phillips1989, bommarco2012, bartomeus2014}.
+% Pollen deposition from visitors depends on a number of factors (\textit{e.g} behaviour on flowers, size of pollinator), and whether this deposited pollen from visitors results in increased fruit production depends on the pollination context (\textit{e.g.} self-pollination) and the life history and resource contexts of the plant (\textit{e.g.} annual vs.
 perennial, determinate vs.
 indeterminate growth, light, soil nutrients and moisture).
-Moving beyond the ``black-box" model of agricultural pollination requires accounting for these steps, and is necessary for understanding the contextual value of pollination services, as well as optimizing crop yield in novel circumstances.
 %affect roughly one-third of the world's agricultural crops \citep{klein2007}
 
-Pollinator visitation is not spatially uniform within fields, as most pollinators are central-place foragers, meaning that visitation rates decline with distance away from their nest, and the bloom of flowering crops is not uniform.
-%REWORD
+\subsection{Insect visitation}
+
+Pollinator visitation is not spatially uniform within fields, as visitation rates typically decline with distance away from their nest site.
 Smaller bees fly shorter distances than larger bees \citep{greenleaf2007,zurbuchen2010}, so their presence at the centre of large fields can be limited \citep{isaacs2010}. 
 Hence, managing the location and density of managed pollinators in relation to their target crops is important for optimal yield of pollinator-dependent crops \citep{fries1983,cresswell2004b}.
-Foraging insects will often specialize on certain species or morphs of flowers in order to forage more efficiently \citep{heinrich1976b, goulson1997}. 
-However, pollination of hybrid seed crops requires movement of pollen between spatially separated lines of plants, so floral specialization can reduce the pollination services in these systems \citep{waytesMsc, gaffney2019}.
-Competition between different species of foraging insects can occur if they deplete floral resources, but foragers can spatially or temporally separate their foraging to reduce competition (\citealp{schaffer1979,thomson1987}, but see \citealp{steffan2000}), thereby increasing their fitness.
-Both resource depletion or interference competition can motivate visitors to reduce competition by increasing their foraging distance, switching between floral morphs more often, or visiting less frequently \citep{heinrich1979, greenleaf2006}.
-Thus, variation in visitation is driven by both distance from their nest (see Chapter 2), as well as competition with foragers from other aggregations, and increased competition can benefit plant fitness.
+Similarly, foragers will often specialize on certain species or morphs of flowers in order to forage more efficiently (floral fidelity, \citealp{heinrich1976b, goulson1997}). 
+Pollination of hybrid seed crops presents a conundrum: it requires movement of pollen between separate lines of plants, meaning that fidelity can reduce the pollen transfer in these systems \citep{waytesMsc, gaffney2019}.
+Competition between different species of foraging insects can occur if they deplete floral resources, but foragers can spatially or temporally separate their foraging to reduce competition (\citealp{schaffer1979,thomson1987}, but see \citealp{steffan2000}).
+This can motivate visitors to reduce competition by increasing their foraging distance, switching between floral morphs more often, or visiting less frequently \citep{heinrich1979, greenleaf2006}.
+Thus, variation in visitation can be driven by distance, competition with other foragers, or floral specialization; however, this is seldom considered, as commercial pollinators are often treated as a single agricultural ``input" (akin to fertilizer).
 % Much of the worldwide agricultural demand for insect pollination is accomplished by the European honey bee, (\textit{Apis mellifera} L., hereafter ``honey bee") because of its large colony size, ease of transport, and ease of breeding (\citealp{winston1991}, but see also \citealp{winfree2008}).
@@
 Insect visitation of flowers can enhance fruit production in flowering plants by increasing either the quantity or quality of pollen deposited on the stigma \citep{stephenson1981,burd1994,aizen2007}, providing a larger range of female mate choice for each flower.
-Many flowering plant species are capable of self-pollination, but typically produce more fruit or seeds from outcrossed pollen \citep{knight2005} transported from conspecific plants by wind or an animal vector, but not all animal visitors are equal from a flowering plant's perspective.
-For example, large-bodied insects can deposit more pollen per visit on the stigma of the flower because they have a greater chance of contacting the stigmatic surface \citep{sahli2007}. 
-Pollinator behaviour is also important, as flower-visiting insects may steal nectar, clean off pollen between visits, or travel mainly between flowers on the same plant \citep{thomson1986, herrera1987}.
+Many flowering plant species are capable of self-pollination, but typically produce more fruit or seeds from outcrossed pollen \citep{knight2005} transported from conspecific plants by wind or an animal vector.
+Not all animal visitors are equal from a flowering plant's perspective: large-bodied insects can deposit more pollen per visit on the stigma of the flower \citep{sahli2007}.
+Similarly, not all pollinators behave the same: flower-visiting insects may steal nectar, groom pollen between visits, or travel mainly between flowers on the same plant \citep{thomson1986, herrera1987}.
 Finally, the benefit of extra pollen deposition is diminishing \citep{plowright1981}, with very high numbers of pollen grains causing less and less of an increase in fruit production \citep{ashman2004, harder2016}.
-%; some are obligate outcrossers, and have self-incompatibility mechanisms in place to prevent fertilization by their own pollen.
-% Other plants have separate male and female flowers, or separate male and female plants, so their pollen must be transported from male flowers to female flowers, either by wind or an animal vector.
+Again, this is seldom considered within agricultural systems, but some do examine optimal rates of stocking.
 
-%REVIEW LANGUAGE
-%RC: POINT OF PARAGRAPH SHOULD BE THAT AFTER POLLEN RECEIPT, PLANT STILL HAS TO DECIDE WHETHER TO ACCEPT IT, OR WAIT TO INVEST LATER (FUTURE-PRESENT TRADEOFFS)
-%RALPH'S ARGUMENT IS WAY TOO GENERAL. POINT SHOULD BE THAT POLLEN OR RESOURCES CAN BE LIMITING (USUALLY RESOURCES), AND THAT PLANT MAY COMPENSATE FOR LOW POLLEN USING EXTRA GROWTH
+\subsection{Plant resources}
+
+%START HERE
+
 Seed production can be limited by plant resources as well as pollen \citep{galen1985, haig1988,campbell1993}, meaning that the benefits of insect pollination depend on the resources available to the plant \citep{stephenson1981, tamburini2017}.
@@
 First, it shows how two important species of commercial pollinators decline with distance from their nesting sites, and how LCBs unexpectedly decline with distance from the edge of the field.
-Second, it sheds light on the relative importance of HBs and LCBs as pollinators, showing that current levels of HB stocking do not strongly influence pollination in commodity canola crops, and that LCBs are likely the primary pollinators of seed canola.
+Second, it sheds light on the relative importance of HBs and LCBs as pollinators, showing that commonly-used levels of HB stocking do not strongly influence yield in commodity canola crops, and that LCBs are likely the primary pollinators of seed canola.
 Finally, it contextualizes the value of pollination alongside plant resources, showing that plant resources and pollen limit production in seed canola, while only plant resources limit commodity production.

### 2022-09-08 Manuscript/main.tex
Worked on Introduction

@@
 Animal pollination of agricultural flowering plants is an important ecosystem service that contributes to about 10\% of total crop production value worldwide \citep{gallai2009}, and animal-pollinated plants produce a large number of important micronutrients in the human diet \citep{eilers2011}.
-Pollination, however, is largely treated as a single process, even though there are many links in the chain of events that result in the production of a fruit.
-Visitation of flowers by animals (typically bees or other insects) can increase pollen deposition on the stigma of the flower, followed by fertilization of the ovules, and maturation of the ovaries into mature fruit \citep{erbar2003, goldberg1994}.
-Each step has many other underlying processes (\textit{e.g.} stigma receptivity, pollen tube growth, ovule abortion, fruit maturation, reviewed in \citealp{real1983, giovannoni2001, erbar2003, takayama2005}, and others), but even at this level of approximation, most studies of agricultural pollination fail to account for important underlying processes.
+Pollination of these crops, however, is largely treated as a single process, even though there are many links in the chain of events that result in the production of a fruit.
+Visitation of flowers by animals (typically bees or other insects) can increase pollen deposition on the stigma of the flower, followed by fertilization of the ovules, and maturation of fruit \citep{erbar2003, goldberg1994}.
+Each step has many other underlying processes (\textit{e.g.} stigma receptivity, pollen tube growth, ovule abortion), but even at this level of approximation, most studies of agricultural pollination fail to account for important underlying processes.
 Moving beyond this ``black-box" model of agricultural pollination requires accounting for these steps, and is needed for contextualizing the value of pollination services, as well as optimizing crop yield in novel circumstances.
@@
 
-\subsection{Insect visitation}
+% INSECT VISITATION
 
-Pollinator visitation is not spatially uniform within fields, as visitation rates typically decline with distance away from their nest site.
+Pollinator visitation is not uniform within fields: visitation rates typically decline with distance away from the pollinators' nest sites.
 Smaller bees fly shorter distances than larger bees \citep{greenleaf2007,zurbuchen2010}, so their presence at the centre of large fields can be limited \citep{isaacs2010}. 
-Hence, managing the location and density of managed pollinators in relation to their target crops is important for optimal yield of pollinator-dependent crops \citep{fries1983,cresswell2004b}.
+Hence, managing the location and density of managed pollinators is important for optimal yield of pollinator-dependent crops \citep{fries1983,cresswell2004b}.
 Similarly, foragers will often specialize on certain species or morphs of flowers in order to forage more efficiently (floral fidelity, \citealp{heinrich1976b, goulson1997}). 
-Pollination of hybrid seed crops presents a conundrum: it requires movement of pollen between separate lines of plants, meaning that fidelity can reduce the pollen transfer in these systems \citep{waytesMsc, gaffney2019}.
-Competition between different species of foraging insects can occur if they deplete floral resources, but foragers can spatially or temporally separate their foraging to reduce competition (\citealp{schaffer1979,thomson1987}, but see \citealp{steffan2000}).
-This can motivate visitors to reduce competition by increasing their foraging distance, switching between floral morphs more often, or visiting less frequently \citep{heinrich1979, greenleaf2006}.
+Pollination of hybrid seed crops presents a challenge for specialized foragers, as it requires movement of pollen between separate lines of plants, meaning that fidelity can reduce pollen transfer \citep{waytesMsc, gaffney2019}.
+Competition for floral resources can occur between different species of foragers, but they can spatially or temporally separate their foraging to reduce competition (\citealp{schaffer1979,thomson1987}, but see \citealp{steffan2000}), such as switching between floral morphs more often, or visiting less frequently \citep{heinrich1979, greenleaf2006}.
 Thus, variation in visitation can be driven by distance, competition with other foragers, or floral specialization; however, this is seldom considered, as commercial pollinators are often treated as a single agricultural ``input" (akin to fertilizer).
@@
 
-Insect visitation of flowers can enhance fruit production in flowering plants by increasing either the quantity or quality of pollen deposited on the stigma \citep{stephenson1981,burd1994,aizen2007}, providing a larger range of female mate choice for each flower.
-Many flowering plant species are capable of self-pollination, but typically produce more fruit or seeds from outcrossed pollen \citep{knight2005} transported from conspecific plants by wind or an animal vector.
-Not all animal visitors are equal from a flowering plant's perspective: large-bodied insects can deposit more pollen per visit on the stigma of the flower \citep{sahli2007}.
-Similarly, not all pollinators behave the same: flower-visiting insects may steal nectar, groom pollen between visits, or travel mainly between flowers on the same plant \citep{thomson1986, herrera1987}.
-Finally, the benefit of extra pollen deposition is diminishing \citep{plowright1981}, with very high numbers of pollen grains causing less and less of an increase in fruit production \citep{ashman2004, harder2016}.
-Again, this is seldom considered within agricultural systems, but some do examine optimal rates of stocking.
+Seed production can be limited by plant resources as well as pollen, meaning that the benefits of insect pollination depend on the resources available to the plant \citep{stephenson1981, marini2015, tamburini2017, tamburini2019}.
+Pollination can enhance fruit production in flowering plants by increasing either the quantity or quality of pollen deposited on the stigma \citep{stephenson1981,burd1994,aizen2007}.
+Many flowering plant species are capable of self-pollination, but can produce more fruit or seeds from outcrossed pollen \citep{knight2005}.
+However, the benefit of this extra pollen deposition is diminishing \citep{plowright1981}, with very high numbers of pollen grains causing less and less of an increase in fruit production \citep{ashman2004, harder2016}.
+% Not all animal visitors are equal from a flowering plant's perspective: large-bodied insects can deposit more pollen per visit on the stigma of the flower \citep{sahli2007}, but some visitors may steal nectar, groom pollen between visits, or travel mainly between flowers on the same plant \citep{thomson1986, herrera1987}, reducing their utility to the plant.
+Pollen limitation can also occur at multiple levels within a plant, reducing the number of seeds per fruit or the number of mature fruit \citep{burd1994}.
+Low pollen deposition cause flower abortion, where poorly-pollinated flowers are cut off from the plant \citep{knight2006}, but an indeterminate growth strategy may help to offset this, by simply making more flowers \citep{doust1982,lawrence1993, sabbahi2006, bos2007}.
+Additional pollen may result in a greater number of seeds per fruit \citep{knight2006}, which in turn may result in a reduction in the size per seed due to competition between ovules or fruit \citep{free1968, mazer1987}.
+Seed size can also vary strongly among plants, and can be affected by resources available to the plant \citep{mazer1987, venable1992}. 
+Therefore, understanding how plants allocate their seed resources under pollen or resource deficits are important for managing agricultural production \citep{bos2007, tamburini2019}.
 
-\subsection{Plant resources}
-
-%START HERE
-
-Seed production can be limited by plant resources as well as pollen \citep{galen1985, haig1988,campbell1993}, meaning that the benefits of insect pollination depend on the resources available to the plant \citep{stephenson1981, tamburini2017}.
-Pollen limitation can also occur at multiple levels within a plant, reducing the number of seeds per fruit, the number of mature fruit, or both \citep{burd1994}.
-Low pollen deposition may reduce the number of mature fruit via flower abortion \citep{knight2006}, where poorly-pollinated flowers are cut off from the plant.
-Plants with an indeterminate growth strategy may compensate for a high flower abortion rate by simply making more flowers, resulting in similar seed production to pollinated plants \citep{doust1982,lawrence1993, sabbahi2006, bos2007}.
-Whether individual plants can compensate for low pollination depends on the time remaining in the season, as well as the resources available to create extra shoots and flowers.
-Pollen limitation may also reduce the number of seeds per fruit, so additional pollen may result in a greater number of seeds per fruit \citep{knight2006}, which in turn may result in a reduction in the size per seed \citep{free1968, mazer1987} due to competition between ovules.
-Seed size can vary strongly among plants, and can be affected by resources available to the plant \citep{mazer1987, venable1992}. 
-For example, \citet{maddox1983} observed a negative size-number tradeoff in \emph{Plantago} seeds, but only after accounting for the positive effect of plant size, indicating that larger plants were better able to provision their seeds.
-Since the size and number of offspring are direct determinants of a given plant's fitness, and the yield of the plant in an agricultural setting, allocation strategies that plants use under situations of pollen or resource deficits are important both theoretically, and in the context of food production \citep{bos2007, tamburini2019}.
+% For example, \citet{maddox1983} observed a negative size-number tradeoff in \emph{Plantago} seeds, but only after accounting for the positive effect of plant size, indicating that larger plants were better able to provision their seeds.
 %, as the optimum seed size may differ depending on the growing conditions \citep{silvertown1989}.
@@
 
-Insect pollination is especially important in the production of hybrid canola crops (\textit{Brassica napus} L.).
-Hybrid ``commodity canola" (used for oil and meal production) is the offspring of two parental ``seed canola" breeding lines, a male-sterile ``female" line and a hermaphroditic  ``male" line \citep{westcott2001,steffan2003,clay2009}.
-Seed canola production requires a large number of pollinators to ensure pollination of the female line (seed from the male line is not harvested), and extra pollination may also increase the yield of commodity canola \citep{morandin2005,rader_phd,bommarco2012,bartomeus2015,perrot2018}.
-However, many studies of commodity canola pollination suffer from either a lack of realistic context, have a number of potential confounding variables, or infer plant-level outcomes from flower-level treatments.
-Greenhouse experiments typically involve unrealistically high pollination, nutrient availability, and water, all of which can influence yield \citep{bartomeus2015,marini2015}.
-Field studies often relate yield to indirect measures of pollination services, such as insect abundance, species richness, or distance from sources of potential pollinators \citep{morandin2005,ricketts2008}, rather than direct measures, such as visitation rates or pollen deposition per stigma.
-These pollination proxies are then related to measures of yield, such as grams of seed per m$^2$, which may be useful to growers, but provide limited information about how plants dynamically respond to pollen exclusion or addition (but see \citealp{sabbahi2005}).
-Net- or cage-treatments exclude insect vistiation from certain plants or flowers, but can alter wind pollination, humidity, light, or pest pressure \citep{olsson1960, neal2004, jauker2008}, meaning that the sole effect of lower insect visitation is confounded by other factors.
-These methods offer an incomplete picture of how pollination relates to yield in canola crops \citep{ouvrard2019}, and obscure estimates of pollinator value in a globally valuable crop species \citep{melathopoulos2015}.
-Thus, whether pollination impacts commodity canola production (or if not, why not) is poorly understood.
+Insect pollination is especially important in the production of canola crops (\textit{Brassica napus} L.).
+Hybrid \emph{commodity canola} (used for oil and meal production) is the offspring of two parental \emph{seed canola} breeding lines, a male-sterile ``female" and a hermaphroditic ``male" line \citep{westcott2001,steffan2003,clay2009}.
+Seed canola production requires a large number of pollinators to ensure pollination of the female line (seed from the male line is not harvested), but there are few published studies that examine pollination in these systems (see \citealp{mesquida1981, mesquida1991}).
+Extra pollination may also increase the yield of commodity canola \citep{morandin2005,rader_phd,bommarco2012,bartomeus2015,perrot2018}, but this is unclear, as many  key studies suffer from either a lack of realistic context, have a number of potential confounding variables, or infer plant-level outcomes from flower-level treatments \citep{ouvrard2019}.
+Greenhouse experiments typically involve unrealistically high levels of pollination, nutrient availability, and water, all of which can interact with yield \citep{bartomeus2015,marini2015}.
+Field studies often relate yield to indirect measures of pollination services, such as insect abundance, species richness, or distance from sources of potential pollinators \citep{morandin2005,ricketts2008}, rather than visitation rates or pollen deposition.
+These proxies provide limited information about how plants dynamically respond to pollen exclusion or addition (but see \citealp{sabbahi2005}).
+Net- or cage-treatments exclude insect visitation from certain plants or flowers, but can alter wind pollination, humidity, light, or pest pressure \citep{olsson1960, neal2004, jauker2008}.
+All of these methods give an incomplete picture of how pollination relates to yield in canola crops \citep{ouvrard2019}, and obscure estimates of pollinator value in a globally valuable crop species \citep{melathopoulos2015}.
+
 %and both honey bees and leafcutter bees are used in Canada 
@@
 
-Fruit production in plants involves a sequence of processes (visitation $\rightarrow$ pollen deposition $\rightarrow$ fruit production $\leftarrow$ plant resources), that determine the magnitude of the link between pollination and the components of crop yield.
-However, most studies of how pollination relates to crop yield either examine each process independently, or omit intermediate steps in the sequence of events (but see \citealp{saez2018}), meaning that the relative importance of visitation and plant resources are unresolved.
-Using both commodity and seed canola provides an opportunity to compare two plant varieties that differ strongly in their pollination requirements, using a similar type of structural model, while accounting for agricultural differences between varieties (spatial arrangement, planting density, irrigation).
-% Since the process linking insect visitation to seed production has several intermediate steps, and is contingent on resource factors, we need a more complete model of crop yield that links plant-level responses to biological processes that occur at the plot and field level.
-%Introduce each component of the path analysis
+Seed production in canola involves a sequence of processes (visitation $\rightarrow$ pollen deposition $\rightarrow$ fruit production $\leftarrow$ plant resources), that determine the magnitude of the link between pollination and the components of crop yield (seed size/number).
+However, other studies of canola pollination focus on individual processes, such as visitation and pollination \citep{cresswell1999, thomson2001}, or visitation and yield \citep{steffan2003, manning2005, hudewenz2013}, but have not incorporated the links in a single framework (but see \citealp{saez2018}), and few have used realistic field data \citep{morandin2005, isaacs2010}.
+In this study, we examine how distance influences pollinator visitation, which in turn influences pollen deposition and seed yield, using commodity and seed canola crops in Alberta, Canada.
+Using both commodity and seed canola provides an opportunity to compare two plant varieties that differ strongly in their pollination requirements, using a similar type of structural model, while accounting for agricultural differences between varieties.
+We expected that extra pollination would increase pollination and seed production in commodity canola, but that the magnitude of the increase would be much higher in seed canola, and that plant size (a proxy for plant resources) would similarly increase seed production.
+This study assesses the strength of the connections between visitation, pollination, and yield, in a globally important crop species, and identifies the relative importance of bee pollination for seed production, using in-field data from two distinct cropping systems.
 
-%SH: SEEMS ODD TO HAVE REFS MIXED IN WITH YOUR HYPOTHESES
-In this study, we modeled how distance influences pollinator visitation, which in turn influences pollen deposition and seed yield, using commodity and hybrid seed canola crops in Alberta, Canada.
-Our five main hypotheses are outlined as follows:
-\begin{enumerate} 
-    \item Foraging honey bees and leafcutter bees are sensitive to distance due to cost of flight \citep{schmid1985}, and deplete floral resources with visitation.
+% Since the processes linking insect visitation to seed production has several intermediate steps, and is contingent on resource factors, we need a more complete model of crop yield that links plant-level responses to biological processes that occur at the plot and field level.
+% This work adds to the body of literature examining the resource context of pollination services \citep{haig1988} within cropping systems \citep{marini2015, tamburini2016, fijen2018, tamburini2019}, and identifies directions of future research in seed production systems.
+
+% Our five main hypotheses are outlined as follows:
+% \begin{enumerate} 
+%     \item Foraging honey bees and leafcutter bees are sensitive to distance due to cost of flight \citep{schmid1985}, and deplete floral resources with visitation.
 Therefore, insect visitation should decline with distance from their hive or shelter to achieve equivalent rewards \citep{dukas1998, cresswell2000}.
-    \item Visiting bees can deposit pollen on stigmas, so areas with high rates visitation should have more pollen deposition on stigmas than areas with low rates of visitation \citep{mesquida1988c, hoyle2007}, depending on foraging behaviour of the bee \citep{free1983}.
-    % \item Plant size is limited by resources, which can be reduced by competition with neighbours, so areas with fewer plants per m$^2$ should have larger plants \citep{angadi2003}. %Not revelvant
-    \item Seed production for a given plant is limited by the resources it is able to sequester.
+%     \item Visiting bees can deposit pollen on stigmas, so areas with high rates visitation should have more pollen deposition on stigmas than areas with low rates of visitation \citep{mesquida1988c, hoyle2007}, depending on foraging behaviour of the bee \citep{free1983}.
+%     % \item Plant size is limited by resources, which can be reduced by competition with neighbours, so areas with fewer plants per m$^2$ should have larger plants \citep{angadi2003}. %Not revelvant
+%     \item Seed production for a given plant is limited by the resources it is able to sequester.
 Therefore, large plants should have more resources at their disposal, and should produce more fruit per plant and produce a higher number of larger seeds per fruit \citep{galen1985, lawrence1993, marini2015}.
-    \item Seed production in resource-rich plants is also limited by pollination.
+%     \item Seed production in resource-rich plants is also limited by pollination.
 Plants in areas with high pollen deposition should have a higher proportion of successful flowers \citep{sabbahi2005}, and a higher number of seeds per pod \citep{morandin2005}.
-\end{enumerate}
-
-%REVIEW
-This study assesses the strength of the connections between visitation, pollination, and yield, in a globally important crop species, and identifies the relative importance of bee pollination for seed production, using in-field data from two distinct cropping systems.
-Other studies of crop pollination focus on individual components, such as visitation and pollination \citep{cresswell1999, thomson2001}, or visitation and yield \citep{steffan2003, manning2005, hudewenz2013}, but have not incorporated the links in a single framework (but see \citealp{saez2018}), and few have used realistic field data \citep{morandin2005, isaacs2010}.
-This work adds to the body of literature examining the resource context of pollination services \citep{haig1988} within cropping systems \citep{marini2015, tamburini2016, fijen2018, tamburini2019}, and identifies directions of future research in seed production systems.
+% \end{enumerate}
 
@@
 Our unique SEM approach allowed us to formulate and test relationships within a causal framework, which we consider to be extremely valuable, and highly underused in agricultural studies.
-Our model serves as an approximation of a dynamic process, but could be built upon by using dynamic linear models \citep{iwasa2000,nord2011} to examine how plants dynamically respond to changes in pollination.
+Our model serves as an approximation of a dynamic process, but could be built upon by using dynamic linear models \citep{iwasa2000, nord2011, saez2018} to examine how plants dynamically respond to changes in pollination.
 These would lend greater understanding to the process of hybrid seed production, and could be used to more accurately predict crop yields in novel scenarios.

### 2022-09-08 sem plots.R
Updated SEM plots

@@ -125,12 +125,8 @@ nodeCoords <- data.frame(name=c('numHives','hbeeDist','lbeeDist','hbeeVis','lbee
                                 'Honey bee\nVisits','Leafcutter\nVisits','Pollen\nCount',
                                 'Plant\nSize','Plant\nDensity','Flower\nDensity','Bay Centre',
                                 'Flowers\nper Plant','Pod Set\n(%)','Seeds\nper Pod','Seed\nSize'),
-                         x=c(0,0,1,0,1,0.5,
-                             2.5,0,1,0.5,
-                             3.5,4,2.5,3.5),
-                         y=c(4,4,4,3,3,2,
-                             0,1,1,0.5,
-                             0,1,3,2))
+                         x=c(0,0,1,0,1,0.5,2.5,0,1,0.5,3.5,4,2.5,3.5),
+                         y=c(4,4,4,3,3,2,0,1,1,0.5,0,1,3,2))
 
 
 #Specify model

### 2022-09-08 Manuscript/main.tex
Updated main text

--- 2022-09-06 Manuscript/main.tex
@@
 
-We examined how bee visitation contributes to pollen deposition and seed yield in two canola crops, and showed a strong link between visitation and yield in seed canola, but not in commodity canola.
+This study examined how visitation contributes to pollen deposition and seed yield in two canola crops, and showed a strong link between visitation and yield in seed canola, but not in commodity canola.
 HB and LCB visitation decreased with distance from their respective hive or shelter, but unexpectedly, LCBs were found more at the edge of the crop.
@@
 \emph{Bulbul}).
-However, \citet{waytesMsc} used male-sterile flowers from seed canola fields and found that HB pollen foragers deposited far less outcrossed pollen ($\sim$ 2 grains per visit), suggesting that much of the pollen deposited on commodity canola stigmas may be self-pollen.
-Because the overall pollen deposition rates found in this study were high, HB visitation seems to have made little difference in the amount of self-pollination, as large amounts of pollen were present on commodity canola stigmas even at the centre of unstocked fields.
-This suggests that commodity canola stigmas are largely saturated with self-pollen, swamping any extra pollen deposition by HBs.
+However, \citet{waytesMsc} used male-sterile flowers from seed canola fields and found that HB pollen foragers deposited far less outcrossed pollen ($\sim$ 2 grains per visit), suggesting that much of the pollen deposited on commodity canola stigmas is self-pollen.
+Because the overall pollen deposition rates found in this study were so high, HB visitation seems to have made little difference in the amount of self-pollination, as large amounts of pollen were present on commodity canola stigmas even at the centre of unstocked fields.
+These results suggest that commodity canola stigmas are largely saturated with self-pollen, swamping any extra pollen deposition by HBs.
 % The typical lifetime of a canola flower is approximately 3 days, and the stigmatic surface is receptive for 24--36 hours within this period \citep{eisikowitch1981,hoyle2007}, so it may be that 10-minutes of observing flower visitors was too short of a time interval to relate to pollen deposition.
@@
 
-Our models also showed that pollen-transferring behaviour of HBs is limited in seed fields, as deposition strongly increased with LCB visitation but not HB visitation.
-HBs in seed fields tended to visit more in the centre of the female bay, even close to the edge of the field, yet pollen deposition was still about 40\% lower.
-LCBs switch between male and female flowers more frequently than HBs, travel further between flowers, transport more viable pollen, and tend not to side-work canola flowers \citep{soroka2001, parker2015, waytesMsc, brunet2019}, all of which may explain their higher pollination efficacy.
-Pollen deposition in seed fields also decreased with distance from the edge of the field, and was lower in the centre of the female bays independent of visitation, suggesting lower pollen tranfer per visit.
-These may have been caused by two separate processes: a) low pollen carryover with distance into the female bays, and b) shorter trips between flowers at the centre of the field.
-Pollen carryover from the edge to the centre of the bay female is likely reduced as LCBs typically visit the edge of the female bay before venturing into the centre \citep{thomson1986, pinnisch1990}.
-\textit{Bombus} take shorter trips between flowers under nectar-rich conditions \citep{pyke1978b, heinrich1979}, suggesting that HBs and LCBs may operate similarly at the centre of seed fields, resulting in lower pollen transfer.
-While manipulating nectar levels within a field to produce greater travel between flowers could be extremely difficult, this suggests that the optimal width of female bays within seed fields may be lower than is currently practiced.
-
-While we found that HBs have no direct effect on pollen deposition in either crop type, they may have an indirect positive effect caused by: a) increasing airborne pollen from male-fertile flowers \citet{pierre2010}, b) lowering nectar and pollen standing crop, causing LCBs to travel further \citep{pyke1978b, heinrich1979}, or c) lowering floral fidelity on higher-rewarding flowers in the male bays \citep{mesquida1978, waytesMsc,gaffney2019}.
-A simple test of this might be to remove HB hives from a seed field (mid-season) and observe changes in LCB visitation before and after the removal.
+%REVIEW THIS
+The limited pollen-transferring behaviour of HBs was also reflected in the pollen counts, as deposition strongly increased with LCB visitation, but not with HB visitation.
+LCBs tend to switch between male and female flowers more frequently than HBs do \citep{waytesMsc}, transport more viable pollen between flowers \citep{parker2015}, and tend not to side-work canola flowers \citep{soroka2001}, which may explain their increased pollination efficacy.
+Pollen deposition in seed fields also decreased with distance from the edge of the field, and was lower in the centre of the female bays, but this was not explained solely by LCB abundance (Figure \ref{fig:allSEM}).
+During foraging bouts, LCBs may travel further between flowers than HBs do \citep{brunet2019}, but pollen carryover from the edge to the centre of the bay female is likely reduced, as LCBs likely visit the edge of the female bay before venturing into the centre \citep{thomson1986, pinnisch1990}.
+Pollen counts decreased with distance into the field (independent of visitation), suggests that pollinators are less efficient at transfering pollen.
+Foraging \textit{Bombus} take shorter trips between flowers under nectar-rich conditions (area-restricted search, \citealp{pyke1978b, heinrich1979}), suggesting that HBs and LCBs may operate similarly at the centre of seed fields, causing lower pollen deposition at the centre of the field where competition is lower.
+% This may be due to lower levels of competition at the centre of the field, leading to a higher nectar (or pollen) standing crop. %LH: more likely that bees at centre of F bays carry less pollen
+%LCBs are extremely fast fliers, and are difficult to follow after they leave an inflorescence, meaning that tracking their movements during an entire foraging bout would be almost impossible.
+% Visits by HB foragers were almost twice as high in the centre of the female bay, but pollen deposition was about 40\% lower (  Figure \ref{fig:allPollen}), which correspondingly is 
+% HBs in seed fields tended to visit more in the centre of the female bay, even close to the edge of the field, yet pollen deposition was still about 40\% lower (Figure \ref{fig:allPollen}).
+% While we found that LCBs also tend to avoid the centre of the female bays, and decrease with distance into the field, this extra dependence could have been caused by the fact that the visitation data represents a short ``snapshot'' of the pollen deposition process.
+% For example, canola flowers are receptive for 1-2 days before the petals dehisce, while the surveys only recorded 5 or 10 minutes of visitation, meaning we may have not captured the deposition process on the time scale that it occurs, and the extra variance is being accounted for by distance from field edge and the centre of the female bay.
+% Leafcutter visitation can be extremely sporadic, so the distance and bay position measurements capture differences in the average visitation process better than 10 minute measurements.
+% Pollen deposition also likely changes over the course of the season, as flower availability decreases.
 
@@
 \citet{mesquida1978} also found that pod set in male-sterile canola declined quickly with distance from the male-fertile plants (due to wind pollination), but the effect we found is likely related to the earlier effect of lower pollen carryover at the centre of the female bays, and possibly the centre of the field.
-Finally, the effect of plant size was roughly 6x larger than that of pollen deposition, indicating that the factors controlling plant size (e.g.
-fertilizer application, soil quality) likely constrain pod production more strongly than pollination alone \citep{marini2015,tamburini2017, gagic2017, tamburini2019}.
+Finally, the effect size of pollen deposition (Z=3.1) was much smaller than that of plant size (Z=19.9), indicating that the factors controlling plant size (e.g.
+fertilizer application, soil quality) likely constrain pod production more strongly than pollination alone \citep{marini2015}.
 
@@
 
-Extra pollination generally results in canola plants producing more, smaller-sized seeds (see review in \citealt{ouvrard2019}, but see also \citealtt{koltowski2005}), whereby the plant allocates the same number of resources to a greater number of fertilized ovules.
-We found mixed support across both crop types: seed size and number in commodity canola was mainly influenced by plant size, while seed size and number in seed canola was influenced by both plant size and pollen deposition.
-Seeds per pod was increased by plant size in both crop types, suggesting greater rates of ovule maturation in the presence of greater plant resources \citep{bouttier1992}. 
-Pollen deposition had a smaller effect on seeds per pod than plant size in seed canola, again suggesting that plant resources limit seed production more strongly than pollen deposition, even in pollen-limited crops \citep{marini2015}.
-In contrast, we found that seed size increased with plant size in seed canola alone, and was not influenced by pollen or visitation in either crop.
-Unexpectedly, plant density had a \emph{positive} effect on seed size in both crop types, which we consider could have been caused by two different processes:
-plant density could be positively related to resource availability if plant survival is higher in plots with better growing conditions (i.e.
-Berkson's paradox, \citep{snoep2014}) or plant density may improve the microclimate conditions of the canola stand, reducing heat or desiccation stress on individual plants.
-We consider the first process more likely, as planting density under uniform conditions typically has little effect on seed size \citep{Angadi2003}.
+We found that seeds per pod in commodity canola was mainly influenced by plant size, while both seed size and seeds per pod was influenced by both plant size and pollen deposition in seed canola. 
+Extra pollination generally results in canola plants producing more, smaller-sized seeds (see review in \citealt{ouvrard2019}, but see also \citealtt{koltowski2005}), as the plant re-allocates resources across a greater number of fertilized ovules.
+Similarly, canola plants can also increase the number of matured ovules depending on the available plant resources \citep{bouttier1992, kirkegaard2018}.
+Our results in seed canola fields showed that pollen deposition had a smaller effect than plant size for seeds per pod (Z = 3.8 vs.
+6.1), suggesting that plant resources limit seed production more strongly than pollen deposition, while plant size was the dominant term for commodity canola fields (Z = 1.2 vs.
+6.6).
+Seed size was affected only by plant size in seed canola, and was not affected by pollen or plant size in commodity canola. 
+Plant size is a measure of the source of photosynthates available to the seeds, while fertilized flowers act as sinks of nutrients, but both of these measures are crude, as both sources and sinks of seed nutrients vary across the season \citep{clarke1979, zhang2018}.
+Canola growth is indeterminate, and poorly-pollinated plants respond by making more branches \citep{mesquida1981, sabbahi2006}, so it may be that large, poorly-pollinated plants have more resources and low numbers of fertilized ovules per flower at the end of the season.
+While we did not quantify pod position on branches, the pods at the end of the branches did appear to have fewer seeds, meaning that variation within plants likely occurred because of late-season seed.
+Unexpectedly, plant density had a \emph{positive} effect on seed size in both crop types, which may be caused by two different processes: a) plant density could be positively related to resource availability if plant survival is higher in plots with better growing conditions (i.e.
+Berkson's paradox, \citep{snoep2014}) or b) plant density may improve the microclimate conditions of the canola stand, reducing heat or desiccation stress on individual plants.
+We consider the first process more likely, as planting density under uniform conditions typically has little effect on seed size (\citealt{Angadi2003}).
+In summary, our results add to a growing body of literature on the context-dependent value of pollination services \citep{marini2015, tamburini2017, tamburini2019}.
 
 % The decrease in seed number at the centre of the bay may ultimately be caused by reduced pollen deposition from lower visitation \citep{mesquida1981,mesquida1982}.
-
 %Increased plant density within a patch can lead to more pollinator visitation \citep{kunin1997}, but not necessarily more visits per flower \citep{klinkhamer1990}.  
@@
 
-\subsection*{Conclusion}
+\subsection{Yield simulations}
 
-This study has revealed some of the detailed aspects of pollination in commodity and seed canola crops.
-First, it shows how two important species of commercial pollinators decline with distance from their nesting sites, and how LCBs unexpectedly decline with distance from the edge of the field.
-Second, it sheds light on the relative importance of HBs and LCBs as pollinators, showing that current levels of HB stocking do not strongly influence pollination in commodity canola crops, and that LCBs are likely the primary pollinators of seed canola.
-Finally, it contextualizes the value of pollination alongside plant resources, showing that plant resources and pollen limit production in seed canola, while only plant resources limit commodity production.
-Our unique SEM approach allowed us to formulate and test relationships within a causal framework, which we consider to be extremely valuable, and highly underused in agricultural studies.
-Our model serves as an approximation of a dynamic process, but could be built upon by using dynamic linear models \citep{iwasa2000,nord2011} to examine how plants dynamically respond to changes in pollination.
+% %RESULTS:
+% The path analysis simulations further confirmed the results of the analysis: HB visitation had little effect on yield in either crop type, but LCB visitation improved yield in seed crops.
+% The simulations showed no large effect of HB stocking on seed size or total yield in commodity fields (Figure \ref{fig:allYield}a, b), aside from the effect associated with distance from the edge of the field.
+% Similarly, the simulations for seed fields showed a small increase in seed size and total yield with distance from the HB hives at the field edges, but the effect of distance from the leafcutter shelters was much more dramatic (compare the spacing of isolines along the x-axis and y-axis in Figures \ref{fig:allYield}c, d).
+% A second set of simulations were run only in seed fields, in order to compare the effect of pollinator distances between the bay edge and centre. 
+% This revealed that not only total seed size and overall yield lower at the bay centre, but that the effect of HB distance is effectively \emph{nil} at the bay centre (yield isolines are essentially horizontal in bay centre, and slightly tilted at the bay edge, Figure \ref{fig:allYield}d, f).
+% Interestingly, the simulations also showed evidence of nonlinear behaviour occurring in the centre of seed field bays, where a local minima in yield appears at approximately 25 m away from HB hives and 45 m away from LCB shelters (Figure \ref{fig:allYield})f), likely because of an interaction between the components of yield (seeds per pod, pods per plant, and weight per seed).
+
+\subsection*{Summary} %RC: VERY CANOLA-FOCUSED
+
+%Taken from pollen section
+HBs may have an indirect positive effect on pollen deposition, as they may cause LCBs to travel farther by lowering overall nectar and pollen standing crop, or release airborne pollen from male-fertile flowers.
+\citet{pierre2010} showed that HBs can increase the amount of airborne pollen by foraging on male-fertile flowers and releasing pollen from the anthers, causing increased yields in nearby male-sterile flowers; therefore, HBs may indirectly contribute to a higher rate of wind pollination.
+HBs may also cause LCBs to forage at further distances away from their shelters.
+Bumble bees move further between flowers when foraging in \textit{Trifolium} fields that have been depleted by HBs \citet{heinrich1979}, so a similar process could occur in canola seed fields. 
+LCBs do not appear to use area-restricted search \citep{brunet2019}, but we expect that the foraging range of leafcutter bees around their shelters would sitill decrease, because if HBs lower pollen and nectar levels at the edge of the field, then leafcutter bees should travel shorter distances to gather the same reward (according to the predictions of Chapter 2).
+We also expect that foraging leafcutter bees would make shorter trips between flowers (similar to \citealp{heinrich1979}), and possibly may switch between bays less frequently \citep{waytesMsc,gaffney2019}, due to a greater floral fidelity on higher-rewarding flowers in the male bay \citep{mesquida1978}.
+If this is true, this would result in a lower rate of (overall) pollen deposition by leafcutter bees during the same period.
+However, testing this would require observations of seed canola fields that were only stocked with leafcutter bees, which is extremely rare in southern Alberta.
+%RC: MAY HAVE TO CHOP FOR THE MANUSCRIPT, BECAUSE IT DOESN'T HAVE OTHER AREA-RESTRICTED SEARCH LIT
+%A simple test of this would be to remove HB hives from a seed field, mid-season, and perform observations of leafcutter visitation patterns before and after the removal.
+
+This study assesses the relative importance of pollination and plant resources for the production of canola crops, using field-realistic data from central and southern Alberta.
+First, it shows that insect visitation changes across small spatial scales (meters for leafcutter bees, tens of meters for HBs), and are at odds with the large scales of Albertan crop fields \citep{fritz2015}.
+Visitation of both HBs and leafcutter bees in canola fields is concentrated at the edge of fields, and is lower at the centre of the female bays in seed canola.	
+Second, HBs have little direct influence on pollen deposition in either crop system, likely due to a high background level of pollen deposition on stigmas in commodity canola, whereby extra pollen deposition is of little benefit to plant reproduction.
+Seed canola plants, in contrast, have much lower levels of pollen deposition overall, and leafcutter bees deliver a large direct benefit to fruit and seed production. 
+The centre of the female bays illustrates this effect: HBs have a higher visitation rate, but pollen deposition, pod set, and seed set are all lower.
+Finally, both plant size and pollination limit seed production in seed canola, but only plant size limits commodity canola production, showing the relative importance of both pollination and plant resources using in-field data.
+
+Several future lines of work could be followed based on this study.
+First, other factors besides total seed yield are important for commodity canola production, such as green seed and oil content \citep{tautorus1994, abbadi2011, ghazani2013}.
+Our work identified the effect of bee pollination on seed production in terms of total weight, but may have overlooked these aspects of yield valuation \citep{bommarco2012}. 
+Secondly, we found that HBs appear to add little pollination value for seed canola crops, but since we did not use fields that had no HBs, there may be unobserved indirect benefits that HBs add.
+For example, they may contribute to better pollination by leafcutter bees by reducing the nectar and pollen standing crop, causing leafcutter bees to forager further away from their shelter \citep{pyke1978b, heinrich1979}, or by increasing the amount of airborne pollen \citep{eisikowitch1981,mesquida1982}.
+Third, while the random-intercept model that we used accounts for field-to-field variation in growing conditions, this also means that we may have marginalized across other factors that were not accounted for by plant size, such as nutrients, soil moisture, crop pests, and variety.
+Pollination benefits to all flowering crops are contextual, even in highly-pollination dependent crops \citep{tamburini2017, tamburini2019}; that is, the effect of additional pollination depends on the levels of other plant resources available during growth \citep{marini2015, bartomeus2015, gagic2017}.
+Finally, SEMs cannot model causal loops \citep{grace2006}, which is closer to the method by which plants respond to lack of pollination (\emph{i.e.} pollination failure $\rightarrow$ plant growth $\rightarrow$ flower production).
+Our model serves as an approximation of this process, but could be built upon by using dynamic linear programming techniques \citep{iwasa2000,nord2011} to examine how plants dynamically respond to pollen failure.
 These would lend greater understanding to the process of hybrid seed production, and could be used to more accurately predict crop yields in novel scenarios.
-
-% Several future lines of work could be followed based on this study.
-% First, other factors besides total seed yield are important for commodity canola production, such as green seed and oil content \citep{tautorus1994, abbadi2011, ghazani2013}.
-% Our work identified the effect of bee pollination on seed production in terms of total weight, but may have overlooked these aspects of yield valuation \citep{bommarco2012}. 
-% Secondly, we found that HBs appear to add little pollination value for seed canola crops, but since we did not use fields that had no HBs, there may be unobserved indirect benefits that HBs add.
-% For example, they may contribute to better pollination by leafcutter bees by reducing the nectar and pollen standing crop, causing leafcutter bees to forager further away from their shelter \citep{pyke1978b, heinrich1979}, or by increasing the amount of airborne pollen \citep{eisikowitch1981,mesquida1982}.
-% Third, while the random-intercept model that we used accounts for field-to-field variation in growing conditions, this also means that we may have marginalized across other factors that were not accounted for by plant size, such as nutrients, soil moisture, crop pests, and variety.
-% Pollination benefits to all flowering crops are contextual, even in highly-pollination dependent crops \citep{tamburini2017, tamburini2019}; that is, the effect of additional pollination depends on the levels of other plant resources available during growth \citep{marini2015, bartomeus2015, gagic2017}.
-% Finally, SEMs cannot model causal loops \citep{grace2006}, which is closer to the method by which plants respond to lack of pollination (\emph{i.e.} pollination failure $\rightarrow$ plant growth $\rightarrow$ flower production).
 

### 2022-09-08 Manuscript/main.tex
Updated manuscript

@@
 We found that seeds per pod in commodity canola was mainly influenced by plant size, while both seed size and seeds per pod was influenced by both plant size and pollen deposition in seed canola. 
-Extra pollination generally results in canola plants producing more, smaller-sized seeds (see review in \citealt{ouvrard2019}, but see also \citealtt{koltowski2005}), as the plant re-allocates resources across a greater number of fertilized ovules.
+Extra pollination generally results in canola plants producing more, smaller-sized seeds (see review in \citealt{ouvrard2019}, but see also \citealt{koltowski2005}), as the plant re-allocates resources across a greater number of fertilized ovules.
 Similarly, canola plants can also increase the number of matured ovules depending on the available plant resources \citep{bouttier1992, kirkegaard2018}.

### 2022-09-22 Manuscript/main.tex
Worked on SH revisions

@@
 \begin{abstract}
-Insect-mediated pollination of crops is an important input to agricultural production, but pollination management suffers from key mechanistic gaps that hinder its greater utility. 
-While pollination services to plants have a solid theoretical and mechanistic framework, agricultural pollination is often treated as a statistical ``black box", without reference to the mechanisms underlying the process of pollination and fruit production.
-We present a causal model that links insect visitation to pollination to three separate components of yield, using two types of canola (\textit{Brassica napus}) production systems.
-%Visitation by honey bees was strongly related to distance in both commodity and seed canola fields, with visitation decreasing with distance away from the edge of the field (where the hives were located).
-%In seed fields, leafcutter bee visitation strongly decreased with distance away from their shelter, but interestingly, also decreased with distance from the edge of the field in high-density shelters, meaning that foragers may be migrating from shelters at the centre of the field to shelters at the edge.
-Commodity canola yield was mainly controlled by plant size, and there was no relationship between \textit{Apis mellifera} visitation and pollen deposition, or deposition and seed yield.
-In comparison, seed canola yield was also controlled by plant size, but there was also a strong relationship between visitation and pollen deposition, as well as deposition and seed yield.
-We also found that \textit{Megachile rotundata} visitation in seed canola strongly increased pollen deposition, but \textit{A. mellifera} visitation did not.
+Insect-mediated pollination of crops is an important input to agricultural production, but pollination management suffers from key knowledge gaps that hinder its greater utility. 
+While a solid theoretical and mechanistic framework for plant pollination exists, the pollination of agricultural crops is often treated as a ``black box”, without reference to the specific mechanisms underlying the processes of pollination and fruit production.
+We present a causal model that links insect visitation to pollination to three separate components of yield, using field data from two types of canola (\emph{Brassica napus}) production systems. 
+Our results demonstrate that yield in commodity canola fields is primarily determined by plant size, and we found no relationship between honey bee visitation and pollen deposition, or pollen deposition and seed yield.
+In contrast, yield in seed production canola fields was similarly controlled by plant size, but there was also a strong relationship between bee visitation and pollen deposition, as well as deposition and seed yield.
+Leafcutting bee visitation in particular strongly increased pollen deposition in seed canola fields, whereas honey bee visitation did not. 
 This model serves as a step towards a dynamic model of pollination services, and points to the contextual importance of pollination services in seed canola production.
-
 \end{abstract}
@@
 Animal pollination of agricultural flowering plants is an important ecosystem service that contributes to about 10\% of total crop production value worldwide \citep{gallai2009}, and animal-pollinated plants produce a large number of important micronutrients in the human diet \citep{eilers2011}.
-Pollination of these crops, however, is largely treated as a single process, even though there are many links in the chain of events that result in the production of a fruit.
-Visitation of flowers by animals (typically bees or other insects) can increase pollen deposition on the stigma of the flower, followed by fertilization of the ovules, and maturation of fruit \citep{erbar2003, goldberg1994}.
-Each step has many other underlying processes (\textit{e.g.} stigma receptivity, pollen tube growth, ovule abortion), but even at this level of approximation, most studies of agricultural pollination fail to account for important underlying processes.
-Moving beyond this ``black-box" model of agricultural pollination requires accounting for these steps, and is needed for contextualizing the value of pollination services, as well as optimizing crop yield in novel circumstances.
+Pollination of these crops, however, is largely treated as a single step, while in reality there are many links in the chain of events that result in fruit production.
+Visitation of flowers by animals (typically bees or other insects) can increase the deposition of pollen onto the stigma of the flower, but in order for fruit set to occur, this must be followed by fertilization of the ovules, and maturation of fruit \citep{erbar2003, goldberg1994}.
+Each step has many other underlying constituent components (\textit{e.g.} stigma receptivity, pollen tube growth, ovule abortion), but even at this coarse level of approximation, most studies of agricultural pollination fail to account for important underlying processes.
+Moving beyond this ``black-box" model of agricultural pollination requires incorporation of these steps, and is needed for contextualizing the value of pollination services, as well as optimizing crop yield in novel circumstances.
 
@@
 Smaller bees fly shorter distances than larger bees \citep{greenleaf2007,zurbuchen2010}, so their presence at the centre of large fields can be limited \citep{isaacs2010}. 
-Hence, managing the location and density of managed pollinators is important for optimal yield of pollinator-dependent crops \citep{fries1983,cresswell2004b}.
+Hence, managing the location and density of pollinators is important for optimal yield of pollinator-dependent crops \citep{fries1983,cresswell2004b}.
 Similarly, foragers will often specialize on certain species or morphs of flowers in order to forage more efficiently (floral fidelity, \citealp{heinrich1976b, goulson1997}). 
@@
 Competition for floral resources can occur between different species of foragers, but they can spatially or temporally separate their foraging to reduce competition (\citealp{schaffer1979,thomson1987}, but see \citealp{steffan2000}), such as switching between floral morphs more often, or visiting less frequently \citep{heinrich1979, greenleaf2006}.
-Thus, variation in visitation can be driven by distance, competition with other foragers, or floral specialization; however, this is seldom considered, as commercial pollinators are often treated as a single agricultural ``input" (akin to fertilizer).
+Thus, variation in visitation can be driven by distance, competition with other foragers, or floral specialization, as well as plant traits such as nectar production and flower size; however, this spatial variation is seldom considered, as commercial pollinators are often treated as a single agricultural ``input" (akin to fertilizer).
 % Much of the worldwide agricultural demand for insect pollination is accomplished by the European honey bee, (\textit{Apis mellifera} L., hereafter ``honey bee") because of its large colony size, ease of transport, and ease of breeding (\citealp{winston1991}, but see also \citealp{winfree2008}).
@@
 Seed production can be limited by plant resources as well as pollen, meaning that the benefits of insect pollination depend on the resources available to the plant \citep{stephenson1981, marini2015, tamburini2017, tamburini2019}.
-Pollination can enhance fruit production in flowering plants by increasing either the quantity or quality of pollen deposited on the stigma \citep{stephenson1981,burd1994,aizen2007}.
+Pollination can enhance fruit production in flowering plants by increasing either the quantity or quality of pollen deposited on the stigma \citep{stephenson1981, burd1994, aizen2007}.
 Many flowering plant species are capable of self-pollination, but can produce more fruit or seeds from outcrossed pollen \citep{knight2005}.
-However, the benefit of this extra pollen deposition is diminishing \citep{plowright1981}, with very high numbers of pollen grains causing less and less of an increase in fruit production \citep{ashman2004, harder2016}.
+However, the returns from this extra pollen deposition are diminishing \citep{plowright1981}, with very high numbers of pollen grains causing decreasing improvements in fruit production \citep{ashman2004, harder2016}.
 % Not all animal visitors are equal from a flowering plant's perspective: large-bodied insects can deposit more pollen per visit on the stigma of the flower \citep{sahli2007}, but some visitors may steal nectar, groom pollen between visits, or travel mainly between flowers on the same plant \citep{thomson1986, herrera1987}, reducing their utility to the plant.
 Pollen limitation can also occur at multiple levels within a plant, reducing the number of seeds per fruit or the number of mature fruit \citep{burd1994}.
-Low pollen deposition cause flower abortion, where poorly-pollinated flowers are cut off from the plant \citep{knight2006}, but an indeterminate growth strategy may help to offset this, by simply making more flowers \citep{doust1982,lawrence1993, sabbahi2006, bos2007}.
+Low pollen deposition can also cause flower abortion, where poorly-pollinated flowers are abcised from the plant \citep{stephenson1981}; an indeterminate growth strategy may offset this by enabling the plant to continue producing more flowers \citep{doust1982, lawrence1993, sabbahi2006, bos2007}.
 Additional pollen may result in a greater number of seeds per fruit \citep{knight2006}, which in turn may result in a reduction in the size per seed due to competition between ovules or fruit \citep{free1968, mazer1987}.
-Seed size can also vary strongly among plants, and can be affected by resources available to the plant \citep{mazer1987, venable1992}. 
-Therefore, understanding how plants allocate their seed resources under pollen or resource deficits are important for managing agricultural production \citep{bos2007, tamburini2019}.
+Seed size can also vary dramatically among plants, and can be affected by resources available to the plant \citep{mazer1987, venable1992}. 
+Therefore, understanding how plants allocate reproduction under pollen or resource deficits are important for managing agricultural production \citep{bos2007, tamburini2019}.
 
@@
 
-Insect pollination is especially important in the production of canola crops (\textit{Brassica napus} L.).
+Insect pollination is especially important in the production of canola (\textit{Brassica napus} L.).
 Hybrid \emph{commodity canola} (used for oil and meal production) is the offspring of two parental \emph{seed canola} breeding lines, a male-sterile ``female" and a hermaphroditic ``male" line \citep{westcott2001,steffan2003,clay2009}.
-Seed canola production requires a large number of pollinators to ensure pollination of the female line (seed from the male line is not harvested), but there are few published studies that examine pollination in these systems (see \citealp{mesquida1981, mesquida1991}).
-Extra pollination may also increase the yield of commodity canola \citep{morandin2005,rader_phd,bommarco2012,bartomeus2015,perrot2018}, but this is unclear, as many  key studies suffer from either a lack of realistic context, have a number of potential confounding variables, or infer plant-level outcomes from flower-level treatments \citep{ouvrard2019}.
+Seed canola production therefore requires a large number of pollinators to ensure pollen transfer from the male to the femal line (seeds from the male line are not harvested), but there are few studies that examine pollination in these seed production systems (but see \citealp{mesquida1981, mesquida1991}).
+Bee pollination may also increase the yield of commodity canola \citep{morandin2005, rader_phd, bommarco2012, bartomeus2015,perrot2018}, but this is unclear, as many key studies suffer from either a lack of realistic context, have a number of potential confounding variables, or infer plant-level outcomes from flower-level treatments \citep{ouvrard2019}.
 Greenhouse experiments typically involve unrealistically high levels of pollination, nutrient availability, and water, all of which can interact with yield \citep{bartomeus2015,marini2015}.
-Field studies often relate yield to indirect measures of pollination services, such as insect abundance, species richness, or distance from sources of potential pollinators \citep{morandin2005,ricketts2008}, rather than visitation rates or pollen deposition.
+Field studies often relate yield to indirect measures of pollination services, such as species richness or distance from sources of potential pollinators, or do not examine production at the plant level \citep{morandin2005, ricketts2008}.
 These proxies provide limited information about how plants dynamically respond to pollen exclusion or addition (but see \citealp{sabbahi2005}).
@@
 Using both commodity and seed canola provides an opportunity to compare two plant varieties that differ strongly in their pollination requirements, using a similar type of structural model, while accounting for agricultural differences between varieties.
-We expected that extra pollination would increase pollination and seed production in commodity canola, but that the magnitude of the increase would be much higher in seed canola, and that plant size (a proxy for plant resources) would similarly increase seed production.
+We expected that extra visitation would increase pollination and seed production in commodity canola, but that the magnitude of the increase would be much higher in seed canola, and that plant size (a proxy for plant resources) would similarly increase seed production.
 This study assesses the strength of the connections between visitation, pollination, and yield, in a globally important crop species, and identifies the relative importance of bee pollination for seed production, using in-field data from two distinct cropping systems.

### 2022-09-24 Manuscript/main.tex
Worked on SH revisions

@@
 Commodity canola fields were selected based on the proximity of honey bee apiaries and site access. 
-28 of the 60 fields were stocked with honey bees at the corner or side of the field (mean: 0.6 hives/hectare, SD: 0.58) while 32 fields were unstocked.
+28 of the 60 fields were stocked with Western honey bees (\emph{Apis mellifera} L., hereafter HB) at the corner or side of the field (mean: 0.6 hives/hectare, SD: 0.58) while 32 fields were unstocked.
 %range: 0.03 - 3.1 Apiaries were stationed at the edges of fields, often near to shrubs or tree-lines to act as a wind break.
@@
 %Maps + climate graphs needed for publication
-During 2015 and 2016, we also surveyed 35 hybrid seed canola fields (15 in 2015, 20 in 2016) near Lethbridge, Alberta, from June through August of each year, all of which had central-pivot irrigation.
-In seed canola fields, bays of hermaphroditic (herafter ``male") and female plants are typically planted in 1- and 6-m wide bays, respectively. 
-Seed fields were stocked with honey bee hives at a rate of 3.6 hives/ha, with apiaries stationed in the corners of fields, and were also stocked with LCB shelters at a rate of approximately 2 shelters/ha (Figure \ref{fig:seedfieldPhoto}, \ref{fig:seedfieldPlots}).
+During 2015 and 2016, we also surveyed 35 hybrid seed canola fields (15 in 2015, 20 in 2016) near Lethbridge, Alberta, from June through August of each year, all of which had central-pivot irrigation, and were stocked with honey bee hives at a rate of 3.6 hives/ha (apiaries stationed in the corners of fields).
+In seed fields, bays of hermaphroditic (herafter ``male") and female plants are typically planted in 1- and 6-m wide bays, respectively. 
+Seed fields were also stocked with shelters (1.3 - 2.6 shelters/ha) containing alfalfa leafcutter bee cocoons (\textit{Megachile rotundata} F., hereafter LCB) at a rate of 50,000-100,000 coocoons/ha (Figure \ref{fig:seedfieldPhoto}, \ref{fig:seedfieldPlots}).
 % (1.3 or 2.6 shelters/ha).
+% at a rate of approximately 2 shelters/ha
 % Shelters used either ``standard" or ``double"  LCB stocking ($\approx$50,000 vs.
@@
 Finally, we incorporated plot-level visitation data from Waytes (\citeyear{waytesMsc}; same years and locations) to more accurately gauge the effect of distance from shelter on visitation rates (647 total plots).
-All surveys occurred on fair-weather days (median air temperature: 24.5$^\circ$C., range: 17--33) with no rain and as minimal wind (less than 30km/hr).
+All surveys occurred on fair-weather days (median temperature: 24.5$^\circ$C., range: 17--33) with no rain and minimal wind ($>$30 km/hr).
 % Mean air temperature was similar between years in Grande Prairie ($\approx$ 22$^\circ$C), but Lethbridge was warmer in 2015 (23 vs. 28$^\circ$C).
@@
 At the end of the growing season, we collected three plants from the same female plot and recorded the plant density per m$^2$ (789 commodity canola plants, 582 seed canola plants).
-After drying the plants, we weighed the entire plant, counted mature pods to estimate pod set, and counted the number of flower pedicels to estimate total flower production. % at 50$^\circ$C
+After drying the plants, we weighed each plant, counted mature pods to estimate pod set, and counted the number of flower pedicels to estimate total flower production. % at 50$^\circ$C
 We estimated seed size and seeds per pod by averaging the seed count and weight from five pods on each plant.
@@
 We also ran a linear model outside of each SEM to predict total yield (g per plant) as a function of the seed size, seeds per pod, and pods per plant (see Table \ref{tab:totalYieldCoefs}).
-After the models were properly fit and validated, we simulated seed size and yield at varying distances from pollinators, using the coefficients from each model to integrate the effect of pollination on yield across all other sub-models (while holding plant density constant).
+After the models were fit and validated, we simulated seed size and yield at varying distances from pollinators, using the coefficients from each model to integrate the effect of pollination on yield across all sub-models (while holding plant density constant).
 % These SEMs let us model how visitation ultimately influences seed yield, while controlling for other confounding factors (e.g. distance into field, measurements taken at different fields).
@@
 The underlying models of each pSEM were specified as generalized linear mixed-effects models (GLMMs).
-GLMMs can model processes that occur at different levels; for example, seed size was modelled at the plant level, while pollen deposition was modeled at the flower level.
-Random intercepts were used to model variance at the field level and plot level, but plot-level variance terms had poor traces and low effective sample sizes, so we omitted plot-level random effects for all models (except for pollen count and pod set in seed fields, see Table \ref{tab:seedCoefs}).
+GLMMs can model processes that occur at different levels; for example, we modeled seed size at the plant level, and pollen deposition at the flower level.
+Random intercepts were used to model variance at the field and plot level, but plot-level variance terms had poor traces and low effective sample sizes, indicating low plot-level variance; therefore, we omitted plot-level random effects for all models (except for pollen count and pod set in seed fields, see Table \ref{tab:seedCoefs}).
 Visitation models used $log$(time) as an ``offset" variable to account for differences in observation times.
@@
 
-All component GLMMs of the pSEM were written in Stan 2.18.1 and run using \texttt{rstan} 2.26.13 \citep{gelman2015,Rstan}.
+All component GLMMs of the pSEM were written in Stan 2.18.1 and run using \texttt{rstan} 2.26.13 \citep{gelman2015, Rstan}.
 We used weakly informative normal priors ($\mu=0, \sigma=5$) for fixed effects and gamma priors ($\alpha=1, \beta=1$) for the variance components.
@@
 \subsection*{Path analysis}
-
-Plant size and pollen deposition were the main drivers of seed production in seed canola, while plant size was the main driver in commodity canola (see Figure \ref{fig:allSEM} for paths and effect sizes).
-HB visitation decreased with distance from the edge of the field in both commodity and seed canola; unexpectedly, LCB visitation also decreased with distance from the edge of the field in seed fields.
-LCB visitation strongly increased pollen deposition was strong in seed canola, but there was no strong effect of HB visitation in either crop type.
-Both crop types had strong negative paths from pods per plant to flowers per plant, indicating that high flower survival suppressed future flower production.
-Plant size increased the number of seeds per pod in both crop types, and also increased seed size in seed canola plants.
-Finally, pollen deposition increased pod set and seeds per pod in seed canola, but did not affect seed or pod production in commodity canola, showing that plant resources matter strongly for both crops, but that increased pollen only benefits seed canola crops.
+The path analysis revealed that plant size and pollen deposition were the main drivers of seed production in seed canola, while plant size alone was the main driver in commodity canola (see Figure \ref{fig:allSEM} for paths and effect sizes).
+LCB visitation strongly increased pollen deposition in seed canola, but there was no strong effect of HB visitation in either seed or commodity canola.
+Plant size increased with distance from the edge of the field in both crops, as well as plant density in seed fields.
+Plant size strongly increased the number of flowers per plant in both crops, and there were strong negative paths from pods per plant to flowers per plant, indicating that high flower survival suppressed future flower production in both crops.
+Plant size increased pod set and seeds per pod in both crop types, and also increased seed size in seed canola plants.
+Pollen deposition increased pod set and seeds per pod in seed canola, but did not affect seed or pod production in commodity canola, showing that plant resources matter strongly for both crops, but that pollen limitation matters only in seed canola.
+Finally, there was an indirect effect (not related to visitation) of bay centre, distance from edge, and distance from LCB shelter on pollen count and pod set in seed fields, pointing to possible differences in pollen transfer even at the same rate of visitation.
 
@@
     \includegraphics[width=\textwidth,keepaspectratio=true]{../Figures/allSEM.png}
-    \caption{Results of path analysis in commodity and seed fields.
-The width of each arrow is proportional to the effect size of each component path (number also displayed).
+    \caption{Results of path analyses in commodity and seed fields.
+\emph{Field Edge Distance} refers to the distance to the edge of the field (and location of HB apiary) and \emph{Shelter Distance} refers to the distance to the nearest LCB shelter.
+The width of each arrow is proportional to the effect size of each component path (number also displayed), with black and red lines representing positive and negative effects, respectively.
 Transparent arrows show path coefficients whose 95\% posterior intervals overlapped zero.}
@@
 
-\subsection*{Visitation}
+\subsection*{Flower Visitation}
 
-Honey bee visitation decreased with distance away from the edge of the field in both commodity and seed canola fields.
-In commodity fields, HB visitation decreased from 12 visits/hr at the edge to 1.8 visits/hr at 400 m into the field (Figure \ref{fig:allVisits}a, apiary of 40 hives).
+% HB visitation decreased with distance from the edge of the field in both commodity and seed canola, and increased with distance from LCB shelters; interestingly, LCB visitation also decreased with distance from the edge of the field in seed fields.
+Honey bee flower visitation per plot decreased with distance away from the edge of the field in both commodity and seed canola fields.
+In commodity fields, HB visitation decreased from 12 visits/hr per plot at the edge to 1.8 visits/hr at 400 m into the field (Figure \ref{fig:allVisits}a, apiary of 40 hives).
 Lower stocking rates decreased HB visitation at the edge of the field to 7.4 visits/hr at 20 hives, while unstocked field edges had an average of 0.8 visits/hr.
 Unsurprisingly (given the higher stocking rate of 160 hives per field), HB visitation was much higher in seed canola fields, and decreased from 96.4 visits/hr at edge to 85.7 visits/hr at the centre of the field (Figure \ref{fig:allVisits}a).
-Visitation was also much lower near LCB shelters, dropping from 81 visits/hr at 20 m to 31 at 2 m (Figure \ref{fig:allVisits}b), likely due to competition with LCBs.
+HB visitation was also much lower near LCB shelters, dropping from 81 visits/hr at 20 m to 31 at 2 m (Figure \ref{fig:allVisits}b), likely due to competition or aggression from LCBs.
 % Visitation rates were higher in both years in Lethbridge (2014: 9.3 visits/hr, 2015: 7.1), but were higher in 2015 than 2014 at Grande Prairie (Z=2.3, p$=$0.02), rising from 5 visits/hr at the field edge in 2014 to 17 visits/hr in 2015.
@@
 
-LCB visitation was much higher close to their shelters, and surprisingly, was also higher at the edge of the field.
-LCB Visitation dropped from 350 visits/hr at 2 m from the shelter to 50 visits/hr at 20 m (Figure \ref{fig:allVisits}b), and also decreased from 119 visits/hr at the edge of the field to 25 at the centre (Figure \ref{fig:allVisits}a, b)
-The difference in LCB visitation between the edge and centre of the female bays was weak (p=0.14), while HB visitation was higher at the centre of the bay (88 vs.
-139 visits/hr, Figure \ref{fig:allVisits}b), indicating that pollination is likely done by different species in different parts of the field.
+LCB flower visitation was much higher close to their shelters, and surprisingly, was also higher at the edge than the centre of the field.
+LCB visitation dropped from 350 visits/hr at 2 m from the shelter to 50 visits/hr at 20 m (Figure \ref{fig:allVisits}b), and also decreased from 119 visits/hr at the edge of the field to 25 at the centre (Figure \ref{fig:allVisits}a, b)
+There was no large difference in LCB visitation between the edge and centre of the female bays, but HB visitation was higher at the centre of the bay (88 vs.
+139 visits/hr, Figure \ref{fig:allVisits}c).
+Together, our results indicate that pollination is likely accomplished by different species in different parts of the field.
 % There was no difference in visitation rates between the male bay and the edge of the female bays (LCB: p$=$0.72, HB: p$=$0.32). 
@@
 
-LCB visitation increased pollen deposition in seed canola fields, but honey bees did not increase pollen deposition in commodity or seed canola fields.
-Pollen deposition on stigmas was high in commodity canola (mean: 293 grains/stigma, SD: 385, range: 0--3981), but honey bee visitation had no impact on this (p$=$0.77, Figure \ref{fig:allPollen}a).
-Pollen deposition declined weakly with distance from the edge of the field (p$=$0.09), but this only amounted to a 6\% average decrease (290 grains/stigma at the field edge vs. 240 at field centre).
-In seed canola, pollen deposition was much lower overall (mean: 22 grains per stigma, SD: 43, range: 0--578), and decreased from 26.3 grains/stigma at the edge to 11.5 at the centre of the field (Figure \ref{fig:allPollen}b) independent of visitation.
+LCB visitation increased pollen deposition in seed canola fields, but honey bees did not increase pollen deposition in commodity or seed canola fields (Figure \ref{fig:allPollen}a).
+Pollen deposition on stigmas was high in commodity canola (mean: 293 grains/stigma, SD: 385, range: 0--3981), but honey bee visitation had no effect.
+Pollen deposition declined weakly with distance from the edge of the field (p$=$0.09), but this only amounted to a 6\% average decrease (290 grains/stigma at the field edge vs.
+240 at field centre, Figure \ref{fig:allPollen}b).
+In seed canola, pollen deposition was much lower overall (mean: 22 grains/stigma, SD: 43, range: 0--578), and decreased from 26.3 grains/stigma at the edge to 11.5 at the centre of the field (Figure \ref{fig:allPollen}b), independent of bee visitation.
 LCB visitation increased pollen deposition from 13 grains/stigma at 0 visits/hr to 25 pollen grains at 100 visits/hr (Figure \ref{fig:allPollen}a), but there was no effect of honey bee visitation (p$=$0.20), implying that most of the pollen deposition in seed fields is the result of LCB visitation.
-Pollen deposition also decreased from 15 grains/stigma at the edge of the female bay to 9 at the centre of the bay independent of visitation, suggesting that pollen may be lost from bees crossing over from male bays.% \citep{pinnisch1990}.%, who likely visit flowers at the edge of the bay first.
+Pollen deposition also decreased from 15 grains/stigma at the edge of the female bay to 9 at the centre of the bay independent of visitation (Figure \ref{fig:allPollen}c), suggesting that bees crossing over into the male bays may deposit less pollen as they move towards the centre.% \citep{pinnisch1990}.%, who likely visit flowers at the edge of the bay first.
 % Flies were also common visitors in commodity fields (Table \ref{tab:propVisitors}), but had no effect on pollen deposition (p$=$0.577), so only honey bees and LCBs were considered as potential pollinators (other flower visitors were rare).
@@
     \includegraphics[width=\textwidth,keepaspectratio=true]{../Figures/allSeeds.png}
-    \caption{Effect of pollen deposition (top row) and plant size (bottom row) on flower survival, seeds per pod, and seed size.}
+    \caption{Marginal effects of pollen deposition (top row) and plant size (bottom row) on flower survival, seeds per pod, and seed size.}
     \label{fig:allSeeds}
@@
 Commodity canola produced fewer flowers per plant than seed canola (mean: 196 vs. 461), and also produced fewer pods per plant (143 vs. 299, Table \ref{tab:dataSummary}).
-Commodity canola also produced more seeds per pod than seed plants (mean: 23 vs 16), but seed size was lower in commodity canola (2.74 vs 3.43 mg/seed). 
-Finally, commodity plants were also lower-yielding than seed canola plants (mean: 6.8 vs 9.5 g seed per plant), but produced more seeds per gram of vegetative biomass than seed canola plants (mean: 0.38 vs.
+In contrast, commodity canola also produced more seeds per pod than seed canola plants (mean: 23 vs. 16), but seed size was lower in commodity canola than seed canola (2.74 vs. 3.43 mg/seed). 
+Finally, commodity plants were also lower-yielding than seed canola plants (mean: 6.8 vs.
+9.5 g seed per plant), but produced more seeds per gram of vegetative biomass than seed canola plants (mean: 0.38 vs.
 0.32), likely due to lower pollen limitation.
 
-Plant size had by far the strongest positive effect on the number of pods produced, and there was evidence of pod set suppressing flower production (see plant paths in Figure \ref{fig:allSEM}), but pollen only directly affected production in seed canola.
-In both commodity and seed canola, plant size had a strong positive effect on the total number of flowers per plant as well as \% pod set (Figure \ref{fig:allSeeds} bottom row), but did not increase seed size in commodity canola.
+Plant size had by far the strongest positive effect on the number of pods produced, and there was evidence of pod set suppressing flower production (see plant paths in Figure \ref{fig:allSEM}), but pollen only directly affected pod and seed production in seed canola.
+
+In both commodity and seed canola, plant size had a strong positive effect on \% pod set and seeds per pod, but did not increase seed size in commodity canola (Figure \ref{fig:allSeeds}d,e,f).
+
 Plant density also had a positive direct effect on seed size in both crops, indicating that areas with better resources can support better-provisioned (but smaller) plants.
@@
 
-Pollen deposition did not alter seed production in commodity canola, nor was there a direct effect of honey bee visitation or distance from field edge (note log-scaled x-axis on Figure \ref{fig:allSeeds}).
+Pollen deposition did not alter seed production in commodity canola (Figure , nor was there a direct effect of honey bee visitation or distance from field edge (note log-scaled x-axis on Figure \ref{fig:allSeeds}).
 Pod set and seeds per pod in seed canola were increased by higher pollen deposition, and decreased with distance away from HB hives as well as distance from LCB shelters.

### 2022-09-24 partial plots.R

@@ -123,7 +123,7 @@ d3 <- with(avgSeedData, #Leafcutters in seed fields
   # coord_cartesian(y=c(0,150),clip='on')+
   ylim(0,150)+
   coord_cartesian(y=c(0,150))+
-  labs(x='Distance from apiary (m)',y='Visits per hour',fill=NULL,col=NULL)+
+  labs(x='Distance from field edge (m)',y='Visits per hour',fill=NULL,col=NULL)+
   scale_colour_manual(values=labCols)+
   scale_fill_manual(values=labCols)
 )
@@ -160,7 +160,7 @@ d2 <- with(avgSeedData, #Lbee visits
   ggplot(aes(x=dist,y=mean))+
   geom_ribbon(aes(ymax=upr,ymin=lwr,fill=type),alpha=0.3)+
   geom_line(aes(col=type))+
-  labs(x='Distance from shelter (m)',y='Visits per hour',
+  labs(x='Distance from LCB shelter (m)',y='Visits per hour',
        fill=NULL,col=NULL)+
   coord_cartesian(y=c(0,300))+
   scale_colour_manual(values=labCols)+
@@ -297,7 +297,7 @@ d3 <- with(avgSeedData, #Lbee dist - seed
   ggplot(aes(x=dist,y=mean))+
   geom_ribbon(aes(ymax=upr,ymin=lwr,fill=type),alpha=0.3)+
   geom_line(aes(col=type))+
-  labs(x='Distance from apiary or shelter (m)',y='Pollen grains per stigma',fill=NULL,col=NULL)+
+  labs(x='Distance from field edge or shelter (m)',y='Pollen grains per stigma',fill=NULL,col=NULL)+
   scale_colour_manual(values=labCols)+
   scale_fill_manual(values=labCols)+
   scale_y_log10())
@@ -361,7 +361,7 @@ d2 <- with(avgSeedData,
   ggplot(aes(x=pol,y=mean))+
   geom_ribbon(aes(ymax=upr,ymin=lwr,fill=type),alpha=0.3)+
   geom_line(aes(col=type))+
-  labs(x='Pollen grains per stigma',y='Flower survival (%)',fill=NULL,col=NULL)+
+  labs(x='Pollen grains per stigma',y='Pod set (%)',fill=NULL,col=NULL)+
   scale_colour_manual(values=labCols)+scale_fill_manual(values=labCols)+
[…]

### 2022-09-24 sem plots.R

@@ -39,7 +39,7 @@ load('./Models/modSummaries_seed.Rdata')
 nodeCoords <- data.frame(name=c('numHives','hbeeDist','hbeeVis','pollen',
                                 'plSize','plDens','flDens',
                                 'flwCount','flwSurv','seedCount','seedWeight'),
-                         labs=c('Number\nof Hives','Distance','Honey bee\nVisits','Pollen\nCount',
+                         labs=c('Number\nof Hives','Field Edge\nDistance','Honey bee\nVisits','Pollen\nCount',
                                 'Plant\nSize','Plant\nDensity','Flower\nDensity',
                                 'Flowers\nper Plant','Pod Set\n(%)','Seeds\nper Pod','Seed\nSize'),
                          x=c(0,1,0.5,0.5,
@@ -118,15 +118,15 @@ commDAG$data <- commDAG$data %>% #Match coefs to dagitty set
 
 # Seed SEM plot -----------------------------------------------------------
 
-nodeCoords <- data.frame(name=c('numHives','hbeeDist','lbeeDist','hbeeVis','lbeeVis','pollen',
+nodeCoords <- data.frame(name=c('hbeeDist','lbeeDist','hbeeVis','lbeeVis','pollen',
                                 'plSize','plDens','flDens','cent',
                                 'flwCount','flwSurv','seedCount','seedWeight'),
-                         labs=c('Number\nof Hives','Honey bee\nDistance','Leafcutter\nDistance',
+                         labs=c('Field Edge\nDistance','Shelter\nDistance',
                                 'Honey bee\nVisits','Leafcutter\nVisits','Pollen\nCount',
                                 'Plant\nSize','Plant\nDensity','Flower\nDensity','Bay Centre',
                                 'Flowers\nper Plant','Pod Set\n(%)','Seeds\nper Pod','Seed\nSize'),
-                         x=c(0,0,1,0,1,0.5,2.5,0,1,0.5,3.5,4,2.5,3.5),
-                         y=c(4,4,4,3,3,2,0,1,1,0.5,0,1,3,2))
+                         x=c(0,1,0,1,0.5,2.5,0,1,0.5,3.5,4,2.5,3.5),
+                         y=c(4,4,3,3,2,0,1,1,0.5,0,1,3,2))
 
 
 #Specify model

### 2022-09-26 Manuscript/main.tex
Finished comments from SH

@@
 \title{Bee visitation, pollination services, and plant yield in commodity and hybrid seed canola}
-\author{Samuel Robinson, Ralph Cartar, Stephen Pernal, Riley Waytes, Shelley Hoover}
-% \author{Samuel Robinson}
-
-\date{}
+\author{Samuel V. J. Robinson$^1$\footnote{Corresponding author: samuel.robinson@ucalgary.ca}, Ralph V. Cartar$^1$,\\Stephen F. Pernal$^2$, Riley Waytes$^3$, Shelley E. Hoover$^4$}
+\date{
+$^1$ Department of Biological Sciences, University of Calgary, Calgary, AB\\
+$^2$ Agriculture and Agri-Food Canada, Beaverlodge Research Farm, Beaverlodge, AB\\
+$^3$ Ministry of Land, Water, and Resource Stewardship, Smithers, BC\\
+$^4$ Department of Biological Sciences, University of Lethbridge, Lethbridge, AB
+}
 
@@
 Using both commodity and seed canola provides an opportunity to compare two plant varieties that differ strongly in their pollination requirements, using a similar type of structural model, while accounting for agricultural differences between varieties.
-We expected that extra visitation would increase pollination and seed production in commodity canola, but that the magnitude of the increase would be much higher in seed canola, and that plant size (a proxy for plant resources) would similarly increase seed production.
+We expected that bee visitation would decrease with distance from each species' hive or shelter, and that lower visitation would result in lower pollen deposition.
+We also expected that higher pollination would increase seed production in commodity canola crops, but that the magnitude of the increase would be higher in seed canola, and that plant size (a proxy for plant resources) would similarly increase seed production.
 This study assesses the strength of the connections between visitation, pollination, and yield, in a globally important crop species, and identifies the relative importance of bee pollination for seed production, using in-field data from two distinct cropping systems.
@@
 In seed fields, bays of hermaphroditic (herafter ``male") and female plants are typically planted in 1- and 6-m wide bays, respectively. 
-Seed fields were also stocked with shelters (1.3 - 2.6 shelters/ha) containing alfalfa leafcutter bee cocoons (\textit{Megachile rotundata} F., hereafter LCB) at a rate of 50,000-100,000 coocoons/ha (Figure \ref{fig:seedfieldPhoto}, \ref{fig:seedfieldPlots}).
+Seed fields were also stocked with shelters (1.3 - 2.6 shelters/ha, Figure \ref{fig:seedfieldPhoto}) containing alfalfa leafcutter bee cocoons (\textit{Megachile rotundata} F., hereafter LCB) at a rate of 50-100,000 coocoons/ha.
 % (1.3 or 2.6 shelters/ha).
@@
 
-\subsection*{Path analysis}
-The path analysis revealed that plant size and pollen deposition were the main drivers of seed production in seed canola, while plant size alone was the main driver in commodity canola (see Figure \ref{fig:allSEM} for paths and effect sizes).
+\subsection*{Path analyses}
+The path analyses revealed that plant size and pollen deposition were the main drivers of seed production in seed canola, while plant size alone was the main driver in commodity canola (see Figure \ref{fig:allSEM} for paths and effect sizes).
 LCB visitation strongly increased pollen deposition in seed canola, but there was no strong effect of HB visitation in either seed or commodity canola.
@@
 Pollen deposition increased pod set and seeds per pod in seed canola, but did not affect seed or pod production in commodity canola, showing that plant resources matter strongly for both crops, but that pollen limitation matters only in seed canola.
-Finally, there was an indirect effect (not related to visitation) of bay centre, distance from edge, and distance from LCB shelter on pollen count and pod set in seed fields, pointing to possible differences in pollen transfer even at the same rate of visitation.
+Finally, there was a direct effect (i.e.
+not mediated by visitation) of bay centre, distance from edge, and distance from LCB shelter on pollen count and pod set in seed fields, pointing to possible differences in pollen transfer even at the same rate of visitation.
+We consider each component of each path analysis in greater detail below.
 
@@
 % HB visitation decreased with distance from the edge of the field in both commodity and seed canola, and increased with distance from LCB shelters; interestingly, LCB visitation also decreased with distance from the edge of the field in seed fields.
-Honey bee flower visitation per plot decreased with distance away from the edge of the field in both commodity and seed canola fields.
+Honey bee flower visitation (per plot) decreased with distance away from the edge of the field in both commodity and seed canola fields.
 In commodity fields, HB visitation decreased from 12 visits/hr per plot at the edge to 1.8 visits/hr at 400 m into the field (Figure \ref{fig:allVisits}a, apiary of 40 hives).
@@
 HB visitation was also much lower near LCB shelters, dropping from 81 visits/hr at 20 m to 31 at 2 m (Figure \ref{fig:allVisits}b), likely due to competition or aggression from LCBs.
+
 % Visitation rates were higher in both years in Lethbridge (2014: 9.3 visits/hr, 2015: 7.1), but were higher in 2015 than 2014 at Grande Prairie (Z=2.3, p$=$0.02), rising from 5 visits/hr at the field edge in 2014 to 17 visits/hr in 2015.
@@
 LCB flower visitation was much higher close to their shelters, and surprisingly, was also higher at the edge than the centre of the field.
+Flower density was higher at further distances into the field in both field types, and had a positive effect on LCB visitation (but not HB visitation) in seed fields.
 LCB visitation dropped from 350 visits/hr at 2 m from the shelter to 50 visits/hr at 20 m (Figure \ref{fig:allVisits}b), and also decreased from 119 visits/hr at the edge of the field to 25 at the centre (Figure \ref{fig:allVisits}a, b)
@@
 
-Plant size had by far the strongest positive effect on the number of pods produced, and there was evidence of pod set suppressing flower production (see plant paths in Figure \ref{fig:allSEM}), but pollen only directly affected pod and seed production in seed canola.
-
+Plant size had by far the strongest positive effect on the number of pods produced (see large plant paths in Figure \ref{fig:allSEM}), and there was evidence of pod set suppressing flower production, but pollen only directly affected seed production in seed canola.
+Pollen deposition did not alter seed production in commodity canola (Figure \ref{fig:allSeeds}a,b,c), nor was there a direct effect of honey bee visitation or distance from field edge, at least at the levels we observed.
 In both commodity and seed canola, plant size had a strong positive effect on \% pod set and seeds per pod, but did not increase seed size in commodity canola (Figure \ref{fig:allSeeds}d,e,f).
-
-Plant density also had a positive direct effect on seed size in both crops, indicating that areas with better resources can support better-provisioned (but smaller) plants.
-Pod set also had a strong negative influence on flowers per plant in both crop types, indicating that high pod set suppresses future flower production.
-
-Pollen deposition did not alter seed production in commodity canola (Figure , nor was there a direct effect of honey bee visitation or distance from field edge (note log-scaled x-axis on Figure \ref{fig:allSeeds}).
-Pod set and seeds per pod in seed canola were increased by higher pollen deposition, and decreased with distance away from HB hives as well as distance from LCB shelters.
-Pod set was also lower in the centre of the female bay, again suggesting that pollen is lost when bees crossing over from male bays.
+Pod set in seed canola decreased with distance away from the field edge and LCB shelters, and was also lower at the centre of the female bay (independent of visitation and pollen deposition).
+This distance effect was not seen in commodity canola, suggesting a more long-term pollen limitation effect in seed canola that was not captured by our snapshot of pollen and visitation.
+Plant density also had a positive direct effect on seed size in both crops; this likely indicates field areas with better microclimate or soil resources rather than density effects \emph{per se}, as plants at edges of the field or in ``field holes" are typically both smaller and less dense.
+Finally, pod set also had a strong negative influence on flowers per plant in both crop types, indicating that high pod set suppresses future flower production.
 
@@
 
-The path analysis simulations further confirmed the results of the analysis: HB visitation had little effect on yield in either crop type, but LCB visitation improved yield in seed crops.
-The simulations showed no large effect of HB stocking on seed size or total yield in commodity fields (Figure \ref{fig:allYield}a, b), aside from the effect associated with distance from the edge of the field.
-Similarly, the simulations for seed fields showed a small increase in seed size and total yield with distance from the HB hives at the field edges, but the effect of distance from the leafcutter shelters was much more dramatic (compare the spacing of isolines along the x-axis and y-axis in Figures \ref{fig:allYield}c, d).
-A second set of simulations were run only in seed fields, in order to compare the effect of pollinator distances between the bay edge and centre. 
-This revealed that not only total seed size and overall yield lower at the bay centre, but that the effect of HB distance is effectively \emph{nil} at the bay centre (yield isolines are essentially horizontal in bay centre, and slightly tilted at the bay edge, Figure \ref{fig:allYield}d, f).
+Our path analysis simulations further confirmed the results of the analysis: HB visitation had little effect on yield in either crop type, but LCB visitation improved yield in seed crops.
+The simulations showed no large effect of HB stocking on seed size or total yield in commodity fields (Figure \ref{fig:allYield}a and b, respectively), aside from the effect associated with distance from the edge of the field.
+Similarly, the simulations for seed fields showed a small increase in seed size and total yield with distance from the HB hives at the field edges, but the effect of distance from the leafcutter shelters was much more dramatic (compare the spacing of isolines along the x-axis and y-axis in Figures \ref{fig:allYield}c and d).
+Simulations run separately for the edge and centre of the female bay revealed that not only are total seed size and total yield lower at the bay centre, but that the effect of HB distance is effectively \emph{nil} at the bay centre (yield isolines are essentially horizontal in bay centre, and slightly tilted at the bay edge, Figure \ref{fig:allYield}d and f).
 Interestingly, the simulations also showed evidence of nonlinear behaviour occurring in the centre of seed field bays, where a local minima in yield appears at approximately 25 m away from HB hives and 45 m away from LCB shelters (Figure \ref{fig:allYield})f), likely because of an interaction between the components of yield (seeds per pod, pods per plant, and weight per seed).
@@
     \includegraphics[width=\textwidth,keepaspectratio=true]{../Figures/allYield.png}
-    \caption{Effect of honey bee distance and leafcutter distance on seed size (first column) and total yield (second column), using coefficients from paths for simulation, while holding plant density constant at its mean value.
+    \caption{Effect of honey bee distance and leafcutter distance on seed size (mg/seed, first column) and total yield (tonnes/hectare, second column), using coefficients from paths for simulation, while holding plant density constant at its mean value.
 Shaded areas shown in a \& b are 95\% quantiles for the simulations.
@@
 
-We examined how bee visitation contributes to pollen deposition and seed yield in two canola crops, and showed a strong link between visitation and yield in seed canola, but not in commodity canola.
-HB and LCB visitation decreased with distance from their respective hive or shelter, but unexpectedly, LCBs were found more at the edge of the crop.
+We examined how bee visitation contributes to pollen deposition and seed yield in two different canola crops, and showed a strong link between visitation and yield in seed canola, but not in commodity canola.
+HB and LCB visitation decreased with distance from their respective hive or shelter, but unexpectedly, LCBs visited more frequently at the edge of the crop.
 HB visitation had little direct influence on pollen deposition in either crop type, while LCB visitation had a positive effect on pollen deposition in seed canola.
@@
 Finally, our simulation results from the path analyses confirmed this, and showed the strong influence of LCB visitation on seed size and yield.
-These results provide more realistic information on the value of pollination services in commodity and seed canola crops, and show how a statistical-mechanistic model of seed production provides richer insite into the process of seed production than linear models alone.
+These results provide more mechanistic information on the value of pollination services in commodity and seed canola crops, and show how a statistical-mechanistic model of seed production provides richer insight into the process of seed production than linear models alone.
 
@@
 
-HB visitation in both field types declined with distance into the field, but overall visitation was much higher than commodity fields, due to the higher HB stocking rate used in seed fields (3.6 vs.
+HB visitation in both field types declined with distance into the field, but overall visitation was much higher in seed fields than commodity fields, due to the higher HB stocking rate used in seed fields (3.6 vs.
 0.6 hives/ha).
-Since HBs travel from their hive outside the edge of the field, this decline was not surprising, but we did not expect a similar decrease in LCB visitation with distance into the field, as their shelters are located \textit{within} the field.
-This decrease with distance into the field may have been caused by LCBs migrating from shelters at the centre of the field to the edge \citep{goerzen1995}, as female LCBs are central-place foragers, and tend to not forage far from their nests \citep{peterson2005,pitts2011, brunet2019}.
+Since HBs travel to the crop from their hive outside the edge of the field, this decline was not surprising \citep{robinson2022}, but we did not expect a similar decrease in LCB visitation with distance into the field, as their shelters are located \textit{within} the field.
+This decrease with distance into the field may have been caused by LCBs migrating from shelters at the centre of the field to the edge \citep{goerzen1995}, as female LCBs are central-place foragers and tend to not forage far from their nests \citep{peterson2005,pitts2011, brunet2019}.
 However, LCBs are not as constrained to a single nest as HBs are, and can drift between shelters within a given field \citep{goerzen1995, pittsSinger2013}.
-LCBs must also forage for leaf materials to create cocoons, but prefer thinner, non-canola leaf types, mainly plants in the families Fabaceae and Rosaceae \citep{sinu2018}.
-Since seed canola fields have very few weeds within the area of the crop, LCBs at the centre of the field may have few choices of leaf material, or alternative pollen and nectar sources.
-Therefore, LCBs likely move from the shelters at which they were released to the shelters at the edge of the field, so as to gain access to better leaf material or different sources of pollen and nectar \citep{horne1995, horne1995b}.
+LCBs must also forage for leaf materials to create cocoons, but seem to prefer thinner leaves than canola, mainly plants in the families Fabaceae and Rosaceae \citep{sinu2018}.
+Since seed canola fields have very few weeds within the crop, LCBs at the centre of the field may have few choices of leaf material, or alternative pollen and nectar sources.
+Therefore, LCBs likely move from the shelters at which they were released to the shelters at the edge of the field, so as to gain access to better leaf material or more diverse pollen and nectar sources \citep{horne1995, horne1995b}.
 % To test this, a mark-recapture study of female LCBs could be done to see if bees migrate to shelters at the edge of the field, or if visitation is higher due to other reasons (\textit{e.g.} feral populations migrating to edge of field, long-distance foraging from centre of field as in \citealp{peterson2005}).
@@
 %Leafcutter-honeybee interactions
-In seed fields, LCB visitation was higher, and HB visitation was correspondingly lower in areas close to LCB shelters. 
-Lower HB visitation may have been driven by lower nectar and pollen resources, as areas close to leafcutter shelters can become depleted in nectar and pollen \citep{currie1997}.
+In seed fields, HB visitation was correspondingly lower in areas close to LCB shelters, suggesting competition between species.
+Lower HB visitation may have been caused by lower nectar and pollen resources, as areas close to leafcutter shelters can become depleted in nectar and pollen \citep{currie1997}.
 HBs also suffer from direct interference by LCBs near to their shelters; during the study we observed LCBs directly harassing HBs during the plot-level observations, attacking HBs both on the flowers and in the air (also seen by \citealp{batra1978} and \citealp{waytesMsc}).
 HB visitation and foraging behaviour varied strongly between the edge and centre of the female bays in seed fields, while there was little difference between LCB visitation rates.
-HB visitation rates were almost twice as high at the centre of the female bay, likely reflecting a stronger need for pollen among LCBs than HBs \citep{cane2011} (although interestingly, there was also no difference in LCB visitation between male and female bays).
+HB visitation rates were almost twice as high at the centre of the female bay, but there was no corresponding difference in LCB visitation between male and female bays; this may reflect a greater need for pollen among LCBs than HBs \citep{cane2011}, as female canola plants produce only nectar.
 
-Very few HBs in the female bay were pollen foragers (1.4\%, see Table \ref{tab:sideWorking}), meaning that foragers who have (recently) come into contact with pollen rare.
+Very few HBs in the female bay were pollen foragers (1.4\%, see Table \ref{tab:sideWorking}), meaning that foragers who have recently come into contact with pollen are rare.
 Both \citet{waytesMsc} and \citet{gaffney2019} showed that HBs exhibit floral fidelity during foraging trips, with minimal crossing between male and female bays ($\sim$5\% of observations, \citealp{waytesMsc}), limiting pollen transfer between the male and female flowers.
@@
 %Pollen deposition in commodity fields
-HB visitation did not increase pollen deposition in commodity canola fields compared to unstocked fields, meaning that wind and/or self-pollination are the likely agents of pollen transfer.
-The stigmas and flowers of \emph{Brassica} are not aligned for dispersal and deposition from the wind, so cross-pollination likely occurs mainly via insects \citep{mesquida1982,cresswell2004}.
+HB visitation did not increase pollen deposition in commodity canola fields compared to unstocked fields, meaning that self-pollination are the likely agents of pollen transfer (\emph{Brassica} flowers are not aligned for dispersal and deposition from the wind, so cross-pollination likely occurs mainly via insects \citep{mesquida1982,cresswell2004}).
 However, wind-induced self-pollination (plant shaking) can increase yield in \textit{Brassica} \citep{williams1986, mesquida1988c}, and fields without bee pollination have outcrossing rates of about 20\% within the field \citep{rakow1987,becker1992}.
@@
 \emph{Bulbul}).
-However, \citet{waytesMsc} used male-sterile flowers from seed canola fields and found that HB pollen foragers deposited far less outcrossed pollen ($\sim$ 2 grains per visit), suggesting that much of the pollen deposited on commodity canola stigmas may be self-pollen.
+However, \citet{waytesMsc} used male-sterile flowers from seed canola fields and found that HB pollen foragers deposited far less outcrossed pollen than previously reported ($\sim$ 2 grains per visit), suggesting that much of the pollen deposited on commodity canola stigmas may be self-pollen.
 Because the overall pollen deposition rates found in this study were high, HB visitation seems to have made little difference in the amount of self-pollination, as large amounts of pollen were present on commodity canola stigmas even at the centre of unstocked fields.
-This suggests that commodity canola stigmas are largely saturated with self-pollen, swamping any extra pollen deposition by HBs.
+This suggests that commodity canola stigmas are largely saturated with self-pollen, effectively ``swamping" any extra pollen deposition by HBs.
 % The typical lifetime of a canola flower is approximately 3 days, and the stigmatic surface is receptive for 24--36 hours within this period \citep{eisikowitch1981,hoyle2007}, so it may be that 10-minutes of observing flower visitors was too short of a time interval to relate to pollen deposition.
@@
 
-Our models also showed that pollen-transferring behaviour of HBs is limited in seed fields, as deposition strongly increased with LCB visitation but not HB visitation.
+Our models also revealed that pollen-transferring behaviour of HBs is limited in seed fields, as deposition strongly increased with LCB visitation but not HB visitation.
 HBs in seed fields tended to visit more in the centre of the female bay, even close to the edge of the field, yet pollen deposition was still about 40\% lower.
 LCBs switch between male and female flowers more frequently than HBs, travel further between flowers, transport more viable pollen, and tend not to side-work canola flowers \citep{soroka2001, parker2015, waytesMsc, brunet2019}, all of which may explain their higher pollination efficacy.
-Pollen deposition in seed fields also decreased with distance from the edge of the field, and was lower in the centre of the female bays independent of visitation, suggesting lower pollen tranfer per visit.
+Pollen deposition in seed fields also decreased with distance from the edge of the field, and was lower in the centre of the female bays independent of visitation, suggesting lower pollen transfer per visit.
 These may have been caused by two separate processes: a) low pollen carryover with distance into the female bays, and b) shorter trips between flowers at the centre of the field.
@@
 
-Plant size increased the rate of pod set in commodity canola, but both plant size and pollen increased pod set in seed canola, suggesting that both pollen deposition and plant resources constrain pod production.
+Plant size increased the proportion of pod set in commodity canola, but both plant size and pollen deposition increased pod set in seed canola, suggesting that both pollen deposition and plant resources constrain pod production.
 This is similar to the findings of \citet{mesquida1981} and \citet{steffan2003}, who found that pod set in male-sterile plants responded positively to visitation, while male-fertile plants had no response (but see \citealp{adegas1992}).
 Both pod set and seeds per pod can increase with extra pollination \citep{jauker2008,sabbahi2005,sabbahi2006,duran2010}, so the low influence of pollination in commodity fields may be due to a high overall level of pollen deposition (Figure \ref{fig:allPollen}).
-There was no additional effect of HB visitation on pod set, meaning that that HB visitation did not cause more pollen deposition or improve its quality through increased outcrossing (as in \citealt{rosa2011}), but this may depend on the variety \citep{adamidis2019}.
+There was no additional effect of HB visitation on pod set, meaning that that HB visitation did not cause more pollen deposition or improve its quality through increased outcrossing (as in \citealt{rosa2011}), but this may depend on the variety \citep{marini2015, adamidis2019}.
 Flowers per plant was reduced by pod set, implying that high pod set suppresses further flower production or increases competition among pods for plant resources.
-The first scenario is more likely, as \citet{sabbahi2006} and \citet{mesquida1981} both found that canola plants compensated for experimental removal of flowers by increasing branch and flower production, until the plant reached about 170 pods.
+The first scenario is more likely, as \citet{sabbahi2006} and \citet{mesquida1981} both found that canola plants compensated for experimental removal of flowers by increasing branch and flower production, until the plant reached about 170 pods per plant (our plants had a mean of 143 and 299 pods per plant in commodity and seed canola, respectively).
 There were also effects of distance on pod set independent of pollen: pod set decreased with distance from the edge of the field, distance to LCB shelters, and was lower at the centre of the female bays.
@@
 First, it shows how two important species of commercial pollinators decline with distance from their nesting sites, and how LCBs unexpectedly decline with distance from the edge of the field.
-Second, it sheds light on the relative importance of HBs and LCBs as pollinators, showing that commonly-used levels of HB stocking do not strongly influence yield in commodity canola crops, and that LCBs are likely the primary pollinators of seed canola.
-Finally, it contextualizes the value of pollination alongside plant resources, showing that plant resources and pollen limit production in seed canola, while only plant resources limit commodity production.
+Second, it sheds light on the relative importance of HBs and LCBs as pollinators, showing that levels of HB stocking used for honey production do not strongly influence yield in commodity canola crops, and the importance of LCBs as primary pollinators of seed canola.
+Finally, it contextualizes the value of pollination alongside plant resources, showing that plant resources and pollen limit production in seed canola, while only plant resources limit production in commodity fields.
 Our unique SEM approach allowed us to formulate and test relationships within a causal framework, which we consider to be extremely valuable, and highly underused in agricultural studies.

### 2022-09-26 Manuscript/supplemental.tex
Worked on SH revisions
Finished comments from SH

@@
 
-\begin{figure}
+\begin{figure}[h]
     \centering
-    \includegraphics[width=\textwidth,keepaspectratio=true]{../Figures/FieldLocations.png}
+    \includegraphics[width=0.9\textwidth,keepaspectratio=true]{../Figures/FieldLocations.png}
     \caption{Map of sampled fields, showing locations of 29 commodity canola fields (14 during 2014, 15 during 2015), and 35 seed canola fields (15 during 2015, 20 during 2016).
@@
 
-\begin{figure}
+\begin{figure}[h]
     \centering
     \includegraphics[width=\textwidth,keepaspectratio=true]{seedfieldBays.jpg}
-    \caption[Hybrid seed field near Rainer, AB]{Hybrid seed field near Rainer, AB, showing the outlines of male and female bays in the foreground, with orange leafcutter bee shelters stationed throughout the field.
+    \caption[Hybrid seed field production field near Rainer, AB]{Hybrid seed field near Rainer, AB, showing the outlines of male and female bays in the foreground, with orange leafcutter bee shelters stationed throughout the field.
 The linear structure on the horizon is the central-pivot irrigation sprinkler.}
@@
 
-\begin{figure}
+\begin{figure}[h]
     \centering
-    \includegraphics[width=0.6\textwidth,keepaspectratio=true]{seedfieldPlots.png}
+    \includegraphics[width=\textwidth,keepaspectratio=true]{seedfieldPlots.png}
     \caption[Plot arrangement for surveys in hybrid seed fields]{Plot arrangement for surveys in hybrid seed fields, showing hypothetical arrangement of leafcutter shelters ($\Delta$), and male-fertile (\Hermaphrodite) and female bays (\Female) at 5m from the edge of the field.
-Plots were placed 5, 20, 100, and 400m along a transect (dashed line) from the field edge nearest to the set of honey bee hives.
-Plots were placed side-by-side in the male bay and edge of the female bay (``edge" plots), and at the 5m and 400m distances, a plot was placed in the centre of the female bay (``centre" plots).}
+Plots were placed along a transect (dashed line) from the field edge nearest to the set of honey bee hives.
+Plots were placed side-by-side in the male bay and edge of the female bay (``edge" plots), and at the 5m and 400m distances, an additional plot was placed in the centre of the female bay (``centre" plots).
+Note: this figure shows a small section of a much larger circular field.}
     \label{fig:seedfieldPlots}
@@
 
-\begin{table}
+\begin{table}[h]
 \caption{Summary of variables used in structural equation models.}
 \centering
-
 \begin{tabular}{l|l|r|r|r|r|r}
@@
 
-During 2015, we recorded whether honey bees were top-working or side-working flowers (see also \citealp{free1973, free1983, mohr1988}).
+In 2015, we recorded whether honey bees were top-working or side-working flowers (see also \citealp{free1973, free1983, mohr1988}).
 Top-working bees landed on the top of the flower and inserted their proboscis down between the petals to access the nectaries of the flower, while side-working bees landed on the side of the flower and stole nectar by inserted their proboscis between the petals, avoiding contact with the stigma or anthers.
@@
 
-\begin{table}
+\begin{table}[h]
+  \caption{Number of flower visitors recorded over a total of 44.8 hours of observation in commodity fields (2014 and 2015), and 46.9 hours of observation in the seed fields (2015 and 2016).
+``Fly" refers to larger calyptrate muscoid flies (families Muscidae, Anthomyiidae, Caliphoridae), while ``Hover fly" refers to Syrphid flies.
+``Other bee" included Halictid and Andrenid bees, while ``Bumble bee" was \textit{Bombus} spp.
+``Butterfly" refers to all visiting Lepidopterans, mostly Pierids.}
+  \centering
     \begin{tabular}{r|r|l|r|l}
@@
     \end{tabular}
-    \caption{Number of flower visitors recorded over a total of 44.8 hours of observation in commodity fields (2014 and 2015), and 46.9 hours of observation in the seed fields (2015 and 2016).
-``Fly" refers to larger calyptrate muscoid flies (families Muscidae, Anthomyiidae, Caliphoridae), while ``Hover fly" refers to Syrphid flies.
-``Other bee" included Halictid and Andrenid bees, while ``Bumble bee" was \textit{Bombus} spp.
-``Butterfly" refers to all visiting Lepidopterans, mostly Pierids.}
     \label{tab:propVisitors}
@@
 
-\begin{table}
+\begin{table}[h]
+\caption[Foraging behaviours of honey bees on commodity and seed canola flowers]{Foraging behaviours of honey bees on commodity and seed canola flowers, recorded during 2015.
+``Top" (top-working) indicates that the bee inserted their proboscis down between the petals from the top of the flower, while ``side" (side-working) indicates that the bee fed from the side of the flower and did not contact the anthers or stigma.
+Pollen foragers had pollen visible on their corbicula, while nectar foragers had none.}
 \begin{tabular}{r|r|l|r|l|r|l}
@@
 \end{tabular}
-\caption[Foraging behaviours of honey bees on commodity and seed canola flowers]{Foraging behaviours of honey bees on commodity and seed canola flowers, recorded during 2015.
-``Top" (top-working) indicates that the bee inserted their proboscis down between the petals from the top of the flower, while ``side" (side-working) indicates that the bee fed from the side of the flower and did not contact the anthers or stigma.
-Pollen foragers had pollen visible on their corbicula, while nectar foragers had none.}
 \label{tab:sideWorking}
@@
 \end{tabular}
+\label{tab:totalYieldCoefs}
 \endgroup{}
-
-\label{tab:totalYieldCoefs}
 \end{table}

### 2022-09-26 sem plots.R

@@ -192,6 +192,5 @@ tidySeedDAG$data <- tidySeedDAG$data %>% #Match coefs to dagitty set
 # Combine plots -----------------------------------------------------------
 
 (p <- ggarrange(commSEM,seedSEM,ncol=1,nrow=2))
-ggsave('./Figures/allSEM.png',p,height = 14,width=12,bg='white')
-
-
+ggsave('./Figures/allSEM_new.png',p,height = 14,width=12,bg='white')
+# ggsave('./Figures/allSEM_new.svg',p,height = 14,width=12,bg='white') #Save to vector graphics file

### 2022-11-07 Manuscript/main.tex
Worked on RW and SP revisions

@@
 \begin{abstract}
-Insect-mediated pollination of crops is an important input to agricultural production, but pollination management suffers from key knowledge gaps that hinder its greater utility. 
+Insect-mediated pollination of crops is an important service to agricultural production, but pollination management suffers from key knowledge gaps that hinder its greater utility. 
 While a solid theoretical and mechanistic framework for plant pollination exists, the pollination of agricultural crops is often treated as a ``black box”, without reference to the specific mechanisms underlying the processes of pollination and fruit production.
@@
 \end{abstract}
-
-% Current Intro Structure:
-% - Animal pollination = important ecosystem service
-%     - NEEDS LEAD-IN TO OTHER PARAGRAPHS
-% - Insect visitation can increase fruit production via better pollen deposition
-% - Size and number of seeds matured depends on availability of plant resources
-% - Trade-offs exist at plant and flower level
-% - Pollination is important in canola production
-% - Insect pollination can increase yields of commercial canola crops 
-% - Fruit production in flowering plants involves a sequence of processes
-%     - SEMs are convenient for modeling this
-% - In this study, We modeled how distance influences pollinator visitation, which in turn influences ...
-%     - List of 5 hypotheses
-
-% Current Discussion structure
-% * Visitation
-% - Honey bee visitation in seed fields was much higher than commercial fields
-% - Hbee decline into field expected, Lbee decline surprising
-% - Hbee visitation lower near to leafcutter shelters
-%     - Which is causing which?
-% * Pollen deposition
-% - Hbees don't influence pollen in commodity fields
-% - In seed fields, lbees influence pollen, but not hbees
-% - Why did honey bees have so little influence on pollen deposition in both commodity and seed canola fields?
-% - Any positive pollination effect of honey bees in hybrid seed fields is likely indirect
-% * Pod production
-% - Commodity field pod production mainly controlled by plant size, not pollen
-% - Seed field pod production influenced by plant size & pollen
-% * Seed size/number
-% - Seed canola size not altered by pollen, but negative relationship b/w seeds per pod & seed size
-% - Number of seeds per pod not altered except by year
-% * Summary
-% - Why no effect of insect pollination in commodity?
-% - Implications for pollination management
-
-% WHAT IS MY MAIN STORY?
-% Q: What is the relative contribution of bees to seed yield in canola? Do they matter relative to plant resources?
-% A: Plant size is the main driver of yield. Leafcutter bees increase pollen deposition and yield, but honey bees do not.
-% Hook:
-% Bee visitation can enhance seed production in crop plants, but only if pollen deposition is limited and plant resources are available.
-% We found that while commodity canola is not pollen-limited, hybrid seed canola is, and while leafcutter bees increase pollen deposition, honey bees do not.
-
-% WHAT DOES THE READER NEED TO KNOW?
 
@@
 
+%Comments from SP:
+% - Could directly contrast results to those of Sabbahi et al 2005, who found 46% increase in yield at 3 colonies/ha
+% - What might the next steps be for testing recommendations in seed fields? LCBs only? Varietal differences? Bay sizes?
+
 \section*{Introduction}
-%SH: PARAGRAPH COULD BE REMOVED/SHORTENED FOR PAPER, BUT FINE FOR THESIS
 Animal pollination of agricultural flowering plants is an important ecosystem service that contributes to about 10\% of total crop production value worldwide \citep{gallai2009}, and animal-pollinated plants produce a large number of important micronutrients in the human diet \citep{eilers2011}.
@@
 
-Pollinator visitation is not uniform within fields: visitation rates typically decline with distance away from the pollinators' nest sites.
+Pollinator visitation is not uniform within fields: visitation rates typically decline with distance away from the pollinators' nest sites \citep{Ricketts2008}.
 Smaller bees fly shorter distances than larger bees \citep{greenleaf2007,zurbuchen2010}, so their presence at the centre of large fields can be limited \citep{isaacs2010}. 
@@
 Similarly, foragers will often specialize on certain species or morphs of flowers in order to forage more efficiently (floral fidelity, \citealp{heinrich1976b, goulson1997}). 
-Pollination of hybrid seed crops presents a challenge for specialized foragers, as it requires movement of pollen between separate lines of plants, meaning that fidelity can reduce pollen transfer \citep{waytesMsc, gaffney2019}.
+Pollination of hybrid seed crops presents a challenge for specialized foragers, as it requires movement of pollen between separate lines of plants, meaning that fidelity can reduce pollen transfer \citep{gaffney2019,waytes2022}.
 Competition for floral resources can occur between different species of foragers, but they can spatially or temporally separate their foraging to reduce competition (\citealp{schaffer1979,thomson1987}, but see \citealp{steffan2000}), such as switching between floral morphs more often, or visiting less frequently \citep{heinrich1979, greenleaf2006}.
@@
 Hybrid \emph{commodity canola} (used for oil and meal production) is the offspring of two parental \emph{seed canola} breeding lines, a male-sterile ``female" and a hermaphroditic ``male" line \citep{westcott2001,steffan2003,clay2009}.
-Seed canola production therefore requires a large number of pollinators to ensure pollen transfer from the male to the femal line (seeds from the male line are not harvested), but there are few studies that examine pollination in these seed production systems (but see \citealp{mesquida1981, mesquida1991}).
-Bee pollination may also increase the yield of commodity canola \citep{morandin2005, rader_phd, bommarco2012, bartomeus2015,perrot2018}, but this is unclear, as many key studies suffer from either a lack of realistic context, have a number of potential confounding variables, or infer plant-level outcomes from flower-level treatments \citep{ouvrard2019}.
+Seed canola production therefore requires a large number of pollinators to ensure pollen transfer from the male to the female line (seeds from the male line are not harvested), but there are few studies that examine pollination in these seed production systems (but see \citealp{mesquida1981, mesquida1991}).
+Bee pollination may also increase the yield of commodity canola \citep{morandin2005, rader_phd, bommarco2012, bartomeus2015,perrot2018}, but this is unclear, as many key studies suffer from either a lack of realistic context, have a number of potential confounding variables, or infer plant-level outcomes from flower-level treatments (reviewed by \citealt{ouvrard2019}).
 Greenhouse experiments typically involve unrealistically high levels of pollination, nutrient availability, and water, all of which can interact with yield \citep{bartomeus2015,marini2015}.
-Field studies often relate yield to indirect measures of pollination services, such as species richness or distance from sources of potential pollinators, or do not examine production at the plant level \citep{morandin2005, ricketts2008}.
+Field studies often relate yield to indirect measures of pollination services, such as species richness or distance from sources of potential pollinators, or do not examine production at the plant level \citep{morandin2005, Ricketts2008}.
 These proxies provide limited information about how plants dynamically respond to pollen exclusion or addition (but see \citealp{sabbahi2005}).
@@
 However, other studies of canola pollination focus on individual processes, such as visitation and pollination \citep{cresswell1999, thomson2001}, or visitation and yield \citep{steffan2003, manning2005, hudewenz2013}, but have not incorporated the links in a single framework (but see \citealp{saez2018}), and few have used realistic field data \citep{morandin2005, isaacs2010}.
-In this study, we examine how distance influences pollinator visitation, which in turn influences pollen deposition and seed yield, using commodity and seed canola crops in Alberta, Canada.
+In this study, we examine how distance influences managed bee visitation, which in turn influences pollen deposition and seed yield, using commodity and seed canola crops in Alberta, Canada.
 Using both commodity and seed canola provides an opportunity to compare two plant varieties that differ strongly in their pollination requirements, using a similar type of structural model, while accounting for agricultural differences between varieties.
@@
 \subsection*{Data collection}
-From June through August of 2014 and 2015, we surveyed 29 commodity canola fields (14 in 2014, 15 in 2015) near Beaverlodge, Alberta and 31 fields (17 in 2014, 14 in 2015) near Lethbridge, Alberta.
+From June through August of 2014 and 2015, we surveyed 29 commodity canola fields (14 in 2014, 15 in 2015) near Beaverlodge, Alberta and 31 fields (17 in 2014, 14 in 2015) near Lethbridge, Alberta (Figure \ref{fig:fieldMap}).
 Commodity canola fields were selected based on the proximity of honey bee apiaries and site access. 
-28 of the 60 fields were stocked with Western honey bees (\emph{Apis mellifera} L., hereafter HB) at the corner or side of the field (mean: 0.6 hives/hectare, SD: 0.58) while 32 fields were unstocked.
-%range: 0.03 - 3.1 Apiaries were stationed at the edges of fields, often near to shrubs or tree-lines to act as a wind break.
-14 of 31 of the fields near Lethbridge were watered using central-pivot irrigation systems.
+Colonies of Western honey bees (\emph{Apis mellifera} L., hereafter HB) were located at the corner or side of 28 of the 60 fields (stocking rates: 0.03 - 3.1 hives/ha) while 32 fields were unstocked.
+%range: 0.03 - 3.1 hives/ha, mean: 0.6, sd: 0.58 Apiaries were stationed at the edges of fields, often near to shrubs or tree-lines to act as a wind break.
+Central-pivot irrigation systems were present at 14 of the 31 fields near Lethbridge.
 Growers were also asked for canola variety information, but there was not enough replication to test for difference between varieties.
@@
 Seed fields were also stocked with shelters (1.3 - 2.6 shelters/ha, Figure \ref{fig:seedfieldPhoto}) containing alfalfa leafcutter bee cocoons (\textit{Megachile rotundata} F., hereafter LCB) at a rate of 50-100,000 coocoons/ha.
+Both HBs and LCBs are managed pollinators that are not native to Alberta, and are uncommon outside of managed pollination systems and honey production yards, so we assumed that the hives and shelters were the sole sources of visiting bees in the observed fields.
+
 % (1.3 or 2.6 shelters/ha).
@@
 
-In both field types, we established set of plots at varying distance from the sources of pollinators. 
-In commodity fields, plots were located at 1 m$^2$ plots at 5, 20, 100, and 500 m (271 total plots), starting at the field edge closest to the set of honey bee hives or potential sources of natural pollinating insects in unstocked fields (forests, shrublands, or grasslands).
-We observed very few wild pollinators (Table \ref{tab:propVisitors}), so these were excluded from the analysis.
+In both field types, we established sets of plots at varying distances from the nesting sources of pollinators. 
+In commodity fields, 1 m$^2$ plots (271 total plots) were located at 5, 20, 100, and 500 m away from the field edge closest to the set of honey bee hives or potential sources of natural pollinating insects in unstocked fields (forests, shrublands, or grasslands).
+We observed very few wild bees in either field type (Table \ref{tab:propVisitors}), so these were excluded from the analysis.
 In seed fields, we established plots at 5, 20, 100 (250 m in 2016), and 400 m into the field along a transect from the nearest set of honey bee hives, using pairs of plots at the edge of adjacent male and female bays (Figure \ref{fig:seedfieldPlots}).
@@
 Distances to nearest shelters were measured using a Nikon\texttrademark Laser 800S Rangefinder.
-Finally, we incorporated plot-level visitation data from Waytes (\citeyear{waytesMsc}; same years and locations) to more accurately gauge the effect of distance from shelter on visitation rates (647 total plots).
-All surveys occurred on fair-weather days (median temperature: 24.5$^\circ$C., range: 17--33) with no rain and minimal wind ($>$30 km/hr).
+Finally, we incorporated plot-level visitation data from Waytes (\citeyear{waytes2022}; same years and locations) to more accurately gauge the effect of distance from shelter on visitation rates (647 total plots).
+All surveys occurred on fair-weather days (median temperature: 24.5$^\circ$C., range: 17--33$^\circ$C.) with no rain and minimal wind ($>$30 km/hr); wind speed and temperature were measured at each site with a Kestral\texttrademark 2500 weather meter.
 % Mean air temperature was similar between years in Grande Prairie ($\approx$ 22$^\circ$C), but Lethbridge was warmer in 2015 (23 vs. 28$^\circ$C).
-%Plots were marked with coloured stakes driven into the soil to locate them later in the season. %Full paper should have a table of climate variables. Windspeed needs sorting out (unit problems?)
+%Plots were marked with coloured stakes driven into the soil to locate them later in the season. %Full paper should have a table of climate variables.
 
-Insect visitation and pollination data were collected once during the main canola bloom at each field (late June - late July), and plants were collected just prior to harvest (mid - late August).
-We recorded the number of insect visits that contacted the stigmas and anthers of flowers during 10 minutes of observation (5 min for seed fields during 2015), recorded the identity of the visitor, and counted the number of open, visitable flowers in each plot (petals had not yet started to dehisce, style had not elongated more than 3-4 millimeters beyond the anthers).
+Insect visitation and pollination data were collected once at each field during the main canola bloom (late June - late July), and plants were collected just prior to harvest (mid - late August).
+We recorded the number of insect visits that contacted the stigmas and anthers of flowers during 10 min of observation (5 min for seed fields during 2015), recorded the identity of the visitor, and counted the number of open, visitable flowers in each plot (petals had not yet started to wilt, style had not elongated more than 3-4 millimeters beyond the anthers).
 To assess pollen deposition, we collected stigmas from five random flowers at each female plot, mounted them in fuchsin gel \citep{beattie1971} on depression slides, and counted the pollen on each stigma using a Leica\texttrademark DME 13595 light microscope under 100x magnification (1294 commodity and 1050 seed canola stigmas).
@@
 We estimated seed size and seeds per pod by averaging the seed count and weight from five pods on each plant.
-Finally, we threshed all the pods for each plant by hand, winnowed them using an air separator, and weighed the total mass of cleaned seeds. % (3872 commodity canola pods, 2885 seed canola pods)
+Finally, we threshed all the pods for each plant by hand, winnowed them using an air separator, and weighed the total mass of cleaned seeds (hereafter ``yield").
+% (3872 commodity canola pods, 2885 seed canola pods)
 
 \subsection*{Analysis}
-To examine how yield is influenced by visitation, we used piecewise structural equation models (pSEM, \citealp{shipley2009}).
+To examine how yield is influenced by visitation, we used piecewise structural equation models (pSEM, \citealp{shipley2009}) implemented in R 4.2.1 \citep{Rcore}.
 Structural equation models (SEMs) are a set of linear models arranged in a causal network, which provides a framework for testing hypotheses about complex systems \citep{grace2012, lefcheck2015}.
@@
 SEMs represent an intermediate class of statistical models, occupying a space somewhere between linear regression (or machine learning) models and dynamic linear models, making them ideal for generating and testing relationships between large sets of variables \citep{grace2006, kline2013}.
-Starting with a simple model (visitation $\rightarrow$ pollen deposition $\rightarrow$ fruit production $\leftarrow$ plant resources), we built a detailed model relating visitation to pollination to seed yield within a causal framework (see Figure \ref{fig:allSEM} in Results).
-We also ran a linear model outside of each SEM to predict total yield (g per plant) as a function of the seed size, seeds per pod, and pods per plant (see Table \ref{tab:totalYieldCoefs}).
+Starting with a simple model (visitation $\rightarrow$ pollen deposition $\rightarrow$ fruit production $\leftarrow$ plant resources), we built a detailed model relating visitation to pollination to seed yield within a causal framework (Figure \ref{fig:allSEM}).
+We also ran a linear model outside of each SEM to predict yield (g per plant) as a function of the seed size, seeds per pod, and pods per plant (see Table \ref{tab:totalYieldCoefs}).
 After the models were fit and validated, we simulated seed size and yield at varying distances from pollinators, using the coefficients from each model to integrate the effect of pollination on yield across all sub-models (while holding plant density constant).
@@
 Visitation models used $log$(time) as an ``offset" variable to account for differences in observation times.
-We observed LCBs directly harassing HBs during the plot-level observations, attacking HBs both on the flowers and in the air (also seen by \citealp{batra1978} and \citealp{waytesMsc}), but HBs were never the aggressor in these interactions, so we treated LCB vistation as a potential cause of HB visitation (Figure \ref{fig:allSEM}).
+We observed LCBs directly harassing HBs during the plot-level observations, attacking HBs both on the flowers and in the air (also seen by \citealp{batra1978} and \citealp{waytes2022}), but HBs were never the aggressor in these interactions, so we treated LCB visitation as a potential cause of HB visitation (Figure \ref{fig:allSEM}).
 Pod set can suppress future vegetative growth and flower production \citep{stephenson1981}, but SEMs do not allow for causal loops \citep{grace2012}, so we included a path from pod set to flower production as the closest approximation of this process.
@@
 Plant and pollen samples were not collected from male bays in seed fields, and there were no large differences in visitation rates for honey bees or LCBs (p = 0.32, 0.72, respectively) once other terms were included as covariates, so bay was excluded from further analysis.
-See Equation sets S1 and S2 for model specifications) Table \ref{tab:dataSummary} for a brief summary of the variables used in each SEM.
+See Equation sets S1 and S2 for GLMM specifications and Table \ref{tab:dataSummary} for a summary of the SEM variables.
 % Random intercepts were used to model variance between fields, within-field (pollen, flower survival, seed count \& size), and within-plot (seed count \& size).
@@
 Similarly, the initial seed field pSEM also had several missing paths (C = 105.6, df = 76, p = 0.01), which were added, making the updated pSEM adequate (C = 72.2, k = 72, p = 0.47).
-Basis sets were generated using the \texttt{dagitty} library in R 4.2.1.
+Basis sets were generated using the \texttt{dagitty} library \citep{textor2016}.
 
@@
 Predictions from models are taken from median values of the posterior, while uncertainty is derived from the 95\% credible intervals (CIs).
-Figures were made using \texttt{ggplot2} and \texttt{ggpubr} \citep{wickham2016,kassambara2020}.
+Figures were made using \texttt{ggplot2} and \texttt{ggpubr} \citep{wickham2016, kassambara2020}.
 
@@
 \subsection*{Path analyses}
-The path analyses revealed that plant size and pollen deposition were the main drivers of seed production in seed canola, while plant size alone was the main driver in commodity canola (see Figure \ref{fig:allSEM} for paths and effect sizes).
+The path analyses revealed that plant size and pollen deposition were the main drivers of yield in seed canola, while plant size was the main driver in commodity canola (see Figure \ref{fig:allSEM} for paths and effect sizes).
 LCB visitation strongly increased pollen deposition in seed canola, but there was no strong effect of HB visitation in either seed or commodity canola.
 Plant size increased with distance from the edge of the field in both crops, as well as plant density in seed fields.
-Plant size strongly increased the number of flowers per plant in both crops, and there were strong negative paths from pods per plant to flowers per plant, indicating that high flower survival suppressed future flower production in both crops.
+Plant size strongly increased the number of flowers per plant in both crops, and there were strong negative paths from pods per plant to flowers per plant, indicating that high flower survival suppressed flower production in both crops.
 Plant size increased pod set and seeds per pod in both crop types, and also increased seed size in seed canola plants.
-Pollen deposition increased pod set and seeds per pod in seed canola, but did not affect seed or pod production in commodity canola, showing that plant resources matter strongly for both crops, but that pollen limitation matters only in seed canola.
+Pollen deposition increased pod set and seeds per pod in seed canola, but had no effect in commodity canola, showing that plant resources matter strongly for both crops, but that pollen limitation matters only in seed canola.
 Finally, there was a direct effect (i.e.
@@
 Finally, commodity plants were also lower-yielding than seed canola plants (mean: 6.8 vs.
-9.5 g seed per plant), but produced more seeds per gram of vegetative biomass than seed canola plants (mean: 0.38 vs.
-0.32), likely due to lower pollen limitation.
+9.5 g seed per plant), but had a lower harvest index (grams seeds per gram of vegetative biomass) than seed canola plants (0.38 vs.
+0.32 g/g), likely due to lower pollen limitation.
 
-Plant size had by far the strongest positive effect on the number of pods produced (see large plant paths in Figure \ref{fig:allSEM}), and there was evidence of pod set suppressing flower production, but pollen only directly affected seed production in seed canola.
-Pollen deposition did not alter seed production in commodity canola (Figure \ref{fig:allSeeds}a,b,c), nor was there a direct effect of honey bee visitation or distance from field edge, at least at the levels we observed.
-In both commodity and seed canola, plant size had a strong positive effect on \% pod set and seeds per pod, but did not increase seed size in commodity canola (Figure \ref{fig:allSeeds}d,e,f).
+Plant size had by far the strongest positive effect on the number of pods produced (see large plant paths in Figure \ref{fig:allSEM}), and there was evidence of pod set suppressing flower production.
+However, pollen deposition did not alter seed or pod production in commodity canola (Figure \ref{fig:allSeeds}a,b,c), nor was there a direct effect of honey bee visitation or distance from field edge, at least at the levels we observed.
+In both commodity and seed canola, plant size had a strong positive effect on percent pod set and seeds per pod, but did not increase seed size in commodity canola (Figure \ref{fig:allSeeds}d,e,f).
 Pod set in seed canola decreased with distance away from the field edge and LCB shelters, and was also lower at the centre of the female bay (independent of visitation and pollen deposition).
 This distance effect was not seen in commodity canola, suggesting a more long-term pollen limitation effect in seed canola that was not captured by our snapshot of pollen and visitation.
-Plant density also had a positive direct effect on seed size in both crops; this likely indicates field areas with better microclimate or soil resources rather than density effects \emph{per se}, as plants at edges of the field or in ``field holes" are typically both smaller and less dense.
+Plant density also had a positive direct effect on seed size in both crops; this likely indicates field areas with better microclimate or soil resources rather than density effects \emph{per se}, as plants at the edges of the field or in ``field holes" are typically both smaller and less dense.
 Finally, pod set also had a strong negative influence on flowers per plant in both crop types, indicating that high pod set suppresses future flower production.
@@
 HB visitation had little direct influence on pollen deposition in either crop type, while LCB visitation had a positive effect on pollen deposition in seed canola.
-We found that commodity canola production is largely limited by plant size, while seed canola production is limited by both pollen and plant size.
-Finally, our simulation results from the path analyses confirmed this, and showed the strong influence of LCB visitation on seed size and yield.
+We found that seed and pod production in commodity canola is largely limited by plant size, while seed canola is limited by both pollen and plant size; our simulation results from the path analyses further confirmed this, showing the strong influence of LCB visitation on seed size and yield.
 These results provide more mechanistic information on the value of pollination services in commodity and seed canola crops, and show how a statistical-mechanistic model of seed production provides richer insight into the process of seed production than linear models alone.
@@
 Lower HB visitation may have been caused by lower nectar and pollen resources, as areas close to leafcutter shelters can become depleted in nectar and pollen \citep{currie1997}.
-HBs also suffer from direct interference by LCBs near to their shelters; during the study we observed LCBs directly harassing HBs during the plot-level observations, attacking HBs both on the flowers and in the air (also seen by \citealp{batra1978} and \citealp{waytesMsc}).
+HBs also suffer from direct interference by LCBs near to their shelters; during the study we observed LCBs directly harassing HBs during the plot-level observations, attacking HBs both on the flowers and in the air (also seen by \citealp{batra1978} and \citealp{waytes2022}).
 HB visitation and foraging behaviour varied strongly between the edge and centre of the female bays in seed fields, while there was little difference between LCB visitation rates.
@@
 Very few HBs in the female bay were pollen foragers (1.4\%, see Table \ref{tab:sideWorking}), meaning that foragers who have recently come into contact with pollen are rare.
-Both \citet{waytesMsc} and \citet{gaffney2019} showed that HBs exhibit floral fidelity during foraging trips, with minimal crossing between male and female bays ($\sim$5\% of observations, \citealp{waytesMsc}), limiting pollen transfer between the male and female flowers.
+Both \citet{waytes2022} and \citet{gaffney2019} showed that HBs exhibit floral fidelity during foraging trips, with minimal crossing between male and female bays ($\sim$5\% of observations, \citealp{waytes2022}), limiting pollen transfer between the male and female flowers.
 Side-working was a very common behaviour among HBs in commodity fields (65\% of the total visits from HBs during 2015 were side-working), as well as the male bays of seed fields (36\%), but not in the female bays (3\%, Table \ref{tab:sideWorking}).
@@
 \emph{Bulbul}).
-However, \citet{waytesMsc} used male-sterile flowers from seed canola fields and found that HB pollen foragers deposited far less outcrossed pollen than previously reported ($\sim$ 2 grains per visit), suggesting that much of the pollen deposited on commodity canola stigmas may be self-pollen.
+However, \citet{waytes2022} used male-sterile flowers from seed canola fields and found that HB pollen foragers deposited far less outcrossed pollen than previously reported ($\sim$ 2 grains per visit), suggesting that much of the pollen deposited on commodity canola stigmas may be self-pollen.
 Because the overall pollen deposition rates found in this study were high, HB visitation seems to have made little difference in the amount of self-pollination, as large amounts of pollen were present on commodity canola stigmas even at the centre of unstocked fields.
@@
 %SH: DOING A BACK-OF-ENVELOPE CALC: 0.23 VISITS/HR X 2 GRAINS/VISIT X 12 HR X 3 DAYS = 5-6 GRAINS PER DAY, LESS THAN 1% OF STIGMA LOAD
-% This runs contrary to other studies in commodity canola (\citealp{sabbahi2005}, but see \citealp{garibaldi2013} and \citealp{waytesMsc}), so why did
+% This runs contrary to other studies in commodity canola (\citealp{sabbahi2005}, but see \citealp{garibaldi2013} and \citealp{waytes2022}), so why did
 
@@
 HBs in seed fields tended to visit more in the centre of the female bay, even close to the edge of the field, yet pollen deposition was still about 40\% lower.
-LCBs switch between male and female flowers more frequently than HBs, travel further between flowers, transport more viable pollen, and tend not to side-work canola flowers \citep{soroka2001, parker2015, waytesMsc, brunet2019}, all of which may explain their higher pollination efficacy.
+LCBs switch between male and female flowers more frequently than HBs, travel further between flowers, transport more viable pollen, and tend not to side-work canola flowers \citep{soroka2001, parker2015, waytes2022, brunet2019}, all of which may explain their higher pollination efficacy.
 Pollen deposition in seed fields also decreased with distance from the edge of the field, and was lower in the centre of the female bays independent of visitation, suggesting lower pollen transfer per visit.
@@
 
-While we found that HBs have no direct effect on pollen deposition in either crop type, they may have an indirect positive effect caused by: a) increasing airborne pollen from male-fertile flowers \citet{pierre2010}, b) lowering nectar and pollen standing crop, causing LCBs to travel further \citep{pyke1978b, heinrich1979}, or c) lowering floral fidelity on higher-rewarding flowers in the male bays \citep{mesquida1978, waytesMsc,gaffney2019}.
+While we found that HBs have no direct effect on pollen deposition in either crop type, they may have an indirect positive effect caused by: a) increasing airborne pollen from male-fertile flowers \citep{pierre2010}, b) lowering nectar and pollen standing crop, causing LCBs to travel further \citep{pyke1978b, heinrich1979}, or c) lowering floral fidelity on higher-rewarding flowers in the male bays \citep{mesquida1978, waytes2022,gaffney2019}.
 A simple test of this might be to remove HB hives from a seed field (mid-season) and observe changes in LCB visitation before and after the removal.

### 2022-11-14 Manuscript/main.tex
Finished revisions from RC

@@
 
-\title{Bee visitation, pollination services, and plant yield in commodity and hybrid seed canola}
+\title{Bee visitation, pollination service, and plant yield in commodity and hybrid seed canola}
 \author{Samuel V. J. Robinson$^1$\footnote{Corresponding author: samuel.robinson@ucalgary.ca}, Ralph V. Cartar$^1$,\\Stephen F. Pernal$^2$, Riley Waytes$^3$, Shelley E. Hoover$^4$}
@@
 \begin{abstract}
-Insect-mediated pollination of crops is an important service to agricultural production, but pollination management suffers from key knowledge gaps that hinder its greater utility. 
-While a solid theoretical and mechanistic framework for plant pollination exists, the pollination of agricultural crops is often treated as a ``black box”, without reference to the specific mechanisms underlying the processes of pollination and fruit production.
+Insect-mediated pollination of crops is an important service to agricultural production, as increased insect visitation can increase fruit production by increasing pollen deposition.
+Unfortunately, pollination is often treated as a ``black box", and pollination management suffers from key knowledge gaps that hinder its greater utility, particularly the specific mechanisms underlying the processes of visitation, pollination, and fruit production.
+% Ultimately this depends on the distance from the source of pollination, the efficacy of the pollinator, and the extent to which the plant is limited by nutrients or pollination.
 We present a causal model that links insect visitation to pollination to three separate components of yield, using field data from two types of canola (\emph{Brassica napus}) production systems. 
@@
 Leafcutting bee visitation in particular strongly increased pollen deposition in seed canola fields, whereas honey bee visitation did not. 
-This model serves as a step towards a dynamic model of pollination services, and points to the contextual importance of pollination services in seed canola production.
+This model serves as a step towards a dynamic model of pollination services, and highlights the relative importance of bee pollination in canola production.
 \end{abstract}
 
-%Journals to consider (Impact Factor):
-% Behavioural Ecology (2.8): no page limit specified - I think this would be the best at this point
-% Ecological Modeling (2.5): no page limit specified
-% Ecology Letters (8.6): max 5000 words, 6 figures/tables
-% Journal of Applied Ecology (5.8): 7500 words, including refs and caption
-% Journal of Animal Ecology (4.6): 8500 words, including refs and captions
-% Oikos (3.4): no page limit specified
-% Oecologia (2.7): 10 printed pages (~35 submitted pages), 100 Euros per extra page
+% Journals to consider:
+% AEE
+% Agronomy Journal
 
@@
 
+%Comments from RC:
+% - Include rug plot in figures? (can't included "adjusted" data points, as this is impossible for GLMs)
+
 \section*{Introduction}
@@
 Pollination of these crops, however, is largely treated as a single step, while in reality there are many links in the chain of events that result in fruit production.
-Visitation of flowers by animals (typically bees or other insects) can increase the deposition of pollen onto the stigma of the flower, but in order for fruit set to occur, this must be followed by fertilization of the ovules, and maturation of fruit \citep{erbar2003, goldberg1994}.
+Visitation of flowers by animals (typically bees or other insects) can increase the deposition of pollen onto the stigma of the flower, but in order for fruit set to occur this must be preceded by gathering plant resources via vegetative growth, and followed by fertilization of the ovules and maturation of fruit \citep{erbar2003, goldberg1994}.
 Each step has many other underlying constituent components (\textit{e.g.} stigma receptivity, pollen tube growth, ovule abortion), but even at this coarse level of approximation, most studies of agricultural pollination fail to account for important underlying processes.
@@
 
-Pollinator visitation is not uniform within fields: visitation rates typically decline with distance away from the pollinators' nest sites \citep{Ricketts2008}.
-Smaller bees fly shorter distances than larger bees \citep{greenleaf2007,zurbuchen2010}, so their presence at the centre of large fields can be limited \citep{isaacs2010}. 
+Pollinator visitation is not uniform within fields of insect-pollinated crops: visitation rates typically decline with distance away from the pollinators' nest sites \citep{Ricketts2008}.
+Smaller bees fly shorter distances than larger bees \citep{greenleaf2007,zurbuchen2010}, so their abundance at the centre of large fields can be low \citep{isaacs2010}. 
 Hence, managing the location and density of pollinators is important for optimal yield of pollinator-dependent crops \citep{fries1983,cresswell2004b}.
@@
 Competition for floral resources can occur between different species of foragers, but they can spatially or temporally separate their foraging to reduce competition (\citealp{schaffer1979,thomson1987}, but see \citealp{steffan2000}), such as switching between floral morphs more often, or visiting less frequently \citep{heinrich1979, greenleaf2006}.
-Thus, variation in visitation can be driven by distance, competition with other foragers, or floral specialization, as well as plant traits such as nectar production and flower size; however, this spatial variation is seldom considered, as commercial pollinators are often treated as a single agricultural ``input" (akin to fertilizer).
+Thus, variation in visitation can be driven by distance, competition with other foragers, or floral specialization, as well as plant traits such as nectar production and flower density; however, this spatial variation is seldom considered, as commercial pollinators are often treated as a single agricultural ``input" (akin to fertilizer).
 % Much of the worldwide agricultural demand for insect pollination is accomplished by the European honey bee, (\textit{Apis mellifera} L., hereafter ``honey bee") because of its large colony size, ease of transport, and ease of breeding (\citealp{winston1991}, but see also \citealp{winfree2008}).
@@
 
-Seed production can be limited by plant resources as well as pollen, meaning that the benefits of insect pollination depend on the resources available to the plant \citep{stephenson1981, marini2015, tamburini2017, tamburini2019}.
+Seed production can be limited by plant resources as well as pollen; therefore, the benefits of insect pollination depend on the resources available to the plant \citep{stephenson1981, marini2015, tamburini2017, tamburini2019}.
 Pollination can enhance fruit production in flowering plants by increasing either the quantity or quality of pollen deposited on the stigma \citep{stephenson1981, burd1994, aizen2007}.
 Many flowering plant species are capable of self-pollination, but can produce more fruit or seeds from outcrossed pollen \citep{knight2005}.
-However, the returns from this extra pollen deposition are diminishing \citep{plowright1981}, with very high numbers of pollen grains causing decreasing improvements in fruit production \citep{ashman2004, harder2016}.
+However, the returns from this extra pollen deposition are diminishing: very high numbers of pollen grains cause decreasing improvement in fruit production \citep{plowright1981,ashman2004, harder2016}.
 % Not all animal visitors are equal from a flowering plant's perspective: large-bodied insects can deposit more pollen per visit on the stigma of the flower \citep{sahli2007}, but some visitors may steal nectar, groom pollen between visits, or travel mainly between flowers on the same plant \citep{thomson1986, herrera1987}, reducing their utility to the plant.
@@
 Hybrid \emph{commodity canola} (used for oil and meal production) is the offspring of two parental \emph{seed canola} breeding lines, a male-sterile ``female" and a hermaphroditic ``male" line \citep{westcott2001,steffan2003,clay2009}.
-Seed canola production therefore requires a large number of pollinators to ensure pollen transfer from the male to the female line (seeds from the male line are not harvested), but there are few studies that examine pollination in these seed production systems (but see \citealp{mesquida1981, mesquida1991}).
-Bee pollination may also increase the yield of commodity canola \citep{morandin2005, rader_phd, bommarco2012, bartomeus2015,perrot2018}, but this is unclear, as many key studies suffer from either a lack of realistic context, have a number of potential confounding variables, or infer plant-level outcomes from flower-level treatments (reviewed by \citealt{ouvrard2019}).
-Greenhouse experiments typically involve unrealistically high levels of pollination, nutrient availability, and water, all of which can interact with yield \citep{bartomeus2015,marini2015}.
+Seed canola production therefore requires a large number of pollinators to ensure pollen transfer from the male to the female line (seeds from the male line are not harvested), but not all species of visiting insects are equally effective at pollen deposition, and few studies examine pollination in these seed production systems \citep{mesquida1981, mesquida1991, waytes2022}.
+Bee pollination may also increase the yield of commodity canola \citep{morandin2005, rader_phd, bommarco2012, bartomeus2015,perrot2018}, but this is unclear, as many key studies suffer from either a lack of realistic context, have a number of potential confounding variables, or infer plant-level outcomes from flower-level treatments that do not account for within-plant allocation of resources (reviewed by \citealt{ouvrard2019}).
+Greenhouse experiments typically involve unrealistically high levels of pollination, nutrient availability, and water, all of which can interact to affect yield \citep{bartomeus2015,marini2015}.
 Field studies often relate yield to indirect measures of pollination services, such as species richness or distance from sources of potential pollinators, or do not examine production at the plant level \citep{morandin2005, Ricketts2008}.
 These proxies provide limited information about how plants dynamically respond to pollen exclusion or addition (but see \citealp{sabbahi2005}).
-Net- or cage-treatments exclude insect visitation from certain plants or flowers, but can alter wind pollination, humidity, light, or pest pressure \citep{olsson1960, neal2004, jauker2008}.
+Net- or cage-treatments exclude insect visitation from certain plants or flowers, but can cause unrealistic yields by altering wind pollination, humidity, light, or pest densities \citep{olsson1960, neal2004, jauker2008}.
 All of these methods give an incomplete picture of how pollination relates to yield in canola crops \citep{ouvrard2019}, and obscure estimates of pollinator value in a globally valuable crop species \citep{melathopoulos2015}.
@@
 In this study, we examine how distance influences managed bee visitation, which in turn influences pollen deposition and seed yield, using commodity and seed canola crops in Alberta, Canada.
-Using both commodity and seed canola provides an opportunity to compare two plant varieties that differ strongly in their pollination requirements, using a similar type of structural model, while accounting for agricultural differences between varieties.
-We expected that bee visitation would decrease with distance from each species' hive or shelter, and that lower visitation would result in lower pollen deposition.
-We also expected that higher pollination would increase seed production in commodity canola crops, but that the magnitude of the increase would be higher in seed canola, and that plant size (a proxy for plant resources) would similarly increase seed production.
+Using both commodity and seed canola provides an opportunity to compare two plant varieties that differ strongly in their pollination requirements, while accounting for agricultural differences between varieties.
+We expected that bee visitation would decrease with distance from each species' hive or shelter, that lower visitation would result in lower pollen deposition, and that species may differ in their pollination ability.
+We also expected that higher pollination would increase seed production in canola crops, but would have the greatest effect in seed canola, and that plant size (a proxy for resource availability) would similarly increase seed production.
 This study assesses the strength of the connections between visitation, pollination, and yield, in a globally important crop species, and identifies the relative importance of bee pollination for seed production, using in-field data from two distinct cropping systems.
@@
 During 2015 and 2016, we also surveyed 35 hybrid seed canola fields (15 in 2015, 20 in 2016) near Lethbridge, Alberta, from June through August of each year, all of which had central-pivot irrigation, and were stocked with honey bee hives at a rate of 3.6 hives/ha (apiaries stationed in the corners of fields).
-In seed fields, bays of hermaphroditic (herafter ``male") and female plants are typically planted in 1- and 6-m wide bays, respectively. 
-Seed fields were also stocked with shelters (1.3 - 2.6 shelters/ha, Figure \ref{fig:seedfieldPhoto}) containing alfalfa leafcutter bee cocoons (\textit{Megachile rotundata} F., hereafter LCB) at a rate of 50-100,000 coocoons/ha.
+In seed fields, bays of hermaphroditic (hereafter ``male") and female plants are typically planted in 1- and 6-m wide linear strips (``bays"), respectively. 
+Seed fields were stocked with shelters (1.3 - 2.6 shelters/ha, Figure \ref{fig:seedfieldPhoto}) containing alfalfa leafcutter bee cocoons (\textit{Megachile rotundata} F., hereafter LCB) at a density of 50-100,000 cocoons/ha.
 Both HBs and LCBs are managed pollinators that are not native to Alberta, and are uncommon outside of managed pollination systems and honey production yards, so we assumed that the hives and shelters were the sole sources of visiting bees in the observed fields.
@@
 To assess pollen deposition, we collected stigmas from five random flowers at each female plot, mounted them in fuchsin gel \citep{beattie1971} on depression slides, and counted the pollen on each stigma using a Leica\texttrademark DME 13595 light microscope under 100x magnification (1294 commodity and 1050 seed canola stigmas).
-At the end of the growing season, we collected three plants from the same female plot and recorded the plant density per m$^2$ (789 commodity canola plants, 582 seed canola plants).
-After drying the plants, we weighed each plant, counted mature pods to estimate pod set, and counted the number of flower pedicels to estimate total flower production. % at 50$^\circ$C
+At the end of the growing season, we collected three plants from the same female plot (789 commodity canola plants, 582 seed canola plants total) and recorded plant density per m$^2$.
+We dryed and weighed each plant, counted mature pods to estimate pod set, and counted flower pedicels to estimate total flower production. % at 50$^\circ$C
 We estimated seed size and seeds per pod by averaging the seed count and weight from five pods on each plant.
-Finally, we threshed all the pods for each plant by hand, winnowed them using an air separator, and weighed the total mass of cleaned seeds (hereafter ``yield").
+Finally, we threshed all the pods for each plant by hand, winnowed them using an air separator, and weighed the total mass of cleaned seeds (hereafter ``plant yield").
 % (3872 commodity canola pods, 2885 seed canola pods)
@@
 SEMs provide a framework for empirical analysis of complex systems, as they allow causal relationships to be formally tested, can provide insight into alternative mechanisms, and are flexible in their assumptions \citep{shipley2009,clough2012, grace2012}.
-SEMs represent an intermediate class of statistical models, occupying a space somewhere between linear regression (or machine learning) models and dynamic linear models, making them ideal for generating and testing relationships between large sets of variables \citep{grace2006, kline2013}.
-Starting with a simple model (visitation $\rightarrow$ pollen deposition $\rightarrow$ fruit production $\leftarrow$ plant resources), we built a detailed model relating visitation to pollination to seed yield within a causal framework (Figure \ref{fig:allSEM}).
-We also ran a linear model outside of each SEM to predict yield (g per plant) as a function of the seed size, seeds per pod, and pods per plant (see Table \ref{tab:totalYieldCoefs}).
-After the models were fit and validated, we simulated seed size and yield at varying distances from pollinators, using the coefficients from each model to integrate the effect of pollination on yield across all sub-models (while holding plant density constant).
+% SEMs represent an intermediate class of statistical models, occupying a space somewhere between linear regression (or machine learning) models and dynamic linear models, making them ideal for generating and testing relationships between large sets of variables \citep{grace2006, kline2013}.
+Starting with a simple model (visitation $\rightarrow$ pollen deposition $\rightarrow$ fruit production $\leftarrow$ plant resources), we built a detailed model relating visitation to pollination to seed and pod production within a causal framework (Figure \ref{fig:allSEM}).
+We also ran a linear model outside of each SEM to predict plant yield (g per plant) as a function of the seed size, seeds per pod, and pods per plant (see Table \ref{tab:totalYieldCoefs}); this can be converted into \emph{total yield} for a given area (t per ha) by multiplying plant yield by plant density.
+After the models were fit and validated, we simulated seed size and total yield at varying distances from pollinators, using the coefficients from each model to integrate the effect of pollination on total yield across all sub-models.
 % These SEMs let us model how visitation ultimately influences seed yield, while controlling for other confounding factors (e.g. distance into field, measurements taken at different fields).
@@
 GLMMs can model processes that occur at different levels; for example, we modeled seed size at the plant level, and pollen deposition at the flower level.
-Random intercepts were used to model variance at the field and plot level, but plot-level variance terms had poor traces and low effective sample sizes, indicating low plot-level variance; therefore, we omitted plot-level random effects for all models (except for pollen count and pod set in seed fields, see Table \ref{tab:seedCoefs}).
-Visitation models used $log$(time) as an ``offset" variable to account for differences in observation times.
+Random intercepts were used to model variance at the field and plot level, but plot-level variance terms had poor traces and low effective sample sizes, indicating low plot-level variance or insufficient sampling; therefore, we omitted plot-level random effects for all models (except for pollen count and pod set in seed fields, see Table \ref{tab:seedCoefs}).
+Visitation models used $log$(observation length) as an ``offset" variable to account for differences in observation lengths.
 We observed LCBs directly harassing HBs during the plot-level observations, attacking HBs both on the flowers and in the air (also seen by \citealp{batra1978} and \citealp{waytes2022}), but HBs were never the aggressor in these interactions, so we treated LCB visitation as a potential cause of HB visitation (Figure \ref{fig:allSEM}).
-Pod set can suppress future vegetative growth and flower production \citep{stephenson1981}, but SEMs do not allow for causal loops \citep{grace2012}, so we included a path from pod set to flower production as the closest approximation of this process.
+Pod set can suppress future vegetative growth and flower production \citep{stephenson1981}, but SEMs do not allow for causal loops \citep{grace2012}, so we included a path from pod set to flower production to approximate this process.
 The direction of the path could be reversed, implying that large flower production reduces the proportion of pod set, but we considered only the first scenario, as \citet{sabbahi2006} showed that low pod set increases flower production.
@@
 \subsection*{Path analyses}
-The path analyses revealed that plant size and pollen deposition were the main drivers of yield in seed canola, while plant size was the main driver in commodity canola (see Figure \ref{fig:allSEM} for paths and effect sizes).
+The path analyses revealed that plant size and pollen deposition were the main drivers of seed and pod production in seed canola, while plant size was the main driver in commodity canola (see Figure \ref{fig:allSEM} for paths and effect sizes).
 LCB visitation strongly increased pollen deposition in seed canola, but there was no strong effect of HB visitation in either seed or commodity canola.
 Plant size increased with distance from the edge of the field in both crops, as well as plant density in seed fields.
-Plant size strongly increased the number of flowers per plant in both crops, and there were strong negative paths from pods per plant to flowers per plant, indicating that high flower survival suppressed flower production in both crops.
+Plant size strongly increased the number of flowers per plant in both crops, and pods per plant strongly reduced to flowers per plant, indicating that high flower survival suppressed flower production in both crops.
 Plant size increased pod set and seeds per pod in both crop types, and also increased seed size in seed canola plants.
@@
 Unsurprisingly (given the higher stocking rate of 160 hives per field), HB visitation was much higher in seed canola fields, and decreased from 96.4 visits/hr at edge to 85.7 visits/hr at the centre of the field (Figure \ref{fig:allVisits}a).
-HB visitation was also much lower near LCB shelters, dropping from 81 visits/hr at 20 m to 31 at 2 m (Figure \ref{fig:allVisits}b), likely due to competition or aggression from LCBs.
+HB visitation was also much lower near LCB shelters, dropping from 81 visits/hr at 20 m to 31 at 2 m (Figure \ref{fig:allVisits}b), likely due to competition or aggression from LCBs; the direct effect of LCB visitation on HB visitation was weak (p = 0.73, after accounting for LCB distance effect).
 
@@
     \includegraphics[width=\textwidth,keepaspectratio=true]{../Figures/allVisits.png}
-    \caption{Effect of distance from a) honey bee apiaries, b) leafcutter shelters, and c) female bay position on visitation rates.
+    \caption{Partial effect of distance from a) honey bee apiaries (at edge of the field), b) leafcutter shelters, and c) female bay position on visitation rates, with shaded regions and line ranges showing 95\% CIs.
 Commodity fields are shown at a stocking rate of 40 hives (black line), while stocking rates are at 160 hives in seed fields (yellow line).}
@@
 
-LCB visitation increased pollen deposition in seed canola fields, but honey bees did not increase pollen deposition in commodity or seed canola fields (Figure \ref{fig:allPollen}a).
+LCB visitation increased pollen deposition in seed canola, but honey bees did not increase pollen deposition in commodity or seed canola (Figure \ref{fig:allPollen}a).
 Pollen deposition on stigmas was high in commodity canola (mean: 293 grains/stigma, SD: 385, range: 0--3981), but honey bee visitation had no effect.
@@
     \includegraphics[width=\textwidth,keepaspectratio=true]{../Figures/allPollen.png}
-    \caption{Effect of a) visitation rate, b) distance from apiary (HB) or shelter (LCB), and c) female bay position on pollen deposition.}
+    \caption{Partial effect of a) visitation rate, b) distance from apiary (HB) or shelter (LCB), and c) female bay position on pollen deposition, with shaded regions and line ranges showing 95\% CIs.}
     \label{fig:allPollen}
@@
     \includegraphics[width=\textwidth,keepaspectratio=true]{../Figures/allSeeds.png}
-    \caption{Marginal effects of pollen deposition (top row) and plant size (bottom row) on flower survival, seeds per pod, and seed size.}
+    \caption{Partial effect of pollen deposition (top row) and plant size (bottom row) on flower survival, seeds per pod, and seed size, with shaded regions showing 95\% CIs.}
     \label{fig:allSeeds}
@@
 In contrast, commodity canola also produced more seeds per pod than seed canola plants (mean: 23 vs. 16), but seed size was lower in commodity canola than seed canola (2.74 vs. 3.43 mg/seed). 
-Finally, commodity plants were also lower-yielding than seed canola plants (mean: 6.8 vs.
+Finally, commodity plants had lower plant yields than seed canola plants (mean: 6.8 vs.
 9.5 g seed per plant), but had a lower harvest index (grams seeds per gram of vegetative biomass) than seed canola plants (0.38 vs.
@@
 
-Our path analysis simulations further confirmed the results of the analysis: HB visitation had little effect on yield in either crop type, but LCB visitation improved yield in seed crops.
-The simulations showed no large effect of HB stocking on seed size or total yield in commodity fields (Figure \ref{fig:allYield}a and b, respectively), aside from the effect associated with distance from the edge of the field.
+Our path analysis simulations further confirmed the results of the analysis: HB visitation had little effect on total yield in either crop type, but LCB visitation improved total yield in seed crops.
+The simulations showed no large effect of HB stocking on seed size or total yield in commodity fields (Figure \ref{fig:allYield}a and b, respectively), aside from the effect of distance from the edge of the field.
 Similarly, the simulations for seed fields showed a small increase in seed size and total yield with distance from the HB hives at the field edges, but the effect of distance from the leafcutter shelters was much more dramatic (compare the spacing of isolines along the x-axis and y-axis in Figures \ref{fig:allYield}c and d).
 Simulations run separately for the edge and centre of the female bay revealed that not only are total seed size and total yield lower at the bay centre, but that the effect of HB distance is effectively \emph{nil} at the bay centre (yield isolines are essentially horizontal in bay centre, and slightly tilted at the bay edge, Figure \ref{fig:allYield}d and f).
-Interestingly, the simulations also showed evidence of nonlinear behaviour occurring in the centre of seed field bays, where a local minima in yield appears at approximately 25 m away from HB hives and 45 m away from LCB shelters (Figure \ref{fig:allYield})f), likely because of an interaction between the components of yield (seeds per pod, pods per plant, and weight per seed).
+Interestingly, the simulations also showed evidence of nonlinear behaviour occurring in the centre of seed field bays, where a local minima in total yield appears at approximately 25 m away from HB hives and 45 m away from LCB shelters (Figure \ref{fig:allYield})f), likely because of an interaction between the components of yield (seeds per pod, pods per plant, and weight per seed).
 
@@
     \includegraphics[width=\textwidth,keepaspectratio=true]{../Figures/allYield.png}
-    \caption{Effect of honey bee distance and leafcutter distance on seed size (mg/seed, first column) and total yield (tonnes/hectare, second column), using coefficients from paths for simulation, while holding plant density constant at its mean value.
+    \caption{Simulated effect of honey bee distance and leafcutter distance on seed size (mg/seed, first column) and total yield (tonnes/hectare, second column), using coefficients from paths for simulation.
 Shaded areas shown in a \& b are 95\% quantiles for the simulations.
@@
 
-We examined how bee visitation contributes to pollen deposition and seed yield in two different canola crops, and showed a strong link between visitation and yield in seed canola, but not in commodity canola.
+% We examined how bee visitation contributes to pollen deposition and seed yield in two different canola crops, and
+Our results showed a strong link between visitation and yield in seed canola, but not in commodity canola.
 HB and LCB visitation decreased with distance from their respective hive or shelter, but unexpectedly, LCBs visited more frequently at the edge of the crop.
@@
 We found that seed and pod production in commodity canola is largely limited by plant size, while seed canola is limited by both pollen and plant size; our simulation results from the path analyses further confirmed this, showing the strong influence of LCB visitation on seed size and yield.
-These results provide more mechanistic information on the value of pollination services in commodity and seed canola crops, and show how a statistical-mechanistic model of seed production provides richer insight into the process of seed production than linear models alone.
+Our results provide more mechanistic information on the value of pollination services in commodity and seed canola crops, and show how a statistical-mechanistic model of seed production provides richer insight into the process of seed production than linear models alone.
 
@@
 0.6 hives/ha).
-Since HBs travel to the crop from their hive outside the edge of the field, this decline was not surprising \citep{robinson2022}, but we did not expect a similar decrease in LCB visitation with distance into the field, as their shelters are located \textit{within} the field.
+Since HBs travel to the crop from their hive outside the edge of the field \citep{robinson2022}, this decline was not surprising, but we did not expect a similar decrease in LCB visitation with distance into the field, as their shelters are located \textit{within} the field.
 This decrease with distance into the field may have been caused by LCBs migrating from shelters at the centre of the field to the edge \citep{goerzen1995}, as female LCBs are central-place foragers and tend to not forage far from their nests \citep{peterson2005,pitts2011, brunet2019}.
@@
 The foragers who were side-working tended to not switch to top-working (personal observation), so this is likely a consistent individual behaviour (at least in experienced foragers).
-Taken together, these pieces of evidence suggests that HBs have limited opportunities for pollen transfer in both commodity and seed fields, as they commonly engage in side-working behaviour in both field types, and pollen foragers typically avoid female bays in seed canola fields.
+Taken together, these pieces of evidence suggests that HBs provide limited pollen transfer in both commodity and seed fields, as they commonly engage in side-working behaviour in both field types, and pollen foragers typically avoid female bays in seed canola fields.
 
@@
 %Pollen deposition in commodity fields
-HB visitation did not increase pollen deposition in commodity canola fields compared to unstocked fields, meaning that self-pollination are the likely agents of pollen transfer (\emph{Brassica} flowers are not aligned for dispersal and deposition from the wind, so cross-pollination likely occurs mainly via insects \citep{mesquida1982,cresswell2004}).
+HB visitation did not increase pollen deposition in commodity canola fields compared to unstocked fields, meaning that self-pollination is the likely agent of pollen transfer (\emph{Brassica} flowers are not aligned for dispersal and deposition from the wind, so cross-pollination likely occurs mainly via insects \citep{mesquida1982,cresswell2004}).
 However, wind-induced self-pollination (plant shaking) can increase yield in \textit{Brassica} \citep{williams1986, mesquida1988c}, and fields without bee pollination have outcrossing rates of about 20\% within the field \citep{rakow1987,becker1992}.
@@
 \emph{Bulbul}).
-However, \citet{waytes2022} used male-sterile flowers from seed canola fields and found that HB pollen foragers deposited far less outcrossed pollen than previously reported ($\sim$ 2 grains per visit), suggesting that much of the pollen deposited on commodity canola stigmas may be self-pollen.
+However, \citet{waytes2022} used male-sterile flowers to estimate pollen deposition and found that HB pollen foragers deposited far less outcrossed pollen than previously reported ($\sim$ 2 grains per visit), suggesting that much of the pollen deposited on commodity canola stigmas may be self-pollen.
 Because the overall pollen deposition rates found in this study were high, HB visitation seems to have made little difference in the amount of self-pollination, as large amounts of pollen were present on commodity canola stigmas even at the centre of unstocked fields.

### 2022-11-14 partial plots.R

@@ -754,7 +754,7 @@ xaxis <- 'Distance from HB hives (m)'
 # summary(exp(commData$plDens_obs))
 
 datList <- expand.grid(hbeeDist=exp(seq(log(1),log(400),length=30)),
-                       plDens=48.5, #plSize=18,
+                       # plDens=48.5, #plSize=18,
                        numHives=c(0,40)
 ) %>% lapply(.,function(x) x)
 
@@ -774,13 +774,15 @@ d_mean <- genCommYield(datList) %>% as.data.frame() %>%
 quantRanges <- c(0.025,0.975) #Ranges of quantiles to use
 
 #Needed for placing annotations at the same place on each plot
-d1 <- d %>% mutate(numHives=factor(numHives)) %>% group_by(hbeeDist,numHives) %>% 
-  summarize(med=median(seedWeight),lwr=quantile(seedWeight,quantRanges[1]),upr=quantile(seedWeight,quantRanges[2]))
+d1 <- d %>% mutate(numHives=factor(numHives)) %>% 
+  group_by(hbeeDist,numHives) %>% 
+  summarize(med=median(seedWeight),lwr=quantile(seedWeight,quantRanges[1]),
+            upr=quantile(seedWeight,quantRanges[2]))
    
 (p1 <- d1 %>% ggplot(aes(x=hbeeDist,y=med,group=numHives))+
   geom_ribbon(aes(ymax=upr,ymin=lwr),alpha=0.3)+
   geom_line(data=d_mean,aes(x=hbeeDist,y=seedWeight))+
-  annotate('text',x=c(300,300),y=c(2.825,2.75),label=c('40 hives','0 hives'))+
+  annotate('text',x=c(300,300),y=c(2.81,2.72),label=c('40 hives','0 hives'))+
   annotate('label',x=300,y=min(d1$lwr)+(max(d1$upr)-min(d1$lwr))*0.2,label='Commodity fields\nSeed size (mg/seed)')+
   labs(x=xaxis,y='Seed size (mg/seed)'))
 
@@ -790,7 +792,7 @@ d2 <-  d %>% mutate(numHives=factor(numHives)) %>% group_by(hbeeDist,numHives) %
 (p2 <- d2 %>% ggplot(aes(x=hbeeDist,y=med,group=numHives))+
   geom_ribbon(aes(ymax=upr,ymin=lwr),alpha=0.3)+
   geom_line(data=d_mean,aes(x=hbeeDist,y=yield_tha))+
[…]

### 2023-01-19 Manuscript/main.tex
Worked on revisions

@@
 
-% Since the processes linking insect visitation to seed production has several intermediate steps, and is contingent on resource factors, we need a more complete model of crop yield that links plant-level responses to biological processes that occur at the plot and field level.
-% This work adds to the body of literature examining the resource context of pollination services \citep{haig1988} within cropping systems \citep{marini2015, tamburini2016, fijen2018, tamburini2019}, and identifies directions of future research in seed production systems.
-
-% Our five main hypotheses are outlined as follows:
-% \begin{enumerate} 
-%     \item Foraging honey bees and leafcutter bees are sensitive to distance due to cost of flight \citep{schmid1985}, and deplete floral resources with visitation.
-Therefore, insect visitation should decline with distance from their hive or shelter to achieve equivalent rewards \citep{dukas1998, cresswell2000}.
-%     \item Visiting bees can deposit pollen on stigmas, so areas with high rates visitation should have more pollen deposition on stigmas than areas with low rates of visitation \citep{mesquida1988c, hoyle2007}, depending on foraging behaviour of the bee \citep{free1983}.
-%     % \item Plant size is limited by resources, which can be reduced by competition with neighbours, so areas with fewer plants per m$^2$ should have larger plants \citep{angadi2003}. %Not revelvant
-%     \item Seed production for a given plant is limited by the resources it is able to sequester.
-Therefore, large plants should have more resources at their disposal, and should produce more fruit per plant and produce a higher number of larger seeds per fruit \citep{galen1985, lawrence1993, marini2015}.
-%     \item Seed production in resource-rich plants is also limited by pollination.
-Plants in areas with high pollen deposition should have a higher proportion of successful flowers \citep{sabbahi2005}, and a higher number of seeds per pod \citep{morandin2005}.
-% \end{enumerate}
-
 \section*{Methods}
@@
 Commodity canola fields were selected based on the proximity of honey bee apiaries and site access. 
-Colonies of Western honey bees (\emph{Apis mellifera} L., hereafter HB) were located at the corner or side of 28 of the 60 fields (stocking rates: 0.03 - 3.1 hives/ha) while 32 fields were unstocked.
+Colonies of Western honey bees (\emph{Apis mellifera} L., hereafter HB) were located at the corner or side of 28 of the 60 fields (stocking rates: 0.03 - 3.1 hives/ha while 32 fields were unstocked.
 %range: 0.03 - 3.1 hives/ha, mean: 0.6, sd: 0.58 Apiaries were stationed at the edges of fields, often near to shrubs or tree-lines to act as a wind break.
+Stocking rates were calculated using the area of the focal field, but since other canola fields (and wild flowering plants) in were in different stages of bloom around the focal field, the \emph{effective} stocking rates were likely lower.
 Central-pivot irrigation systems were present at 14 of the 31 fields near Lethbridge.
@@
 
-%Maps + climate graphs needed for publication
-During 2015 and 2016, we also surveyed 35 hybrid seed canola fields (15 in 2015, 20 in 2016) near Lethbridge, Alberta, from June through August of each year, all of which had central-pivot irrigation, and were stocked with honey bee hives at a rate of 3.6 hives/ha (apiaries stationed in the corners of fields).
+During 2015 and 2016, we also surveyed 35 hybrid seed canola fields (15 in 2015, 20 in 2016) near Lethbridge, Alberta, from June through August of each year, all of which had central-pivot irrigation, and were stocked with HB hives at a rate of 2.5 hives/ha (160 hives per quarter section, apiaries stationed in the corners or sides of field).
 In seed fields, bays of hermaphroditic (hereafter ``male") and female plants are typically planted in 1- and 6-m wide linear strips (``bays"), respectively. 
@@
 
-% (1.3 or 2.6 shelters/ha).
-% at a rate of approximately 2 shelters/ha
-% Shelters used either ``standard" or ``double"  LCB stocking ($\approx$50,000 vs.
-100,000 cocoons/ha), and shelters were placed at either ``standard" or ``double" densities (1.3 vs.
-2.6 shelters/ha) in each field.
-% Double stocking rates were only used in fields with double shelter density, creating three combinations of LCB stocking: ``standard", ``double shelter", and ``double shelter and double stocking".
-%Woudick 5,6 = 64 shelters (single), Woudick 2 = 113 shelters (double + bees), Woudick 3 = 128 shelters Graham 1 = 135 shelters
-
-% We recorded air temperature and wind speed before beginning observations (Table \ref{tab:weather}).
-% \begin{table}[h]
-%     \centering
-%     \begin{tabular}{r|r|l|l|l|l}
-%          Year & Area & Nectar volume & Nectar \% & Temperature & Wind Speed \\ \hline
-%          2014 & Grande Prairie & 0.82 $\pm$ 0.035 & 56.1 $\pm$ 0.14 & 22.8 $\pm 0.9$ & 16.4 $\pm 2.0$  \\
-%          2014 & Lethbridge & 0.85 $\pm$ 0.033 & 58.4 $\pm$ 0.15 & 24.7 $\pm 0.8$ & 4.6 $\pm 0.7$ \\
-%          2015 & Grande Prairie & 0.63 $\pm$ 0.025 & 60.4 $\pm$ 0.22 & 21.7 $\pm 0.7$ & 26.7 $\pm 3.9$ \\
-%          2015 & Lethbridge & 0.40 $\pm$ 0.021 & 58.4 $\pm$ 0.18 & 27.4 $\pm 0.7$ & 11.7 $\pm 1.5$ \\
-%          2016 & Lethbridge & 0 & 0 & 23.5 $\pm 0.7$ & 6.2 $\pm 0.9$ \\
-%     \end{tabular}
-%     \caption{Nectar volume ($\mu$L), concentration (\%), air temperature (C) and wind speed (km/hr), averaged across all observations for each year and area.
-Nectar standing crop in seed canola was negligible in 2015 and 2016.}
-%     \label{tab:weather}
-% \end{table}
-
 In both field types, we established sets of plots at varying distances from the nesting sources of pollinators. 
-In commodity fields, 1 m$^2$ plots (271 total plots) were located at 5, 20, 100, and 500 m away from the field edge closest to the set of honey bee hives or potential sources of natural pollinating insects in unstocked fields (forests, shrublands, or grasslands).
+In commodity fields, 1 m$^2$ plots (271 total plots) were located at 5, 20, 100, and 500 m away from the field edge closest to the set of HB hives or potential sources of natural pollinating insects in unstocked fields (forests, shrublands, or grasslands).
 We observed very few wild bees in either field type (Table \ref{tab:propVisitors}), so these were excluded from the analysis.
-In seed fields, we established plots at 5, 20, 100 (250 m in 2016), and 400 m into the field along a transect from the nearest set of honey bee hives, using pairs of plots at the edge of adjacent male and female bays (Figure \ref{fig:seedfieldPlots}).
+In seed fields, we established plots at 5, 20, 100 (250 m in 2016), and 400 m into the field along a transect from the nearest set of HB hives, using pairs of plots at the edge of adjacent male and female bays (Figure \ref{fig:seedfieldPlots}).
 To examine within-bay variation in visitation, we established a plot at the centre of the female bay at the 5m and 400m plot in each field. 
@@
 % Mean air temperature was similar between years in Grande Prairie ($\approx$ 22$^\circ$C), but Lethbridge was warmer in 2015 (23 vs. 28$^\circ$C).
-%Plots were marked with coloured stakes driven into the soil to locate them later in the season. %Full paper should have a table of climate variables.
+% Plots were marked with coloured stakes driven into the soil to locate them later in the season. %Full paper should have a table of climate variables.
 
@@
 Random intercepts were used to model variance at the field and plot level, but plot-level variance terms had poor traces and low effective sample sizes, indicating low plot-level variance or insufficient sampling; therefore, we omitted plot-level random effects for all models (except for pollen count and pod set in seed fields, see Table \ref{tab:seedCoefs}).
-Visitation models used $log$(observation length) as an ``offset" variable to account for differences in observation lengths.
+All visitation models used $log$(observation length) as an ``offset" variable to account for differences in observation lengths.
+Commodity HB visitation models using stocking rate rather than number of hives fit the data equally well ($\Delta$AIC = 0.2) and did not change any other results; seed fields all had identical HB stocking rates, so this was not included as a covariate in seed HB visitation models.
 We observed LCBs directly harassing HBs during the plot-level observations, attacking HBs both on the flowers and in the air (also seen by \citealp{batra1978} and \citealp{waytes2022}), but HBs were never the aggressor in these interactions, so we treated LCB visitation as a potential cause of HB visitation (Figure \ref{fig:allSEM}).
@@
 The direction of the path could be reversed, implying that large flower production reduces the proportion of pod set, but we considered only the first scenario, as \citet{sabbahi2006} showed that low pod set increases flower production.
-Plant and pollen samples were not collected from male bays in seed fields, and there were no large differences in visitation rates for honey bees or LCBs (p = 0.32, 0.72, respectively) once other terms were included as covariates, so bay was excluded from further analysis.
+Plant and pollen samples were not collected from male bays in seed fields, and there were no large differences in visitation rates for HBs or LCBs (p = 0.32, 0.72, respectively) once other terms were included as covariates, so bay was excluded from further analysis.
 See Equation sets S1 and S2 for GLMM specifications and Table \ref{tab:dataSummary} for a summary of the SEM variables.
 % Random intercepts were used to model variance between fields, within-field (pollen, flower survival, seed count \& size), and within-plot (seed count \& size).
-% Continuous responses were modeled using log-normal (plant density, plant size), square-root normal (flower density), and exponential-normal distributions (weight per seed), while counts were modeled as a negative-binomial (honey bee visits, pollen grains per stigma, flowers per plant, seeds per pod) or zero-inflated negative-binomial distribution (LCB visits) with a log-link function.
+% Continuous responses were modeled using log-normal (plant density, plant size), square-root normal (flower density), and exponential-normal distributions (weight per seed), while counts were modeled as a negative-binomial (HB visits, pollen grains per stigma, flowers per plant, seeds per pod) or zero-inflated negative-binomial distribution (LCB visits) with a log-link function.
 (Move to appendix)
@@
 % \begin{itemize}
-% 	\item Honey bee visitation depends on distance from their hive
-%     \item Pollen deposition depends on honey bee visitation
+% 	\item HB visitation depends on distance from their hive
+%     \item Pollen deposition depends on HB visitation
 %     \item Seeds per pod depends on pollen deposition
@@
 % \begin{itemize}
-% 	\item Honey bee visitation depends on distance from edge of field (proxy for distance from hives), bay position, bay type, and distance to leafcutter shelter
+% 	\item HB visitation depends on distance from edge of field (proxy for distance from hives), bay position, bay type, and distance to leafcutter shelter
 %     \item leafcutter bee visitation depends on distance from their shelter, bay position, and bay type
-%     \item Pollen deposition depends on honey bee and leafcutter visitation
+%     \item Pollen deposition depends on HB and leafcutter visitation
 %     \item Seeds per pod depends on pollen deposition
@@
 % HB visitation decreased with distance from the edge of the field in both commodity and seed canola, and increased with distance from LCB shelters; interestingly, LCB visitation also decreased with distance from the edge of the field in seed fields.
-Honey bee flower visitation (per plot) decreased with distance away from the edge of the field in both commodity and seed canola fields.
-In commodity fields, HB visitation decreased from 12 visits/hr per plot at the edge to 1.8 visits/hr at 400 m into the field (Figure \ref{fig:allVisits}a, apiary of 40 hives).
+HB flower visitation (per plot) decreased with distance away from the edge of the field in both commodity and seed canola fields.
+In commodity fields, HB visitation decreased from 12 visits/hr per plot at the edge to 1.8 visits/hr at 400 m into the field (Figure \ref{fig:allVisits}a, apiary of 40 hives, i.e.
+0.625 hives/ha in a 64 ha quarter-section).
 Lower stocking rates decreased HB visitation at the edge of the field to 7.4 visits/hr at 20 hives, while unstocked field edges had an average of 0.8 visits/hr.
@@
 
-LCB visitation increased pollen deposition in seed canola, but honey bees did not increase pollen deposition in commodity or seed canola (Figure \ref{fig:allPollen}a).
-Pollen deposition on stigmas was high in commodity canola (mean: 293 grains/stigma, SD: 385, range: 0--3981), but honey bee visitation had no effect.
+LCB visitation increased pollen deposition in seed canola, but HB visitation did not increase pollen deposition in commodity or seed canola (Figure \ref{fig:allPollen}a).
+Pollen deposition on stigmas was high in commodity canola (mean: 293 grains/stigma, SD: 385, range: 0--3981), but HB visitation had no effect.
 Pollen deposition declined weakly with distance from the edge of the field (p$=$0.09), but this only amounted to a 6\% average decrease (290 grains/stigma at the field edge vs.
@@
 In seed canola, pollen deposition was much lower overall (mean: 22 grains/stigma, SD: 43, range: 0--578), and decreased from 26.3 grains/stigma at the edge to 11.5 at the centre of the field (Figure \ref{fig:allPollen}b), independent of bee visitation.
-LCB visitation increased pollen deposition from 13 grains/stigma at 0 visits/hr to 25 pollen grains at 100 visits/hr (Figure \ref{fig:allPollen}a), but there was no effect of honey bee visitation (p$=$0.20), implying that most of the pollen deposition in seed fields is the result of LCB visitation.
+LCB visitation increased pollen deposition from 13 grains/stigma at 0 visits/hr to 25 pollen grains at 100 visits/hr (Figure \ref{fig:allPollen}a), but there was no effect of HB visitation (p$=$0.20), implying that most of the pollen deposition in seed fields is the result of LCB visitation.
 Pollen deposition also decreased from 15 grains/stigma at the edge of the female bay to 9 at the centre of the bay independent of visitation (Figure \ref{fig:allPollen}c), suggesting that bees crossing over into the male bays may deposit less pollen as they move towards the centre.% \citep{pinnisch1990}.%, who likely visit flowers at the edge of the bay first.
-% Flies were also common visitors in commodity fields (Table \ref{tab:propVisitors}), but had no effect on pollen deposition (p$=$0.577), so only honey bees and LCBs were considered as potential pollinators (other flower visitors were rare).
+% Flies were also common visitors in commodity fields (Table \ref{tab:propVisitors}), but had no effect on pollen deposition (p$=$0.577), so only HBs and LCBs were considered as potential pollinators (other flower visitors were rare).
 
@@
 Plant size had by far the strongest positive effect on the number of pods produced (see large plant paths in Figure \ref{fig:allSEM}), and there was evidence of pod set suppressing flower production.
-However, pollen deposition did not alter seed or pod production in commodity canola (Figure \ref{fig:allSeeds}a,b,c), nor was there a direct effect of honey bee visitation or distance from field edge, at least at the levels we observed.
+However, pollen deposition did not alter seed or pod production in commodity canola (Figure \ref{fig:allSeeds}a,b,c), nor was there a direct effect of HB visitation or distance from field edge, at least at the levels we observed.
 In both commodity and seed canola, plant size had a strong positive effect on percent pod set and seeds per pod, but did not increase seed size in commodity canola (Figure \ref{fig:allSeeds}d,e,f).
@@
 
-HB visitation in both field types declined with distance into the field, but overall visitation was much higher in seed fields than commodity fields, due to the higher HB stocking rate used in seed fields (3.6 vs.
+HB visitation in both field types declined with distance into the field, but overall visitation was much higher in seed fields than commodity fields, due to the higher HB stocking rate used in seed fields (mean: 2.5 vs.
 0.6 hives/ha).
@@
 Finally, it contextualizes the value of pollination alongside plant resources, showing that plant resources and pollen limit production in seed canola, while only plant resources limit production in commodity fields.
-Our unique SEM approach allowed us to formulate and test relationships within a causal framework, which we consider to be extremely valuable, and highly underused in agricultural studies.
-Our model serves as an approximation of a dynamic process, but could be built upon by using dynamic linear models \citep{iwasa2000, nord2011, saez2018} to examine how plants dynamically respond to changes in pollination.
+Our unique SEM approach serves as an approximation of a dynamic process, but could be extended with dynamic linear models \citep{iwasa2000, nord2011, saez2018} to examine how plants respond to changes in pollination over time.
 These would lend greater understanding to the process of hybrid seed production, and could be used to more accurately predict crop yields in novel scenarios.
@@
 
+\section{Acknowledgments}
+
+This work was supported by the Alberta Crop Industry Development Fund (#20014C001R), the Alfalfa Seed Commission Fund, the Canadian Bee Research Fund, and the Alberta Beekeepers Commission.
+We thank our tireless field assistants, Breannalee Beer, Zac Wagman, Chris Isaacs, Ian Johnson, Krista Fjordbotten, Jeff Kearns, Sam Knight, and Haley Shade. 
+We also thank Megan Abarmayan, Shahid Majid, Mohamed Ibrahim, Ashley Londeau, and Joseph Desmarais, for their additional help with processing plants and flower stigmas, and Lynae Ovinge for her support in the lab.
+Thanks to Ria van Giessen, Alfonso Parra, and Miki Miheguli at BASF for giving us access to their seed fields in 2015. 
+Finally, many thanks to the farmers who gave us access to their land for this study, in particular: Dave Hofer, Ron Lamb, Dave McKee, Gord and James Graham, and many others.
+
 \singlespacing

### 2023-01-19 Manuscript/manuscript_files/figures.tex
Worked on revisions

\documentclass[12pt]{article} % use larger type; default would be 10pt

\usepackage[utf8]{inputenc} % set input encoding (not needed with XeLaTeX)
\usepackage{geometry} % to change the page dimensions
 \geometry{margin=1in} 
\usepackage{graphicx} % support the \includegraphics command and options

\begin{document}

\section*{Figures}

Figure 1: Results of path analyses in commodity and seed fields. \emph{Field Edge Distance} refers to the distance to the edge of the field (and location of HB apiary) and \emph{Shelter Distance} refers to the distance to the nearest LCB shelter. The width of each arrow is proportional to the effect size of each component path (number also displayed), with black and red lines representing positive and negative effects, respectively. Transparent arrows show path coefficients whose 95\% CIs overlapped zero.

\vspace{0.5cm}

Figure 2: Partial effect of distance from a) honey bee apiaries (at edge of the field), b) leafcutter shelters, and c) female bay position on visitation rates, with shaded regions and line ranges showing 95\% CIs. Commodity fields are shown at a stocking rate of 40 hives (black line), while stocking rates are at 160 hives in seed fields (yellow line).

\vspace{0.5cm}

Figure 3: Partial effect of a) visitation rate, b) distance from apiary (HB) or shelter (LCB), and c) female bay position on pollen deposition, with shaded regions and line ranges showing 95\% CIs.

\vspace{0.5cm}

Figure 4: Partial effect of pollen deposition (top row) and plant size (bottom row) on flower survival, seeds per pod, and seed size, with shaded regions showing 95\% CIs.

\vspace{0.5cm}

Figure 5: Simulated effect of honey bee distance and leafcutter distance on seed size (mg/seed, first column) and total yield (tonnes/hectare, second column), using coefficients from paths for simulation. Shaded areas shown in a \& b are 95\% quantiles for the simulations. Lines on panels c - f are isolines of constant seed size (c, e) or yield (d, f).

\clearpage

\begin{figure}
    \centering
    \includegraphics[width=\textwidth,keepaspectratio=true]{allSEM.png}
\end{figure}

\begin{figure}
    \centering
    \includegraphics[width=\textwidth,keepaspectratio=true]{allVisits.png}
\end{figure}

\begin{figure}
    \centering
    \includegraphics[width=\textwidth,keepaspectratio=true]{allPollen.png}
\end{figure}

\begin{figure}
    \centering
    \includegraphics[width=\textwidth,keepaspectratio=true]{allSeeds.png}
\end{figure}

\begin{figure}
    \centering
    \includegraphics[width=\textwidth,keepaspectratio=true]{allYield.png}
    \label{fig:allYield}
\end{figure}

\end{document}

### 2023-01-19 Manuscript/manuscript_files/supplemental.tex
Worked on revisions

--- 2022-09-26 Manuscript/supplemental.tex
@@
-%%%%%%%%%% Merge with supplemental materials %%%%%%%%%%
+\documentclass[12pt]{article} % use larger type; default would be 10pt
+
+\usepackage[utf8]{inputenc} % set input encoding (not needed with XeLaTeX)
+\usepackage{geometry} % to change the page dimensions
+\geometry{margin=1in} % for example, change the margins to 2 inches all round
+\usepackage{graphicx} % support the \includegraphics command and options
+\usepackage{booktabs} % for much better looking tables
+\usepackage{array} % for better arrays (eg matrices) in maths
+\usepackage{paralist} % very flexible & customizable lists (eg. enumerate/itemize, etc.)
+\usepackage{verbatim} % adds environment for commenting out blocks of text & for better verbatim
+\usepackage{subfig} % make it possible to include more than one captioned figure/table in a single float
+\usepackage[round]{natbib} % Natural science bibliography package
+\usepackage{pdflscape} %Landscape pages
+\usepackage{amsmath} %Mathematics 
+\usepackage{hyperref} %URLs and Hyperlinks
+\hypersetup{hidelinks=true} %Turns off coloured links
+\usepackage{longtable} %Multi-page tables
+\usepackage{multirow} %Better tables
+\usepackage{marvosym} %Male/female/hermaphrodite symbols
+\usepackage{caption} %Add captions to non-floats
+\usepackage{calc} %Simple arithmetic for arguments
+\usepackage{ifthen} %Allows if-then statements
+\usepackage[breakable]{tcolorbox} %Allows boxes to be made, and allows boxes to be breakable
+\usepackage{capt-of} %Allows captions outside of float environments
+\usepackage{setspace} %Double/1.5 spacing
+\usepackage{multirow} %Multirow tables
+\usepackage{sectsty}
+\allsectionsfont{\sffamily\mdseries\upshape}
+
 %%%%%%%%%% Prefix a "S" to all equations, figures, tables and reset the counter %%%%%%%%%%
@@
 \setcounter{table}{0}
-%\setcounter{page}{1} 
 \makeatletter
@@
 \renewcommand{\citenumfont}[1]{S#1}
-%\pagenumbering{gobble}
 
-\clearpage
+\begin{document}
+
 \section*{Appendix A: Additional figures and tables}
@@
     \centering
-    \includegraphics[width=0.9\textwidth,keepaspectratio=true]{../Figures/FieldLocations.png}
+    \includegraphics[width=0.9\textwidth,keepaspectratio=true]{FieldLocations.png}
     \caption{Map of sampled fields, showing locations of 29 commodity canola fields (14 during 2014, 15 during 2015), and 35 seed canola fields (15 during 2015, 20 during 2016).
 Seed canola is grown only in southern Alberta, while commodity canola is grown across both the northern and southern regions.}
-    \label{fig:fieldMap}
 \end{figure}
@@
 The linear structure on the horizon is the central-pivot irrigation sprinkler.}
-    \label{fig:seedfieldPhoto}
 \end{figure}
@@
 Note: this figure shows a small section of a much larger circular field.}
-    \label{fig:seedfieldPlots}
 \end{figure}
@@
 \end{tabular}
-
-\label{tab:dataSummary}
 \end{table}
@@
     \end{tabular}
-    \label{tab:propVisitors}
 \end{table}
@@
 \end{tabular}
-\label{tab:sideWorking}
 \end{table}
@@
 \begin{longtable}{l|l|r|r|r|r|r|l|r|r}
-
 \caption{Summary of parameters for commodity canola models} \\
-
 \hline
@@
 \hline
-\label{tab:commCoefs}
 \end{longtable}
@@
 \hline
-\label{tab:seedCoefs}
 \end{longtable}
@@
 \end{table}
+
+\bibliographystyle{humanbio}
+\begin{thebibliography}{}
+
+\bibitem[\protect\astroncite{Free and Ferguson}{1983}]{free1983}
+Free, J.~B. and Ferguson, A.~W. 1983.
+\newblock Foraging behaviour of honeybees on oilseed rape.
+\newblock {\em Bee World}, 64(1):22--24.
+
+\bibitem[\protect\astroncite{Free and Williams}{1973}]{free1973}
+Free, J.~B. and Williams, I.~H. 1973.
+\newblock The foraging behaviour of honeybees (\emph{Apis mellifera} {L.}) on
+  brussels sprout (\emph{Brassica oleracea} {L.}).
+\newblock {\em Journal of Applied Ecology}, 10(2):489--499.
+
+\bibitem[\protect\astroncite{Mohr and Jay}{1988}]{mohr1988}
+Mohr, N.~A. and Jay, S.~C. 1988.
+\newblock Nectar- and pollen-collecting behaviour of honeybees on canola
+  (\emph{Brassica campestris} {L}. and \emph{Brassica napus} {L}.).
+\newblock {\em Journal of Apicultural Research}, 27(2):131--136.
+
+\end{thebibliography}
+
+\end{document}

### 2023-01-19 partial plots.R

@@ -20,6 +20,8 @@ summaryDat <- function(x){
   data.frame(min=min(x),mean=mean(x),med=median(x),max=max(x))
 } 
 
+ciOverlap <- function(lwr1,upr1,lwr2,upr2)  !(lwr1>upr2 & upr1>upr2 | upr1<lwr2 & upr1<upr2) #Do posterior quantiles overlap?
+
 load('../Models/datalist_commodity.Rdata') #Commodity data
 commData <- datalist
 load('../Models/datalist_seed.Rdata') #Seed data
@@ -55,6 +57,12 @@ avgSeedData$logLbeeDistCent <- mean(log(with(seedData,c(lbee_dist,lbee_dist_extr
 
 load('../Models/modSummaries_commodity.Rdata') #Commodity data models
 load('../Models/modSummaries_seed.Rdata') #Seed data models
+
+#Yearly models
+load('../Models/modSummaries2014_commodity.Rdata') 
+load('../Models/modSummaries2015_commodity.Rdata')
+load('../Models/modSummaries2015_seed.Rdata') 
+load('../Models/modSummaries2016_seed.Rdata') 
 
 # Visitation plots --------------------------------------------------------
 
@@ -1029,6 +1037,28 @@ commPars %>%
   # column_spec(1, width = "8em") %>%
   collapse_rows(columns=1,longtable_clean_cut=FALSE) %>% 
   clipr::write_clip() #Writes to clipboard
+
+#Other version comparing parameters between years
+m1 <- lapply(modSummaries2014_commodity,function(x) x$summary) %>% bind_rows(.id='model') %>% filter(model!='yield')
+m2 <- lapply(modSummaries2015_commodity,function(x) x$summary) %>% bind_rows(.id='model') %>% filter(model!='yield')
+
+yearOverlap <- list('Y2014'=m1,'Y2015'=m2) %>% bind_rows(.id='data') %>% 
+  select(data:param,mean,lwr,upr) %>% 
+  filter(data!='Both') %>% 
+  pivot_wider(names_from=data,values_from=c(mean,lwr,upr)) %>% 
+  mutate(overlap=ciOverlap(lwr_Y2014,upr_Y2014,lwr_Y2015,upr_Y2015)) 
+
+commPars %>% select(-median:-upr,-n_eff,-Rhat) %>% 
+  bind_cols(yearOverlap)
[…]

### 2023-01-19 yield path analysis commodity.R

@@ -208,8 +208,6 @@ for(i in 1:length(modList)){
   }
 }
 
-
-
 #Posterior predictive checks - OK 
 PPplots(modList[[1]],datalist$plDens_obs,c('predPlDens','plDens_resid','predPlDens_resid'),
         index = datalist$obsPlDens_ind,main='Plant Density')
@@ -242,7 +240,6 @@ compareRE(modList[[8]],'ranEffYield_field',1) #Intercepts
 compareRE(modList[[8]],'ranEffYield_field',2) #Slopes
 compareRE(modList[[8]],'ranEffYield_plot',1,0.3) #Intercepts
 compareRE(modList[[8]],'ranEffYield_plot',2,0.3) #Slopes - right skew
-
 
 # Run claims models ---------------------
 
@@ -326,3 +323,189 @@ read.csv('./Commodity model claims 3/claimsList_updated.csv',sep=',',strip.white
 read.csv('./Commodity model claims 3/claimsList_updated2.csv',sep=',',strip.white = TRUE) %>% 
   mutate(pval=pnorm(-abs(Z))*2) %>% 
   shipley.dSep(.,pval,param)
+
+# Run yearly version of main models ---------------------------------------
+
+# library(rstan)
+# setwd('./Models')
+# rstan_options(auto_write = TRUE) #Avoids recompilation
+# rstan_options(javascript = FALSE)
+# options(mc.cores = 6)
+# 
+# #Split datalist into 2014 and 2015 sets
+# 
+# datalist$plSizePlot_obs <- NULL #Not used
+# 
+# is2015 <- datalist$is2015 #Field-level
+# is2015_plot <- with(datalist,is2015[plotIndex])
+# is2015_flw <- with(datalist,is2015[plotIndex[flowerIndex]])
+# is2015_plant <- with(datalist,is2015[plotIndex[plantIndex]])
+# 
+# #2014 dataset
+# datalist2014 <- lapply(datalist,function(x){
+#   l <- length(x)
+#   if(l==60){
+#     r <- x[!is2015]
+#   } else if(l==271){
+#     r <- x[!is2015_plot]
+#   } else if(l==1294){
+#     r <- x[!is2015_flw]
+#   } else if(l==788){
+#     r <- x[!is2015_plant]
+#   } else r <- x
+#   return(r)
+# })
+# datalist2014$Nfield <- sum(!is2015); datalist2014$Nplot <- sum(!is2015_plot)
[…]

### 2023-01-19 yield path analysis seed.R

@@ -71,13 +71,24 @@ load('./datalist_seed.Rdata')
 # plantsAllSeed$Field <- gsub('Unrah','Unruh',plantsAllSeed$Field) #Fixes spelling error
 # seedsAllSeed$Field <- gsub('Unrah','Unruh',seedsAllSeed$Field)
 # seedsAllSeed$EdgeCent <- ifelse(seedsAllSeed$EdgeCent=='Cent','Center',seedsAllSeed$EdgeCent) #Fixes cent/center
-# rm(allFields,allPlants,allPollen,allSeeds,allSurvey,behav2015,visitors2016,nectar2016,folder)
+# rm(allFields,allPlants,allPollen,allSeeds,allSurvey,behav2015,visitors2016,nectar2016,folder,survey2015,survey2016)
 # #Set 'negative' missing pods (mistake in counting) to NA.
 # plantsAllSeed <- mutate(plantsAllSeed,Missing=ifelse(Missing<0,NA,Missing))
 # seedsAllSeed <- mutate(seedsAllSeed,Missing=ifelse(Missing<0,NA,Missing))
 # #Extra seed field data (from Riley W.)
 # rileyExtra <- read.csv('../Seed field analysis/rileyExtra.csv')
 # setwd('~/Projects/UofC/canola_yield_project')
+# 
+# # Filter for yearly model runs, if needed
+# {
+#   yfilt <- 2016
+#   rileyExtra <- filter(rileyExtra,Year==yfilt)
+#   fieldsAllSeed <- filter(fieldsAllSeed,Year==yfilt) %>% droplevels()
+#   surveyAllSeed <- filter(surveyAllSeed,Year==yfilt) %>% droplevels()
+#   pollenAllSeed <- filter(pollenAllSeed,Year==yfilt) %>% droplevels()
+#   plantsAllSeed <- filter(plantsAllSeed,Year==yfilt) %>% droplevels()
+#   seedsAllSeed <- filter(seedsAllSeed,Year==yfilt) %>% droplevels()
+# }
 # 
 # #Organize names of extra sites from Riley
 # rileyExtra$site <- factor(rileyExtra$site)
@@ -108,7 +119,6 @@ load('./datalist_seed.Rdata')
 # #   unite(ID,Year,Field,Distance,EdgeCent,Branch,Pods,Missing,remove=F) %>%
 # #   left_join(temp,by='ID') %>%  select(-ID)
 # # rm(temp)
-# 
[…]

### 2023-01-19 Manuscript/manuscript_files/supplemental.tex
Updated tables in supplemental

@@
 
-\begin{longtable}{l|l|r|r|r|r|r|l|r|r}
-\caption{Summary of parameters for commodity canola models} \\
+% \begin{longtable}{l|l|r|r|r|r|r|l|r|r} %First manuscript
+% \caption{Summary of parameters for commodity canola models} \\
+% \hline
+% Model & Parameter & Mean & SD & Median & Min & Max & P-value & N$_{eff}$ & $\hat{R}$\\
+% \hline
+% \endfirsthead
+% \multicolumn{10}{@{}l}{\textit{(continued)}}\\
+% \hline
+% Model & Parameter & Mean & SD & Median & Min & Max & P-value & N$_{eff}$ & $\hat{R}$\\
+% \hline
+% \endhead
+%  & Intercept & 3.76 & 0.05 & 3.77 & 3.66 & 3.87 & $<$0.0001 & 855 & 1.005\\
+% \cline{2-10}
+%  & HB distance & 0.02 & 0.01 & 0.02 & 0.00 & 0.04 & 0.0868 & 10154 & 1.000\\
+% \cline{2-10}
+%  & Sigma & 0.31 & 0.02 & 0.31 & 0.28 & 0.34 & - & 5039 & 0.999\\
+% \cline{2-10}
+% \multirow{-4}{*}{\raggedright\arraybackslash Plant density} & Sigma (field) & 0.37 & 0.04 & 0.37 & 0.30 & 0.46 & - & 3774 & 1.000\\
+% \cline{1-10}
+%  & Intercept & 5.24 & 0.24 & 5.24 & 4.77 & 5.72 & $<$0.0001 & 2108 & 1.001\\
+% \cline{2-10}
+%  & Plant density & -0.70 & 0.06 & -0.70 & -0.82 & -0.57 & $<$0.0001 & 2097 & 1.001\\
+% \cline{2-10}
+%  & HB distance & 0.03 & 0.01 & 0.03 & 0.01 & 0.06 & 0.0095 & 9212 & 1.000\\
+% \cline{2-10}
+%  & Sigma (field) & 0.22 & 0.04 & 0.22 & 0.15 & 0.29 & - & 1456 & 1.000\\
+% \cline{2-10}
+% \multirow{-5}{*}{\raggedright\arraybackslash Plant size} & Sigma & 0.64 & 0.02 & 0.64 & 0.61 & 0.68 & - & 7845 & 0.999\\
+% \cline{1-10}
+%  & Intercept & 5.74 & 4.70 & 5.70 & -3.62 & 15.01 & 0.222 & 1822 & 1.001\\
+% \cline{2-10}
+%  & Plant size & -1.66 & 0.98 & -1.66 & -3.60 & 0.25 & 0.0926 & 1632 & 1.001\\
+% \cline{2-10}
+%  & HB distance & 0.75 & 0.11 & 0.75 & 0.53 & 0.96 & $<$0.0001 & 6878 & 1.000\\
+% \cline{2-10}
+%  & Plant density & -0.41 & 0.74 & -0.42 & -1.86 & 1.06 & 0.5792 & 2243 & 1.001\\
+% \cline{2-10}
+%  & Sigma & 3.52 & 0.17 & 3.51 & 3.19 & 3.87 & - & 4976 & 0.999\\
+% \cline{2-10}
+% \multirow{-6}{*}{\raggedright\arraybackslash Flower density} & Sigma (field) & 3.55 & 0.39 & 3.53 & 2.88 & 4.40 & - & 4133 & 1.000\\
+% \cline{1-10}
+%  & Intercept & -1.98 & 0.45 & -1.96 & -2.89 & -1.17 & $<$0.0001 & 936 & 1.006\\
+% \cline{2-10}
+%  & HB distance & -0.31 & 0.10 & -0.31 & -0.50 & -0.13 & 0.0011 & 3526 & 1.001\\
+% \cline{2-10}
+%  & Number of hives & 0.72 & 0.15 & 0.72 & 0.43 & 1.04 & $<$0.0001 & 1534 & 1.003\\
+% \cline{2-10}
+%  & Flower density & 0.03 & 0.04 & 0.03 & -0.06 & 0.12 & 0.541 & 2397 & 1.000\\
+% \cline{2-10}
+%  & Sigma (field) & 1.44 & 0.34 & 1.43 & 0.80 & 2.14 & - & 494 & 1.014\\
+% \cline{2-10}
+% \multirow{-6}{*}{\raggedright\arraybackslash HB visits} & Phi & 0.35 & 0.08 & 0.34 & 0.22 & 0.53 & - & 1630 & 1.003\\
+% \cline{1-10}
+%  & Intercept & 2.56 & 0.04 & 2.56 & 2.50 & 2.63 & $<$0.0001 & 594 & 1.006\\
+% \cline{2-10}
+%  & Plant size & 0.94 & 0.01 & 0.94 & 0.92 & 0.96 & $<$0.0001 & 1709 & 1.002\\
+% \cline{2-10}
+%  & Pods per plant & -0.16 & 0.01 & -0.16 & -0.19 & -0.14 & $<$0.0001 & 2108 & 1.003\\
+% \cline{2-10}
+%  & Phi (field) & 0.16 & 0.02 & 0.16 & 0.13 & 0.19 & - & 3461 & 1.000\\
+% \cline{2-10}
+%  & Intercept (Phi) & 2.17 & 0.32 & 2.17 & 1.56 & 2.81 & - & 1517 & 1.001\\
+% \cline{2-10}
+%  & Plant size (Phi) & 0.66 & 0.11 & 0.66 & 0.44 & 0.87 & - & 1587 & 1.002\\
+% \cline{2-10}
+% \multirow{-7}{*}{\raggedright\arraybackslash Flowers per plant} & SigmaPhi (field) & 0.66 & 0.12 & 0.65 & 0.45 & 0.90 & - & 844 & 1.005\\
+% \cline{1-10}
+%  & Intercept & 0.66 & 0.08 & 0.66 & 0.50 & 0.82 & $<$0.0001 & 1946 & 0.999\\
+% \cline{2-10}
+%  & HB visits & 0.00 & 0.03 & 0.00 & -0.05 & 0.05 & 0.96 & 3292 & 1.000\\
+% \cline{2-10}
+%  & Plant size & 0.13 & 0.03 & 0.13 & 0.08 & 0.18 & $<$0.0001 & 3345 & 1.000\\
+% \cline{2-10}
+%  & Pollen count & 0.16 & 0.11 & 0.15 & -0.05 & 0.38 & 0.1515 & 638 & 1.002\\
+% \cline{2-10}
+%  & Sigma (field) & 0.29 & 0.03 & 0.29 & 0.23 & 0.37 & - & 2675 & 1.000\\
+% \cline{2-10}
+% \multirow{-6}{*}{\raggedright\arraybackslash Pods per plant} & Phi & 3.35 & 0.07 & 3.35 & 3.21 & 3.48 & - & 3828 & 1.003\\
+% \cline{1-10}
+%  & Intercept & 25.07 & 1.77 & 25.07 & 21.64 & 28.54 & $<$0.0001 & 2277 & 1.000\\
+% \cline{2-10}
+%  & HB visits & 0.17 & 0.21 & 0.17 & -0.24 & 0.60 & 0.4284 & 4417 & 1.000\\
+% \cline{2-10}
+%  & Pollen count & -0.97 & 0.84 & -0.98 & -2.60 & 0.68 & 0.2447 & 707 & 1.003\\
+% \cline{2-10}
+%  & Plant size & 4.31 & 0.65 & 4.31 & 3.03 & 5.58 & $<$0.0001 & 2229 & 1.000\\
+% \cline{2-10}
+%  & Pods per plant & 0.56 & 0.29 & 0.56 & 0.00 & 1.12 & 0.0529 & 4888 & 0.999\\
+% \cline{2-10}
+%  & Flowers per plant & -2.80 & 0.65 & -2.79 & -4.08 & -1.55 & $<$0.0001 & 2105 & 1.000\\
+% \cline{2-10}
+%  & Sigma & 4.06 & 0.12 & 4.06 & 3.83 & 4.29 & - & 6604 & 1.000\\
+% \cline{2-10}
+%  & Sigma (field) & 1.98 & 0.26 & 1.96 & 1.51 & 2.53 & - & 2526 & 0.999\\
+% \cline{2-10}
+% \multirow{-9}{*}{\raggedright\arraybackslash Seeds per pod} & Lambda & 2.00 & 1.03 & 1.74 & 0.84 & 4.64 & - & 3265 & 1.000\\
+% \cline{1-10}
+%  & Intercept & 0.64 & 0.54 & 0.64 & -0.40 & 1.72 & 0.2367 & 1402 & 1.000\\
+% \cline{2-10}
+%  & HB visits & 0.02 & 0.04 & 0.02 & -0.05 & 0.09 & 0.6113 & 2748 & 1.000\\
+% \cline{2-10}
+%  & Pollen count & -0.15 & 0.17 & -0.15 & -0.48 & 0.20 & 0.3744 & 358 & 1.008\\
+% \cline{2-10}
+%  & Seeds per pod & 0.00 & 0.01 & 0.00 & -0.01 & 0.02 & 0.4508 & 3348 & 1.000\\
+% \cline{2-10}
+%  & Plant size & -0.03 & 0.12 & -0.03 & -0.26 & 0.20 & 0.7955 & 1633 & 1.000\\
+% \cline{2-10}
+%  & Plant density & 0.30 & 0.08 & 0.30 & 0.14 & 0.45 & 0.0001 & 1704 & 1.001\\
+% \cline{2-10}
+%  & HB distance & 0.02 & 0.01 & 0.02 & -0.01 & 0.05 & 0.1686 & 1404 & 1.003\\
+% \cline{2-10}
+%  & Pods per plant & 0.11 & 0.04 & 0.11 & 0.02 & 0.19 & 0.0159 & 3037 & 1.000\\
+% \cline{2-10}
+%  & Flowers per plant & 0.11 & 0.12 & 0.11 & -0.13 & 0.34 & 0.363 & 1526 & 1.000\\
+% \cline{2-10}
+%  & Flower density & -0.03 & 0.01 & -0.03 & -0.04 & -0.02 & $<$0.0001 & 2213 & 1.003\\
+% \cline{2-10}
+%  & Sigma & 0.52 & 0.03 & 0.52 & 0.46 & 0.59 & - & 2100 & 1.000\\
+% \cline{2-10}
+%  & Sigma (field) & 0.47 & 0.05 & 0.47 & 0.37 & 0.58 & - & 2828 & 0.999\\
+% \cline{2-10}
+% \multirow{-13}{*}{\raggedright\arraybackslash Seed size} & Lambda & 2.71 & 0.48 & 2.63 & 2.08 & 3.86 & - & 1792 & 1.001\\
+% \hline
+% \end{longtable}
+% \endgroup{}
+
+\clearpage
+
+\begingroup\fontsize{9}{11}\selectfont
+\begin{longtable}{l|l|r|r|l|l|l}
+\caption{Summary of parameters for commodity canola models.
+p-values indicate whether means differed from zero (variance terms were excluded).
+Means are also shown for 2014 and 2015 models, with * indicating whether parameters differed between years (i.e.
+posterior 95\% quantiles did not overlap).} \\
 \hline
-Model & Parameter & Mean & SD & Median & Min & Max & P-value & N$_{eff}$ & $\hat{R}$\\
+Model & Parameter & Mean & SD & p-value & Mean$_{2014}$ & Mean$_{2015}$\\
 \hline
 \endfirsthead
-\multicolumn{10}{@{}l}{\textit{(continued)}}\\
+\multicolumn{7}{@{}l}{\textit{(continued)}}\\
 \hline
-Model & Parameter & Mean & SD & Median & Min & Max & P-value & N$_{eff}$ & $\hat{R}$\\
+Model & Parameter & Mean & SD & p-value & Mean$_{2014}$ & Mean$_{2015}$\\
 \hline
 \endhead
- & Intercept & 3.76 & 0.05 & 3.77 & 3.66 & 3.87 & $<$0.0001 & 855 & 1.005\\
-\cline{2-10}
- & HB distance & 0.02 & 0.01 & 0.02 & 0.00 & 0.04 & 0.0868 & 10154 & 1.000\\
-\cline{2-10}
- & Sigma & 0.31 & 0.02 & 0.31 & 0.28 & 0.34 & - & 5039 & 0.999\\
-\cline{2-10}
-\multirow{-4}{*}{\raggedright\arraybackslash Plant density} & Sigma (field) & 0.37 & 0.04 & 0.37 & 0.30 & 0.46 & - & 3774 & 1.000\\
-\cline{1-10}
- & Intercept & 5.24 & 0.24 & 5.24 & 4.77 & 5.72 & $<$0.0001 & 2108 & 1.001\\
-\cline{2-10}
- & Plant density & -0.70 & 0.06 & -0.70 & -0.82 & -0.57 & $<$0.0001 & 2097 & 1.001\\
-\cline{2-10}
- & HB distance & 0.03 & 0.01 & 0.03 & 0.01 & 0.06 & 0.0095 & 9212 & 1.000\\
-\cline{2-10}
- & Sigma (field) & 0.22 & 0.04 & 0.22 & 0.15 & 0.29 & - & 1456 & 1.000\\
-\cline{2-10}
-\multirow{-5}{*}{\raggedright\arraybackslash Plant size} & Sigma & 0.64 & 0.02 & 0.64 & 0.61 & 0.68 & - & 7845 & 0.999\\
-\cline{1-10}
- & Intercept & 5.74 & 4.70 & 5.70 & -3.62 & 15.01 & 0.222 & 1822 & 1.001\\
-\cline{2-10}
- & Plant size & -1.66 & 0.98 & -1.66 & -3.60 & 0.25 & 0.0926 & 1632 & 1.001\\
-\cline{2-10}
- & HB distance & 0.75 & 0.11 & 0.75 & 0.53 & 0.96 & $<$0.0001 & 6878 & 1.000\\
-\cline{2-10}
- & Plant density & -0.41 & 0.74 & -0.42 & -1.86 & 1.06 & 0.5792 & 2243 & 1.001\\
-\cline{2-10}
- & Sigma & 3.52 & 0.17 & 3.51 & 3.19 & 3.87 & - & 4976 & 0.999\\
-\cline{2-10}
-\multirow{-6}{*}{\raggedright\arraybackslash Flower density} & Sigma (field) & 3.55 & 0.39 & 3.53 & 2.88 & 4.40 & - & 4133 & 1.000\\
-\cline{1-10}
- & Intercept & -1.98 & 0.45 & -1.96 & -2.89 & -1.17 & $<$0.0001 & 936 & 1.006\\
-\cline{2-10}
- & HB distance & -0.31 & 0.10 & -0.31 & -0.50 & -0.13 & 0.0011 & 3526 & 1.001\\
-\cline{2-10}
- & Number of hives & 0.72 & 0.15 & 0.72 & 0.43 & 1.04 & $<$0.0001 & 1534 & 1.003\\
-\cline{2-10}
- & Flower density & 0.03 & 0.04 & 0.03 & -0.06 & 0.12 & 0.541 & 2397 & 1.000\\
-\cline{2-10}
- & Sigma (field) & 1.44 & 0.34 & 1.43 & 0.80 & 2.14 & - & 494 & 1.014\\
-\cline{2-10}
-\multirow{-6}{*}{\raggedright\arraybackslash HB visits} & Phi & 0.35 & 0.08 & 0.34 & 0.22 & 0.53 & - & 1630 & 1.003\\
-\cline{1-10}
- & Intercept & 2.56 & 0.04 & 2.56 & 2.50 & 2.63 & $<$0.0001 & 594 & 1.006\\
-\cline{2-10}
- & Plant size & 0.94 & 0.01 & 0.94 & 0.92 & 0.96 & $<$0.0001 & 1709 & 1.002\\
-\cline{2-10}
- & Pods per plant & -0.16 & 0.01 & -0.16 & -0.19 & -0.14 & $<$0.0001 & 2108 & 1.003\\
-\cline{2-10}
- & Phi (field) & 0.16 & 0.02 & 0.16 & 0.13 & 0.19 & - & 3461 & 1.000\\
-\cline{2-10}
- & Intercept (Phi) & 2.17 & 0.32 & 2.17 & 1.56 & 2.81 & - & 1517 & 1.001\\
-\cline{2-10}
- & Plant size (Phi) & 0.66 & 0.11 & 0.66 & 0.44 & 0.87 & - & 1587 & 1.002\\
-\cline{2-10}
-\multirow{-7}{*}{\raggedright\arraybackslash Flowers per plant} & SigmaPhi (field) & 0.66 & 0.12 & 0.65 & 0.45 & 0.90 & - & 844 & 1.005\\
-\cline{1-10}
- & Intercept & 0.66 & 0.08 & 0.66 & 0.50 & 0.82 & $<$0.0001 & 1946 & 0.999\\
-\cline{2-10}
- & HB visits & 0.00 & 0.03 & 0.00 & -0.05 & 0.05 & 0.96 & 3292 & 1.000\\
-\cline{2-10}
- & Plant size & 0.13 & 0.03 & 0.13 & 0.08 & 0.18 & $<$0.0001 & 3345 & 1.000\\
-\cline{2-10}
- & Pollen count & 0.16 & 0.11 & 0.15 & -0.05 & 0.38 & 0.1515 & 638 & 1.002\\
-\cline{2-10}
- & Sigma (field) & 0.29 & 0.03 & 0.29 & 0.23 & 0.37 & - & 2675 & 1.000\\
-\cline{2-10}
-\multirow{-6}{*}{\raggedright\arraybackslash Pods per plant} & Phi & 3.35 & 0.07 & 3.35 & 3.21 & 3.48 & - & 3828 & 1.003\\
-\cline{1-10}
- & Intercept & 25.07 & 1.77 & 25.07 & 21.64 & 28.54 & $<$0.0001 & 2277 & 1.000\\
-\cline{2-10}
- & HB visits & 0.17 & 0.21 & 0.17 & -0.24 & 0.60 & 0.4284 & 4417 & 1.000\\
-\cline{2-10}
- & Pollen count & -0.97 & 0.84 & -0.98 & -2.60 & 0.68 & 0.2447 & 707 & 1.003\\
-\cline{2-10}
- & Plant size & 4.31 & 0.65 & 4.31 & 3.03 & 5.58 & $<$0.0001 & 2229 & 1.000\\
-\cline{2-10}
- & Pods per plant & 0.56 & 0.29 & 0.56 & 0.00 & 1.12 & 0.0529 & 4888 & 0.999\\
-\cline{2-10}
- & Flowers per plant & -2.80 & 0.65 & -2.79 & -4.08 & -1.55 & $<$0.0001 & 2105 & 1.000\\
-\cline{2-10}
- & Sigma & 4.06 & 0.12 & 4.06 & 3.83 & 4.29 & - & 6604 & 1.000\\
-\cline{2-10}
- & Sigma (field) & 1.98 & 0.26 & 1.96 & 1.51 & 2.53 & - & 2526 & 0.999\\
-\cline{2-10}
-\multirow{-9}{*}{\raggedright\arraybackslash Seeds per pod} & Lambda & 2.00 & 1.03 & 1.74 & 0.84 & 4.64 & - & 3265 & 1.000\\
-\cline{1-10}
- & Intercept & 0.64 & 0.54 & 0.64 & -0.40 & 1.72 & 0.2367 & 1402 & 1.000\\
-\cline{2-10}
- & HB visits & 0.02 & 0.04 & 0.02 & -0.05 & 0.09 & 0.6113 & 2748 & 1.000\\
-\cline{2-10}
- & Pollen count & -0.15 & 0.17 & -0.15 & -0.48 & 0.20 & 0.3744 & 358 & 1.008\\
-\cline{2-10}
- & Seeds per pod & 0.00 & 0.01 & 0.00 & -0.01 & 0.02 & 0.4508 & 3348 & 1.000\\
-\cline{2-10}
- & Plant size & -0.03 & 0.12 & -0.03 & -0.26 & 0.20 & 0.7955 & 1633 & 1.000\\
-\cline{2-10}
- & Plant density & 0.30 & 0.08 & 0.30 & 0.14 & 0.45 & 0.0001 & 1704 & 1.001\\
-\cline{2-10}
- & HB distance & 0.02 & 0.01 & 0.02 & -0.01 & 0.05 & 0.1686 & 1404 & 1.003\\
-\cline{2-10}
- & Pods per plant & 0.11 & 0.04 & 0.11 & 0.02 & 0.19 & 0.0159 & 3037 & 1.000\\
-\cline{2-10}
- & Flowers per plant & 0.11 & 0.12 & 0.11 & -0.13 & 0.34 & 0.363 & 1526 & 1.000\\
-\cline{2-10}
- & Flower density & -0.03 & 0.01 & -0.03 & -0.04 & -0.02 & $<$0.0001 & 2213 & 1.003\\
-\cline{2-10}
- & Sigma & 0.52 & 0.03 & 0.52 & 0.46 & 0.59 & - & 2100 & 1.000\\
-\cline{2-10}
- & Sigma (field) & 0.47 & 0.05 & 0.47 & 0.37 & 0.58 & - & 2828 & 0.999\\
-\cline{2-10}
-\multirow{-13}{*}{\raggedright\arraybackslash Seed size} & Lambda & 2.71 & 0.48 & 2.63 & 2.08 & 3.86 & - & 1792 & 1.001\\
+ & HB distance & 0.016 & 0.010 & 0.0868 & 0.02 & 0.012\\
+\cline{2-7}
+ & Sigma & 0.309 & 0.016 & - & 0.307 & 0.318\\
+\cline{2-7}
+\multirow{-3}{*}{\raggedright\arraybackslash Plant density} & Sigma (field) & 0.371 & 0.040 & - & 0.387 & 0.365\\
+\cline{1-7}
+ & Plant density & -0.695 & 0.063 & $<$0.0001 & -0.826 & -0.492\\
+\cline{2-7}
+ & HB distance & 0.032 & 0.012 & 0.0095 & 0.025 & 0.042\\
+\cline{2-7}
+ & Sigma (field) & 0.217 & 0.036 & - & 0.189 & 0.196\\
+\cline{2-7}
+\multirow{-4}{*}{\raggedright\arraybackslash Plant size} & Sigma & 0.640 & 0.018 & - & 0.65 & 0.626\\
+\cline{1-7}
+ & Plant size & -1.658 & 0.985 & 0.0926 & -0.602 & -2.193\\
+\cline{2-7}
+ & HB distance & 0.750 & 0.111 & $<$0.0001 & 0.885 & 0.518\\
+\cline{2-7}
+ & Plant density & -0.409 & 0.737 & 0.5792 & -0.573 & 0.279\\
+\cline{2-7}
+ & Sigma & 3.520 & 0.171 & - & 3.965* & 2.663*\\
+\cline{2-7}
+\multirow{-5}{*}{\raggedright\arraybackslash Flower density} & Sigma (field) & 3.554 & 0.389 & - & 3.779 & 2.834\\
+\cline{1-7}
+ & HB distance & -0.313 & 0.096 & 0.0011 & -0.442 & -0.262\\
+\cline{2-7}
+ & Number of hives & 0.720 & 0.153 & $<$0.0001 & 0.848 & 0.654\\
+\cline{2-7}
+ & Flower density & 0.028 & 0.045 & 0.541 & 0.137 & -0.117\\
+\cline{2-7}
+ & Sigma (field) & 1.441 & 0.340 & - & 1.019 & 1.383\\
+\cline{2-7}
+\multirow{-5}{*}{\raggedright\arraybackslash HB visits} & Phi & 0.350 & 0.080 & - & 0.29 & 0.396\\
+\cline{1-7}
+ & Plant size & 0.937 & 0.010 & $<$0.0001 & 0.935 & 0.946\\
+\cline{2-7}
+ & Pods per plant & -0.162 & 0.013 & $<$0.0001 & -0.136* & -0.242*\\
+\cline{2-7}
+ & Phi (field) & 0.160 & 0.016 & - & 0.141 & 0.165\\
+\cline{2-7}
+ & Plant size (Phi) & 0.659 & 0.110 & - & 0.884* & 0.196*\\
+\cline{2-7}
+\multirow{-5}{*}{\raggedright\arraybackslash Flowers per plant} & SigmaPhi (field) & 0.660 & 0.116 & - & 0.61 & 0.897\\
+\cline{1-7}
+ & HB visits & 0.001 & 0.026 & 0.96 & 0.003 & 0.033\\
+\cline{2-7}
+ & Plant size & 0.133 & 0.026 & $<$0.0001 & 0.108 & 0.167\\
+\cline{2-7}
+ & Pollen count & 0.158 & 0.110 & 0.1515 & 0.244 & 0.045\\
+\cline{2-7}
+ & Sigma (field) & 0.294 & 0.034 & - & 0.351 & 0.231\\
+\cline{2-7}
+\multirow{-5}{*}{\raggedright\arraybackslash Pods per plant} & Phi & 3.346 & 0.067 & - & 3.036* & 3.975*\\
+\cline{1-7}
+ & HB visits & 0.170 & 0.214 & 0.4284 & 0.262 & 0.342\\
+\cline{2-7}
+ & Pollen count & -0.974 & 0.837 & 0.2447 & 0.219 & -2.117\\
+\cline{2-7}
+ & Plant size & 4.310 & 0.650 & $<$0.0001 & 3.855 & 2.899\\
+\cline{2-7}
+ & Pods per plant & 0.557 & 0.288 & 0.0529 & 0.722 & 0.623\\
+\cline{2-7}
+ & Flowers per plant & -2.799 & 0.648 & $<$0.0001 & -2.221 & -1.576\\
+\cline{2-7}
+ & Sigma & 4.057 & 0.117 & - & 4.243 & 3.744\\
+\cline{2-7}
+ & Sigma (field) & 1.976 & 0.261 & - & 1.591 & 1.517\\
+\cline{2-7}
+\multirow{-8}{*}{\raggedright\arraybackslash Seeds per pod} & Lambda & 2.001 & 1.029 & - & 1.714 & 1.855\\
+\cline{1-7}
+ & HB visits & 0.019 & 0.037 & 0.6113 & -0.033 & 0.027\\
+\cline{2-7}
+ & Pollen count & -0.152 & 0.171 & 0.3744 & -0.341 & 0.147\\
+\cline{2-7}
+ & Seeds per pod & 0.004 & 0.006 & 0.4508 & -0.001 & 0.014\\
+\cline{2-7}
+ & Plant size & -0.031 & 0.118 & 0.7955 & 0.143 & -0.332\\
+\cline{2-7}
+ & Plant density & 0.298 & 0.078 & 0.0001 & 0.289 & 0.353\\
+\cline{2-7}
+ & HB distance & 0.021 & 0.015 & 0.1686 & -0.013 & 0.076\\
+\cline{2-7}
+ & Pods per plant & 0.108 & 0.045 & 0.0159 & 0.126 & 0.042\\
+\cline{2-7}
+ & Flowers per plant & 0.110 & 0.121 & 0.363 & -0.033 & 0.357\\
+\cline{2-7}
+ & Flower density & -0.030 & 0.007 & $<$0.0001 & -0.022 & -0.04\\
+\cline{2-7}
+ & Sigma & 0.520 & 0.033 & - & 0.492 & 0.542\\
+\cline{2-7}
+ & Sigma (field) & 0.468 & 0.052 & - & 0.416 & 0.494\\
+\cline{2-7}
+\multirow{-12}{*}{\raggedright\arraybackslash Seed size} & Lambda & 2.714 & 0.478 & - & 2.478 & 3.234\\
 \hline
@@
 \endgroup{}
+
+\clearpage
 
@@
 
+% \begingroup\fontsize{9}{11}\selectfont %First manuscript
+% \begin{longtable}{l|l|r|r|r|r|r|l|r|r}
+% \caption{Summary of parameters for seed canola models} \\
+% \hline
+% Model & Parameter & Mean & SD & Median & Min & Max & P-value & N$_{eff}$ & $\hat{R}$\\
+% \hline
+% \endfirsthead
+% \multicolumn{10}{@{}l}{\textit{(continued)}}\\
+% \hline
+% Model & Parameter & Mean & SD & Median & Min & Max & P-value & N$_{eff}$ & $\hat{R}$\\
+% \hline
+% \endhead
+%  & Intercept & 3.60 & 0.06 & 3.60 & 3.47 & 3.73 & $<$0.0001 & 524 & 1.004\\
+% \cline{2-10}
+%  & HB distance & 0.06 & 0.01 & 0.06 & 0.04 & 0.07 & $<$0.0001 & 5750 & 0.999\\
+% \cline{2-10}
+%  & Sigma & 0.27 & 0.01 & 0.27 & 0.24 & 0.30 & - & 5199 & 0.999\\
+% \cline{2-10}
+% \multirow{-4}{*}{\raggedright\arraybackslash Plant density} & Sigma (field) & 0.36 & 0.05 & 0.36 & 0.28 & 0.48 & - & 4182 & 1.000\\
+% \cline{1-10}
+%  & Intercept & 6.08 & 0.25 & 6.08 & 5.57 & 6.56 & $<$0.0001 & 2480 & 1.000\\
+% \cline{2-10}
+%  & Plant density & -0.79 & 0.07 & -0.80 & -0.92 & -0.66 & $<$0.0001 & 2470 & 1.000\\
+% \cline{2-10}
+%  & HB distance & 0.07 & 0.01 & 0.07 & 0.05 & 0.10 & $<$0.0001 & 6446 & 0.999\\
+% \cline{2-10}
+%  & Sigma & 0.50 & 0.03 & 0.50 & 0.45 & 0.56 & - & 2332 & 1.000\\
+% \cline{2-10}
+%  & Sigma (field) & 0.15 & 0.04 & 0.15 & 0.08 & 0.23 & - & 1053 & 1.001\\
+% \cline{2-10}
+% \multirow{-6}{*}{\raggedright\arraybackslash Plant size} & Nu (DF) & 1.91 & 0.32 & 1.87 & 1.37 & 2.65 & $<$0.0001 & 2700 & 1.000\\
+% \cline{1-10}
+%  & Intercept & 0.48 & 0.56 & 0.46 & -0.58 & 1.64 & 0.3827 & 661 & 1.005\\
+% \cline{2-10}
+%  & HB distance & 1.11 & 0.12 & 1.11 & 0.87 & 1.36 & $<$0.0001 & 5389 & 1.000\\
+% \cline{2-10}
+%  & Sigma & 4.06 & 0.24 & 4.05 & 3.59 & 4.56 & - & 2404 & 1.001\\
+% \cline{2-10}
+%  & Sigma (field) & 3.48 & 0.47 & 3.44 & 2.70 & 4.49 & - & 2640 & 1.001\\
+% \cline{2-10}
+% \multirow{-5}{*}{\raggedright\arraybackslash Flower density} & Nu (DF) & 1.88 & 0.38 & 1.84 & 1.30 & 2.68 & $<$0.0001 & 1500 & 1.004\\
+% \cline{1-10}
+%  & Intercept & 3.08 & 0.10 & 3.08 & 2.87 & 3.28 & $<$0.0001 & 2722 & 1.002\\
+% \cline{2-10}
+%  & Flower density & -0.01 & 0.01 & -0.01 & -0.03 & 0.01 & 0.5267 & 4150 & 1.000\\
+% \cline{2-10}
+%  & HB distance & -0.02 & 0.05 & -0.03 & -0.12 & 0.07 & 0.6229 & 4410 & 1.000\\
+% \cline{2-10}
+%  & LCB distance & 0.42 & 0.09 & 0.42 & 0.24 & 0.58 & $<$0.0001 & 5053 & 1.000\\
+% \cline{2-10}
+%  & Bay centre & 0.45 & 0.21 & 0.45 & 0.07 & 0.88 & 0.0284 & 6486 & 0.999\\
+% \cline{2-10}
+%  & Phi & 0.72 & 0.09 & 0.72 & 0.55 & 0.92 & - & 4354 & 1.001\\
+% \cline{2-10}
+%  & Theta (ZI) & 0.32 & 0.03 & 0.32 & 0.26 & 0.38 & - & 3955 & 1.001\\
+% \cline{2-10}
+% \multirow{-8}{*}{\raggedright\arraybackslash HB visits} & Sigma (field) & 0.41 & 0.11 & 0.41 & 0.22 & 0.64 & - & 600 & 1.001\\
+% \cline{1-10}
+%  & Intercept & 2.25 & 0.14 & 2.25 & 1.96 & 2.51 & $<$0.0001 & 1734 & 1.002\\
+% \cline{2-10}
+%  & LCB distance & -0.79 & 0.07 & -0.79 & -0.94 & -0.65 & $<$0.0001 & 4016 & 1.000\\
+% \cline{2-10}
+%  & HB distance & -0.32 & 0.06 & -0.32 & -0.43 & -0.21 & $<$0.0001 & 5128 & 1.000\\
+% \cline{2-10}
+%  & Bay centre & -0.34 & 0.23 & -0.34 & -0.77 & 0.16 & 0.1458 & 6667 & 1.000\\
+% \cline{2-10}
+%  & Flower density & 0.03 & 0.01 & 0.03 & 0.01 & 0.05 & 0.0115 & 4364 & 1.000\\
+% \cline{2-10}
+%  & Sigma (field) & 0.63 & 0.13 & 0.62 & 0.40 & 0.91 & - & 1072 & 1.004\\
+% \cline{2-10}
+%  & Phi & 0.70 & 0.11 & 0.69 & 0.50 & 0.93 & - & 3097 & 0.999\\
+% \cline{2-10}
+% \multirow{-8}{*}{\raggedright\arraybackslash LCB visits} & Theta (ZI) & 0.25 & 0.04 & 0.25 & 0.15 & 0.33 & - & 2383 & 1.000\\
+% \cline{1-10}
+%  & Intercept & 2.49 & 0.19 & 2.50 & 2.12 & 2.85 & $<$0.0001 & 1141 & 1.002\\
+% \cline{2-10}
+%  & HB visits & 0.05 & 0.04 & 0.05 & -0.03 & 0.12 & 0.195 & 2317 & 1.000\\
+% \cline{2-10}
+%  & LCB visits & 0.15 & 0.06 & 0.14 & 0.02 & 0.26 & 0.0155 & 2239 & 1.000\\
+% \cline{2-10}
+%  & Bay centre & -0.55 & 0.13 & -0.55 & -0.80 & -0.30 & $<$0.0001 & 2540 & 1.000\\
+% \cline{2-10}
+%  & HB distance & -0.17 & 0.04 & -0.17 & -0.25 & -0.09 & $<$0.0001 & 2265 & 1.003\\
+% \cline{2-10}
+%  & LCB distance & -0.35 & 0.14 & -0.35 & -0.63 & -0.07 & 0.0164 & 2513 & 1.000\\
+% \cline{2-10}
+%  & Flower density & -0.03 & 0.02 & -0.03 & -0.06 & 0.01 & 0.1284 & 2058 & 1.001\\
+% \cline{2-10}
+%  & Sigma (field) & 0.86 & 0.13 & 0.85 & 0.64 & 1.15 & - & 2978 & 1.000\\
+% \cline{2-10}
+%  & Sigma (plot) & 0.65 & 0.06 & 0.65 & 0.53 & 0.78 & - & 1142 & 1.003\\
+% \cline{2-10}
+% \multirow{-10}{*}{\raggedright\arraybackslash Pollen count} & Phi & 0.82 & 0.04 & 0.82 & 0.74 & 0.90 & - & 5125 & 0.999\\
+% \cline{1-10}
+%  & Intercept & 3.05 & 0.04 & 3.05 & 2.96 & 3.14 & $<$0.0001 & 3283 & 0.999\\
+% \cline{2-10}
+%  & Plant size & 0.93 & 0.01 & 0.93 & 0.90 & 0.95 & $<$0.0001 & 3712 & 0.999\\
+% \cline{2-10}
+%  & Bay centre & 0.09 & 0.02 & 0.09 & 0.06 & 0.12 & $<$0.0001 & 6790 & 0.999\\
+% \cline{2-10}
+%  & Pods per plant & -0.14 & 0.01 & -0.14 & -0.17 & -0.12 & $<$0.0001 & 5503 & 0.999\\
+% \cline{2-10}
+%  & Sigma (field) & 0.08 & 0.01 & 0.08 & 0.06 & 0.11 & - & 2649 & 1.000\\
+% \cline{2-10}
+%  & Intercept (Phi) & 2.24 & 0.32 & 2.24 & 1.62 & 2.87 & - & 2875 & 1.001\\
+% \cline{2-10}
+% \multirow{-7}{*}{\raggedright\arraybackslash Flowers per plant} & Plant size (Phi) & 0.38 & 0.10 & 0.39 & 0.19 & 0.57 & - & 2871 & 1.001\\
+% \cline{1-10}
+%  & Intercept & 0.18 & 0.12 & 0.18 & -0.05 & 0.40 & 0.1211 & 2261 & 1.000\\
+% \cline{2-10}
+%  & Pollen count & 0.12 & 0.04 & 0.12 & 0.03 & 0.20 & 0.0074 & 915 & 1.004\\
+% \cline{2-10}
+%  & Plant size & 0.19 & 0.03 & 0.19 & 0.14 & 0.24 & $<$0.0001 & 4570 & 1.000\\
+% \cline{2-10}
+%  & Bay centre & -0.21 & 0.06 & -0.21 & -0.33 & -0.10 & 0.0003 & 1886 & 1.000\\
+% \cline{2-10}
+%  & HB distance & -0.12 & 0.02 & -0.12 & -0.15 & -0.08 & $<$0.0001 & 1929 & 1.002\\
+% \cline{2-10}
+%  & LCB distance & -0.21 & 0.06 & -0.21 & -0.34 & -0.10 & 0.0005 & 2637 & 1.000\\
+% \cline{2-10}
+%  & Flower density & 0.00 & 0.01 & 0.00 & -0.02 & 0.01 & 0.5456 & 2998 & 1.000\\
+% \cline{2-10}
+%  & Sigma (plot) & 0.30 & 0.03 & 0.30 & 0.25 & 0.35 & - & 1367 & 1.004\\
+% \cline{2-10}
+%  & Sigma (field) & 0.37 & 0.06 & 0.36 & 0.27 & 0.49 & - & 2905 & 1.000\\
+% \cline{2-10}
+%  & Intercept (Phi) & 3.07 & 0.38 & 3.05 & 2.36 & 3.85 & - & 2268 & 1.004\\
+% \cline{2-10}
+% \multirow{-11}{*}{\raggedright\arraybackslash Pods per plant} & Plant size (Phi) & 0.22 & 0.12 & 0.22 & -0.01 & 0.44 & - & 2538 & 1.003\\
+% \cline{1-10}
+%  & Intercept & 25.38 & 2.29 & 25.48 & 20.64 & 29.38 & $<$0.0001 & 1651 & 1.001\\
+% \cline{2-10}
+%  & Pollen count & 1.21 & 0.32 & 1.20 & 0.61 & 1.87 & 0.0001 & 1046 & 1.002\\
+% \cline{2-10}
+%  & Plant size & 4.76 & 0.78 & 4.76 & 3.24 & 6.23 & $<$0.0001 & 1752 & 1.001\\
+% \cline{2-10}
+%  & Bay centre & -0.50 & 0.45 & -0.50 & -1.39 & 0.38 & 0.2639 & 5315 & 0.999\\
+% \cline{2-10}
+%  & HB distance & -0.02 & 0.12 & -0.01 & -0.25 & 0.21 & 0.881 & 3007 & 1.000\\
+% \cline{2-10}
+%  & Flower density & -0.11 & 0.06 & -0.11 & -0.23 & 0.00 & 0.0451 & 2596 & 1.000\\
+% \cline{2-10}
+%  & Pods per plant & 1.65 & 0.35 & 1.65 & 0.94 & 2.34 & $<$0.0001 & 2485 & 1.001\\
+% \cline{2-10}
+%  & Flowers per plant & -4.26 & 0.74 & -4.27 & -5.60 & -2.73 & $<$0.0001 & 1571 & 1.001\\
+% \cline{2-10}
+%  & Sigma & 4.25 & 0.16 & 4.25 & 3.92 & 4.56 & - & 2951 & 1.000\\
+% \cline{2-10}
+%  & Sigma (field) & 1.97 & 0.32 & 1.95 & 1.41 & 2.68 & - & 1767 & 1.002\\
+% \cline{2-10}
+% \multirow{-11}{*}{\raggedright\arraybackslash Seeds per pod} & Lambda & 1.67 & 1.00 & 1.39 & 0.60 & 4.28 & - & 2448 & 0.999\\
+% \cline{1-10}
+%  & Intercept & 1.17 & 0.50 & 1.18 & 0.21 & 2.16 & 0.0189 & 2004 & 1.001\\
+% \cline{2-10}
+%  & Pollen count & -0.02 & 0.05 & -0.02 & -0.12 & 0.08 & 0.7002 & 2345 & 1.000\\
+% \cline{2-10}
+%  & Seeds per pod & -0.01 & 0.01 & -0.01 & -0.03 & 0.00 & 0.0765 & 3719 & 0.999\\
+% \cline{2-10}
+%  & Plant size & 0.23 & 0.06 & 0.23 & 0.12 & 0.34 & $<$0.0001 & 3607 & 1.000\\
+% \cline{2-10}
+%  & Plant density & 0.41 & 0.11 & 0.41 & 0.20 & 0.63 & 0.0002 & 1988 & 1.000\\
+% \cline{2-10}
+%  & LCB distance & 0.07 & 0.07 & 0.07 & -0.06 & 0.22 & 0.3146 & 4466 & 1.000\\
+% \cline{2-10}
+%  & Sigma & 0.75 & 0.03 & 0.75 & 0.69 & 0.81 & - & 3533 & 1.000\\
+% \cline{2-10}
+%  & Sigma (field) & 0.36 & 0.06 & 0.35 & 0.25 & 0.49 & - & 2060 & 1.000\\
+% \cline{2-10}
+% \multirow{-9}{*}{\raggedright\arraybackslash Seed size} & Lambda & 4.44 & 1.22 & 4.23 & 2.70 & 7.42 & - & 2125 & 1.000\\
+% \hline
+% \end{longtable}
+% \endgroup{}
+
 \begingroup\fontsize{9}{11}\selectfont
 
-\begin{longtable}{l|l|r|r|r|r|r|l|r|r}
-
-\caption{Summary of parameters for seed canola models} \\
-
+\begin{longtable}{l|l|r|r|l|l|l}
+\caption{Summary of parameters for seed canola models.
+p-values indicate whether means differed from zero (variance terms were excluded).
+Means are also shown for 2015 and 2016 models, with * indicating whether parameters differed between years (i.e.
+posterior 95\% quantiles did not overlap).} \\
 \hline
-Model & Parameter & Mean & SD & Median & Min & Max & P-value & N$_{eff}$ & $\hat{R}$\\
+Model & Parameter & Mean & SD & p-value & Mean$_{2015}$ & Mean$_{2016}$\\
 \hline
 \endfirsthead
-\multicolumn{10}{@{}l}{\textit{(continued)}}\\
+\multicolumn{7}{@{}l}{\textit{(continued)}}\\
 \hline
-Model & Parameter & Mean & SD & Median & Min & Max & P-value & N$_{eff}$ & $\hat{R}$\\
+Model & Parameter & Mean & SD & p-value & Mean$_{2015}$ & Mean$_{2016}$\\
 \hline
 \endhead
- & Intercept & 3.60 & 0.06 & 3.60 & 3.47 & 3.73 & $<$0.0001 & 524 & 1.004\\
-\cline{2-10}
- & HB distance & 0.06 & 0.01 & 0.06 & 0.04 & 0.07 & $<$0.0001 & 5750 & 0.999\\
-\cline{2-10}
- & Sigma & 0.27 & 0.01 & 0.27 & 0.24 & 0.30 & - & 5199 & 0.999\\
-\cline{2-10}
-\multirow{-4}{*}{\raggedright\arraybackslash Plant density} & Sigma (field) & 0.36 & 0.05 & 0.36 & 0.28 & 0.48 & - & 4182 & 1.000\\
-\cline{1-10}
- & Intercept & 6.08 & 0.25 & 6.08 & 5.57 & 6.56 & $<$0.0001 & 2480 & 1.000\\
-\cline{2-10}
- & Plant density & -0.79 & 0.07 & -0.80 & -0.92 & -0.66 & $<$0.0001 & 2470 & 1.000\\
-\cline{2-10}
- & HB distance & 0.07 & 0.01 & 0.07 & 0.05 & 0.10 & $<$0.0001 & 6446 & 0.999\\
-\cline{2-10}
- & Sigma & 0.50 & 0.03 & 0.50 & 0.45 & 0.56 & - & 2332 & 1.000\\
-\cline{2-10}
- & Sigma (field) & 0.15 & 0.04 & 0.15 & 0.08 & 0.23 & - & 1053 & 1.001\\
-\cline{2-10}
-\multirow{-6}{*}{\raggedright\arraybackslash Plant size} & Nu (DF) & 1.91 & 0.32 & 1.87 & 1.37 & 2.65 & $<$0.0001 & 2700 & 1.000\\
-\cline{1-10}
- & Intercept & 0.48 & 0.56 & 0.46 & -0.58 & 1.64 & 0.3827 & 661 & 1.005\\
-\cline{2-10}
- & HB distance & 1.11 & 0.12 & 1.11 & 0.87 & 1.36 & $<$0.0001 & 5389 & 1.000\\
-\cline{2-10}
- & Sigma & 4.06 & 0.24 & 4.05 & 3.59 & 4.56 & - & 2404 & 1.001\\
-\cline{2-10}
- & Sigma (field) & 3.48 & 0.47 & 3.44 & 2.70 & 4.49 & - & 2640 & 1.001\\
-\cline{2-10}
-\multirow{-5}{*}{\raggedright\arraybackslash Flower density} & Nu (DF) & 1.88 & 0.38 & 1.84 & 1.30 & 2.68 & $<$0.0001 & 1500 & 1.004\\
-\cline{1-10}
- & Intercept & 3.08 & 0.10 & 3.08 & 2.87 & 3.28 & $<$0.0001 & 2722 & 1.002\\
-\cline{2-10}
- & Flower density & -0.01 & 0.01 & -0.01 & -0.03 & 0.01 & 0.5267 & 4150 & 1.000\\
-\cline{2-10}
- & HB distance & -0.02 & 0.05 & -0.03 & -0.12 & 0.07 & 0.6229 & 4410 & 1.000\\
-\cline{2-10}
- & LCB distance & 0.42 & 0.09 & 0.42 & 0.24 & 0.58 & $<$0.0001 & 5053 & 1.000\\
-\cline{2-10}
- & Bay centre & 0.45 & 0.21 & 0.45 & 0.07 & 0.88 & 0.0284 & 6486 & 0.999\\
-\cline{2-10}
- & Phi & 0.72 & 0.09 & 0.72 & 0.55 & 0.92 & - & 4354 & 1.001\\
-\cline{2-10}
- & Theta (ZI) & 0.32 & 0.03 & 0.32 & 0.26 & 0.38 & - & 3955 & 1.001\\
-\cline{2-10}
-\multirow{-8}{*}{\raggedright\arraybackslash HB visits} & Sigma (field) & 0.41 & 0.11 & 0.41 & 0.22 & 0.64 & - & 600 & 1.001\\
-\cline{1-10}
- & Intercept & 2.25 & 0.14 & 2.25 & 1.96 & 2.51 & $<$0.0001 & 1734 & 1.002\\
-\cline{2-10}
- & LCB distance & -0.79 & 0.07 & -0.79 & -0.94 & -0.65 & $<$0.0001 & 4016 & 1.000\\
-\cline{2-10}
- & HB distance & -0.32 & 0.06 & -0.32 & -0.43 & -0.21 & $<$0.0001 & 5128 & 1.000\\
-\cline{2-10}
- & Bay centre & -0.34 & 0.23 & -0.34 & -0.77 & 0.16 & 0.1458 & 6667 & 1.000\\
-\cline{2-10}
- & Flower density & 0.03 & 0.01 & 0.03 & 0.01 & 0.05 & 0.0115 & 4364 & 1.000\\
-\cline{2-10}
- & Sigma (field) & 0.63 & 0.13 & 0.62 & 0.40 & 0.91 & - & 1072 & 1.004\\
-\cline{2-10}
- & Phi & 0.70 & 0.11 & 0.69 & 0.50 & 0.93 & - & 3097 & 0.999\\
-\cline{2-10}
-\multirow{-8}{*}{\raggedright\arraybackslash LCB visits} & Theta (ZI) & 0.25 & 0.04 & 0.25 & 0.15 & 0.33 & - & 2383 & 1.000\\
-\cline{1-10}
- & Intercept & 2.49 & 0.19 & 2.50 & 2.12 & 2.85 & $<$0.0001 & 1141 & 1.002\\
-\cline{2-10}
- & HB visits & 0.05 & 0.04 & 0.05 & -0.03 & 0.12 & 0.195 & 2317 & 1.000\\
-\cline{2-10}
- & LCB visits & 0.15 & 0.06 & 0.14 & 0.02 & 0.26 & 0.0155 & 2239 & 1.000\\
-\cline{2-10}
- & Bay centre & -0.55 & 0.13 & -0.55 & -0.80 & -0.30 & $<$0.0001 & 2540 & 1.000\\
-\cline{2-10}
- & HB distance & -0.17 & 0.04 & -0.17 & -0.25 & -0.09 & $<$0.0001 & 2265 & 1.003\\
-\cline{2-10}
- & LCB distance & -0.35 & 0.14 & -0.35 & -0.63 & -0.07 & 0.0164 & 2513 & 1.000\\
-\cline{2-10}
- & Flower density & -0.03 & 0.02 & -0.03 & -0.06 & 0.01 & 0.1284 & 2058 & 1.001\\
-\cline{2-10}
- & Sigma (field) & 0.86 & 0.13 & 0.85 & 0.64 & 1.15 & - & 2978 & 1.000\\
-\cline{2-10}
- & Sigma (plot) & 0.65 & 0.06 & 0.65 & 0.53 & 0.78 & - & 1142 & 1.003\\
-\cline{2-10}
-\multirow{-10}{*}{\raggedright\arraybackslash Pollen count} & Phi & 0.82 & 0.04 & 0.82 & 0.74 & 0.90 & - & 5125 & 0.999\\
-\cline{1-10}
- & Intercept & 3.05 & 0.04 & 3.05 & 2.96 & 3.14 & $<$0.0001 & 3283 & 0.999\\
-\cline{2-10}
- & Plant size & 0.93 & 0.01 & 0.93 & 0.90 & 0.95 & $<$0.0001 & 3712 & 0.999\\
-\cline{2-10}
- & Bay centre & 0.09 & 0.02 & 0.09 & 0.06 & 0.12 & $<$0.0001 & 6790 & 0.999\\
-\cline{2-10}
- & Pods per plant & -0.14 & 0.01 & -0.14 & -0.17 & -0.12 & $<$0.0001 & 5503 & 0.999\\
-\cline{2-10}
- & Sigma (field) & 0.08 & 0.01 & 0.08 & 0.06 & 0.11 & - & 2649 & 1.000\\
-\cline{2-10}
- & Intercept (Phi) & 2.24 & 0.32 & 2.24 & 1.62 & 2.87 & - & 2875 & 1.001\\
-\cline{2-10}
-\multirow{-7}{*}{\raggedright\arraybackslash Flowers per plant} & Plant size (Phi) & 0.38 & 0.10 & 0.39 & 0.19 & 0.57 & - & 2871 & 1.001\\
-\cline{1-10}
- & Intercept & 0.18 & 0.12 & 0.18 & -0.05 & 0.40 & 0.1211 & 2261 & 1.000\\
-\cline{2-10}
- & Pollen count & 0.12 & 0.04 & 0.12 & 0.03 & 0.20 & 0.0074 & 915 & 1.004\\
-\cline{2-10}
- & Plant size & 0.19 & 0.03 & 0.19 & 0.14 & 0.24 & $<$0.0001 & 4570 & 1.000\\
-\cline{2-10}
- & Bay centre & -0.21 & 0.06 & -0.21 & -0.33 & -0.10 & 0.0003 & 1886 & 1.000\\
-\cline{2-10}
- & HB distance & -0.12 & 0.02 & -0.12 & -0.15 & -0.08 & $<$0.0001 & 1929 & 1.002\\
-\cline{2-10}
- & LCB distance & -0.21 & 0.06 & -0.21 & -0.34 & -0.10 & 0.0005 & 2637 & 1.000\\
-\cline{2-10}
- & Flower density & 0.00 & 0.01 & 0.00 & -0.02 & 0.01 & 0.5456 & 2998 & 1.000\\
-\cline{2-10}
- & Sigma (plot) & 0.30 & 0.03 & 0.30 & 0.25 & 0.35 & - & 1367 & 1.004\\
-\cline{2-10}
- & Sigma (field) & 0.37 & 0.06 & 0.36 & 0.27 & 0.49 & - & 2905 & 1.000\\
-\cline{2-10}
- & Intercept (Phi) & 3.07 & 0.38 & 3.05 & 2.36 & 3.85 & - & 2268 & 1.004\\
-\cline{2-10}
-\multirow{-11}{*}{\raggedright\arraybackslash Pods per plant} & Plant size (Phi) & 0.22 & 0.12 & 0.22 & -0.01 & 0.44 & - & 2538 & 1.003\\
-\cline{1-10}
- & Intercept & 25.38 & 2.29 & 25.48 & 20.64 & 29.38 & $<$0.0001 & 1651 & 1.001\\
-\cline{2-10}
- & Pollen count & 1.21 & 0.32 & 1.20 & 0.61 & 1.87 & 0.0001 & 1046 & 1.002\\
-\cline{2-10}
- & Plant size & 4.76 & 0.78 & 4.76 & 3.24 & 6.23 & $<$0.0001 & 1752 & 1.001\\
-\cline{2-10}
- & Bay centre & -0.50 & 0.45 & -0.50 & -1.39 & 0.38 & 0.2639 & 5315 & 0.999\\
-\cline{2-10}
- & HB distance & -0.02 & 0.12 & -0.01 & -0.25 & 0.21 & 0.881 & 3007 & 1.000\\
-\cline{2-10}
- & Flower density & -0.11 & 0.06 & -0.11 & -0.23 & 0.00 & 0.0451 & 2596 & 1.000\\
-\cline{2-10}
- & Pods per plant & 1.65 & 0.35 & 1.65 & 0.94 & 2.34 & $<$0.0001 & 2485 & 1.001\\
-\cline{2-10}
- & Flowers per plant & -4.26 & 0.74 & -4.27 & -5.60 & -2.73 & $<$0.0001 & 1571 & 1.001\\
-\cline{2-10}
- & Sigma & 4.25 & 0.16 & 4.25 & 3.92 & 4.56 & - & 2951 & 1.000\\
-\cline{2-10}
- & Sigma (field) & 1.97 & 0.32 & 1.95 & 1.41 & 2.68 & - & 1767 & 1.002\\
-\cline{2-10}
-\multirow{-11}{*}{\raggedright\arraybackslash Seeds per pod} & Lambda & 1.67 & 1.00 & 1.39 & 0.60 & 4.28 & - & 2448 & 0.999\\
-\cline{1-10}
- & Intercept & 1.17 & 0.50 & 1.18 & 0.21 & 2.16 & 0.0189 & 2004 & 1.001\\
-\cline{2-10}
- & Pollen count & -0.02 & 0.05 & -0.02 & -0.12 & 0.08 & 0.7002 & 2345 & 1.000\\
-\cline{2-10}
- & Seeds per pod & -0.01 & 0.01 & -0.01 & -0.03 & 0.00 & 0.0765 & 3719 & 0.999\\
-\cline{2-10}
- & Plant size & 0.23 & 0.06 & 0.23 & 0.12 & 0.34 & $<$0.0001 & 3607 & 1.000\\
-\cline{2-10}
- & Plant density & 0.41 & 0.11 & 0.41 & 0.20 & 0.63 & 0.0002 & 1988 & 1.000\\
-\cline{2-10}
- & LCB distance & 0.07 & 0.07 & 0.07 & -0.06 & 0.22 & 0.3146 & 4466 & 1.000\\
-\cline{2-10}
- & Sigma & 0.75 & 0.03 & 0.75 & 0.69 & 0.81 & - & 3533 & 1.000\\
-\cline{2-10}
- & Sigma (field) & 0.36 & 0.06 & 0.35 & 0.25 & 0.49 & - & 2060 & 1.000\\
-\cline{2-10}
-\multirow{-9}{*}{\raggedright\arraybackslash Seed size} & Lambda & 4.44 & 1.22 & 4.23 & 2.70 & 7.42 & - & 2125 & 1.000\\
+ & HB distance & 0.055 & 0.010 & $<$0.0001 & 0.075 & 0.041\\
+\cline{2-7}
+ & Sigma & 0.272 & 0.015 & - & 0.324* & 0.229*\\
+\cline{2-7}
+\multirow{-3}{*}{\raggedright\arraybackslash Plant density} & Sigma (field) & 0.364 & 0.049 & - & 0.332 & 0.375\\
+\cline{1-7}
+ & Plant density & -0.794 & 0.069 & $<$0.0001 & -0.65 & -0.912\\
+\cline{2-7}
+ & HB distance & 0.074 & 0.013 & $<$0.0001 & 0.07 & 0.075\\
+\cline{2-7}
+ & Sigma & 0.505 & 0.029 & - & 0.561 & 0.491\\
+\cline{2-7}
+ & Sigma (field) & 0.151 & 0.037 & - & 0.141 & 0.146\\
+\cline{2-7}
+\multirow{-5}{*}{\raggedright\arraybackslash Plant size} & Nu (DF) & 1.905 & 0.325 & $<$0.0001 & 1.974 & 2.988\\
+\cline{1-7}
+ & HB distance & 1.109 & 0.124 & $<$0.0001 & 1.481 & 0.982\\
+\cline{2-7}
+ & Sigma & 4.055 & 0.244 & - & 5.232* & 3.688*\\
+\cline{2-7}
+ & Sigma (field) & 3.485 & 0.466 & - & 3.483 & 1.976\\
+\cline{2-7}
+\multirow{-4}{*}{\raggedright\arraybackslash Flower density} & Nu (DF) & 1.875 & 0.376 & $<$0.0001 & 3.045 & 3.999\\
+\cline{1-7}
+ & Flower density & -0.007 & 0.011 & 0.5267 & -0.018 & 0.033\\
+\cline{2-7}
+ & HB distance & -0.024 & 0.050 & 0.6229 & -0.128 & 0.012\\
+\cline{2-7}
+ & LCB distance & 0.415 & 0.085 & $<$0.0001 & 0.421 & 0.403\\
+\cline{2-7}
+ & Bay centre & 0.452 & 0.206 & 0.0284 & 0.441 & 0.382\\
+\cline{2-7}
+ & Phi & 0.719 & 0.094 & - & 0.632 & 0.796\\
+\cline{2-7}
+ & Theta (ZI) & 0.320 & 0.029 & - & 0.291 & 0.328\\
+\cline{2-7}
+\multirow{-7}{*}{\raggedright\arraybackslash HB visits} & Sigma (field) & 0.413 & 0.108 & - & 0.263 & 0.532\\
+\cline{1-7}
+ & LCB distance & -0.790 & 0.074 & $<$0.0001 & -0.752 & -0.858\\
+\cline{2-7}
+ & HB distance & -0.319 & 0.055 & $<$0.0001 & -0.374 & -0.233\\
+\cline{2-7}
+ & Bay centre & -0.335 & 0.231 & 0.1458 & -0.104 & -0.576\\
+\cline{2-7}
+ & Flower density & 0.028 & 0.011 & 0.0115 & 0.018 & 0.055\\
+\cline{2-7}
+ & Sigma (field) & 0.629 & 0.129 & - & 0.617 & 0.602\\
+\cline{2-7}
+ & Phi & 0.698 & 0.112 & - & 0.717 & 0.643\\
+\cline{2-7}
+\multirow{-7}{*}{\raggedright\arraybackslash LCB visits} & Theta (ZI) & 0.248 & 0.045 & - & 0.195 & 0.278\\
+\cline{1-7}
+ & HB visits & 0.050 & 0.039 & 0.195 & 0.038 & 0.079\\
+\cline{2-7}
+ & LCB visits & 0.146 & 0.060 & 0.0155 & 0.151 & 0.115\\
+\cline{2-7}
+ & Bay centre & -0.550 & 0.129 & $<$0.0001 & -0.424 & -0.626\\
+\cline{2-7}
+ & HB distance & -0.169 & 0.039 & $<$0.0001 & -0.166 & -0.171\\
+\cline{2-7}
+ & LCB distance & -0.348 & 0.145 & 0.0164 & 0.08 & -0.506\\
+\cline{2-7}
+ & Flower density & -0.026 & 0.017 & 0.1284 & -0.009 & -0.032\\
+\cline{2-7}
+ & Sigma (field) & 0.862 & 0.130 & - & 0.639 & 0.964\\
+\cline{2-7}
+ & Sigma (plot) & 0.651 & 0.064 & - & 0.663 & 0.679\\
+\cline{2-7}
+\multirow{-9}{*}{\raggedright\arraybackslash Pollen count} & Phi & 0.817 & 0.042 & - & 0.958 & 0.724\\
+\cline{1-7}
+ & Plant size & 0.926 & 0.013 & $<$0.0001 & 0.933 & 0.925\\
+\cline{2-7}
+ & Bay centre & 0.091 & 0.016 & $<$0.0001 & 0.08 & 0.09\\
+\cline{2-7}
+ & Pods per plant & -0.141 & 0.012 & $<$0.0001 & -0.215* & -0.118*\\
+\cline{2-7}
+ & Sigma (field) & 0.082 & 0.014 & - & 0.11 & 0.06\\
+\cline{2-7}
+\multirow{-5}{*}{\raggedright\arraybackslash Flowers per plant} & Plant size (Phi) & 0.384 & 0.097 & - & 0.606 & 0.14\\
+\cline{1-7}
+ & Pollen count & 0.119 & 0.044 & 0.0074 & -0.009 & 0.186\\
+\cline{2-7}
+ & Plant size & 0.190 & 0.027 & $<$0.0001 & 0.216 & 0.147\\
+\cline{2-7}
+ & Bay centre & -0.212 & 0.059 & 0.0003 & -0.362 & -0.113\\
+\cline{2-7}
+ & HB distance & -0.115 & 0.019 & $<$0.0001 & -0.118 & -0.131\\
+\cline{2-7}
+ & LCB distance & -0.214 & 0.062 & 0.0005 & -0.135 & -0.254\\
+\cline{2-7}
+ & Flower density & -0.005 & 0.008 & 0.5456 & -0.02 & 0.009\\
+\cline{2-7}
+ & Sigma (plot) & 0.296 & 0.026 & - & 0.259 & 0.32\\
+\cline{2-7}
+ & Sigma (field) & 0.366 & 0.056 & - & 0.105* & 0.464*\\
+\cline{2-7}
+\multirow{-9}{*}{\raggedright\arraybackslash Pods per plant} & Plant size (Phi) & 0.222 & 0.115 & - & 0.492 & -0.032\\
+\cline{1-7}
+ & Pollen count & 1.208 & 0.317 & 0.0001 & 0.369 & 1.48\\
+\cline{2-7}
+ & Plant size & 4.757 & 0.776 & $<$0.0001 & 4.309 & 3.009\\
+\cline{2-7}
+ & Bay centre & -0.502 & 0.449 & 0.2639 & -0.621 & -0.655\\
+\cline{2-7}
+ & HB distance & -0.018 & 0.120 & 0.881 & -0.287 & 0.128\\
+\cline{2-7}
+ & Flower density & -0.114 & 0.057 & 0.0451 & 0.02 & -0.184\\
+\cline{2-7}
+ & Pods per plant & 1.647 & 0.352 & $<$0.0001 & 3.201 & 1.305\\
+\cline{2-7}
+ & Flowers per plant & -4.257 & 0.743 & $<$0.0001 & -3.396 & -2.971\\
+\cline{2-7}
+ & Sigma & 4.250 & 0.156 & - & 4.14 & 4.252\\
+\cline{2-7}
+ & Sigma (field) & 1.972 & 0.322 & - & 1.476 & 1.972\\
+\cline{2-7}
+\multirow{-10}{*}{\raggedright\arraybackslash Seeds per pod} & Lambda & 1.673 & 0.995 & - & 1.5 & 1.453\\
+\cline{1-7}
+ & Pollen count & -0.020 & 0.051 & 0.7002 & -0.016 & 0.013\\
+\cline{2-7}
+ & Seeds per pod & -0.013 & 0.007 & 0.0765 & 0.016* & -0.04*\\
+\cline{2-7}
+ & Plant size & 0.233 & 0.055 & $<$0.0001 & 0.255 & 0.129\\
+\cline{2-7}
+ & Plant density & 0.413 & 0.110 & 0.0002 & 0.508 & 0.047\\
+\cline{2-7}
+ & LCB distance & 0.072 & 0.072 & 0.3146 & -0.117 & 0.138\\
+\cline{2-7}
+ & Sigma & 0.751 & 0.030 & - & 0.768 & 0.686\\
+\cline{2-7}
+ & Sigma (field) & 0.358 & 0.061 & - & 0.333 & 0.298\\
+\cline{2-7}
+\multirow{-8}{*}{\raggedright\arraybackslash Seed size} & Lambda & 4.436 & 1.219 & - & 3.491 & 4.191\\
 \hline
@@
 
+% \begin{table}[h] %First manuscript
+% \centering\begingroup\fontsize{9}{11}\selectfont
+% \caption{Summary of parameters for total yield models} 
+% \begin{tabular}{l|l|r|r|r|r|r|r|r|r|r}
+% \hline
+% Field Type & Parameter & Mean & SD & Z & median & Min & Max & p-value & N$_{eff}$ & $\hat{R}$\\
+% \hline
+%  & Intercept & -0.318 & 0.042 & -7.62 & -0.317 & -0.397 & -0.236 & 0.000 & 982 & 1.000\\
+% \cline{2-11}
+%  & Predicted Yield & 1.007 & 0.018 & 55.64 & 1.007 & 0.972 & 1.044 & 0.000 & 1044 & 1.000\\
+% \cline{2-11}
+%  & Sigma (field intercept) & 0.119 & 0.041 & 2.89 & 0.112 & 0.051 & 0.216 & 0.004 & 292 & 1.020\\
+% \cline{2-11}
+%  & Sigma (field slope) & 0.026 & 0.019 & 1.37 & 0.023 & 0.001 & 0.072 & 0.170 & 295 & 1.013\\
+% \cline{2-11}
+%  & Sigma (plot intercept) & 0.389 & 0.037 & 10.47 & 0.388 & 0.318 & 0.465 & 0.000 & 506 & 1.005\\
+% \cline{2-11}
+%  & Sigma (plot slope) & 0.169 & 0.017 & 9.86 & 0.168 & 0.135 & 0.204 & 0.000 & 556 & 1.006\\
+% \cline{2-11}
+%  & Sigma & 0.253 & 0.008 & 33.30 & 0.253 & 0.239 & 0.268 & 0.000 & 2002 & 1.000\\
+% \cline{2-11}
+%  & Correlation (Int:Slope field) & -0.400 & 0.448 & -0.89 & -0.525 & -0.944 & 0.626 & 0.372 & 660 & 1.005\\
+% \cline{2-11}
+% \multirow{-9}{*}{\raggedright\arraybackslash Commodity} & Correlation (Int:Slope plot) & -0.989 & 0.007 & -140.44 & -0.990 & -0.998 & -0.972 & 0.000 & 936 & 1.005\\
+% \cline{1-11}
+%  & Intercept & -0.210 & 0.072 & -2.90 & -0.210 & -0.348 & -0.066 & 0.004 & 738 & 1.007\\
+% \cline{2-11}
+%  & Predicted Yield & 0.856 & 0.025 & 34.62 & 0.856 & 0.806 & 0.904 & 0.000 & 672 & 1.008\\
+% \cline{2-11}
+%  & Sigma (field intercept) & 0.040 & 0.018 & 2.28 & 0.038 & 0.011 & 0.079 & 0.022 & 226 & 1.005\\
+% \cline{2-11}
+%  & Sigma (field slope) & 0.010 & 0.007 & 1.56 & 0.009 & 0.001 & 0.023 & 0.118 & 217 & 1.005\\
+% \cline{2-11}
+%  & Sigma (plot intercept) & 0.097 & 0.013 & 7.26 & 0.097 & 0.072 & 0.124 & 0.000 & 470 & 1.005\\
+% \cline{2-11}
+%  & Sigma (plot slope) & 0.032 & 0.005 & 5.83 & 0.032 & 0.021 & 0.043 & 0.000 & 379 & 1.006\\
+% \cline{2-11}
+%  & Sigma & 0.289 & 0.012 & 23.59 & 0.289 & 0.266 & 0.314 & 0.000 & 1218 & 1.001\\
+% \cline{2-11}
+%  & Correlation (Int:Slope field) & -0.470 & 0.436 & -1.08 & -0.616 & -0.946 & 0.603 & 0.281 & 457 & 1.005\\
+% \cline{2-11}
+% \multirow{-9}{*}{\raggedright\arraybackslash Seed} & Correlation (Int:Slope plot) & -0.902 & 0.038 & -23.81 & -0.909 & -0.954 & -0.808 & 0.000 & 486 & 1.007\\
+% \hline
+% \end{tabular}
+% \label{tab:totalYieldCoefs}
+% \endgroup{}
+% \end{table}
+
 \begin{table}[h]
 \centering\begingroup\fontsize{9}{11}\selectfont
-\caption{Summary of parameters for total yield models}
-
-\begin{tabular}{l|l|r|r|r|r|r|r|r|r|r}
+\caption{Summary of parameters for total yield models. p-values indicate whether means differed from zero (variance terms were excluded).}
+\begin{tabular}{l|l|r|r|l}
 \hline
-Field Type & Parameter & Mean & SD & Z & median & Min & Max & p-value & N$_{eff}$ & $\hat{R}$\\
+Field Type & Parameter & Mean & SD & p-value\\
 \hline
- & Intercept & -0.318 & 0.042 & -7.62 & -0.317 & -0.397 & -0.236 & 0.000 & 982 & 1.000\\
-\cline{2-11}
- & Predicted Yield & 1.007 & 0.018 & 55.64 & 1.007 & 0.972 & 1.044 & 0.000 & 1044 & 1.000\\
-\cline{2-11}
- & Sigma (field intercept) & 0.119 & 0.041 & 2.89 & 0.112 & 0.051 & 0.216 & 0.004 & 292 & 1.020\\
-\cline{2-11}
- & Sigma (field slope) & 0.026 & 0.019 & 1.37 & 0.023 & 0.001 & 0.072 & 0.170 & 295 & 1.013\\
-\cline{2-11}
- & Sigma (plot intercept) & 0.389 & 0.037 & 10.47 & 0.388 & 0.318 & 0.465 & 0.000 & 506 & 1.005\\
-\cline{2-11}
- & Sigma (plot slope) & 0.169 & 0.017 & 9.86 & 0.168 & 0.135 & 0.204 & 0.000 & 556 & 1.006\\
-\cline{2-11}
- & Sigma & 0.253 & 0.008 & 33.30 & 0.253 & 0.239 & 0.268 & 0.000 & 2002 & 1.000\\
-\cline{2-11}
- & Correlation (Int:Slope field) & -0.400 & 0.448 & -0.89 & -0.525 & -0.944 & 0.626 & 0.372 & 660 & 1.005\\
-\cline{2-11}
-\multirow{-9}{*}{\raggedright\arraybackslash Commodity} & Correlation (Int:Slope plot) & -0.989 & 0.007 & -140.44 & -0.990 & -0.998 & -0.972 & 0.000 & 936 & 1.005\\
-\cline{1-11}
- & Intercept & -0.210 & 0.072 & -2.90 & -0.210 & -0.348 & -0.066 & 0.004 & 738 & 1.007\\
-\cline{2-11}
- & Predicted Yield & 0.856 & 0.025 & 34.62 & 0.856 & 0.806 & 0.904 & 0.000 & 672 & 1.008\\
-\cline{2-11}
- & Sigma (field intercept) & 0.040 & 0.018 & 2.28 & 0.038 & 0.011 & 0.079 & 0.022 & 226 & 1.005\\
-\cline{2-11}
- & Sigma (field slope) & 0.010 & 0.007 & 1.56 & 0.009 & 0.001 & 0.023 & 0.118 & 217 & 1.005\\
-\cline{2-11}
- & Sigma (plot intercept) & 0.097 & 0.013 & 7.26 & 0.097 & 0.072 & 0.124 & 0.000 & 470 & 1.005\\
-\cline{2-11}
- & Sigma (plot slope) & 0.032 & 0.005 & 5.83 & 0.032 & 0.021 & 0.043 & 0.000 & 379 & 1.006\\
-\cline{2-11}
- & Sigma & 0.289 & 0.012 & 23.59 & 0.289 & 0.266 & 0.314 & 0.000 & 1218 & 1.001\\
-\cline{2-11}
- & Correlation (Int:Slope field) & -0.470 & 0.436 & -1.08 & -0.616 & -0.946 & 0.603 & 0.281 & 457 & 1.005\\
-\cline{2-11}
-\multirow{-9}{*}{\raggedright\arraybackslash Seed} & Correlation (Int:Slope plot) & -0.902 & 0.038 & -23.81 & -0.909 & -0.954 & -0.808 & 0.000 & 486 & 1.007\\
+ & Intercept & -0.318 & 0.042 & $<$0.0001\\
+\cline{2-5}
+ & Predicted Yield & 1.007 & 0.018 & $<$0.0001\\
+\cline{2-5}
+ & Sigma (field intercept) & 0.119 & 0.041 & -\\
+\cline{2-5}
+ & Sigma (field slope) & 0.026 & 0.019 & -\\
+\cline{2-5}
+ & Sigma (plot intercept) & 0.389 & 0.037 & -\\
+\cline{2-5}
+ & Sigma (plot slope) & 0.169 & 0.017 & -\\
+\cline{2-5}
+ & Sigma & 0.253 & 0.008 & -\\
+\cline{2-5}
+ & Correlation (Int:Slope field) & -0.400 & 0.448 & -\\
+\cline{2-5}
+\multirow{-9}{*}{\raggedright\arraybackslash Commodity} & Correlation (Int:Slope plot) & -0.989 & 0.007 & -\\
+\cline{1-5}
+ & Intercept & -0.210 & 0.072 & 0.0037\\
+\cline{2-5}
+ & Predicted Yield & 0.856 & 0.025 & $<$0.0001\\
+\cline{2-5}
+ & Sigma (field intercept) & 0.040 & 0.018 & -\\
+\cline{2-5}
+ & Sigma (field slope) & 0.010 & 0.007 & -\\
+\cline{2-5}
+ & Sigma (plot intercept) & 0.097 & 0.013 & -\\
+\cline{2-5}
+ & Sigma (plot slope) & 0.032 & 0.005 & -\\
+\cline{2-5}
+ & Sigma & 0.289 & 0.012 & -\\
+\cline{2-5}
+ & Correlation (Int:Slope field) & -0.470 & 0.436 & -\\
+\cline{2-5}
+\multirow{-9}{*}{\raggedright\arraybackslash Seed} & Correlation (Int:Slope plot) & -0.902 & 0.038 & -\\
 \hline
 \end{tabular}
-\label{tab:totalYieldCoefs}
 \endgroup{}

### 2023-01-19 partial plots.R

@@ -995,8 +995,19 @@ commNames <- data.frame(name=c('numHives','hbeeDist','hbeeVis','pollen',
                                 'Plant size','Plant density','Flower density',
                                 'Flowers per plant','Pods per plant','Seeds per pod','Seed size'))
 
+#Compare parameters between years
+m1 <- lapply(modSummaries2014_commodity,function(x) x$summary) %>% bind_rows(.id='model') 
+m2 <- lapply(modSummaries2015_commodity,function(x) x$summary) %>% bind_rows(.id='model') 
+yearOverlap <- list('Y2014'=m1,'Y2015'=m2) %>% bind_rows(.id='data') %>%
+    select(data:param,mean,lwr,upr) %>% filter(data!='Both') %>%
+    pivot_wider(names_from=data,values_from=c(mean,lwr,upr)) %>%
+    mutate(overlap=ciOverlap(lwr_Y2014,upr_Y2014,lwr_Y2015,upr_Y2015)) %>% 
+    select(contains('mean'),overlap)
+
+#Create coefficient table
 commPars <- lapply(modSummaries_commodity,function(x) x$summary) %>% #Get path coefficients
   bind_rows(.id='model') %>% 
+  bind_cols(yearOverlap) %>% 
   filter(model!='yield') %>% #,!grepl('(int|sigma|lambda|Phi|phi|rho)',param)) %>%
   # mutate(param=gsub('int','Intercept',param))
   mutate(model=case_when(
@@ -1013,7 +1024,7 @@ commPars <- lapply(modSummaries_commodity,function(x) x$summary) %>% #Get path c
   select(-model) %>% rename(model=labs) %>% 
   left_join(commNames,by=c('param'='name')) %>%
   mutate(param=ifelse(is.na(labs),param,labs)) %>% 
-  select(model,param,mean:Rhat,-Z) %>% 
+  select(model,param,mean:overlap,-Z) %>% 
   mutate(param=capFirst(param)) %>% 
   mutate(param=case_when(
     param=='Int' ~ 'Intercept',
@@ -1028,8 +1039,10 @@ commPars <- lapply(modSummaries_commodity,function(x) x$summary) %>% #Get path c
     TRUE ~ formatC(pval)
   ))
 
+#Version in first draft
 commPars %>%
[…]

### 2023-01-23 Manuscript/manuscript_files/supplemental.tex
Worked on revisions

@@
 
+\begin{figure}[h]
+    \centering
+    \includegraphics[width=\textwidth,keepaspectratio=true]{both_beeInt_time.png}
+    \caption[Visitation model intercepts over time]{HB and LCB visitation models used random intercepts to account for variation between fields as well as over time.
+There was little systematic variation in HB intercepts across time, or between commodity field locations (Grand Prairie and Lethbridge), but there was a slight systematic decrease in seed field LCB intercepts during 2015, indicating that visitation rates declined across the season (this was not seen during the 2016 field season).}
+\end{figure}
+
 \begin{table}[h]
@@
 \cline{2-7}
- & Plant density (m$^2$) & 3.77 & 3.77 & 0.48 & 1.79 & 5.02\\
+ & Plant density (m$^2$) & 48.53 & 43.50 & 22.91 & 6 & 151\\
 \cline{2-7}
@@
 \cline{2-7}
- & Plant density (m$^2$) & 3.58 & 3.64 & 0.46 & 2.40 & 4.49\\
+ & Plant density (m$^2$) & 39.65 & 38.00 & 16.87 & 11 & 89\\
 \cline{2-7}

### 2023-01-23 partial plots.R

@@ -561,11 +561,6 @@ d2 <- with(avgSeedData,
 (p <- ggarrange(p1,p2,p3,p4,p5,p6,nrow=2,ncol=3,common.legend = FALSE,labels='auto'))
 ggsave('allSeeds.png',p,bg='white',width = 10,height=6)
 
-# Total yield and seed size - plant density --------------------------
-
-
-
-
 # Total yield and seed size for commodity fields -----------------------------------------------------
 
 # avgCommData$flDensMean$mean #Avg sqrt flw dens
@@ -948,7 +943,7 @@ commDatSummary <- with(commData,list(
   'HB visitation (hr$^{-1}$)'=6*hbeeVis/totalTime,
   'Flower density (m$^2$)'=(flDens+flDensMean)^2,
   'Pollen per stigma'=pollenCount,
-  'Plant density (m$^2$)'=plDens_obs,
+  'Plant density (m$^2$)'=exp(plDens_obs),
   'Plant vegetative mass (g)'=VegMass,'Plant seed mass (g)'=yield,'Harvest index (g/g)'=yield/VegMass,
   'Flowers per plant'=flwCount,'Pods per plant'=podCount,'Seeds per pod'=seedCount,'Seed size (mg)'=seedMass
   )) %>% 
@@ -963,7 +958,7 @@ seedDatSummary <- with(seedData,list(
   'Bay Edge/Centre'=c(isCent,isCent_extra),
   'Flower density (m$^2$)'=(c(flDens_obs,flDens_obs_extra)+flDensMean)^2,
   'Pollen per stigma'=pollenCount,
-  'Plant density (m$^2$)'=plDens_obs,
+  'Plant density (m$^2$)'=exp(plDens_obs),
   'Plant vegetative mass (g)'=exp(plantSize),
   'Plant seed mass (g)'=yield,
   'Harvest index (g/g)'=yield/exp(plantSize),

### 2023-01-23 yield path analysis commodity.R

@@ -226,7 +226,7 @@ compareRE(modList[[1]],'intPlDens_field')
 compareRE(modList[[1]],'intPlSize_field')
 # compareRE(modList[[1]],'intPlSize_plot') #Not great. Most overlap zero, and N_eff for sigma is low
 compareRE(modList[[1]],'intFlDens_field') 
-compareRE(modList[[2]],'intVisit_field') #skew-normal, but looks OK
+compareRE(modList[[2]],'intHbeeVis_field') #skew-normal, but looks OK
 compareRE(modList[[3]],'intPollen_field')
 compareRE(modList[[4]],'intFlwCount_field')
 compareRE(modList[[4]],'intFlwCount_plot')
@@ -240,6 +240,19 @@ compareRE(modList[[8]],'ranEffYield_field',1) #Intercepts
 compareRE(modList[[8]],'ranEffYield_field',2) #Slopes
 compareRE(modList[[8]],'ranEffYield_plot',1,0.3) #Intercepts
 compareRE(modList[[8]],'ranEffYield_plot',2,0.3) #Slopes - right skew
+
+#Compare visitation random intercepts across time ("does visitation differ throughout time"?)
+(pars <- extract(modList[[2]],pars='intHbeeVis_field')[[1]] %>% 
+  apply(.,2,function(x) quantile(x,c(0.1,0.5,0.9))) %>% 
+  t() %>% data.frame(datalist$fieldName) %>% setNames(c('lwr','med','upr','fieldName')))
+load("../Commodity field analysis/commodityfieldDataAll.RData")
+rm(AICc,brix2mgul,deltaAIC,DIC,plotFixedTerms,predFixef,se,varComp,zeroCheck,conversion,visitorsAll,visitors2015)
+p <- fieldsAll %>% mutate(fieldName=paste(Year,Field,sep=' ')) %>% 
+  left_join(pars,by='fieldName') %>% mutate(doy=as.numeric(format(Surveyed,format='%j'))) %>% 
+  ggplot(aes(x=doy,y=med,ymax=upr,ymin=lwr))+geom_pointrange()+
+  facet_grid(Year~Area,scales='free_x')+geom_hline(yintercept = 0,linetype='dashed')+
+  labs(x='Day of year',y='Field-level random intercept',title = 'Commodity visitation')
+ggsave('../Figures/comm_hbeeInt_time.png',p,width = 8,height=8)
 
 # Run claims models ---------------------
 

### 2023-01-23 yield path analysis seed.R

@@ -77,23 +77,34 @@ load('./datalist_seed.Rdata')
 # seedsAllSeed <- mutate(seedsAllSeed,Missing=ifelse(Missing<0,NA,Missing))
 # #Extra seed field data (from Riley W.)
 # rileyExtra <- read.csv('../Seed field analysis/rileyExtra.csv')
-# setwd('~/Projects/UofC/canola_yield_project')
+# # setwd('~/Projects/UofC/canola_yield_project') #Multivac path
+# setwd('~/Documents/canola_yield_project') #Galpern01 path
 # 
-# # Filter for yearly model runs, if needed
-# {
-#   yfilt <- 2016
-#   rileyExtra <- filter(rileyExtra,Year==yfilt)
-#   fieldsAllSeed <- filter(fieldsAllSeed,Year==yfilt) %>% droplevels()
-#   surveyAllSeed <- filter(surveyAllSeed,Year==yfilt) %>% droplevels()
-#   pollenAllSeed <- filter(pollenAllSeed,Year==yfilt) %>% droplevels()
-#   plantsAllSeed <- filter(plantsAllSeed,Year==yfilt) %>% droplevels()
-#   seedsAllSeed <- filter(seedsAllSeed,Year==yfilt) %>% droplevels()
-# }
+# # # Filter for yearly model runs, if needed
+# # {
+# #   yfilt <- 2016
+# #   rileyExtra <- filter(rileyExtra,Year==yfilt)
+# #   fieldsAllSeed <- filter(fieldsAllSeed,Year==yfilt) %>% droplevels()
+# #   surveyAllSeed <- filter(surveyAllSeed,Year==yfilt) %>% droplevels()
+# #   pollenAllSeed <- filter(pollenAllSeed,Year==yfilt) %>% droplevels()
+# #   plantsAllSeed <- filter(plantsAllSeed,Year==yfilt) %>% droplevels()
+# #   seedsAllSeed <- filter(seedsAllSeed,Year==yfilt) %>% droplevels()
+# # }
+# 
+# #Fix date structure in Riley's fields
+# rileyExtra$date <- as.character(rileyExtra$date)
+# rileyExtra$date[grepl('-',rileyExtra$date)] <- as.character(as.Date(rileyExtra$date,format='%d-%b-%y')[grepl('-',rileyExtra$date)])
+# rileyExtra$date[grepl('/',rileyExtra$date)] <- as.character(as.Date(rileyExtra$date,format='%m/%d/%Y')[grepl('/',rileyExtra$date)])
[…]

### 2023-01-24 Manuscript/manuscript_files/supplemental.tex
Worked on revisions

@@
     \includegraphics[width=\textwidth,keepaspectratio=true]{seedfieldBays.jpg}
-    \caption[Hybrid seed field production field near Rainer, AB]{Hybrid seed field near Rainer, AB, showing the outlines of male and female bays in the foreground, with orange leafcutter bee shelters stationed throughout the field.
+    \caption[Hybrid seed field production field near Rainer, AB]{Hybrid seed field near Rainer, AB, showing the outlines of male and female bays in the foreground, with orange leafcutting bee shelters stationed throughout the field.
 The linear structure on the horizon is the central-pivot irrigation sprinkler.}
@@
     \includegraphics[width=\textwidth,keepaspectratio=true]{seedfieldPlots.png}
-    \caption[Plot arrangement for surveys in hybrid seed fields]{Plot arrangement for surveys in hybrid seed fields, showing hypothetical arrangement of leafcutter shelters ($\Delta$), and male-fertile (\Hermaphrodite) and female bays (\Female) at 5m from the edge of the field.
+    \caption[Plot arrangement for surveys in hybrid seed fields]{Plot arrangement for surveys in hybrid seed fields, showing hypothetical arrangement of leafcutting bee shelters ($\Delta$), and male-fertile (\Hermaphrodite) and female bays (\Female) at 5m from the edge of the field.
 Plots were placed along a transect (dashed line) from the field edge nearest to the set of honey bee hives.
@@
 In 2015, we recorded whether honey bees were top-working or side-working flowers (see also \citealp{free1973, free1983, mohr1988}).
-Top-working bees landed on the top of the flower and inserted their proboscis down between the petals to access the nectaries of the flower, while side-working bees landed on the side of the flower and stole nectar by inserted their proboscis between the petals, avoiding contact with the stigma or anthers.
+Top-working bees landed on the top of the flower and inserted their proboscis down between the petals to access the nectaries of the flower, while side-working bees landed on the side of the flower and stole nectar by inserting their proboscis between the petals, avoiding contact with the stigma or anthers.
 Additionally, we recorded whether honey bees were pollen or nectar foragers (pollen foragers had a visible pollen load on their corbicula, while nectar foragers had none).
@@
 Therefore, foraging honey bees in seed canola fields tend to treat male-fertile flowers similar to commodity canola flowers, but seem to top-work flowers more in commodity canola than seed fields.
-Leafcutter bee foraging behaviours were not recorded, but seemed to almost exclusively top-work flowers in seed canola fields.
+Leafcutting bee foraging behaviours were not recorded, but anecdoctally, most seemed to almost exclusively top-work flowers in seed canola fields.
 
@@
     Butterfly & 16 & 1.82 & 0 & 0 \\
-    Leafcutter bee & 4 & 0.456 & 1675 & 19.9 \\
+    Leafcutting bee & 4 & 0.456 & 1675 & 19.9 \\
     % \hline

### 2023-01-25 Manuscript/manuscript_files/supplemental.tex
Finished revisions

@@
     \caption[Visitation model intercepts over time]{HB and LCB visitation models used random intercepts to account for variation between fields as well as over time.
-There was little systematic variation in HB intercepts across time, or between commodity field locations (Grand Prairie and Lethbridge), but there was a slight systematic decrease in seed field LCB intercepts during 2015, indicating that visitation rates declined across the season (this was not seen during the 2016 field season).}
+There was little systematic variation in HB intercepts across time, or between commodity field locations (Beaverlodge and Lethbridge), but there was a slight systematic decrease in seed field LCB intercepts during 2015, indicating that visitation rates declined across the season (this was not seen during the 2016 field season).}
 \end{figure}
@@
 
-Pollen- and nectar-foraging honey bees had different patterns of side-working, both on commodity canola, and the male and female lines of seed canola.
+Pollen- and nectar-foraging honey bees had different patterns of side-working, both on commodity canola, and the male and female bays of seed canola (Table S3).
 Side-working was common in nectar foragers, but was more common in commodity canola (64\%) than in the male (36\%) or female bays (2.8\%) of seed canola, indicating that a large proportion of honey bees foraging on canola flowers may never come in contact with the stigmas.
-Pollen foragers were almost uniformly top-foragers in both commodity and seed fields (Table \ref{tab:sideWorking}), and pollen foragers were much less common in the female bays (1.4\%) than in the male bays (15\%), or in commodity fields (18\%).
+Pollen foragers were almost uniformly top-foragers in both commodity and seed fields, and pollen foragers were much less common in the female bays (1.4\%) than in the male bays (15\%), or in commodity fields (18\%).
 Therefore, foraging honey bees in seed canola fields tend to treat male-fertile flowers similar to commodity canola flowers, but seem to top-work flowers more in commodity canola than seed fields.

### 2023-02-09 Manuscript/manuscript_files/supplemental.tex
Finished revisions, and added DryadData folder

--- 2023-01-23 Manuscript/manuscript_files/supplemental.tex
@@
 % \cline{2-10}
-%  & Pods per plant & -0.16 & 0.01 & -0.16 & -0.19 & -0.14 & $<$0.0001 & 2108 & 1.003\\
+%  & \% Pod Set & -0.16 & 0.01 & -0.16 & -0.19 & -0.14 & $<$0.0001 & 2108 & 1.003\\
 % \cline{2-10}
@@
 % \cline{2-10}
-% \multirow{-6}{*}{\raggedright\arraybackslash Pods per plant} & Phi & 3.35 & 0.07 & 3.35 & 3.21 & 3.48 & - & 3828 & 1.003\\
+% \multirow{-6}{*}{\raggedright\arraybackslash \% Pod Set} & Phi & 3.35 & 0.07 & 3.35 & 3.21 & 3.48 & - & 3828 & 1.003\\
 % \cline{1-10}
@@
 % \cline{2-10}
-%  & Pods per plant & 0.56 & 0.29 & 0.56 & 0.00 & 1.12 & 0.0529 & 4888 & 0.999\\
+%  & \% Pod Set & 0.56 & 0.29 & 0.56 & 0.00 & 1.12 & 0.0529 & 4888 & 0.999\\
 % \cline{2-10}
@@
 % \cline{2-10}
-%  & Pods per plant & 0.11 & 0.04 & 0.11 & 0.02 & 0.19 & 0.0159 & 3037 & 1.000\\
+%  & \% Pod Set & 0.11 & 0.04 & 0.11 & 0.02 & 0.19 & 0.0159 & 3037 & 1.000\\
 % \cline{2-10}
@@
 \cline{2-7}
- & Pods per plant & -0.162 & 0.013 & $<$0.0001 & -0.136* & -0.242*\\
+ & \% Pod Set & -0.162 & 0.013 & $<$0.0001 & -0.136* & -0.242*\\
 \cline{2-7}
@@
 \cline{2-7}
-\multirow{-5}{*}{\raggedright\arraybackslash Pods per plant} & Phi & 3.346 & 0.067 & - & 3.036* & 3.975*\\
+\multirow{-5}{*}{\raggedright\arraybackslash \% Pod Set} & Phi & 3.346 & 0.067 & - & 3.036* & 3.975*\\
 \cline{1-7}
@@
 \cline{2-7}
- & Pods per plant & 0.557 & 0.288 & 0.0529 & 0.722 & 0.623\\
+ & \% Pod Set & 0.557 & 0.288 & 0.0529 & 0.722 & 0.623\\
 \cline{2-7}
@@
 \cline{2-7}
- & Pods per plant & 0.108 & 0.045 & 0.0159 & 0.126 & 0.042\\
+ & \% Pod Set & 0.108 & 0.045 & 0.0159 & 0.126 & 0.042\\
 \cline{2-7}
@@
 % \cline{2-10}
-%  & Pods per plant & -0.14 & 0.01 & -0.14 & -0.17 & -0.12 & $<$0.0001 & 5503 & 0.999\\
+%  & \% Pod Set & -0.14 & 0.01 & -0.14 & -0.17 & -0.12 & $<$0.0001 & 5503 & 0.999\\
 % \cline{2-10}
@@
 % \cline{2-10}
-% \multirow{-11}{*}{\raggedright\arraybackslash Pods per plant} & Plant size (Phi) & 0.22 & 0.12 & 0.22 & -0.01 & 0.44 & - & 2538 & 1.003\\
+% \multirow{-11}{*}{\raggedright\arraybackslash \% Pod Set} & Plant size (Phi) & 0.22 & 0.12 & 0.22 & -0.01 & 0.44 & - & 2538 & 1.003\\
 % \cline{1-10}
@@
 % \cline{2-10}
-%  & Pods per plant & 1.65 & 0.35 & 1.65 & 0.94 & 2.34 & $<$0.0001 & 2485 & 1.001\\
+%  & \% Pod Set & 1.65 & 0.35 & 1.65 & 0.94 & 2.34 & $<$0.0001 & 2485 & 1.001\\
 % \cline{2-10}
@@
 \cline{2-7}
- & Pods per plant & -0.141 & 0.012 & $<$0.0001 & -0.215* & -0.118*\\
+ & \% Pod Set & -0.141 & 0.012 & $<$0.0001 & -0.215* & -0.118*\\
 \cline{2-7}
@@
 \cline{2-7}
-\multirow{-9}{*}{\raggedright\arraybackslash Pods per plant} & Plant size (Phi) & 0.222 & 0.115 & - & 0.492 & -0.032\\
+\multirow{-9}{*}{\raggedright\arraybackslash \% Pod Set} & Plant size (Phi) & 0.222 & 0.115 & - & 0.492 & -0.032\\
 \cline{1-7}
@@
 \cline{2-7}
- & Pods per plant & 1.647 & 0.352 & $<$0.0001 & 3.201 & 1.305\\
+ & \% Pod Set & 1.647 & 0.352 & $<$0.0001 & 3.201 & 1.305\\
 \cline{2-7}
@@
 Formulas for total yield models are  using \texttt{lmer}-style R formulas.
-Predicted yield for each plant was calculated as: pods per plant $\times$ seeds per pod $\times$ weight per seed.
+Predicted yield for each plant was calculated as: \% Pod Set $\times$ flowers per plant $\times$ seeds per pod $\times$ weight per seed.
 Terms on right side of $\sim$ indicate fixed effects, while terms in brackets indicate random intercepts (and slopes).

### 2023-02-09 DryadData/predDryadData.R

@@ -1,0 +1,133 @@
+library(ggplot2)
+library(dplyr)
+library(tidyr)
+
+setwd('~/Projects/UofC/canola_yield_project/')
+
+# Commodity field data -----------------
+
+#Dryad commodity field visitation data - from other paper
+tempSurvey <- read.csv('C://Users//Samuel//Desktop//doi_10.5061_dryad.vhhmgqnvj__v3//commodityVisitation.csv')
+
+# data.frame(FieldNumber=tempSurvey$Field,FieldName=paste(surveyAllComm$Field,surveyAllComm$Year)) %>% 
+#   unique %>% arrange(FieldName) #Numbered field IDs from Field name + Year
+
+load("./Commodity field analysis/commodityfieldDataAll.RData")
+
+rm(AICc,brix2mgul,deltaAIC,DIC,plotFixedTerms,predFixef,se,
+   varComp,zeroCheck,conversion,visitorsAll,visitors2015)
+fieldsAllComm <- fieldsAll; flowersAllComm <- flowersAll; plantsAllComm <- plantsAll;
+seedsAllComm <- seedsAll; surveyAllComm <- surveyAll;
+rm(fieldsAll,flowersAll,plantsAll,seedsAll,surveyAll)
+
+#Unique field names
+fieldNames <- unique(paste(surveyAllComm$Field,surveyAllComm$Year))
+
+#Commodity plant data
+seedTemp <- seedsAllComm %>% select(Field,Year,Distance,Plant,Pod:PodMass) %>% 
+  mutate(Field=factor(paste(Field,Year),levels=fieldNames)) %>%
+  mutate(Field=as.numeric(Field)) %>% 
+  group_by(Field,Year,Distance,Plant,Pod) %>% 
+  mutate(N=1:n()) %>% filter(N==1) %>% ungroup() %>% select(-N) %>% 
+  pivot_longer(c(PodCount,PodMass)) %>% 
+  pivot_wider(values_from=value,names_from = c(name,Pod),names_sep = '') 
+
+plantsAllComm %>% 
+  mutate(Field=factor(paste(Field,Year),levels=fieldNames)) %>%
+  mutate(Field=as.numeric(Field)) %>% 
+  mutate(SeedCount=ifelse(is.nan(SeedCount),NA,SeedCount)) %>% 
+  mutate(AvPodCount=round(AvPodCount,1)) %>% 
+  select(-contains('SEPod')) %>% 
[…]

### 2023-02-09 Seed field analysis/canola seed pollination all.R

@@ -96,16 +96,24 @@ allPollen=bind_rows(transmute(pollen2015,Field,Distance,Treatment,Variety,minDis
 rm(pollen2015,pollen2016)
 
 #Plant data
-allPlants=bind_rows(transmute(plants2015,Year,Field,Distance,EdgeCent,EdgeDir,Variety,VegMass,SeedMass,Branch,Pods,Missing,AvPodCount,AvPodMass,lbee=Leafbee,hbee=Honeybee,TotalTime=5),
-                    transmute(plants2016,Year,Field,Distance,EdgeCent,EdgeDir,Variety,VegMass,SeedMass,Branch,Pods,Missing,AvPodCount,AvPodMass,lbee=Leafcutterbee,hbee=HoneybeeNectar+HoneybeePollen,TotalTime=10)) %>%
+allPlants=bind_rows(transmute(plants2015,Year,Field,Distance,EdgeCent,EdgeDir,Plant,Variety,VegMass,
+                              SeedMass,Branch,Pods,Missing,AvPodCount,AvPodMass,lbee=Leafbee,
+                              hbee=Honeybee,TotalTime=5),
+                    transmute(plants2016,Year,Field,Distance,EdgeCent,EdgeDir,Plant,Variety,VegMass,
+                              SeedMass,Branch,Pods,Missing,AvPodCount,AvPodMass,lbee=Leafcutterbee,
+                              hbee=HoneybeeNectar+HoneybeePollen,TotalTime=10)) %>%
   mutate(Field=factor(Field),EdgeCent=factor(ifelse(EdgeCent=='Cent','Center',EdgeCent))) %>%
   mutate(EdgeDir=factor(ifelse(nchar(EdgeDir)>2,substr(EdgeDir,1,1),EdgeDir))) %>%
   mutate(Variety=factor(Variety))
 rm(plants2015,plants2016)
 
 #Seed data
-allSeeds=bind_rows(transmute(seeds2015,Year,Field,Distance,EdgeCent,EdgeDir,Variety,VegMass,SeedMass,Branch,Pods,Missing,Pod,PodCount,PodMass,lbee=Leafbee,hbee=Honeybee,TotalTime=5),
-                   transmute(seeds2016,Year,Field,Distance,EdgeCent,EdgeDir,Variety,VegMass,SeedMass,Branch,Pods,Missing,Pod,PodCount,PodMass,lbee=Leafcutterbee,hbee=HoneybeeNectar+HoneybeePollen,TotalTime=10))
[…]

### 2023-02-09 yield path analysis commodity.R

@@ -15,7 +15,7 @@ prestheme=theme(legend.position='right',
                 axis.title=element_text(size=20),
                 title=element_text(size=20),
                 panel.grid.major=element_blank(),panel.grid.minor=element_blank(),
-                panel.border=element_rect(size=1,colour='black'),
+                panel.border=element_rect(linewidth=1,colour='black'),
                 strip.text=element_text(size=15))
 theme_set(theme_bw()+prestheme) #Sets graph theme to B/Ws + prestheme
 rm(prestheme)

### 2023-02-09 Manuscript/manuscript_files/figures.tex

@@
 
-Figure 2: Partial effect of distance from a) honey bee apiaries (at edge of the field), b) leafcutter shelters, and c) female bay position on visitation rates, with shaded regions and line ranges showing 95\% CIs.
+Figure 2: Partial effect of distance from a) honey bee apiaries (at edge of the field), b) leafcutting bee shelters, and c) female bay position on visitation rates, with shaded regions and line ranges showing 95\% CIs.
 Commodity fields are shown at a stocking rate of 40 hives (black line), while stocking rates are at 160 hives in seed fields (yellow line).
@@
 
-Figure 5: Simulated effect of honey bee distance and leafcutter distance on seed size (mg/seed, first column) and total yield (tonnes/hectare, second column), using coefficients from paths for simulation.
+Figure 5: Simulated effect of honey bee apiary distance and leafcutting bee shelter distance on seed size (mg/seed, first column) and total yield (tonnes/hectare, second column), using coefficients from paths for simulation.
 Shaded areas shown in a \& b are 95\% quantiles for the simulations.
